### 2016-01-21 thesis/thesis.tex
First commit

%%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\bibliographystyle{plain}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{listings,jlisting}
\lstset{%
    language={},
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\ttfamily},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

\title{mruby Bytecode Loader Using Bluetooth Supported Multi-VM}
\author{Takuro Yamamoto}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to its complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to execute effectively multiple mruby programs in concurrent or/and parallel.
In this paper, to improve the development efficiency, the Bluetooth Loader that transferres bytecodes of mruby applications is implemented as an extension of mruby on TECS.
In addition, multiple mruby programs run cooperatively in the proposed framework.
This paper demonstrates the advantages of the proposed framework with experimental results.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

An approach of efficient software development is to use component-based techniques.
CBD (Component-Based Development) is a design technique for constituting reusable components \cite{Crnkovic:2005:CSE:1062455.1062631}.
Complex and large scale software systems can be developed efficiently using component-based techniques.
That is because software componentization provides high-reusability and easy verification.
It also makes a system flexible in extensions and specification changes.

In addition, another approach of efficient software development is to develop with script languages.
Most of current software are programmed in C language, and the development with C takes a high cost and more time to develop.
Script languages make software engineering more efficient and shorten a development period because script languages have high-productivity from their usability.
Java script, Perl, Python, Lua and Ruby are well-known as representative script languages.

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as worst-execution time, response time are very important factors.
That is why it is difficult to apply the script languages to embedded systems.

mruby on TECS is a component-based framework for running script program \cite{7153813}.
It is integrated two technologies.
One is mruby, which is a script language for embedded systems \cite{5959588}.
The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{4208825}.
TECS supports to effectively run mruby script language on embedded systems.
It also makes execution time 100 times faster than that of mruby.

This paper proposes two additional functions of mruby on TECS, Bluetooth Loader and user-friendly multithread.
mruby on TECS has some problems at present.
One of these is that working efficiency is low because only supports a SD card in mruby on TECS platform for LEGO MINDSTORMS EV3 to load mruby programs.
In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
If a new function, Bluetooth Loader, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
It can improve the efficiency.
Moreover, in the current system if users attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by users.
In addition users must prepare as many VMs as the number of threads because a RiteVM supports only a thread.
Thus that is a big burden on users.
Another new function enables users to run a multithread programs more easily.
Specifically, a cycle handler of switching tasks is implemented.
This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
\\

{\bf Contributions}
\begin{enumerate}
\item Improve the work efficiency in development: \mbox{}\\
\ Bluetooth Loader helps users develop software.
Users do not need to insert and pull out repeatedly, and that improves the software development efficiency.
\item Implement multithreads in mruby on TECS: \mbox{}\\
\ There is a probrem in multithreading of the current mruby on TECS.
It is that users need to be well acquainted the RTOS if multiple mruby programs execute in multithreading. 
In this proposed framework, it is easy for users to use multithreading because multiple tasks are switched cyclically.
Users can easily program multithreading.
Multithreaded programing makes the range of software expand.
\end{enumerate}

The paper is organized as follows:
Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
Section \ref{sec:Bluetooth Loader} and Section \ref{sec:Multithread} describe the design and implementation of the proposed framework in detail.
Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.

\section{Background}
\label{sec:Background}
Figure \ref{fig:proposed} shows the system proposed in this paper.
The bytecodes are transferred from the host to the target device with Bluetooth.
The RiteVMs and mruby library are assumed to be prepared in advance.
Each bytecode are allocated respectively with its own RiteVM.
Users can run some bytecodes transferred with Bluetooth Loader in multi-thread.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
    \caption{Proposed Framework}
    \label{fig:proposed}
\end{figure}

This section describes the basic technology, which is mruby on TECS, a component-based framework for running script programs.
In mruby on TECS two technologies are used, mruby and TECS which are the basis for mruby on TECS.
To explain the system, mruby and TECS are also respectively described in this section.

\subsection{mruby}
\label{sec:mruby}
mruby is the light-weight implementation of Ruby programming language complying to part of the ISO standard.

Ruby is a object-oriented script language.
As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
Ruby can run a program with fewer code lines than C language.
Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.

mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
In addition VM (Virtual Machine) mechanism is used in mruby, so mruby programs can run on any operating system as long as VM is implemented.
RiteVM is a VM in mruby, that runs mruby programs.
The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates a mruby code into a bytecode, which is a intermidiate code that can be interpreted by RiteVM.
The bytecodes can run on a Rite VM, thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{Mechanism of mruby/RiteVM}
    \label{fig:mruby}
\end{figure}

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS help decrease the complexity and difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase the productivity and reduce development duplication  because a common part of software is regarded as a component.

The component deployment and composition in TECS are statically performed, which gives optimization.
As a result, the overheads of execution time and memory consumption can be reduced.
There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.

\subsubsection{Component Model}\mbox{}\\

Figure \ref{fig:component} shows a component diagram.
A {\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
Functions of a {\it cell} are implemented in the C language.

A type of a {\it entry}/{\it call} port is defined by a {\it signature} which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it call} port of a {\it cell} can be connected to the {\it entry} port of another {\it cell} with the same {\it signature}.
A {\it celltype} is the definition of a {\it cell}.
{\it Celltype} defines one or more {\it call}/{\it entry} ports, attributes and internal variables.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Description}\mbox{}\\

The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
The component description in TECS is mentioned with an example shown in Figure \ref{fig:component} as follow.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} description defines an interface of a {\it cell}.
        A {\it signature} name is described following the keyword {\it signature}.
        It also has the prefix ``s".
        In this way, a {\it signature} is defined such as sMotor shown in Figure \ref{signature}.
        To make the definition of an interface clear, specifiers such as in and out are used in TECS.
        [in] and [out] represent input and output, respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor{
    int32_t getCounts(void);
    ER resetCounts(void);
    ER setPower([in]int power);
    ER stop([in] bool_t brake);
    ER rotate([in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking);
    void initializePort([in]int32_t type);
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}

    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
        In the same way, {\it call} ports can be declared.
        Attributes and valuables follow the keyword attr and var respectively.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller{
    call sMotor cMotor;
};

celltype tMotor{
    entry sMotor eMotor;
    attr{
        int32_t attr = 100;
    };
    var{
        int32_t var;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}

    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
        To compose {\it cell}s a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor{
};

cell tCaller Caller{
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

\end{description}

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running script language.
This framework uses two technologies, mruby and TECS.

\subsubsection{System Model}\mbox{}\\

The system model of mruby on TECS is shown in Figure \ref{fig:system_model}.
Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge plays a role to call a native program (e.g.,C legacy code) from an mruby program.
The mruby-TECS bridge provides native libraries for mruby.
It also gives TECS components to receive the invocation from an mruby program.
The mruby-TECS bridge is described in more detail bellow.

As the target RTOS, TOPPERS/HRP2 \cite{6913200} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{6332346} and TOPPERS/ASP.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{System Model}
    \label{fig:system_model}
\end{figure}

\subsubsection{mruby-TECS Bridge}\mbox{}\\

There is a great difference between the execution time of mruby and C language.
According to  \cite{7153813}, mruby programs are several hundreds times slower than C programs.
The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
Thus it is difficult to use mruby for all of code.

The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of code run quickly.

Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.pdf}
    \caption{mruby-TECS Bridge}
    \label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates two things.
One is a {\it celltype} to receive invocation from the mruby program.
The other thing is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.

A code of an mruby-TECS bridge is generated.
The generation code supports registration of classes and methods for mruby.
The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in a mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

\section{Bluetooth Loader}
\label{sec:Bluetooth Loader}
This section describes an additional function of mruby on TECS, Bluetooth Loader.
In the current system, all binary data including bytecodes are in a SD card.
Users must insert and pull out the SD card every time the source program are modified.
It causes a low work efficiency that such a work must be repeated.
In the system with Bluetooth Loader, the users' burden can be reduced.
The work that a SD card is in and out needs to be done just once in the beginning.

The development flow using Bluetooth Loader is shown in Figure \ref{fig:bluetooth_loader}.
The RiteVM and mruby library are compiled and copied in the SD card at the first.
These are assumed not to be modified.
The binary data transferred with Bluetooth is the bytecode of the main source.
In the host, the source files, which is identified by the .rb extension, are edited and compiled into the bytecodes by a mruby compiler.
The generated bytecodes are transferred from the host to the target device with Bluetooth.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
    \caption{Development Flow using Bluetooth Loader}
    \label{fig:bluetooth_loader}
\end{figure}

\subsection{Component of Bluetooth Loader}
The proposed framework provides components of Bluetooth Loader to use the function.
A component of Bluetooth Loader is an extension of the RiteVM component, which is described in \cite{7153813}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
This bytecode in the build description means that prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
TOPPERS/HRP2 is described in \cite{6913200}.
The MrubyBluetooth1 is a component of Bluetooth Loader.
A bytecode which is a compiled mruby program in the host is transferred and received at the top of the Bluetooth Loader component.
In this framework, ZMODEM \cite{forsberg1988zmodem} is used as a binary transfer protocol.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
    \caption{Component Diagram of Bluetooth Loader}
    \label{fig:component_bluetooth}
\end{figure}

Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of Bluetooth Loader, which is like MrubyBluetooth1.
First, a pointer of mrb\_state structure is initialized.
mrb\_state is a set of states and global variables used in mruby.
Second, the bytecode of mruby libraries is read.
mruby libraries are a set of Ruby classes such as motor class and sensor class.
For example, motor class defines methods to rotate and stop a motor.
The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: mrubyFile and irep.
Here, the mrubyFile indicates the program files of mruby libraries.
[omit] is only used for the TECS generator, thus the attribute, mrubyFile, does not consume memory.
The irep is the pointer of the array stored the bytecode of mruby libraries.
In short the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
Third, the bytecode of the mruby program transferred with Bluetooth is read .
The bytecode transmitted via Bluetooth is stored in an array of type uint8\_t, which is the same as type char.
The array is different from that of holding the mruby library bytecode.
Two bytecodes are read separately in the mrb\_state.
Finally, a mruby task runs.
When the mruby program is modified, only the bytecode of the modified program should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of Bluetooth Loader}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep=C_EXP("&$cell_global$_irep");
    };
}; 
\end{lstlisting}
\caption{Celltype Description for Bluetooth Loader}
\label{celltype_mrubybluetooth}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main(CELLIDX idx)
{
  /* Receive the bytecode via Bluetooth */
  test_serial_loader(SIO_PORT_BT);

  /* Declaration variables */
  CELLCB	*p_cellcb;
  mrb_state *mrb;
  mrbc_context *c;

  if (VALID_IDX(idx)) {
    p_cellcb = GET_CELLCB(idx);
  }

  /* New interpreter instance */
  mrb = mrb_open();
  if (mrb == NULL) {
  //cSerialPort_write("Invalid mrb_state, exiting test driver\n", 39);
    return;
  }
  /* New */
  c = mrbc_context_new(mrb);

  if(is_cInit_joined()){
    // TECS Bridge
    cInit_initializeBridge( mrb );
  }

  /* Load mruby liblary bytecode and run */
  mrb_load_irep_cxt(mrb, ATTR_irep, c);
  /* Load main mruby bytecode and run */
  mrb_load_irep_cxt(mrb, app_binary_buf, c);

  if (mrb->exc) {
    mrb_p(mrb, mrb_obj_value(mrb->exc));
    exit(0);
  }
  /* Free */ 
  mrbc_context_free(mrb, c);
  /* Free interpreter instance */
  mrb_close(mrb);
}

\end{lstlisting}
\caption{Main code for Bluetooth Loader}
\label{maincode_mrubybluetooth}
\end{figure}
\section{Multi-thread}
\label{sec:Multithread}
This section describes implementation of multithreading in the proposed framework.
mruby on TECS has supported multithreading.
However, multithread processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for users.
In the proposed framework, multithread processing is user-friendly because users do not need the knowledge than before.
A cyclic handler that switches tasks is implemented, and that enables users to develop applications without concern for multithreading.

 \subsection{rot\_rdq}
The case is assumed that there are two tasks with the same priority, and both are in a infinite loop.
In the current system, when one task is executed first, another task would not be executed.
That is because the task with first execution runs in a loop.

The rot\_rdq is a service call of $\mu$ITRON.
When rot\_rdq is called, tasks with the same priority are switched as shown Figure \ref{fig:rot_rdq}.
The argument of rot\_rdq is the priority.

The rot\_rdq can be performed if the number of tasks is more than two.
For example, three tasks are in the order: task 1, 2 and 3.
In this case, the order is changed, task 2, 3 and 1, when the rot\_rdq is called.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/rot_rdq.pdf}
    \caption{rot\_rdq}
    \label{fig:rot_rdq}
\end{figure}

\subsection{Component of Cyclic Handler}
Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
CyclicHandler {\it cell} configurates the cyclic handler based on ITRON.
Cyclic handlers based on ITRON are described in detail [].
The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
Here, rot\_rdq is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port which is connected tkernel.eiKernel to call functions of the kernel, an {\it entry} port and an attribute, priority.
The attribute, priority is used as an arguments of rot\_rdq.

Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
In this case, the cyclic handler is executed when it is generated because the attribute is TA\_STA.
Also, the cyclic handler is executed every 100 microseconds.
In another part, the priority of CyclicMain {\it cell} is described.
EV3\_MRUBY\_VM\_PRIORITY defines the priority of mruby tasks.
In the main of CyclicMain, rot\_rdq is implemented and the priority is passed as the argument.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
    \caption{Component Diagram of Cyclic Handler}
    \label{fig:cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
celltype tCyclicHandler {
    [inline] entry sCyclic eCyclic;
    call  siHandlerBody  ciBody; 
    attr {
    	ID     id = C_EXP( "CYCHDLRID_$id$" );
    	[omit] ATR    attribute = C_EXP("TA_NULL");
    	[omit] RELTIM cyclicTime;
    	[omit] RELTIM cyclicPhase = 0;
        [omit] ACPTN  accessPattern[4] = 
            { C_EXP("OMIT"), C_EXP("OMIT"), C_EXP("OMIT"), C_EXP("OMIT") };
    };
    FACTORY{
    	write( "tecsgen.cfg",
            "#include \"$ct$_tecsgen.h\"" );
    	write( "$ct$_factory.h",
            "#include \"kernel_cfg.h\"" );
    };
};

celltype tCyclicMain{
    require tKernel.eiKernel;
    entry siHandlerBody eiBody;
    attr {
        PRI priority;
    };
};
    \end{lstlisting}
    \caption{Celltype Description of Cyclic Handler}
    \label{celltype_cyclic_handler}
\end{figure}

\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tCyclicHandler CyclicHandler{
    ciBody = CyclicMain.eiBody;
    attribute = C_EXP("TA_STA");
    cyclicTime = 100;
    cyclicPhase = 0;
};

cell tCyclicMain CyclicMain{
    priority = 
        C_EXP("EV3_MRUBY_VM_PRIORITY");
};
   \end{lstlisting}
    \caption{Build Description of Cyclic Handler}
    \label{build_cyclic_handler}
\end{figure}

\section{Evaluation}
\label{sec:Evaluation}
To analyze the advantages and disadvantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
        \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
        \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
        \item the comparison of the application execution time with singlethreading, co-routine and multithreading.
\end{itemize}

This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.1.0.

\section{Related work}
\label{sec:Related work}

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccc}
        & Bluetooth & \shortstack{Preemptive-multithread\\(multiVM)} & \shortstack{Nonpreemptive-multithread\\(co-routine)} & GIL \\ \hline
        mruby on TECS& & \checkmark & \checkmark & \\
        mruby & & & \checkmark &\\
        Owl system & & \checkmark & & \checkmark \\
        Lua & & \checkmark & \checkmark \\
        Proposed framework& \checkmark & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparion}
\end{table*}
The open-source run-time systems for scripting languages have been developed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}

mruby on TECS is a component-based framework for running mruby programs.
The programs on mruby-on-TECS can execute about one hundred times faster than the mruby programs.
Software can be also developed with component base by mruby on TECS.
However, despite the fact that multithreading has been supported in the current mruby on TECS, users need to be familiar with functions of a RTOS to use multithreading.
The co-routine is supported as same as mruby.

mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
mruby has supported co-routine, but not supported multithreading for RTOSs.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip [].
python-on-a-chip supports multithread managed by GIL (Global Interpreter Lock).
GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
GIL leads the limitation of the concurrency on multithreading.

Lua is one of the most popular script languages for embedded systems.
Lua supports co-routines, referred to collaborative multithreading.
A co-routine in Lua is used as an independently executed thread.
A co-routine can just suspend and resume multiple routines. 
Thus, a Lua co-routine is not like multithreads in multithread systems.

Table \ref{tab:comparion} shows a comparison between the proposed work and previous works.

\section{Conclusion}
\label{sec:Conclusion}

%&=& &=& &=& 
% Reference
%&=& &=& &=& 
\bibliography{ref.bib}

\end{document}

### 2016-01-21 thesis/thesis.tex
update

@@
 For embedded systems, the real-time properties such as worst-execution time, response time are very important factors.
-That is why it is difficult to apply the script languages to embedded systems.
+Therefore, it is difficult to apply the script languages to embedded systems.
 
@@
 TECS supports to effectively run mruby script language on embedded systems.
-It also makes execution time 100 times faster than that of mruby.
+mruby on TECS also makes execution time 100 times faster than that of mruby.
 
@@
 mruby on TECS has some problems at present.
-One of these is that working efficiency is low because only supports a SD card in mruby on TECS platform for LEGO MINDSTORMS EV3 to load mruby programs.
+One of these is that working efficiency is low because mruby on TECS only supports a SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
 In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
@@
 Moreover, in the current system if users attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by users.
-In addition users must prepare as many VMs as the number of threads because a RiteVM supports only a thread.
+In addition users must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
 Thus that is a big burden on users.
@@
 The RiteVMs and mruby library are assumed to be prepared in advance.
-Each bytecode are allocated respectively with its own RiteVM.
+Each bytecode is allocated respectively with its own RiteVM.
 Users can run some bytecodes transferred with Bluetooth Loader in multi-thread.
@@
 This section describes the basic technology, which is mruby on TECS, a component-based framework for running script programs.
-In mruby on TECS two technologies are used, mruby and TECS which are the basis for mruby on TECS.
+In mruby on TECS, two technologies are used, mruby and TECS which are the basis for mruby on TECS.
 To explain the system, mruby and TECS are also respectively described in this section.
@@
 TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS help decrease the complexity and difficulty because the generated component diagram can visualize the structure of whole software.
+TECS helps decrease the complexity and difficulty because the generated component diagram can visualize the structure of whole software.
 It can also help increase the productivity and reduce development duplication  because a common part of software is regarded as a component.
@@
 However, multithread processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for users.
-In the proposed framework, multithread processing is user-friendly because users do not need the knowledge than before.
+In the proposed framework, multithread processing is user-friendly because users need the less knowledge than before.
 A cyclic handler that switches tasks is implemented, and that enables users to develop applications without concern for multithreading.
@@
 mruby on TECS is a component-based framework for running mruby programs.
-The programs on mruby-on-TECS can execute about one hundred times faster than the mruby programs.
+The programs on mruby-on-TECS can execute about 100 times faster than the mruby programs.
 Software can be also developed with component base by mruby on TECS.
-However, despite the fact that multithreading has been supported in the current mruby on TECS, users need to be familiar with functions of a RTOS to use multithreading.
+Although multithreading has been supported in the current mruby on TECS, users need to be familiar with functions of a RTOS to use multithreading.
 The co-routine is supported as same as mruby.

### 2016-01-23 thesis/thesis.tex
modify remarks

@@
-%%
+%
 % File: thesis.tex
@@
 
-\title{mruby Bytecode Loader Using Bluetooth Supported Multi-VM}
+\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
 \author{Takuro Yamamoto}
@@
 \begin{abstract}
-In recent years, the productivity of embedded systems has become a problem due to its complexity and large-scale.
+In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
 For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
 In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to execute effectively multiple mruby programs in concurrent or/and parallel.
-In this paper, to improve the development efficiency, the Bluetooth Loader that transferres bytecodes of mruby applications is implemented as an extension of mruby on TECS.
+Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
+In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
 In addition, multiple mruby programs run cooperatively in the proposed framework.
-This paper demonstrates the advantages of the proposed framework with experimental results.
+Experimental results demonstrates the advantages of the proposed framework.
 \end{abstract}
@@
 
-This paper proposes two additional functions of mruby on TECS, Bluetooth Loader and user-friendly multithread.
+This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
 mruby on TECS has some problems at present.
@@
 In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
-If a new function, Bluetooth Loader, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
+If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
 It can improve the efficiency.
-Moreover, in the current system if users attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by users.
-In addition users must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
-Thus that is a big burden on users.
-Another new function enables users to run a multithread programs more easily.
+Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
+In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
+Thus that is a big burden on developers.
+Another new feature enables developers to run a multitask programs more easily.
 Specifically, a cycle handler of switching tasks is implemented.
@@
 \begin{enumerate}
-\item Improve the work efficiency in development: \mbox{}\\
-\ Bluetooth Loader helps users develop software.
-Users do not need to insert and pull out repeatedly, and that improves the software development efficiency.
-\item Implement multithreads in mruby on TECS: \mbox{}\\
-\ There is a probrem in multithreading of the current mruby on TECS.
-It is that users need to be well acquainted the RTOS if multiple mruby programs execute in multithreading. 
-In this proposed framework, it is easy for users to use multithreading because multiple tasks are switched cyclically.
-Users can easily program multithreading.
-Multithreaded programing makes the range of software expand.
+\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
+\ mruby bytecode loader using Bluetooth helps developers develop software.
+Developers do not need to insert and pull out repeatedly, and that improves the software development efficiency.
+\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
+\ There is a probrem in multitasking of the current mruby on TECS.
+It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
+In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
+Developers can easily program multitasking.
+Multitasked programing makes the range of software expand.
 \end{enumerate}
@@
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:Bluetooth Loader} and Section \ref{sec:Multithread} describe the design and implementation of the proposed framework in detail.
+Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
 Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.
@@
 \label{sec:Background}
-Figure \ref{fig:proposed} shows the system proposed in this paper.
+Figure \ref{fig:proposed} shows a system model of the proposed framework.
 The bytecodes are transferred from the host to the target device with Bluetooth.
 The RiteVMs and mruby library are assumed to be prepared in advance.
-Each bytecode is allocated respectively with its own RiteVM.
-Users can run some bytecodes transferred with Bluetooth Loader in multi-thread.
+Each bytecode is allocated to a RiteVM, respectively.
+Developers can run some bytecodes transferred with Bluetooth in multitask.
 
@@
     \includegraphics[width=8cm,clip]{figure/proposed.pdf}
-    \caption{Proposed Framework}
+    \caption{System Model}
     \label{fig:proposed}
@@
 
-This section describes the basic technology, which is mruby on TECS, a component-based framework for running script programs.
-In mruby on TECS, two technologies are used, mruby and TECS which are the basis for mruby on TECS.
+This section describes mruby on TECS on which the proposed framework is based.
+mruby on TECS is a component-based framework for running script programs.
+In mruby on TECS, two technologies are integrated: mruby and TECS.
 To explain the system, mruby and TECS are also respectively described in this section.
@@
 The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates a mruby code into a bytecode, which is a intermidiate code that can be interpreted by RiteVM.
+The mruby compiler translates a mruby code into a bytecode, which is an intermidiate code that can be interpreted by RiteVM.
 The bytecodes can run on a Rite VM, thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
@@
 
-\section{Bluetooth Loader}
-\label{sec:Bluetooth Loader}
-This section describes an additional function of mruby on TECS, Bluetooth Loader.
+\section{mruby Bytecode Loader Using Bluetooth}
+\label{sec:mruby bytecode loader using Bluetooth}
+This section describes an additional function of mruby on TECS, mruby bytecode loader using Bluetooth.
 In the current system, all binary data including bytecodes are in a SD card.
-Users must insert and pull out the SD card every time the source program are modified.
+Developers must insert and pull out the SD card every time the source program are modified.
 It causes a low work efficiency that such a work must be repeated.
-In the system with Bluetooth Loader, the users' burden can be reduced.
+mruby bytecode loader using Bluetooth makes the developers' burden decrease.
 The work that a SD card is in and out needs to be done just once in the beginning.
 
-The development flow using Bluetooth Loader is shown in Figure \ref{fig:bluetooth_loader}.
+The development flow in mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
 The RiteVM and mruby library are compiled and copied in the SD card at the first.
@@
     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
-    \caption{Development Flow using Bluetooth Loader}
+    \caption{Development Flow in mruby bytecode loader using Bluetooth}
     \label{fig:bluetooth_loader}
@@
 
-\subsection{Component of Bluetooth Loader}
-The proposed framework provides components of Bluetooth Loader to use the function.
-A component of Bluetooth Loader is an extension of the RiteVM component, which is described in \cite{7153813}.
+\subsection{Component of mruby bytecode loader using Bluetooth}
+The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
+A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{7153813}.
 The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
@@
 TOPPERS/HRP2 is described in \cite{6913200}.
-The MrubyBluetooth1 is a component of Bluetooth Loader.
-A bytecode which is a compiled mruby program in the host is transferred and received at the top of the Bluetooth Loader component.
+The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
+A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
 In this framework, ZMODEM \cite{forsberg1988zmodem} is used as a binary transfer protocol.
@@
     \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
-    \caption{Component Diagram of Bluetooth Loader}
+    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
     \label{fig:component_bluetooth}
@@
 
-Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of Bluetooth Loader, which is like MrubyBluetooth1.
+Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of mruby bytecode loader using Bluetooth, which is like MrubyBluetooth1.
 First, a pointer of mrb\_state structure is initialized.
@@
     \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
-    \caption{Control Flow of Bluetooth Loader}
+    \caption{Control Flow of mruby bytecode loader using Bluetooth}
     \label{fig:control_flow}
@@
 \end{lstlisting}
-\caption{Celltype Description for Bluetooth Loader}
+\caption{Celltype Description for mruby bytecode loader using Bluetooth}
 \label{celltype_mrubybluetooth}
@@
   /* Receive the bytecode via Bluetooth */
-  test_serial_loader(SIO_PORT_BT);
+  serial_loader(SIO_PORT_BT);
 
@@
   if (mrb == NULL) {
-  //cSerialPort_write("Invalid mrb_state, exiting test driver\n", 39);
+    /* Invalid mrb_state */
     return;
   }
-  /* New */
+  /* New mruby context */
   c = mrbc_context_new(mrb);
@@
   if(is_cInit_joined()){
-    // TECS Bridge
+    /* Initialization of mruby TECS Bridge */
     cInit_initializeBridge( mrb );
@@
   mrb_load_irep_cxt(mrb, ATTR_irep, c);
-  /* Load main mruby bytecode and run */
+  /* Load mruby application bytecode and run */
   mrb_load_irep_cxt(mrb, app_binary_buf, c);
@@
   if (mrb->exc) {
+    /* Failure to execute */
     mrb_p(mrb, mrb_obj_value(mrb->exc));
@@
   }
-  /* Free */ 
+  /* Free mruby context */ 
   mrbc_context_free(mrb, c);
@@
 \end{lstlisting}
-\caption{Main code for Bluetooth Loader}
+\caption{Main code for mruby bytecode loader using Bluetooth}
 \label{maincode_mrubybluetooth}
 \end{figure}
-\section{Multi-thread}
-\label{sec:Multithread}
-This section describes implementation of multithreading in the proposed framework.
-mruby on TECS has supported multithreading.
-However, multithread processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for users.
-In the proposed framework, multithread processing is user-friendly because users need the less knowledge than before.
-A cyclic handler that switches tasks is implemented, and that enables users to develop applications without concern for multithreading.
+\section{Multitask}
+\label{sec:Multitask}
+This section describes implementation of multitasking in the proposed framework.
+mruby on TECS has supported multitasking.
+However, multitask processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for developers.
+In the proposed framework, multitask processing is user-friendly because developers need the less knowledge than before.
+A cyclic handler that switches tasks is implemented, and that enables developers to develop applications without concern for multitasking.
 
@@
 In this case, the cyclic handler is executed when it is generated because the attribute is TA\_STA.
-Also, the cyclic handler is executed every 100 microseconds.
+The cyclic handler is executed every 1 msec.
 In another part, the priority of CyclicMain {\it cell} is described.
@@
     };
-    FACTORY{
-    	write( "tecsgen.cfg",
-            "#include \"$ct$_tecsgen.h\"" );
-    	write( "$ct$_factory.h",
-            "#include \"kernel_cfg.h\"" );
-    };
 };
@@
     attribute = C_EXP("TA_STA");
-    cyclicTime = 100;
+    cyclicTime = 1;
     cyclicPhase = 0;
@@
         \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
-        \item the comparison of the application execution time with singlethreading, co-routine and multithreading.
+        \item the comparison of the application execution time with singletasking, co-routine and multitasking.
 \end{itemize}
@@
     \begin{tabular}{c||c|ccc}
-        & Bluetooth & \shortstack{Preemptive-multithread\\(multiVM)} & \shortstack{Nonpreemptive-multithread\\(co-routine)} & GIL \\ \hline
+        & \shortstack{mruby bytecode loader\\using Bluetooth} & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
         mruby on TECS& & \checkmark & \checkmark & \\
@@
 Software can be also developed with component base by mruby on TECS.
-Although multithreading has been supported in the current mruby on TECS, users need to be familiar with functions of a RTOS to use multithreading.
+Although multitasking has been supported in the current mruby on TECS, developers need to be familiar with functions of a RTOS to use multitasking.
 The co-routine is supported as same as mruby.
@@
 mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
-mruby has supported co-routine, but not supported multithreading for RTOSs.
+mruby has supported co-routine, but not supported multitasking for RTOSs.
 
@@
 The interpreter of the Owl system is the same as that of python-on-a-chip [].
-python-on-a-chip supports multithread managed by GIL (Global Interpreter Lock).
+python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
 GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
-GIL leads the limitation of the concurrency on multithreading.
+GIL leads the limitation of the concurrency on multitasking.
 
 Lua is one of the most popular script languages for embedded systems.
-Lua supports co-routines, referred to collaborative multithreading.
+Lua supports co-routines, referred to collaborative multitasking.
 A co-routine in Lua is used as an independently executed thread.
 A co-routine can just suspend and resume multiple routines. 
-Thus, a Lua co-routine is not like multithreads in multithread systems.
+Thus, a Lua co-routine is not like multitasks in multitask systems.
 
-Table \ref{tab:comparion} shows a comparison between the proposed work and previous works.
+Table \ref{tab:comparion} shows a comparison between the proposed framework and previous work.
 

### 2016-01-25 thesis/diff/0125_thesis.tex
add diff

--- 2016-01-23 thesis/thesis.tex
@@
 \maketitle
-
 \begin{abstract}
@@
 This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
-\\
 
-{\bf Contributions}
+{\bf Contribution}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
+The proposed framework gives the contribution in the following points. 
 \begin{enumerate}
@@
 \ mruby bytecode loader using Bluetooth helps developers develop software.
-Developers do not need to insert and pull out repeatedly, and that improves the software development efficiency.
+Developers do not need to insert and pull out repeatedly and also to restart an OS.
+Thus, the software development efficiency is improved.
 \item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
@@
 
-The paper is organized as follows:
+{\bf Organization}: The paper is organized as follows.
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
@@
 \label{sec:Evaluation}
+This section mentions experimental results and their consideration.
 To analyze the advantages and disadvantages of the proposed framework, the evaluations are performed as follows.
@@
 
+The 100,000 times loop program is used as mruby application for evaluation.
+In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
+
+The comparison of the application execution time with singletasking, co-routine and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is 1 msec.
+Co-routine takes twice the time of singletask to execute an mruby application.
+On the other hands, multitasking's execution time is about the same as singletasking's.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
+    \caption{Comparison of the application execution time with singletask, co-routine and multitask}
+    \label{fig:comparison_s_c_m}
+\end{figure}
+
 \section{Related work}
@@
     \begin{tabular}{c||c|ccc}
-        & \shortstack{mruby bytecode loader\\using Bluetooth} & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
-        mruby on TECS& & \checkmark & \checkmark & \\
-        mruby & & & \checkmark &\\
-        Owl system & & \checkmark & & \checkmark \\
-        Lua & & \checkmark & \checkmark \\
-        Proposed framework& \checkmark & \checkmark & \checkmark \\
+        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
+        mruby on TECS     &            & \checkmark & \checkmark &            \\
+        mruby             &            &            & \checkmark &            \\
+        Owl system        &            & -          & -          & \checkmark \\
+        Lua               &            & -          & \checkmark &            \\
+        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
     \end{tabular}
@@
 \label{sec:Conclusion}
+This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
+The proposed framework provides developers the efficient development without disconnecting a SD card and restarting an OS.
+Furthermore, the proposed user-friendly multitasking can be used as the same as singletasking because of the low overhead.
 
-%&=& &=& &=& 
-% Reference
-%&=& &=& &=& 
+%%%%%%%%%%%%%
+% Reference %
+%%%%%%%%%%%%%
 \bibliography{ref.bib}

### 2016-01-25 thesis/thesis.tex
update

@@
 \label{sec:Conclusion}
+This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
+The proposed framework provides developers the efficient development without disconnecting a SD card and restarting an OS.
+Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
+In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking shows their advantages.
+The proposed multitasking is compared with singletasking and co-routine.
 
-%&=& &=& &=& 
-% Reference
-%&=& &=& &=& 
+%%%%%%%%%%%%%
+% Reference %
+%%%%%%%%%%%%%
 \bibliography{ref.bib}

### 2016-01-26 thesis/diff/0127_thesis.tex
update

--- 2016-01-25 thesis/thesis.tex
@@
 In addition, multiple mruby programs run cooperatively in the proposed framework.
-Experimental results demonstrates the advantages of the proposed framework.
+Experimental results demonstrate the advantages of the proposed framework.
 \end{abstract}
@@
 \ mruby bytecode loader using Bluetooth helps developers develop software.
-Developers do not need to insert and pull out repeatedly and also to restart an OS.
+Developers do not need to insert and pull out a SD card repeatedly and also to restart an OS.
 Thus, the software development efficiency is improved.
@@
 In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
-Developers can easily program multitasking.
 Multitasked programing makes the range of software expand.
@@
 
-The 100,000 times loop program is used as mruby application for evaluation.
+The 100,000 times loop program is used as mruby application for evaluation of execution time.
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.

### 2016-01-28 thesis/thesis.tex
update

@@
 Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
-In this paper, to improve the development efficiency, the mruby bytecode loader using Bluetooth is implemented as an extension of mruby on TECS.
+To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
 In addition, multiple mruby programs run cooperatively in the proposed framework.
-Experimental results demonstrates the advantages of the proposed framework.
+Experimental results demonstrate the advantages of the proposed framework.
 \end{abstract}
@@
 mruby on TECS has some problems at present.
-One of these is that working efficiency is low because mruby on TECS only supports a SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
+One of these is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
 In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
@@
 
-{\bf Contribution}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
+{\bf Contributions}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
 The proposed framework gives the contribution in the following points. 
@@
 \ mruby bytecode loader using Bluetooth helps developers develop software.
-Developers do not need to insert and pull out repeatedly and also to restart an OS.
+Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
 Thus, the software development efficiency is improved.
 \item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
-\ There is a probrem in multitasking of the current mruby on TECS.
+\ There is a problem in multitasking of the current mruby on TECS.
 It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking. 
 In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
-Developers can easily program multitasking.
 Multitasked programing makes the range of software expand.
@@
 The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates a mruby code into a bytecode, which is an intermidiate code that can be interpreted by RiteVM.
+The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by RiteVM.
 The bytecodes can run on a Rite VM, thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
@@
 The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in a mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
 
@@
 This section describes an additional function of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, all binary data including bytecodes are in a SD card.
+In the current system, all binary data including bytecodes are in an SD card.
 Developers must insert and pull out the SD card every time the source program are modified.
@@
 mruby bytecode loader using Bluetooth makes the developers' burden decrease.
-The work that a SD card is in and out needs to be done just once in the beginning.
+The work that an SD card is in and out needs to be done just once in the beginning.
 
@@
 The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the source files, which is identified by the .rb extension, are edited and compiled into the bytecodes by a mruby compiler.
+In the host, the source files, which is identified by the .rb extension, are edited and compiled into the bytecodes by an mruby compiler.
 The generated bytecodes are transferred from the host to the target device with Bluetooth.
@@
 Two bytecodes are read separately in the mrb\_state.
-Finally, a mruby task runs.
+Finally, an mruby task runs.
 When the mruby program is modified, only the bytecode of the modified program should be transferred.
@@
   /* Receive the bytecode via Bluetooth */
-  serial_loader(SIO_PORT_BT);
+  bluetooth_loader();
 
@@
 
-  /* Load mruby liblary bytecode and run */
+  /* Load mruby library bytecode and run */
   mrb_load_irep_cxt(mrb, ATTR_irep, c);
@@
 The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
-CyclicHandler {\it cell} configurates the cyclic handler based on ITRON.
+CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
 Cyclic handlers based on ITRON are described in detail [].
@@
 In this case, the cyclic handler is executed when it is generated because the attribute is TA\_STA.
-The cyclic handler is executed every 1 msec.
+The cyclic handler is executed every one msec.
 In another part, the priority of CyclicMain {\it cell} is described.
@@
 
-\section{Evaluation}
+\section{Experimental Evaluation}
 \label{sec:Evaluation}
@@
         \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
-        \item the comparison of the application execution time with singletasking, co-routine and multitasking.
+        \item the comparison of the application execution time with singletasking, co-routine, and multitasking.
 \end{itemize}
@@
 
-The 100,000 times loop program is used as mruby application for evaluation.
+The 100,000 times loop program is used as mruby application for evaluation of execution time.
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
 
-The comparison of the application execution time with singletasking, co-routine and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is 1 msec.
+The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
 Co-routine takes twice the time of singletask to execute an mruby application.
@@
     \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
-    \caption{Comparison of the application execution time with singletask, co-routine and multitask}
+    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
     \label{fig:comparison_s_c_m}
@@
         & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
+        Lua               &            & -          & \checkmark &            \\
+        Owl system        &            & -          & -          & \checkmark \\
+        mruby             &            &            & \checkmark &            \\
         mruby on TECS     &            & \checkmark & \checkmark &            \\
-        mruby             &            &            & \checkmark &            \\
-        Owl system        &            & -          & -          & \checkmark \\
-        Lua               &            & -          & \checkmark &            \\
         Proposed framework& \checkmark & \checkmark & \checkmark &            \\
@@
 \end{table*}
-The open-source run-time systems for scripting languages have been developed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}
+The open-source run-time systems for scripting languages have been proposed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}.
 
-mruby on TECS is a component-based framework for running mruby programs.
-The programs on mruby-on-TECS can execute about 100 times faster than the mruby programs.
-Software can be also developed with component base by mruby on TECS.
-Although multitasking has been supported in the current mruby on TECS, developers need to be familiar with functions of a RTOS to use multitasking.
-The co-routine is supported as same as mruby.
-
-mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
-mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
-mruby has supported co-routine, but not supported multitasking for RTOSs.
+Lua is one of the most popular script languages for embedded systems.
+Lua supports co-routines, referred to collaborative multitasking.
+A co-routine in Lua is used as an independently executed thread.
+A co-routine can just suspend and resume multiple routines. 
+Thus, a Lua co-routine is not like multitasks in multitask systems.
 
@@
 
-Lua is one of the most popular script languages for embedded systems.
-Lua supports co-routines, referred to collaborative multitasking.
-A co-routine in Lua is used as an independently executed thread.
-A co-routine can just suspend and resume multiple routines. 
-Thus, a Lua co-routine is not like multitasks in multitask systems.
+mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
+mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
+mruby has supported co-routine, but not supported multitasking for RTOSs.
+
+mruby on TECS is a component-based framework for running mruby programs.
+The programs on mruby-on-TECS can execute about 100 times faster than the mruby programs.
+Software can be also developed with component base by mruby on TECS.
+Although multitasking has been supported in the current mruby on TECS, developers need to be familiar with functions of an RTOS to use multitasking.
+The co-routine is supported as same as mruby.
 
@@
 This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
-The proposed framework provides developers the efficient development without disconnecting a SD card and restarting an OS.
+The proposed framework provides developers the efficient development without disconnecting an SD card and restarting an OS.
 Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.

### 2016-01-31 thesis/thesis.tex
update

@@
 The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
-The component description in TECS is mentioned with an example shown in Figure \ref{fig:component} as follow.
+TECS is written in .cdl file (component description language).
+The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.
 
@@
 Here, the mrubyFile indicates the program files of mruby libraries.
-[omit] is only used for the TECS generator, thus the attribute, mrubyFile, does not consume memory.
+{\it [omit]} is only used for the TECS generator, thus the attribute, mrubyFile, does not consume memory.
 The irep is the pointer of the array stored the bytecode of mruby libraries.
@@
 However, multitask processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for developers.
-In the proposed framework, multitask processing is user-friendly because developers need the less knowledge than before.
-A cyclic handler that switches tasks is implemented, and that enables developers to develop applications without concern for multitasking.
+One of approaches for multitasking is co-routine.
+Co-routines are scheduled by developers with APIs such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
+Besides, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking, but it leaves the scheduling to developers such as co-routine.
+In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
+A cyclic handler calls {\it rotateReadyQueue} that switches tasks, which enables developers to develop applications without concern for multitasking.
 
-\subsection{rot\_rdq}
+\subsection{rotateReadyQueue}
 The case is assumed that there are two tasks with the same priority, and both are in a infinite loop.
@@
 
-The rot\_rdq is a service call of $\mu$ITRON.
-When rot\_rdq is called, tasks with the same priority are switched as shown Figure \ref{fig:rot_rdq}.
-The argument of rot\_rdq is the priority.
+The {\it rotateReadyQueue} is a service call of $\mu$ITRON.
+When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown Figure \ref{fig:rotateReadyQueue}.
+The argument of {\it rotateReadyQueue} is the priority.
 
-The rot\_rdq can be performed if the number of tasks is more than two.
+The {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
 For example, three tasks are in the order: task 1, 2 and 3.
-In this case, the order is changed, task 2, 3 and 1, when the rot\_rdq is called.
+In this case, the order is changed, task 2, 3 and 1, when the {\it rotateReadyQueue} is called.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/rot_rdq.pdf}
-    \caption{rot\_rdq}
-    \label{fig:rot_rdq}
+    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
+    \caption{rotateReadyQueue}
+    \label{fig:rotateReadyQueue}
 \end{figure}
@@
 CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
-Here, rot\_rdq is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port which is connected tkernel.eiKernel to call functions of the kernel, an {\it entry} port and an attribute, priority.
-The attribute, priority is used as an arguments of rot\_rdq.
+Here, {\it rotateReadyQueue} is implemented as the body.
+Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port which is connected {\it tkernel.eiKernel} to call functions of the kernel, an {\it entry} port and an attribute, priority.
+The attribute, priority is used as an arguments of {\it rotateReadyQueue}.
 
@@
 EV3\_MRUBY\_VM\_PRIORITY defines the priority of mruby tasks.
-In the main of CyclicMain, rot\_rdq is implemented and the priority is passed as the argument.
+In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
+If developers do not need the cyclic handler, the .cdl files shown as Figure \ref{celltype_cyclic_handler}, \ref{build_cyclic_handler} should be commented out such as {\it //import($<$**.cdl$>$);}.
+This ease comes from component-based development with TECS.
 
@@
 \end{figure}
-
 \begin{figure}[t]
@@
 
+\subsection{Synchronization of Multiple Tasks}
+In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
+Eventflag, one of synchronous processing, is applied to synchronize the starting of multiple mruby applications.
+Each task sets the flag pattern such as 0x01 (01) and 0x02 (10), and then waits the flag pattern, 0x3 (11), with AND.
+This process can also apply to the case of the more tasks.
+For example, in the case of the four tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND.
+In the proposed framework, the set pattern and wait pattern is defined as attributes of the component.
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without if statements.
+The components of eventflag are built with {\it [optional]} in TECS.
+{\it [optional]} means that the codes are run only when the call port is connected.
+The same file can be used even if developers would not like to use eventflag.
+In other words, it is not necessary to compile/link the different file.
+These features are also advantages of component-based development.
+
 \section{Experimental Evaluation}
@@
         \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
-        \item the comparison of the overheads for each cyclic period of calling rot\_rdq.
+        \item the comparison of the overheads for each cyclic period of calling {\it rotateReadyQueue}.
         \item the comparison of the application execution time with singletasking, co-routine, and multitasking.
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
+    \caption{Comparison of the overheads for each cyclic period of calling rotateReadyQueue}
+    \label{fig:comparison_msec}
+\end{figure}
+
 The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
@@
 On the other hands, multitasking's execution time is about the same as singletasking's.
+Switching tasks's overhead is also evaluated, that is about three micro seconds on average.
+Therefore, the overheads of multitasking is 1 \% or less because the number of switching tasks is about 500.
 

### 2016-02-05 thesis/diff/0203_thesis.tex
update

--- 2016-01-31 thesis/thesis.tex
@@
 \documentclass[conference,compsoc]{IEEEtran}
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtranBST2/IEEEtran}
 \usepackage[dvipdfmx]{graphicx}
@@
 To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
+The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
+mruby application bytecode modified frequently is sent from a host to a target device by developers.
+mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compailation.
 In addition, multiple mruby programs run cooperatively in the proposed framework.
+In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
 Experimental results demonstrate the advantages of the proposed framework.
@@
 mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
-In addition VM (Virtual Machine) mechanism is used in mruby, so mruby programs can run on any operating system as long as VM is implemented.
+In addition, VM (Virtual Machine) mechanism is used in mruby, so mruby programs can run on any operating system as long as VM is implemented.
 RiteVM is a VM in mruby, that runs mruby programs.
@@
 The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by RiteVM.
-The bytecodes can run on a Rite VM, thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
+The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
 \begin{figure}[t]
@@
 The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
-TECS is written in .cdl file (component description language).
+TECS code is written in .cdl (component description language) file.
 The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.
@@
 As the target RTOS, TOPPERS/HRP2 \cite{6913200} is used in this paper.
-TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
+TOPPERS/HRP2 is an RTOS based on \$micro\$ITRON with memory protection.
 However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{6332346} and TOPPERS/ASP.
@@
 The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the source files, which is identified by the .rb extension, are edited and compiled into the bytecodes by an mruby compiler.
+In the host, the source files (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
 The generated bytecodes are transferred from the host to the target device with Bluetooth.
@@
 The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
-This bytecode in the build description means that prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.
+This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.
 
@@
 Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of mruby bytecode loader using Bluetooth, which is like MrubyBluetooth1.
-First, a pointer of mrb\_state structure is initialized.
-mrb\_state is a set of states and global variables used in mruby.
+First, a pointer of {\it mrb\_state} structure is initialized.
+{\it mrb\_state} is a set of states and global variables used in mruby.
 Second, the bytecode of mruby libraries is read.
@@
 For example, motor class defines methods to rotate and stop a motor.
-The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: mrubyFile and irep.
-Here, the mrubyFile indicates the program files of mruby libraries.
-{\it [omit]} is only used for the TECS generator, thus the attribute, mrubyFile, does not consume memory.
+The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
+The {\it mrubyFile} indicates the program files of mruby libraries.
+{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
 The irep is the pointer of the array stored the bytecode of mruby libraries.
@@
 The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the mrb\_state.
+Two bytecodes are read separately in the {\it mrb\_state}.
 Finally, an mruby task runs.
@@
       [omit]char_t *mrubyFile;
-      char_t *irep=C_EXP("&$cell_global$_irep");
+      char_t *irep=C_EXP("&\$cell_global\$_irep");
     };
@@
 One of approaches for multitasking is co-routine.
-Co-routines are scheduled by developers with APIs such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
-Besides, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking, but it leaves the scheduling to developers such as co-routine.
-In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
+Co-routine is scheduled by developers with the functions such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
+Besides, as another method, {\it delay}, a service call of \$micro\$ITRON, can be used for multitasking, but it leaves the scheduling to developers such as co-routine.
+In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of \$micro\$ITRON, is implemented.
 A cyclic handler calls {\it rotateReadyQueue} that switches tasks, which enables developers to develop applications without concern for multitasking.
@@
 
-The {\it rotateReadyQueue} is a service call of $\mu$ITRON.
+The {\it rotateReadyQueue} is a service call of \$micro\$ITRON.
 When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown Figure \ref{fig:rotateReadyQueue}.
@@
 CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
-Cyclic handlers based on ITRON are described in detail [].
+Cyclic handlers based on ITRON are described in detail \cite{ITRON_spec}.
 The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
@@
 CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
-Here, {\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port which is connected {\it tkernel.eiKernel} to call functions of the kernel, an {\it entry} port and an attribute, priority.
-The attribute, priority is used as an arguments of {\it rotateReadyQueue}.
+{\it rotateReadyQueue} is implemented as the body.
+Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
+The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
+The attribute is used as an arguments of {\it rotateReadyQueue}.
 
@@
 In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
-In this case, the cyclic handler is executed when it is generated because the attribute is TA\_STA.
+In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA}.
 The cyclic handler is executed every one msec.
@@
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
-If developers do not need the cyclic handler, the .cdl files shown as Figure \ref{celltype_cyclic_handler}, \ref{build_cyclic_handler} should be commented out such as {\it //import($<$**.cdl$>$);}.
+If developers do not need the cyclic handler, the .cdl files shown as Figure \ref{celltype_cyclic_handler}, \ref{build_cyclic_handler} should be commented out such as {\it //import(\$<\$**.cdl\$>\$);}.
 This ease comes from component-based development with TECS.
@@
     attr {
-    	ID     id = C_EXP( "CYCHDLRID_$id$" );
+    	ID     id = C_EXP( "CYCHDLRID_\$id\$" );
     	[omit] ATR    attribute = C_EXP("TA_NULL");
@@
     cyclicTime = 1;
-    cyclicPhase = 0;
+    cyclicPhase = 1;
 };
@@
 For example, in the case of the four tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND.
-In the proposed framework, the set pattern and wait pattern is defined as attributes of the component.
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without if statements.
+In the proposed framework, the set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag}.
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without "if" statements.
 The components of eventflag are built with {\it [optional]} in TECS.
 {\it [optional]} means that the codes are run only when the call port is connected.
-The same file can be used even if developers would not like to use eventflag.
+The identical file can be used even if developers would not like to use eventflag.
 In other words, it is not necessary to compile/link the different file.
 These features are also advantages of component-based development.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
+    \caption{The design for Eventflag using TECS}
+    \label{fig:Eventflag}
+\end{figure}
 
@@
 \begin{itemize}
-        \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
+        \item the comparison of the size and transfer time between an mruby application including mruby library and not.
+        \item the comparison of the application execution time with singletasking, co-routine, and multitasking.
         \item the comparison of the overheads for each cyclic period of calling {\it rotateReadyQueue}.
-        \item the comparison of the application execution time with singletasking, co-routine, and multitasking.
 \end{itemize}
 
-This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.1.0.
-
+This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 The 100,000 times loop program is used as mruby application for evaluation of execution time.
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
+
+The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
+In the proposed framework, developers send only mruby application and prepare mruby library in advance.
+Therefore, the design can send the bytecode faster.
+In addition, the design can save the time to insert an SD card.
+These advantages lead to improving the work efficiency.
+
+\begin{table}[t]
+    \centering
+    \caption{Comparison of the size and transfer time between an mruby application including mruby libraries and not}
+    \begin{tabular}{c||c|c}
+                        & mruby Application \& Library & mruby Application  \\ \hline
+          Size          & 14,044 bytes                 & 199 bytes          \\ %\hline
+          Transfer Time & 356.015 msec                 & 58.708 msec        \\
+    \end{tabular}
+    \label{tab:size_and_time}
+\end{table}
+
+The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
+Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
+This result shows the proposed design is superior to co-routine in terms of execution time.
+Switching tasks's overhead is also evaluated, that is about three \$micro\$sec on average.
+The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
+Therefore, the overheads of multitasking is 0.5 \% or less, and multitasking can be used without the overheads.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
+    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
+    \label{fig:comparison_s_c_m}
+\end{figure}
+
+Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
+A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
+More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
+The execution time of each cyclic time are much the same.
+That is because the overhead of switching tasks (about 3 \$micro\$sec) is small in comparison with the execution time.
+The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
 
@@
     \label{fig:comparison_msec}
-\end{figure}
-
-The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-Co-routine takes twice the time of singletask to execute an mruby application.
-On the other hands, multitasking's execution time is about the same as singletasking's.
-Switching tasks's overhead is also evaluated, that is about three micro seconds on average.
-Therefore, the overheads of multitasking is 1 \% or less because the number of switching tasks is about 500.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
-    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
-    \label{fig:comparison_s_c_m}
 \end{figure}
@@
 Lua is one of the most popular script languages for embedded systems.
-Lua supports co-routines, referred to collaborative multitasking.
+Lua supports co-routine, referred to collaborative multitasking.
 A co-routine in Lua is used as an independently executed thread.
@@
 The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip [].
+The interpreter of the Owl system is the same as that of python-on-a-chip \cite{python-on-a-chip}.
 python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
@@
 mruby on TECS is a component-based framework for running mruby programs.
-The programs on mruby-on-TECS can execute about 100 times faster than the mruby programs.
+The programs on mruby on TECS can execute about 100 times faster than the mruby programs.
 Software can be also developed with component base by mruby on TECS.
@@
 Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
-In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking shows their advantages.
+In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
+mruby bytecode loader using Bluetooth can improve the work efficiency.
 The proposed multitasking is compared with singletasking and co-routine.
+This experimental result shows the effectiveness of the proposed framework because of the low overhead.
+
+The proposed framework is developed in component-base by TECS.
+The facilities such as the loader, the cyclic handler, and the eventflag are implemented as components.
+Developers can easily add or remove the facilities as necessary.
 
@@
 %%%%%%%%%%%%%
-\bibliography{ref.bib}
+\bibliography{ref}
 

### 2016-02-05 thesis/thesis.tex
update

@@
 \documentclass[conference,compsoc]{IEEEtran}
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtranBST2/IEEEtran}
+\usepackage{url}
 \usepackage[dvipdfmx]{graphicx}
@@
 In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers needs to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
+Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
 To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
-In addition, multiple mruby programs run cooperatively in the proposed framework.
+The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
+mruby application bytecode modified frequently is sent from a host to a target device by developers.
+mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compailation.
+In addition, multiple mruby programs cooperatively run in the proposed framework.
+In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
 Experimental results demonstrate the advantages of the proposed framework.
@@
 The component deployment and composition in TECS are statically performed, which gives optimization.
-As a result, the overheads of execution time and memory consumption can be reduced.
+As a result, the overhead of execution time and memory consumption can be reduced.
 There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.
@@
       [omit]char_t *mrubyFile;
-      char_t *irep=C_EXP("&$cell_global$_irep");
+      char_t *irep_lib=C_EXP("&$cell_global$_irep");
+      uint8_t irep_app[COUNT_STK_T(TMAX_APP_BINARY_SIZE)] __attribute__((nocommon));
     };
@@
 {
-  /* Receive the bytecode via Bluetooth */
-  bluetooth_loader();
-
   /* Declaration variables */
-  CELLCB	*p_cellcb;
   mrb_state *mrb;
@@
 
-  if (VALID_IDX(idx)) {
-    p_cellcb = GET_CELLCB(idx);
-  }
-
   /* New interpreter instance */
   mrb = mrb_open();
-  if (mrb == NULL) {
-    /* Invalid mrb_state */
-    return;
-  }
+  // Error Check for mrb_state
+
   /* New mruby context */
@@
 
-  if(is_cInit_joined()){
-    /* Initialization of mruby TECS Bridge */
-    cInit_initializeBridge( mrb );
-  }
+  // Initialization of mruby TECS Bridge
+
+  /* Receive the bytecode via Bluetooth */
+  bluetooth_loader( ATTR_app );
 
   /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_irep, c);
+  mrb_load_irep_cxt(mrb, ATTR_lib, c);
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, app_binary_buf, c);
+  mrb_load_irep_cxt(mrb, ATTR_app, c);
 
@@
 One of approaches for multitasking is co-routine.
-Co-routines are scheduled by developers with APIs such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
-Besides, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking, but it leaves the scheduling to developers such as co-routine.
+Co-routine is scheduled by developers with the functions such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
+Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking, but developers have to schedule as the same as co-routine.
 In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
@@
 \subsection{rotateReadyQueue}
-The case is assumed that there are two tasks with the same priority, and both are in a infinite loop.
+The case is assumed that there are two tasks with the same priority, and both tasks are in an infinite loop.
 In the current system, when one task is executed first, another task would not be executed.
-That is because the task with first execution runs in a loop.
+That is because the task with first execution runs in the loop.
 
-The {\it rotateReadyQueue} is a service call of $\mu$ITRON.
-When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown Figure \ref{fig:rotateReadyQueue}.
+When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
 The argument of {\it rotateReadyQueue} is the priority.
@@
 The {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
-For example, three tasks are in the order: task 1, 2 and 3.
-In this case, the order is changed, task 2, 3 and 1, when the {\it rotateReadyQueue} is called.
+For example, three tasks are in the order: task 1, 2, and 3.
+In this case, the order is changed, task 2, 3 and, 1, when the {\it rotateReadyQueue} is called.
 
@@
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
-If developers do not need the cyclic handler, the .cdl files shown as Figure \ref{celltype_cyclic_handler}, \ref{build_cyclic_handler} should be commented out such as {\it //import($<$**.cdl$>$);}.
+If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$**.cdl$>$);}.
 This ease comes from component-based development with TECS.
@@
     attr {
-    	ID     id = C_EXP( "CYCHDLRID_$id$" );
     	[omit] ATR    attribute = C_EXP("TA_NULL");
@@
     	[omit] RELTIM cyclicPhase = 0;
-        [omit] ACPTN  accessPattern[4] =
-            { C_EXP("OMIT"), C_EXP("OMIT"), C_EXP("OMIT"), C_EXP("OMIT") };
     };
@@
     priority =
-        C_EXP("EV3_MRUBY_VM_PRIORITY");
+        C_EXP("RITEVM_PRIORITY");
 };
@@
 
-\subsection{Synchronization of Multiple Tasks}
+\subsection{Synchronization of Multiple RiteVM Tasks}
 In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
@@
 This process can also apply to the case of the more tasks.
-For example, in the case of the four tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND.
-In the proposed framework, the set pattern and wait pattern is defined as attributes of the component.
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without if statements.
+For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND.
+
+In the proposed framework, the set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag}.
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements.
 The components of eventflag are built with {\it [optional]} in TECS.
 {\it [optional]} means that the codes are run only when the call port is connected.
-The same file can be used even if developers would not like to use eventflag.
+The identical file can be used even if developers do not use eventflag.
 In other words, it is not necessary to compile/link the different file.
 These features are also advantages of component-based development.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
+    \caption{The design for Eventflag using TECS}
+    \label{fig:Eventflag}
+\end{figure}
 
@@
 \begin{itemize}
-        \item the comparison of the size and transfer time between an mruby application including mruby libraries and not.
-        \item the comparison of the overheads for each cyclic period of calling {\it rotateReadyQueue}.
-        \item the comparison of the application execution time with singletasking, co-routine, and multitasking.
+        \item the comparison of the size and transfer time between an mruby application including mruby library and not
+        \item the comparison of the application execution time with singletasking, co-routine, and multitasking
+        \item the comparison of the overhead for each cyclic period of calling {\it rotateReadyQueue}
 \end{itemize}
 
-This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.1.0.
-
+This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 The 100,000 times loop program is used as mruby application for evaluation of execution time.
@@
 
-\begin{figure}[t]
+The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
+In the proposed framework, developers send only mruby application and prepare mruby library in advance.
+Therefore, the design can send the bytecode faster.
+In addition, the design can save the time to insert an SD card.
+These advantages lead to improving the work efficiency.
+
+\begin{table}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
-    \caption{Comparison of the overheads for each cyclic period of calling rotateReadyQueue}
-    \label{fig:comparison_msec}
-\end{figure}
+    \caption{Comparison of the size and transfer time between an mruby application including mruby libraries and not}
+    \begin{tabular}{c||c|c}
+                        & mruby Application \& Library & mruby Application  \\ \hline
+          Size          & 14,044 bytes                 & 199 bytes          \\ %\hline
+          Transfer Time & 356.015 msec                 & 58.708 msec        \\
+    \end{tabular}
+    \label{tab:size_and_time}
+\end{table}
 
@@
 In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-Co-routine takes twice the time of singletask to execute an mruby application.
-On the other hands, multitasking's execution time is about the same as singletasking's.
-Switching tasks's overhead is also evaluated, that is about three micro seconds on average.
-Therefore, the overheads of multitasking is 1 \% or less because the number of switching tasks is about 500.
+Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
+This result shows the proposed design is superior to co-routine in terms of execution time.
+Switching tasks's overhead is also evaluated, that is about three $\mu$sec on average.
+The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
+Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
 
@@
 
-\section{Related work}
+Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
+A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
+More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
+Each execution time of cyclic period is the same as the others.
+That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
+The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
+    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
+    \label{fig:comparison_msec}
+\end{figure}
+
+\section{Related Work}
 \label{sec:Related work}
@@
         & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
-        Lua               &            & -          & \checkmark &            \\
-        Owl system        &            & -          & -          & \checkmark \\
-        mruby             &            &            & \checkmark &            \\
-        mruby on TECS     &            & \checkmark & \checkmark &            \\
+        Lua \cite{Ierusalimschy:2007:EL:1238844.1238846} &            & -          & \checkmark &            \\
+        Owl system \cite{180964}                         &            & -          & -          & \checkmark \\
+        mruby \cite{5959588}                             &            &            & \checkmark &            \\
+        mruby on TECS \cite{7153813}                     &            & \checkmark & \checkmark &            \\
         Proposed framework& \checkmark & \checkmark & \checkmark &            \\
@@
 \end{table*}
-The open-source run-time systems for scripting languages have been proposed such as follow: mruby on TECS \cite{7153813}, mruby \cite{5959588}, the Owl system \cite{180964}, and Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}.
+The open-source run-time systems for scripting languages have been proposed such as follow:
+Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}, the Owl system \cite{180964}, mruby \cite{5959588}, and mruby on TECS \cite{7153813}.
 
 Lua is one of the most popular script languages for embedded systems.
-Lua supports co-routines, referred to collaborative multitasking.
+Lua supports co-routine, referred to collaborative multitasking.
 A co-routine in Lua is used as an independently executed thread.

### 2016-02-05 thesis/thesis.tex
update

@@
 An approach of efficient software development is to use component-based techniques.
-CBD (Component-Based Development) is a design technique for constituting reusable components \cite{Crnkovic:2005:CSE:1062455.1062631}.
+CBD (Component-Based Development) is a design technique for constituting reusable components \cite{par:Crnkovic}.
 Complex and large scale software systems can be developed efficiently using component-based techniques.
@@
 It also makes a system flexible in extensions and specification changes.
+There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems
 
@@
 
-mruby on TECS is a component-based framework for running script program \cite{7153813}.
+mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
 It is integrated two technologies.
-One is mruby, which is a script language for embedded systems \cite{5959588}.
-The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{4208825}.
+One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
+The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS}.
 TECS supports to effectively run mruby script language on embedded systems.
@@
 mruby on TECS has some problems at present.
-One of these is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 to load mruby programs.
+One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
 In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
@@
 Another new feature enables developers to run a multitask programs more easily.
-Specifically, a cycle handler of switching tasks is implemented.
+Specifically, a cyclic handler of switching tasks is implemented.
 This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
@@
 
-Ruby is a object-oriented script language.
+Ruby is a object-oriented script language \cite{url:Ruby}.
 As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
@@
 };
-
 celltype tMotor{
@@
 };
-
 cell tCaller Caller{
@@
 
-As the target RTOS, TOPPERS/HRP2 \cite{6913200} is used in this paper.
+As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
 TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{6332346} and TOPPERS/ASP.
+However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.
 
@@
 There is a great difference between the execution time of mruby and C language.
-According to  \cite{7153813}, mruby programs are several hundreds times slower than C programs.
+According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
 The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
@@
 The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
-A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{7153813}.
+A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
 The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
@@
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
-TOPPERS/HRP2 is described in \cite{6913200}.
+TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:ht-tecs}.
 The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
 A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
-In this framework, ZMODEM \cite{forsberg1988zmodem} is used as a binary transfer protocol.
+In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.
 
@@
       [omit]char_t *mrubyFile;
-      char_t *irep_lib=C_EXP("&$cell_global$_irep");
-      uint8_t irep_app[COUNT_STK_T(TMAX_APP_BINARY_SIZE)] __attribute__((nocommon));
+      char_t *irepLib=C_EXP("&$cell_global$_irep");
+      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
+              __attribute__((nocommon));
     };
@@
   mrbc_context *c;
-
   /* New interpreter instance */
   mrb = mrb_open();
-  // Error Check for mrb_state
-
+  // Omit: error check for mrb_state
   /* New mruby context */
   c = mrbc_context_new(mrb);
-
-  // Initialization of mruby TECS Bridge
-
+  // Omit: initialization of mruby-TECS bridge
   /* Receive the bytecode via Bluetooth */
   bluetooth_loader( ATTR_app );
-
   /* Load mruby library bytecode and run */
@@
   mrb_load_irep_cxt(mrb, ATTR_app, c);
-
   if (mrb->exc) {
@@
 CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
-Cyclic handlers based on ITRON are described in detail \cite{ITRON_spec}.
+Cyclic handlers based on ITRON are described in detail \cite{par:microITRON}.
 The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
@@
 };
-
 celltype tCyclicMain{
@@
 };
-
 cell tCyclicMain CyclicMain{
@@
         & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
-        Lua \cite{Ierusalimschy:2007:EL:1238844.1238846} &            & -          & \checkmark &            \\
-        Owl system \cite{180964}                         &            & -          & -          & \checkmark \\
-        mruby \cite{5959588}                             &            &            & \checkmark &            \\
-        mruby on TECS \cite{7153813}                     &            & \checkmark & \checkmark &            \\
+        Lua \cite{url:Lua}, \cite{par:Lua} &            & -          & \checkmark &            \\
+        Owl system \cite{par:owl}                         &            & -          & -          & \checkmark \\
+        mruby \cite{par:mruby}, \cite{url:mruby}                             &            &            & \checkmark &            \\
+        mruby on TECS \cite{par:mrubyonTECS}                     &            & \checkmark & \checkmark &            \\
         Proposed framework& \checkmark & \checkmark & \checkmark &            \\
@@
 The open-source run-time systems for scripting languages have been proposed such as follow:
-Lua \cite{Ierusalimschy:2007:EL:1238844.1238846}, the Owl system \cite{180964}, mruby \cite{5959588}, and mruby on TECS \cite{7153813}.
+Lua \cite{url:Lua}, \cite{par:Lua}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
@@
 The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip \cite{python-on-a-chip}.
+The interpreter of the Owl system is the same as that of python-on-a-chip \cite{url:python-on-a-chip}.
 python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
@@
 
+In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in muliti-VM.
+Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
 %%%%%%%%%%%%%

### 2016-02-06 thesis/thesis.tex
update

@@
 \label{sec:mruby bytecode loader using Bluetooth}
-This section describes an additional function of mruby on TECS, mruby bytecode loader using Bluetooth.
+This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
 In the current system, all binary data including bytecodes are in an SD card.
-Developers must insert and pull out the SD card every time the source program are modified.
+Developers must insert and pull out the SD card every time the source programs are modified.
 It causes a low work efficiency that such a work must be repeated.
@@
 The work that an SD card is in and out needs to be done just once in the beginning.
+
+mruby programs are consisted of mruby application and libraries.
+mruby application is the main code of the application.
+mruby libraries are the code defining the functions for application such as Ruby class. 
+The mruby bytecodes including mruby application and libraries can be sent and run.
+However it is wasteful in terms of the size and time to send because libraries are not frequently modified. 
+In the proposed framework, mruby application only sends, and mruby libraries are preserved in the SD card beforehand.
 
@@
   /* Receive the bytecode via Bluetooth */
-  bluetooth_loader( ATTR_app );
+  bluetooth_loader( ATTR_irepApp );
   /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_lib, c);
+  mrb_load_irep_cxt(mrb, ATTR_irepLib, c);
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_app, c);
+  mrb_load_irep_cxt(mrb, ATTR_irepApp, c);
   if (mrb->exc) {
@@
 However, multitask processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for developers.
+
 One of approaches for multitasking is co-routine.
-Co-routine is scheduled by developers with the functions such as {\it resume} and {\it yield}, and thus co-routine does not receive the OS's support.
-Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking, but developers have to schedule as the same as co-routine.
+Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\it resume} and {\it yield}. 
+(Ruby co-routine is defined in class Fiber \cite{url:co-routine})
+Co-routine is a non-preemptive mulititasking, and does not receive the OS's support because developers have to switch tasks manually.
+Co-routine can not take advantege of multi core processing.
+
+Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking.
+This service call delays the execution of the own task for the time of the argument.
+In the approach of {\it delay} fubction, developers have to schedule as the same as co-routine.
+
 In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
-A cyclic handler calls {\it rotateReadyQueue} that switches tasks, which enables developers to develop applications without concern for multitasking.
+{\it rotateReadyQueue} rotates the precedence of the task with the priority of the argument.
+A cyclic handler calls {\it rotateReadyQueue}, which enables developers to develop applications without concern for multitasking.
 
@@
 For example, three tasks are in the order: task 1, 2, and 3.
-In this case, the order is changed, task 2, 3 and, 1, when the {\it rotateReadyQueue} is called.
+In this case, the order is rotated, task 2, 3 and, 1, when the {\it rotateReadyQueue} is called.
 
@@
 The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
-CyclicHandler {\it cell} configures the cyclic handler based on ITRON.
+CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
 Cyclic handlers based on ITRON are described in detail \cite{par:microITRON}.
@@
 In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
-In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA}.
+In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
 The cyclic handler is executed every one msec.
@@
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
-If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$**.cdl$>$);}.
+If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
 This ease comes from component-based development with TECS.
@@
 In the proposed framework, the set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag}.
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements.
-The components of eventflag are built with {\it [optional]} in TECS.
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
+Developers do not need to modify the .c file because the .cdl files in accordance with the number of RiteVMs are prepared. 
+In additon, the components of Eventflag are built with {\it [optional]} in TECS.
 {\it [optional]} means that the codes are run only when the call port is connected.
-The identical file can be used even if developers do not use eventflag.
-In other words, it is not necessary to compile/link the different file.
+The .c file does not be rewritten even if developers do not use Eventflag. 
 These features are also advantages of component-based development.
@@
 This section mentions experimental results and their consideration.
-To analyze the advantages and disadvantages of the proposed framework, the evaluations are performed as follows.
+To analyze the advantages of the proposed framework, the evaluations are performed as follows.
 \begin{itemize}
@@
 
+These evaluations are performed in order to indicate that mruby bytecode loader improves the work efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
 This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
-The 100,000 times loop program is used as mruby application for evaluation of execution time.
-In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
 
@@
 The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+The 100,000 times loop program is used as mruby application for evaluation of execution time.
+In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
 In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
@@
 mruby bytecode loader using Bluetooth can improve the work efficiency.
-The proposed multitasking is compared with singletasking and co-routine.
-This experimental result shows the effectiveness of the proposed framework because of the low overhead.
+The proposed multitasking has the effectiveness in terms of execution time compared with singletasking and co-routine because of the low overhead.
 
 The proposed framework is developed in component-base by TECS.
-The facilities such as the loader, the cyclic handler, and the eventflag are implemented as components.
+The facilities such as the loader, the cyclic handler, and the Eventflag are implemented as components.
 Developers can easily add or remove the facilities as necessary.
+Component-based development can increase the productivity and decrease the complexity.
 
-In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in muliti-VM.
+In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
 Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.

### 2016-02-08 EMSOFT2016/diff/0127_thesis.tex
update

--- 2016-01-26 thesis/diff/0127_thesis.tex
@@
 
-The rot\_rdq is a service call of $\mu$ITRON.
+The rot\_rdq is a service call of \$micro\$ITRON.
 When rot\_rdq is called, tasks with the same priority are switched as shown Figure \ref{fig:rot_rdq}.

### 2016-02-08 EMSOFT2016/diff/0201_thesis.tex
update

--- 2016-01-31 thesis/thesis.tex
@@
 CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
-Here, {\it rotateReadyQueue} is implemented as the body.
+{\it rotateReadyQueue} is implemented as the body.
 Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port which is connected {\it tkernel.eiKernel} to call functions of the kernel, an {\it entry} port and an attribute, priority.
@@
 
+\begin{table}[t]
+    \centering
+    \caption{Comparison of the size and transfer time between an mruby application including mruby libraries and not}
+    \begin{tabular}{c||c|c}
+                        & mruby Application \& Library & mruby Application  \\ \hline
+          Size          & 14,044 bytes                 & 199 bytes          \\ %\hline
+          Transfer Time & 356.015 msec                 & 58.708 msec        \\
+    \end{tabular}
+    \label{tab:size_and_time}
+\end{table}
+
 The 100,000 times loop program is used as mruby application for evaluation of execution time.
@@
 Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
-In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking shows their advantages.
+In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
 The proposed multitasking is compared with singletasking and co-routine.

### 2016-02-08 EMSOFT2016/diff/0208_thesis.tex
update

--- 2016-02-06 thesis/thesis.tex
@@
 
-The system model of mruby on TECS is shown in Figure \ref{fig:system_model}.
+The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
 Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
@@
     \centering
+    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
+    \caption{System Model of existing mruby on TECS}
+    \label{fig:mrubyontecs}
+\end{figure}
+\begin{figure}[t]
+    \centering
     \includegraphics[width=8cm,clip]{figure/system_model.pdf}
-    \caption{System Model}
+    \caption{Specific System Model of the proposed framework}
     \label{fig:system_model}
@@
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
-TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:ht-tecs}.
+TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
 The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
@@
 Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to insert an SD card.
+In addition, the design can save the time to insert an SD card to restart an OS.
 These advantages lead to improving the work efficiency.
@@
     \caption{Comparion of the proposed and previous work}
-    \begin{tabular}{c||c|ccc}
-        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
-        Lua \cite{url:Lua}, \cite{par:Lua} &            & -          & \checkmark &            \\
-        Owl system \cite{par:owl}                         &            & -          & -          & \checkmark \\
-        mruby \cite{par:mruby}, \cite{url:mruby}                             &            &            & \checkmark &            \\
-        mruby on TECS \cite{par:mrubyonTECS}                     &            & \checkmark & \checkmark &            \\
-        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
+    \begin{tabular}{c||c|cccccc}
+        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
+        Lua \cite{url:Lua}, \cite{par:Lua}           &            & \checkmark & Partially  &            &            & \checkmark \\
+        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            & \checkmark \\
+        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            & \checkmark \\
+        mruby \cite{par:mruby}, \cite{url:mruby}     &            & \checkmark &            &            &            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            & \checkmark \\
+        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
     \end{tabular}
@@
 The open-source run-time systems for scripting languages have been proposed such as follow:
-Lua \cite{url:Lua}, \cite{par:Lua}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+eLua \cite{url:eLua},  python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
-Lua is one of the most popular script languages for embedded systems.
+eLua offers the full implementation of Lua programming language to the embedded systems.
+Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
 Lua supports co-routine, referred to collaborative multitasking.
@@
 
+python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
+The VM runs a significant subset of Python language with few resources on a microcontroller.
+p14p can run multiple stackless green threads.
+
 The Owl system is an embedded Python run-time system.
@@
 The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip \cite{url:python-on-a-chip}.
-python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
-GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
-GIL leads the limitation of the concurrency on multitasking.
+The interpreter of the Owl system is the same as that of python-on-a-chip.
 

### 2016-02-08 thesis/abstract.tex
update

\documentclass[a4j,10pt,twocolumn]{utf8/abstract}
%\documentclass[a4j,9pt,twocolumn]{abstract}
\usepackage[dvipdfmx]{graphicx}
\usepackage[varg]{txfonts}
%%% \begin{document}の前に，各エントリーを記述する

\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}	% 論文のタイトル
\author{山本 拓朗} 		% 著者
\studentid{09C12174} 	% 学籍番号
\lab{潮}		% 研究室名

% 英語なら以下2行を定義
\englishtitle
\jptitle{Bluetoothを用いたマルチVM対応mrubyバイトコードローダ}  % 日本語のタイトル

\begin{document}
\absttitle 		% 表題の出力

\section{まえがき}
近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．

組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた \cite{mrubyontecs}．

現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．

本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する.
\section{mruby on TECS}
mruby on TECSは，組み込み向けの高生産性なスクリプト言語のひとつであるmruby (軽量Ruby) と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせた，組込みソフトウェアのコンポーネントベース開発が可能なフレーム―ワークである.

スクリプト言語は生産性が高い反面，C言語に比べると実行速度が遅いので，組込みシステムに適用するのは難しい.
mruby on TECSでは，mruby-TECS BridgeによってmrubyプログラムからC言語レベルの関数を呼ぶことが可能になっている.
mruby on TECSは，mrubyに比べて，アプリケーションを約100倍速く実行できる.

現状のmruby on TECSでは，mrubyアプリケーションを修正する度にホスト・ターゲットデバイス間でSDカードを抜き差し，再度OSを起動する必要がある.
その上，複数のmrubyアプリケーションを並列実行させる場合，開発者がタスクを待ち状態へ遷移させるようなOSの機能を呼び出さなければならない.
　
\section{提案フレームワーク}
提案フレームワークは，mruby on TECSをベースにしてBluetoothを用いたmrubyバイトコードローダと実用的なマルチタスク処理の実装を行った.
システムモデルを図\ref{fig:system_model}に示す.

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
    \caption{System Model}
    \label{fig:system_model}
\end{figure}

提案フレームワークでは，はじめの1度のみmrubyアプリケーション部分を除いたプラットフォームをコンパイル・リンクする．
ホスト側では，mrubyアプリケーション (.rb) をバイトコード (.mrb) にコンパイルし，Bluetoothを通してターゲットデバイスにバイトコードを送信する.
ターゲットデバイス側では，RiteVMに実装されたローダが送られたファイルを受信し，すでにリンクされているmrubyライブラリと合わせてアプリケーションを実行する.
この過程で開発することで，SDカードを抜き差しする手間やOSを起動し直す時間が省けるので，作業効率を上げることができる.

さらに，現状のmruby on TECSでは使用するのが難しかったマルチタスク処理を，$\mu$ITRON \cite{microITRON} のサービスコールである{\it rotateReadyQueue}を周期ハンドラで周期的に呼び出すことで，開発者にとって使いやすい設計にした.
{\it rotateReadyQueue}は，同じ優先度のタスクの実行順序を切り替える機能である.
複数タスク間の同期にはイベントフラグ処理を適用し，すべてのタスクが同時に起動するように実装した.
イベントフラグのセットパターンや待ちパターンは，各コンポーネントの属性として定義する.
これによって，VMの数に関わらず，同じ.cファイルを利用することが可能になる.

提案フレームワークでは，RiteVMや周期ハンドラ，イベントフラグはすべてTECSのコンポーネントとして実装されているので，開発者の必要に応じて機能を付けたり外したりすることも容易に実現できる.

\section{結論}
mruby on TECSの機能として，Bluetoothを用いたmrubyバイトコードローダと実用的なマルチタスク処理を提案した.
実験評価では，ローダによる作業効率の向上やオーバーヘッドの少ないマルチタスク設計の有用性を示した.

%\bibliographystyle{junsrt}
%\bibliography{refs}
\begin{thebibliography}{2}
\bibitem{mrubyontecs} Azumi, T. and Nagahara, Y. and Oyama, H. and Nishio, N., 
    ``mruby on TECS: Component-Based Framework for Running Script Program," 
    Proceedings of the 18th IEEE International Symposium on Real-Time Distributed Computing (ISORC), 
    pp.252-259, 
    2015.

    \bibitem{microITRON} Hiroaki Takada and Ken Sakamura,
    ``$\mu$ITRON for Small-Scale Embedded Systems",
    IEEE Micro,
    vol.15,
    no.6,
    pp.46-54,
    1995.
\end{thebibliography}
\newpage
\pagebreak
\end{document}

### 2016-02-09 EMSOFT2016/thesis.tex
update

--- 2016-02-08 EMSOFT2016/diff/0208_thesis.tex
@@
 \documentclass[conference,compsoc]{IEEEtran}
-\bibliographystyle{IEEEtranBST2/IEEEtran}
 \usepackage{url}
@@
 mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compailation.
+mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compilation.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
 In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
+Synchronization of starting multiple tasks is also implemented with Eventflag. 
 Experimental results demonstrate the advantages of the proposed framework.
@@
 Although script languages are easy to use and read, their execution time are slower than C language's.
-For embedded systems, the real-time properties such as worst-execution time, response time are very important factors.
+For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
 Therefore, it is difficult to apply the script languages to embedded systems.
@@
 One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
-The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS}.
-TECS supports to effectively run mruby script language on embedded systems.
+The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS} \cite{url:TOPPERS}.
+mruby on TECS supports to effectively run mruby script language on embedded systems.
 mruby on TECS also makes execution time 100 times faster than that of mruby.
@@
 This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
-mruby on TECS has some problems at present.
+mruby on TECS has several problems at present.
 One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
-If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
+In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly and the OS should be restarted.
+If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and mruby application codes are transferred from a host to a target device by Bluetooth.
 It can improve the efficiency.
@@
 Thus that is a big burden on developers.
-Another new feature enables developers to run a multitask programs more easily.
+Another new feature enables developers to run multitasking programs more easily.
 Specifically, a cyclic handler of switching tasks is implemented.
@@
 In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
+Synchronization of tasks is implemented.
 Multitasked programing makes the range of software expand.
@@
 Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
-Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.
+Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
 
@@
 \label{sec:Background}
-Figure \ref{fig:proposed} shows a system model of the proposed framework.
+Figure \ref{fig:proposed} shows the system model of the proposed framework.
 The bytecodes are transferred from the host to the target device with Bluetooth.
@@
 Each bytecode is allocated to a RiteVM, respectively.
-Developers can run some bytecodes transferred with Bluetooth in multitask.
+Developers can run bytecodes transferred with Bluetooth in multitask.
 
@@
 mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
-In addition, VM (Virtual Machine) mechanism is used in mruby, so mruby programs can run on any operating system as long as VM is implemented.
+In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
 RiteVM is a VM in mruby, that runs mruby programs.
@@
         In the same way, {\it call} ports can be declared.
-        Attributes and valuables follow the keyword attr and var respectively.\\
+        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.\\
 \begin{figure}[t]
@@
         A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
-        To compose {\it cell}s a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
+        To compose {\it cell}s, a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
         In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
@@
 
-An mruby-TECS bridge plays a role to call a native program (e.g.,C legacy code) from an mruby program.
+An mruby-TECS bridge plays a role to call a native program (e.g. C legacy code) from an mruby program.
 The mruby-TECS bridge provides native libraries for mruby.
@@
 As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
-TOPPERS/HRP2 is an RTOS based on $\mu$ITRON with memory protection.
+TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
 However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.
@@
     \label{fig:mrubyontecs}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
-    \caption{Specific System Model of the proposed framework}
-    \label{fig:system_model}
 \end{figure}
@@
 \label{sec:mruby bytecode loader using Bluetooth}
+Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
+    \caption{Detailed System Model of the proposed framework}
+    \label{fig:system_model}
+\end{figure}
 This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
@@
 Developers must insert and pull out the SD card every time the source programs are modified.
+The OS in the target device should be also restarted.
 It causes a low work efficiency that such a work must be repeated.
@@
 (Ruby co-routine is defined in class Fiber \cite{url:co-routine})
-Co-routine is a non-preemptive mulititasking, and does not receive the OS's support because developers have to switch tasks manually.
-Co-routine can not take advantege of multi core processing.
+Co-routine is a non-preemptive multitasking, and does not receive the OS's support because developers have to switch tasks manually.
+Co-routine can not take advantage of multi core processing.
 
@@
 This service call delays the execution of the own task for the time of the argument.
-In the approach of {\it delay} fubction, developers have to schedule as the same as co-routine.
+In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
 
@@
 CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
-Cyclic handlers based on ITRON are described in detail \cite{par:microITRON}.
+Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
 The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
@@
 In another part, the priority of CyclicMain {\it cell} is described.
-EV3\_MRUBY\_VM\_PRIORITY defines the priority of mruby tasks.
+RITEVM\_PRIORITY defines the priority of mruby tasks.
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
@@
 This result shows the proposed design is superior to co-routine in terms of execution time.
-Switching tasks's overhead is also evaluated, that is about three $\mu$sec on average.
+Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
 The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
@@
     \caption{Comparion of the proposed and previous work}
-    \begin{tabular}{c||c|cccccc}
-        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
-        Lua \cite{url:Lua}, \cite{par:Lua}           &            & \checkmark & Partially  &            &            & \checkmark \\
-        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            & \checkmark \\
-        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            & \checkmark \\
-        mruby \cite{par:mruby}, \cite{url:mruby}     &            & \checkmark &            &            &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            & \checkmark \\
-        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+    \begin{tabular}{c||c|ccccccc}
+        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & VM Scheduler & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
+        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &            &            & \checkmark \\
+        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &            &            & \checkmark \\
+        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &            &            & \checkmark \\
+        mruby \cite{par:mruby}                       &            & \checkmark &            &            &            &            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            &            & \checkmark \\
+        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
     \end{tabular}
@@
 The open-source run-time systems for scripting languages have been proposed such as follow:
-eLua \cite{url:eLua},  python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
-
-eLua offers the full implementation of Lua programming language to the embedded systems.
-Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
-Lua supports co-routine, referred to collaborative multitasking.
-A co-routine in Lua is used as an independently executed thread.
-A co-routine can just suspend and resume multiple routines.
-Thus, a Lua co-routine is not like multitasks in multitask systems.
+python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
@@
 The interpreter of the Owl system is the same as that of python-on-a-chip.
+
+eLua offers the full implementation of Lua programming language to the embedded systems.
+Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
+Lua supports co-routine, referred to collaborative multitasking.
+A co-routine in Lua is used as an independently executed thread.
+A co-routine can just suspend and resume multiple routines.
+Thus, a Lua co-routine is not like multitasks in multitask systems.
 
@@
 %%%%%%%%%%%%%
+\bibliographystyle{IEEEtranBST2/IEEEtran}
 \bibliography{ref}

### 2016-02-09 thesis/abstract.tex
update

@@
 \usepackage[dvipdfmx]{graphicx}
+\usepackage{amssymb}
 \usepackage[varg]{txfonts}
@@
 近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．
-
-組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた \cite{mrubyontecs}．
+組込みソフトウェア開発の生産性の向上を目的として，組込みシステム向けのスクリプト言語であるmruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSが提案されている \cite{mrubyontecs}．
 
 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
-さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
 
 本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
-さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する.
-\section{mruby on TECS}
-mruby on TECSは，組み込み向けの高生産性なスクリプト言語のひとつであるmruby (軽量Ruby) と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせた，組込みソフトウェアのコンポーネントベース開発が可能なフレーム―ワークである.
+さらに，複数のmrubyアプリケーションを協調動作できるフレームワークを提案する.
 
-スクリプト言語は生産性が高い反面，C言語に比べると実行速度が遅いので，組込みシステムに適用するのは難しい.
-mruby on TECSでは，mruby-TECS BridgeによってmrubyプログラムからC言語レベルの関数を呼ぶことが可能になっている.
-mruby on TECSは，mrubyに比べて，アプリケーションを約100倍速く実行できる.
+\section{既存フレームワークの問題点}
+mruby on TECSは，mrubyと，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである.
 
-現状のmruby on TECSでは，mrubyアプリケーションを修正する度にホスト・ターゲットデバイス間でSDカードを抜き差し，再度OSを起動する必要がある.
-その上，複数のmrubyアプリケーションを並列実行させる場合，開発者がタスクを待ち状態へ遷移させるようなOSの機能を呼び出さなければならない.
+スクリプト言語は生産性が高い反面，C言語に比べると実行速度が遅いため，組込みシステムに適用するのは難しい.
+mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べて，アプリケーションを約100倍速く実行できる.
+
+mruby on TECSでは，mrubyプログラムを修正する度にターゲットデバイスでSDカードを抜き差しし，OSを再起動する必要がある.
+さらに，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
 　
 \section{提案フレームワーク}
-提案フレームワークは，mruby on TECSをベースにしてBluetoothを用いたmrubyバイトコードローダと実用的なマルチタスク処理の実装を行った.
+提案フレームワークは，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダと，実用的なマルチタスク処理の実装を行った.
 システムモデルを図\ref{fig:system_model}に示す.
-
 \begin{figure}[h]
     \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
+    \includegraphics[width=7cm,clip]{Abst_SystemModel.pdf}
     \caption{System Model}
@@
 
-提案フレームワークでは，はじめの1度のみmrubyアプリケーション部分を除いたプラットフォームをコンパイル・リンクする．
-ホスト側では，mrubyアプリケーション (.rb) をバイトコード (.mrb) にコンパイルし，Bluetoothを通してターゲットデバイスにバイトコードを送信する.
-ターゲットデバイス側では，RiteVMに実装されたローダが送られたファイルを受信し，すでにリンクされているmrubyライブラリと合わせてアプリケーションを実行する.
-この過程で開発することで，SDカードを抜き差しする手間やOSを起動し直す時間が省けるので，作業効率を上げることができる.
+提案フレームワークでは，プラットフォーム（図\ref{fig:system_model}の下部）をコンパイル・リンクし，ターゲットデバイス上で起動する.
+ホストPC側では，mrubyアプリケーション (.rb) をバイトコード (.mrb) にコンパイルし，Bluetoothを通してターゲットデバイスにバイトコードを転送する.
+ターゲットデバイス側では，RiteVMに実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmrubyライブラリと合わせてアプリケーションを実行する.
+これによって，SDカードを抜き差しする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
 
-さらに，現状のmruby on TECSでは使用するのが難しかったマルチタスク処理を，$\mu$ITRON \cite{microITRON} のサービスコールである{\it rotateReadyQueue}を周期ハンドラで周期的に呼び出すことで，開発者にとって使いやすい設計にした.
-{\it rotateReadyQueue}は，同じ優先度のタスクの実行順序を切り替える機能である.
+さらに，各VMの処理を平等に実行するRiteVMスケジューラを提供することで，マルチタスク処理を効率的に利用できる.
+%$\mu$ITRON \cite{microITRON} のサービスコールである{\it rotateReadyQueue}を使った
+%開発者にとって使いやすい設計にした.
+%{\it rotateReadyQueue}は，同じ優先度のタスクの実行順序を切り替える機能である.
 複数タスク間の同期にはイベントフラグ処理を適用し，すべてのタスクが同時に起動するように実装した.
 イベントフラグのセットパターンや待ちパターンは，各コンポーネントの属性として定義する.
-これによって，VMの数に関わらず，同じ.cファイルを利用することが可能になる.
+これによって，VMの数に関わらず，同じCファイルを利用できる.
 
-提案フレームワークでは，RiteVMや周期ハンドラ，イベントフラグはすべてTECSのコンポーネントとして実装されているので，開発者の必要に応じて機能を付けたり外したりすることも容易に実現できる.
+提案フレームワークでは，RiteVMやRiteVMスケジューラ，イベントフラグはすべてTECSのコンポーネントとして実装されているため，開発者の必要に応じて容易に機能の取り外しができる.
+
+表\ref{tab:comparion}に，提案フレームワークと既存フレームワークの比較を示す.
+提案フレームワークでは，Bluetoothを用いたバイトコードローダに加え，VMスケジューラおよびアプリケーションの同期が可能になった.
 
 \section{結論}
-mruby on TECSの機能として，Bluetoothを用いたmrubyバイトコードローダと実用的なマルチタスク処理を提案した.
-実験評価では，ローダによる作業効率の向上やオーバーヘッドの少ないマルチタスク設計の有用性を示した.
+Bluetoothを用いたmrubyバイトコードローダによって，mruby on TECSでのソフトウェア開発の作業効率を向上させ，RiteVMスケジューラは複数のmrubyアプリケーションを効率良く実行する.
+さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる.
+
+実験評価では，ローダによる作業効率の向上やオーバヘッドの少ないマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
+
+\begin{table}[t]
+    \centering
+    \caption{Comparion of the proposed and previous work}
+    \scriptsize
+    \begin{tabular}{c||c|c|c|c}
+        & \shortstack{Bluetooth\\Loader} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization\\of Application} \\ \hline
+        eLua                &            &            & &           \\
+        Owl system          &            &            & &           \\
+        mruby on TECS       &            & \checkmark & &           \\
+        Proposed framework  & \checkmark & \checkmark & \checkmark &\checkmark \\
+    \end{tabular}
+    \label{tab:comparion}
+\end{table}
 
@@
 %\bibliography{refs}
-\begin{thebibliography}{2}
-\bibitem{mrubyontecs} Azumi, T. and Nagahara, Y. and Oyama, H. and Nishio, N., 
+\begin{thebibliography}{1}
+\bibitem{mrubyontecs} T. Azumi, and Y. Nagahara, and H. Oyama, and N. Nishio, 
     ``mruby on TECS: Component-Based Framework for Running Script Program," 
@@
     2015. 
-
-    \bibitem{microITRON} Hiroaki Takada and Ken Sakamura,
-    ``$\mu$ITRON for Small-Scale Embedded Systems",
-    IEEE Micro,
-    vol.15,
-    no.6,
-    pp.46-54,
-    1995.
 \end{thebibliography}

### 2016-02-09 EMSOFT2016/thesis.tex
update

@@
 Multitasked programing makes the range of software expand.
+\item To focus on the advantage of component-based developments: \mbox{}\\
+\ The proposed framework has been developed with component-based.
+Component-based development gives various benefits.
+This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
@@
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
+Section \ref{sec:Design and Implementation} describe the design and implementation of the proposed framework in detail.
 Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
@@
 
-\section{mruby Bytecode Loader Using Bluetooth}
-\label{sec:mruby bytecode loader using Bluetooth}
+\section{Design and Implementation}
+\label{sec:Design and Implementation}
 Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
+Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
+
 \begin{figure}[t]
@@
 \end{figure}
+\subsection{mruby Bytecode Loader Using Bluetooth}
+\label{sec:mruby bytecode loader using Bluetooth}
 This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
@@
 
-\subsection{Component of mruby bytecode loader using Bluetooth}
+\subsubsection{Component of mruby bytecode loader using Bluetooth} \mbox{}\\
+
 The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
@@
 \end{figure}
-\section{Multitask}
+\subsection{Multitask}
 \label{sec:Multitask}
@@
 
-In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
-{\it rotateReadyQueue} rotates the precedence of the task with the priority of the argument.
-A cyclic handler calls {\it rotateReadyQueue}, which enables developers to develop applications without concern for multitasking.
+In the proposed framework, as an approach for multitask processing, RiteVM scheduler is implemented.
+The RiteVM scheduler is a fair scheduler and runs multiple tasks equally.
 
-\subsection{rotateReadyQueue}
+\subsubsection{RiteVM Scheduler} \mbox{}\\
+
+The RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+{\it rotateReadyQueue} is described as follows.
+
 The case is assumed that there are two tasks with the same priority, and both tasks are in an infinite loop.
@@
 
-\subsection{Component of Cyclic Handler}
+\subsubsection{Component of RiteVM Scheduler} \mbox{}\\
+
 Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
@@
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
-If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
-This ease comes from component-based development with TECS.
 
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
+\subsubsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
+
 In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
@@
 This process can also apply to the case of the more tasks.
-For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND.
-
-In the proposed framework, the set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag}.
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
-Developers do not need to modify the .c file because the .cdl files in accordance with the number of RiteVMs are prepared. 
-In additon, the components of Eventflag are built with {\it [optional]} in TECS.
-{\it [optional]} means that the codes are run only when the call port is connected.
-The .c file does not be rewritten even if developers do not use Eventflag. 
-These features are also advantages of component-based development.
+For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND as shown in Figure \ref{fig:Eventflag} (A).
 
@@
 
+\subsection{Benefits of Component-Based Development}
+This section describes the design using the benefits of component-based development.
+
+In the framework, RiteVM, RiteVM scheduler, and Eventflag are implemented as components.
+Therefore, developers can easily add or remove these components and also reuse them.
+For example, if developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
+
+In additon, the code size can desrease by developing with component-based. 
+In the proposed framework, the advantage is applied in the Eventflag component.
+The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
+Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
+In additon, the components of Eventflag are built with {\it [optional]} in TECS.
+{\it [optional]} means that the codes are run only when the call port is connected.
+The .c file does not be rewritten even if developers do not use Eventflag.
+
 \section{Experimental Evaluation}
@@
 \begin{itemize}
-    \item the comparison of the size and transfer time between an mruby application including mruby library and not
-    \item the comparison of the application execution time with singletasking, co-routine, and multitasking
-    \item the comparison of the overhead for each cyclic period of calling {\it rotateReadyQueue}
+    \item Size and transfer time for mruby programs
+    \item Execution time with singletasking, co-routine, and multitasking
+    \item Overhead for cyclic time
+    \item Code size using the benefit of CBD 
 \end{itemize}
@@
         mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &            &            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & $\triangle$&            & \checkmark \\
         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
     \end{tabular}
-    \label{tab:comparion}
+    \label{tab:comparison}
 \end{table*}
@@
 
-Table \ref{tab:comparion} shows a comparison between the proposed framework and previous work.
+Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
 
@@
 The proposed framework is developed in component-base by TECS.
-The facilities such as the loader, the cyclic handler, and the Eventflag are implemented as components.
+The facilities such as the RiteVM, the scheduler, and the Eventflag are implemented as components.
 Developers can easily add or remove the facilities as necessary.

### 2016-02-10 EMSOFT2016/thesis.tex
update

@@
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
+In the proposed framework, RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
 Synchronization of starting multiple tasks is also implemented with Eventflag. 
@@
 One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly and the OS should be restarted.
-If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and mruby application codes are transferred from a host to a target device by Bluetooth.
-It can improve the efficiency.
-Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
-In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
-Thus that is a big burden on developers.
-Another new feature enables developers to run multitasking programs more easily.
-Specifically, a cyclic handler of switching tasks is implemented.
-This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+In the current development process, it is annoying that the SD card should be inserted and pulled out repeatedly and the OS should be restarted.
+%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
+%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
+Although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
+Thus, that is a big burden on developers.
 
-{\bf Contributions}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
-The proposed framework gives the contribution in the following points.
+This paper proposes mruby bytecode loader using Bluetooth and RiteVM scheduler for fairly executing mruby programs.
+To improve the development efficiency, mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
+RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+%Specifically, a cyclic handler of switching tasks is implemented.
+%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+
+{\bf Contributions}: The proposed framework gives the contribution in the following points.
 \begin{enumerate}
@@
 Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
- Thus, the software development efficiency is improved.
+The loader supports the countinuous loading, which saves the pairing time for Bluetooth.
+
 \item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
 \ There is a problem in multitasking of the current mruby on TECS.
-It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking.
-In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
-Synchronization of tasks is implemented.
-Multitasked programing makes the range of software expand.
+It is that developers need to be well acquainted with the RTOS if multiple mruby programs execute in multitasking.
+In the proposed framework, it is easy for developers to use multitasking because RiteVM sceduler switches tasks cyclically.
+Synchronization of multipe tasks is also implemented.
+
 \item To focus on the advantage of component-based developments: \mbox{}\\
@@
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:Design and Implementation} describe the design and implementation of the proposed framework in detail.
+Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework in detail.
 Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
@@
 TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps decrease the complexity and difficulty because the generated component diagram can visualize the structure of whole software.
-It can also help increase the productivity and reduce development duplication  because a common part of software is regarded as a component.
+TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
+It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.
 
@@
 Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
+RiteVM reads the own bytecode and executes it.
+The mruby applications run at the same time because of synchronization processing.
+RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
 
@@
 This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, all binary data including bytecodes are in an SD card.
-Developers must insert and pull out the SD card every time the source programs are modified.
+In the current system, all binary data including bytecodes are saved in an SD card.
+Developers must insert and pull out the SD card every time the application programs are modified.
 The OS in the target device should be also restarted.
-It causes a low work efficiency that such a work must be repeated.
+It causes a low development efficiency to repeat that.
 mruby bytecode loader using Bluetooth makes the developers' burden decrease.
-The work that an SD card is in and out needs to be done just once in the beginning.
+%The work that an SD card is in and out needs to be done just once in the beginning.
+Developers should just once carry out the work to insert the SD card and start the OS.
 
 mruby programs are consisted of mruby application and libraries.
-mruby application is the main code of the application.
-mruby libraries are the code defining the functions for application such as Ruby class. 
+mruby application is the main code, which developers should program.
+mruby libraries are the codes defining the functions for application such as Ruby classes. 
 The mruby bytecodes including mruby application and libraries can be sent and run.
 However it is wasteful in terms of the size and time to send because libraries are not frequently modified. 
-In the proposed framework, mruby application only sends, and mruby libraries are preserved in the SD card beforehand.
+In the proposed framework, mruby applications are only sent, and mruby libraries are preserved in the SD card beforehand.
 
 The development flow in mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-The RiteVM and mruby library are compiled and copied in the SD card at the first.
-These are assumed not to be modified.
-The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the source files (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
+The platform including RiteVM and mruby library is compiled and copied in the SD card at the first.
+%These are assumed not to be modified.
+%The binary data transferred with Bluetooth is the bytecode of the main source.
+In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
 The generated bytecodes are transferred from the host to the target device with Bluetooth.
+
+Moreover, developers can save the time of Bluetooth pairing since the loader can continuously load the bytecode.
 
@@
 
-\subsubsection{Component of mruby bytecode loader using Bluetooth} \mbox{}\\
+\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
 
-The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
+The proposed framework provides mruby bytecode loader using Bluetooth as TECS component.
 A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
@@
 TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
-The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
-A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
+The MrubyBluetooth1 is a component of RiteVM with mruby bytecode loader using Bluetooth.
+A bytecode in the host is transferred and received at the top of the component.
 In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.
@@
 
-Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of mruby bytecode loader using Bluetooth, which is like MrubyBluetooth1.
-First, a pointer of {\it mrb\_state} structure is initialized.
+Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of RiteVM with mruby bytecode loader using Bluetooth such as MrubyBluetooth1.
+The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
+
+First, a pointer of {\it mrb\_state} and {\it mrbc\_context} are initialized.
 {\it mrb\_state} is a set of states and global variables used in mruby.
-Second, the bytecode of mruby libraries is read.
+
+Second, RiteVM reads the bytecode of mruby libraries.
 mruby libraries are a set of Ruby classes such as motor class and sensor class.
@@
 {\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
-The irep is the pointer of the array stored the bytecode of mruby libraries.
-In short the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
-Third, the bytecode of the mruby program transferred with Bluetooth is read .
-The bytecode transmitted via Bluetooth is stored in an array of type uint8\_t, which is the same as type char.
+The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
+In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+
+Third, RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
+The mruby application bytecode is stored in an array of type uint8\_t, which is the same as type char.
 The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the {\it mrb\_state}.
-Finally, an mruby task runs.
-When the mruby program is modified, only the bytecode of the modified program should be transferred.
+Two bytecodes are read separately in the RiteVM.
+
+Finally, the mruby task runs.
+When the mruby application is modified, only the bytecode of the modified application should be transferred.
 mruby libraries need not be touched because libraries are not normally changed.
-The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
 \begin{figure}[t]
@@
       [omit]char_t *mrubyFile;
-      char_t *irepLib=C_EXP("&$cell_global$_irep");
-      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
-              __attribute__((nocommon));
+      char_t *irep=C_EXP("&$cell_global$_irep");
+%      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
+%              __attribute__((nocommon));
     };
@@
   /* Receive the bytecode via Bluetooth */
-  bluetooth_loader( ATTR_irepApp );
+  bluetooth_loader( App_bytecode );
   /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_irepLib, c);
+  mrb_load_irep_cxt(mrb, ATTR_irep, c);
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_irepApp, c);
+  mrb_load_irep_cxt(mrb, App_bytecode, c);
   if (mrb->exc) {
@@
 \begin{itemize}
-    \item Size and transfer time for mruby programs
+    \item Size and time for transferred mruby bytecodes
     \item Execution time with singletasking, co-routine, and multitasking
@@
 
-The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
+The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
 In the proposed framework, developers send only mruby application and prepare mruby library in advance.
@@
 In addition, the design can save the time to insert an SD card to restart an OS.
-These advantages lead to improving the work efficiency.
+These advantages lead improvement of the work efficiency.
 
@@
     \centering
-    \caption{Comparison of the size and transfer time between an mruby application including mruby libraries and not}
-    \begin{tabular}{c||c|c}
-                        & mruby Application \& Library & mruby Application  \\ \hline
-          Size          & 14,044 bytes                 & 199 bytes          \\ %\hline
-          Transfer Time & 356.015 msec                 & 58.708 msec        \\
+    \caption{Comparison of the size and load process time between an mruby application including mruby libraries and not}
+    \begin{tabular}{c||c|c|c}
+                            & App\&Lib   & App        &   App\&Lib / App \\ \hline
+          Bytecode Size     & 14,044 bytes & 199 bytes  &                    \\ %\hline
+          Load Process Time & 305.081 msec & 7.774 msec &                    \\
+          Compilation Time  &              &            &                    \\
     \end{tabular}
@@
 
+CodeSize
+
 \section{Related Work}
@@
     \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C function} & \shortstack{Legacy code of\\embedded system} & VM managenment & VM Scheduler & \shortstack{Synchronization of\\application} & Co-routine \\ \hline
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
@@
 The proposed framework provides developers the efficient development without disconnecting an SD card and restarting an OS.
-Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
+Furthermore, RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
 In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
 mruby bytecode loader using Bluetooth can improve the work efficiency.
-The proposed multitasking has the effectiveness in terms of execution time compared with singletasking and co-routine because of the low overhead.
+RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
 
 The proposed framework is developed in component-base by TECS.
-The facilities such as the RiteVM, the scheduler, and the Eventflag are implemented as components.
-Developers can easily add or remove the facilities as necessary.
-Component-based development can increase the productivity and decrease the complexity.
+The facilities such as the RiteVM, the RiteVM scheduler, and the Eventflag are implemented as components.
+Developers can easily add or remove the facilities as necessary, and also reuse them.
+Component-based development can increase productivity and decrease complexity.
 

### 2016-02-11 EMSOFT2016/thesis.tex
update

@@
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-In the proposed framework, RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
 Synchronization of starting multiple tasks is also implemented with Eventflag. 
@@
 
-This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
+%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
 mruby on TECS has several problems at present.
-One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
+One of the problems is that software development efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
 In the current development process, it is annoying that the SD card should be inserted and pulled out repeatedly and the OS should be restarted.
@@
 
-This paper proposes mruby bytecode loader using Bluetooth and RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
-RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
+To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
+The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
 %Specifically, a cyclic handler of switching tasks is implemented.
@@
 \begin{enumerate}
-\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
-\ mruby bytecode loader using Bluetooth helps developers develop software.
-Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
-The loader supports the countinuous loading, which saves the pairing time for Bluetooth.
+\item To improve the software development efficiency: \mbox{}\\
+\ Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
+The loader supports the countinuous loading, which saves the Bluetooth set-up time.
+Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
+\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
+\ Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
+In additon, synchronization of multipel tasks is also implemented.
 
-\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
-\ There is a problem in multitasking of the current mruby on TECS.
-It is that developers need to be well acquainted with the RTOS if multiple mruby programs execute in multitasking.
-In the proposed framework, it is easy for developers to use multitasking because RiteVM sceduler switches tasks cyclically.
-Synchronization of multipe tasks is also implemented.
-
-\item To focus on the advantage of component-based developments: \mbox{}\\
-\ The proposed framework has been developed with component-based.
-Component-based development gives various benefits.
- This paper shows the specific examples for the benefits of component-based development. 
+\item To focus on the benefits of component-based developments: \mbox{}\\
+\ This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
@@
 In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
-RiteVM is a VM in mruby, that runs mruby programs.
+A RiteVM is a VM in mruby, that runs mruby programs.
 The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by RiteVM.
+The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
 The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
@@
 Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
-RiteVM reads the own bytecode and executes it.
+The RiteVM reads the own bytecode and executes it.
 The mruby applications run at the same time because of synchronization processing.
-RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
+The RiteVM scheuler switches tasks as multiple tasks can run in concurrent.
 
@@
 \end{figure}
+
 \subsection{mruby Bytecode Loader Using Bluetooth}
 \label{sec:mruby bytecode loader using Bluetooth}
-This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
+This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
 In the current system, all binary data including bytecodes are saved in an SD card.
@@
 It causes a low development efficiency to repeat that.
-mruby bytecode loader using Bluetooth makes the developers' burden decrease.
+An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
 %The work that an SD card is in and out needs to be done just once in the beginning.
@@
 The mruby bytecodes including mruby application and libraries can be sent and run.
-However it is wasteful in terms of the size and time to send because libraries are not frequently modified. 
-In the proposed framework, mruby applications are only sent, and mruby libraries are preserved in the SD card beforehand.
+However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
+The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved in the SD card beforehand.
+Due to this design, RiteVMs can share the mruby libraries.
+In additon, a RiteVM can use the own library that other RiteVMs should not use.
 
-The development flow in mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-The platform including RiteVM and mruby library is compiled and copied in the SD card at the first.
+The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
+The platform including RiteVMs and mruby library is compiled and copied in the SD card at the first.
 %These are assumed not to be modified.
@@
 
-The proposed framework provides mruby bytecode loader using Bluetooth as TECS component.
-A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
+The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
+The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
+The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
 This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.
@@
 
-Second, RiteVM reads the bytecode of mruby libraries.
+Second, the RiteVM reads the bytecode of mruby libraries.
 mruby libraries are a set of Ruby classes such as motor class and sensor class.
@@
 
-Third, RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
-The mruby application bytecode is stored in an array of type uint8\_t, which is the same as type char.
+Third, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
+The mruby application bytecode is stored in an array of type uint8\_t such as {\it irepApp}, which is a tMrubyBluetooth variable as shown in \ref{celltype_mrubybluetooth}.
 The array is different from that of holding the mruby library bytecode.
@@
       char_t *irep=C_EXP("&$cell_global$_irep");
-%      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
-%              __attribute__((nocommon));
+    };
+    var{
+        uint8_t *irepApp;
     };
@@
 \end{lstlisting}
-\caption{Celltype Description for mruby bytecode loader using Bluetooth}
+\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
 \label{celltype_mrubybluetooth}
@@
   /* Receive the bytecode via Bluetooth */
-  bluetooth_loader( App_bytecode );
+  bluetooth_loader( VAR_irepApp );
   /* Load mruby library bytecode and run */
@@
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, App_bytecode, c);
+  mrb_load_irep_cxt(mrb, VAR_irepApp, c);
   if (mrb->exc) {
@@
 \end{lstlisting}
-\caption{Main code for mruby bytecode loader using Bluetooth}
+\caption{Main code for RiteVM with mruby bytecode loader using Bluetooth}
 \label{maincode_mrubybluetooth}
@@
 
-Besides, as another method, {\it delay}, a service call of $\mu$ITRON, can be used for multitasking.
+Besides, as another method, {\it delay()}, a service call of $\mu$ITRON, can be used for multitasking.
 This service call delays the execution of the own task for the time of the argument.
-In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
+%In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
+{\it delay()} is needed when scheduling fixed-priority tasks.
+However, the programming applied to {\it delay()} is difficult to use in the case of fair scheduling.
 
-In the proposed framework, as an approach for multitask processing, RiteVM scheduler is implemented.
-The RiteVM scheduler is a fair scheduler and runs multiple tasks equally.
+As an approach for multitask processing, the proposed framework provides the RiteVM scheuler which is a fair scheduler and runs multiple tasks equally.
+The RiteVM scheuler is utilized only when application tasks have the same priority.
+mruby applications can run in concurrent without developers calling the OS's function.
+The application programs can also utilize the existing programs since the structures of the programs are not changed.
 
@@
 
-The RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
@@
 
-In the framework, RiteVM, RiteVM scheduler, and Eventflag are implemented as components.
+In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
+For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
+This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
 
@@
 
-These evaluations are performed in order to indicate that mruby bytecode loader improves the work efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
+These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
 This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
@@
 In addition, the design can save the time to insert an SD card to restart an OS.
-These advantages lead improvement of the work efficiency.
+These advantages lead improvement of the software development efficiency.
 
@@
 \label{sec:Conclusion}
-This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
-The proposed framework provides developers the efficient development without disconnecting an SD card and restarting an OS.
-Furthermore, RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
-In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
-mruby bytecode loader using Bluetooth can improve the work efficiency.
-RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
+This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
+The loader provides developers with the software development efficiency without disconnecting an SD card and restarting an OS.
+The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
+%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
+The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
+In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
+The loader can improve the software development efficiency on mruby on TECS.
+The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
 
 The proposed framework is developed in component-base by TECS.
-The facilities such as the RiteVM, the RiteVM scheduler, and the Eventflag are implemented as components.
-Developers can easily add or remove the facilities as necessary, and also reuse them.
+The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
+Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
 Component-based development can increase productivity and decrease complexity.
@@
 Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
-%%%%%%%%%%%%%
-% Reference %
-%%%%%%%%%%%%%
+
+%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{IEEEtranBST2/IEEEtran}

### 2016-02-11 thesis/abstract.tex
update

@@
 
-表\ref{tab:comparion}に，提案フレームワークと既存フレームワークの比較を示す.
+表\ref{tab:comparison}に，提案フレームワークと既存フレームワークの比較を示す.
 提案フレームワークでは，Bluetoothを用いたバイトコードローダに加え，VMスケジューラおよびアプリケーションの同期が可能になった.
@@
     \end{tabular}
-    \label{tab:comparion}
+    \label{tab:comparison}
 \end{table}
@@
     ``mruby on TECS: Component-Based Framework for Running Script Program," 
-    Proceedings of the 18th IEEE International Symposium on Real-Time Distributed Computing (ISORC), 
+    in Proceedings of the 18th IEEE International Symposium on Real-Time Distributed Computing (ISORC), 
     pp.252-259, 

### 2016-02-11 thesis/thesis.tex
update

@@
 %
-\input{dummy/dummy.tex}
-\documentclass[conference,compsoc]{IEEEtran}
-\bibliographystyle{IEEEtranBST2/IEEEtran}
+\input{../EMSOFT2016/dummy/dummy.tex}
+\documentclass[a4j,12pt,oneside,openany,english]{jsbook}
 \usepackage{url}
@@
 \usepackage{amssymb}
+\usepackage{utf8/book2report}
+\usepackage{utf8/thesis}
+\usepackage{lscape}
 \usepackage{listings,jlisting}
@@
 
-\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
-\author{Takuro Yamamoto}
-\date{\today}
+% \title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+% \author{Takuro Yamamoto}
+% \date{\today}
 
 \begin{document}
-\maketitle
+\thispagestyle{empty}
+\begin{center}
+\vspace*{5mm}
+{\Huge {\bf Bachelor's Thesis}}\\
+\vspace{2cm}
+%{\Large 題\hspace{8mm}目}\\
+%\vspace{1cm}
+\underline{\LARGE{mruby Bytecode Loader}} \\
+\vspace{0.5cm}
+\underline{\Large{Using Bluetooth in Multi-VM Environment}} \\
+\vspace{12mm}
+{\large Supervisor}\\
+\vspace{6mm}
+\underline{\Large Professor Toshimitsu Ushio}\\
+\underline{\Large Assistant Professor Takuya Azumi}\\
+\vspace{8mm}
+{\large By}\\
+\vspace{6mm}
+\underline{\Large Takuro Yamamoto}\\
+\vspace{10mm}
+{\Large February 15, 2016}\\
+\vspace{14mm}
+{\Large Division of Systems Science and Applied Informatics,\\Department of Systems Science,\\Schoolo of Engineering Science, Osaka University}\\
+\end{center}
+\clearpage
+\setcounter{page}{0}
+\pagenumbering{roman}
+%\maketitle
+
 \begin{abstract}
@@
 mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compailation.
+mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compilation.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-In the proposed framework, the cyclic handler switching tasks is implemented, and multitasking processing is more easy-to-use than that of mruby on TECS.
+In the proposed framework, RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+Synchronization of starting multiple tasks is also implemented with Eventflag. 
 Experimental results demonstrate the advantages of the proposed framework.
 \end{abstract}
-\section{Introduction}
+\clearpage
+\tableofcontents
+\clearpage
+\setcounter{page}{0}
+\pagenumbering{arabic}
+\chapter{Introduction}
 In these days, embedded systems have been required the high-quality and the high-performance.
@@
 This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
-mruby on TECS has some problems at present.
+mruby on TECS has several problems at present.
 One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-In the current development process, it is annoying that the SD card should be insert and pulled out repeatedly.
-If a new feature, mruby bytecode loader Bluetooth, is used, the procedure is carried out only once at the beginning and a program code is transferred from a host to a target device by Bluetooth.
-It can improve the efficiency.
-Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks would not run unless a OS's function must be called by developers.
-In addition developers must prepare as many VMs as the number of threads because one RiteVM supports only one thread.
-Thus that is a big burden on developers.
-Another new feature enables developers to run a multitask programs more easily.
-Specifically, a cyclic handler of switching tasks is implemented.
-This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+In the current development process, it is annoying that the SD card should be inserted and pulled out repeatedly and the OS should be restarted.
+%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
+%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
+Although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
+Thus, that is a big burden on developers.
 
-{\bf Contributions}: This paper proposes mruby bytecode loader using Bluetooth and user-friendly multitasking.
-The proposed framework gives the contribution in the following points.
+This paper proposes mruby bytecode loader using Bluetooth and RiteVM scheduler for fairly executing mruby programs.
+To improve the development efficiency, mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
+RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+%Specifically, a cyclic handler of switching tasks is implemented.
+%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+
+{\bf Contributions}: The proposed framework gives the contribution in the following points.
 \begin{enumerate}
@@
 Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
-Thus, the software development efficiency is improved.
+The loader supports the countinuous loading, which saves the pairing time for Bluetooth.
+
 \item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
 \ There is a problem in multitasking of the current mruby on TECS.
-It is that developers need to be well acquainted the RTOS if multiple mruby programs execute in multitasking.
-In the proposed framework, it is easy for developers to use multitasking because multiple tasks are switched cyclically.
-Multitasked programing makes the range of software expand.
+It is that developers need to be well acquainted with the RTOS if multiple mruby programs execute in multitasking.
+In the proposed framework, it is easy for developers to use multitasking because RiteVM sceduler switches tasks cyclically.
+Synchronization of multipe tasks is also implemented.
+
+\item To focus on the advantage of component-based developments: \mbox{}\\
+\ The proposed framework has been developed with component-based.
+Component-based development gives various benefits.
+ This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
@@
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:mruby bytecode loader using Bluetooth} and Section \ref{sec:Multitask} describe the design and implementation of the proposed framework in detail.
-Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discuses related work, and then Section \ref{sec:Conclusion} concludes.
+Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework in detail.
+Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
 
-\section{Background}
+\chapter{Background}
 \label{sec:Background}
-Figure \ref{fig:proposed} shows a system model of the proposed framework.
+Figure \ref{fig:proposed} shows the system model of the proposed framework.
 The bytecodes are transferred from the host to the target device with Bluetooth.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/proposed.pdf}
     \caption{System Model}
@@
 
-\subsection{mruby}
+\section{mruby}
 \label{sec:mruby}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/mruby.pdf}
     \caption{Mechanism of mruby/RiteVM}
@@
 
-\subsection{TECS}
+\section{TECS}
 \label{sec:TECS}
 TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps decrease the complexity and difficulty because the generated component diagram can visualize the structure of whole software.
-It can also help increase the productivity and reduce development duplication  because a common part of software is regarded as a component.
+TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
+It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.
 
@@
 
-\subsubsection{Component Model}\mbox{}\\
+\subsection{Component Model}\mbox{}\\
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
     \caption{Component Diagram}
@@
 
-\subsubsection{Component Description}\mbox{}\\
+\subsection{Component Description}\mbox{}\\
 
@@
 
-\subsection{mruby on TECS}
+\section{mruby on TECS}
 \label{sec:mruby on TECS}
@@
 
-\subsubsection{System Model}\mbox{}\\
+\subsection{System Model}\mbox{}\\
 
-The system model of mruby on TECS is shown in Figure \ref{fig:system_model}.
+The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
 Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
-    \caption{System Model}
-    \label{fig:system_model}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/mrubyontecs.pdf}
+    \caption{System Model of existing mruby on TECS}
+    \label{fig:mrubyontecs}
 \end{figure}
 
-\subsubsection{mruby-TECS Bridge}\mbox{}\\
+\subsection{mruby-TECS Bridge}\mbox{}\\
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/mruby_TECS_bridge.pdf}
     \caption{mruby-TECS Bridge}
@@
 
+\chapter{Design and Implementation}
+\label{sec:Design and Implementation}
+Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
+Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
+RiteVM reads the own bytecode and executes it.
+The mruby applications run at the same time because of synchronization processing.
+RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/system_model.pdf}
+    \caption{Detailed System Model of the proposed framework}
+    \label{fig:system_model}
+\end{figure}
+
 \section{mruby Bytecode Loader Using Bluetooth}
@@
 This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, all binary data including bytecodes are in an SD card.
-Developers must insert and pull out the SD card every time the source programs are modified.
-It causes a low work efficiency that such a work must be repeated.
+In the current system, all binary data including bytecodes are saved in an SD card.
+Developers must insert and pull out the SD card every time the application programs are modified.
+The OS in the target device should be also restarted.
+It causes a low development efficiency to repeat that.
 mruby bytecode loader using Bluetooth makes the developers' burden decrease.
-The work that an SD card is in and out needs to be done just once in the beginning.
+%The work that an SD card is in and out needs to be done just once in the beginning.
+Developers should just once carry out the work to insert the SD card and start the OS.
 
 mruby programs are consisted of mruby application and libraries.
-mruby application is the main code of the application.
-mruby libraries are the code defining the functions for application such as Ruby class. 
+mruby application is the main code, which developers should program.
+mruby libraries are the codes defining the functions for application such as Ruby classes. 
 The mruby bytecodes including mruby application and libraries can be sent and run.
 However it is wasteful in terms of the size and time to send because libraries are not frequently modified. 
-In the proposed framework, mruby application only sends, and mruby libraries are preserved in the SD card beforehand.
+In the proposed framework, mruby applications are only sent, and mruby libraries are preserved in the SD card beforehand.
 
 The development flow in mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-The RiteVM and mruby library are compiled and copied in the SD card at the first.
-These are assumed not to be modified.
-The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the source files (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
+The platform including RiteVM and mruby library is compiled and copied in the SD card at the first.
+%These are assumed not to be modified.
+%The binary data transferred with Bluetooth is the bytecode of the main source.
+In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
 The generated bytecodes are transferred from the host to the target device with Bluetooth.
+
+Moreover, developers can save the time of Bluetooth pairing since the loader can continuously load the bytecode.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/bluetooth_loader.pdf}
     \caption{Development Flow in mruby bytecode loader using Bluetooth}
@@
 
-\subsection{Component of mruby bytecode loader using Bluetooth}
-The proposed framework provides components of mruby bytecode loader using Bluetooth to use the function.
+\subsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
+
+The proposed framework provides mruby bytecode loader using Bluetooth as TECS component.
 A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
@@
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
-TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:ht-tecs}.
-The MrubyBluetooth1 is a component of mruby bytecode loader using Bluetooth.
-A bytecode which is a compiled mruby program in the host is transferred and received at the top of the mruby bytecode loader using Bluetooth component.
+TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
+The MrubyBluetooth1 is a component of RiteVM with mruby bytecode loader using Bluetooth.
+A bytecode in the host is transferred and received at the top of the component.
 In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/component_bluetooth.pdf}
     \caption{Component Diagram of mruby bytecode loader using Bluetooth}
@@
 {\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
-The irep is the pointer of the array stored the bytecode of mruby libraries.
-In short the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
-Third, the bytecode of the mruby program transferred with Bluetooth is read .
-The bytecode transmitted via Bluetooth is stored in an array of type uint8\_t, which is the same as type char.
+The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
+In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+
+Third, RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
+The mruby application bytecode is stored in an array of type uint8\_t, which is the same as type char.
 The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the {\it mrb\_state}.
-Finally, an mruby task runs.
-When the mruby program is modified, only the bytecode of the modified program should be transferred.
+Two bytecodes are read separately in the RiteVM.
+
+Finally, the mruby task runs.
+When the mruby application is modified, only the bytecode of the modified application should be transferred.
 mruby libraries need not be touched because libraries are not normally changed.
-The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
 \begin{figure}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/control_flow.pdf}
     \caption{Control Flow of mruby bytecode loader using Bluetooth}
@@
 This service call delays the execution of the own task for the time of the argument.
-In the approach of {\it delay} fubction, developers have to schedule as the same as co-routine.
+In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
 
-In the proposed framework, as an approach for multitask processing, {\it rotateReadyQueue}, a service call of $\mu$ITRON, is implemented.
-{\it rotateReadyQueue} rotates the precedence of the task with the priority of the argument.
-A cyclic handler calls {\it rotateReadyQueue}, which enables developers to develop applications without concern for multitasking.
+In the proposed framework, as an approach for multitask processing, RiteVM scheduler is implemented.
+The RiteVM scheduler is a fair scheduler and runs multiple tasks equally.
 
-\subsection{rotateReadyQueue}
+\subsection{RiteVM Scheduler} \mbox{}\\
+
+The RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+{\it rotateReadyQueue} is described as follows.
+
 The case is assumed that there are two tasks with the same priority, and both tasks are in an infinite loop.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
     \caption{rotateReadyQueue}
@@
 
-\subsection{Component of Cyclic Handler}
+\subsection{Component of RiteVM Scheduler} \mbox{}\\
+
 Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
@@
 In another part, the priority of CyclicMain {\it cell} is described.
-EV3\_MRUBY\_VM\_PRIORITY defines the priority of mruby tasks.
+RITEVM\_PRIORITY defines the priority of mruby tasks.
 In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
-If developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
-This ease comes from component-based development with TECS.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/cyclic_handler.pdf}
     \caption{Component Diagram of Cyclic Handler}
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
+\subsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
+
 In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
     \caption{The design for Eventflag using TECS}
@@
 
-\section{Experimental Evaluation}
+\section{Benefits of Component-Based Development}
+This section describes the design using the benefits of component-based development.
+
+In the framework, RiteVM, RiteVM scheduler, and Eventflag are implemented as components.
+Therefore, developers can easily add or remove these components and also reuse them.
+For example, if developers do not need the cyclic handler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tCyclicHandler.cdl$>$);}.
+
+In additon, the code size can desrease by developing with component-based. 
+In the proposed framework, the advantage is applied in the Eventflag component.
+The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
+This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
+Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
+In additon, the components of Eventflag are built with {\it [optional]} in TECS.
+{\it [optional]} means that the codes are run only when the call port is connected.
+The .c file does not be rewritten even if developers do not use Eventflag.
+
+\chapter{Experimental Evaluation}
 \label{sec:Evaluation}
@@
 \begin{itemize}
-    \item the comparison of the size and transfer time between an mruby application including mruby library and not
-    \item the comparison of the application execution time with singletasking, co-routine, and multitasking
-    \item the comparison of the overhead for each cyclic period of calling {\it rotateReadyQueue}
+    \item Size and time for transferred mruby bytecodes
+    \item Execution time with singletasking, co-routine, and multitasking
+    \item Overhead for cyclic time
+    \item Code size using the benefit of CBD 
 \end{itemize}
@@
 
-The size and transfer time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-The bytecode of mruby application including library is larger and slower than that of only mruby application in terms of size and transfer time.
+The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
 In the proposed framework, developers send only mruby application and prepare mruby library in advance.
 Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to insert an SD card.
-These advantages lead to improving the work efficiency.
+In addition, the design can save the time to insert an SD card to restart an OS.
+These advantages lead improvement of the work efficiency.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/comparison_s_c_m.pdf}
     \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
+    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/comparison_msec.pdf}
     \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
@@
 
-\section{Related Work}
+CodeSize
+
+\chapter{Related Work}
 \label{sec:Related work}
+The open-source run-time systems for scripting languages have been proposed such as follow:
+python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
-\begin{table*}[t]
-    \centering
-    \caption{Comparion of the proposed and previous work}
-    \begin{tabular}{c||c|ccc}
-        & Bluetooth Loader & \shortstack{Preemptive-multitask\\(multi-VM)} & \shortstack{Nonpreemptive-multitask\\(co-routine)} & GIL \\ \hline
-        Lua \cite{url:Lua}, \cite{par:Lua} &            & -          & \checkmark &            \\
-        Owl system \cite{par:owl}                         &            & -          & -          & \checkmark \\
-        mruby \cite{par:mruby}, \cite{url:mruby}                             &            &            & \checkmark &            \\
-        mruby on TECS \cite{par:mrubyonTECS}                     &            & \checkmark & \checkmark &            \\
-        Proposed framework& \checkmark & \checkmark & \checkmark &            \\
-    \end{tabular}
-    \label{tab:comparion}
-\end{table*}
-The open-source run-time systems for scripting languages have been proposed such as follow:
-Lua \cite{url:Lua}, \cite{par:Lua}, the Owl system \cite{par:owl}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
+The VM runs a significant subset of Python language with few resources on a microcontroller.
+p14p can run multiple stackless green threads.
 
-Lua is one of the most popular script languages for embedded systems.
+The Owl system is an embedded Python run-time system.
+The Owl is a complete system for ARM Cortex-M3 microcontrollers.
+The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
+The interpreter of the Owl system is the same as that of python-on-a-chip.
+
+eLua offers the full implementation of Lua programming language to the embedded systems.
+Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
 Lua supports co-routine, referred to collaborative multitasking.
@@
 Thus, a Lua co-routine is not like multitasks in multitask systems.
-
-The Owl system is an embedded Python run-time system.
-The Owl is a complete system for ARM Cortex-M3 microcontrollers.
-The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip \cite{url:python-on-a-chip}.
-python-on-a-chip supports multitask managed by GIL (Global Interpreter Lock).
-GIL locks a CPU in order to prevent the non-thread-safe code from sharing the other threads.
-GIL leads the limitation of the concurrency on multitasking.
 
@@
 
-Table \ref{tab:comparion} shows a comparison between the proposed framework and previous work.
+Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
 
-\section{Conclusion}
+\begin{landscape}
+\begin{table}[t]
+    \centering
+    \caption{Comparion of the proposed and previous work}
+    \footnotesize
+    \begin{tabular}{c||c|ccccccc}
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
+        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & $\triangle$&            & \checkmark \\
+        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
+    \end{tabular}
+    \label{tab:comparison}
+\end{table}
+\end{landscape}
+
+\chapter{Conclusion}
 \label{sec:Conclusion}
@@
 The proposed framework provides developers the efficient development without disconnecting an SD card and restarting an OS.
-Furthermore, the proposed multitasking can be use more easily than the current mruby on TECS.
+Furthermore, RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
 In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
 mruby bytecode loader using Bluetooth can improve the work efficiency.
-The proposed multitasking has the effectiveness in terms of execution time compared with singletasking and co-routine because of the low overhead.
+RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
 
 The proposed framework is developed in component-base by TECS.
-The facilities such as the loader, the cyclic handler, and the Eventflag are implemented as components.
-Developers can easily add or remove the facilities as necessary.
-Component-based development can increase the productivity and decrease the complexity.
+The facilities such as the RiteVM, the RiteVM scheduler, and the Eventflag are implemented as components.
+Developers can easily add or remove the facilities as necessary, and also reuse them.
+Component-based development can increase productivity and decrease complexity.
 
@@
 Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
-%%%%%%%%%%%%%
-% Reference %
-%%%%%%%%%%%%%
-\bibliography{ref}
+
+%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgement}
+	I would like to express my deep sense of gratitude to my adviser Professor
+	Toshimitsu Ushio and Assistant Professor Takuya Azumi, Graduate School of Engineering Science, Osaka University,
+	for their invaluable, constructive advice and constant encouragement during this work.
+	Professor Ushio and Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
+
+    I also would like to thank all members of Ushio Laboratory for their kind help and cooperation.
+\end{acknowledgement}
+
+%%%%%%%%%%%% Publication List %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{utf8/myjunsrt}
+\bibliography{../EMSOFT2016/ref}
 

### 2016-02-12 EMSOFT2016/thesis.tex
update

@@
 \lstset{%
-    language={},
+    language={c},%
     basicstyle={\small},%
@@
     commentstyle={\small\itshape},%
-    keywordstyle={\small\bfseries},%
+    keywordstyle={\small},%\bfseries},%
     ndkeywordstyle={\small},%
@@
     numbersep=1zw,%
-    lineskip=-0.5ex%
+    %lineskip=-0.5ex%
 }
@@
 mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compilation.
+mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
@@
 mruby on TECS has several problems at present.
-One of the problems is that software development efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-In the current development process, it is annoying that the SD card should be inserted and pulled out repeatedly and the OS should be restarted.
+One of the problems is low software development efficiency.
+mruby on TECS only supports a strage device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
+For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
+Developers should also restart an OS on a target device.
 %Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
 %In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
-Although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
-Thus, that is a big burden on developers.
+Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
+These problem are a big burden on developers.
 
 This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
+To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
 The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
@@
 
-{\bf Contributions}: The proposed framework gives the contribution in the following points.
+{\bf Contribution}: The proposed framework gives the contribution in the following points.
 \begin{enumerate}
-\item To improve the software development efficiency: \mbox{}\\
-\ Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
+    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage device and also to restart an OS.
 The loader supports the countinuous loading, which saves the Bluetooth set-up time.
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
-\ Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
+\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
 In additon, synchronization of multipel tasks is also implemented.
-
-\item To focus on the benefits of component-based developments: \mbox{}\\
-\ This paper shows the specific examples for the benefits of component-based development. 
+\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
@@
 signature sMotor{
-    int32_t getCounts(void);
-    ER resetCounts(void);
-    ER setPower([in]int power);
-    ER stop([in] bool_t brake);
-    ER rotate([in] int degrees, [in] uint32_t speed_abs,
-              [in] bool_t blocking);
-    void initializePort([in]int32_t type);
+    int32_t getCounts( void );
+    ER resetCounts( void );
+    ER setPower( [in]int power );
+    ER stop( [in] bool_t brake );
+    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
+              [in] bool_t blocking );
+    void initializePort( [in]int32_t type );
 };
@@
 This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, all binary data including bytecodes are saved in an SD card.
-Developers must insert and pull out the SD card every time the application programs are modified.
-The OS in the target device should be also restarted.
+In the current system, the platform including mruby bytecodes are saved in a storage device.
+Developers must rewrite the storage device every time the application programs are modified.
+The OS on the target device should be also restarted.
 It causes a low development efficiency to repeat that.
@@
 %The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to insert the SD card and start the OS.
+Developers should just once carry out the work to connect the storage device and start the OS.
 
@@
 However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
-The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved in the SD card beforehand.
+The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage device beforehand.
 Due to this design, RiteVMs can share the mruby libraries.
@@
 
-The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-The platform including RiteVMs and mruby library is compiled and copied in the SD card at the first.
+%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
+In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage device at the first.
 %These are assumed not to be modified.
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
-    \caption{Development Flow in mruby bytecode loader using Bluetooth}
-    \label{fig:bluetooth_loader}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
+%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
+%     \label{fig:bluetooth_loader}
+% \end{figure}
 
@@
 The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
-This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.
+This generated bytecode is prepared beforehand in the storage device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
 
@@
       [omit]char_t *mrubyFile;
-      char_t *irep=C_EXP("&$cell_global$_irep");
+      char_t *irep =
+                C_EXP("&$cell_global$_irep");
     };
@@
 void
-eMrubyBody_main(CELLIDX idx)
+eMrubyBody_main( CELLIDX idx )
 {
@@
   /* New mruby context */
-  c = mrbc_context_new(mrb);
+  c = mrbc_context_new( mrb );
   // Omit: initialization of mruby-TECS bridge
@@
   /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_irep, c);
+  mrb_load_irep_cxt( mrb, ATTR_irep, c );
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, VAR_irepApp, c);
-  if (mrb->exc) {
+  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
+  if ( mrb->exc ) {
     /* Failure to execute */
-    mrb_p(mrb, mrb_obj_value(mrb->exc));
-    exit(0);
+    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
+    exit( 0 );
   }
   /* Free mruby context */
-  mrbc_context_free(mrb, c);
+  mrbc_context_free( mrb, c );
   /* Free interpreter instance */
-  mrb_close(mrb);
+  mrb_close( mrb );
 }
@@
 The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
+Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
 The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
@@
 Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to insert an SD card to restart an OS.
+In addition, the design can save the time to connect a storage device to restart an OS.
 These advantages lead improvement of the software development efficiency.
@@
     \begin{tabular}{c||c|c|c}
-                            & App\&Lib   & App        &   App\&Lib / App \\ \hline
-          Bytecode Size     & 14,044 bytes & 199 bytes  &                    \\ %\hline
-          Load Process Time & 305.081 msec & 7.774 msec &                    \\
-          Compilation Time  &              &            &                    \\
+                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
+          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
+          Load Process Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
+          Compilation Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
     \end{tabular}
@@
 This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
-The loader provides developers with the software development efficiency without disconnecting an SD card and restarting an OS.
+The loader provides developers with the software development efficiency without rewriting a storage device and restarting an OS.
 The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.

### 2016-02-13 EMSOFT2016/thesis.tex
update

@@
 \documentclass[conference,compsoc]{IEEEtran}
-\usepackage{url}
 \usepackage[dvipdfmx]{graphicx}
 \usepackage{amssymb}
+\usepackage{enumerate,cite,url}
 \usepackage{listings,jlisting}
@@
     ndkeywordstyle={\small},%
-    stringstyle={\small\ttfamily},
+    stringstyle={\small\it},
     frame={tb},
@@
 One of the problems is low software development efficiency.
-mruby on TECS only supports a strage device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
+mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
 For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
@@
 \begin{enumerate}
-    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage device and also to restart an OS.
+    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
 The loader supports the countinuous loading, which saves the Bluetooth set-up time.
@@
 This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, the platform including mruby bytecodes are saved in a storage device.
-Developers must rewrite the storage device every time the application programs are modified.
+In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
+Developers must rewrite the storage/ROM device every time the application programs are modified.
 The OS on the target device should be also restarted.
@@
 %The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to connect the storage device and start the OS.
+Developers should just once carry out the work to connect the storage/ROM device and start the OS.
 
@@
 However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
-The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage device beforehand.
+The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
 Due to this design, RiteVMs can share the mruby libraries.
@@
 %The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage device at the first.
+In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
 %These are assumed not to be modified.
@@
 The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
-This generated bytecode is prepared beforehand in the storage device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
+This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
 
@@
 For example, motor class defines methods to rotate and stop a motor.
-The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
+The tMrubyBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
 The {\it mrubyFile} indicates the program files of mruby libraries.
@@
       [omit]char_t *mrubyFile;
-      char_t *irep =
-                C_EXP("&$cell_global$_irep");
+      char_t *irep = C_EXP("&$cell_global$_irep");
+      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
     };
     var{
-        uint8_t *irepApp;
+        [size_is(irepAppSize)] uint8_t *irepApp;
     };
@@
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
 {\it rotateReadyQueue} is described as follows.
@@
     \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
-    \caption{rotateReadyQueue}
+    \caption{The design of RiteVM sceduler}
     \label{fig:rotateReadyQueue}
@@
 
+In addtion, the end of mruby applications is synchronized to accept the continuous loading.
+The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
+All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.
+
 \begin{figure}[t]
@@
     \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
-    \caption{The design for Eventflag using TECS}
+    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
     \label{fig:Eventflag}
@@
 \begin{itemize}
+%    \item Execution time of the platform
     \item Size and time for transferred mruby bytecodes
@@
     \item Overhead for cyclic time
+%    \item Synchronization of mruby applications
     \item Code size using the benefit of CBD 
@@
 Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
-The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
-In the proposed framework, developers send only mruby application and prepare mruby library in advance.
-Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to connect a storage device to restart an OS.
+The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
+The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
+%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
+%Therefore, the design can send the bytecode faster.
+In addition, the design can save the time to connect a storage/ROM device to restart an OS.
 These advantages lead improvement of the software development efficiency.
@@
 
-CodeSize
+To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
+(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
+In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
+(B) is not modified, and can be utilized regardless of the number of RiteVMs.
+Moreover, lines of two .cdl files are equal.
+The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
+
+\begin{table}[t]
+    \centering
+    \caption{Lines of .c and .cdl file for the number of RiteVM}
+    \begin{tabular}{c||cc|c}
+                & (A)       & (B)     & Diff  \\ \hline
+        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
+        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
+        \multicolumn{3}{l}{  }\\
+        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
+    \end{tabular}
+    \label{tab:codesize}
+\end{table}
 
@@
     \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
@@
         mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & $\triangle$&            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
@@
 Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
+The proposed framework supports the loader, the VM scheuler, and synchronization of application.
 
@@
 This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
-The loader provides developers with the software development efficiency without rewriting a storage device and restarting an OS.
+The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
 The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.

### 2016-02-13 abstract/abstract.tex
update

--- 2016-02-11 thesis/abstract.tex
@@
 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
-さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
 
@@
     \includegraphics[width=7cm,clip]{Abst_SystemModel.pdf}
-    \caption{System Model}
+    \caption{システムモデル}
     \label{fig:system_model}
@@
     \centering
-    \caption{Comparion of the proposed and previous work}
+    \caption{関連研究}
     \scriptsize
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|c|c|c}
@@
     \end{tabular}
+    }
     \label{tab:comparison}

### 2016-02-13 thesis/thesis.tex
update

@@
 \documentclass[a4j,12pt,oneside,openany,english]{jsbook}
-\usepackage{url}
 \usepackage[dvipdfmx]{graphicx}
@@
 \usepackage{utf8/thesis}
+\usepackage{enumerate,cite,url}
 \usepackage{lscape}
@@
     commentstyle={\small\itshape},%
-    keywordstyle={\small\bfseries},%
+    keywordstyle={\small},%\bfseries},%
     ndkeywordstyle={\small},%
-    stringstyle={\small\ttfamily},
+    stringstyle={\small\it},
     frame={tb},
@@
 mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand in an SD card at the time of the first compilation.
+mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-In the proposed framework, RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
 Synchronization of starting multiple tasks is also implemented with Eventflag. 
@@
 
-This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and user-friendly multitask.
+%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
 mruby on TECS has several problems at present.
-One of the problems is that working efficiency is low because mruby on TECS only supports an SD card in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-In the current development process, it is annoying that the SD card should be inserted and pulled out repeatedly and the OS should be restarted.
+One of the problems is low software development efficiency.
+mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
+For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
+Developers should also restart an OS on a target device.
 %Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
 %In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
-Although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
-Thus, that is a big burden on developers.
+Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
+These problem are a big burden on developers.
 
-This paper proposes mruby bytecode loader using Bluetooth and RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, mruby bytecode loader using Bluetooth enables developers to insert an SD card only once at the beginning and to transfer mruby application codes from a host to a target device.
-RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
+To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
+The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
 %Specifically, a cyclic handler of switching tasks is implemented.
@@
 
-{\bf Contributions}: The proposed framework gives the contribution in the following points.
+{\bf Contribution}: The proposed framework gives the contribution in the following points.
 \begin{enumerate}
-\item To improve the  work efficiency in software development on mruby on TECS: \mbox{}\\
-\ mruby bytecode loader using Bluetooth helps developers develop software.
-Developers do not need to insert and pull out an SD card repeatedly and also to restart an OS.
-The loader supports the countinuous loading, which saves the pairing time for Bluetooth.
-
-\item To effectively execute multiple mruby programs in concurrent or/and parallel: \mbox{}\\
-\ There is a problem in multitasking of the current mruby on TECS.
-It is that developers need to be well acquainted with the RTOS if multiple mruby programs execute in multitasking.
-In the proposed framework, it is easy for developers to use multitasking because RiteVM sceduler switches tasks cyclically.
-Synchronization of multipe tasks is also implemented.
-
-\item To focus on the advantage of component-based developments: \mbox{}\\
-\ The proposed framework has been developed with component-based.
-Component-based development gives various benefits.
- This paper shows the specific examples for the benefits of component-based development. 
+    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
+The loader supports the countinuous loading, which saves the Bluetooth set-up time.
+Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
+\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
+In additon, synchronization of multipel tasks is also implemented.
+\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
@@
 \label{sec:mruby bytecode loader using Bluetooth}
-This section describes an additional feature of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, all binary data including bytecodes are saved in an SD card.
-Developers must insert and pull out the SD card every time the application programs are modified.
-The OS in the target device should be also restarted.
+This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
+In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
+Developers must rewrite the storage/ROM device every time the application programs are modified.
+The OS on the target device should be also restarted.
 It causes a low development efficiency to repeat that.
-mruby bytecode loader using Bluetooth makes the developers' burden decrease.
+An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
 %The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to insert the SD card and start the OS.
+Developers should just once carry out the work to connect the storage/ROM device and start the OS.
 
@@
 The mruby bytecodes including mruby application and libraries can be sent and run.
-However it is wasteful in terms of the size and time to send because libraries are not frequently modified. 
-In the proposed framework, mruby applications are only sent, and mruby libraries are preserved in the SD card beforehand.
+However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
+The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
+Due to this design, RiteVMs can share the mruby libraries.
+In additon, a RiteVM can use the own library that other RiteVMs should not use.
 
-The development flow in mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-The platform including RiteVM and mruby library is compiled and copied in the SD card at the first.
+%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
+In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
 %These are assumed not to be modified.
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/bluetooth_loader.pdf}
-    \caption{Development Flow in mruby bytecode loader using Bluetooth}
-    \label{fig:bluetooth_loader}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/bluetooth_loader.pdf}
+%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
+%     \label{fig:bluetooth_loader}
+% \end{figure}
 
@@
 
-The proposed framework provides mruby bytecode loader using Bluetooth as TECS component.
-A component of mruby bytecode loader using Bluetooth is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages RiteVM configuration such as automatically generates the bytecode in the build description.
-This generated bytecode is prepared beforehand in the SD card such as mruby libraries, and different from a bytecode transferred with Bluetooth.
+The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
+The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
+The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
+This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
 
@@
 
-Second, RiteVM reads the bytecode of mruby libraries.
+Second, the RiteVM reads the bytecode of mruby libraries.
 mruby libraries are a set of Ruby classes such as motor class and sensor class.
 For example, motor class defines methods to rotate and stop a motor.
-The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
+The tMrubyBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
 The {\it mrubyFile} indicates the program files of mruby libraries.
@@
       [omit]char_t *mrubyFile;
-      char_t *irep=C_EXP("&$cell_global$_irep");
-%      uint8_t irepApp[COUNT_STK_T(TMAX_APP_BINARY_SIZE)]
-%              __attribute__((nocommon));
+      char_t *irep = C_EXP("&$cell_global$_irep");
+      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
+    };
+    var{
+        [size_is(irepAppSize)] uint8_t *irepApp;
     };
@@
   /* New mruby context */
-  c = mrbc_context_new(mrb);
+  c = mrbc_context_new( mrb );
   // Omit: initialization of mruby-TECS bridge
   /* Receive the bytecode via Bluetooth */
-  bluetooth_loader( App_bytecode );
+  bluetooth_loader( VAR_irepApp );
   /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt(mrb, ATTR_irep, c);
+  mrb_load_irep_cxt( mrb, ATTR_irep, c );
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt(mrb, App_bytecode, c);
-  if (mrb->exc) {
+  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
+  if ( mrb->exc ) {
     /* Failure to execute */
-    mrb_p(mrb, mrb_obj_value(mrb->exc));
-    exit(0);
+    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
+    exit( 0 );
   }
   /* Free mruby context */
-  mrbc_context_free(mrb, c);
+  mrbc_context_free( mrb, c );
   /* Free interpreter instance */
-  mrb_close(mrb);
+  mrb_close( mrb );
 }
@@
 
-The RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
 {\it rotateReadyQueue} is described as follows.
@@
 
-When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
+When {\it rotateReadyQueue} is called, tasks with the same priority are switched.
 The argument of {\it rotateReadyQueue} is the priority.
@@
     \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
-    \caption{rotateReadyQueue}
+    \caption{The design of RiteVM sceduler}
     \label{fig:rotateReadyQueue}
@@
     \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
-    \caption{The design for Eventflag using TECS}
+    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
     \label{fig:Eventflag}
@@
 The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
-In the proposed framework, developers send only mruby application and prepare mruby library in advance.
-Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to insert an SD card to restart an OS.
-These advantages lead improvement of the work efficiency.
+The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
+Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
+The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
+The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
+%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
+%Therefore, the design can send the bytecode faster.
+In addition, the design can save the time to connect a storage/ROM device to restart an OS.
+These advantages lead improvement of the software development efficiency.
 
@@
 Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-
+The proposed framework supports the loader, the VM scheuler, and synchronization of application.
 \begin{landscape}
@@
         mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & $\triangle$&            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & 			   &            & \checkmark \\
         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
@@
 \label{sec:Conclusion}
-This paper has presented the mruby bytecode loader using Bluetooth in multi-VM on mruby on TECS.
-The proposed framework provides developers the efficient development without disconnecting an SD card and restarting an OS.
-Furthermore, RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
-In the evaluation, experimental results of the mruby bytecode loader and proposed multitasking show their advantages.
-mruby bytecode loader using Bluetooth can improve the work efficiency.
-RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
+This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
+The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
+The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
+%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
+The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
+In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
+The loader can improve the software development efficiency on mruby on TECS.
+The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
 
 The proposed framework is developed in component-base by TECS.
-The facilities such as the RiteVM, the RiteVM scheduler, and the Eventflag are implemented as components.
-Developers can easily add or remove the facilities as necessary, and also reuse them.
+The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
+Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
 Component-based development can increase productivity and decrease complexity.
@@
 
-    I also would like to thank all members of Ushio Laboratory for their kind help and cooperation.
+    I am deeply grateful to my advisers Hiroshi Oyama, Hiroshi Mimaki, Takuya Ishikawa, and Kazuaki Tanaka,
+    for their helpful comments on this thesis and warm encouragement.
+
+    Finally, I would like to thank all members of Ushio Laboratory for their kind help and cooperation.
 \end{acknowledgement}
-
-%%%%%%%%%%%% Publication List %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%% Publication List %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter*{Publication List}
+\section*{Domestic Conference Proceedings}
+\begin{enumerate}[{[}1{]}]
+\item
+    T. Yamamoto, H. Oyama and T. Azumi,
+    ``{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment},"
+    \emph{Proceedings of ETNET2016}, 2016.
+    (in Japanese)
+\end{enumerate}
+\addcontentsline{toc}{chapter}{Published List}
+
 \end{document}

### 2016-02-14 EMSOFT2016/thesis.tex
update

@@
 In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
+While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
 This result shows the proposed design is superior to co-routine in terms of execution time.
+The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
 Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
-The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
-Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
+%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
+%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
+The scheuler interrupts and switches tasks, which causes this overhead.
 
@@
 That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
+This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
 The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
@@
 The loader can improve the software development efficiency on mruby on TECS.
-The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.
+The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
+%because of the low overhead.
 

### 2016-02-14 thesis/thesis.tex
update

@@
 
-When {\it rotateReadyQueue} is called, tasks with the same priority are switched.
+When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
 The argument of {\it rotateReadyQueue} is the priority.

### 2016-02-17 ETNET2016/thesis.tex
add ETNET2016

--- 2016-02-14 EMSOFT2016/thesis.tex
@@
+%        File: thesis.tex
+%     Created: Tue Feb 16 06:00 PM 2016 J
+% Last Change: Tue Feb 16 06:00 PM 2016 J
 %
-% File: thesis.tex
-% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
-% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
-%
-\input{dummy/dummy.tex}
-\documentclass[conference,compsoc]{IEEEtran}
+\input{../dummy/dummy.tex}
+\documentclass[submit]{ipsj_v2/UTF8/ipsj}
+%\documentclass{ipsj}
+
+\usepackage{latexsym}
 \usepackage[dvipdfmx]{graphicx}
@@
 
-\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
-\author{Takuro Yamamoto}
-\date{\today}
+\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
+\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
+\def\|{\verb|}
+
+\setcounter{巻数}{57}
+\setcounter{号数}{1}
+\setcounter{page}{1}
+
+\受付{2015}{3}{4}
+%\再受付{2015}{7}{16}   %省略可能
+%\再再受付{2015}{7}{20} %省略可能
+\採録{2015}{8}{1}
 
 \begin{document}
+
+\title{Bluetoothを用いたマルチVM対応\\mrubyバイトコードローダ}
+
+\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+
+\affiliate{IPSJ}{情報処理学会\\
+IPSJ, Chiyoda, Tokyo 101--0062, Japan}
+
+\paffiliate{JU}{情報処理大学\\
+Johoshori University}
+
+\author{山本 拓朗}{Takuro Yamamoto}{IPSJ}[joho.taro@ipsj.or.jp]
+\author{大山 博司}{Hiroshi Oyama}{IPSJ}
+\author{安積 卓也}{Takuya Azumi}{IPSJ,JU}[gakkai.jiro@ipsj.or.jp]
+
+\begin{abstract}
+近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．
+
+組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
+
+現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
+さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+
+本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
+さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する.
+
+\end{abstract}
+
+\begin{jkeyword}
+情報処理学会論文誌ジャーナル，\LaTeX，スタイルファイル，べからず集
+\end{jkeyword}
+
+\begin{eabstract}
+This document is a guide to prepare a draft for submitting to IPSJ
+Journal, and the final camera-ready manuscript of a paper to appear in
+IPSJ Journal, using {\LaTeX} and special style files.  Since this
+document itself is produced with the style files, it will help you to
+refer its source file which is distributed with the style files.
+\end{eabstract}
+
+\begin{ekeyword}
+IPSJ Journal, \LaTeX, style files, ``Dos and Don'ts'' list
+\end{ekeyword}
+
 \maketitle
-\begin{abstract}
-In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
-For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
-In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
-To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
-The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
-mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
-In addition, multiple mruby programs cooperatively run in the proposed framework.
-A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
-Synchronization of starting multiple tasks is also implemented with Eventflag. 
-Experimental results demonstrate the advantages of the proposed framework.
-\end{abstract}
-\section{Introduction}
-In these days, embedded systems have been required the high-quality and the high-performance.
-Due to this trend, the complexity of embedded systems also increases and the scale is larger.
-For example, IoT (Internet of Things) applications.
-The low production cost and the short developing period of time are also needed.
 
-An approach of efficient software development is to use component-based techniques.
-CBD (Component-Based Development) is a design technique for constituting reusable components \cite{par:Crnkovic}.
-Complex and large scale software systems can be developed efficiently using component-based techniques.
-That is because software componentization provides high-reusability and easy verification.
-It also makes a system flexible in extensions and specification changes.
-There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems
+\section{はじめに}
+近年，組込みシステムは高品質・高性能化に伴い，複雑化・大規模化している．
+例えば，IoTアプリケーションがある．
+その上，製品の低コスト化や短期間での開発も要求されている．
 
-In addition, another approach of efficient software development is to develop with script languages.
-Most of current software are programmed in C language, and the development with C takes a high cost and more time to develop.
-Script languages make software engineering more efficient and shorten a development period because script languages have high-productivity from their usability.
-Java script, Perl, Python, Lua and Ruby are well-known as representative script languages.
+ソフトウェアを効率的に開発するアプローチのひとつに，コンポーネントベース開発がある．
+コンポーネントベース開発は，再利用可能なコンポーネントを構成するための設計手法である\cite{par:Crnkovic}．
+コンポーネント化されたソフトウェアは，再利用性が高く，検証が容易になるため，コンポーネントベース開発を適用することで，複雑かつ大規模なソフトウェアを効率的に開発することができる．
+システムの拡張や仕様変更にも柔軟に対応できる．
+組込みシステムのコンポーネント技術として，TECS\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SAVEapproach}がある．
 
-Although script languages are easy to use and read, their execution time are slower than C language's.
-For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
-Therefore, it is difficult to apply the script languages to embedded systems.
+効率的なソフトウェア開発のもう一つのアプローチとして，スクリプト言語がある．
+現在のソフトウェアのほとんどはC言語で開発されているが，C言語による開発はコストが高く，開発期間も長くなる．
+スクリプト言語は，その使いやすさから高い生産性をもっているため，効率的かつ短期間での開発ができる．
+有名なスクリプト言語として，Java script，Perl，Python，Lua，Rubyなどがある．
 
-mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
-It is integrated two technologies.
-One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
-The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS} \cite{url:TOPPERS}.
-mruby on TECS supports to effectively run mruby script language on embedded systems.
-mruby on TECS also makes execution time 100 times faster than that of mruby.
+しかし，スクリプト言語は可読性や使いやすさが高い反面，C言語よりも実行時間が遅い．
+組込みシステムにとって，最悪実行時間や応答時間といったリアルタイム性は非常に重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
 
-%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
-mruby on TECS has several problems at present.
-One of the problems is low software development efficiency.
-mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
-For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
-Developers should also restart an OS on a target device.
-%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
-%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
-Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
-These problem are a big burden on developers.
+%mruby on TECSは，スクリプト言語であるmruby使用したコンポーネントベース開発が可能なフレームワークである\cite{par:mrubyonTECS}．
+mruby on TECS は，mruby(軽量Ruby) と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである\cite{par:mrubyonTECS}.
+mruby on TECS では，mruby プログラムからC 言語の関数を呼ぶ機能を提供しており，mruby に比べて，アプリケーションを約100 倍速く実行できる.
 
-This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
-The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
-%Specifically, a cyclic handler of switching tasks is implemented.
-%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+現状のmruby on TECSでは，いくつかの問題がある．
+mruby on TECS は，mrubyプログラムをロードするための方法として，記憶装置しか対応していないため，作業効率が悪い．
+(LEGO MINDSTORMS EV3 のプラットフォーム\cite{par:EV3})
+mrubyプログラムを修正する度に，SDカードの抜き差しやROMへの書き込みを行う必要がある．
+%mruby on TECS では，mruby プログラムを修正する度にターゲットデバイスでSD カードまたはROMに書き込みし，OS を再起動する必要がある.
+さらに，mruby on TECS はマルチVMに対応してるが，複数のmruby アプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOS の機能を呼び出さなければならない.
 
-{\bf Contribution}: The proposed framework gives the contribution in the following points.
-\begin{enumerate}
-    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
-The loader supports the countinuous loading, which saves the Bluetooth set-up time.
-Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
-In additon, synchronization of multipel tasks is also implemented.
-\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
-\end{enumerate}
+% mrubyバイトコードローダによって，開発者ははじめの一度だけ記憶装置にプラットフォーム部分を書き込み，mrubyアプリケーションのバイトコードをホストからターゲットデバイスへBluetoothを用いて転送し，実行することが可能になる．
+% 繰り返してSDカードの抜き差しやROMへの書き込みをする手間が省けるため，作業効率は向上する．
+% RiteVMスケジューラは複数のmrubyアプリケーションを
+提案フレームワークは，mruby on TECS を拡張して，Bluetooth を用いたmruby バイトコードローダと，実用的なマルチタスク処理の実装を行った.
+提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する.
+ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する. 
+ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する.
+これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
+さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる.
 
-{\bf Organization}: The paper is organized as follows.
-Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework in detail.
-Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
+% Contribution: The proposed framework gives the contribution in the following points.
+% 1) To improve the software development efficiency:
+% Developers do not need to rewrite a storage/ROM device and also to restart an OS. 
+% The loader supports the countinuous loading, which saves the Bluetooth setup time. 
+% Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
+% 2) To effectively execute multiple mruby programs in concurrent or/and parallel: 
+% Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
+% In additon, synchronization of multiple tasks is also implemented.
+% 3) To focus on the benefits of component-based developments:
+% This paper shows the specific examples for the benefits of component-based development.
 
-\section{Background}
-\label{sec:Background}
-Figure \ref{fig:proposed} shows the system model of the proposed framework.
-The bytecodes are transferred from the host to the target device with Bluetooth.
-The RiteVMs and mruby library are assumed to be prepared in advance.
-Each bytecode is allocated to a RiteVM, respectively.
-Developers can run bytecodes transferred with Bluetooth in multitask.
+% Organization: The paper is organized as follows. 
+% Section 2 introduces the basic technologies i.e. mruby, TECS and mruby on TECS. 
+% Section 3 describes the design and implementation of the proposed framework in detail. 
+% Section 4 evaluates the proposed framework, Section 5 discusses related work, and then Section 6 concludes this paper.
+
+\section{既存フレームワーク}
+\label{fig:background}
+図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
+RiteVMとmrubyライブラリを含むプラットフォーム部分は，はじめにターゲットデバイス上で起動されている．
+mrubyアプリケーションのバイトコードは，ホストからターゲットデバイスへと転送される．
+それぞれバイトコードは，RiteVMに割り当てられ，並行して起動される．
+
+この章では，提案フレームワークのベースになっているmruby on TECSについて述べる．
+mruby on TECSで利用されているmrubyとTECSについても述べる．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/proposed.pdf}
     \caption{System Model}
@@
 
-This section describes mruby on TECS on which the proposed framework is based.
-mruby on TECS is a component-based framework for running script programs.
-In mruby on TECS, two technologies are integrated: mruby and TECS.
-To explain the system, mruby and TECS are also respectively described in this section.
+\subsection{mruby}
+mrubyは，ISO規格の一部に準拠したRubyの軽量実装である．
+Ruby\cite{url:Ruby}は，オブジェクト指向型のスクリプト言語である．
+特徴としてシンプルな文法なため読みやすくかつ使いやすい上に，C言語よりも少ないコード量で記述できる．
+他にも，クラスやメソッドといったオブジェクト指向関数，例外，ガベージコレクションなどの機能により，生産性を向上させることができる．
 
-\subsection{mruby}
-\label{sec:mruby}
-mruby is the light-weight implementation of Ruby programming language complying to part of the ISO standard.
+mrubyは，Rubyの可読性や使いやすさはそのままに，リソースが少なく起動が速いため，組込みシステムに適している．
+mrubyには，RiteVMと呼ばれるVMが実装されているため，どのOS上でもアプリケーションを起動させることができる．
+図\ref{fig:mruby}にRiteVMのメカニズムを示す．
+mrubyコンパイラは，mrubyプログラム(.rb)を，中間言語であるバイトコード(.mrb)にコンパイルする．
+RiteVMが実装されいれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
 
-Ruby is a object-oriented script language \cite{url:Ruby}.
-As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
-Ruby can run a program with fewer code lines than C language.
-Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.
-
-mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
-In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
-A RiteVM is a VM in mruby, that runs mruby programs.
-The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
-The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
 \begin{figure}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby.pdf}
     \caption{Mechanism of mruby/RiteVM}
@@
 \subsection{TECS}
-\label{sec:TECS}
-TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
-It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.
+TECS (TOPPERS Embedded Component System)は，組込みシステム向けのコンポーネントシステムである．
+TECSによるコンポーネントベース開発は，システム全体の構造を可視化するため，システムの複雑さや難しさを減らすことができる．
+さらに，ソフトウェアの共通部分はコンポーネントとして扱われるため，開発の重複を減らし，生産性を向上させる．
 
-The component deployment and composition in TECS are statically performed, which gives optimization.
-As a result, the overhead of execution time and memory consumption can be reduced.
-There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.
+TECSでのコンポーネントの生成と結合は静的に行われるため，最適化され，実行時間や消費メモリのオーバヘッドは少ない．
+他の特徴として，C言語での実装，ソースレベルでの移植性，コンポーネントの粒度が小さいことなどがある．
 
-\subsubsection{Component Model}\mbox{}\\
+\subsubsection{Component Model}
+図\ref{fig:component}にコンポーネント図の例を示す．
+{\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
 
-Figure \ref{fig:component} shows a component diagram.
-A {\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
 A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
     \caption{Component Diagram}
@@
 
-\subsubsection{Component Description}\mbox{}\\
-
+\subsubsection{Component Description}
 The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mrubyontecs.pdf}
     \caption{System Model of existing mruby on TECS}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby_TECS_bridge.pdf}
     \caption{mruby-TECS Bridge}
@@
 \label{sec:Design and Implementation}
+図\ref{fig:system_model}に提案フレームワークの詳細なシステムモデルを示す．
+ホストから転送されたmrubyアプリケーションのバイトコードは，それぞれのRiteVMに実装されたローダで受信され，同期処理により同時に実行される．
+RiteVMスケジューラがタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作することができる．
+　
 Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/system_model.pdf}
     \caption{Detailed System Model of the proposed framework}
@@
 \label{sec:mruby bytecode loader using Bluetooth}
-This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
-Developers must rewrite the storage/ROM device every time the application programs are modified.
-The OS on the target device should be also restarted.
-It causes a low development efficiency to repeat that.
-An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
-%The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to connect the storage/ROM device and start the OS.
+この章では，Bluetoothを用いたmrubyバイトコードローダについて述べる．
+現状のmruby on TECSでは，mrubyバイトコードをプラットフォームに組み込んでいるため，mrubyプログラムを修正する度にプラットフォーム部分をもう一度コンパイル・リンクし，SDカードやROMといったデバイスに再度書き込み，OSを再起動する必要がある．
+このような作業を繰り返すことで，作業効率は悪くなる．
+提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし記憶デバイスに書き込むのは，はじめの一度だけで良いため，作業効率を向上させることができる．
 
-mruby programs are consisted of mruby application and libraries.
-mruby application is the main code, which developers should program.
-mruby libraries are the codes defining the functions for application such as Ruby classes. 
-The mruby bytecodes including mruby application and libraries can be sent and run.
-However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
-The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
-Due to this design, RiteVMs can share the mruby libraries.
-In additon, a RiteVM can use the own library that other RiteVMs should not use.
+mrubyプログラムは，アプリケーション部分とライブラリ部分に分けられる．
+mrubyアプリケーションは，開発者が主にプログラムするメインのコードであり，mrubyライブラリには，motorクラスやsensorクラスといったRubyクラスのようにアプリケーションで利用される関数群が定義されている．
+アプリケーションとライブラリを含んだmrubyバイトコードを転送し，実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組込み，アプリケーション部分のみを転送する設計にした．
+このような設計にすることで，ライブラリは頻繁に変更されないため，毎回コンパイルする無駄を省くことができる．
+さらに，各RiteVMでライブラリを共有することや，RiteVM固有のライブラリを持つことも可能になる．
 
-%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
-%These are assumed not to be modified.
-%The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
-The generated bytecodes are transferred from the host to the target device with Bluetooth.
+提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している．
 
-Moreover, developers can save the time of Bluetooth pairing since the loader can continuously load the bytecode.
+\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
+提案フレームワークでは，mrubyバイトコードローダはTECSのコンポーネントとして提供されている．
+このコンポーネントは，RiteVMのコンポーネントの拡張として実装されている．(詳細については\cite{par:mrubyonTECS}を参照)
+このコンポーネントでは，転送されたバイトコードの受信に加え，RiteVMのコンフィグレーションが行われる．
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
-%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
-%     \label{fig:bluetooth_loader}
-% \end{figure}
-
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
-
-The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
-The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
-This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
-
-Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
-The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
-TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
-The MrubyBluetooth1 is a component of RiteVM with mruby bytecode loader using Bluetooth.
-A bytecode in the host is transferred and received at the top of the component.
-In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.
+図\ref{fig:component_bluetooth}に，MrubyTask1とMrubyBluetooth1のコンポーネントの例を示す．
+MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2 \ref{url:HRP2}\ref{par:HRP2})のタスクである．
+MrubyBluetooth1は，mrubyバイトコードを実装したRiteVMのコンポーネントであり，このコンポーネントのはじめで転送されてきたバイトコードを受信する．
+提案フレームワークでは，バイナリ転送プロトコルとして，ZMODEを適用した．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_bluetooth.pdf}
     \caption{Component Diagram of mruby bytecode loader using Bluetooth}
@@
 
-Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of RiteVM with mruby bytecode loader using Bluetooth such as MrubyBluetooth1.
-The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
+図\ref{fig:control_flow}に，ローダを実装したRiteVMがmrubyプログラムを実行するまでの制御フロー，図\ref{maincode_mrubybluetooth}には，RiteVMコンポーネントのソースコードを示す．
 
-First, a pointer of {\it mrb\_state} and {\it mrbc\_context} are initialized.
-{\it mrb\_state} is a set of states and global variables used in mruby.
+はじめに，{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する．
+{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
 
-Second, the RiteVM reads the bytecode of mruby libraries.
-mruby libraries are a set of Ruby classes such as motor class and sensor class.
-For example, motor class defines methods to rotate and stop a motor.
-The tMrubyBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
-The {\it mrubyFile} indicates the program files of mruby libraries.
-{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
-The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
-In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+次に，mrubyライブラリのバイトコードを読み込む．
+図\ref{celltype_mrubybluetooth}に示すように，tMrubyBluetoothのセルは属性を持っている．
+{\it mrubyFile}はmrubyライブラリのファイルを示しており，{\it [omit]}はTECSジェネレータによってのみ使えわれるため，この属性はメモリを消費することない．
+{\it irep}は，mrubyライブラリのバイトコードが格納されている配列へのポインタである．
+つまり，mrubyライブラリは始めのコンパイル時にコンポーネントの属性として，配列に保存されている．
 
-Third, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
-The mruby application bytecode is stored in an array of type uint8\_t such as {\it irepApp}, which is a tMrubyBluetooth variable as shown in \ref{celltype_mrubybluetooth}.
-The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the RiteVM.
+次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む．
+mrubyアプリケーションのバイトコードは，図\ref{celltype_mrubybluetooth}に示す，内部変数uint8\_t型の配列{\it irepApp}に格納されている．
+２つのバイトコードは，それぞれ別の配列に保存されており，別々に読み込まれる．
 
-Finally, the mruby task runs.
-When the mruby application is modified, only the bytecode of the modified application should be transferred.
-mruby libraries need not be touched because libraries are not normally changed.
+最後に，RiteVMはmrubyアプリケーションであるタスクを実行する．
+mrubyアプリケーションのプログラムが修正された場合は，そのバイトコードのみを再転送する．
+
 \begin{figure}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/control_flow.pdf}
     \caption{Control Flow of mruby bytecode loader using Bluetooth}
@@
 \label{sec:Multitask}
-This section describes implementation of multitasking in the proposed framework.
-mruby on TECS has supported multitasking.
-However, multitask processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for developers.
+この章では，提案フレームワークでのマルチタスク処理の設計にちて述べる．
+mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの知識を熟知している必要がある．
 
-One of approaches for multitasking is co-routine.
-Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\it resume} and {\it yield}. 
-(Ruby co-routine is defined in class Fiber \cite{url:co-routine})
-Co-routine is a non-preemptive multitasking, and does not receive the OS's support because developers have to switch tasks manually.
-Co-routine can not take advantage of multi core processing.
+マルチタスク処理のアプローチのひとつにコルーチンがある．
+コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並列動作を行うことができる．
+(Rubyのコルーチンは，Fiberクラスに定義されている．\cite{url:co-routine})
+コルーチンは，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるので，OSのサポートやマルチコアの恩恵を受けることができない．
 
-Besides, as another method, {\it delay()}, a service call of $\mu$ITRON, can be used for multitasking.
-This service call delays the execution of the own task for the time of the argument.
-%In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
-{\it delay()} is needed when scheduling fixed-priority tasks.
-However, the programming applied to {\it delay()} is difficult to use in the case of fair scheduling.
+その他のアプローチとして，μITRONのサービスコールである{\it delay()}使った手法がある．
+このサービスコールは，引数として与えられた時間だけ，そのタスクの起動を遅らせる．
+{\it delay()}は，固定優先度スケジューリングの場合に用いられるが，フェアスケジューリングの場合には使用することが難しい．
 
-As an approach for multitask processing, the proposed framework provides the RiteVM scheuler which is a fair scheduler and runs multiple tasks equally.
-The RiteVM scheuler is utilized only when application tasks have the same priority.
-mruby applications can run in concurrent without developers calling the OS's function.
-The application programs can also utilize the existing programs since the structures of the programs are not changed.
+提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを実装し，複数のタスクを平等に並行動作させる．
+このスケジューラはアプリケーションタスクが同じ優先度を持つ場合に利用でき，開発者がOSの関数を呼び出すことなく，マルチタスク処理が可能になる．
+その上，既存のアプリケーションプログラムの構造を変えること使うことができる．
 
-\subsubsection{RiteVM Scheduler} \mbox{}\\
+\subsubsection{RiteVM Scheduler}
+RiteVMスケジューラは，周期ハンドラであり，μITRONのサービスコールである{\it rotateReadyQueue}を呼び出す．
+{\it rotateReadyQueue}は，同優先度のタスクの実行を切り替える関数である．
+RiteVMスケジューラの設計を図\ref{fig:rotateReadyQueue}に示す．
 
-A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
-In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
-The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
-{\it rotateReadyQueue} is described as follows.
+無限ループを持った同優先度の2つのタスクの場合を考える．
+現状のシステムでは，始めにタスクが起動すると，そのタスクが無限ループに入るため，もう片方のタスクが起動することができない．
 
-The case is assumed that there are two tasks with the same priority, and both tasks are in an infinite loop.
-In the current system, when one task is executed first, another task would not be executed.
-That is because the task with first execution runs in the loop.
+{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示すように，タスクの起動が切り替わる．
+{\it rotateReadyQueue}の引数は，優先度である．
 
-When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
-The argument of {\it rotateReadyQueue} is the priority.
-
-The {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
-For example, three tasks are in the order: task 1, 2, and 3.
-In this case, the order is rotated, task 2, 3 and, 1, when the {\it rotateReadyQueue} is called.
+{\it rotateReadyQueue}は，2つ以上のタスクの場合にでも利用できる．
+例えば，３つのタスク，task 1, 2, 3が順に起動する場合，{\it rotateReadyQueue}が呼ばれると，task 2, 3, 1の順にタスクの起動は切り替わる．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
     \caption{The design of RiteVM sceduler}
@@
 
-\subsubsection{Component of RiteVM Scheduler} \mbox{}\\
+\subsubsection{Component of RiteVM Scheduler}
+図\ref{fig:cyclic_handler}にRiteVMスケジューラのコンポーネント図を示す．
+RiteVMスケジューラのコンポーネントは，CyclicHandlerとCyclicMainから構成される．
+CyclicHandlerセルは，μITRONの周期ハンドラの設定を行う．
+μITRONの周期ハンドラは，\cite{par:microITRON}に詳しく書かれている．
 
-Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
-The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
-CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
-Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
-The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
-CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
-CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
-{\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
-The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
-The attribute is used as an arguments of {\it rotateReadyQueue}.
+周期ハンドラは，5つの引数を持っている．(ID, attribute, cyclic time, cyclic phase, access pattern)
+CyclicHandlerセルは，3つの引数をセルの属性として持っている．
+CyclicMainセルは，周期ハンドラの処理を行うコンポーネントであり，{\it rotateReadyQueue}が実装されている．
+図\ref{celltype_cyclic_handler}に，セルタイプtCyclicMainのセルタイプ記述を示す．
+{\it call}ポートは，カーネルの機能を使用するためにカーネルセルの{\it entry}ポート({\it tkernel.eiKernel})に接続されている．
+属性は，{\it rotateReadyQueue}の引数として使われる．
 
-Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
-In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
-In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
-The cyclic handler is executed every one msec.
-In another part, the priority of CyclicMain {\it cell} is described.
-RITEVM\_PRIORITY defines the priority of mruby tasks.
-In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
+図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組み上げ記述を示す．
+
+CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
+attributeは{\it TA\_STA}であるので，OSが起動すると周期ハンドラが実行状態となる．
+周期時間は，1msecである．
+CyclicMainセル部分には，属性としてpriorityが記述されている．
+RITEVM\_PRIORITYはmrubyタスクの優先度として定義されている．
+この属性は，{\it rotateReadyQueue}の引数として与えられる．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/cyclic_handler.pdf}
     \caption{Component Diagram of Cyclic Handler}
@@
 
-\subsubsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
+\subsubsection{Synchronization of Multiple RiteVM Tasks}
+複数のmrubyアプリケーションの起動を同期させるために，提案フレームワークでは，同期処理の手法としてイベントフラグを適用した．
+タスクはそれぞれ0x01(01)，0x02(10)のパターンをセットし，待ちパターン0x3(11)でAND待ちする．
+この機構は，2つ以上のタスクの場合でも適用できる．
+例えば，タスクが4つの場合，タスクはそれぞれ，0x01(0001), 0x02(0010), 0x04 (0100), 0x08 (1000)のパターンをセットし，待ちパターン0x0f(1111) でAND待ちする．(図\ref{fig:Eventflag} (A))
 
-In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
-Eventflag, one of synchronous processing, is applied to synchronize the starting of multiple mruby applications.
-Each task sets the flag pattern such as 0x01 (01) and 0x02 (10), and then waits the flag pattern, 0x3 (11), with AND.
-This process can also apply to the case of the more tasks.
-For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND as shown in Figure \ref{fig:Eventflag} (A).
-
-In addtion, the end of mruby applications is synchronized to accept the continuous loading.
-The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
-All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.
+さらに，提案フレームワークでは，バイトコードの連続ローディングに対応するため，アプリケーションの終了も同期を行う．
+これによって，すぐに終了するようなアプリケーションのRiteVMが，次のロードの待機状態に入るのを防ぐことができる．
+すべてのアプリケーションは同時に終了し，すべてのRiteVMは同時に次のロードの待機状態へと入る．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
     \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
@@
 \subsection{Benefits of Component-Based Development}
-This section describes the design using the benefits of component-based development.
+この章では，コンポーネントベース開発の利点を使った設計について述べる．
 
-In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
-Therefore, developers can easily add or remove these components and also reuse them.
-For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
-This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
+提案フレームワークでは，RiteVMやRiteVMスケジューラ，イベントフラグはコンポーネントとして提供されているため，開発者はそれらのコンポーネントを容易に付け外し，再利用することができる．
+例えば，RiteVMスケジューラの機能を外したい場合，図\ref{celltype_cyclic_handler}，\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}のようにコメントアウトすることで容易に実現できる．
+開発者は，カーネルのコンフィグレーションファイルを修正する手間を省くことができる．
 
-In additon, the code size can desrease by developing with component-based. 
-In the proposed framework, the advantage is applied in the Eventflag component.
-The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
-Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
-In additon, the components of Eventflag are built with {\it [optional]} in TECS.
-{\it [optional]} means that the codes are run only when the call port is connected.
-The .c file does not be rewritten even if developers do not use Eventflag.
+それに加えて，コンポーネントベース開発ではコード量を減らすことができる．
+提案フレームワークでは，イベントフラグにこの利点は見られる．
+図\ref{fig:Eventflag}に示されるように，イベントフラグのセットパターンと待ちパターンを属性として定義する．
+{\it cEventflag\_set(ATTR\_setPattern)}に見られるこの設計によって，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じCファイルを使用できる．
+さらに，TECSのオプションである{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグの結合を切った場合にでも同じCファイルを利用することができる．
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_s_c_m.pdf}
     \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
+    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_msec.pdf}
     \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
@@
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtranBST2/IEEEtran}
-\bibliography{ref}
+\bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}
+\bibliography{../EMSOFT2016/ref}
+
+\begin{biography}
+\profile{m,E}{情報 太郎}{1970年生．1992年情報処理大学理学部情報科学科卒業．
+1994年同大学大学院修士課程修了．同年情報処理学会入社．オンライン出版の研究
+に従事．電子情報通信学会，IEEE，ACM 各会員．}
+%
+\profile{n}{処理 花子}{1960年生．1982年情報処理大学理学部情報科学科卒業．
+1984年同大学大学院修士課程修了．1987年同博士課程修了．理学博士．1987年情報処
+理大学助手．1992年架空大学助教授．1997年同大教授．オンライン出版の研究
+に従事．2010年情報処理記念賞受賞．電子情報通信学会，IEEE，IEEE-CS，ACM
+各会員．}
+%
+\profile{h,L}{学会 次郎}{1950年生．1974年架空大学大学院修士課程修了．
+1987年同博士課程修了．工学博士．1977年架空大学助手．1992年情報処理大学助
+教授．1987年同大教授．2000年から情報処理学会顧問．オンライン出版の研究
+に従事．2010年情報処理記念賞受賞．情報処理学会理事．電子情報通信学会，
+IEEE，IEEE-CS，ACM 各会員．}
+\end{biography}
 

### 2016-02-17 thesis/thesis.tex
add ETNET2016

@@
 \vspace{14mm}
-{\Large Division of Systems Science and Applied Informatics,\\Department of Systems Science,\\Schoolo of Engineering Science, Osaka University}\\
+{\Large Division of Systems Science and Applied Informatics,\\Department of Systems Science,\\School of Engineering Science, Osaka University}\\
 \end{center}

### 2016-02-17 ETNET2016/thesis.tex
ETNET2016 first

@@
 %
-\input{../dummy/dummy.tex}
+\input{../EMSOFT2016/dummy/dummy.tex}
 \documentclass[submit]{ipsj_v2/UTF8/ipsj}
@@
 
-\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+%\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
 
-\affiliate{IPSJ}{情報処理学会\\
-IPSJ, Chiyoda, Tokyo 101--0062, Japan}
+\affiliate{OU}{大阪大学基礎工学部\\
+School of Engineering Science, Osaka University}
 
-\paffiliate{JU}{情報処理大学\\
-Johoshori University}
+\affiliate{OKUMA}{オークマ株式会社\\
+OKUMA Corporation}
 
-\author{山本 拓朗}{Takuro Yamamoto}{IPSJ}[joho.taro@ipsj.or.jp]
-\author{大山 博司}{Hiroshi Oyama}{IPSJ}
-\author{安積 卓也}{Takuya Azumi}{IPSJ,JU}[gakkai.jiro@ipsj.or.jp]
+\affiliate{GOU}{大阪大学基礎工学研究科\\
+Graduate School of Engineering Science, Osaka University}
+
+\author{山本 拓朗}{Takuro Yamamoto}{OU}%[joho.taro@ipsj.or.jp]
+\author{大山 博司}{Hiroshi Oyama}{OKUMA}%
+\author{安積 卓也}{Takuya Azumi}{GOU}%[gakkai.jiro@ipsj.or.jp]
 
@@
 
-\begin{jkeyword}
-情報処理学会論文誌ジャーナル，\LaTeX，スタイルファイル，べからず集
-\end{jkeyword}
+% \begin{jkeyword}
+% 情報処理学会論文誌ジャーナル，\LaTeX，スタイルファイル，べからず集
+% \end{jkeyword}
 
-\begin{eabstract}
-This document is a guide to prepare a draft for submitting to IPSJ
-Journal, and the final camera-ready manuscript of a paper to appear in
-IPSJ Journal, using {\LaTeX} and special style files.  Since this
-document itself is produced with the style files, it will help you to
-refer its source file which is distributed with the style files.
-\end{eabstract}
-
-\begin{ekeyword}
-IPSJ Journal, \LaTeX, style files, ``Dos and Don'ts'' list
-\end{ekeyword}
+% \begin{eabstract}
+% This document is a guide to prepare a draft for submitting to IPSJ
+% Journal, and the final camera-ready manuscript of a paper to appear in
+% IPSJ Journal, using {\LaTeX} and special style files.  Since this
+% document itself is produced with the style files, it will help you to
+% refer its source file which is distributed with the style files.
+% \end{eabstract}
+%
+% \begin{ekeyword}
+% IPSJ Journal, \LaTeX, style files, ``Dos and Don'ts'' list
+% \end{ekeyword}
 
@@
 
+本論文における貢献は次のとおりである．
+\begin{itemize}
+        \item　mrubyバイトコードローダの実装により，mruby on TECSを使ったソフトウェア開発における作業効率を向上させる．
+        \item　RiteVMスケジューラの実装により，複数のmrubyプログラムを効率的に並行・並列動作させる．
+        \item　コンポーネントベース開発の利点を明らかにする．
+\end{itemize}
 % Contribution: The proposed framework gives the contribution in the following points.
@@
 
+本論文の構成を次に述べる．
+まず\ref{sec:Background}章で，提案フレームワークのベースであるmruby on TECSについて述べる．
+\ref{sec:Design and Implementation}章では，提案フレームワークの設計と実装について述べる．
+\ref{sec:Evaluation}章では，ローダを使用した場合の作業効率の比較，RiteVMを使用した場合の実行時間のオーバヘッドを評価する．
+\ref{sec:Related Work}章では，関連研究について述べる．
+最後に，\ref{sec:Conclusion}章で本論文をまとめる．
+
 % Organization: The paper is organized as follows. 
@@
 \section{既存フレームワーク}
-\label{fig:background}
+\label{sec:Background}
 図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
@@
 
-\subsubsection{Component Model}
+\subsubsection{コンポーネントモデル}
 図\ref{fig:component}にコンポーネント図の例を示す．
-{\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
+TECSでは，インスタンス化されたコンポーネントはセル({\it cell})と呼ばれ，受け口({\it entry})，呼び口({\it call})，属性，内部変数を持つ．
+受け口は自身の機能を提供するインタフェースで，呼び口は他のセルの機能を利用するためのインタフェースである．
+セルは複数の受け口や呼び口を持つことができる．
+セルの提供する関数は，C言語で実装される．
 
-A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
-Functions of a {\it cell} are implemented in the C language.
+受け口と呼び口の型は，セルの機能を使うためのインタフェースであるシグニチャによって定義される．
+セルの呼び口は，同じシグニチャを持つ他のセルの受け口と結合できる．
 
-A type of a {\it entry}/{\it call} port is defined by a {\it signature} which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it call} port of a {\it cell} can be connected to the {\it entry} port of another {\it cell} with the same {\it signature}.
-A {\it celltype} is the definition of a {\it cell}.
-{\it Celltype} defines one or more {\it call}/{\it entry} ports, attributes and internal variables.
+セルの型は，セルタイプと呼ばれ，受け口，呼び口，属性，内部変数の組を定義している．
 
@@
 
-\subsubsection{Component Description}
-The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
-TECS code is written in .cdl (component description language) file.
-The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.
+\subsubsection{コンポーネント記述}
+TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述の3つに分類され，.cdlファイルに記述する．
+図\ref{fig:component}に示されるコンポーネント記述について次に述べる．
+\begin{description}
+    \item[{\bf シグニチャ記述}]\mbox{}\\
+        シグニチャ記述は，セルのインタフェースを定義する．
+        {\it signature}キーワードに続けて，シグニチャ名(接頭辞``s")を記述する．
+        図\ref{signature}のようにシグニチャsMotorを定義することができる.
+        TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，[in]と[out]という指定子がつけられる．
 
-\begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
-        The {\it signature} description defines an interface of a {\it cell}.
-        A {\it signature} name is described following the keyword {\it signature}.
-        It also has the prefix ``s".
-        In this way, a {\it signature} is defined such as sMotor shown in Figure \ref{signature}.
-        To make the definition of an interface clear, specifiers such as in and out are used in TECS.
-        [in] and [out] represent input and output, respectively.\\
 \begin{figure}[t]
@@
 
-    \item[{\bf Celltype Description}]\mbox{}\\
-        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
-        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
-        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
-        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
-        In the same way, {\it call} ports can be declared.
-        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.\\
+    \item[{\bf セルタイプ記述}]\mbox{}\\
+        セルタイプ記述は，受け口，呼び口，属性，内部変数を用いてセルタイプを定義する．
+        {\it celltype}キーワードに続けて，セルタイプ名(接頭辞``t")を記述する．
+        図\ref{celltype}に示すように，受け口は，{\it entry}キーワードに続けて，シグニチャ名, 受け口名を記述する．
+        同様にして，呼び口も定義できる．
+        属性と変数は，それぞれ{\it attr}，{\it var}キーワードを用いて列挙する．
+
 \begin{figure}[t]
@@
 
-    \item[{\bf Build Description}]\mbox{}\\
-        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
-        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
+    \item[{\bf 組上げ記述}]\mbox{}\\
+        組上げ記述は，セルをインスタンス化し，セル同士を結合する．
+        {\it cell}キーワードに続けて，セルタイプ名，セル名を記述する．
+        呼び口名，``="，結合先の受け口名の順に記述し，セル同士を結合する．
+        図\ref{build}の例では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが接続されている．
+
 \begin{figure}[t]
@@
 \label{sec:mruby on TECS}
-mruby on TECS is a component-based framework for running script language.
-This framework uses two technologies, mruby and TECS.
+mruby on TECSは，mruby(軽量Ruby)を用いた組込みソフトウェアのコンポーネントベース開発が可能なフレームワークである．
 
-\subsubsection{System Model}\mbox{}\\
+\subsubsection{システムモデル}
+図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
+mrubyバイトコードはそれぞれ，コンポーネント化されたRTOSのタスクとして，RiteVM上で実行される．
+TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
 
-The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
-Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
-TECS components support various embedded drivers such as motor and sensor drivers.
+mruby-TECSブリッジによって，mrubyプログラムからC言語の関数を呼び出すことができる．
+mruby-TECSブリッジについては，以下で詳しく説明する．
 
-An mruby-TECS bridge plays a role to call a native program (e.g. C legacy code) from an mruby program.
-The mruby-TECS bridge provides native libraries for mruby.
-It also gives TECS components to receive the invocation from an mruby program.
-The mruby-TECS bridge is described in more detail bellow.
-
-As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
-TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.
+本研究では，RTOSとして，TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}を使用した．
+TOPPERS/HRP2は，μITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
+しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK \cite{par:OSEK}やTOPPERS/ASP \cite{url:ASP}といったRTOSにも対応しているので，mruby on TECSはRTOSに依存しない．
 
@@
 
-\subsubsection{mruby-TECS Bridge}\mbox{}\\
+\subsubsection{mruby-TECSブリッジ}
+mrubyとC言語には，実行時間に大きな差がある．
+\cite{par:mrubyonTECS}によると, mrubyプログラムは，C言語より実行時間が数百倍遅い．
+これによって，mrubyプログラムをすべてアプリケーションに使用することは難しい．
+mrubyを使用することにより，生産性やメンテナンス性を向上させることができる一方で，アクチュエータやセンサを制御するようなアプリケーションの重要な部分をC言語で実装することも必要である．
 
-There is a great difference between the execution time of mruby and C language.
-According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
-The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
-Thus it is difficult to use mruby for all of code.
-
-The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
-On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of code run quickly.
-
-Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
-The left side of BridgeMotor belongs to the mruby program.
-The right side of BridgeMotor belongs to TECS component.
+図\ref{fig:mruby_TECS_bridge}に，モータ制御に対するmruby-TECSブリッジの例を示す．
+BridgeMotorの左部分は，mrubyプログラムであり，右部分は，TECSのコンポーネントである．
 \begin{figure}[t]
@@
 
-The mruby-TECS bridge generates two things.
-One is a {\it celltype} to receive invocation from the mruby program.
-The other thing is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.
+mruby-TECSブリッジは，mrubyプログラムからの呼び出しを受け取るためのセルタイプと，C関数を呼び出すためのmrubyクラスを生成する．
+生成されたmruby-TECSブリッジのコードがmrubyのクラスとメソッドを登録する．
+これによって，mrubyプログラムからあるメソッドが呼ばれると，mruby-TECSブリッジがTECSコンポーネントで定義されたC関数を呼び出す．
 
-A code of an mruby-TECS bridge is generated.
-The generation code supports registration of classes and methods for mruby.
-The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
-
-\section{Design and Implementation}
+\section{設計と実装}
 \label{sec:Design and Implementation}
@@
 RiteVMスケジューラがタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作することができる．
-　
-Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
-Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
-The RiteVM reads the own bytecode and executes it.
-The mruby applications run at the same time because of synchronization processing.
-The RiteVM scheuler switches tasks as multiple tasks can run in concurrent.
 　
@@
 
-\subsection{mruby Bytecode Loader Using Bluetooth}
+\subsection{Bluetoothを用いたmrubyバイトコードローダ}
 \label{sec:mruby bytecode loader using Bluetooth}
@@
 
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
+\subsubsection{ローダを実装したRiteVMのコンポーネント}
 提案フレームワークでは，mrubyバイトコードローダはTECSのコンポーネントとして提供されている．
@@
 \end{figure}
-\subsection{Multitask}
+\subsection{マルチタスク処理}
 \label{sec:Multitask}
@@
 
-\subsubsection{RiteVM Scheduler}
+\subsubsection{RiteVMスケジューラ}
 RiteVMスケジューラは，周期ハンドラであり，μITRONのサービスコールである{\it rotateReadyQueue}を呼び出す．
@@
 
-\subsubsection{Component of RiteVM Scheduler}
+\subsubsection{RiteVMスケジューラのコンポーネント}
 図\ref{fig:cyclic_handler}にRiteVMスケジューラのコンポーネント図を示す．
@@
 
-図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組み上げ記述を示す．
+図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組上げ記述を示す．
 
@@
 
-\subsubsection{Synchronization of Multiple RiteVM Tasks}
+\subsubsection{mrubyアプリケーションの同期機構}
 複数のmrubyアプリケーションの起動を同期させるために，提案フレームワークでは，同期処理の手法としてイベントフラグを適用した．
@@
 
-\subsection{Benefits of Component-Based Development}
+\subsection{コンポーネントベース開発の利点}
 この章では，コンポーネントベース開発の利点を使った設計について述べる．
@@
 
-\section{Experimental Evaluation}
+\section{評価実験}
 \label{sec:Evaluation}
-This section mentions experimental results and their consideration.
-To analyze the advantages of the proposed framework, the evaluations are performed as follows.
+この章では，評価実験の結果と考察について述べる．
+提案フレームワークの利点を分析するため，以下の評価を行った．
 \begin{itemize}
-%    \item Execution time of the platform
-    \item Size and time for transferred mruby bytecodes
-    \item Execution time with singletasking, co-routine, and multitasking
-    \item Overhead for cyclic time
-%    \item Synchronization of mruby applications
-    \item Code size using the benefit of CBD 
+%    \item プラットフォームの起動時間
+    \item 転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間
+    \item シングルタスク，コルーチン，マルチタスクの実行時間
+    \item 周期時間によるオーバヘッド
+%   \item mrubyアプリケーションの同期
+    \item コンポーネントベース開発を利用したコードサイズ 
 \end{itemize}
 
-These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
-This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
+% These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
+本評価実験は，ターゲットデバイスとして，LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip)を使用し，コンパイラは，gcc 4.9.3 -O2 および mruby version 1.2.0である．
 
-The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
-Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
-The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
-The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
-%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
-%Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to connect a storage/ROM device to restart an OS.
-These advantages lead improvement of the software development efficiency.
+表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，mrubyライブラリとアプリケーションのバイトコードのサイズ，ロードにかかる処理時間，コンパイル時間の比較を示す．
+0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msecである．
+同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msecである．
+mrubyアプリケーションのみのバイトコードの方が，ライブラリを含めた場合よりも，すべての点で優れている．
+これは，RiteVMひとつの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
+さらに，この設計では，SDカードやROMを接続したり，OSを再起動する手間も省くことができる．
+以上より，提案フレームワークは，既存フレームワークより作業効率を向上させることができる．
+
+% The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
+% The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
+% Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
+% The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
+% The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
+% %In the proposed framework, developers send only mruby application and prepare mruby library in advance.
+% %Therefore, the design can send the bytecode faster.
+% In addition, the design can save the time to connect a storage/ROM device to restart an OS.
+% These advantages lead improvement of the software development efficiency.
 
@@
 
-The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-The 100,000 times loop program is used as mruby application for evaluation of execution time.
-In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
-In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
-This result shows the proposed design is superior to co-routine in terms of execution time.
-The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
-Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
-%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
-%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-The scheuler interrupts and switches tasks, which causes this overhead.
+次に，図\ref{fig:comparison_s_c_m}に，シングルタスク，コルーチン，マルチタスクの実行時間を示す．
+評価用のアプリケーションとして，100,000回ループするプログラムを適用した．
+マルチタスクおよびコルーチンは，2つのタスクでそれぞれ50,000回ループするプログラムを用いた．
+マルチタスクの実行時間は，シングルタスクよりも遅いが，コルーチンより速い．
+この結果から，提案フレームワークのマルチタスク処理は，コルーチンより有効である．
+RiteVMスケジューラのオーバヘッドは，約5\%である．
+タスクの切り替えそのものにかかる時間は，約3μsecである．
+RiteVMスケジューラは，周期的に割り込み，タスクの切り替えの処理を行うため，これがオーバヘッドとなっている．
+
+% The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+% The 100,000 times loop program is used as mruby application for evaluation of execution time.
+% In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
+% In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
+% While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
+% This result shows the proposed design is superior to co-routine in terms of execution time.
+% The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
+% Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
+% %The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
+% %Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
+% The scheuler interrupts and switches tasks, which causes this overhead.
 
@@
 
-Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
-A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
-More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
-Each execution time of cyclic period is the same as the others.
-That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
-This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
-The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
+図\ref{fig:comparison_msec}は，RiteVMスケジューラの周期時間ごとの実行時間を示している．
+この評価では，TOPPERS/HRP2の仕様により周期時間の下限を1msecとした．
+また，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を10msecとした．
+周期時間が大きいほど，タスクの切り替え回数は減少するため，実行時間は小さくなることが分かる．
+1msecと10msecでは，約3\%減少している．
+1msecと8msecでは，約1\%減少している．
+タスクを並行動作させるには，より小さい周期時間の方が好まれるが，オーバヘッドは大きくなる．
+しかし，周期時間によるオーバヘッドは，誤差に埋もれるほど小さい．
+
+% Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
+% A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
+% More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
+% Each execution time of cyclic period is the same as the others.
+% That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
+% This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
+% The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
 
@@
 
-To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
-(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
-(B) is not modified, and can be utilized regardless of the number of RiteVMs.
-Moreover, lines of two .cdl files are equal.
-The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
+表\ref{tab:codesize}に，2つの.cファイルと.cdlファイルのコード行数の比較を示す．
+(A)と(B)はそれぞれ，図\ref{fig:Eventflag}の上部と下部を指している．
+(A)の.cファイルは，RiteVMの数に比例して増えているのに対して，(B)の.cファイルは同じである．
+つまり，(B)はRiteVMの数にかかわらず，修正することなく同一のファイルを使用できる．
+さらに，.cdlファイルは両者違いはない．
+コンポーネントベース開発を上手く活用することで，コードの行数を減らすことができ，高い生産性やメンテナンス性につながる．
+その上，同じ.cファイルを利用できるため，開発者が違うファイルをリンクする手間を省くことも可能になる．
+
+% To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
+% (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
+% In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
+% (B) is not modified, and can be utilized regardless of the number of RiteVMs.
+% Moreover, lines of two .cdl files are equal.
+% The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
 
@@
 
-\section{Related Work}
-\label{sec:Related work}
+\section{関連研究}
+\label{sec:Related Work}
 
@@
 \end{table*}
-The open-source run-time systems for scripting languages have been proposed such as follow:
-python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+現在，オープンソースのスクリプト言語のランタイムシステムとして，次のものが開発されている.
+python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, mruby on TECS \cite{par:mrubyonTECS}.
 
-python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
-The VM runs a significant subset of Python language with few resources on a microcontroller.
-p14p can run multiple stackless green threads.
+python-on-a-chip(p14p)は，PyMyteと呼ばれるPythonVMを使用する，Pythonランタイムシステムである．
+PyMyteは，マイクロコントローラー上で低リソースでPythonプログラムを実行する．
+p14pは，スタックレスなグリーンスレッドを複数動作させることができる．
 
-The Owl system is an embedded Python run-time system.
-The Owl is a complete system for ARM Cortex-M3 microcontrollers.
-The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip.
+Owl systemは，組込みシステム向けのPythonランタイムシステムであり，ARM Cortex-M3 マイクロコントローラー上で動く．
+Owlツールチェーンは，Pythonコードから，マイコン上で直接起動するメモリイメージを生成する．
+Owl systemは，p14pのインタプリタを使用している．
 
-eLua offers the full implementation of Lua programming language to the embedded systems.
-Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
-Lua supports co-routine, referred to collaborative multitasking.
-A co-routine in Lua is used as an independently executed thread.
-A co-routine can just suspend and resume multiple routines.
-Thus, a Lua co-routine is not like multitasks in multitask systems.
+eLuaは，Luaを組込みシステム向けの完全な実装である．
+Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
+Luaは，協調的マルチタスク処理が可能なコルーチンをサポートしているが，コルーチンは，ノンプリエンプティブであるため，マルチタスク処理のようなプログラムを行うのは難しい．
 
-mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
-mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
-mruby has supported co-routine, but not supported multitasking for RTOSs.
+mruby(軽量Ruby)は，組込みシステムに適したスクリプト言語である．
+mrubyプログラムは，RiteVM上で実行される．
+mrubyは，コルーチンをサポートしているが，RTOSのマルチタスクには対応していない．
 
-mruby on TECS is a component-based framework for running mruby programs.
-The programs on mruby on TECS can execute about 100 times faster than the mruby programs.
-Software can be also developed with component base by mruby on TECS.
-Although multitasking has been supported in the current mruby on TECS, developers need to be familiar with functions of an RTOS to use multitasking.
-The co-routine is supported as same as mruby.
+mruby on TECSは，mrubyを使ったコンポーネントベース開発が可能なフレームワークである．
+mruby on TECSは，mrubyより実行速度が100倍速い．
+mruby on TECSは，マルチタスクをサポートしているが，マルチタスク処理を行うには，開発者がRTOSの機能を呼び出す必要がある．
 
-Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-The proposed framework supports the loader, the VM scheuler, and synchronization of application.
+表\ref{tab:comparison}に，提案フレームワークと既存研究の比較を示す．
+提案フレームワークでは，ローダに加えて，VMスケジューラとアプリケーションの同期機構を提供する．
 
@@
 \label{sec:Conclusion}
-This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
-The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
-The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
-%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
-The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
-In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
-The loader can improve the software development efficiency on mruby on TECS.
-The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
-%because of the low overhead.
+本研究では，mruby on TECSの拡張として，Bluetoothを用いたmrubyバイトコードローダとRiteVMスケジューラを提案した．
+mrubyバイトコードローダによって，開発者はSDカードやROMを再接続したり，OSを再起動する手間が省けるため，mruby on TECSでのソフトウェア開発の作業効率を向上させる．
+ローダは，Bluetoothだけでなく，有線のシリアル通信にも対応しているため，様々な組込みシステムに適用できる．
+RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行する.
+実験評価では，ローダによる作業効率の向上やオーバヘッドの少ないマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
 
-The proposed framework is developed in component-base by TECS.
-The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
-Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
-Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
-Component-based development can increase productivity and decrease complexity.
+さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる.
+RiteVMスケジューラも容易に付け外しできるため，開発者は，フェアスケジューリングか固定優先度スケジューリングかを選択することもできる．
+コンポーネントベース開発は，生産性を向上させ，システムの複雑さを減らすことができる．
 
-In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
-Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+ソフトウェア開発をさらに効率よく行うために，プラグインを使用したRiteVMやmruby-TECSブリッジの.cdlファイルの自動生成や，コマンドライン上でのバイトコードの転送などを提供することが，今後の課題である．
 

### 2016-02-18 ETNET2016/thesis.tex
update

@@
 \input{../EMSOFT2016/dummy/dummy.tex}
-\documentclass[submit]{ipsj_v2/UTF8/ipsj}
+%\documentclass[submit]{ipsj_v2/UTF8/ipsj}
 %\documentclass{ipsj}
+%\documentclass[submit,techrep]{ipsj_v2/UTF8/ipsj}
+\documentclass[submit,techrep]{ipsj}
 
@@
     identifierstyle={\small},%
-    commentstyle={\small\itshape},%
+    commentstyle={\scriptsize\itshape},%
     keywordstyle={\small},%\bfseries},%
@@
     numbersep=1zw,%
-    %lineskip=-0.5ex%
+    lineskip=-1.5ex%
 }
@@
 
-\setcounter{巻数}{57}
-\setcounter{号数}{1}
+\setcounter{巻数}{53}%vol53=2012
+\setcounter{号数}{10}
 \setcounter{page}{1}
-
-\受付{2015}{3}{4}
-%\再受付{2015}{7}{16}   %省略可能
-%\再再受付{2015}{7}{20} %省略可能
-\採録{2015}{8}{1}
 
@@
 
-%\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
 
@@
 近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．
-
 組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
-
 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
 さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
-
 本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
@@
 
-% \begin{eabstract}
-% This document is a guide to prepare a draft for submitting to IPSJ
-% Journal, and the final camera-ready manuscript of a paper to appear in
-% IPSJ Journal, using {\LaTeX} and special style files.  Since this
-% document itself is produced with the style files, it will help you to
-% refer its source file which is distributed with the style files.
-% \end{eabstract}
-%
+\begin{eabstract}
+In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
+For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
+In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
+Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of RTOSs to effectively execute multiple mruby programs in concurrent or/and parallel.
+To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
+In addition, multiple mruby programs cooperatively run in the proposed framework.
+A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+\end{eabstract}
+
 % \begin{ekeyword}
@@
 \section{はじめに}
-近年，組込みシステムは高品質・高性能化に伴い，複雑化・大規模化している．
-例えば，IoTアプリケーションがある．
-その上，製品の低コスト化や短期間での開発も要求されている．
+近年，組込みシステムは高品質・高性能化に伴い，複雑化・大規模化している上に，製品の低コスト化や短期間での開発も要求されている．
 
 ソフトウェアを効率的に開発するアプローチのひとつに，コンポーネントベース開発がある．
-コンポーネントベース開発は，再利用可能なコンポーネントを構成するための設計手法である\cite{par:Crnkovic}．
+%コンポーネントベース開発は，再利用可能なコンポーネントを構成するための設計手法である．
 コンポーネント化されたソフトウェアは，再利用性が高く，検証が容易になるため，コンポーネントベース開発を適用することで，複雑かつ大規模なソフトウェアを効率的に開発することができる．
 システムの拡張や仕様変更にも柔軟に対応できる．
-組込みシステムのコンポーネント技術として，TECS\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SAVEapproach}がある．
+組込みシステムのコンポーネント技術として，TECS\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}などがある．
 
@@
 スクリプト言語は，その使いやすさから高い生産性をもっているため，効率的かつ短期間での開発ができる．
-有名なスクリプト言語として，Java script，Perl，Python，Lua，Rubyなどがある．
+有名なスクリプト言語として，Ruby, Perl，Python，Luaなどがある．
 
@@
 %mruby on TECSは，スクリプト言語であるmruby使用したコンポーネントベース開発が可能なフレームワークである\cite{par:mrubyonTECS}．
-mruby on TECS は，mruby(軽量Ruby) と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである\cite{par:mrubyonTECS}.
+mruby on TECS は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである\cite{par:mrubyonTECS}.
 mruby on TECS では，mruby プログラムからC 言語の関数を呼ぶ機能を提供しており，mruby に比べて，アプリケーションを約100 倍速く実行できる.
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/proposed.pdf}
-    \caption{System Model}
+    \caption{システムモデル}
     \label{fig:proposed}
@@
 \subsection{mruby}
-mrubyは，ISO規格の一部に準拠したRubyの軽量実装である．
-Ruby\cite{url:Ruby}は，オブジェクト指向型のスクリプト言語である．
-特徴としてシンプルな文法なため読みやすくかつ使いやすい上に，C言語よりも少ないコード量で記述できる．
-他にも，クラスやメソッドといったオブジェクト指向関数，例外，ガベージコレクションなどの機能により，生産性を向上させることができる．
+% mrubyは，ISO規格の一部に準拠したRubyの軽量実装である．
+% Ruby\cite{url:Ruby}は，オブジェクト指向型のスクリプト言語である．
+% 特徴としてシンプルな文法なため読みやすくかつ使いやすい上に，C言語よりも少ないコード量で記述できる．
+% 他にも，クラスやメソッドといったオブジェクト指向関数，例外，ガベージコレクションなどの機能により，生産性を向上させることができる．
 
@@
 mrubyには，RiteVMと呼ばれるVMが実装されているため，どのOS上でもアプリケーションを起動させることができる．
-図\ref{fig:mruby}にRiteVMのメカニズムを示す．
+%図\ref{fig:mruby}にRiteVMのメカニズムを示す．
 mrubyコンパイラは，mrubyプログラム(.rb)を，中間言語であるバイトコード(.mrb)にコンパイルする．
-RiteVMが実装されいれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
+RiteVMが実装されていれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby.pdf}
-    \caption{Mechanism of mruby/RiteVM}
-    \label{fig:mruby}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby.pdf}
+%     \caption{Mechanism of mruby/RiteVM}
+%     \label{fig:mruby}
+% \end{figure}
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
-    \caption{Component Diagram}
+    \caption{TECSコンポーネント図の例}
     \label{fig:component}
@@
 図\ref{fig:component}に示されるコンポーネント記述について次に述べる．
-\begin{description}
-    \item[{\bf シグニチャ記述}]\mbox{}\\
+% \begin{description}
+%     \item[{\bf シグニチャ記述}]\mbox{}\\
         シグニチャ記述は，セルのインタフェースを定義する．
@@
 \end{lstlisting}
-\caption{Signature Description}
+\caption{シグニチャ記述}
 \label{signature}
@@
 
-    \item[{\bf セルタイプ記述}]\mbox{}\\
+    % \item[{\bf セルタイプ記述}]\mbox{}\\
         セルタイプ記述は，受け口，呼び口，属性，内部変数を用いてセルタイプを定義する．
@@
     entry sMotor eMotor;
-    attr{
-        int32_t attr = 100;
-    };
-    var{
-        int32_t var;
-    };
+    attr{ int32_t attr = 100; };
+    var{ int32_t var; };
 };
 \end{lstlisting}
-\caption{Celltype Description}
+\caption{セルタイプ記述}
 \label{celltype}
@@
 
-    \item[{\bf 組上げ記述}]\mbox{}\\
+    % \item[{\bf 組上げ記述}]\mbox{}\\
         組上げ記述は，セルをインスタンス化し，セル同士を結合する．
@@
 \end{lstlisting}
-\caption{Build Description}
+\caption{組上げ記述}
 \label{build}
@@
 
-\end{description}
+% \end{description}
 
@@
 \subsubsection{システムモデル}
-図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
+%図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
 mrubyバイトコードはそれぞれ，コンポーネント化されたRTOSのタスクとして，RiteVM上で実行される．
@@
 
-本研究では，RTOSとして，TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}を使用した．
+本研究では，RTOSとして，TOPPERS/HRP2\cite{par:hr-tecs}を使用した．
 TOPPERS/HRP2は，μITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
-しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK \cite{par:OSEK}やTOPPERS/ASP \cite{url:ASP}といったRTOSにも対応しているので，mruby on TECSはRTOSに依存しない．
+しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{url:ASP}といったRTOSにも対応しているので，mruby on TECSはRTOSに依存しない．
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mrubyontecs.pdf}
-    \caption{System Model of existing mruby on TECS}
-    \label{fig:mrubyontecs}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mrubyontecs.pdf}
+%     \caption{System Model of existing mruby on TECS}
+%     \label{fig:mrubyontecs}
+% \end{figure}
 
-\subsubsection{mruby-TECSブリッジ}
-mrubyとC言語には，実行時間に大きな差がある．
-\cite{par:mrubyonTECS}によると, mrubyプログラムは，C言語より実行時間が数百倍遅い．
-これによって，mrubyプログラムをすべてアプリケーションに使用することは難しい．
-mrubyを使用することにより，生産性やメンテナンス性を向上させることができる一方で，アクチュエータやセンサを制御するようなアプリケーションの重要な部分をC言語で実装することも必要である．
-
-図\ref{fig:mruby_TECS_bridge}に，モータ制御に対するmruby-TECSブリッジの例を示す．
-BridgeMotorの左部分は，mrubyプログラムであり，右部分は，TECSのコンポーネントである．
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby_TECS_bridge.pdf}
-    \caption{mruby-TECS Bridge}
-    \label{fig:mruby_TECS_bridge}
-\end{figure}
-
-mruby-TECSブリッジは，mrubyプログラムからの呼び出しを受け取るためのセルタイプと，C関数を呼び出すためのmrubyクラスを生成する．
-生成されたmruby-TECSブリッジのコードがmrubyのクラスとメソッドを登録する．
-これによって，mrubyプログラムからあるメソッドが呼ばれると，mruby-TECSブリッジがTECSコンポーネントで定義されたC関数を呼び出す．
-
+% \subsubsection{mruby-TECSブリッジ}
+% mrubyとC言語には，実行時間に大きな差がある．
+% \cite{par:mrubyonTECS}によると, mrubyプログラムは，C言語より実行時間が数百倍遅い．
+% これによって，mrubyプログラムをすべてアプリケーションに使用することは難しい．
+% mrubyを使用することにより，生産性やメンテナンス性を向上させることができる一方で，アクチュエータやセンサを制御するようなアプリケーションの重要な部分をC言語で実装することも必要である．
+%
+% 図\ref{fig:mruby_TECS_bridge}に，モータ制御に対するmruby-TECSブリッジの例を示す．
+% BridgeMotorの左部分は，mrubyプログラムであり，右部分は，TECSのコンポーネントである．
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby_TECS_bridge.pdf}
+%     \caption{mruby-TECS Bridge}
+%     \label{fig:mruby_TECS_bridge}
+% \end{figure}
+%
+% mruby-TECSブリッジは，mrubyプログラムからの呼び出しを受け取るためのセルタイプと，C関数を呼び出すためのmrubyクラスを生成する．
+% 生成されたmruby-TECSブリッジのコードがmrubyのクラスとメソッドを登録する．
+% これによって，mrubyプログラムからあるメソッドが呼ばれると，mruby-TECSブリッジがTECSコンポーネントで定義されたC関数を呼び出す．
+%
 \section{設計と実装}
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/system_model.pdf}
-    \caption{Detailed System Model of the proposed framework}
+    \caption{提案フレームワークの詳細なシステムモデル}
     \label{fig:system_model}
@@
 mrubyアプリケーションは，開発者が主にプログラムするメインのコードであり，mrubyライブラリには，motorクラスやsensorクラスといったRubyクラスのようにアプリケーションで利用される関数群が定義されている．
-アプリケーションとライブラリを含んだmrubyバイトコードを転送し，実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組込み，アプリケーション部分のみを転送する設計にした．
-このような設計にすることで，ライブラリは頻繁に変更されないため，毎回コンパイルする無駄を省くことができる．
+アプリケーションとライブラリを含んだmrubyバイトコードを転送し，実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組み込み，アプリケーション部分のみを転送する設計にした．
+この設計にすることで，転送するバイトコードのサイズや処理時間の無駄を省くことができる．
 さらに，各RiteVMでライブラリを共有することや，RiteVM固有のライブラリを持つことも可能になる．
@@
 図\ref{fig:component_bluetooth}に，MrubyTask1とMrubyBluetooth1のコンポーネントの例を示す．
-MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2 \ref{url:HRP2}\ref{par:HRP2})のタスクである．
+MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2\cite{par:HRP2})のタスクである．
 MrubyBluetooth1は，mrubyバイトコードを実装したRiteVMのコンポーネントであり，このコンポーネントのはじめで転送されてきたバイトコードを受信する．
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_bluetooth.pdf}
-    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
+    \caption{ローダを実装したRiteVMのコンポーネント図}
     \label{fig:component_bluetooth}
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/control_flow.pdf}
-    \caption{Control Flow of mruby bytecode loader using Bluetooth}
+    \caption{ローダの処理フローチャート}
     \label{fig:control_flow}
@@
   };
-    var{
-        [size_is(irepAppSize)] uint8_t *irepApp;
-    };
+  var{ [size_is(irepAppSize)] uint8_t *irepApp; };
 };
 \end{lstlisting}
-\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
+\caption{ローダを実装したRiteVMのセルタイプ記述}
 \label{celltype_mrubybluetooth}
@@
 \begin{lstlisting}
-void
-eMrubyBody_main( CELLIDX idx )
-{
-  /* Declaration variables */
-  mrb_state *mrb;
-  mrbc_context *c;
-  /* New interpreter instance */
-  mrb = mrb_open();
-  // Omit: error check for mrb_state
-  /* New mruby context */
-  c = mrbc_context_new( mrb );
-  // Omit: initialization of mruby-TECS bridge
-  /* Receive the bytecode via Bluetooth */
+void eMrubyBody_main( CELLIDX idx ){
+  /*Omit: Declaration variables*/
+  mrb=mrb_open(); /*New interpreter instance*/
+  /*Omit: error check for mrb_state*/
+  c=mrbc_context_new( mrb ); /*New mruby context*/
+  /*Omit: initialization of mruby-TECS bridge*/
+  /*Receive the bytecode via Bluetooth*/
   bluetooth_loader( VAR_irepApp );
-  /* Load mruby library bytecode and run */
+  /*Load mruby library bytecode and run*/
   mrb_load_irep_cxt( mrb, ATTR_irep, c );
-  /* Load mruby application bytecode and run */
+  /*Load mruby application bytecode and run*/
   mrb_load_irep_cxt( mrb, VAR_irepApp, c );
-  if ( mrb->exc ) {
-    /* Failure to execute */
-    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
-    exit( 0 );
-  }
-  /* Free mruby context */
-  mrbc_context_free( mrb, c );
-  /* Free interpreter instance */
-  mrb_close( mrb );
+  mrbc_context_free( mrb, c ); /*Free mruby context*/
+  mrb_close( mrb ); /*Free interpreter instance*/
 }
@@
 \end{lstlisting}
-\caption{Main code for RiteVM with mruby bytecode loader using Bluetooth}
+\caption{ローダを実装したRiteVMのメインコード}
 \label{maincode_mrubybluetooth}
@@
 \label{sec:Multitask}
-この章では，提案フレームワークでのマルチタスク処理の設計にちて述べる．
-mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの知識を熟知している必要がある．
+この章では，提案フレームワークでのマルチタスク処理の設計について述べる．
+%mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの知識を熟知している必要がある．
 
@@
 コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並列動作を行うことができる．
-(Rubyのコルーチンは，Fiberクラスに定義されている．\cite{url:co-routine})
+(Rubyのコルーチンは，Fiberクラス\cite{url:co-routine}に定義されている．)
 コルーチンは，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるので，OSのサポートやマルチコアの恩恵を受けることができない．
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
-    \caption{The design of RiteVM sceduler}
+    \caption{RiteVMスケジューラの設計}
     \label{fig:rotateReadyQueue}
@@
 \subsubsection{RiteVMスケジューラのコンポーネント}
-図\ref{fig:cyclic_handler}にRiteVMスケジューラのコンポーネント図を示す．
+%図\ref{fig:cyclic_handler}にRiteVMスケジューラのコンポーネント図を示す．
 RiteVMスケジューラのコンポーネントは，CyclicHandlerとCyclicMainから構成される．
@@
 CyclicMainセルは，周期ハンドラの処理を行うコンポーネントであり，{\it rotateReadyQueue}が実装されている．
-図\ref{celltype_cyclic_handler}に，セルタイプtCyclicMainのセルタイプ記述を示す．
-{\it call}ポートは，カーネルの機能を使用するためにカーネルセルの{\it entry}ポート({\it tkernel.eiKernel})に接続されている．
+%図\ref{celltype_cyclic_handler}に，セルタイプtCyclicMainのセルタイプ記述を示す．
+{\it call}ポートは，カーネルの機能である{\it rotateReadyQueue}を使用するためにカーネルセルの{\it entry}ポート({\it tkernel.eiKernel})に接続されている．
 属性は，{\it rotateReadyQueue}の引数として使われる．
 
-図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組上げ記述を示す．
+%図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組上げ記述を示す．
+図\ref{build_cyclic_handler}に，RiteVMスケジューラのコンポーネント組上げ記述を示す．
 
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/cyclic_handler.pdf}
-    \caption{Component Diagram of Cyclic Handler}
-    \label{fig:cyclic_handler}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \begin{lstlisting}
-celltype tCyclicHandler {
-    [inline] entry sCyclic eCyclic;
-    call  siHandlerBody  ciBody;
-    attr {
-    	[omit] ATR    attribute = C_EXP("TA_NULL");
-    	[omit] RELTIM cyclicTime;
-    	[omit] RELTIM cyclicPhase = 0;
-    };
-};
-celltype tCyclicMain{
-    require tKernel.eiKernel;
-    entry siHandlerBody eiBody;
-    attr {
-        PRI priority;
-    };
-};
-    \end{lstlisting}
-    \caption{Celltype Description of Cyclic Handler}
-    \label{celltype_cyclic_handler}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/cyclic_handler.pdf}
+%     \caption{Component Diagram of Cyclic Handler}
+%     \label{fig:cyclic_handler}
+% \end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \begin{lstlisting}
+% celltype tCyclicHandler {
+%     [inline] entry sCyclic eCyclic;
+%     call  siHandlerBody  ciBody;
+%     attr {
+%     	[omit] ATR    attribute = C_EXP("TA_NULL");
+%     	[omit] RELTIM cyclicTime;
+%     	[omit] RELTIM cyclicPhase = 0;
+%     };
+% };
+% celltype tCyclicMain{
+%     require tKernel.eiKernel;
+%     entry siHandlerBody eiBody;
+%     attr {
+%         PRI priority;
+%     };
+% };
+%     \end{lstlisting}
+%     \caption{Celltype Description of Cyclic Handler}
+%     \label{celltype_cyclic_handler}
+% \end{figure}
 \begin{figure}[t]
@@
 cell tCyclicMain CyclicMain{
-    priority =
-        C_EXP("RITEVM_PRIORITY");
+    priority = C_EXP("RITEVM_PRIORITY");
 };
    \end{lstlisting}
-    \caption{Build Description of Cyclic Handler}
+    \caption{RiteVMスケジューラの組上げ記述}
     \label{build_cyclic_handler}
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
-    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
+    \caption{TECSを用いたイベントフラグの設計 {\scriptsize *差分のみ示す}}
     \label{fig:Eventflag}
@@
 提案フレームワークでは，RiteVMやRiteVMスケジューラ，イベントフラグはコンポーネントとして提供されているため，開発者はそれらのコンポーネントを容易に付け外し，再利用することができる．
-例えば，RiteVMスケジューラの機能を外したい場合，図\ref{celltype_cyclic_handler}，\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}のようにコメントアウトすることで容易に実現できる．
+例えば，RiteVMスケジューラの機能を外したい場合，図\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}のようにコメントアウトすることで容易に実現できる．
 開発者は，カーネルのコンフィグレーションファイルを修正する手間を省くことができる．
@@
 %   \item mrubyアプリケーションの同期
-    \item コンポーネントベース開発を利用したコードサイズ 
+    \item コンポーネントベース開発を利用したコード行数
 \end{itemize}
@@
 % These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
-本評価実験は，ターゲットデバイスとして，LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip)を使用し，コンパイラは，gcc 4.9.3 -O2 および mruby version 1.2.0である．
+本評価実験は，ターゲットデバイスとして，LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip)を使用した．
+コンパイラは，gcc 4.9.3 -O2 および mrubyのバージョンは，1.2.0である．
 
@@
     \centering
-    \caption{Comparison of the size and load process time between an mruby application including mruby libraries and not}
+    \caption{転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間}
     \begin{tabular}{c||c|c|c}
@@
           Load Process Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
-          Compilation Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
+          Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
     \end{tabular}
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_s_c_m.pdf}
-    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
+    \caption{シングルタスク，コルーチン，マルチタスクの実行時間}
     \label{fig:comparison_s_c_m}
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_msec.pdf}
-    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
+    \caption{周期時間によるオーバヘッド}
     \label{fig:comparison_msec}
@@
 
-表\ref{tab:codesize}に，2つの.cファイルと.cdlファイルのコード行数の比較を示す．
+表\ref{tab:codesize}に，2つの.cファイルと.cdlファイルのコード行数と変更行数の比較を示す．
 (A)と(B)はそれぞれ，図\ref{fig:Eventflag}の上部と下部を指している．
-(A)の.cファイルは，RiteVMの数に比例して増えているのに対して，(B)の.cファイルは同じである．
-つまり，(B)はRiteVMの数にかかわらず，修正することなく同一のファイルを使用できる．
+(A)の.cファイルは，RiteVMの数に比例して増えているのに対して，(B)の.cファイルは同じである上に，RiteVMの数にかかわらず，修正することなく同一のファイルを使用できる．
 さらに，.cdlファイルは両者違いはない．
 コンポーネントベース開発を上手く活用することで，コードの行数を減らすことができ，高い生産性やメンテナンス性につながる．
-その上，同じ.cファイルを利用できるため，開発者が違うファイルをリンクする手間を省くことも可能になる．
+その上，同じ.cファイルを利用できるため，開発者がファイルを修正する手間を省くことも可能になる．
 
@@
     \centering
-    \caption{Lines of .c and .cdl file for the number of RiteVM}
+    \caption{コンポーネントベース開発を利用したコード行数} 
     \begin{tabular}{c||cc|c}
                 & (A)       & (B)     & Diff  \\ \hline
-        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
-        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
-        \multicolumn{3}{l}{  }\\
+        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
+        %\multicolumn{3}{l}{  }\\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
@@
     \centering
-    \caption{Comparion of the proposed and previous work}
+    \caption{関連研究}
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|ccccccc}
         & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
-        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
+        python-on-a-chip\cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
+        Owl system\cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        eLua\cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        mruby\cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
+        mruby on TECS\cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
     \end{tabular}
+}
     \label{tab:comparison}
@@
 現在，オープンソースのスクリプト言語のランタイムシステムとして，次のものが開発されている.
-python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, mruby on TECS \cite{par:mrubyonTECS}.
+python-on-a-chip\cite{url:python-on-a-chip}, the Owl system\cite{par:owl}, eLua\cite{url:eLua}, mruby\cite{par:mruby},\cite{url:mruby}, mruby on TECS\cite{par:mrubyonTECS}.
 
@@
 eLuaは，Luaを組込みシステム向けの完全な実装である．
-Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
+%Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
 Luaは，協調的マルチタスク処理が可能なコルーチンをサポートしているが，コルーチンは，ノンプリエンプティブであるため，マルチタスク処理のようなプログラムを行うのは難しい．
 
-mruby(軽量Ruby)は，組込みシステムに適したスクリプト言語である．
-mrubyプログラムは，RiteVM上で実行される．
+%mruby(軽量Ruby)は，組込みシステムに適したスクリプト言語である．
+%mrubyプログラムは，RiteVM上で実行される．
 mrubyは，コルーチンをサポートしているが，RTOSのマルチタスクには対応していない．
 
-mruby on TECSは，mrubyを使ったコンポーネントベース開発が可能なフレームワークである．
-mruby on TECSは，mrubyより実行速度が100倍速い．
+%mruby on TECSは，mrubyを使ったコンポーネントベース開発が可能なフレームワークである．
+%mruby on TECSは，mrubyより実行速度が100倍速い．
 mruby on TECSは，マルチタスクをサポートしているが，マルチタスク処理を行うには，開発者がRTOSの機能を呼び出す必要がある．
@@
 
-\section{Conclusion}
+\section{おわりに}
 \label{sec:Conclusion}
 本研究では，mruby on TECSの拡張として，Bluetoothを用いたmrubyバイトコードローダとRiteVMスケジューラを提案した．
-mrubyバイトコードローダによって，開発者はSDカードやROMを再接続したり，OSを再起動する手間が省けるため，mruby on TECSでのソフトウェア開発の作業効率を向上させる．
+mrubyバイトコードローダによって，開発者はSDカードやROMを上書きしたり，OSを再起動する手間が省けるため，mruby on TECSでのソフトウェア開発の作業効率を向上させる．
 ローダは，Bluetoothだけでなく，有線のシリアル通信にも対応しているため，様々な組込みシステムに適用できる．
@@
 \bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}
-\bibliography{../EMSOFT2016/ref}
+\bibliography{ETNET}
 
-\begin{biography}
-\profile{m,E}{情報 太郎}{1970年生．1992年情報処理大学理学部情報科学科卒業．
-1994年同大学大学院修士課程修了．同年情報処理学会入社．オンライン出版の研究
-に従事．電子情報通信学会，IEEE，ACM 各会員．}
-%
-\profile{n}{処理 花子}{1960年生．1982年情報処理大学理学部情報科学科卒業．
-1984年同大学大学院修士課程修了．1987年同博士課程修了．理学博士．1987年情報処
-理大学助手．1992年架空大学助教授．1997年同大教授．オンライン出版の研究
-に従事．2010年情報処理記念賞受賞．電子情報通信学会，IEEE，IEEE-CS，ACM
-各会員．}
-%
-\profile{h,L}{学会 次郎}{1950年生．1974年架空大学大学院修士課程修了．
-1987年同博士課程修了．工学博士．1977年架空大学助手．1992年情報処理大学助
-教授．1987年同大教授．2000年から情報処理学会顧問．オンライン出版の研究
-に従事．2010年情報処理記念賞受賞．情報処理学会理事．電子情報通信学会，
-IEEE，IEEE-CS，ACM 各会員．}
-\end{biography}
+% \begin{biography}
+% \profile{m,E}{情報 太郎}{1970年生．1992年情報処理大学理学部情報科学科卒業．
+% 1994年同大学大学院修士課程修了．同年情報処理学会入社．オンライン出版の研究
+% に従事．電子情報通信学会，IEEE，ACM 各会員．}
+% %
+% \profile{n}{処理 花子}{1960年生．1982年情報処理大学理学部情報科学科卒業．
+% 1984年同大学大学院修士課程修了．1987年同博士課程修了．理学博士．1987年情報処
+% 理大学助手．1992年架空大学助教授．1997年同大教授．オンライン出版の研究
+% に従事．2010年情報処理記念賞受賞．電子情報通信学会，IEEE，IEEE-CS，ACM
+% 各会員．}
+% %
+% \profile{h,L}{学会 次郎}{1950年生．1974年架空大学大学院修士課程修了．
+% 1987年同博士課程修了．工学博士．1977年架空大学助手．1992年情報処理大学助
+% 教授．1987年同大教授．2000年から情報処理学会顧問．オンライン出版の研究
+% に従事．2010年情報処理記念賞受賞．情報処理学会理事．電子情報通信学会，
+% IEEE，IEEE-CS，ACM 各会員．}
+% \end{biography}
 

### 2016-02-21 ETNET2016/thesis.tex
update

@@
 \begin{abstract}
-近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．
+近年，組込みシステムは複雑化・大規模化しているため，ソフトウェアの生産性が問題になっている．
 組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
@@
 さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する.
-
+\vspace{-5mm}
 \end{abstract}
@@
 A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+\vspace{-5mm}
 \end{eabstract}
@@
 \section{はじめに}
+\vspace{-2mm}
 近年，組込みシステムは高品質・高性能化に伴い，複雑化・大規模化している上に，製品の低コスト化や短期間での開発も要求されている．
 
-ソフトウェアを効率的に開発するアプローチのひとつに，コンポーネントベース開発がある．
+ソフトウェアを効率的に開発するアプローチに，コンポーネントベース開発がある．
 %コンポーネントベース開発は，再利用可能なコンポーネントを構成するための設計手法である．
-コンポーネント化されたソフトウェアは，再利用性が高く，検証が容易になるため，コンポーネントベース開発を適用することで，複雑かつ大規模なソフトウェアを効率的に開発することができる．
-システムの拡張や仕様変更にも柔軟に対応できる．
-組込みシステムのコンポーネント技術として，TECS\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}などがある．
+コンポーネント化されたソフトウェアは，再利用性が高く，検証が容易になるため，複雑・大規模なソフトウェアを効率的に開発できる．
+システムの拡張や仕様変更に柔軟に対応できる．
+組込みシステムのコンポーネント技術として，TECS (TOPPERS Embedded Component System)\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}がある．
 
 効率的なソフトウェア開発のもう一つのアプローチとして，スクリプト言語がある．
-現在のソフトウェアのほとんどはC言語で開発されているが，C言語による開発はコストが高く，開発期間も長くなる．
-スクリプト言語は，その使いやすさから高い生産性をもっているため，効率的かつ短期間での開発ができる．
+現在の組込みソフトウェアのほとんどはC言語で開発されているが，C言語による開発はコストが高く，開発期間も長くなる．
+スクリプト言語は，その使いやすさから高い生産性を持っているため，効率的かつ短期間での開発ができる．
 有名なスクリプト言語として，Ruby, Perl，Python，Luaなどがある．
 
-しかし，スクリプト言語は可読性や使いやすさが高い反面，C言語よりも実行時間が遅い．
-組込みシステムにとって，最悪実行時間や応答時間といったリアルタイム性は非常に重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
+しかし，スクリプト言語は生産性が高い反面，C言語よりも実行時間が遅い．
+組込みシステムにとって，デッドラインを守るといったリアルタイム性は重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
 
 %mruby on TECSは，スクリプト言語であるmruby使用したコンポーネントベース開発が可能なフレームワークである\cite{par:mrubyonTECS}．
-mruby on TECS は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである\cite{par:mrubyonTECS}.
-mruby on TECS では，mruby プログラムからC 言語の関数を呼ぶ機能を提供しており，mruby に比べて，アプリケーションを約100 倍速く実行できる.
+mruby on TECS \cite{par:mrubyonTECS}は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステム向けのコンポーネントシステムであるTECSを利用したフレームワークである.
+mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べてアプリケーションを約100倍速く実行できる.
 
 現状のmruby on TECSでは，いくつかの問題がある．
-mruby on TECS は，mrubyプログラムをロードするための方法として，記憶装置しか対応していないため，作業効率が悪い．
-(LEGO MINDSTORMS EV3 のプラットフォーム\cite{par:EV3})
-mrubyプログラムを修正する度に，SDカードの抜き差しやROMへの書き込みを行う必要がある．
+mruby on TECSは，mrubyプログラムをロードするための方法として，SDカードやROMへの書き込みにしか対応していないため，作業効率が悪い．
+例えば，LEGO MINDSTORMS EV3のプラットフォーム\cite{par:EV3}を利用した場合，mrubyプログラムを修正する度に，SDカードの抜き差しを行う必要がある．
 %mruby on TECS では，mruby プログラムを修正する度にターゲットデバイスでSD カードまたはROMに書き込みし，OS を再起動する必要がある.
-さらに，mruby on TECS はマルチVMに対応してるが，複数のmruby アプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOS の機能を呼び出さなければならない.
+さらに，mruby on TECSはマルチVMに対応してるが，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
 
@@
 % RiteVMスケジューラは複数のmrubyアプリケーションを
-提案フレームワークは，mruby on TECS を拡張して，Bluetooth を用いたmruby バイトコードローダと，実用的なマルチタスク処理の実装を行った.
-提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する.
-ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する. 
-ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する.
-これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
-さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる.
+本論文では，上記の問題を解決するため，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダおよびRiteVMスケジューラを提案する．
+% 提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する.
+% ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する. 
+% ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する.
+% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
+% RiteVMに実装されたローダが，ホストから転送されたバイトコードを受信し，アプリケーションを実行する．
+% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
+% さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる.
 
 本論文における貢献は次のとおりである．
-\begin{itemize}
-        \item　mrubyバイトコードローダの実装により，mruby on TECSを使ったソフトウェア開発における作業効率を向上させる．
-        \item　RiteVMスケジューラの実装により，複数のmrubyプログラムを効率的に並行・並列動作させる．
-        \item　コンポーネントベース開発の利点を明らかにする．
-\end{itemize}
+mrubyバイトコードローダにより，ソフトウェア開発における作業効率を向上させる．
+RiteVMスケジューラにより，複数のmrubyプログラムを効率的に並行・並列動作させる．
+コンポーネントベース開発の利点を明らかにする．
 % Contribution: The proposed framework gives the contribution in the following points.
@@
 \ref{sec:Design and Implementation}章では，提案フレームワークの設計と実装について述べる．
-\ref{sec:Evaluation}章では，ローダを使用した場合の作業効率の比較，RiteVMを使用した場合の実行時間のオーバヘッドを評価する．
+\ref{sec:Evaluation}章では，提案フレームワークの作業効率や実行時間のオーバヘッドを評価する．
 \ref{sec:Related Work}章では，関連研究について述べる．
@@
 % Section 4 evaluates the proposed framework, Section 5 discusses related work, and then Section 6 concludes this paper.
-
-\section{既存フレームワーク}
+\vspace{-2mm}
+\section{mruby on TECS (既存フレームワーク)}
+\vspace{-2mm}
 \label{sec:Background}
-図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
-RiteVMとmrubyライブラリを含むプラットフォーム部分は，はじめにターゲットデバイス上で起動されている．
-mrubyアプリケーションのバイトコードは，ホストからターゲットデバイスへと転送される．
-それぞれバイトコードは，RiteVMに割り当てられ，並行して起動される．
-
+% 図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
+% RiteVMとmrubyライブラリを含むプラットフォーム部分は，はじめにターゲットデバイス上で起動されている．
+% mrubyアプリケーションのバイトコードは，ホストからターゲットデバイスへと転送される．
+% それぞれバイトコードは，RiteVMに割り当てられ，並行して起動される．
+%
 この章では，提案フレームワークのベースになっているmruby on TECSについて述べる．
 mruby on TECSで利用されているmrubyとTECSについても述べる．
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/proposed.pdf}
-    \caption{システムモデル}
-    \label{fig:proposed}
-\end{figure}
-
-\subsection{mruby}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/proposed.pdf}
+%     \caption{システムモデル}
+%     \label{fig:proposed}
+% \end{figure}
+\vspace{-5mm}
+\subsection{mruby (軽量Ruby)}
 % mrubyは，ISO規格の一部に準拠したRubyの軽量実装である．
@@
 
-mrubyは，Rubyの可読性や使いやすさはそのままに，リソースが少なく起動が速いため，組込みシステムに適している．
-mrubyには，RiteVMと呼ばれるVMが実装されているため，どのOS上でもアプリケーションを起動させることができる．
+mrubyは，Rubyの高い生産性を持ち，少ないリソースで起動が速いため，組込みシステムに適している．
+mrubyには，RiteVMと呼ばれるVMが実装されており，どのOS上でも同じmrubyプログラムを起動できる．
 %図\ref{fig:mruby}にRiteVMのメカニズムを示す．
 mrubyコンパイラは，mrubyプログラム(.rb)を，中間言語であるバイトコード(.mrb)にコンパイルする．
-RiteVMが実装されていれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
+%RiteVMが実装されていれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
 
@@
 % \end{figure}
+\vspace{-5mm}
+\subsection{TECS\cite{par:TECS}}
+%TECSは，組込みシステム向けのコンポーネントシステムである．
+TECSによるコンポーネントベース開発は，ソフトウェアの再利用性を上げるため，生産性を向上できる．
+%システム全体の構造を可視化するため，システムの難しさを減らすことができる．
+%ソフトウェアの共通部分はコンポーネントとして扱われるため，開発の重複を減らし，生産性を向上させる．
 
-\subsection{TECS}
-TECS (TOPPERS Embedded Component System)は，組込みシステム向けのコンポーネントシステムである．
-TECSによるコンポーネントベース開発は，システム全体の構造を可視化するため，システムの複雑さや難しさを減らすことができる．
-さらに，ソフトウェアの共通部分はコンポーネントとして扱われるため，開発の重複を減らし，生産性を向上させる．
-
-TECSでのコンポーネントの生成と結合は静的に行われるため，最適化され，実行時間や消費メモリのオーバヘッドは少ない．
-他の特徴として，C言語での実装，ソースレベルでの移植性，コンポーネントの粒度が小さいことなどがある．
+% TECSでのコンポーネントの生成と結合は静的に行われるため，最適化され，実行時間や消費メモリのオーバヘッドは少ない．
+% 他の特徴として，C言語での実装，ソースレベルでの移植性，コンポーネントの粒度が小さいことなどがある．
 
@@
 図\ref{fig:component}にコンポーネント図の例を示す．
-TECSでは，インスタンス化されたコンポーネントはセル({\it cell})と呼ばれ，受け口({\it entry})，呼び口({\it call})，属性，内部変数を持つ．
+TECSでは，インスタンス化されたコンポーネントはセル({\it cell})と呼ばれ，受け口({\it entry})，呼び口({\it call})，属性，変数を持つ．
 受け口は自身の機能を提供するインタフェースで，呼び口は他のセルの機能を利用するためのインタフェースである．
@@
 セルの呼び口は，同じシグニチャを持つ他のセルの受け口と結合できる．
-
-セルの型は，セルタイプと呼ばれ，受け口，呼び口，属性，内部変数の組を定義している．
+セルの型は，セルタイプと呼ばれ，受け口，呼び口，属性，変数の組を定義している．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
+    \vspace{-4mm}
     \caption{TECSコンポーネント図の例}
+    \vspace{-5mm}
     \label{fig:component}
@@
 \subsubsection{コンポーネント記述}
-TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述の3つに分類され，.cdlファイルに記述する．
-図\ref{fig:component}に示されるコンポーネント記述について次に述べる．
+TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述に分類され，.cdlファイルに記述する．
+図\ref{fig:component}のコンポーネント記述について次に述べる．
+
 % \begin{description}
@@
         シグニチャ記述は，セルのインタフェースを定義する．
-        {\it signature}キーワードに続けて，シグニチャ名(接頭辞``s")を記述する．
-        図\ref{signature}のようにシグニチャsMotorを定義することができる.
+        図\ref{signature}に示す通り，{\it signature}キーワードに続けて，シグニチャ名(sMotor)を記述する．
+        %図\ref{signature}のようにシグニチャsMotorを定義できる.
         TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，[in]と[out]という指定子がつけられる．
@@
 \end{lstlisting}
+    \vspace{-2mm}
 \caption{シグニチャ記述}
+\vspace{-5mm}
 \label{signature}
@@
     % \item[{\bf セルタイプ記述}]\mbox{}\\
-        セルタイプ記述は，受け口，呼び口，属性，内部変数を用いてセルタイプを定義する．
-        {\it celltype}キーワードに続けて，セルタイプ名(接頭辞``t")を記述する．
-        図\ref{celltype}に示すように，受け口は，{\it entry}キーワードに続けて，シグニチャ名, 受け口名を記述する．
+        セルタイプ記述は，受け口，呼び口，属性，変数を用いてセルタイプを定義する．
+        {\it celltype}キーワードに続けて，セルタイプ名(tCaller)を記述する．
+        図\ref{celltype}に示す通り，受け口は，{\it entry}キーワードに続けて，シグニチャ名, 受け口名を記述する．
         同様にして，呼び口も定義できる．
@@
 \end{lstlisting}
+    \vspace{-2mm}
 \caption{セルタイプ記述}  
+\vspace{-4mm}
 \label{celltype}
@@
     % \item[{\bf 組上げ記述}]\mbox{}\\
-        組上げ記述は，セルをインスタンス化し，セル同士を結合する．
+        組上げ記述は，セルをインスタンス化し，セルを結合する．
         {\it cell}キーワードに続けて，セルタイプ名，セル名を記述する．
-        呼び口名，``="，結合先の受け口名の順に記述し，セル同士を結合する．
-        図\ref{build}の例では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが接続されている．
+        呼び口名，``="，結合先の受け口名の順に記述し，セルを結合する．
+        図\ref{build}では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが接続されている．
 
@@
 \end{lstlisting}
+    \vspace{-2mm}
 \caption{組上げ記述}
+\vspace{-4mm}
 \label{build}
@@
 % \end{description}
-
+\vspace{-5mm} 
 \subsection{mruby on TECS}
 \label{sec:mruby on TECS}
-mruby on TECSは，mruby(軽量Ruby)を用いた組込みソフトウェアのコンポーネントベース開発が可能なフレームワークである．
-
-\subsubsection{システムモデル}
+mruby on TECSは，mrubyを用いた組込みソフトウェアのコンポーネントベース開発が可能なフレームワークである．
+%\subsubsection{システムモデル}
 %図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
 mrubyバイトコードはそれぞれ，コンポーネント化されたRTOSのタスクとして，RiteVM上で実行される．
-TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
+%TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
 
 mruby-TECSブリッジによって，mrubyプログラムからC言語の関数を呼び出すことができる．
-mruby-TECSブリッジについては，以下で詳しく説明する．
+%mruby-TECSブリッジについては，以下で詳しく説明する．
 
 本研究では，RTOSとして，TOPPERS/HRP2\cite{par:hr-tecs}を使用した．
-TOPPERS/HRP2は，μITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
-しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{url:ASP}といったRTOSにも対応しているので，mruby on TECSはRTOSに依存しない．
+TOPPERS/HRP2は，$\mu$ITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
+しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{url:ASP}といったRTOSにも対応しているため，mruby on TECSはRTOSに依存しない．
 
@@
 %
+\vspace{-2mm}
 \section{設計と実装}
+\vspace{-2mm}
 \label{sec:Design and Implementation}
-図\ref{fig:system_model}に提案フレームワークの詳細なシステムモデルを示す．
-ホストから転送されたmrubyアプリケーションのバイトコードは，それぞれのRiteVMに実装されたローダで受信され，同期処理により同時に実行される．
-RiteVMスケジューラがタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作することができる．
-　
+図\ref{fig:system_model}に提案フレームワークのシステムモデルを示す．
+ホストから転送されたmrubyアプリケーションのバイトコードは，それぞれのRiteVMに実装されたローダで受信され，同期処理され実行される．
+RiteVMスケジューラはタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作できる．
+また，mrubyアプリケーションの起動は同期機構により同期される．　
 \begin{figure}[t]
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/system_model.pdf}
-    \caption{提案フレームワークの詳細なシステムモデル}
+    \vspace{-2mm}
+    \caption{提案フレームワークのシステムモデル}
+\vspace{-3mm}
     \label{fig:system_model}
 \end{figure}
-
+\vspace{-3mm}
 \subsection{Bluetoothを用いたmrubyバイトコードローダ}
@@
 この章では，Bluetoothを用いたmrubyバイトコードローダについて述べる．
-現状のmruby on TECSでは，mrubyバイトコードをプラットフォームに組み込んでいるため，mrubyプログラムを修正する度にプラットフォーム部分をもう一度コンパイル・リンクし，SDカードやROMといったデバイスに再度書き込み，OSを再起動する必要がある．
-このような作業を繰り返すことで，作業効率は悪くなる．
-提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし記憶デバイスに書き込むのは，はじめの一度だけで良いため，作業効率を向上させることができる．
+既存フレームワークでは，mrubyバイトコードをプラットフォームに組み込んでいるため，mrubyプログラムを修正する度にプラットフォーム部分をもう一度コンパイル・リンクし，SDカードやROMに再度書き込み，OSを再起動する必要がある．
+%このような作業を繰り返すことで，作業効率は悪くなる．
+提案フレームワークでは，一度だけSDカードやROMに書き込むため，作業効率を向上できる．
 
 mrubyプログラムは，アプリケーション部分とライブラリ部分に分けられる．
-mrubyアプリケーションは，開発者が主にプログラムするメインのコードであり，mrubyライブラリには，motorクラスやsensorクラスといったRubyクラスのようにアプリケーションで利用される関数群が定義されている．
-アプリケーションとライブラリを含んだmrubyバイトコードを転送し，実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組み込み，アプリケーション部分のみを転送する設計にした．
-この設計にすることで，転送するバイトコードのサイズや処理時間の無駄を省くことができる．
-さらに，各RiteVMでライブラリを共有することや，RiteVM固有のライブラリを持つことも可能になる．
+%mrubyアプリケーションは，開発者が主にプログラムするメインのコードであり，mrubyライブラリには，motorクラスやsensorクラスといったRubyクラスのようにアプリケーションで利用される関数群が定義されている．
+アプリケーションとライブラリをまとめたバイトコードを転送・実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組み込み，アプリケーション部分のみを転送する．
+この設計により，転送するバイトコードのサイズや処理時間の無駄を省ける．
+さらに，各RiteVMでライブラリを共有することや，固有のライブラリを持つことも可能になる．
 
-提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している．
+%提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している.
 
 \subsubsection{ローダを実装したRiteVMのコンポーネント}
-提案フレームワークでは，mrubyバイトコードローダはTECSのコンポーネントとして提供されている．
-このコンポーネントは，RiteVMのコンポーネントの拡張として実装されている．(詳細については\cite{par:mrubyonTECS}を参照)
+%ローダを実装したRiteVMはTECSのコンポーネントとして提供されている．
+ローダは，mruby on TECSで提供されているRiteVMコンポーネント\cite{par:mrubyonTECS}を拡張して実装した．
+
 このコンポーネントでは，転送されたバイトコードの受信に加え，RiteVMのコンフィグレーションが行われる．
@@
 図\ref{fig:component_bluetooth}に，MrubyTask1とMrubyBluetooth1のコンポーネントの例を示す．
-MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2\cite{par:HRP2})のタスクである．
-MrubyBluetooth1は，mrubyバイトコードを実装したRiteVMのコンポーネントであり，このコンポーネントのはじめで転送されてきたバイトコードを受信する．
-提案フレームワークでは，バイナリ転送プロトコルとして，ZMODEを適用した．
+MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2)のタスクである．
+MrubyBluetooth1は，ローダを実装したRiteVMのコンポーネントであり，転送されるバイトコードを受信する．
+バイナリ転送プロトコルは，ZMODEMを適用した．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_bluetooth.pdf}
+    \vspace{-2mm}
     \caption{ローダを実装したRiteVMのコンポーネント図}
+\vspace{-5mm}
     \label{fig:component_bluetooth}
@@
 
-図\ref{fig:control_flow}に，ローダを実装したRiteVMがmrubyプログラムを実行するまでの制御フロー，図\ref{maincode_mrubybluetooth}には，RiteVMコンポーネントのソースコードを示す．
+図\ref{fig:control_flow}に，ローダを実装したRiteVMがmrubyプログラムを実行するまでのフローチャートを示す．
 
-はじめに，{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する．
-{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
+はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する．
+%{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
 
 次に，mrubyライブラリのバイトコードを読み込む．
-図\ref{celltype_mrubybluetooth}に示すように，tMrubyBluetoothのセルは属性を持っている．
-{\it mrubyFile}はmrubyライブラリのファイルを示しており，{\it [omit]}はTECSジェネレータによってのみ使えわれるため，この属性はメモリを消費することない．
+図\ref{celltype_mrubybluetooth}に示す通り，tMrubyBluetoothのセルは属性を持っている．
+{\it mrubyFile}はmrubyライブラリのファイルを示しており，{\it [omit]}はTECSジェネレータによってのみ使われるため，この属性はメモリを消費しない．
 {\it irep}は，mrubyライブラリのバイトコードが格納されている配列へのポインタである．
-つまり，mrubyライブラリは始めのコンパイル時にコンポーネントの属性として，配列に保存されている．
+つまり，mrubyライブラリは始めのコンパイル時にコンポーネントの属性として，配列に保存される．
 
 次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む．
-mrubyアプリケーションのバイトコードは，図\ref{celltype_mrubybluetooth}に示す，内部変数uint8\_t型の配列{\it irepApp}に格納されている．
+mrubyアプリケーションのバイトコードは，変数uint8\_t型の配列{\it irepApp}に格納される．
 ２つのバイトコードは，それぞれ別の配列に保存されており，別々に読み込まれる．
@@
 mrubyアプリケーションのプログラムが修正された場合は，そのバイトコードのみを再転送する．
+以上の処理のソースコードを図\ref{maincode_mrubybluetooth}に示す．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/control_flow.pdf}
+    \vspace{-2mm}
     \caption{ローダの処理フローチャート}
+\vspace{-5mm}
     \label{fig:control_flow}
@@
 \end{lstlisting}
+    \vspace{-2mm}
 \caption{ローダを実装したRiteVMのセルタイプ記述}
+\vspace{-4mm}
 \label{celltype_mrubybluetooth}
@@
 \end{lstlisting}
+    \vspace{-2mm}
 \caption{ローダを実装したRiteVMのメインコード}
+\vspace{-3mm}
 \label{maincode_mrubybluetooth}
 \end{figure} 
+\vspace{-5mm}
 \subsection{マルチタスク処理}
@@
 マルチタスク処理のアプローチのひとつにコルーチンがある．
-コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並列動作を行うことができる．
-(Rubyのコルーチンは，Fiberクラス\cite{url:co-routine}に定義されている．)
-コルーチンは，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるので，OSのサポートやマルチコアの恩恵を受けることができない．
+コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並列動作できるが，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるので，OSのサポートやマルチコアの恩恵を受けることができない．
+Rubyのコルーチンは，Fiberクラス\cite{url:co-routine}に定義されている．
 
-その他のアプローチとして，μITRONのサービスコールである{\it delay()}使った手法がある．
+その他にも，$\mu$ITRONのサービスコールである{\it delay()}を使った手法がある．
 このサービスコールは，引数として与えられた時間だけ，そのタスクの起動を遅らせる．
@@
 
-提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを実装し，複数のタスクを平等に並行動作させる．
+提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを提供し，複数のタスクを平等に並行動作させる．
 このスケジューラはアプリケーションタスクが同じ優先度を持つ場合に利用でき，開発者がOSの関数を呼び出すことなく，マルチタスク処理が可能になる．
-その上，既存のアプリケーションプログラムの構造を変えること使うことができる．
+その上，既存のアプリケーションプログラムの構造を変えることなく使うことができる．
 
 \subsubsection{RiteVMスケジューラ}
-RiteVMスケジューラは，周期ハンドラであり，μITRONのサービスコールである{\it rotateReadyQueue}を呼び出す．
-{\it rotateReadyQueue}は，同優先度のタスクの実行を切り替える関数である．
+RiteVMスケジューラは，周期ハンドラであり，同優先度のタスクの実行を切り替える$\mu$ITRONのサービスコールである{\it rotateReadyQueue}を周期的に呼び出す．
+%{\it rotateReadyQueue}は，同優先度のタスクの実行を切り替える関数である．
 RiteVMスケジューラの設計を図\ref{fig:rotateReadyQueue}に示す．
 
-無限ループを持った同優先度の2つのタスクの場合を考える．
-現状のシステムでは，始めにタスクが起動すると，そのタスクが無限ループに入るため，もう片方のタスクが起動することができない．
+% 無限ループを持った同優先度の2つのタスクの場合を考える．
+% 現状のシステムでは，始めにタスクが起動すると，そのタスクが無限ループに入るため，もう片方のタスクが起動することができない．
 
@@
 {\it rotateReadyQueue}は，2つ以上のタスクの場合にでも利用できる．
-例えば，３つのタスク，task 1, 2, 3が順に起動する場合，{\it rotateReadyQueue}が呼ばれると，task 2, 3, 1の順にタスクの起動は切り替わる．
+例えば，３つのタスクA, B, Cが順に起動する場合，{\it rotateReadyQueue}が呼ばれると，B, C, Aの順にタスクの起動は切り替わる．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
+    \vspace{-2mm}
     \caption{RiteVMスケジューラの設計}
+\vspace{-5mm}
     \label{fig:rotateReadyQueue}
@@
 RiteVMスケジューラのコンポーネントは，CyclicHandlerとCyclicMainから構成される．
-CyclicHandlerセルは，μITRONの周期ハンドラの設定を行う．
-μITRONの周期ハンドラは，\cite{par:microITRON}に詳しく書かれている．
-
-周期ハンドラは，5つの引数を持っている．(ID, attribute, cyclic time, cyclic phase, access pattern)
-CyclicHandlerセルは，3つの引数をセルの属性として持っている．
+CyclicHandlerセルは，3つの属性(attribute, cyclicTime, cyclicPhase)を持っており，$\mu$ITRONの周期ハンドラ\cite{par:microITRON}の設定を行う．
+%$\mu$ITRONの周期ハンドラは，\cite{par:microITRON}に詳しく書かれている．
+%周期ハンドラは，5つの引数(ID, attribute, cyclic time, cyclic phase, access pattern)を持っている．
+%CyclicHandlerセルは，3つの属性(attribute, cyclicTime, cyclicPhase)を持っている．
 CyclicMainセルは，周期ハンドラの処理を行うコンポーネントであり，{\it rotateReadyQueue}が実装されている．
 %図\ref{celltype_cyclic_handler}に，セルタイプtCyclicMainのセルタイプ記述を示す．
-{\it call}ポートは，カーネルの機能である{\it rotateReadyQueue}を使用するためにカーネルセルの{\it entry}ポート({\it tkernel.eiKernel})に接続されている．
+呼び口は，カーネルの機能である{\it rotateReadyQueue}を使用するためにカーネルセルの受け口({\it tkernel.eiKernel})に接続されている．
 属性は，{\it rotateReadyQueue}の引数として使われる．
@@
 %図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組上げ記述を示す．
-図\ref{build_cyclic_handler}に，RiteVMスケジューラのコンポーネント組上げ記述を示す．
-
-CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
-attributeは{\it TA\_STA}であるので，OSが起動すると周期ハンドラが実行状態となる．
-周期時間は，1msecである．
-CyclicMainセル部分には，属性としてpriorityが記述されている．
-RITEVM\_PRIORITYはmrubyタスクの優先度として定義されている．
-この属性は，{\it rotateReadyQueue}の引数として与えられる．
+図\ref{build_cyclic_handler}に，RiteVMスケジューラの組上げ記述を示す．
+%CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
+attributeには，OSが起動すると実行状態になる{\it TA\_STA}，周期時間には，1msecが与えられる．
+CyclicMainセル部分は，属性priorityを持っており，mrubyタスクの優先度であるRITEVM\_PRIORITYが与えられる．
 
@@
    \end{lstlisting}
+    \vspace{-2mm}
     \caption{RiteVMスケジューラの組上げ記述}
+\vspace{-3mm}
     \label{build_cyclic_handler}
@@
 \subsubsection{mrubyアプリケーションの同期機構}
-複数のmrubyアプリケーションの起動を同期させるために，提案フレームワークでは，同期処理の手法としてイベントフラグを適用した．
-タスクはそれぞれ0x01(01)，0x02(10)のパターンをセットし，待ちパターン0x3(11)でAND待ちする．
-この機構は，2つ以上のタスクの場合でも適用できる．
-例えば，タスクが4つの場合，タスクはそれぞれ，0x01(0001), 0x02(0010), 0x04 (0100), 0x08 (1000)のパターンをセットし，待ちパターン0x0f(1111) でAND待ちする．(図\ref{fig:Eventflag} (A))
+複数のmrubyアプリケーションの起動を同期させるために，イベントフラグを適用した．
+%タスクはそれぞれ0x01(01)，0x02(10)のパターンをセットし，待ちパターン0x3(11)でAND待ちする．
+%この機構は，2つ以上のタスクの場合でも適用できる．
+タスクが4つの場合，タスクはそれぞれ，0x01(0001), 0x02(0010), 0x04(0100), 0x08(1000)のパターンをセットし，待ちパターン0x0f(1111) でAND待ちする．(図\ref{fig:Eventflag} (A))
 
-さらに，提案フレームワークでは，バイトコードの連続ローディングに対応するため，アプリケーションの終了も同期を行う．
-これによって，すぐに終了するようなアプリケーションのRiteVMが，次のロードの待機状態に入るのを防ぐことができる．
-すべてのアプリケーションは同時に終了し，すべてのRiteVMは同時に次のロードの待機状態へと入る．
+さらに，バイトコードの連続ローディングに対応するため，アプリケーションの終了も同期する．
+これにより，すぐに終了するアプリケーションのRiteVMが次のロード待機状態に入るのを防げ，すべてのRiteVMは同時に次のロード待機状態になる．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
+    \vspace{-2mm}
     \caption{TECSを用いたイベントフラグの設計 {\scriptsize *差分のみ示す}}
+\vspace{-3mm}
     \label{fig:Eventflag}
 \end{figure}
-
+\vspace{-5mm}
 \subsection{コンポーネントベース開発の利点}
 この章では，コンポーネントベース開発の利点を使った設計について述べる．
-
-提案フレームワークでは，RiteVMやRiteVMスケジューラ，イベントフラグはコンポーネントとして提供されているため，開発者はそれらのコンポーネントを容易に付け外し，再利用することができる．
-例えば，RiteVMスケジューラの機能を外したい場合，図\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}のようにコメントアウトすることで容易に実現できる．
-開発者は，カーネルのコンフィグレーションファイルを修正する手間を省くことができる．
+提案フレームワークは，RiteVMやRiteVMスケジューラ，イベントフラグをコンポーネントとして提供しているため，開発者はそれらのコンポーネントを容易に付け外したり，再利用できる．
+例えば，RiteVMスケジューラの機能を外したい場合，図\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}とコメントアウトするだけで良いため，開発者はカーネルの設定ファイルを修正する手間を省くことができる．
 
 それに加えて，コンポーネントベース開発ではコード量を減らすことができる．
-提案フレームワークでは，イベントフラグにこの利点は見られる．
-図\ref{fig:Eventflag}に示されるように，イベントフラグのセットパターンと待ちパターンを属性として定義する．
-{\it cEventflag\_set(ATTR\_setPattern)}に見られるこの設計によって，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じCファイルを使用できる．
-さらに，TECSのオプションである{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグの結合を切った場合にでも同じCファイルを利用することができる．
+図\ref{fig:Eventflag} (B)に示す通り，イベントフラグのセットパターンと待ちパターンを属性として定義する．
+{\it cEventflag\_set(ATTR\_setPattern)}のように，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じCファイルを使用できる．
+さらに，TECSのオプション{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグの結合を切った場合にでも同じCファイルを利用できる．
 
+\vspace{-2mm}
 \section{評価実験}
+\vspace{-2mm}
 \label{sec:Evaluation}
 この章では，評価実験の結果と考察について述べる．
-提案フレームワークの利点を分析するため，以下の評価を行った．
-\begin{itemize}
-%    \item プラットフォームの起動時間
-    \item 転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間
-    \item シングルタスク，コルーチン，マルチタスクの実行時間
-    \item 周期時間によるオーバヘッド
-%   \item mrubyアプリケーションの同期
-    \item コンポーネントベース開発を利用したコード行数
-\end{itemize}
+提案フレームワークの利点を分析するため，
+%プラットフォームの起動時間
+転送するバイトコードのサイズと処理時間およびコンパイル時間, 
+シングルタスク，コルーチン，マルチタスクの実行時間, 
+周期時間によるオーバヘッド,
+%mrubyアプリケーションの同期
+コンポーネントベース開発を利用したコード行数
+の評価を行った．
+% \begin{itemize}
+% %    \item プラットフォームの起動時間
+%     \item 転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間
+%     \item シングルタスク，コルーチン，マルチタスクの実行時間
+%     \item 周期時間によるオーバヘッド
+% %   \item mrubyアプリケーションの同期
+%     \item コンポーネントベース開発を利用したコード行数
+% \end{itemize}
 
@@
 
-表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，mrubyライブラリとアプリケーションのバイトコードのサイズ，ロードにかかる処理時間，コンパイル時間の比較を示す．
-0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msecである．
-同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msecである．
+表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，ライブラリとアプリケーションを合わせたバイトコードのサイズ，ロード処理時間，コンパイル時間の比較を示す\footnote{0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msecである．
+同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msecである．}．
 mrubyアプリケーションのみのバイトコードの方が，ライブラリを含めた場合よりも，すべての点で優れている．
-これは，RiteVMひとつの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
-さらに，この設計では，SDカードやROMを接続したり，OSを再起動する手間も省くことができる．
-以上より，提案フレームワークは，既存フレームワークより作業効率を向上させることができる．
+これはRiteVM一つの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
+さらに，この設計ではSDカードやROMを上書きしたり，OSを再起動する手間も省くことができる．
+以上より，提案フレームワークは，既存フレームワークより作業効率を向上できる．
 
@@
     \centering
-    \caption{転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間}
+    \caption{バイトコードのサイズと処理時間およびコンパイル時間}
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|c|c}
@@
     \end{tabular}
+    }
+    \vspace{-5mm}
     \label{tab:size_and_time}
@@
 次に，図\ref{fig:comparison_s_c_m}に，シングルタスク，コルーチン，マルチタスクの実行時間を示す．
-評価用のアプリケーションとして，100,000回ループするプログラムを適用した．
-マルチタスクおよびコルーチンは，2つのタスクでそれぞれ50,000回ループするプログラムを用いた．
-マルチタスクの実行時間は，シングルタスクよりも遅いが，コルーチンより速い．
-この結果から，提案フレームワークのマルチタスク処理は，コルーチンより有効である．
-RiteVMスケジューラのオーバヘッドは，約5\%である．
-タスクの切り替えそのものにかかる時間は，約3μsecである．
+評価用アプリケーションとして，100,000回ループするプログラム(マルチタスクおよびコルーチンは，2つのタスクでそれぞれ50,000回ループ)を用いた．
+実行時間の観点では，提案手法のマルチタスクは，コルーチンより有効である．
+シングルタスクと比べても，RiteVMスケジューラのオーバヘッドは約5\%と実用的に問題ない．
+タスクの切り替えそのものにかかる時間は，約3$\mu$secである．
 RiteVMスケジューラは，周期的に割り込み，タスクの切り替えの処理を行うため，これがオーバヘッドとなっている．
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_s_c_m.pdf}
+    \vspace{-2mm}
     \caption{シングルタスク，コルーチン，マルチタスクの実行時間}
+\vspace{-3mm}
     \label{fig:comparison_s_c_m}
@@
 この評価では，TOPPERS/HRP2の仕様により周期時間の下限を1msecとした．
-また，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を10msecとした．
+また，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を8msecとした．
 周期時間が大きいほど，タスクの切り替え回数は減少するため，実行時間は小さくなることが分かる．
-1msecと10msecでは，約3\%減少している．
-1msecと8msecでは，約1\%減少している．
-タスクを並行動作させるには，より小さい周期時間の方が好まれるが，オーバヘッドは大きくなる．
-しかし，周期時間によるオーバヘッドは，誤差に埋もれるほど小さい．
+%1msecと10msecでは，約3\%減少している．
+1msecと8msecでは，約1\%しか減少していない．
+小さい周期時間でもオーバヘッドは大きくないため，効率的にタスクを並行動作できる．
+%しかし，周期時間によるオーバヘッドは，誤差に埋もれるほど小さい．
 
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_msec.pdf}
+    \vspace{-2mm}
     \caption{周期時間によるオーバヘッド}
+\vspace{-3mm}
     \label{fig:comparison_msec}
@@
 (A)の.cファイルは，RiteVMの数に比例して増えているのに対して，(B)の.cファイルは同じである上に，RiteVMの数にかかわらず，修正することなく同一のファイルを使用できる．
-さらに，.cdlファイルは両者違いはない．
-コンポーネントベース開発を上手く活用することで，コードの行数を減らすことができ，高い生産性やメンテナンス性につながる．
-その上，同じ.cファイルを利用できるため，開発者がファイルを修正する手間を省くことも可能になる．
+.cdlファイルは両者違いはない．
+コンポーネントベース開発を上手く活用することで，コードの行数が減ることを示した．%高い生産性やメンテナンス性につながる．
+その上，同じ.cファイルを利用できるため，開発者がファイルを修正する手間を省くこともできる．
 
@@
         .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
-        %\multicolumn{3}{l}{  }\\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
     \end{tabular}
+    \vspace{-3mm}
     \label{tab:codesize}
@@
 
+\vspace{-2mm}
 \section{関連研究}
+\vspace{-2mm}
 \label{sec:Related Work}
+% \begin{table*}[t]
+%     \centering
+%     \caption{関連研究}
+%     {\tabcolsep=0.1cm
+%     \begin{tabular}{c||c|ccccccc}
+%         & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+%         python-on-a-chip\cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
+%         Owl system\cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
+%         eLua\cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+%         mruby\cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
+%         mruby on TECS\cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
+%         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
+%     \end{tabular}
+% }
+%     \label{tab:comparison}
+% \end{table*}
+現在，オープンソースのスクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている.
+python-on-a-chip\cite{url:python-on-a-chip}, Owl system\cite{par:owl}, eLua\cite{url:eLua}, mruby\cite{par:mruby}, mruby on TECS\cite{par:mrubyonTECS}.
 
-\begin{table*}[t]
-    \centering
-    \caption{関連研究}
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
-        python-on-a-chip\cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-        Owl system\cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        eLua\cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        mruby\cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS\cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
-        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
-    \end{tabular}
-}
-    \label{tab:comparison}
-\end{table*}
-現在，オープンソースのスクリプト言語のランタイムシステムとして，次のものが開発されている.
-python-on-a-chip\cite{url:python-on-a-chip}, the Owl system\cite{par:owl}, eLua\cite{url:eLua}, mruby\cite{par:mruby},\cite{url:mruby}, mruby on TECS\cite{par:mrubyonTECS}.
+python-on-a-chip (p14p)は，PyMyteと呼ばれるPythonVMを使用するPythonランタイムシステムである．
+PyMyteは，低リソースでPythonプログラムを実行する．
+p14pでは，複数のグリーンスレッドを並列動作できる．
 
-python-on-a-chip(p14p)は，PyMyteと呼ばれるPythonVMを使用する，Pythonランタイムシステムである．
-PyMyteは，マイクロコントローラー上で低リソースでPythonプログラムを実行する．
-p14pは，スタックレスなグリーンスレッドを複数動作させることができる．
-
-Owl systemは，組込みシステム向けのPythonランタイムシステムであり，ARM Cortex-M3 マイクロコントローラー上で動く．
+Owl systemは，組込みシステム向けのPythonランタイムシステムであり，ARM Cortex-M3 マイコン上で動く．
 Owlツールチェーンは，Pythonコードから，マイコン上で直接起動するメモリイメージを生成する．
@@
 
-eLuaは，Luaを組込みシステム向けの完全な実装である．
+eLuaは，Luaの組込みシステム向け実装である．
 %Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
-Luaは，協調的マルチタスク処理が可能なコルーチンをサポートしているが，コルーチンは，ノンプリエンプティブであるため，マルチタスク処理のようなプログラムを行うのは難しい．
+Luaは，コルーチンをサポートしているが，ノンプリエンプティブであるため，マルチタスク処理のようなプログラムを行うのは難しい．
 
@@
 %mruby on TECSは，mrubyより実行速度が100倍速い．
-mruby on TECSは，マルチタスクをサポートしているが，マルチタスク処理を行うには，開発者がRTOSの機能を呼び出す必要がある．
+mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの機能を呼び出す必要がある．
 
-表\ref{tab:comparison}に，提案フレームワークと既存研究の比較を示す．
-提案フレームワークでは，ローダに加えて，VMスケジューラとアプリケーションの同期機構を提供する．
+%表\ref{tab:comparison}に，提案フレームワークと既存研究の比較を示す．
+%提案フレームワークでは，ローダに加えて，VMスケジューラとアプリケーションの同期機構を提供する．
 
+\vspace{-2mm}
 \section{おわりに}
+\vspace{-2mm}
 \label{sec:Conclusion}
 本研究では，mruby on TECSの拡張として，Bluetoothを用いたmrubyバイトコードローダとRiteVMスケジューラを提案した．
-mrubyバイトコードローダによって，開発者はSDカードやROMを上書きしたり，OSを再起動する手間が省けるため，mruby on TECSでのソフトウェア開発の作業効率を向上させる．
+ローダによって，開発者はSDカードやROMを上書きしたり，OSを再起動する手間が省けるため，ソフトウェア開発の作業効率を向上できる．
 ローダは，Bluetoothだけでなく，有線のシリアル通信にも対応しているため，様々な組込みシステムに適用できる．
-RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行する.
-実験評価では，ローダによる作業効率の向上やオーバヘッドの少ないマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
+RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行し，同期機構によりタスク起動を同期する.
+実験評価では，ローダによる作業効率の向上やマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
 
 さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる.
-RiteVMスケジューラも容易に付け外しできるため，開発者は，フェアスケジューリングか固定優先度スケジューリングかを選択することもできる．
-コンポーネントベース開発は，生産性を向上させ，システムの複雑さを減らすことができる．
+%RiteVMスケジューラも容易に付け外しできるため，開発者は，フェアスケジューリングか固定優先度スケジューリングかを選択することもできる．
+%コンポーネントベース開発は，生産性を向上させ，システムの複雑さを減らすことができる．
 
@@
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-3mm}
+\footnotesize
 \bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}

### 2016-02-21 ETNET2016/thesis.tex
update

@@
 TOPPERS/HRP2は，$\mu$ITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
-しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{url:ASP}といったRTOSにも対応しているため，mruby on TECSはRTOSに依存しない．
+しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{par:ASP}といったRTOSにも対応しているため，mruby on TECSはRTOSに依存しない．
 

### 2016-02-21 EMSOFT2016/thesis.tex
update

@@
 mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
+mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
@@
 Although script languages are easy to use and read, their execution time are slower than C language's.
-For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
+For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
 Therefore, it is difficult to apply the script languages to embedded systems.
@@
 \item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
-In additon, synchronization of multipel tasks is also implemented.
+In additon, synchronization of multiple tasks is also implemented.
 \item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
@@
 TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
+TECS helps decrease difficulty because the generated component diagram can visualize the structure of whole software.
 It can also help increase productivity and reduce development duplication because a common part of software is regarded as a component.
@@
 TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.
+However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.
 
@@
 %Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to connect a storage/ROM device to restart an OS.
+In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
 These advantages lead improvement of the software development efficiency.
@@
 In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
+%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
 This result shows the proposed design is superior to co-routine in terms of execution time.
-The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
+Moreover, developers can utilize the scheuler practically because the overhead of the RiteVM scheuler is about 5 \%.
 Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
@@
 A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
-More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
-Each execution time of cyclic period is the same as the others.
-That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
-This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
-The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
+More than eight msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
+%Each execution time of cyclic period is the same as the others.
+%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
+The execution time decreases as the cyclic time become larger, because the number of switching tasks decreases.
+The execution time of one msec is only about 1 \% lager than that of eight msec.
+The RiteVM scheuler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
+%This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
+%The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
 
@@
 (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
-(B) is not modified, and can be utilized regardless of the number of RiteVMs.
+In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
+(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
 Moreover, lines of two .cdl files are equal.
-The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
+The skillfull component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
 
@@
                 & (A)       & (B)     & Diff  \\ \hline
-        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
-        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
-        \multicolumn{3}{l}{  }\\
+        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
@@
 Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
-Component-based development can increase productivity and decrease complexity.
+Component-based development can increase productivity.
 

### 2016-02-22 EMSOFT2016/thesis.tex
update

@@
 To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
-The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
-%Specifically, a cyclic handler of switching tasks is implemented.
-%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.
+The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+%Specifically, a periodic handler of switching tasks is implemented.
+%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.
 
@@
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
-In additon, synchronization of multiple tasks is also implemented.
+\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
+In addition, synchronization of multiple tasks is also implemented.
 \item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
@@
 The mruby applications run at the same time because of synchronization processing.
-The RiteVM scheuler switches tasks as multiple tasks can run in concurrent.
+The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
 
@@
 
-As an approach for multitask processing, the proposed framework provides the RiteVM scheuler which is a fair scheduler and runs multiple tasks equally.
-The RiteVM scheuler is utilized only when application tasks have the same priority.
+As an approach for multitask processing, the proposed framework provides the RiteVM scheduler which is a fair scheduler and runs multiple tasks equally.
+The RiteVM scheduler is utilized only when application tasks have the same priority.
 mruby applications can run in concurrent without developers calling the OS's function.
@@
 
-A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
@@
 
-Figure \ref{fig:cyclic_handler} shows a component diagram of the cyclic handler.
-The components of cyclic handler consist of two components: CyclicHandler and CyclicMain.
-CyclicHandler {\it cell} configures the cyclic handler based on $\mu$ITRON.
+Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
+The components of periodic handler consist of two components: CyclicHandler and CyclicMain.
+CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
 Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
-The cyclic handler has five arguments: ID, attribute, cyclic time, cyclic phase and access pattern.
+The periodic handler has five arguments: ID, attribute, periodic time, periodic phase and access pattern.
 CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
-CyclicMain {\it cell} is a component to perform the processing body of a cyclic handler.
+CyclicMain {\it cell} is a component to perform the processing body of a periodic handler.
 {\it rotateReadyQueue} is implemented as the body.
@@
 Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
-In the part of CyclicHandler {\it cell}, configurations of a cyclic handler is described such as attribute, cyclicTime and cyclicPhase.
-In this case, the cyclic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the cyclic handler is in an operational state after the creation.
-The cyclic handler is executed every one msec.
+In the part of CyclicHandler {\it cell}, configurations of a periodic handler is described such as attribute, cyclicTime and cyclicPhase.
+In this case, the periodic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the periodic handler is in an operational state after the creation.
+The periodic handler is executed every one msec.
 In another part, the priority of CyclicMain {\it cell} is described.
@@
 
-In addtion, the end of mruby applications is synchronized to accept the continuous loading.
+In addition, the end of mruby applications is synchronized to accept the continuous loading.
 The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
@@
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
+For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
 This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
 
-In additon, the code size can desrease by developing with component-based. 
+In addition, the code size can decrease by developing with component-based. 
 In the proposed framework, the advantage is applied in the Eventflag component.
@@
 Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
-In additon, the components of Eventflag are built with {\it [optional]} in TECS.
+In addition, the components of Eventflag are built with {\it [optional]} in TECS.
 {\it [optional]} means that the codes are run only when the call port is connected.
@@
     \item Execution time with singletasking, co-routine, and multitasking
-    \item Overhead for cyclic time
+    \item Overhead for periodic time
 %    \item Synchronization of mruby applications
@@
 Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
-The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
+The mruby application bytecode is smaller and faster than that of including mruby libraries in all terms.
 The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
@@
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
-In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
+In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is one msec.
 %While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
 This result shows the proposed design is superior to co-routine in terms of execution time.
-Moreover, developers can utilize the scheuler practically because the overhead of the RiteVM scheuler is about 5 \%.
+Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
 Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
@@
 %Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-The scheuler interrupts and switches tasks, which causes this overhead.
+The scheduler interrupts and switches tasks, which causes this overhead.
 
@@
 
-Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
-A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
-More than eight msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
+Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
+A lower limit of the periodic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
+More than eight msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
 %Each execution time of cyclic period is the same as the others.
 %That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
-The execution time decreases as the cyclic time become larger, because the number of switching tasks decreases.
+The execution time decreases as the periodic time become larger, because the number of switching tasks decreases.
 The execution time of one msec is only about 1 \% lager than that of eight msec.
-The RiteVM scheuler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
-%This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
-%The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
+The RiteVM scheduler with small periodic time can effectively execute multiple tasks because the periodic time overhead is not large.
+%This results also shows the overhead becomes smaller as the periodic time is larger, because the overhead depends on the number of switching tasks.
+%The smaller periodic time is better in multitasking due to concurrent and/or parallel processing.
 
@@
 Moreover, lines of two .cdl files are equal.
-The skillfull component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
+The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
 
@@
     \centering
-    \caption{Comparion of the proposed and previous work}
+    \caption{Comparison of the proposed and previous work}
     \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
@@
 python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
-The VM runs a significant subset of Python language with few resources on a microcontroller.
+The VM runs a significant subset of Python language with few resources on a micro-controller.
 p14p can run multiple stackless green threads.
@@
 The Owl system is an embedded Python run-time system.
-The Owl is a complete system for ARM Cortex-M3 microcontrollers.
-The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
+The Owl is a complete system for ARM Cortex-M3 micro-controllers.
+The Owl toolchain produces relocatable memory images, that are directly runnable on the micro-controller, from Python code objects.
 The interpreter of the Owl system is the same as that of python-on-a-chip.
@@
 Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-The proposed framework supports the loader, the VM scheuler, and synchronization of application.
+The proposed framework supports the loader, the VM scheduler, and synchronization of application.
 
@@
 \label{sec:Conclusion}
-This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
+This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
 The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
@@
 %Thus, the proposed framework can be utilized on the deveces without Bluetooth.
-The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
+The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
 In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
 The loader can improve the software development efficiency on mruby on TECS.
-The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
+The RiteVM scheduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
 %because of the low overhead.
@@
 The proposed framework is developed in component-base by TECS.
-The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+The facilities such as RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
-Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
+Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily removed.
 Component-based development can increase productivity.

### 2016-02-22 ETNET2016/thesis.tex
update

@@
 
-mrubyは，Rubyの高い生産性を持ち，少ないリソースで起動が速いため，組込みシステムに適している．
-mrubyには，RiteVMと呼ばれるVMが実装されており，どのOS上でも同じmrubyプログラムを起動できる．
+mrubyは，Rubyの高い生産性を持ち，少ないリソースで動くため，組込みシステムに適している．
+mrubyには，RiteVMと呼ばれるVMが実装されており，どのOS上でも同じmrubyプログラムを実行できる．
 %図\ref{fig:mruby}にRiteVMのメカニズムを示す．
@@
 \label{sec:mruby on TECS}
-mruby on TECSは，mrubyを用いた組込みソフトウェアのコンポーネントベース開発が可能なフレームワークである．
+mruby on TECSは，mrubyを用いたコンポーネントベース開発が可能なフレームワークである．
 %\subsubsection{システムモデル}
 %図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
-mrubyバイトコードはそれぞれ，コンポーネント化されたRTOSのタスクとして，RiteVM上で実行される．
+mrubyバイトコードはそれぞれ，コンポーネント化されたRTOS (リアルタイムOS)のタスクとして，RiteVM上で実行される．
 %TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
@@
 RiteVMスケジューラはタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作できる．
-また，mrubyアプリケーションの起動は同期機構により同期される．　
+mrubyアプリケーションの起動はイベントフラグを用いた同期機構により同期される．　
 \begin{figure}[t]
@@
 ローダは，mruby on TECSで提供されているRiteVMコンポーネント\cite{par:mrubyonTECS}を拡張して実装した．
-
 このコンポーネントでは，転送されたバイトコードの受信に加え，RiteVMのコンフィグレーションが行われる．
@@
 MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2)のタスクである．
-MrubyBluetooth1は，ローダを実装したRiteVMのコンポーネントであり，転送されるバイトコードを受信する．
+MrubyBluetooth1は，ローダを実装したRiteVMコンポーネントであり，転送されるバイトコードを受信する．
 バイナリ転送プロトコルは，ZMODEMを適用した．
@@
 
-図\ref{fig:control_flow}に，ローダを実装したRiteVMがmrubyプログラムを実行するまでのフローチャートを示す．
-
-はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する．
+図\ref{fig:control_flow}にローダを実装したRiteVMがmrubyプログラムを実行するまでのフローチャート，図\ref{maincode_mrubybluetooth}に処理のソースコードを示す．
+．
+はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する(図\ref{fig:control_flow}:A，図\ref{maincode_mrubybluetooth}:2-5行目)．
 %{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
 
-次に，mrubyライブラリのバイトコードを読み込む．
+次に，mrubyライブラリのバイトコードを読み込む(図\ref{fig:control_flow}:B，図\ref{maincode_mrubybluetooth}:8行目)．
 図\ref{celltype_mrubybluetooth}に示す通り，tMrubyBluetoothのセルは属性を持っている．
@@
 
-次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む．
+次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む(図\ref{fig:control_flow}:C，図\ref{maincode_mrubybluetooth}:10,12行目)．
 mrubyアプリケーションのバイトコードは，変数uint8\_t型の配列{\it irepApp}に格納される．
@@
 
-最後に，RiteVMはmrubyアプリケーションであるタスクを実行する．
+最後に，RiteVMはmrubyアプリケーションであるタスクを実行する(図\ref{fig:control_flow}:D，図\ref{maincode_mrubybluetooth}:12行目)．
 mrubyアプリケーションのプログラムが修正された場合は，そのバイトコードのみを再転送する．
-以上の処理のソースコードを図\ref{maincode_mrubybluetooth}に示す．
+%以上の処理のソースコードを図\ref{maincode_mrubybluetooth}に示す．
 
@@
   /*Omit: initialization of mruby-TECS bridge*/
+  /*Load mruby library bytecode and run*/
+  mrb_load_irep_cxt( mrb, ATTR_irep, c );
   /*Receive the bytecode via Bluetooth*/
   bluetooth_loader( VAR_irepApp );
-  /*Load mruby library bytecode and run*/
-  mrb_load_irep_cxt( mrb, ATTR_irep, c );
   /*Load mruby application bytecode and run*/
@@
 マルチタスク処理のアプローチのひとつにコルーチンがある．
-コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並列動作できるが，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるので，OSのサポートやマルチコアの恩恵を受けることができない．
+コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並行動作できるが，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるため，OSのサポートやマルチコアの恩恵を受けることができない．
 Rubyのコルーチンは，Fiberクラス\cite{url:co-routine}に定義されている．
@@
 
-提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを提供し，複数のタスクを平等に並行動作させる．
-このスケジューラはアプリケーションタスクが同じ優先度を持つ場合に利用でき，開発者がOSの関数を呼び出すことなく，マルチタスク処理が可能になる．
+提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを提供し，複数のVMを平等に並行動作させる．
+RiteVMスケジューラはRiteVMタスクが同じ優先度を持つ場合に利用でき，開発者がOSの関数を呼び出すことなく，マルチタスク処理が可能になる．
 その上，既存のアプリケーションプログラムの構造を変えることなく使うことができる．
@@
 \subsubsection{RiteVMスケジューラ}
-RiteVMスケジューラは，周期ハンドラであり，同優先度のタスクの実行を切り替える$\mu$ITRONのサービスコールである{\it rotateReadyQueue}を周期的に呼び出す．
+RiteVMスケジューラは，周期ハンドラを利用して実装し，同優先度のタスクの実行を切り替える$\mu$ITRONのサービスコールである{\it rotateReadyQueue}を周期的に呼び出す．
 %{\it rotateReadyQueue}は，同優先度のタスクの実行を切り替える関数である．
@@
 
-{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示すように，タスクの起動が切り替わる．
+{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示す通り，タスクの起動が切り替わる．
 {\it rotateReadyQueue}の引数は，優先度である．
@@
 %CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
-attributeには，OSが起動すると実行状態になる{\it TA\_STA}，周期時間には，1msecが与えられる．
+attributeには，OSが起動すると実行状態になる{\it TA\_STA}，周期時間には，1msが与えられる．
 CyclicMainセル部分は，属性priorityを持っており，mrubyタスクの優先度であるRITEVM\_PRIORITYが与えられる．
@@
 \subsubsection{mrubyアプリケーションの同期機構}
-複数のmrubyアプリケーションの起動を同期させるために，イベントフラグを適用した．
+複数のmrubyアプリケーションの起動を同期させるために，イベントフラグを用いて同期処理を行った．
 %タスクはそれぞれ0x01(01)，0x02(10)のパターンをセットし，待ちパターン0x3(11)でAND待ちする．
 %この機構は，2つ以上のタスクの場合でも適用できる．
-タスクが4つの場合，タスクはそれぞれ，0x01(0001), 0x02(0010), 0x04(0100), 0x08(1000)のパターンをセットし，待ちパターン0x0f(1111) でAND待ちする．(図\ref{fig:Eventflag} (A))
+RiteVMが4つの場合，各VMはそれぞれ，イベントフラグに0x01(0001), 0x02(0010), 0x04(0100), 0x08(1000)のパターンをセットし，待ち状態へと遷移する(図\ref{fig:Eventflag} (A))．
+イベントフラグが待ちパターン0x0f(1111)になると，各VMは実行可能状態になり，アプリケーションを同時に実行する．
 
 さらに，バイトコードの連続ローディングに対応するため，アプリケーションの終了も同期する．
-これにより，すぐに終了するアプリケーションのRiteVMが次のロード待機状態に入るのを防げ，すべてのRiteVMは同時に次のロード待機状態になる．
+終了も同期することで，すぐに終了するアプリケーションのRiteVMが次のロード待機状態に入るのを防げ，すべてのRiteVMは同時に次のロード待機状態になる．
 
@@
 {\it cEventflag\_set(ATTR\_setPattern)}のように，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じCファイルを使用できる．
-さらに，TECSのオプション{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグの結合を切った場合にでも同じCファイルを利用できる．
+さらに，TECSのオプション{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグを利用しない場合でも同じCファイルを利用できる．
 
@@
 本評価実験は，ターゲットデバイスとして，LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip)を使用した．
-コンパイラは，gcc 4.9.3 -O2 および mrubyのバージョンは，1.2.0である．
+コンパイラは，gcc 4.9.3 -O2 および mrubyのバージョンは1.2.0である．
 
-表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，ライブラリとアプリケーションを合わせたバイトコードのサイズ，ロード処理時間，コンパイル時間の比較を示す\footnote{0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msecである．
-同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msecである．}．
+表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，ライブラリとアプリケーションを合わせたバイトコードのサイズ，ロード処理時間，コンパイル時間の比較を示す\footnote{0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msである．
+同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msである．}．
 mrubyアプリケーションのみのバイトコードの方が，ライブラリを含めた場合よりも，すべての点で優れている．
-これはRiteVM一つの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
+上記の結果は，RiteVM一つの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
 さらに，この設計ではSDカードやROMを上書きしたり，OSを再起動する手間も省くことができる．
@@
 シングルタスクと比べても，RiteVMスケジューラのオーバヘッドは約5\%と実用的に問題ない．
-タスクの切り替えそのものにかかる時間は，約3$\mu$secである．
+タスクの切り替えそのものにかかる時間は，約3$\mu$sある．
 RiteVMスケジューラは，周期的に割り込み，タスクの切り替えの処理を行うため，これがオーバヘッドとなっている．
@@
 図\ref{fig:comparison_msec}は，RiteVMスケジューラの周期時間ごとの実行時間を示している．
-この評価では，TOPPERS/HRP2の仕様により周期時間の下限を1msecとした．
-また，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を8msecとした．
+この評価では，TOPPERS/HRP2の仕様により周期時間の下限を1msとした．
+一方で，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を8msとした．
 周期時間が大きいほど，タスクの切り替え回数は減少するため，実行時間は小さくなることが分かる．
 %1msecと10msecでは，約3\%減少している．
-1msecと8msecでは，約1\%しか減少していない．
+1msと8msでは，約1\%しか減少していない．
 小さい周期時間でもオーバヘッドは大きくないため，効率的にタスクを並行動作できる．
@@
 コンポーネントベース開発を上手く活用することで，コードの行数が減ることを示した．%高い生産性やメンテナンス性につながる．
-その上，同じ.cファイルを利用できるため，開発者がファイルを修正する手間を省くこともできる．
+その上，RiteVMの数に限らず同じ.cファイルを利用できる．%ため，開発者がファイルを修正する手間を省くこともできる．
 
@@
         .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
         .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
@@
 % \end{table*}
-現在，オープンソースのスクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている.
+現在，スクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている.
 python-on-a-chip\cite{url:python-on-a-chip}, Owl system\cite{par:owl}, eLua\cite{url:eLua}, mruby\cite{par:mruby}, mruby on TECS\cite{par:mrubyonTECS}.
@@
 PyMyteは，低リソースでPythonプログラムを実行する．
-p14pでは，複数のグリーンスレッドを並列動作できる．
+p14pでは，複数のグリーンスレッドを並行動作できる．
 
@@
 %Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
-Luaは，コルーチンをサポートしているが，ノンプリエンプティブであるため，マルチタスク処理のようなプログラムを行うのは難しい．
+Luaは，コルーチンをサポートしているが，ノンプリエンプティブであるため，マルチタスク処理を行うのは難しい．
 
@@
 
-ソフトウェア開発をさらに効率よく行うために，プラグインを使用したRiteVMやmruby-TECSブリッジの.cdlファイルの自動生成や，コマンドライン上でのバイトコードの転送などを提供することが，今後の課題である．
+ソフトウェア開発をさらに効率よく行うために，%プラグインを使用したRiteVMやmruby-TECSブリッジの.cdlファイルの自動生成や，
+VM間の通信機能や，コマンドライン上でのバイトコード転送機能を提供することが，今後の課題である．
 

### 2016-02-22 thesis/thesis.tex
update

@@
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
 Synchronization of starting multiple tasks is also implemented with Eventflag. 
@@
 
-%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
+%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
 mruby on TECS has several problems at present.
@@
 This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
-The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
+To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
+The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
 %Specifically, a cyclic handler of switching tasks is implemented.
@@
 \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
-The loader supports the countinuous loading, which saves the Bluetooth set-up time.
+The loader supports the continuous loading, which saves the Bluetooth set-up time.
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
-In additon, synchronization of multiple tasks is also implemented.
+\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
+In addition, synchronization of multiple tasks is also implemented.
 \item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
@@
 
-\subsection{Component Model}\mbox{}\\
+\subsection{Component Model}
 
@@
 
-\subsection{Component Description}\mbox{}\\
+\subsection{Component Description}
 
@@
 
-\subsection{System Model}\mbox{}\\
+\subsection{System Model}
 
@@
 
-\subsection{mruby-TECS Bridge}\mbox{}\\
+\subsection{mruby-TECS Bridge}
 
@@
 Due to this design, RiteVMs can share the mruby libraries.
-In additon, a RiteVM can use the own library that other RiteVMs should not use.
+In addition, a RiteVM can use the own library that other RiteVMs should not use.
 
@@
 
-\subsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
+\subsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
 
@@
 
-\subsection{RiteVM Scheduler} \mbox{}\\
+\subsection{RiteVM Scheduler}
 
@@
     \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
-    \caption{The design of RiteVM sceduler}
+    \caption{The design of RiteVM scheduler}
     \label{fig:rotateReadyQueue}
@@
 
-\subsection{Component of RiteVM Scheduler} \mbox{}\\
+\subsection{Component of RiteVM Scheduler}
 
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
+\subsection{Synchronization of Multiple RiteVM Tasks}
 
@@
 
-In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
+For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
 This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
 
-In additon, the code size can desrease by developing with component-based. 
+In addition, the code size can decrease by developing with component-based. 
 In the proposed framework, the advantage is applied in the Eventflag component.
@@
 This result shows the proposed design is superior to co-routine in terms of execution time.
-Moreover, developers can utilize the scheuler practically because the overhead of the RiteVM scheuler is about 5 \%.
+Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
 Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
@@
 The execution time of one msec is only about 1 \% lager than that of eight msec.
-The RiteVM scheuler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
+The RiteVM scheduler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
 %This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
@@
 Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-The proposed framework supports the loader, the VM scheuler, and synchronization of application.
+The proposed framework supports the loader, the VM scheduler, and synchronization of application.
 \begin{landscape}
@@
     \centering
-    \caption{Comparion of the proposed and previous work}
+    \caption{Comparison of the proposed and previous work}
     \footnotesize
     \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Management & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
@@
 \label{sec:Conclusion}
-This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
+This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
 The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
 The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
-%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
-The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
+%Thus, the proposed framework can be utilized on the devices without Bluetooth.
+The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
 In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
 The loader can improve the software development efficiency on mruby on TECS.
-The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
+The RiteVM scheduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
 %because of the low overhead.
@@
 In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
-Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+%Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+Moreover, synchronization functionality between the RiteVMs will be proposed, and developers can send a bytecode with ZMODEM protocol on the commend line.
 

### 2016-02-23 ETNET2016/thesis.tex
ETNET2016 fin.

@@
 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
-さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
 本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
-さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する.
-\vspace{-5mm}
+さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する．
+\vspace{-4mm}
 \end{abstract}
@@
 In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of RTOSs to effectively execute multiple mruby programs in concurrent or/and parallel.
+Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of RTOSs to effectively execute multiple mruby programs in concurrent.
 To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
 In addition, multiple mruby programs cooperatively run in the proposed framework.
-A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
-\vspace{-5mm}
+%A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
+\vspace{-4mm}
 \end{eabstract}
@@
 スクリプト言語は，その使いやすさから高い生産性を持っているため，効率的かつ短期間での開発ができる．
-有名なスクリプト言語として，Ruby, Perl，Python，Luaなどがある．
+有名なスクリプト言語として，Ruby，Perl，Python，Luaなどがある．
 
-しかし，スクリプト言語は生産性が高い反面，C言語よりも実行時間が遅い．
-組込みシステムにとって，デッドラインを守るといったリアルタイム性は重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
+しかし，スクリプト言語は生産性が高い反面，C言語よりも実行時間が遅く，実行時間にばらつきがある．
+多くの組込みシステムは，リアルタイム性が重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
 
 %mruby on TECSは，スクリプト言語であるmruby使用したコンポーネントベース開発が可能なフレームワークである\cite{par:mrubyonTECS}．
-mruby on TECS \cite{par:mrubyonTECS}は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステム向けのコンポーネントシステムであるTECSを利用したフレームワークである.
-mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べてアプリケーションを約100倍速く実行できる.
+mruby on TECS \cite{par:mrubyonTECS}は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステム向けのコンポーネントシステムであるTECSを利用したフレームワークである．
+mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べてアプリケーションを約100倍速く実行できる．
 
@@
 例えば，LEGO MINDSTORMS EV3のプラットフォーム\cite{par:EV3}を利用した場合，mrubyプログラムを修正する度に，SDカードの抜き差しを行う必要がある．
-%mruby on TECS では，mruby プログラムを修正する度にターゲットデバイスでSD カードまたはROMに書き込みし，OS を再起動する必要がある.
-さらに，mruby on TECSはマルチVMに対応してるが，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
+%mruby on TECS では，mruby プログラムを修正する度にターゲットデバイスでSD カードまたはROMに書き込みし，OS を再起動する必要がある．
+さらに，mruby on TECSはマルチVMに対応しているが，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない．
 
@@
 本論文では，上記の問題を解決するため，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダおよびRiteVMスケジューラを提案する．
-% 提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する.
-% ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する. 
-% ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する.
-% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
+% 提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する．
+% ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する． 
+% ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する．
+% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる．
 % RiteVMに実装されたローダが，ホストから転送されたバイトコードを受信し，アプリケーションを実行する．
-% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
-% さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる.
+% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる．
+% さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる．
 
-本論文における貢献は次のとおりである．
+本論文における貢献は次の通りである．
 mrubyバイトコードローダにより，ソフトウェア開発における作業効率を向上させる．
-RiteVMスケジューラにより，複数のmrubyプログラムを効率的に並行・並列動作させる．
+RiteVMスケジューラにより，複数のmrubyプログラムを効率的に並行動作させる．
 コンポーネントベース開発の利点を明らかにする．
@@
 % Developers do not need to rewrite a storage/ROM device and also to restart an OS. 
-% The loader supports the countinuous loading, which saves the Bluetooth setup time. 
+% The loader supports the continuous loading, which saves the Bluetooth setup time. 
 % Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
 % 2) To effectively execute multiple mruby programs in concurrent or/and parallel: 
-% Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
-% In additon, synchronization of multiple tasks is also implemented.
+% Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
+% In addition, synchronization of multiple tasks is also implemented.
 % 3) To focus on the benefits of component-based developments:
@@
 % 図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
-% RiteVMとmrubyライブラリを含むプラットフォーム部分は，はじめにターゲットデバイス上で起動されている．
+% RiteVMとmrubyライブラリを含むプラットフォーム部分は，始めにターゲットデバイス上で起動されている．
 % mrubyアプリケーションのバイトコードは，ホストからターゲットデバイスへと転送される．
@@
 
-mrubyは，Rubyの高い生産性を持ち，少ないリソースで動くため，組込みシステムに適している．
+mrubyは，Rubyの高い生産性を持ち，Rubyより少ないリソースで動作するため，組込みシステムに適している．
 mrubyには，RiteVMと呼ばれるVMが実装されており，どのOS上でも同じmrubyプログラムを実行できる．
@@
 \subsubsection{コンポーネント記述}
-TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述に分類され，.cdlファイルに記述する．
+TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述に分類され，cdlファイルに記述する．
 図\ref{fig:component}のコンポーネント記述について次に述べる．
@@
         %図\ref{signature}のようにシグニチャsMotorを定義できる.
-        TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，[in]と[out]という指定子がつけられる．
+        TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，[in]と[out]という指定子が付けられる．
 
@@
         {\it celltype}キーワードに続けて，セルタイプ名(tCaller)を記述する．
-        図\ref{celltype}に示す通り，受け口は，{\it entry}キーワードに続けて，シグニチャ名, 受け口名を記述する．
+        図\ref{celltype}に示す通り，受け口は，{\it entry}キーワードに続けて，シグニチャ名，受け口名を記述する．
         同様にして，呼び口も定義できる．
@@
 %TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
-
-mruby-TECSブリッジによって，mrubyプログラムからC言語の関数を呼び出すことができる．
+さらに，mruby-TECSブリッジによって，mrubyプログラムからC言語の関数を呼び出すことができる．
 %mruby-TECSブリッジについては，以下で詳しく説明する．
@@
 
-%提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している.
+%提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している．
 
@@
 MrubyBluetooth1は，ローダを実装したRiteVMコンポーネントであり，転送されるバイトコードを受信する．
-バイナリ転送プロトコルは，ZMODEMを適用した．
+バイナリ転送プロトコルは，汎用性が良く，パフォーマンスが高いため，ZMODEM\cite{par:ZMODEM}を適用した．
 
@@
 図\ref{fig:control_flow}にローダを実装したRiteVMがmrubyプログラムを実行するまでのフローチャート，図\ref{maincode_mrubybluetooth}に処理のソースコードを示す．
-．
-はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する(図\ref{fig:control_flow}:A，図\ref{maincode_mrubybluetooth}:2-5行目)．
+
+はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する(図\ref{fig:control_flow}：A，図\ref{maincode_mrubybluetooth}：2-5行目)．
 %{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
 
-次に，mrubyライブラリのバイトコードを読み込む(図\ref{fig:control_flow}:B，図\ref{maincode_mrubybluetooth}:8行目)．
+次に，mrubyライブラリのバイトコードを読み込む(図\ref{fig:control_flow}：B，図\ref{maincode_mrubybluetooth}：8行目)．
 図\ref{celltype_mrubybluetooth}に示す通り，tMrubyBluetoothのセルは属性を持っている．
@@
 
-次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む(図\ref{fig:control_flow}:C，図\ref{maincode_mrubybluetooth}:10,12行目)．
+次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む(図\ref{fig:control_flow}：C，図\ref{maincode_mrubybluetooth}：10，12行目)．
 mrubyアプリケーションのバイトコードは，変数uint8\_t型の配列{\it irepApp}に格納される．
@@
 
-最後に，RiteVMはmrubyアプリケーションであるタスクを実行する(図\ref{fig:control_flow}:D，図\ref{maincode_mrubybluetooth}:12行目)．
+最後に，RiteVMはmrubyアプリケーションであるタスクを実行する(図\ref{fig:control_flow}：D，図\ref{maincode_mrubybluetooth}：12行目)．
 mrubyアプリケーションのプログラムが修正された場合は，そのバイトコードのみを再転送する．
@@
   /*Omit: Declaration variables*/
-  mrb=mrb_open(); /*New interpreter instance*/
+  mrb=mrb_open(); /*New mrb_state*/
   /*Omit: error check for mrb_state*/
-  c=mrbc_context_new( mrb ); /*New mruby context*/
+  c=mrbc_context_new( mrb ); /*New mrbc_context*/
   /*Omit: initialization of mruby-TECS bridge*/
@@
 
-マルチタスク処理のアプローチのひとつにコルーチンがある．
+マルチタスク処理のアプローチの一つにコルーチンがある．
 コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並行動作できるが，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるため，OSのサポートやマルチコアの恩恵を受けることができない．
@@
 
-{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示す通り，タスクの起動が切り替わる．
+{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示す通り，同優先度タスクの実行順序が切り替わる．
 {\it rotateReadyQueue}の引数は，優先度である．
@@
 {\it rotateReadyQueue}は，2つ以上のタスクの場合にでも利用できる．
-例えば，３つのタスクA, B, Cが順に起動する場合，{\it rotateReadyQueue}が呼ばれると，B, C, Aの順にタスクの起動は切り替わる．
+例えば，３つのタスクA，B，Cが順に起動する場合，{\it rotateReadyQueue}が呼ばれると，B，C，Aの順にタスクの実行順序は切り替わる．
 
@@
 RiteVMスケジューラのコンポーネントは，CyclicHandlerとCyclicMainから構成される．
-CyclicHandlerセルは，3つの属性(attribute, cyclicTime, cyclicPhase)を持っており，$\mu$ITRONの周期ハンドラ\cite{par:microITRON}の設定を行う．
+CyclicHandlerセルは，3つの属性(attribute，cyclicTime，cyclicPhase)を持っており，$\mu$ITRONの周期ハンドラ\cite{par:microITRON}の設定を行う．
 %$\mu$ITRONの周期ハンドラは，\cite{par:microITRON}に詳しく書かれている．
@@
 %CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
-attributeには，OSが起動すると実行状態になる{\it TA\_STA}，周期時間には，1msが与えられる．
+attributeには，OSが起動すると実行状態になる属性である{\it TA\_STA}，周期時間には，1msが与えられる．
 CyclicMainセル部分は，属性priorityを持っており，mrubyタスクの優先度であるRITEVM\_PRIORITYが与えられる．
@@
 %この機構は，2つ以上のタスクの場合でも適用できる．
-RiteVMが4つの場合，各VMはそれぞれ，イベントフラグに0x01(0001), 0x02(0010), 0x04(0100), 0x08(1000)のパターンをセットし，待ち状態へと遷移する(図\ref{fig:Eventflag} (A))．
+RiteVMが4つの場合，各VMはそれぞれ，イベントフラグに0x01(0001)，0x02(0010)，0x04(0100)，0x08(1000)のパターンをセットし，待ち状態へと遷移する(図\ref{fig:Eventflag} (A))．
 イベントフラグが待ちパターン0x0f(1111)になると，各VMは実行可能状態になり，アプリケーションを同時に実行する．
@@
 この章では，コンポーネントベース開発の利点を使った設計について述べる．
-提案フレームワークは，RiteVMやRiteVMスケジューラ，イベントフラグをコンポーネントとして提供しているため，開発者はそれらのコンポーネントを容易に付け外したり，再利用できる．
+提案フレームワークは，RiteVMやRiteVMスケジューラ，イベントフラグをコンポーネントとして提供しているため，開発者はそれらのコンポーネントを容易に付け外し，再利用できる．
 例えば，RiteVMスケジューラの機能を外したい場合，図\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}とコメントアウトするだけで良いため，開発者はカーネルの設定ファイルを修正する手間を省くことができる．
@@
 図\ref{fig:Eventflag} (B)に示す通り，イベントフラグのセットパターンと待ちパターンを属性として定義する．
-{\it cEventflag\_set(ATTR\_setPattern)}のように，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じCファイルを使用できる．
+{\it cEventflag\_set(ATTR\_setPattern)}のように，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じcファイルを使用できる．
 さらに，TECSのオプション{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグを利用しない場合でも同じCファイルを利用できる．
@@
 %プラットフォームの起動時間
-転送するバイトコードのサイズと処理時間およびコンパイル時間, 
-シングルタスク，コルーチン，マルチタスクの実行時間, 
-周期時間によるオーバヘッド,
-%mrubyアプリケーションの同期
-コンポーネントベース開発を利用したコード行数
-の評価を行った．
+転送するバイトコードのサイズと処理時間およびコンパイル時間，シングルタスク，コルーチン，マルチタスクの実行時間，周期時間によるオーバヘッド，コンポーネントベース開発を利用したコード行数の評価を行った．
 % \begin{itemize}
@@
 上記の結果は，RiteVM一つの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
-さらに，この設計ではSDカードやROMを上書きしたり，OSを再起動する手間も省くことができる．
+さらに，この設計ではSDカードやROMを上書きする手間や，OSを再起動する手間も省くことができる．
 以上より，提案フレームワークは，既存フレームワークより作業効率を向上できる．
@@
           Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
-          Load Process Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
+          Loading Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
           Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
@@
 % %Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-% The scheuler interrupts and switches tasks, which causes this overhead.
+% The scheduler interrupts and switches tasks, which causes this overhead.
 
@@
 
-表\ref{tab:codesize}に，2つの.cファイルと.cdlファイルのコード行数と変更行数の比較を示す．
+表\ref{tab:codesize}に，2つのcファイルとcdlファイルのコード行数と変更行数の比較を示す．
 (A)と(B)はそれぞれ，図\ref{fig:Eventflag}の上部と下部を指している．
-(A)の.cファイルは，RiteVMの数に比例して増えているのに対して，(B)の.cファイルは同じである上に，RiteVMの数にかかわらず，修正することなく同一のファイルを使用できる．
-.cdlファイルは両者違いはない．
+(A)のcファイルは，RiteVMの数に比例して増えているのに対して，(B)のcファイルは同じである上に，RiteVMの数に関わらず，修正することなく同一のファイルを使用できる．
+cdlファイルに差はない．
 コンポーネントベース開発を上手く活用することで，コードの行数が減ることを示した．%高い生産性やメンテナンス性につながる．
-その上，RiteVMの数に限らず同じ.cファイルを利用できる．%ため，開発者がファイルを修正する手間を省くこともできる．
+その上，RiteVMの数に限らず同じcファイルを利用できる．%ため，開発者がファイルを修正する手間を省くこともできる．
 
-% To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
+% To indicate the superior of component-based development, the comparison of code lines between two c files is shown in Table \ref{tab:codesize}.
 % (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-% In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
+% In terms of c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
 % (B) is not modified, and can be utilized regardless of the number of RiteVMs.
-% Moreover, lines of two .cdl files are equal.
+% Moreover, lines of two cdl files are equal.
 % The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
@@
                 & (A)       & (B)     & Diff  \\ \hline
-        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
-        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
+        c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
     \end{tabular}
-    \vspace{-3mm}
+    \vspace{-2mm}
     \label{tab:codesize}
@@
 
-\vspace{-2mm}
+\vspace{-1mm}
 \section{関連研究}
@@
 % \end{table*}
-現在，スクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている.
-python-on-a-chip\cite{url:python-on-a-chip}, Owl system\cite{par:owl}, eLua\cite{url:eLua}, mruby\cite{par:mruby}, mruby on TECS\cite{par:mrubyonTECS}.
+現在，スクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている．
+python-on-a-chip\cite{url:python-on-a-chip}，Owl system\cite{par:owl}，eLua\cite{url:eLua}，mruby\cite{par:mruby}，mruby on TECS\cite{par:mrubyonTECS}．
 
@@
 
-\vspace{-2mm}
+\vspace{-1mm}
 \section{おわりに}
@@
 本研究では，mruby on TECSの拡張として，Bluetoothを用いたmrubyバイトコードローダとRiteVMスケジューラを提案した．
-ローダによって，開発者はSDカードやROMを上書きしたり，OSを再起動する手間が省けるため，ソフトウェア開発の作業効率を向上できる．
+ローダによって，開発者はSDカードやROMを上書きする手間や，OSを再起動する手間が省けるため，ソフトウェア開発の作業効率を向上できる．
 ローダは，Bluetoothだけでなく，有線のシリアル通信にも対応しているため，様々な組込みシステムに適用できる．
-RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行し，同期機構によりタスク起動を同期する.
-実験評価では，ローダによる作業効率の向上やマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
+RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行し，同期機構によりタスク起動を同期する．
+実験評価では，ローダによる作業効率の向上やマルチタスク設計の有用性，コンポーネントベース開発の利点を示した．
 
-さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる.
+さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる．
 %RiteVMスケジューラも容易に付け外しできるため，開発者は，フェアスケジューリングか固定優先度スケジューリングかを選択することもできる．
@@
 
-ソフトウェア開発をさらに効率よく行うために，%プラグインを使用したRiteVMやmruby-TECSブリッジの.cdlファイルの自動生成や，
+ソフトウェア開発をさらに効率良く行うために，%プラグインを使用したRiteVMやmruby-TECSブリッジのcdlファイルの自動生成や，
 VM間の通信機能や，コマンドライン上でのバイトコード転送機能を提供することが，今後の課題である．
@@
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-3mm}
-\footnotesize
+\vspace{-2mm}
 \bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}

### 2016-03-19 EMSOFT2016/diff/0317_thesis.tex
update

--- 2016-02-22 EMSOFT2016/thesis.tex
@@
 \input{dummy/dummy.tex}
-\documentclass[conference,compsoc]{IEEEtran}
-\usepackage[dvipdfmx]{graphicx}
+\documentclass{sig-alternate-05-2015}
+%\usepackage[dvipdfmx]{graphicx}
 \usepackage{amssymb}
@@
 
+% Copyright
+\setcopyright{acmcopyright}
+
 \title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
-\author{Takuro Yamamoto}
-\date{\today}
+\numberofauthors{3}
+\author{
+\alignauthor
+Takuro Yamamoto\\
+    \affaddr{Graduate School of Osaka University}
+       % \affaddr{1932 Wallamaloo Lane}\\
+       % \affaddr{Wallamaloo, New Zealand}\\
+       % \email{trovato@corporation.com}
+\alignauthor
+Hiroshi Oyama\\
+    \affaddr{OKUMA Corporation}
+       % \affaddr{P.O. Box 1212}\\
+       % \affaddr{Dublin, Ohio 43017-6221}\\
+       % \email{webmaster@marysville-ohio.com}
+\alignauthor
+Takuya Azumi\\
+    \affaddr{Graduate School of Osaka University}
+       % \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+       % \affaddr{Hekla, Iceland}\\
+       % \email{larst@affiliation.org}
+}
+%\author{Takuro Yamamoto}
+%\date{\today}
 
@@
 This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
+To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
 The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
@@
 \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
-The loader supports the countinuous loading, which saves the Bluetooth set-up time.
+The loader supports the continuous loading, which saves the Bluetooth set-up time.
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
+    \includegraphics[width=8cm,clip]{figure/proposed.eps}
     \caption{System Model}
@@
 Ruby can run a program with fewer code lines than C language.
-Ruby improves the productivity of a software development owing to not only simple grammar also object-oriented functions such as classes and methods, exceptions, and garbage collection.
+Ruby improves the productivity of a software development owing to not only simple grammar but also object-oriented functions such as classes and methods, exceptions, and garbage collection.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
+    \includegraphics[width=8cm,clip]{figure/mruby.eps}
     \caption{Mechanism of mruby/RiteVM}
@@
 
-\subsubsection{Component Model}\mbox{}\\
-
+\subsubsection{Component Model}
 Figure \ref{fig:component} shows a component diagram.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
+    \includegraphics[width=8cm,clip]{figure/component_diagram.eps}
     \caption{Component Diagram}
@@
 
-\subsubsection{System Model}\mbox{}\\
-
+\subsubsection{System Model}
 The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mrubyontecs.pdf}
+    \includegraphics[width=8cm,clip]{figure/mrubyontecs.eps}
     \caption{System Model of existing mruby on TECS}
@@
 
-\subsubsection{mruby-TECS Bridge}\mbox{}\\
-
+\subsubsection{mruby-TECS Bridge}
 There is a great difference between the execution time of mruby and C language.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.pdf}
+    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.eps}
     \caption{mruby-TECS Bridge}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.pdf}
+    \includegraphics[width=8cm,clip]{figure/system_model.eps}
     \caption{Detailed System Model of the proposed framework}
@@
 %     \centering
-%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.pdf}
+%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.eps}
 %     \caption{Development Flow in mruby bytecode loader using Bluetooth}
@@
 
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
-
+\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
 The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
+    \includegraphics[width=8cm,clip]{figure/component_bluetooth.eps}
     \caption{Component Diagram of mruby bytecode loader using Bluetooth}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
+    \includegraphics[width=8cm,clip]{figure/control_flow.eps}
     \caption{Control Flow of mruby bytecode loader using Bluetooth}
@@
 
-\subsubsection{RiteVM Scheduler} \mbox{}\\
-
+\subsubsection{RiteVM Scheduler}
 A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
-    \caption{The design of RiteVM sceduler}
+    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.eps}
+    \caption{The design of RiteVM scheduler}
     \label{fig:rotateReadyQueue}
@@
 
-\subsubsection{Component of RiteVM Scheduler} \mbox{}\\
-
+\subsubsection{Component of RiteVM Scheduler}
 Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
+    \includegraphics[width=8cm,clip]{figure/cyclic_handler.eps}
     \caption{Component Diagram of Cyclic Handler}
@@
 
-\subsubsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
-
+\subsubsection{Synchronization of Multiple RiteVM Tasks}
 In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
+    \includegraphics[width=8cm,clip]{figure/Eventflag.eps}
     \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
@@
 
-In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove these components and also reuse them.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.pdf}
+    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.eps}
     \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_msec.pdf}
+    \includegraphics[width=8cm,clip]{figure/comparison_msec.eps}
     \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
@@
 The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
-%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
+%Thus, the proposed framework can be utilized on the devices without Bluetooth.
 The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
@@
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtranBST2/IEEEtran}
+\bibliographystyle{abbrv}
 \bibliography{ref}

### 2016-03-19 EMSOFT2016/thesis.tex
update

@@
 
+% Copyright
+\setcopyright{acmcopyright}
+
 \title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
-\author{Takuro Yamamoto}
-\date{\today}
+\numberofauthors{3}
+\author{
+\alignauthor
+Takuro Yamamoto\\
+    \affaddr{Graduate School of Engineering Science, Osaka University}
+       % \affaddr{1932 Wallamaloo Lane}\\
+       % \affaddr{Wallamaloo, New Zealand}\\
+       % \email{trovato@corporation.com}
+\alignauthor
+Hiroshi Oyama\\
+    \affaddr{OKUMA Corporation}
+       % \affaddr{P.O. Box 1212}\\
+       % \affaddr{Dublin, Ohio 43017-6221}\\
+       % \email{webmaster@marysville-ohio.com}
+\alignauthor
+Takuya Azumi\\
+    \affaddr{Graduate School of Engineering Science, Osaka University}
+       % \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+       % \affaddr{Hekla, Iceland}\\
+       % \email{larst@affiliation.org}
+}
+%\author{Takuro Yamamoto}
+%\date{\today}
 
@@
 
-%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
+%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
 mruby on TECS has several problems at present.
 One of the problems is low software development efficiency.
-mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
+mruby on TECS only supports a storage/ROM device to load mruby programs. 
+%in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3}.
 For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
@@
 \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
-The loader supports the countinuous loading, which saves the Bluetooth set-up time.
+The loader supports the continuous loading, which saves the Bluetooth set-up time.
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
 \item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
-In addition, synchronization of multiple tasks is also implemented.
+\item {\bf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
 \item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/proposed.pdf}
-    \caption{System Model}
+    \includegraphics[width=8cm,clip]{figure/proposed.eps}
+    \caption{System Model of the proposed framework}
     \label{fig:proposed}
@@
 mruby is the light-weight implementation of Ruby programming language complying to part of the ISO standard.
-
 Ruby is a object-oriented script language \cite{url:Ruby}.
@@
 TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps decrease difficulty because the generated component diagram can visualize the structure of whole software.
-It can also help increase productivity and reduce development duplication because a common part of software is regarded as a component.
+TECS helps increase productivity and reduce development duplication because the reusability of software is improved.
+TECS also helps decrease complexity of the system because the generated component diagram can visualize the structure of whole software.
 
@@
         To make the definition of an interface clear, specifiers such as in and out are used in TECS.
-        [in] and [out] represent input and output, respectively.\\
+        [in] and [out] represent input and output, respectively.
 \begin{figure}[t]
@@
 \end{figure}
-
     \item[{\bf Celltype Description}]\mbox{}\\
@@
         To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
-        In the same way, {\it call} ports can be declared.
-        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.\\
+        In the same way, {\it call} ports can be defined.
+        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.
 \begin{figure}[t]
@@
     attr{
-        int32_t attr = 100;
+        int32_t attribute;
     };
     var{
-        int32_t var;
+        int32_t variable;
     };
@@
 \end{figure}
-
     \item[{\bf Build Description}]\mbox{}\\
@@
         To compose {\it cell}s, a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
-        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.\\
+        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.
 \begin{figure}[t]
@@
 The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
-Thus it is difficult to use mruby for all of code.
+Thus it is difficult to use mruby for all codes.
 
 The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
-On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of code run quickly.
+On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of codes run quickly.
 
@@
 One is a {\it celltype} to receive invocation from the mruby program.
-The other thing is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.
+The other is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.
 
@@
 \label{sec:mruby bytecode loader using Bluetooth}
+\footnote{
+mruby bytecode loader is intended to improve the development efficiency, therefore software developers should use it for development phase.
+Complete software should be compiled and linked in the storage/ROM device beforehand.
+}
 This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
@@
 mruby programs are consisted of mruby application and libraries.
-mruby application is the main code, which developers should program.
+mruby application is the main code which software developers should program.
 mruby libraries are the codes defining the functions for application such as Ruby classes. 
 The mruby bytecodes including mruby application and libraries can be sent and run.
-However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
+However, it is also wasteful in terms of the size and time to send bytecodes because libraries are not frequently modified. 
 The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
 Due to this design, RiteVMs can share the mruby libraries.
-In additon, a RiteVM can use the own library that other RiteVMs should not use.
+In addition, a RiteVM can use the own library that other RiteVMs should not use.
 
@@
 
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\
-
+\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/component_bluetooth.eps}
+    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
+    \label{fig:component_bluetooth}
+\end{figure}
 The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
 The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
-This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.
+The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generation the mruby library bytecode.
+This generated bytecode is prepared beforehand in the storage/ROM device, and different from a bytecode transferred with Bluetooth.
 
-Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and MrubyBluetooth1 {\it cell}s.
+Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
 TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
-The MrubyBluetooth1 is a component of RiteVM with mruby bytecode loader using Bluetooth.
+The RiteVMBluetooth1 is the component of RiteVM with mruby bytecode loader using Bluetooth.
 A bytecode in the host is transferred and received at the top of the component.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_bluetooth.pdf}
-    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
-    \label{fig:component_bluetooth}
+    \includegraphics[width=8cm,clip]{figure/control_flow.eps}
+    \caption{Process Flow of mruby bytecode loader using Bluetooth}
+    \label{fig:control_flow}
 \end{figure}
 
-Figure \ref{fig:control_flow} shows the process of executing mruby program in a component of RiteVM with mruby bytecode loader using Bluetooth such as MrubyBluetooth1.
-The concrete main code of tMrubyBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
-
-First, a pointer of {\it mrb\_state} and {\it mrbc\_context} are initialized.
-{\it mrb\_state} is a set of states and global variables used in mruby.
-
-Second, the RiteVM reads the bytecode of mruby libraries.
-mruby libraries are a set of Ruby classes such as motor class and sensor class.
-For example, motor class defines methods to rotate and stop a motor.
-The tMrubyBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
-The {\it mrubyFile} indicates the program files of mruby libraries.
-{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
-The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
-In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
-
-Third, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth.
-The mruby application bytecode is stored in an array of type uint8\_t such as {\it irepApp}, which is a tMrubyBluetooth variable as shown in \ref{celltype_mrubybluetooth}.
-The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the RiteVM.
-
-Finally, the mruby task runs.
-When the mruby application is modified, only the bytecode of the modified application should be transferred.
-mruby libraries need not be touched because libraries are not normally changed.
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
-    \caption{Control Flow of mruby bytecode loader using Bluetooth}
-    \label{fig:control_flow}
-\end{figure}
 \begin{figure}[t]
@@
 \begin{lstlisting}
-celltype tMrubyBluetooth{
+/* tRiteVMBluetooth.cdl */
+celltype tRiteVMBluetooth{
     entry sTaskBody eMrubyBody;
+    [optional] call sEventflag cEventflag[];
+    [optional] call sSemaphore cSemaphore;
     attr{
-      [omit]char_t *mrubyFile;
-      char_t *irep = C_EXP("&$cell_global$_irep");
-      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
+      [omit]char_t *mrubyLib;
+      char_t *irepLib = 
+                    C_EXP("&$cell_global$_irep");
+      uint32_t irepAppSize = 
+                    C_EXP( BUFFER_SIZE );
+      FLGPTN setptn;
     };
     var{
+        mrb_state *mrb;
+        mrbc_context *context;
         [size_is(irepAppSize)] uint8_t *irepApp;
@@
 \end{figure}
+
+Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with mruby bytecode loader using Bluetooth such as RiteVMBluetooth1.
+The concrete main code of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
+
+First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Figure \ref{maincode_mrubybluetooth}:6-7).
+The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
+This process is exclusively carried out by the semaphore.
+
+Second, pointers of {\it mrb\_state} and {\it mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Figure \ref{maincode_mrubybluetooth}:9-14).
+{\it mrb\_state} is a set of states and global variables used in mruby.
+Synchronization of multiple tasks is performed in this processing phase.
+The RiteVM that ended up here waits for the other RiteVM to finish loading and initialization.
+
+Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Figure \ref{maincode_mrubybluetooth}:17-19).
+mruby libraries are a set of Ruby classes such as motor class and sensor class.
+For example, motor class defines methods to rotate and stop a motor.
+The tRiteVMBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
+The {\it mrubyLib} indicates the program files of mruby libraries.
+{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyLib}, does not consume memory.
+The {\it irepLib} is the pointer of the array stored the bytecode of mruby libraries.
+In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+
+Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Figure \ref{maincode_mrubybluetooth}:20-22).
+The mruby application bytecode is stored in an array of {\it irepApp}.
+The array is different from that of holding the mruby library bytecode.
+Two bytecodes are read separately in the RiteVM.
+
+Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Figure \ref{maincode_mrubybluetooth}:20-22).
+When the mruby application is modified, only the bytecode of the modified application should be transferred.
+mruby libraries need not be touched because libraries are not normally changed.
+
+The process shown in Figure \ref{maincode_mrubybluetooth}:23-28 is carried out when an exception occurs.
+When all mruby applications finish, mrb\_state and mrbc\_context are freed (Figure \ref{maincode_mrubybluetooth}:31-34).
+The proposed framework supports continuous loading, thus this process loops.
+After freeing variables, RiteVM will become the state to wait for the next mruby application bytecode.
 \begin{figure}[t]
@@
 \begin{lstlisting}
+/* tRiteVMBluetooth.c */
 void
@@
 {
-  /* Declaration variables */
-  mrb_state *mrb;
-  mrbc_context *c;
-  /* New interpreter instance */
-  mrb = mrb_open();
-  // Omit: error check for mrb_state
-  /* New mruby context */
-  c = mrbc_context_new( mrb );
-  // Omit: initialization of mruby-TECS bridge
+  /* Omit: start of exclusive process by semaphore */
   /* Receive the bytecode via Bluetooth */
   bluetooth_loader( VAR_irepApp );
-  /* Load mruby library bytecode and run */
-  mrb_load_irep_cxt( mrb, ATTR_irep, c );
+  /* Omit: end of exclusive process by semaphore */
+  /* New interpreter instance */
+  VAR_mrb = mrb_open();
+  /* Omit: error check for mrb_state */
+  /* New mruby context */
+  VAR_context = mrbc_context_new( VAR_mrb );
+  /* Omit: initialization of mruby-TECS bridge */
+  /* Omit: synchronization of
+                starting mruby application */
+  /* Load mruby library bytecode */
+  mrb_load_irep_cxt( VAR_mrb,
+                        ATTR_irepLib, VAR_context );
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
+  mrb_load_irep_cxt( VAR_mrb,
+                        VAR_irepApp, VAR_context );
   if ( mrb->exc ) {
     /* Failure to execute */
-    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
+    mrb_p( VAR_mrb, 
+                mrb_obj_value( VAR_mrb->exc ) );
     exit( 0 );
   }
+  /* Omit: synchronization of
+                finishing mruby application */
   /* Free mruby context */
-  mrbc_context_free( mrb, c );
+  mrbc_context_free( VAR_mrb, VAR_context );
   /* Free interpreter instance */
-  mrb_close( mrb );
+  mrb_close( VAR_mrb );
 }
@@
 \end{figure}
-\subsection{Multitask}
-\label{sec:Multitask}
-This section describes implementation of multitasking in the proposed framework.
+\subsection{RiteVM Scheduler}
+\label{sec:RiteVM Scheduler}
+This section describes implementation of RiteVM scheduler in the proposed framework.
 mruby on TECS has supported multitasking.
@@
 
-\subsubsection{RiteVM Scheduler} \mbox{}\\
-
+\subsubsection{Design of RiteVM Scheduler}
 A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
@@
 
-\subsubsection{Component of RiteVM Scheduler} \mbox{}\\
-
-Figure \ref{fig:cyclic_handler} shows a component diagram of the periodic handler.
-The components of periodic handler consist of two components: CyclicHandler and CyclicMain.
+\subsubsection{Component of RiteVM Scheduler}
+Figure \ref{fig:cyclic_handler} shows the component diagram of RiteVM scheduler.
+The component of RiteVM scheduler consist of CyclicHandler and RiteVMSchedulerMain.
 CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
 Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
-The periodic handler has five arguments: ID, attribute, periodic time, periodic phase and access pattern.
-CyclicHandler {\it cell} has these arguments as attributes of the {\it cell}.
-CyclicMain {\it cell} is a component to perform the processing body of a periodic handler.
+CyclicHandler {\it cell} has attributes of the {\it cell}.
+RiteVMSchedulerMain {\it cell} is a component to perform the processing body of a periodic handler.
 {\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tCyclicMain {\it celltype}, which has a {\it call} port, an {\it entry} port and an attribute.
-The {\it call} port is connected with the {\it entry} port of the Kernel {\it cell} ({\it tkernel.eiKernel}) to call functions of the kernel. 
+Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is the {\it composite cell} consisting of two {\it cell}s.
+The {\it call} port of RiteVMSchedulerMain is connected with the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call functions of the kernel. 
 The attribute is used as an arguments of {\it rotateReadyQueue}.
 
-Figure \ref{build_cyclic_handler} shows a build description that corresponds to the component diagram shown in Figure \ref{fig:cyclic_handler}.
-In the part of CyclicHandler {\it cell}, configurations of a periodic handler is described such as attribute, cyclicTime and cyclicPhase.
-In this case, the periodic handler is executed when it is generated because the attribute is {\it TA\_STA} that represents the periodic handler is in an operational state after the creation.
-The periodic handler is executed every one msec.
-In another part, the priority of CyclicMain {\it cell} is described.
+Figure \ref{build_cyclic_handler} shows the build description of RiteVM scheduler.
+RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
+In this case, RiteVM scheduler is executed when it is generated because the attribute is {\it TA\_STA} that represents the periodic handler is in an operational state after the creation.
+The scheduler executes every one msec.
 RITEVM\_PRIORITY defines the priority of mruby tasks.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/cyclic_handler.pdf}
-    \caption{Component Diagram of Cyclic Handler}
+    \includegraphics[width=8cm,clip]{figure/cyclic_handler.eps}
+    \caption{Component Diagram of RiteVM Scheduler}
     \label{fig:cyclic_handler}
@@
     \begin{lstlisting}
+/* tRiteVMScheduler.cdl */
 celltype tCyclicHandler {
@@
     	[omit] RELTIM cyclicTime;
-    	[omit] RELTIM cyclicPhase = 0;
+    	[omit] RELTIM cyclicPhase;
     };
 };
-celltype tCyclicMain{
+celltype tRiteVMSchedulerMain {
     require tKernel.eiKernel;
@@
 };
+
+composite tRiteVMScheduler {
+    attr {
+        ATR    attribute      = C_EXP("TA_NULL");
+        RELTIM cyclicTime  = 1;
+        RELTIM cyclicPhase = 1;
+        PRI    priority;
+    };
+    cell tRiteVMSchedulerMain RiteVMSchedulerMain {
+        priority = composite.priority;
+    };
+    cell tCyclicHandler CyclicHandler {
+        ciBody      = RiteVMSchedulerMain.eiBody;
+        attribute   = composite.attribute;
+        cyclicTime  = composite.cyclicTime;
+        cyclicPhase = composite.cyclicPhase;
+    };
+};
     \end{lstlisting}
-    \caption{Celltype Description of Cyclic Handler}
+    \caption{Celltype Description of RiteVM Scheduler}
     \label{celltype_cyclic_handler}
@@
     \begin{lstlisting}
-cell tCyclicHandler CyclicHandler{
-    ciBody = CyclicMain.eiBody;
+cell tRiteVMScheduler RiteVMScheduler {
     attribute   = C_EXP("TA_STA");
@@
     cyclicPhase = 1;
-};
-cell tCyclicMain CyclicMain{
     priority    =
@@
 \end{lstlisting}
-    \caption{Build Description of Cyclic Handler}
+    \caption{Build Description of RiteV Scheduler}
     \label{build_cyclic_handler}
@@
 
-\subsubsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\
-
+\subsection{Synchronization of Multiple RiteVM Tasks}
 In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
@@
 
-\subsection{Benefits of Component-Based Development}
-This section describes the design using the benefits of component-based development.
+\subsection{Utilization of Component-Based Development}
+This section describes the design applying component-based development.
 
-In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
+In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
+For example, if RiteVM scheduler is not necessary for software, developers should only comment out the .cdl file such as {\it //import(<tRiteVMScheduler.cdl>);}.
 This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
@@
 %    \item Synchronization of mruby applications
-    \item Code size using the benefit of CBD 
+    \item Code size utilizing component-based development 
 \end{itemize}
@@
 These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
-This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
+This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 
+\subsection{Evaluation: Improving the software development efficiency by mruby bytecode loader}
 The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
@@
     \caption{Comparison of the size and load process time between an mruby application including mruby libraries and not}
+    \scriptsize
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|c|c}
@@
           Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
-          Load Process Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
+          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
           Compilation Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
     \end{tabular}
+    }
     \label{tab:size_and_time}
@@
 
+\subsection{Evaluation: RiteVM Scheduler}
 The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
@@
 
+\subsection{Evaluation: Synchronization of multiple RiteVM tasks}
+
+\subsection{Evaluation: Benefits of component-based development}
 To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
@@
     \caption{Lines of .c and .cdl file for the number of RiteVM}
+    \scriptsize
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||cc|c}
@@
     \end{tabular}
+    }
     \label{tab:codesize}
@@
     \caption{Comparison of the proposed and previous work}
+    \scriptsize
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|ccccccc}
@@
 %because of the low overhead.
+In addition, synchronization of multiple RiteVM tasks is implemented.
 
@@
 
-In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
-Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+In the future, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+
+%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowledgement}
+    We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
 
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtranBST2/IEEEtran}
+\bibliographystyle{abbrv}
 \bibliography{ref}

### 2016-03-22 EMSOFT2016/paper.tex
update

--- 2016-03-19 EMSOFT2016/thesis.tex
@@
 \setcopyright{acmcopyright}
+% DOI
+\doi{10.475/123_4}
+% ISBN
+\isbn{123-4567-24-567/08/06}
+%Conference
+\conferenceinfo{EMSOFT '16}{October 2--7, 2016, Pittsburgh, USA}
+\acmPrice{\$15.00}
 
@@
 Takuro Yamamoto\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}
-       % \affaddr{1932 Wallamaloo Lane}\\
+    \affaddr{Graduate School of Engineering Science, Osaka University}\\
+    \affaddr{Osaka, JAPAN}\\
        % \affaddr{Wallamaloo, New Zealand}\\
@@
 Hiroshi Oyama\\
-    \affaddr{OKUMA Corporation}
-       % \affaddr{P.O. Box 1212}\\
+    \affaddr{OKUMA Corporation}\\
+    \affaddr{Aichi, JAPAN}
        % \affaddr{Dublin, Ohio 43017-6221}\\
@@
 Takuya Azumi\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}
-       % \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+    \affaddr{Graduate School of Engineering Science, Osaka University}\\
+    \affaddr{Osaka, JAPAN}\\
        % \affaddr{Hekla, Iceland}\\
@@
 \end{abstract}
+
+\keywords{embedded software; script language; component system;}
 \section{Introduction}
@@
 
+In addtion, there are component systems for embedded systems.
+AUTOSAR (AUTomotive Open System ARchitecture) \cite{} is a worldwide development partnership of vehicle manufactures.
+
+SaveCCM \cite{par:SAVEapproach} is a component model for embedded control application.
+SaveCCM is a simple model which is flexible to facilitate analysis of real-time and dependability.
+
+Koala \cite{par:Koala} is a component model that helps to manage the growing complexity and diversity of software in consumer electronics products.
+
 \section{Conclusion}

### 2016-03-29 EMSOFT2016/paper.tex
support \myit and \mybf

@@
 
-\keywords{embedded software; script language; component system;}
+\keywords{embedded software; script language; component based development;}
 \section{Introduction}
@@
 
-{\bf Contribution}: The proposed framework gives the contribution in the following points.
+{\mybf Contribution}: The proposed framework gives the contribution in the following points.
 \begin{enumerate}
-\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
+\item {\mybf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
 The loader supports the continuous loading, which saves the Bluetooth set-up time.
 Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
-\item {\bf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
-\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
+\item {\mybf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
+\item {\mybf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
+\item {\mybf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
 \end{enumerate}
 
-{\bf Organization}: The paper is organized as follows.
+{\mybf Organization}: The paper is organized as follows.
 Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
@@
 Figure \ref{fig:component} shows a component diagram.
-A {\it cell} which is an instance of a component in TECS consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
-A {\it entry} port is an interface to provide functions with other {\it cell}s, and a {\it call} port is an interface to use functions of other {\it cell}s.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
-Functions of a {\it cell} are implemented in the C language.
+A {\myit cell} which is an instance of a component in TECS consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
+A {\myit entry} port is an interface to provide functions with other {\myit cell}s, and a {\myit call} port is an interface to use functions of other {\myit cell}s.
+A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
+Functions of a {\myit cell} are implemented in the C language.
 
-A type of a {\it entry}/{\it call} port is defined by a {\it signature} which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it call} port of a {\it cell} can be connected to the {\it entry} port of another {\it cell} with the same {\it signature}.
-A {\it celltype} is the definition of a {\it cell}.
-{\it Celltype} defines one or more {\it call}/{\it entry} ports, attributes and internal variables.
+A type of a {\myit entry}/{\myit call} port is defined by a {\myit signature} which is a set of functions.
+A {\myit signature} is the interface definition of a {\myit cell}.
+The {\myit call} port of a {\myit cell} can be connected to the {\myit entry} port of another {\myit cell} with the same {\myit signature}.
+A {\myit celltype} is the definition of a {\myit cell}.
+{\myit Celltype} defines one or more {\myit call}/{\myit entry} ports, attributes and internal variables.
 
@@
 \subsubsection{Component Description}
-The description of a component in TECS is divided into three parts, {\it signature}, {\it celltype}, and build description.
+The description of a component in TECS is divided into three parts, {\myit signature}, {\myit celltype}, and build description.
 TECS code is written in .cdl (component description language) file.
@@
 \begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
-        The {\it signature} description defines an interface of a {\it cell}.
-        A {\it signature} name is described following the keyword {\it signature}.
+    \item[{\mybf Signature Description}]\mbox{}\\
+        The {\myit signature} description defines an interface of a {\myit cell}.
+        A {\myit signature} name is described following the keyword {\myit signature}.
         It also has the prefix ``s".
-        In this way, a {\it signature} is defined such as sMotor shown in Figure \ref{signature}.
+        In this way, a {\myit signature} is defined such as sMotor shown in Figure \ref{signature}.
         To make the definition of an interface clear, specifiers such as in and out are used in TECS.
@@
 \end{figure}
-    \item[{\bf Celltype Description}]\mbox{}\\
-        The {\it celltype} description defines {\it entry} ports, {\it call} ports, attributes, and valuables of a {\it celltype}.
-        An example of a {\it celltype} description is shown in Figure \ref{celltype}.
-        A {\it celltype} name following the keyword {\it celltype} with the prefix ``t" and elements of a {\it celltype} is described.
-        To define {\it entry} ports, a {\it signature} such as sMotor, and an {\it entry} port name such as eMotor follow the keyword {\it entry}.
-        In the same way, {\it call} ports can be defined.
-        Attributes and valuables follow the keyword {\it attr} and {\it var} respectively.
+    \item[{\mybf Celltype Description}]\mbox{}\\
+        The {\myit celltype} description defines {\myit entry} ports, {\myit call} ports, attributes, and valuables of a {\myit celltype}.
+        An example of a {\myit celltype} description is shown in Figure \ref{celltype}.
+        A {\myit celltype} name following the keyword {\myit celltype} with the prefix ``t" and elements of a {\myit celltype} is described.
+        To define {\myit entry} ports, a {\myit signature} such as sMotor, and an {\myit entry} port name such as eMotor follow the keyword {\myit entry}.
+        In the same way, {\myit call} ports can be defined.
+        Attributes and valuables follow the keyword {\myit attr} and {\myit var} respectively.
 \begin{figure}[t]
@@
 \end{figure}
-    \item[{\bf Build Description}]\mbox{}\\
-        The build description is used to instantiate {\it cell}s and connect {\it cell}s.
+    \item[{\mybf Build Description}]\mbox{}\\
+        The build description is used to instantiate {\myit cell}s and connect {\myit cell}s.
         Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name such as tMotor, and a {\it cell} name such as Motor follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, a {\it signature}, a {\it entry} port in order are described.
-        In this example, a {\it entry} port eMotor in a {\it cell} Motor is connected to a {\it call} port cMotor in a {\it cell} Caller.
+        A {\myit celltype} name such as tMotor, and a {\myit cell} name such as Motor follow the keyword {\myit cell}.
+        To compose {\myit cell}s, a {\myit call} port, a {\myit signature}, a {\myit entry} port in order are described.
+        In this example, a {\myit entry} port eMotor in a {\myit cell} Motor is connected to a {\myit call} port cMotor in a {\myit cell} Caller.
 \begin{figure}[t]
@@
 The mruby-TECS bridge generates two things.
-One is a {\it celltype} to receive invocation from the mruby program.
+One is a {\myit celltype} to receive invocation from the mruby program.
 The other is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.
@@
 The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.
 
@@
 
-Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
-The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2).
+Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\myit cell}s.
+The MrubyTask1 {\myit cell} is a componentized task of the RTOS (TOPPERS/HRP2).
 TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
@@
 
-Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with mruby bytecode loader using Bluetooth such as RiteVMBluetooth1.
-The concrete main code of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
-
-First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Figure \ref{maincode_mrubybluetooth}:6-7).
-The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
-This process is exclusively carried out by the semaphore.
-
-Second, pointers of {\it mrb\_state} and {\it mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Figure \ref{maincode_mrubybluetooth}:9-14).
-{\it mrb\_state} is a set of states and global variables used in mruby.
-Synchronization of multiple tasks is performed in this processing phase.
-The RiteVM that ended up here waits for the other RiteVM to finish loading and initialization.
-
-Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Figure \ref{maincode_mrubybluetooth}:17-19).
-mruby libraries are a set of Ruby classes such as motor class and sensor class.
-For example, motor class defines methods to rotate and stop a motor.
-The tRiteVMBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
-The {\it mrubyLib} indicates the program files of mruby libraries.
-{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyLib}, does not consume memory.
-The {\it irepLib} is the pointer of the array stored the bytecode of mruby libraries.
-In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
-
-Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Figure \ref{maincode_mrubybluetooth}:20-22).
-The mruby application bytecode is stored in an array of {\it irepApp}.
-The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the RiteVM.
-
-Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Figure \ref{maincode_mrubybluetooth}:20-22).
-When the mruby application is modified, only the bytecode of the modified application should be transferred.
-mruby libraries need not be touched because libraries are not normally changed.
-
-The process shown in Figure \ref{maincode_mrubybluetooth}:23-28 is carried out when an exception occurs.
-When all mruby applications finish, mrb\_state and mrbc\_context are freed (Figure \ref{maincode_mrubybluetooth}:31-34).
-The proposed framework supports continuous loading, thus this process loops.
-After freeing variables, RiteVM will become the state to wait for the next mruby application bytecode.
 \begin{figure}[t]
@@
 \end{figure}
+
+Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with mruby bytecode loader using Bluetooth such as RiteVMBluetooth1.
+The concrete main code of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
+
+First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Figure \ref{maincode_mrubybluetooth}:6-7).
+The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
+This process is exclusively carried out by the semaphore.
+
+Second, pointers of {\myit mrb\_state} and {\myit mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Figure \ref{maincode_mrubybluetooth}:9-14).
+{\myit mrb\_state} is a set of states and global variables used in mruby.
+Synchronization of multiple tasks is performed in this processing phase.
+The RiteVM that ended up here waits for the other RiteVM to finish loading and initialization.
+
+Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Figure \ref{maincode_mrubybluetooth}:17-19).
+mruby libraries are a set of Ruby classes such as motor class and sensor class.
+For example, motor class defines methods to rotate and stop a motor.
+The tRiteVMBluetooth {\myit cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
+The {\myit mrubyLib} indicates the program files of mruby libraries.
+{\myit [omit]} is only used for the TECS generator, thus the attribute, {\myit mrubyLib}, does not consume memory.
+The {\myit irepLib} is the pointer of the array stored the bytecode of mruby libraries.
+In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+
+Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Figure \ref{maincode_mrubybluetooth}:20-22).
+The mruby application bytecode is stored in an array of {\myit irepApp}.
+The array is different from that of holding the mruby library bytecode.
+Two bytecodes are read separately in the RiteVM.
+
+Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Figure \ref{maincode_mrubybluetooth}:20-22).
+When the mruby application is modified, only the bytecode of the modified application should be transferred.
+mruby libraries need not be touched because libraries are not normally changed.
+
+The process shown in Figure \ref{maincode_mrubybluetooth}:23-28 is carried out when an exception occurs.
+When all mruby applications finish, mrb\_state and mrbc\_context are freed (Figure \ref{maincode_mrubybluetooth}:31-34).
+The proposed framework supports continuous loading, thus this process loops.
+After freeing variables, RiteVM will become the state to wait for the next mruby application bytecode.
 \subsection{RiteVM Scheduler}
@@
 One of approaches for multitasking is co-routine.
-Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\it resume} and {\it yield}. 
+Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\myit resume} and {\myit yield}. 
 (Ruby co-routine is defined in class Fiber \cite{url:co-routine})
@@
 
-Besides, as another method, {\it delay()}, a service call of $\mu$ITRON, can be used for multitasking.
+Besides, as another method, {\myit delay()}, a service call of $\mu$ITRON, can be used for multitasking.
 This service call delays the execution of the own task for the time of the argument.
-%In the approach of {\it delay} function, developers have to schedule as the same as co-routine.
-{\it delay()} is needed when scheduling fixed-priority tasks.
-However, the programming applied to {\it delay()} is difficult to use in the case of fair scheduling.
+%In the approach of {\myit delay} function, developers have to schedule as the same as co-routine.
+{\myit delay()} is needed when scheduling fixed-priority tasks.
+However, the programming applied to {\myit delay()} is difficult to use in the case of fair scheduling.
 
@@
 \subsubsection{Design of RiteVM Scheduler}
-A RiteVM scheduler is a periodic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
-In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+A RiteVM scheduler is a periodic handler, and calls {\myit rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+In other words, the RiteVM scheduler calls {\myit rotateReadyQueue} cyclically.
 The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
-{\it rotateReadyQueue} is described as follows.
+{\myit rotateReadyQueue} is described as follows.
 
@@
 
-When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
-The argument of {\it rotateReadyQueue} is the priority.
+When {\myit rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
+The argument of {\myit rotateReadyQueue} is the priority.
 
-The {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
+The {\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
 For example, three tasks are in the order: task 1, 2, and 3.
-In this case, the order is rotated, task 2, 3 and, 1, when the {\it rotateReadyQueue} is called.
+In this case, the order is rotated, task 2, 3 and, 1, when the {\myit rotateReadyQueue} is called.
 
@@
 The component of RiteVM scheduler consist of CyclicHandler and RiteVMSchedulerMain.
-CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
+CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
 Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
-CyclicHandler {\it cell} has attributes of the {\it cell}.
-RiteVMSchedulerMain {\it cell} is a component to perform the processing body of a periodic handler.
-{\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is the {\it composite cell} consisting of two {\it cell}s.
-The {\it call} port of RiteVMSchedulerMain is connected with the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call functions of the kernel. 
-The attribute is used as an arguments of {\it rotateReadyQueue}.
+CyclicHandler {\myit cell} has attributes of the {\myit cell}.
+RiteVMSchedulerMain {\myit cell} is a component to perform the processing body of a periodic handler.
+{\myit rotateReadyQueue} is implemented as the body.
+Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\myit celltype}, which is the {\myit composite cell} consisting of two {\myit cell}s.
+The {\myit call} port of RiteVMSchedulerMain is connected with the {\myit entry} port of the Kernel {\myit cell} ({\myit tKernel.eiKernel}) to call functions of the kernel. 
+The attribute is used as an arguments of {\myit rotateReadyQueue}.
 
 Figure \ref{build_cyclic_handler} shows the build description of RiteVM scheduler.
-RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
-In this case, RiteVM scheduler is executed when it is generated because the attribute is {\it TA\_STA} that represents the periodic handler is in an operational state after the creation.
+RiteVMScheduler {\myit cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
+In this case, RiteVM scheduler is executed when it is generated because the attribute is {\myit TA\_STA} that represents the periodic handler is in an operational state after the creation.
 The scheduler executes every one msec.
 RITEVM\_PRIORITY defines the priority of mruby tasks.
-In the main of CyclicMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
+In the main of CyclicMain, {\myit rotateReadyQueue} is implemented and the priority is passed as the argument.
 
@@
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if RiteVM scheduler is not necessary for software, developers should only comment out the .cdl file such as {\it //import(<tRiteVMScheduler.cdl>);}.
+For example, if RiteVM scheduler is not necessary for software, developers should only comment out the .cdl file such as {\myit //import(<tRiteVMScheduler.cdl>);}.
 This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
@@
 The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
-This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
+This design such as {\myit cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
 Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
-In addition, the components of Eventflag are built with {\it [optional]} in TECS.
-{\it [optional]} means that the codes are run only when the call port is connected.
+In addition, the components of Eventflag are built with {\myit [optional]} in TECS.
+{\myit [optional]} means that the codes are run only when the call port is connected.
 The .c file does not be rewritten even if developers do not use Eventflag.
@@
 
-\subsection{Evaluation: Improving the software development efficiency by mruby bytecode loader}
+\subsection{Improving the software development efficiency by mruby bytecode loader}
 The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
@@
 
-\subsection{Evaluation: RiteVM Scheduler}
+\subsection{RiteVM Scheduler}
 The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
@@
 
-\subsection{Evaluation: Synchronization of multiple RiteVM tasks}
+\subsection{Synchronization of multiple RiteVM tasks}
 
-\subsection{Evaluation: Benefits of component-based development}
+\subsection{Benefits of component-based development}
 To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
@@
     \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
@@
 We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
-
+This work was supported by JSPS KAKENHI Grant Number 15H05305.
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-06 EMSOFT2016/diff/0330_paper.tex
update

--- 2016-03-29 EMSOFT2016/paper.tex
@@
 Complex and large scale software systems can be developed efficiently using component-based techniques.
-That is because software componentization provides high-reusability and easy verification.
+That is because software componentization provides high-reusability.
+Verification of component-based systems has been researched \cite{par:Blaming} \cite{par:Verification}.
 It also makes a system flexible in extensions and specification changes.
@@
     \includegraphics[width=8cm,clip]{figure/proposed.eps}
+    \vspace{1mm}
     \caption{System Model of the proposed framework}
+    \vspace{1mm}
     \label{fig:proposed}
@@
 
-mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
+mruby is suitable for embedded systems because of execution with less amount of resources and takes over the usability and readability of Ruby.
 In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
@@
     \includegraphics[width=8cm,clip]{figure/mruby.eps}
+    \vspace{1mm}
     \caption{Mechanism of mruby/RiteVM}
+    \vspace{1mm}
     \label{fig:mruby}
@@
     \includegraphics[width=8cm,clip]{figure/component_diagram.eps}
+    \vspace{1mm}
     \caption{Component Diagram}
+    \vspace{1mm}
     \label{fig:component}
@@
 \end{lstlisting}
+\vspace{1mm}
 \caption{Signature Description}
+\vspace{1mm}
 \label{signature}
@@
     attr{
-        int32_t attribute;
+        int32_t port;
     };
     var{
-        int32_t variable;
+        int32_t currentSpeed = 0;
     };
@@
 \end{lstlisting}
+\vspace{1mm}
 \caption{Celltype Description}
+\vspace{1mm}
 \label{celltype}
@@
 \end{lstlisting}
+\vspace{1mm}
 \caption{Build Description}
+\vspace{1mm}
 \label{build}
@@
     \includegraphics[width=8cm,clip]{figure/mrubyontecs.eps}
+    \vspace{1mm}
 \caption{System Model of existing mruby on TECS}
+    \vspace{1mm}
 \label{fig:mrubyontecs}
@@
     \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.eps}
+    \vspace{1mm}
 \caption{mruby-TECS Bridge}
+    \vspace{1mm}
 \label{fig:mruby_TECS_bridge}
@@
 Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
-Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
-The RiteVM reads the own bytecode and executes it.
+Each mruby application bytecode transferred from the host to the target deviceis received by the loader in the RiteVM.
+The RiteVM reads the transferred bytecode and executes it with libraries.
 The mruby applications run at the same time because of synchronization processing.
-The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
+The RiteVM scheduler switches RiteVM tasks as multiple tasks can run in concurrent.
+This section explains these proposed functionalities.
 
@@
     \includegraphics[width=8cm,clip]{figure/system_model.eps}
+    \vspace{1mm}
 \caption{Detailed System Model of the proposed framework}
+    \vspace{1mm}
 \label{fig:system_model}
@@
 %     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.eps}
+%     \vspace{1mm}
 % \caption{Development Flow in mruby bytecode loader using Bluetooth}
+%     \vspace{1mm}
 % \label{fig:bluetooth_loader}
@@
     \includegraphics[width=8cm,clip]{figure/component_bluetooth.eps}
+    \vspace{1mm}
 \caption{Component Diagram of mruby bytecode loader using Bluetooth}
+    \vspace{1mm}
 \label{fig:component_bluetooth}
@@
     \includegraphics[width=8cm,clip]{figure/control_flow.eps}
+    \vspace{1mm}
 \caption{Process Flow of mruby bytecode loader using Bluetooth}
+    \vspace{1mm}
 \label{fig:control_flow}
@@
 \end{lstlisting}
+\vspace{1mm}
 \caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
+\vspace{1mm}
 \label{celltype_mrubybluetooth}
@@
 \end{lstlisting}
+\vspace{1mm}
 \caption{Main code for RiteVM with mruby bytecode loader using Bluetooth}
+\vspace{1mm}
 \label{maincode_mrubybluetooth}
@@
 
-First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Figure \ref{maincode_mrubybluetooth}:6-7).
+First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
 The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
@@
 
-Second, pointers of {\myit mrb\_state} and {\myit mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Figure \ref{maincode_mrubybluetooth}:9-14).
+Second, pointers of {\myit mrb\_state} and {\myit mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
+{\myit VAR\_mrb} and {\myit VAR\_context} shows the variable of the {\myit cell}.
 {\myit mrb\_state} is a set of states and global variables used in mruby.
@@
 
-Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Figure \ref{maincode_mrubybluetooth}:17-19).
+Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Lines 17-19 in Figure \ref{maincode_mrubybluetooth}).
 mruby libraries are a set of Ruby classes such as motor class and sensor class.
@@
 The tRiteVMBluetooth {\myit cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
+{\myit ATTR} shows the attribute, which is a fixed value and not rewritten unlike {\myit VAR}.
 The {\myit mrubyLib} indicates the program files of mruby libraries.
+{\myit mrubyLib} is the attribute because mruby libraries are not modified in the proposed development process.
 {\myit [omit]} is only used for the TECS generator, thus the attribute, {\myit mrubyLib}, does not consume memory.
@@
 
-Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Figure \ref{maincode_mrubybluetooth}:20-22).
+Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
 The mruby application bytecode is stored in an array of {\myit irepApp}.
@@
 
+The RiteVM scheduler is a fair scheduler and implemented as a TECS component in the proposed framework.
+Therefore, when developers create software in priority-based scheduling, the RiteVM scheduler can be easily removed.
 \subsubsection{Design of RiteVM Scheduler}
@@
     \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.eps}
+    \vspace{1mm}
 \caption{The design of RiteVM scheduler}
+    \vspace{1mm}
 \label{fig:rotateReadyQueue}
@@
     \includegraphics[width=8cm,clip]{figure/cyclic_handler.eps}
+    \vspace{1mm}
 \caption{Component Diagram of RiteVM Scheduler}
+    \vspace{1mm}
 \label{fig:cyclic_handler}
@@
     \end{lstlisting}
+    \vspace{1mm}
 \caption{Celltype Description of RiteVM Scheduler}
+    \vspace{1mm}
 \label{celltype_cyclic_handler}
@@
 \end{lstlisting}
+    \vspace{1mm}
 \caption{Build Description of RiteV Scheduler}
+    \vspace{1mm}
 \label{build_cyclic_handler}
@@
     \includegraphics[width=8cm,clip]{figure/Eventflag.eps}
-    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
+    \vspace{1mm}
+\caption{The design for Eventflag using TECS (only differences)}
+    \vspace{1mm}
 \label{fig:Eventflag}
@@
     \item Size and time for transferred mruby bytecodes
-    \item Execution time with singletasking, co-routine, and multitasking
+    \item Execution time with singletasking, co-routine, and proposed multitasking
     \item Overhead for periodic time
-%    \item Synchronization of mruby applications
+    \item Synchronization of multiple RiteVM tasks
     \item Code size utilizing component-based development 
@@
 \subsection{Improving the software development efficiency by mruby bytecode loader}
+The mruby bytecode loader using Bluetooth can save time to develop software.
+In the proposed framework, developers do not need to rewrite a storage/ROM device because the bytecode should be just transferred.
+For example, when mruby programs are modified, developers must pull out an SD card from the target device, connect the host PC, compile/link the platform, and insert the SD card in the target device, in the experimental environment such as LEGO MINDSTORMS EV3.
+In addtion, it can save the time to restart a target OS.
+\subsubsection{Size and time for transferred mruby bytecodes}
+In the framework, to further improve the software development efficiency, developers transfers only the mruby application bytecode and mruby libraries are incorporated in the platform.
 The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
@@
 %Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
+%In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
 These advantages lead improvement of the software development efficiency.
@@
     \centering
+    \vspace{1mm}
 \caption{Comparison of the size and load process time between an mruby application including mruby libraries and not}
-    \scriptsize
+    \vspace{1mm}
+    %\scriptsize
     {\tabcolsep=0.1cm
@@
           Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
-          Compilation Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
+          Compile Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
     \end{tabular}
@@
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
+\subsubsection{Execution time with singletasking, co-routine, and purposed multitasking}
 In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is one msec.
@@
 Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
-Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
+The scheduler interrupts and switches tasks, which causes this overhead.
+It takes about three $\mu$sec on average to switch tasks once.
 %The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
 %Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-The scheduler interrupts and switches tasks, which causes this overhead.
 
@@
     \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.eps}
+    \vspace{1mm}
 \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
+    \vspace{1mm}
 \label{fig:comparison_s_c_m}
@@
 
+\subsubsection{Overhead for periodic time}
 Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
@@
 %This results also shows the overhead becomes smaller as the periodic time is larger, because the overhead depends on the number of switching tasks.
-%The smaller periodic time is better in multitasking due to concurrent and/or parallel processing.
+The smaller periodic time is better in multitasking due to concurrent and/or parallel processing.
 
@@
     \includegraphics[width=8cm,clip]{figure/comparison_msec.eps}
-    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
+    \vspace{1mm}
+\caption{Comparison of the overhead for each cyclic period of RiteVM scheduler}
+    \vspace{1mm}
 \label{fig:comparison_msec}
@@
 \subsection{Synchronization of multiple RiteVM tasks}
+To execute mulitiple mruby applications, synchronization mechanism of RiteVM tasks is supported in the proposed framework.
+We measured the time from first RiteVM task executing to last RiteVM task executing, and confirm that the time is within (periodic time)$\times$(the number of RiteVM tasks $-$ 1).
+Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
+The periodic time is one msec, and the number of RiteVM is four.
+The time is within three msec as shown in Figure \ref{fig:eval_synchronization}, which shows synchronization of multiple RiteVM tasks is performed.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/eval_synchronization.eps}
+    \vspace{1mm}
+\caption{Synchronization of four RiteVM tasks}
+    \vspace{1mm}
+\label{fig:eval_synchronization}
+\end{figure}
 
 \subsection{Benefits of component-based development}
-To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
+In the proposed framework, RiteVMs, RiteVM scheduler, and Eventflags are implemented as TECS components.
+Developers can easily add or remove the functionalities by modifying the CDL file.
+Moreover, component-based development decreases code sizes and improve productivity and maintainability.
+\subsubsection{Code size utilizing component-based development}
+To indicate the superior of component-based development, the comparison of code lines between two C and CDL files is shown in Table \ref{tab:codesize}.
 (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
-(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
-Moreover, lines of two .cdl files are equal.
+In terms of C, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
+(B)'s C file can be utilized without modification, regardless of the number of RiteVMs.
+Moreover, lines of two CDL files are equal.
 The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
@@
     \centering
-    \caption{Lines of .c and .cdl file for the number of RiteVM}
-    \scriptsize
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||cc|c}
+    \vspace{1mm}
+\caption{Lines of C and CDL file for the number of RiteVM}
+    \vspace{1mm}
+    %\scriptsize
+    {\tabcolsep=0.2cm
+    \begin{tabular}{c||c|c|c}
                 & (A)       & (B)     & Diff  \\ \hline
-        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
-        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
+        C (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
@@
     \centering
+    \vspace{1mm}
 \caption{Comparison of the proposed and previous work}
-    \scriptsize
-    {\tabcolsep=0.1cm
+    \vspace{1mm}
+    %\scriptsize
+    {\tabcolsep=0.05cm
     \begin{tabular}{c||c|ccccccc}
@@
 mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
+RiteVM supports only single thread.
 mruby has supported co-routine, but not supported multitasking for RTOSs.
@@
 
-In addtion, there are component systems for embedded systems.
-AUTOSAR (AUTomotive Open System ARchitecture) \cite{} is a worldwide development partnership of vehicle manufactures.
-
-SaveCCM \cite{par:SAVEapproach} is a component model for embedded control application.
-SaveCCM is a simple model which is flexible to facilitate analysis of real-time and dependability.
-
-Koala \cite{par:Koala} is a component model that helps to manage the growing complexity and diversity of software in consumer electronics products.
+% In addtion, there are component systems for embedded systems.
+% AUTOSAR (AUTomotive Open System ARchitecture) \cite{} is a worldwide development partnership of vehicle manufactures.
+%
+% SaveCCM \cite{par:SAVEapproach} is a component model for embedded control application.
+% SaveCCM is a simple model which is flexible to facilitate analysis of real-time and dependability.
+%
+% Koala \cite{par:Koala} is a component model that helps to manage the growing complexity and diversity of software in consumer electronics products.
 
@@
 \label{sec:Conclusion}
-This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
+This paper has presented an extended framework of mruby on TECS:
+mruby bytecode loader using Bluetooth and RiteVM scheduler.
 The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
@@
 Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
-Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily removed.
+Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily added and removed.
+When software in priority-based scheduling is developed, developers only have to remove the RiteVM scheduler.
 Component-based development can increase productivity.
 
-In the future, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+Our prototype system and application programs used in the performance evaluation are all open-source, and may be downloaded from our website \cite{url:download}.
+
+In the future, the CDL files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+Moreover, we will support mruby libraries to mrbgems, which is a distribution packaging system for mruby.
 
@@
 \section{Acknowledgement}
+This work was supported by JSPS KAKENHI Grant Number 15H05305.
 We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
-This work was supported by JSPS KAKENHI Grant Number 15H05305.
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-04-06 EMSOFT2016/diff/0406_paper.tex
update

--- 2016-04-06 EMSOFT2016/diff/0330_paper.tex
@@
 
-\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
 \numberofauthors{3}
@@
     \affaddr{OKUMA Corporation}\\
-    \affaddr{Aichi, JAPAN}
+    \affaddr{Aichi, JAPAN}\\
        % \affaddr{Dublin, Ohio 43017-6221}\\
@@
 \begin{abstract}
-In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
+In recent years, the productivity of embedded systems has a problem due to their complexity and large-scale.
 For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
@@
 Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
-To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
+To improve the development efficiency, this paper proposes a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
 The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
-mruby application bytecode modified frequently is sent from a host to a target device by developers.
+mruby application bytecode is modified frequently and sent from a host to a target device by developers.
 mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
@@
 
-\keywords{embedded software; script language; component based development;}
+\keywords{embedded software; script language; component-based development;}
 \section{Introduction}
@@
 Verification of component-based systems has been researched \cite{par:Blaming} \cite{par:Verification}.
-It also makes a system flexible in extensions and specification changes.
+It also visualize the entire system due to component diagrams, and makes a system flexible in extensions and specification changes.
 There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems
@@
 In addition, another approach of efficient software development is to develop with script languages.
-Most of current software are programmed in C language, and the development with C takes a high cost and more time to develop.
+Most of current software are programmed in C language.
+Development with C language makes the code size increase, and takes a high cost and more time to develop.
 Script languages make software engineering more efficient and shorten a development period because script languages have high-productivity from their usability.
-Java script, Perl, Python, Lua and Ruby are well-known as representative script languages.
+Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.
 
-Although script languages are easy to use and read, their execution time are slower than C language's.
-For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
+Although script languages are easy to use and read, their execution time are larger than C language's.
+For embedded systems, the real-time properties such as estimation of worst-case execution time are very important factors.
 Therefore, it is difficult to apply the script languages to embedded systems.
 
-mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
+To improve the above probles, mruby on TECS has been proposed, which is a component-based framework for running script program \cite{par:mrubyonTECS}.
 It is integrated two technologies.
@@
 
-%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
+%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
 mruby on TECS has several problems at present.
@@
 For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
-Developers should also restart an OS on a target device.
+Developers should also restart an RTOS on a target device.
 %Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
@@
 Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
-These problem are a big burden on developers.
+These problems makes the burden heavy for developers.
 
-This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
-The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
+This paper proposes an extended framework of mruby on TECS: a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
+To improve the development efficiency, the proposed framework enables developers to implement the platform in a storage device only once at the beginning and to transfer mruby application programs from a host to a target device using the Bluetooth Loader.
+A RiteVM is a virtual machine for mruby.
+The RiteVM scheduler manages the execution of multiple RiteVMs, and enables developers to program multitasking more easily than mruby on TECS.
 %Specifically, a periodic handler of switching tasks is implemented.
@@
 \begin{enumerate}
-\item {\mybf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
+\item {\mybf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an RTOS.
 The loader supports the continuous loading, which saves the Bluetooth set-up time.
-Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\mybf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
+Therefore, the Bluetooth loader for mruby bytecode helps developers develop software.
+\item {\mybf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can implement multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
 \item {\mybf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
@@
 Each bytecode is allocated to a RiteVM, respectively.
-Developers can run bytecodes transferred with Bluetooth in multitask.
+Bytecodes transferred with Bluetooth from the host can run in multitask.
 
@@
 The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
-The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
+The bytecodes can run on a RiteVM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
 \begin{figure}[t]
@@
 \label{sec:TECS}
-TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
+TECS is a component system suitable for embedded systems.
 TECS helps increase productivity and reduce development duplication because the reusability of software is improved.
-TECS also helps decrease complexity of the system because the generated component diagram can visualize the structure of whole software.
+TECS also helps developers understand the system because the generated component diagram can visualize the structure of whole software.
 
 The component deployment and composition in TECS are statically performed, which gives optimization.
-As a result, the overhead of execution time and memory consumption can be reduced.
+As a result, the overhead of connection of components and the memory consumption can be reduced.
 There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.
@@
 The description of a component in TECS is divided into three parts, {\myit signature}, {\myit celltype}, and build description.
-TECS code is written in .cdl (component description language) file.
+TECS code is written in CDL (component description language) file.
 The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.
@@
 \begin{lstlisting}
-signature sMotor{
+signature sMotor {
     int32_t getCounts( void );
@@
     \item[{\mybf Celltype Description}]\mbox{}\\
-        The {\myit celltype} description defines {\myit entry} ports, {\myit call} ports, attributes, and valuables of a {\myit celltype}.
+        The {\myit celltype} description defines {\myit entry} ports, {\myit call} ports, attributes, and variable of a {\myit celltype}.
         An example of a {\myit celltype} description is shown in Figure \ref{celltype}.
@@
         In the same way, {\myit call} ports can be defined.
-        Attributes and valuables follow the keyword {\myit attr} and {\myit var} respectively.
+        Attributes and variables follow the keyword {\myit attr} and {\myit var} respectively.
 \begin{figure}[t]
@@
 \begin{lstlisting}
-celltype tCaller{
+celltype tCaller {
     call sMotor cMotor;
 };
-celltype tMotor{
+celltype tMotor {
     entry sMotor eMotor;
-    attr{
+    attr {
         int32_t port;
     };
-    var{
+    var {
         int32_t currentSpeed = 0;
@@
         In this example, a {\myit entry} port eMotor in a {\myit cell} Motor is connected to a {\myit call} port cMotor in a {\myit cell} Caller.
+        The {\myit C\_EXP} is the keyword to use macros defined in C files.
+
 \begin{figure}[t]
@@
 \begin{lstlisting}
-cell tMotor Motor{
+cell tMotor Motor {
+    port = C_EXP("PORT_A");
 };
-cell tCaller Caller{
+cell tCaller Caller {
     cMotor = Motor.eMotor;
@@
 The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
-On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of codes run quickly.
+On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of codes run quickly.
 
@@
 Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
-Each mruby application bytecode transferred from the host to the target deviceis received by the loader in the RiteVM.
+Each mruby application bytecode transferred from the host to the target devices received by the loader in the RiteVM.
 The RiteVM reads the transferred bytecode and executes it with libraries.
@@
 
-\subsection{mruby Bytecode Loader Using Bluetooth}
-\label{sec:mruby bytecode loader using Bluetooth}
+\subsection{Bluetooth Loader for mruby Bytecode}
+\label{sec:Bluetooth loader for mruby bytecode}
+This section describes an additional functionality of mruby on TECS, Bluetooth loader for mruby bytecode.
 \footnote{
-mruby bytecode loader is intended to improve the development efficiency, therefore software developers should use it for development phase.
+Bluetooth loader is intended to improve the development efficiency, therefore software developers should use it for development phase.
 Complete software should be compiled and linked in the storage/ROM device beforehand.
 }
-This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
 In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
 Developers must rewrite the storage/ROM device every time the application programs are modified.
-The OS on the target device should be also restarted.
+The RTOS on the target device should be also restarted.
 It causes a low development efficiency to repeat that.
-An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
+A Bluetooth loader for mruby bytecode makes the developers' burden decrease.
 %The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to connect the storage/ROM device and start the OS.
+Developers should just once carry out the work to connect the storage/ROM device and start the RTOS.
 
@@
 
-%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
+%The development flow in a Bluetooth loader for mruby bytecode is shown in Figure \ref{fig:bluetooth_loader}.
 In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
@@
 %     \vspace{1mm}
-% \caption{Development Flow in mruby bytecode loader using Bluetooth}
+% \caption{Development Flow in Bluetooth loader for mruby bytecode}
 %     \vspace{1mm}
@@
 
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
+\subsubsection{Component of RiteVM with Bluetooth loader for mruby bytecode}
 \begin{figure}[t]
@@
     \vspace{1mm}
-\caption{Component Diagram of mruby bytecode loader using Bluetooth}
+\caption{Component Diagram of Bluetooth loader for mruby bytecode}
     \vspace{1mm}
@@
 \end{figure}
-The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
+The proposed framework provides a RiteVM with Bluetooth loader for mruby bytecode as TECS component.
 The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generation the mruby library bytecode.
+The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generating the mruby library bytecode.
 This generated bytecode is prepared beforehand in the storage/ROM device, and different from a bytecode transferred with Bluetooth.
@@
 TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
-The RiteVMBluetooth1 is the component of RiteVM with mruby bytecode loader using Bluetooth.
+The RiteVMBluetooth1 is the component of RiteVM with Bluetooth loader for mruby bytecode.
 A bytecode in the host is transferred and received at the top of the component.
@@
     \vspace{1mm}
-\caption{Process Flow of mruby bytecode loader using Bluetooth}
+\caption{Process Flow of Bluetooth loader for mruby bytecode}
     \vspace{1mm}
@@
 /* tRiteVMBluetooth.cdl */
-celltype tRiteVMBluetooth{
+celltype tRiteVMBluetooth1 {
     entry sTaskBody eMrubyBody;
@@
     [optional] call sSemaphore cSemaphore;
-    attr{
+    attr {
       [omit]char_t *mrubyLib;
@@
     };
-    var{
+    var {
         mrb_state *mrb;
@@
 \vspace{1mm}
-\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
+\caption{Celltype Description for RiteVM with Bluetooth loader for mruby bytecode}
 \vspace{1mm}
@@
 \vspace{1mm}
-\caption{Main code for RiteVM with mruby bytecode loader using Bluetooth}
+\caption{Main code for RiteVM with Bluetooth loader for mruby bytecode}
 \vspace{1mm}
@@
 
-Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with mruby bytecode loader using Bluetooth such as RiteVMBluetooth1.
+Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with Bluetooth loader for mruby bytecode such as RiteVMBluetooth1.
 The concrete main code of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
 
-First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
+First, the Bluetooth loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
 The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
@@
 
-Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Figure \ref{maincode_mrubybluetooth}:20-22).
+Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
 When the mruby application is modified, only the bytecode of the modified application should be transferred.
@@
 Therefore, when developers create software in priority-based scheduling, the RiteVM scheduler can be easily removed.
+
 \subsubsection{Design of RiteVM Scheduler}
-A RiteVM scheduler is a periodic handler, and calls {\myit rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+A RiteVM scheduler is a periodic handler and {\myit rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority, is implemented as the main process of the handler.
 In other words, the RiteVM scheduler calls {\myit rotateReadyQueue} cyclically.
@@
 
-The {\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
-For example, three tasks are in the order: task 1, 2, and 3.
-In this case, the order is rotated, task 2, 3 and, 1, when the {\myit rotateReadyQueue} is called.
+{\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
+For example, three tasks are in the order: task1, task2, and, task3.
+In this case, the order is rotated, task2, task3, and, task1, when the {\myit rotateReadyQueue} is called.
 
@@
 CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
-Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
+%Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
+\cite{par:microITRON} describes cyclic handlers based on $\mu$ITRON in detail.
 CyclicHandler {\myit cell} has attributes of the {\myit cell}.
@@
     \vspace{1mm}
-\caption{Build Description of RiteV Scheduler}
+\caption{Build Description of RiteVM Scheduler}
     \vspace{1mm}
@@
 This section describes the design applying component-based development.
-
-In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
+In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
 Therefore, developers can easily add or remove these components and also reuse them.
-For example, if RiteVM scheduler is not necessary for software, developers should only comment out the .cdl file such as {\myit //import(<tRiteVMScheduler.cdl>);}.
+For example, if RiteVM scheduler is not necessary for software, developers should only comment out the CDL file such as {\myit //import(<tRiteVMScheduler.cdl>);}.
 This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
@@
 The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
-This design such as {\myit cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
-Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
+This design such as {\myit cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical C file.
+Developers do not need to modify the C file because the CDL files are prepared in accordance with the number of RiteVMs.
 In addition, the components of Eventflag are built with {\myit [optional]} in TECS.
 {\myit [optional]} means that the codes are run only when the call port is connected.
-The .c file does not be rewritten even if developers do not use Eventflag.
+The C file does not be rewritten even if developers do not use Eventflag.
 
@@
 %    \item Execution time of the platform
-    \item Size and time for transferred mruby bytecodes
+    \item Size and time of transferred mruby bytecodes by Bluetooth loader
     \item Execution time with singletasking, co-routine, and proposed multitasking
@@
 
-These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
+These evaluations are performed in order to indicate that a Bluetooth loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
 This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 
-\subsection{Improving the software development efficiency by mruby bytecode loader}
-The mruby bytecode loader using Bluetooth can save time to develop software.
+\subsection{Improving the software development efficiency by Bluetooth loader}
+The Bluetooth loader for mruby bytecode can save development time.
 In the proposed framework, developers do not need to rewrite a storage/ROM device because the bytecode should be just transferred.
 For example, when mruby programs are modified, developers must pull out an SD card from the target device, connect the host PC, compile/link the platform, and insert the SD card in the target device, in the experimental environment such as LEGO MINDSTORMS EV3.
-In addtion, it can save the time to restart a target OS.
-\subsubsection{Size and time for transferred mruby bytecodes}
+In addtion, it can save the time to restart a target RTOS.
+
+%\subsubsection{Size and time for transferred mruby bytecodes}
 In the framework, to further improve the software development efficiency, developers transfers only the mruby application bytecode and mruby libraries are incorporated in the platform.
@@
 In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
+
 \subsubsection{Execution time with singletasking, co-routine, and purposed multitasking}
@@
 We measured the time from first RiteVM task executing to last RiteVM task executing, and confirm that the time is within (periodic time)$\times$(the number of RiteVM tasks $-$ 1).
+%The cases that the number of RiteVM tasks is two, three, and four 
 Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
@@
     \vspace{1mm}
-\caption{Synchronization of four RiteVM tasks}
+\caption{Synchronization of multiple RiteVM tasks}
     \vspace{1mm}
@@
 Moreover, component-based development decreases code sizes and improve productivity and maintainability.
-\subsubsection{Code size utilizing component-based development}
+
+%\subsubsection{Code size utilizing component-based development}
 To indicate the superior of component-based development, the comparison of code lines between two C and CDL files is shown in Table \ref{tab:codesize}.
 (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-In terms of C, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
+In terms of C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVM increases.
 (B)'s C file can be utilized without modification, regardless of the number of RiteVMs.
-Moreover, lines of two CDL files are equal.
+Moreover, code lines of two CDL files are equal.
 The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
@@
     \vspace{1mm}
-\caption{Lines of C and CDL file for the number of RiteVM}
+\caption{Code Lines of C and CDL file for the number of RiteVM}
     \vspace{1mm}
@@
 \caption{Comparison of the proposed and previous work}
-    \vspace{1mm}
+    \vspace{2mm}
     %\scriptsize
@@
         eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
         mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
@@
 The open-source run-time systems for scripting languages have been proposed such as follow:
-python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
-python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
+{\mybf python-on-a-chip:} python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
 The VM runs a significant subset of Python language with few resources on a micro-controller.
@@
 
-The Owl system is an embedded Python run-time system.
+{\mybf Owl system:} The Owl system is an embedded Python run-time system.
 The Owl is a complete system for ARM Cortex-M3 micro-controllers.
@@
 
-eLua offers the full implementation of Lua programming language to the embedded systems.
+{\mybf eLua:} eLua offers the full implementation of Lua programming language to the embedded systems.
 Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
@@
 
-mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
+{\mybf Squirrel:} Squirrel is an object-oriented programming language, designed to be a lightweight scripting language that fits in real-time requirements of applications.
+Squirrel is inspired by especially Lua.
+The API is very similar to Lua and the table code is based on the Lua one.
+Squirrel also supports co-routine as well as Lua.
+
+{\mybf mruby:} mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
 mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
@@
 
-mruby on TECS is a component-based framework for running mruby programs.
+{\mybf mruby on TECS:} mruby on TECS is a component-based framework for running mruby programs.
 The programs on mruby on TECS can execute about 100 times faster than the mruby programs.
@@
 
-Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-The proposed framework supports the loader, the VM scheduler, and synchronization of application.
+Table \ref{tab:comparison} shows a comparison of the proposed framework and previous work.
+Note that the proposed framework has demonstrated all features shown in Table \ref{tab:comparison}.
+In particular, the proposed framework supports the loader, the VM scheduler, and synchronization of application.
 
@@
 This paper has presented an extended framework of mruby on TECS:
-mruby bytecode loader using Bluetooth and RiteVM scheduler.
-The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
+Bluetooth loader for mruby bytecode and RiteVM scheduler.
+The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an RTOS.
 The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
@@
 Component-based development can increase productivity.
-
 Our prototype system and application programs used in the performance evaluation are all open-source, and may be downloaded from our website \cite{url:download}.

### 2016-04-08 EMSOFT2016/diff/0407_thesis.tex
update

--- 2016-04-06 EMSOFT2016/diff/0406_paper.tex
@@
 We measured the time from first RiteVM task executing to last RiteVM task executing, and confirm that the time is within (periodic time)$\times$(the number of RiteVM tasks $-$ 1).
-%The cases that the number of RiteVM tasks is two, three, and four 
-Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
-The periodic time is one msec, and the number of RiteVM is four.
-The time is within three msec as shown in Figure \ref{fig:eval_synchronization}, which shows synchronization of multiple RiteVM tasks is performed.
+Figure \ref{fig:eval_synchronization} shows the cases where the number of RiteVM tasks is two, three, and four.
+% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
+% The periodic time is one msec, and the number of RiteVM is four.
+The periodic time is one msec.
+The time is within one msec, two msec, and three msec respectively as shown in Figure \ref{fig:eval_synchronization}, which shows synchronization of multiple RiteVM tasks is performed.
 

### 2016-04-08 EMSOFT2016/paper.tex
update

@@
 \begin{abstract}
-In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
-For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
-In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
-To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
-The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
-mruby application bytecode modified frequently is sent from a host to a target device by developers.
-mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
-In addition, multiple mruby programs cooperatively run in the proposed framework.
-A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
-Synchronization of starting multiple tasks is also implemented with Eventflag. 
+Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
+To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
+In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
+Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
+To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
+The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
+The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
+In addition, multiple mruby programs can run cooperatively in the proposed framework.
+Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
+Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
 Experimental results demonstrate the advantages of the proposed framework.
@@
 
-\keywords{embedded software; script language; component based development;}
+\keywords{embedded software; scripting language; component-based development}
 \section{Introduction}
-In these days, embedded systems have been required the high-quality and the high-performance.
-Due to this trend, the complexity of embedded systems also increases and the scale is larger.
-For example, IoT (Internet of Things) applications.
-The low production cost and the short developing period of time are also needed.
+Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
+This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
 
-An approach of efficient software development is to use component-based techniques.
-CBD (Component-Based Development) is a design technique for constituting reusable components \cite{par:Crnkovic}.
-Complex and large scale software systems can be developed efficiently using component-based techniques.
-That is because software componentization provides high-reusability and easy verification.
-It also makes a system flexible in extensions and specification changes.
-There are TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} as a typical component-based development for embedded systems
+Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
+Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
+% Complex and large scale software systems can be developed efficiently using component-based techniques.
+% That is because software componentization provides high-reusability.
+Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
+Individual component diagrams enable the visualization of an entire system.
+%It also visualize the entire system due to component diagrams, and makes a system flexible in extensions and specification changes.
+In addition, component-based systems are flexible with regard to extensibility and specification changes.
+The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
 
-In addition, another approach of efficient software development is to develop with script languages.
-Most of current software are programmed in C language, and the development with C takes a high cost and more time to develop.
-Script languages make software engineering more efficient and shorten a development period because script languages have high-productivity from their usability.
-Java script, Perl, Python, Lua and Ruby are well-known as representative script languages.
+In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
+Currently, most software are programmed in C language.
+However, development in C language results in large code size, incurs high costs, and requires significant development time.
+In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts. 
+% script languages have high-productivity from their usability.
+% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.
 
-Although script languages are easy to use and read, their execution time are slower than C language's.
-For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
-Therefore, it is difficult to apply the script languages to embedded systems.
+For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
+Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
+Therefore, applying scripting languages to embedded systems is difficult.
 
-mruby on TECS is a component-based framework for running script program \cite{par:mrubyonTECS}.
-It is integrated two technologies.
-One is mruby, which is a script language for embedded systems \cite{par:mruby}, \cite{url:mruby}.
-The other is TECS (TOPPERS Embedded Component System), which is a component-based framework for embedded systems \cite{par:TECS} \cite{url:TOPPERS}.
-mruby on TECS supports to effectively run mruby script language on embedded systems.
-mruby on TECS also makes execution time 100 times faster than that of mruby.
+To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
+This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
+% mruby on TECS supports to effectively run mruby script language on embedded systems.
+% mruby on TECS also makes execution time 100 times faster than that of mruby.
 
-%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
-mruby on TECS has several problems at present.
-One of the problems is low software development efficiency.
-mruby on TECS only supports a storage/ROM device to load mruby programs. 
-%in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3}.
-For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
-Developers should also restart an OS on a target device.
-%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
-%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
-Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
-These problem are a big burden on developers.
+%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
+Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
+Moreover, mruby on TECS only supports a storage/ROM device for loading mruby programs.
+Consequently, if mruby programs are modified, a secure digital (SD) card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart real-time operating systems (RTOSs) on the target device.
+In addition, although mruby on TECS can support multiple virtual machines (multi-VMs), executing multiple tasks requires the developers to call the OS function.
 
-This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
-To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
-The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
-%Specifically, a periodic handler of switching tasks is implemented.
-%This paper evaluates the proposed framework in term of data transfer rate, overhead of periodic handler and execution time.
+This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
+To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
+Note that RiteVM is the Ruby VM specifically designed for embedded systems.
+The RiteVM scheduler manages the execution of multiple RiteVMs and allows developers to program multitasking more easily than the current version of mruby on TECS.
 
-{\mybf Contribution}: The proposed framework gives the contribution in the following points.
+{\mybf Contributions}: The proposed framework provides the following contributions:
 \begin{enumerate}
-\item {\mybf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
-The loader supports the continuous loading, which saves the Bluetooth set-up time.
-Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-\item {\mybf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
-\item {\mybf To synchronize the execution of multiple RiteVM tasks:} The proposed framework provides the synchronization of multiple RiteVM tasks (mruby applications).
-\item {\mybf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
+\item {\mybf Improved software development efficiency.}
+Developers do not need to rewrite a storage/ROM device and restart an RTOS.
+The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
+\item {\mybf Execution of multiple mruby programs concurrently or in parallel.}
+Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
+\item {\mybf Synchronized execution of multiple RiteVM tasks.}
+The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
+\item {\mybf Benefits of CBD:}
+The paper focuses on the benefits of CBD and provides specific examples.
 \end{enumerate}
 
-{\mybf Organization}: The paper is organized as follows.
-Section \ref{sec:Background} introduces the basic technologies i.e. mruby, TECS and mruby on TECS.
-Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework in detail.
-Section \ref{sec:Evaluation} evaluates the proposed framework, Section \ref{sec:Related work} discusses related work, and then Section \ref{sec:Conclusion} concludes this paper.
+{\mybf Organization}: The reminder of this paper is organized as follows.
+Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
+Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
+Section \ref{sec:Evaluation} evaluates the proposed framework.
+Related work is discussed in Section \ref{sec:Related work}.
+Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
+    \vspace{0.5mm}
+    \caption{System model of the proposed framework}
+    \vspace{1mm}
+    \label{fig:proposed}
+\end{figure}
 
@@
 Figure \ref{fig:proposed} shows the system model of the proposed framework.
-The bytecodes are transferred from the host to the target device with Bluetooth.
-The RiteVMs and mruby library are assumed to be prepared in advance.
-Each bytecode is allocated to a RiteVM, respectively.
-Developers can run bytecodes transferred with Bluetooth in multitask.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/proposed.eps}
-    \caption{System Model of the proposed framework}
-    \label{fig:proposed}
-\end{figure}
-
-This section describes mruby on TECS on which the proposed framework is based.
-mruby on TECS is a component-based framework for running script programs.
-In mruby on TECS, two technologies are integrated: mruby and TECS.
-To explain the system, mruby and TECS are also respectively described in this section.
+Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
+Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
+Bytecodes transferred from the host via Bluetooth can run in multitask.
 
@@
 \label{sec:mruby}
-mruby is the light-weight implementation of Ruby programming language complying to part of the ISO standard.
-Ruby is a object-oriented script language \cite{url:Ruby}.
-As the main feature, Ruby is easy-to-use and easy-to-read due to its simple grammar.
-Ruby can run a program with fewer code lines than C language.
-Ruby improves the productivity of a software development owing to not only simple grammar but also object-oriented functions such as classes and methods, exceptions, and garbage collection.
+mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
+It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
 
-mruby is suitable for embedded systems because of faster execution with less amount of resources and takes over the usability and readability of Ruby.
-In addition, VM (Virtual Machine) mechanism is used in mruby, therefore mruby programs can run on any operating system as long as VM is implemented.
-A RiteVM is a VM in mruby, that runs mruby programs.
-The RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which is an intermediate code that can be interpreted by a RiteVM.
-The bytecodes can run on a Rite VM, and thus mruby programs can be executed on any target devices if only RiteVMs are implemented.
+mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
 \begin{figure}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby.eps}
-    \caption{Mechanism of mruby/RiteVM}
+    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
+    \vspace{0.5mm}
+    \caption{mruby/RiteVM mechanism}
+    \vspace{1mm}
     \label{fig:mruby}
@@
 \label{sec:TECS}
-TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
-TECS helps increase productivity and reduce development duplication because the reusability of software is improved.
-TECS also helps decrease complexity of the system because the generated component diagram can visualize the structure of whole software.
+TECS is a component system suitable for embedded systems.
+TECS can increase productivity and reduce development costs due to improved reusability of software components.
+TECS also provides component diagrams, which help developers visualize the overall structure of a system.
 
-The component deployment and composition in TECS are statically performed, which gives optimization.
-As a result, the overhead of execution time and memory consumption can be reduced.
-There are other features of TECS, implementation in C language, source level portability, fine-grained component, etc.
+In TECS, component deployment and composition are performed statically.
+Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
+    % \vspace{0.5mm}
+    \caption{Component Diagram}
+    \vspace{1mm}
+    \label{fig:component}
+\end{figure}
 
@@
 Figure \ref{fig:component} shows a component diagram.
-A {\myit cell} which is an instance of a component in TECS consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
-A {\myit entry} port is an interface to provide functions with other {\myit cell}s, and a {\myit call} port is an interface to use functions of other {\myit cell}s.
+A {\myit cell}, which is an instance of a component in TECS, consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
+An {\myit entry} port is an interface that provides functions to other {\myit cell}s, and a {\myit call} port is an interface that enables the use of other {\myit cell}'s functions.
 A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
-Functions of a {\myit cell} are implemented in the C language.
+{\myit Cell} functions are implemented in C.
 
-A type of a {\myit entry}/{\myit call} port is defined by a {\myit signature} which is a set of functions.
+The type of {\myit entry}/{\myit call} port is defined by a {\myit signature}, which is a set of functions.
 A {\myit signature} is the interface definition of a {\myit cell}.
-The {\myit call} port of a {\myit cell} can be connected to the {\myit entry} port of another {\myit cell} with the same {\myit signature}.
-A {\myit celltype} is the definition of a {\myit cell}.
-{\myit Celltype} defines one or more {\myit call}/{\myit entry} ports, attributes and internal variables.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/component_diagram.eps}
-    \caption{Component Diagram}
-    \label{fig:component}
-\end{figure}
+The {\myit cell}'s  {\myit call} port can be connected to the {\myit entry} port of another {\myit cell} by the same {\myit signature}.
+Here, {\myit celltype} defines one or more {\myit call}/{\myit entry} ports, attributes, and internal variables of a {\myit cell}.
 
 \subsubsection{Component Description}
-The description of a component in TECS is divided into three parts, {\myit signature}, {\myit celltype}, and build description.
-TECS code is written in .cdl (component description language) file.
-The component description is mentioned with an example shown in Figure \ref{fig:component} as follow.
+In TECS, components are described by {\myit signature}, {\myit celltype}, and build written in component description language (CDL).
+% TECS code is written in CDL (component description language) file.
+These components are described as follows.
 
@@
     \item[{\mybf Signature Description}]\mbox{}\\
-        The {\myit signature} description defines an interface of a {\myit cell}.
-        A {\myit signature} name is described following the keyword {\myit signature}.
-        It also has the prefix ``s".
-        In this way, a {\myit signature} is defined such as sMotor shown in Figure \ref{signature}.
-        To make the definition of an interface clear, specifiers such as in and out are used in TECS.
-        [in] and [out] represent input and output, respectively.
+        The {\myit signature} defines a {\myit cell} interface.
+        The {\myit signature} name follows the keyword {\myit signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
 \begin{figure}[t]
@@
     \item[{\mybf Celltype Description}]\mbox{}\\
-        The {\myit celltype} description defines {\myit entry} ports, {\myit call} ports, attributes, and valuables of a {\myit celltype}.
-        An example of a {\myit celltype} description is shown in Figure \ref{celltype}.
-        A {\myit celltype} name following the keyword {\myit celltype} with the prefix ``t" and elements of a {\myit celltype} is described.
-        To define {\myit entry} ports, a {\myit signature} such as sMotor, and an {\myit entry} port name such as eMotor follow the keyword {\myit entry}.
-        In the same way, {\myit call} ports can be defined.
-        Attributes and valuables follow the keyword {\myit attr} and {\myit var} respectively.
+        The {\myit celltype} defines {\myit entry} ports, {\myit call} ports, attributes, and variables.
+        A {\myit celltype} name with the prefix ``t'' follows the keyword {\myit celltype}, e.g., tCaller (Figure \ref{celltype}).
+        To define {\myit entry} ports, a {\myit signature}, e.g., sMotor, and an {\myit entry} port name, e.g., eMotor, follow the keyword {\myit entry}.
+        {\myit Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\myit attr} and {\myit var}, respectively.
 \begin{figure}[t]
@@
 \begin{lstlisting}
-celltype tCaller{
+celltype tCaller {
     call sMotor cMotor;
 };
-celltype tMotor{
+celltype tMotor {
     entry sMotor eMotor;
-    attr{
-        int32_t attribute;
+    attr {
+        int32_t port;
     };
-    var{
-        int32_t variable;
+    var {
+        int32_t currentSpeed = 0;
     };
@@
     \item[{\mybf Build Description}]\mbox{}\\
-        The build description is used to instantiate {\myit cell}s and connect {\myit cell}s.
+        The build description is used to instantiate and connect {\myit cell}s.
         Figure \ref{build} shows an example of a build description.
-        A {\myit celltype} name such as tMotor, and a {\myit cell} name such as Motor follow the keyword {\myit cell}.
-        To compose {\myit cell}s, a {\myit call} port, a {\myit signature}, a {\myit entry} port in order are described.
-        In this example, a {\myit entry} port eMotor in a {\myit cell} Motor is connected to a {\myit call} port cMotor in a {\myit cell} Caller.
+        A {\myit celltype} name and {\myit cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\myit cell}.
+        To compose {\myit cell}s, a {\myit call} port, {\myit cell}'s name, and an {\myit entry} port are described in that order.
+        In Figure \ref{build}, {\myit entry} port eMotor in {\myit cell} Motor is connected to {\myit call} port cMotor in {\myit cell} Caller.
+        {\myit C\_EXP} calls macros defined in C files.
+
 \begin{figure}[t]
@@
 \label{sec:mruby on TECS}
-mruby on TECS is a component-based framework for running script language.
-This framework uses two technologies, mruby and TECS.
+% mruby on TECS is a component-based framework for running script language.
+% This framework uses two technologies, mruby and TECS.
 
 \subsubsection{System Model}
-The system model of mruby on TECS is shown in Figure \ref{fig:mrubyontecs}.
-Each mruby program, which is bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
 TECS components support various embedded drivers such as motor and sensor drivers.
 
-An mruby-TECS bridge plays a role to call a native program (e.g. C legacy code) from an mruby program.
-The mruby-TECS bridge provides native libraries for mruby.
-It also gives TECS components to receive the invocation from an mruby program.
-The mruby-TECS bridge is described in more detail bellow.
+An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% The mruby-TECS bridge is described in more detail bellow.
 
-As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
-TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
 However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mrubyontecs.eps}
-    \caption{System Model of existing mruby on TECS}
+    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+    \vspace{0.5mm}
+\caption{System model of existing mruby on TECS}
+    \vspace{1mm}
 \label{fig:mrubyontecs}
@@
 \subsubsection{mruby-TECS Bridge}
-There is a great difference between the execution time of mruby and C language.
-According to  \cite{par:mrubyonTECS}, mruby programs are several hundreds times slower than C programs.
-The execution of mruby bytecode on a RiteVM is not as efficient as that of C language.
-Thus it is difficult to use mruby for all codes.
+There is a significant difference between the execution times of mruby and C language codes.
+According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+Thus, it is difficult to use mruby exclusively.
 
-The use of Ruby on embedded devices provides the benefit of productivity and maintainability due to the ease to use and read.
-On the other hands, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make a critical section of codes run quickly.
+Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
 
-Figure \ref{fig:mruby_TECS_bridge} shows an example of use of an mruby-TECS bridge for controlling a motor.
+Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
 The left side of BridgeMotor belongs to the mruby program.
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby_TECS_bridge.eps}
-    \caption{mruby-TECS Bridge}
+    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+    \vspace{0.5mm}
+\caption{mruby-TECS bridge}
+    \vspace{1mm}
 \label{fig:mruby_TECS_bridge}
@@
 
-The mruby-TECS bridge generates two things.
-One is a {\myit celltype} to receive invocation from the mruby program.
-The other is an mruby class that corresponds to the TECS component specified by the developers to invoke a C function from the mruby program.
+The mruby-TECS bridge generates a {\myit celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
 
-A code of an mruby-TECS bridge is generated.
-The generation code supports registration of classes and methods for mruby.
-The methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, an mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.
+The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.
 
@@
 Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
-Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
-The RiteVM reads the own bytecode and executes it.
-The mruby applications run at the same time because of synchronization processing.
-The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.
+Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
+The RiteVM reads the transferred bytecode and executes it with libraries.
+The mruby applications run simultaneously due to synchronized processing.
+The RiteVM scheduler switches RiteVM tasks because multiple tasks can run concurrently.
+The following subsection explains these functionalities.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/system_model.eps}
-    \caption{Detailed System Model of the proposed framework}
+    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
+    \vspace{0.5mm}
+\caption{Detailed system model of the proposed framework}
+    \vspace{1mm}
 \label{fig:system_model}
@@
 
-\subsection{mruby Bytecode Loader Using Bluetooth}
-\label{sec:mruby bytecode loader using Bluetooth}
-\footnote{
-mruby bytecode loader is intended to improve the development efficiency, therefore software developers should use it for development phase.
-Complete software should be compiled and linked in the storage/ROM device beforehand.
+\subsection{Bluetooth Loader for mruby Bytecode}
+\label{sec:Bluetooth loader for mruby bytecode}
+This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader, for mruby bytecode.\footnote{
+The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
+Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
 }
-This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
-In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
-Developers must rewrite the storage/ROM device every time the application programs are modified.
-The OS on the target device should be also restarted.
-It causes a low development efficiency to repeat that.
-An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
-%The work that an SD card is in and out needs to be done just once in the beginning.
-Developers should just once carry out the work to connect the storage/ROM device and start the OS.
+In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
+Developers must rewrite the storage/ROM device every time the programs are modified.
+In addition, the RTOS on the target device needs to be restarted.
+The repetition hinders development efficiency.
+The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.
 
-mruby programs are consisted of mruby application and libraries.
-mruby application is the main code which software developers should program.
-mruby libraries are the codes defining the functions for application such as Ruby classes. 
-The mruby bytecodes including mruby application and libraries can be sent and run.
-However, it is also wasteful in terms of the size and time to send bytecodes because libraries are not frequently modified. 
-The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
-Due to this design, RiteVMs can share the mruby libraries.
-In addition, a RiteVM can use the own library that other RiteVMs should not use.
+mruby programs consist of an mruby application and mruby libraries.
+An mruby application is the main program code, mruby libraries define the functions for the application, such as Ruby classes. 
+The mruby bytecodes including both an mruby application and mruby libraries can be transferred and executed on the target device.
+However, this is also wasteful in terms of bytecode size and the time required to transfer the bytecodes, because the libraries are not modified frequently.
+With the proposed framework, only mruby applications are transferred, and the mruby libraries are preserved on the storage/ROM device beforehand.
+As a result, RiteVMs can share mruby libraries.
+In addition, a RiteVM can use its own library, which other RiteVMs should not use.
 
-%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
-In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
-%These are assumed not to be modified.
-%The binary data transferred with Bluetooth is the bytecode of the main source.
-In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
-The generated bytecodes are transferred from the host to the target device with Bluetooth.
+In the proposed framework, a platform that includes RiteVMs and an mruby library is first compiled and copied to the storage/ROM device.
+On the host, the mruby application programs (.rb files) are edited and compiled to bytecodes (.mrb files) by an mruby compiler.
+The generated bytecodes are transferred from the host to the target device via Bluetooth.
+This saves time since Bluetooth pairing can be avoided because the loader can load the bytecode continuously.
 
-Moreover, developers can save the time of Bluetooth pairing since the loader can continuously load the bytecode.
-
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{figure/bluetooth_loader.eps}
-%     \caption{Development Flow in mruby bytecode loader using Bluetooth}
-%     \label{fig:bluetooth_loader}
-% \end{figure}
-
-\subsubsection{Component of RiteVM with mruby bytecode loader using Bluetooth}
+\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
 \begin{figure}[t]
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_bluetooth.eps}
-    \caption{Component Diagram of mruby bytecode loader using Bluetooth}
+    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
+    \vspace{0.5mm}
+\caption{Component diagram of Bluetooth loader for mruby bytecode}
+    \vspace{1mm}
 \label{fig:component_bluetooth}
 \end{figure}
-The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
-The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
-The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generation the mruby library bytecode.
-This generated bytecode is prepared beforehand in the storage/ROM device, and different from a bytecode transferred with Bluetooth.
+The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
+This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
+It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
+This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.
 
 Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\myit cell}s.
-The MrubyTask1 {\myit cell} is a componentized task of the RTOS (TOPPERS/HRP2).
-TOPPERS/HRP2 is described in \cite{url:HRP2}, \cite{par:hr-tecs}.
-The RiteVMBluetooth1 is the component of RiteVM with mruby bytecode loader using Bluetooth.
-A bytecode in the host is transferred and received at the top of the component.
-In this framework, ZMODEM \cite{par:zmodem} is used as a binary transfer protocol.
+The MrubyTask1 {\myit cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
+The RiteVMBluetooth1 {\myit cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
+Bytecode on the host is transferred and received.
+In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/control_flow.eps}
-    \caption{Process Flow of mruby bytecode loader using Bluetooth}
+    \includegraphics[width=8.6cm,clip]{figure/control_flow.eps}
+    \vspace{0.5mm}
+\caption{Process flow of Bluetooth loader for mruby bytecode}
+    \vspace{1mm}
 \label{fig:control_flow}
@@
 \end{lstlisting}
-\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
+\vspace{1mm}
+\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
+\vspace{1mm}
 \label{celltype_mrubybluetooth}
@@
   /* Omit: synchronization of
-                starting mruby application */
+                initializing mruby application */
   /* Load mruby library bytecode */
@@
   /* Omit: synchronization of
-                finishing mruby application */
+                terminating mruby application */
   /* Free mruby context */
@@
 \end{lstlisting}
-\caption{Main code for RiteVM with mruby bytecode loader using Bluetooth}
+\vspace{1mm}
+\caption{Main code for RiteVM with Bluetooth loader for mruby bytecode}
+\vspace{1mm}
 \label{maincode_mrubybluetooth}
@@
 
-Figure \ref{fig:control_flow} shows the process flow of executing mruby program in the component of RiteVM with mruby bytecode loader using Bluetooth such as RiteVMBluetooth1.
-The concrete main code of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
+Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
+The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.
 
-First, the mruby bytecode loader receives the mruby application bytecode transferred from the host (Figure \ref{fig:control_flow}:A, Figure \ref{maincode_mrubybluetooth}:6-7).
-The bytecode is stored in the component variable such as VAR\_irepApp shown in Figure \ref{celltype_mrubybluetooth}.
+First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
+The bytecode is stored in a component variable, such as {\myit VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
 This process is exclusively carried out by the semaphore.
 
-Second, pointers of {\myit mrb\_state} and {\myit mrbc\_context}, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}:B, Figure \ref{maincode_mrubybluetooth}:9-14).
+Second, {\myit mrb\_state} and {\myit mrbc\_context} pointers, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}(B); lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
+{\myit VAR\_mrb} and {\myit VAR\_context} show the variables of the {\myit cell}.
 {\myit mrb\_state} is a set of states and global variables used in mruby.
-Synchronization of multiple tasks is performed in this processing phase.
-The RiteVM that ended up here waits for the other RiteVM to finish loading and initialization.
+The synchronization of multiple tasks is performed in this processing phase.
+The RiteVM that finishes execution at this point waits for the another RiteVM to finish loading and initialization.
 
-Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}:C, Figure \ref{maincode_mrubybluetooth}:17-19).
-mruby libraries are a set of Ruby classes such as motor class and sensor class.
-For example, motor class defines methods to rotate and stop a motor.
-The tRiteVMBluetooth {\myit cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
-The {\myit mrubyLib} indicates the program files of mruby libraries.
-{\myit [omit]} is only used for the TECS generator, thus the attribute, {\myit mrubyLib}, does not consume memory.
-The {\myit irepLib} is the pointer of the array stored the bytecode of mruby libraries.
-In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.
+Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); lines 17-19 in Figure \ref{maincode_mrubybluetooth}).
+The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
+For example, the motor class defines methods to rotate and stop a motor.
+The tRiteVMBluetooth {\myit cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
+{\myit ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\myit VAR}.
+The {\myit mrubyLib} indicates the program files of the mruby libraries, and is an attribute because mruby libraries are not modified in the proposed development process.
+Here, {\myit [omit]} is only used for the TECS generator; thus, the attribute {\myit mrubyLib} does not consume memory.
+{\myit irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
+To summarize, the bytecode of mruby libraries is stored as an attribute of the component during the first compilation.
 
-Fourth, the RiteVM reads the bytecode of the mruby application transferred with Bluetooth (Figure \ref{fig:control_flow}:D, Figure \ref{maincode_mrubybluetooth}:20-22).
-The mruby application bytecode is stored in an array of {\myit irepApp}.
-The array is different from that of holding the mruby library bytecode.
-Two bytecodes are read separately in the RiteVM.
+Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
+The mruby application bytecode is stored in an array of {\myit irepApp}, which differs from the array that holds the mruby library bytecode.
+Note that two bytecodes are read separately in the RiteVM.
 
-Finally, the mruby task runs (Figure \ref{fig:control_flow}:E, Figure \ref{maincode_mrubybluetooth}:20-22).
-When the mruby application is modified, only the bytecode of the modified application should be transferred.
-mruby libraries need not be touched because libraries are not normally changed.
+Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
+When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
 
-The process shown in Figure \ref{maincode_mrubybluetooth}:23-28 is carried out when an exception occurs.
-When all mruby applications finish, mrb\_state and mrbc\_context are freed (Figure \ref{maincode_mrubybluetooth}:31-34).
-The proposed framework supports continuous loading, thus this process loops.
-After freeing variables, RiteVM will become the state to wait for the next mruby application bytecode.
+The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
+When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
+The proposed framework supports continuous loading; thus, this process loops.
+After the variables are freed, the RiteVM waits for the next mruby application bytecode.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/rotateReadyQueue.eps}
+    \vspace{0.5mm}
+\caption{RiteVM scheduler design}
+    \vspace{1mm}
+\label{fig:rotateReadyQueue}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
+    % \vspace{0.5mm}
+\caption{Component diagram of RiteVM scheduler}
+    \vspace{1mm}
+\label{fig:cyclic_handler}
+\end{figure}
+
 \subsection{RiteVM Scheduler}
 \label{sec:RiteVM Scheduler}
-This section describes implementation of RiteVM scheduler in the proposed framework.
-mruby on TECS has supported multitasking.
-However, multitask processing in mruby on TECS requires the knowledge of the RTOS (TOPPERS/HRP2) for developers.
+This section describes the implementation of the RiteVM scheduler in the proposed framework.
+mruby on TECS supports multitasking; however, multitask processing in mruby on TECS requires the developers to have knowledge about the RTOS (TOPPERS/HRP2).
 
-One of approaches for multitasking is co-routine.
-Co-routine is a cooperative thread, and scheduled by developers with the functions such as {\myit resume} and {\myit yield}. 
-(Ruby co-routine is defined in class Fiber \cite{url:co-routine})
-Co-routine is a non-preemptive multitasking, and does not receive the OS's support because developers have to switch tasks manually.
-Co-routine can not take advantage of multi core processing.
+One approach for multitasking is a co-routine, which is a cooperative thread scheduled by developers with functions such as {\myit resume} and {\myit yield} (the Ruby co-routine is defined in the Fiber class \cite{url:co-routine}).
+A co-routine is non-preemptive multitasking, which does not receive OS support because developers must switch tasks manually.
+A co-routine cannot take advantage of multicore processing.
 
-Besides, as another method, {\myit delay()}, a service call of $\mu$ITRON, can be used for multitasking.
-This service call delays the execution of the own task for the time of the argument.
-%In the approach of {\myit delay} function, developers have to schedule as the same as co-routine.
+As another method, {\myit delay()}, which is a service call of $\mu$ITRON, can be used for multitasking.
+This service call delays the execution of its own task for the time of the argument.
 {\myit delay()} is needed when scheduling fixed-priority tasks.
-However, the programming applied to {\myit delay()} is difficult to use in the case of fair scheduling.
+However, the programming applied to {\myit delay()} is difficult to use with fair scheduling.
 
-As an approach for multitask processing, the proposed framework provides the RiteVM scheduler which is a fair scheduler and runs multiple tasks equally.
-The RiteVM scheduler is utilized only when application tasks have the same priority.
-mruby applications can run in concurrent without developers calling the OS's function.
-The application programs can also utilize the existing programs since the structures of the programs are not changed.
+For multitask processing, the proposed framework provides the RiteVM scheduler, which is a fair scheduler that runs multiple tasks equally.
+Note that the RiteVM scheduler is utilized only when application tasks have equal priority.
+mruby applications can run concurrently without calling an OS function.
+The application programs can also utilize existing programs because their structures do not change.
 
-\subsubsection{Design of RiteVM Scheduler}
-A RiteVM scheduler is a periodic handler, and calls {\myit rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
+The RiteVM scheduler is a fair scheduler that is implemented as a TECS component in the proposed framework.
+Therefore, when developers create software with priority-based scheduling, the RiteVM scheduler can be removed easily.
+
+\subsubsection{RiteVM Scheduler Design}
+A RiteVM scheduler is a periodic handler, and {\myit rotateReadyQueue}, which is a service call of $\mu$ITRON to switch tasks with equal priority, is implemented as the main process of the handler.
 In other words, the RiteVM scheduler calls {\myit rotateReadyQueue} cyclically.
@@
 
-The case is assumed that there are two tasks with the same priority, and both tasks are in an infinite loop.
-In the current system, when one task is executed first, another task would not be executed.
-That is because the task with first execution runs in the loop.
+Here, assumed that two tasks with equal priority are in an infinite loop.
+In the current system, when one task is executed first, the other task would not be executed because the first task runs in the loop.
 
-When {\myit rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
-The argument of {\myit rotateReadyQueue} is the priority.
+When {\myit rotateReadyQueue} is called, tasks with equal priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
+Note that the argument of {\myit rotateReadyQueue} is the priority.
 
-The {\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
-For example, three tasks are in the order: task 1, 2, and 3.
-In this case, the order is rotated, task 2, 3 and, 1, when the {\myit rotateReadyQueue} is called.
+In addition, {\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
+For example, three tasks are in the order task1, task2, and task3.
+In this case, the order is rotated to task2, task3, and task1 when {\myit rotateReadyQueue} is called.
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.eps}
-    \caption{The design of RiteVM scheduler}
-    \label{fig:rotateReadyQueue}
-\end{figure}
-
-\subsubsection{Component of RiteVM Scheduler}
-Figure \ref{fig:cyclic_handler} shows the component diagram of RiteVM scheduler.
-The component of RiteVM scheduler consist of CyclicHandler and RiteVMSchedulerMain.
-CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
-Cyclic handlers based on $\mu$ITRON are described in detail \cite{par:microITRON}.
-CyclicHandler {\myit cell} has attributes of the {\myit cell}.
-RiteVMSchedulerMain {\myit cell} is a component to perform the processing body of a periodic handler.
-{\myit rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\myit celltype}, which is the {\myit composite cell} consisting of two {\myit cell}s.
-The {\myit call} port of RiteVMSchedulerMain is connected with the {\myit entry} port of the Kernel {\myit cell} ({\myit tKernel.eiKernel}) to call functions of the kernel. 
-The attribute is used as an arguments of {\myit rotateReadyQueue}.
-
-Figure \ref{build_cyclic_handler} shows the build description of RiteVM scheduler.
-RiteVMScheduler {\myit cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
-In this case, RiteVM scheduler is executed when it is generated because the attribute is {\myit TA\_STA} that represents the periodic handler is in an operational state after the creation.
-The scheduler executes every one msec.
-RITEVM\_PRIORITY defines the priority of mruby tasks.
-In the main of CyclicMain, {\myit rotateReadyQueue} is implemented and the priority is passed as the argument.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/cyclic_handler.eps}
-    \caption{Component Diagram of RiteVM Scheduler}
-    \label{fig:cyclic_handler}
-\end{figure}
 \begin{figure}[t]
@@
     \end{lstlisting}
-    \caption{Celltype Description of RiteVM Scheduler}
+    \vspace{1mm}
+\caption{Celltype description of RiteVM scheduler}
+    \vspace{1mm}
 \label{celltype_cyclic_handler}
@@
 \end{lstlisting}
-    \caption{Build Description of RiteV Scheduler}
+    \vspace{1mm}
+\caption{Build description of RiteVM scheduler}
+    \vspace{1mm}
 \label{build_cyclic_handler}
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
-In the proposed framework, RiteVMs read mruby bytecodes, and then execute the applications.
-Eventflag, one of synchronous processing, is applied to synchronize the starting of multiple mruby applications.
-Each task sets the flag pattern such as 0x01 (01) and 0x02 (10), and then waits the flag pattern, 0x3 (11), with AND.
-This process can also apply to the case of the more tasks.
-For example, in the case of the four RiteVM tasks, each task sets the flag pattern such as 0x01 (0001), 0x02 (0010), 0x04 (0100)  and 0x08 (1000), and then waits 0x0f (1111) with AND as shown in Figure \ref{fig:Eventflag} (A).
+\subsubsection{Component of RiteVM Scheduler}
 
-In addition, the end of mruby applications is synchronized to accept the continuous loading.
-The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
-All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.
+Figure \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
+The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
+The CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
+Cyclic handlers based on $\mu$ITRON are described in the literature \cite{par:microITRON}.
+The CyclicHandler {\myit cell} has the attributes of the {\myit cell}.
+The RiteVMSchedulerMain {\myit cell} processes the body of a periodic handler.
+Note that {\myit rotateReadyQueue} is implemented as the body.
+Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\myit celltype}, which is a {\myit composite cell} consisting of two {\myit cell}s.
+The {\myit call} port of RiteVMSchedulerMain is connected to the {\myit entry} port of the Kernel {\myit cell} ({\myit tKernel.eiKernel}) to call kernel functions.
+The attribute is used as the {\myit rotateReadyQueue} arguments.
+
+Figure \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
+The RiteVMScheduler {\myit cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
+In this case, the RiteVM scheduler is executed when it is generated, because the attribute is {\myit TA\_STA}, which indicates that the periodic handler is in an operational state after creation.
+Note that the scheduler executes every 1 msec.
+RITEVM\_PRIORITY defines the priority of mruby tasks.
+In the function of RiteVMSchedulerMain, {\myit rotateReadyQueue} is implemented and the priority is passed as the argument.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/Eventflag.eps}
-    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
+    \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
+    \vspace{0.5mm}
+\caption{Design of Eventflag using TECS (only differences are shown)}
+    \vspace{1mm}
 \label{fig:Eventflag}
@@
 
+\subsection{Synchronization of Multiple RiteVM Tasks}
+In the proposed framework, RiteVMs read mruby bytecodes and then execute applications.
+Eventflag is applied to synchronize the initiation of multiple mruby applications.
+Each task sets a flag pattern, such as 0x01 (01) and 0x02 (10), and then waits for the flag pattern 0x3 (11) with AND.
+This process can also be applied to more tasks.
+For example, for four RiteVM tasks, each task sets a flag pattern, such as 0x01 (0001), 0x02 (0010), 0x04 (0100), and 0x08 (1000), and then waits 0x0f (1111) with AND, as shown in Figure \ref{fig:Eventflag}(A).
+
+In addition, the termination of mruby applications is synchronized to accept continuous loading.
+This termination synchronization prevents a RiteVM whose application finishes immediately from waiting for the next loading.
+Thus, all mruby applications finish at the same time, and all RiteVMs wait to receive the next mruby application bytecodes.
+
 \subsection{Utilization of Component-Based Development}
-This section describes the design applying component-based development.
+% This section describes the design applying component-based development.
+In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
+Therefore, developers can add, remove, or reuse these components easily.
+For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\myit //import(<tRiteVMScheduler.cdl>);}.
+CBD eliminates the need for developers to rewrite kernel configuration files.
 
-In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
-Therefore, developers can easily add or remove these components and also reuse them.
-For example, if RiteVM scheduler is not necessary for software, developers should only comment out the .cdl file such as {\myit //import(<tRiteVMScheduler.cdl>);}.
-This advantage of CBD saves developers the labor of rewriting a kernel configuration file.
-
-In addition, the code size can decrease by developing with component-based. 
-In the proposed framework, the advantage is applied in the Eventflag component.
+In addition, the code size can be reduced by using CBD. 
+In the proposed framework, this advantage is applied in the Eventflag component.
 The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
-This design such as {\myit cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
-Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
-In addition, the components of Eventflag are built with {\myit [optional]} in TECS.
-{\myit [optional]} means that the codes are run only when the call port is connected.
-The .c file does not be rewritten even if developers do not use Eventflag.
-
-\section{Experimental Evaluation}
-\label{sec:Evaluation}
-This section mentions experimental results and their consideration.
-To analyze the advantages of the proposed framework, the evaluations are performed as follows.
-\begin{itemize}
-%    \item Execution time of the platform
-    \item Size and time for transferred mruby bytecodes
-    \item Execution time with singletasking, co-routine, and multitasking
-    \item Overhead for periodic time
-%    \item Synchronization of mruby applications
-    \item Code size utilizing component-based development 
-\end{itemize}
-
-These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
-This paper demonstrates the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
-
-\subsection{Improving the software development efficiency by mruby bytecode loader}
-The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
-Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
-The mruby application bytecode is smaller and faster than that of including mruby libraries in all terms.
-The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
-%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
-%Therefore, the design can send the bytecode faster.
-In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
-These advantages lead improvement of the software development efficiency.
+This design, e.g., {\myit cEventflag\_set(ATTR\_setPattern)}, enables the program without ``if'' statements and reuses an identical C file.
+Developers do not need to modify the C file because the CDL files are prepared according to the number of RiteVMs.
+In addition, the Eventflag components are built with {\myit [optional]} in TECS.
+Here, {\myit [optional]} means that the code is run only when the call port is connected.
+Note that the C file does not need to be rewritten even if the Eventflag is not used.
 
@@
     \centering
-    \caption{Comparison of the size and load process time between an mruby application including mruby libraries and not}
-    \scriptsize
+    \vspace{1mm}
+\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
+    \vspace{1mm}
+    %\scriptsize
     {\tabcolsep=0.1cm
@@
 
-\subsection{RiteVM Scheduler}
-The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-The 100,000 times loop program is used as mruby application for evaluation of execution time.
-In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
-In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is one msec.
-%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
-This result shows the proposed design is superior to co-routine in terms of execution time.
-Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
-Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
-%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
-%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-The scheduler interrupts and switches tasks, which causes this overhead.
+\section{Experimental Evaluation}
+\label{sec:Evaluation}
+This section discusses experimental results.
+To analyze the advantages of the proposed framework, we evaluated the following.
+\begin{itemize}
+%    \item Execution time of the platform
+    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
+    \item Execution time with singletasking, co-routine, and proposed multitasking
+    \item Overhead for periodic time
+    \item Synchronization of multiple RiteVM tasks
+    \item Code size with CBD 
+\end{itemize}
+
+These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
+In addition, we focused on benefits of CBD.
+We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_s_c_m.eps}
-    \caption{Comparison of the application execution time with singletask, co-routine, and multitask}
+    \includegraphics[width=8.6cm,clip]{figure/comparison_s_c_m.eps}
+    \vspace{0.5mm}
+\caption{Comparison of application execution time with singletask, co-routine, and multitask}
+    \vspace{1mm}
 \label{fig:comparison_s_c_m}
 \end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/comparison_msec.eps}
+    \vspace{0.5mm}
+\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
+    \vspace{1mm}
+\label{fig:comparison_msec}
+\end{figure}
 
+\subsection{Improving Software Development Efficiency by Bluetooth Loader}
+The Bluetooth loader for mruby bytecode can reduce the development time.
+With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
+For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
+In addition, the proposed framework eliminates the need to restart the target RTOS.
+
+%\subsubsection{Size and time for transferred mruby bytecodes}
+In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
+The size, load process time, and compilation time for an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
+The overhead of load processing to load a zero byte bytecode is 50.933 msec.
+Similarly, compilation overhead to compile a zero byte program is 46.9 msec.
+The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
+The difference increases as the number of RiteVMs increases because 50 msec of overhead is incurred per RiteVM. 
+These advantages improve the efficiency of software development.
+
+\subsection{RiteVM Scheduler}
+A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
+Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.
+
+\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
+In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
+This shows that the proposed design is superior to co-routine in terms of execution time.
+Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
+The scheduler interrupts and switches tasks, which causes this overhead.
+It takes approximately 3 $\mu$sec on average to switch tasks once.
+
+\subsubsection{Periodic Time Overhead}
 Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
-A lower limit of the periodic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
-More than eight msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
-%Each execution time of cyclic period is the same as the others.
-%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
-The execution time decreases as the periodic time become larger, because the number of switching tasks decreases.
-The execution time of one msec is only about 1 \% lager than that of eight msec.
-The RiteVM scheduler with small periodic time can effectively execute multiple tasks because the periodic time overhead is not large.
-%This results also shows the overhead becomes smaller as the periodic time is larger, because the overhead depends on the number of switching tasks.
-%The smaller periodic time is better in multitasking due to concurrent and/or parallel processing.
+The lower limit of the periodic time is 1 msec due to the specifications of TOPPERS/HRP2, i.e., the RTOS.
+% More than 8 msec do not be evaluated in this paper because it is thought the larger periodic time influences applications.
+The execution time decreases as the periodic time increases, because the number of switched tasks decreases.
+Note that an execution time of 1 msec is approximately 1\% greater than that of 8 msec.
+The RiteVM scheduler with a short periodic time can execute multiple tasks effectively because the periodic time overhead is not large.
+Note that a smaller periodic time is better for multitasking due to concurrent or parallel processing.
 
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/comparison_msec.eps}
-    \caption{Comparison of the overhead for each cyclic period of calling rotateReadyQueue}
-    \label{fig:comparison_msec}
+    \includegraphics[width=8.6cm,clip]{figure/eval_synchronization.eps}
+    \vspace{0.5mm}
+\caption{Synchronization of multiple RiteVM tasks}
+    \vspace{1mm}
+\label{fig:eval_synchronization}
 \end{figure}
-
-\subsection{Synchronization of multiple RiteVM tasks}
-
-\subsection{Benefits of component-based development}
-To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
-(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
-(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
-Moreover, lines of two .cdl files are equal.
-The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.
 
@@
     \centering
-    \caption{Lines of .c and .cdl file for the number of RiteVM}
-    \scriptsize
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||cc|c}
+    \vspace{1mm}
+    \caption{C and CDL file code for the number of RiteVMs}
+    \vspace{1mm}
+    %\scriptsize
+    {\tabcolsep=0.2cm
+    \begin{tabular}{c||c|c|c}
                 & (A)       & (B)     & Diff  \\ \hline
-        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
-        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
+        C (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
@@
 
-\section{Related Work}
-\label{sec:Related work}
-
 \begin{table*}[t]
     \centering
-    \caption{Comparison of the proposed and previous work}
-    \scriptsize
-    {\tabcolsep=0.1cm
+    \vspace{1mm}
+\caption{Comparison of proposed and previous methods}
+    \vspace{2mm}
+    %\scriptsize
+    {\tabcolsep=0.05cm
     \begin{tabular}{c||c|ccccccc}
@@
 \end{table*}
-The open-source run-time systems for scripting languages have been proposed such as follow:
-python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
-python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
-The VM runs a significant subset of Python language with few resources on a micro-controller.
-p14p can run multiple stackless green threads.
+\subsection{Synchronization of Multiple RiteVM Tasks}
+To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
+We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
+It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
+Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
+% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
+% The periodic time is one msec, and the number of RiteVM is four.
+The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
+As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.
 
-The Owl system is an embedded Python run-time system.
-The Owl is a complete system for ARM Cortex-M3 micro-controllers.
-The Owl toolchain produces relocatable memory images, that are directly runnable on the micro-controller, from Python code objects.
-The interpreter of the Owl system is the same as that of python-on-a-chip.
+\subsection{Benefits of Component-Based Development}
+In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
+Developers can add or remove the functionalities easily by modifying the CDL file.
+Moreover, CBD decreases code size and improves productivity and maintainability.
 
-eLua offers the full implementation of Lua programming language to the embedded systems.
-Lua is one of the most popular script languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
-Lua supports co-routine, referred to collaborative multitasking.
+%\subsubsection{Code size utilizing component-based development}
+To demonstrate the superiority of CBD, a comparison of the number of lines of codes between two C and CDL files is shown in Table \ref{tab:codesize}.
+In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Figure \ref{fig:Eventflag}, respectively. 
+For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
+Note that (B)'s C file can be utilized without modification regardless of the number of RiteVMs.
+Moreover, the number of code lines of two CDL files are equal.
+Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.
+
+\section{Related Work}
+\label{sec:Related work}
+
+Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+
+{\mybf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
+The VM runs a significant subset of the Python language with few resources on a microcontroller.
+p14p can also run multiple stackless green threads.
+
+{\mybf Owl system:} The Owl system is an embedded Python runtime system.
+It is a complete system for ARM Cortex-M3 microcontrollers.
+The Owl toolchain produces relocatable memory images that are directly runnable on the microcontroller from Python code objects.
+Note that the Owl system interpreter is the same as that of python-on-a-chip.
+
+{\mybf eLua:} eLua (embedded Lua) offers a full implementation of the Lua programming language for embedded systems.
+Lua is one of the most popular scripting languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
+Lua supports a co-routine, which is referred to as cooperative multitasking.
 A co-routine in Lua is used as an independently executed thread.
-A co-routine can just suspend and resume multiple routines.
-Thus, a Lua co-routine is not like multitasks in multitask systems.
+Note that a co-routine can only suspend and resume multiple routines; thus, a Lua co-routine is not like multitasks in multitask systems.
 
-mruby, the lightweight implementation of the Ruby language, has been proposed for embedded systems.
+{\mybf Squirrel:} Squirrel is an object-oriented programming language designed as a lightweight scripting language that satisfies the real-time requirements of applications.
+Squirrel was inspired by Lua.
+The Squirrel API is very similar to Lua and the table code is based on that of Lua; Squirrel also supports co-routines.
+
+{\mybf mruby:} mruby, a lightweight implementation of the Ruby language, has been proposed for embedded systems.
 mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
-mruby has supported co-routine, but not supported multitasking for RTOSs.
+Note that the RiteVM only supports a single thread.
+In addition, mruby supports co-routines but does not support multitasking for RTOSs.
 
-mruby on TECS is a component-based framework for running mruby programs.
-The programs on mruby on TECS can execute about 100 times faster than the mruby programs.
-Software can be also developed with component base by mruby on TECS.
-Although multitasking has been supported in the current mruby on TECS, developers need to be familiar with functions of an RTOS to use multitasking.
-The co-routine is supported as same as mruby.
+{\mybf mruby on TECS:} mruby on TECS is a component-based framework for running mruby programs.
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+In addition, software can be developed using CBD with mruby on TECS.
+Although multitasking has been supported in the current mruby on TECS, developers must be familiar with the functions of the RTOS to use multitasking.
+Co-routines are also supported by mruby on TECS.
 
-Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
-The proposed framework supports the loader, the VM scheduler, and synchronization of application.
-
-In addtion, there are component systems for embedded systems.
-AUTOSAR (AUTomotive Open System ARchitecture) \cite{} is a worldwide development partnership of vehicle manufactures.
-
-SaveCCM \cite{par:SAVEapproach} is a component model for embedded control application.
-SaveCCM is a simple model which is flexible to facilitate analysis of real-time and dependability.
-
-Koala \cite{par:Koala} is a component model that helps to manage the growing complexity and diversity of software in consumer electronics products.
+Table \ref{tab:comparison} compares the proposed framework to previous methods.
+The proposed framework implements all of the features shown in the table.
+In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
 
@@
 \label{sec:Conclusion}
-This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
-The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
-The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
+This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
+The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
+The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
 %Thus, the proposed framework can be utilized on the devices without Bluetooth.
-The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
-In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
-The loader can improve the software development efficiency on mruby on TECS.
-The RiteVM scheduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
-%because of the low overhead.
-In addition, synchronization of multiple RiteVM tasks is implemented.
+The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
+Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
+The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
+In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
 
-The proposed framework is developed in component-base by TECS.
-The facilities such as RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
-Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
-Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily removed.
-Component-based development can increase productivity.
+The proposed framework is developed using CBD.
+In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
+Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
+For software developed with priority-based scheduling, developers only have to remove the RiteVM scheduler.
+% Component-based development can increase productivity.
+Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.
 
-In the future, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
+In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin, and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
+Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
 

### 2016-04-26 EMSOFT2016/blind.tex
update

--- 2016-04-08 EMSOFT2016/paper.tex
@@
 
-\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
+\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
 \numberofauthors{3}
-\author{
-\alignauthor
-Takuro Yamamoto\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Wallamaloo, New Zealand}\\
-       % \email{trovato@corporation.com}
-\alignauthor
-Hiroshi Oyama\\
-    \affaddr{OKUMA Corporation}\\
-    \affaddr{Aichi, JAPAN}\\
-       % \affaddr{Dublin, Ohio 43017-6221}\\
-       % \email{webmaster@marysville-ohio.com}
-\alignauthor
-Takuya Azumi\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Hekla, Iceland}\\
-       % \email{larst@affiliation.org}
-}
+% \author{
+% \alignauthor
+% Takuro Yamamoto\\
+%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
+%     \affaddr{Osaka, JAPAN}\\
+%        % \affaddr{Wallamaloo, New Zealand}\\
+%        % \email{trovato@corporation.com}
+% \alignauthor
+% Hiroshi Oyama\\
+%     \affaddr{OKUMA Corporation}\\
+%     \affaddr{Aichi, JAPAN}\\
+%        % \affaddr{Dublin, Ohio 43017-6221}\\
+%        % \email{webmaster@marysville-ohio.com}
+% \alignauthor
+% Takuya Azumi\\
+%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
+%     \affaddr{Osaka, JAPAN}\\
+%        % \affaddr{Hekla, Iceland}\\
+%        % \email{larst@affiliation.org}
+% }
 %\author{Takuro Yamamoto}
@@
 %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgement}
-This work was supported by JSPS KAKENHI Grant Number 15H05305.
-We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
+% \section{Acknowledgement}
+% This work was supported by JSPS KAKENHI Grant Number 15H05305.
+% We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{abbrv}
-\bibliography{ref}
+\bibliography{blind}
 

### 2016-05-25 CPSNA2016/paper.tex
add CPSNA

--- 2016-04-08 EMSOFT2016/paper.tex
@@
 \input{dummy/dummy.tex}
-\documentclass{sig-alternate-05-2015}
-%\usepackage[dvipdfmx]{graphicx}
+\documentclass[conference]{IEEEtran}
+\usepackage[dvipdfmx]{graphicx}
 \usepackage{amssymb}
@@
 
-% Copyright
-\setcopyright{acmcopyright}
-% DOI
-\doi{10.475/123_4}
-% ISBN
-\isbn{123-4567-24-567/08/06}
-%Conference
-\conferenceinfo{EMSOFT '16}{October 2--7, 2016, Pittsburgh, USA}
-\acmPrice{\$15.00}
-
-\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
-\numberofauthors{3}
-\author{
-\alignauthor
-Takuro Yamamoto\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Wallamaloo, New Zealand}\\
-       % \email{trovato@corporation.com}
-\alignauthor
-Hiroshi Oyama\\
-    \affaddr{OKUMA Corporation}\\
-    \affaddr{Aichi, JAPAN}\\
-       % \affaddr{Dublin, Ohio 43017-6221}\\
-       % \email{webmaster@marysville-ohio.com}
-\alignauthor
-Takuya Azumi\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Hekla, Iceland}\\
-       % \email{larst@affiliation.org}
+\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
+\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
+\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
+\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
 }
-%\author{Takuro Yamamoto}
-%\date{\today}
 
@@
 
-\keywords{embedded software; scripting language; component-based development}
 \section{Introduction}
@@
 % That is because software componentization provides high-reusability.
-Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
+% Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
 Individual component diagrams enable the visualization of an entire system.
@@
 
-{\mybf Contributions}: The proposed framework provides the following contributions:
+{\bf Contributions}: The proposed framework provides the following contributions:
 \begin{enumerate}
-\item {\mybf Improved software development efficiency.}
+\item {\bf Improved software development efficiency.}
 Developers do not need to rewrite a storage/ROM device and restart an RTOS.
 The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
-\item {\mybf Execution of multiple mruby programs concurrently or in parallel.}
+\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
 Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
-\item {\mybf Synchronized execution of multiple RiteVM tasks.}
+\item {\bf Synchronized execution of multiple RiteVM tasks.}
 The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
-\item {\mybf Benefits of CBD:}
+\item {\bf Benefits of CBD:}
 The paper focuses on the benefits of CBD and provides specific examples.
@@
 
-{\mybf Organization}: The reminder of this paper is organized as follows.
+{\bf Organization}: The reminder of this paper is organized as follows.
 Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
@@
     \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
-    \vspace{0.5mm}
     \caption{System model of the proposed framework}
-    \vspace{1mm}
     \label{fig:proposed}
@@
     \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
-    \vspace{0.5mm}
     \caption{mruby/RiteVM mechanism}
-    \vspace{1mm}
     \label{fig:mruby}
@@
     \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
-    % \vspace{0.5mm}
     \caption{Component Diagram}
-    \vspace{1mm}
     \label{fig:component}
@@
 Figure \ref{fig:component} shows a component diagram.
-A {\myit cell}, which is an instance of a component in TECS, consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
-An {\myit entry} port is an interface that provides functions to other {\myit cell}s, and a {\myit call} port is an interface that enables the use of other {\myit cell}'s functions.
-A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
-{\myit Cell} functions are implemented in C.
+A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
+An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+{\it Cell} functions are implemented in C.
 
-The type of {\myit entry}/{\myit call} port is defined by a {\myit signature}, which is a set of functions.
-A {\myit signature} is the interface definition of a {\myit cell}.
-The {\myit cell}'s  {\myit call} port can be connected to the {\myit entry} port of another {\myit cell} by the same {\myit signature}.
-Here, {\myit celltype} defines one or more {\myit call}/{\myit entry} ports, attributes, and internal variables of a {\myit cell}.
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
 
 \subsubsection{Component Description}
-In TECS, components are described by {\myit signature}, {\myit celltype}, and build written in component description language (CDL).
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
 % TECS code is written in CDL (component description language) file.
@@
 \begin{description}
-    \item[{\mybf Signature Description}]\mbox{}\\
-        The {\myit signature} defines a {\myit cell} interface.
-        The {\myit signature} name follows the keyword {\myit signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+    \item[{\bf Signature Description}]\mbox{}\\
+        The {\it signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
@@
 \end{lstlisting}
-\vspace{1mm}
 \caption{Signature Description}
-\vspace{1mm}
 \label{signature}
 \end{figure}
-    \item[{\mybf Celltype Description}]\mbox{}\\
-        The {\myit celltype} defines {\myit entry} ports, {\myit call} ports, attributes, and variables.
-        A {\myit celltype} name with the prefix ``t'' follows the keyword {\myit celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\myit entry} ports, a {\myit signature}, e.g., sMotor, and an {\myit entry} port name, e.g., eMotor, follow the keyword {\myit entry}.
-        {\myit Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\myit attr} and {\myit var}, respectively.
+    \item[{\bf Celltype Description}]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
 \begin{figure}[t]
@@
 \end{lstlisting}
-\vspace{1mm}
 \caption{Celltype Description}
-\vspace{1mm}
 \label{celltype}
 \end{figure}
-    \item[{\mybf Build Description}]\mbox{}\\
-        The build description is used to instantiate and connect {\myit cell}s.
+    \item[{\bf Build Description}]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
         Figure \ref{build} shows an example of a build description.
-        A {\myit celltype} name and {\myit cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\myit cell}.
-        To compose {\myit cell}s, a {\myit call} port, {\myit cell}'s name, and an {\myit entry} port are described in that order.
-        In Figure \ref{build}, {\myit entry} port eMotor in {\myit cell} Motor is connected to {\myit call} port cMotor in {\myit cell} Caller.
-        {\myit C\_EXP} calls macros defined in C files.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
 
@@
 \end{lstlisting}
-\vspace{1mm}
 \caption{Build Description}
-\vspace{1mm}
 \label{build}
@@
     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
-    \vspace{0.5mm}
 \caption{System model of existing mruby on TECS}
-    \vspace{1mm}
 \label{fig:mrubyontecs}
@@
     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
-    \vspace{0.5mm}
 \caption{mruby-TECS bridge}
-    \vspace{1mm}
 \label{fig:mruby_TECS_bridge}
@@
 
-The mruby-TECS bridge generates a {\myit celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
 
@@
 Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.
+Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
 
@@
     \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
-    \vspace{0.5mm}
 \caption{Detailed system model of the proposed framework}
-    \vspace{1mm}
 \label{fig:system_model}
@@
     \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
-    \vspace{0.5mm}
 \caption{Component diagram of Bluetooth loader for mruby bytecode}
-    \vspace{1mm}
 \label{fig:component_bluetooth}
@@
 
-Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\myit cell}s.
-The MrubyTask1 {\myit cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
-The RiteVMBluetooth1 {\myit cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
+Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
+The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
+The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
 Bytecode on the host is transferred and received.
@@
     \includegraphics[width=8.6cm,clip]{figure/control_flow.eps}
-    \vspace{0.5mm}
 \caption{Process flow of Bluetooth loader for mruby bytecode}
-    \vspace{1mm}
 \label{fig:control_flow}
@@
 \end{lstlisting}
-\vspace{1mm}
 \caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
-\vspace{1mm}
 \label{celltype_mrubybluetooth}
@@
 \end{lstlisting}
-\vspace{1mm}
 \caption{Main code for RiteVM with Bluetooth loader for mruby bytecode}
-\vspace{1mm}
 \label{maincode_mrubybluetooth}
@@
 First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
-The bytecode is stored in a component variable, such as {\myit VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
+The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
 This process is exclusively carried out by the semaphore.
 
-Second, {\myit mrb\_state} and {\myit mrbc\_context} pointers, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}(B); lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
-{\myit VAR\_mrb} and {\myit VAR\_context} show the variables of the {\myit cell}.
-{\myit mrb\_state} is a set of states and global variables used in mruby.
+Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}(B); lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
+{\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
+{\it mrb\_state} is a set of states and global variables used in mruby.
 The synchronization of multiple tasks is performed in this processing phase.
@@
 For example, the motor class defines methods to rotate and stop a motor.
-The tRiteVMBluetooth {\myit cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
-{\myit ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\myit VAR}.
-The {\myit mrubyLib} indicates the program files of the mruby libraries, and is an attribute because mruby libraries are not modified in the proposed development process.
-Here, {\myit [omit]} is only used for the TECS generator; thus, the attribute {\myit mrubyLib} does not consume memory.
-{\myit irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
+The tRiteVMBluetooth {\it cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
+{\it ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\it VAR}.
+The {\it mrubyLib} indicates the program files of the mruby libraries, and is an attribute because mruby libraries are not modified in the proposed development process.
+Here, {\it [omit]} is only used for the TECS generator; thus, the attribute {\it mrubyLib} does not consume memory.
+{\it irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
 To summarize, the bytecode of mruby libraries is stored as an attribute of the component during the first compilation.
@@
 Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
-The mruby application bytecode is stored in an array of {\myit irepApp}, which differs from the array that holds the mruby library bytecode.
+The mruby application bytecode is stored in an array of {\it irepApp}, which differs from the array that holds the mruby library bytecode.
 Note that two bytecodes are read separately in the RiteVM.
@@
     \includegraphics[width=8.6cm,clip]{figure/rotateReadyQueue.eps}
-    \vspace{0.5mm}
 \caption{RiteVM scheduler design}
-    \vspace{1mm}
 \label{fig:rotateReadyQueue}
@@
     \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
-    % \vspace{0.5mm}
 \caption{Component diagram of RiteVM scheduler}
-    \vspace{1mm}
 \label{fig:cyclic_handler}
@@
 
-One approach for multitasking is a co-routine, which is a cooperative thread scheduled by developers with functions such as {\myit resume} and {\myit yield} (the Ruby co-routine is defined in the Fiber class \cite{url:co-routine}).
+One approach for multitasking is a co-routine, which is a cooperative thread scheduled by developers with functions such as {\it resume} and {\it yield} (the Ruby co-routine is defined in the Fiber class \cite{url:co-routine}).
 A co-routine is non-preemptive multitasking, which does not receive OS support because developers must switch tasks manually.
@@
 
-As another method, {\myit delay()}, which is a service call of $\mu$ITRON, can be used for multitasking.
+As another method, {\it delay()}, which is a service call of $\mu$ITRON, can be used for multitasking.
 This service call delays the execution of its own task for the time of the argument.
-{\myit delay()} is needed when scheduling fixed-priority tasks.
-However, the programming applied to {\myit delay()} is difficult to use with fair scheduling.
+{\it delay()} is needed when scheduling fixed-priority tasks.
+However, the programming applied to {\it delay()} is difficult to use with fair scheduling.
 
@@
 \subsubsection{RiteVM Scheduler Design}
-A RiteVM scheduler is a periodic handler, and {\myit rotateReadyQueue}, which is a service call of $\mu$ITRON to switch tasks with equal priority, is implemented as the main process of the handler.
-In other words, the RiteVM scheduler calls {\myit rotateReadyQueue} cyclically.
+A RiteVM scheduler is a periodic handler, and {\it rotateReadyQueue}, which is a service call of $\mu$ITRON to switch tasks with equal priority, is implemented as the main process of the handler.
+In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
 The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
-{\myit rotateReadyQueue} is described as follows.
+{\it rotateReadyQueue} is described as follows.
 
@@
 
-When {\myit rotateReadyQueue} is called, tasks with equal priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
-Note that the argument of {\myit rotateReadyQueue} is the priority.
+When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
+Note that the argument of {\it rotateReadyQueue} is the priority.
 
-In addition, {\myit rotateReadyQueue} can be performed if the number of tasks is more than two.
+In addition, {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
 For example, three tasks are in the order task1, task2, and task3.
-In this case, the order is rotated to task2, task3, and task1 when {\myit rotateReadyQueue} is called.
+In this case, the order is rotated to task2, task3, and task1 when {\it rotateReadyQueue} is called.
 
@@
     \end{lstlisting}
-    \vspace{1mm}
 \caption{Celltype description of RiteVM scheduler}
-    \vspace{1mm}
 \label{celltype_cyclic_handler}
@@
 \end{lstlisting}
-    \vspace{1mm}
 \caption{Build description of RiteVM scheduler}
-    \vspace{1mm}
 \label{build_cyclic_handler}
@@
 The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
-The CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
+The CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
 Cyclic handlers based on $\mu$ITRON are described in the literature \cite{par:microITRON}.
-The CyclicHandler {\myit cell} has the attributes of the {\myit cell}.
-The RiteVMSchedulerMain {\myit cell} processes the body of a periodic handler.
-Note that {\myit rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\myit celltype}, which is a {\myit composite cell} consisting of two {\myit cell}s.
-The {\myit call} port of RiteVMSchedulerMain is connected to the {\myit entry} port of the Kernel {\myit cell} ({\myit tKernel.eiKernel}) to call kernel functions.
-The attribute is used as the {\myit rotateReadyQueue} arguments.
+The CyclicHandler {\it cell} has the attributes of the {\it cell}.
+The RiteVMSchedulerMain {\it cell} processes the body of a periodic handler.
+Note that {\it rotateReadyQueue} is implemented as the body.
+Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
+The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
+The attribute is used as the {\it rotateReadyQueue} arguments.
 
 Figure \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
-The RiteVMScheduler {\myit cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
-In this case, the RiteVM scheduler is executed when it is generated, because the attribute is {\myit TA\_STA}, which indicates that the periodic handler is in an operational state after creation.
+The RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
+In this case, the RiteVM scheduler is executed when it is generated, because the attribute is {\it TA\_STA}, which indicates that the periodic handler is in an operational state after creation.
 Note that the scheduler executes every 1 msec.
 RITEVM\_PRIORITY defines the priority of mruby tasks.
-In the function of RiteVMSchedulerMain, {\myit rotateReadyQueue} is implemented and the priority is passed as the argument.
+In the function of RiteVMSchedulerMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.
 
@@
     \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
-    \vspace{0.5mm}
 \caption{Design of Eventflag using TECS (only differences are shown)}
-    \vspace{1mm}
 \label{fig:Eventflag}
@@
 Therefore, developers can add, remove, or reuse these components easily.
-For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\myit //import(<tRiteVMScheduler.cdl>);}.
+For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
 CBD eliminates the need for developers to rewrite kernel configuration files.
@@
 The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
-This design, e.g., {\myit cEventflag\_set(ATTR\_setPattern)}, enables the program without ``if'' statements and reuses an identical C file.
+This design, e.g., {\it cEventflag\_set(ATTR\_setPattern)}, enables the program without ``if'' statements and reuses an identical C file.
 Developers do not need to modify the C file because the CDL files are prepared according to the number of RiteVMs.
-In addition, the Eventflag components are built with {\myit [optional]} in TECS.
-Here, {\myit [optional]} means that the code is run only when the call port is connected.
+In addition, the Eventflag components are built with {\it [optional]} in TECS.
+Here, {\it [optional]} means that the code is run only when the call port is connected.
 Note that the C file does not need to be rewritten even if the Eventflag is not used.
@@
     \centering
-    \vspace{1mm}
 \caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
-    \vspace{1mm}
     %\scriptsize
@@
 \label{sec:Evaluation}
-This section discusses experimental results.
-To analyze the advantages of the proposed framework, we evaluated the following.
-\begin{itemize}
+% This section discusses experimental results.
+% To analyze the advantages of the proposed framework, we evaluated the following.
+% \begin{itemize}
 %     \item Execution time of the platform
-    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
-    \item Execution time with singletasking, co-routine, and proposed multitasking
-    \item Overhead for periodic time
-    \item Synchronization of multiple RiteVM tasks
-    \item Code size with CBD 
-\end{itemize}
+%     \item Size and time of transferred mruby bytecodes by the Bluetooth loader
+%     \item Execution time with singletasking, co-routine, and proposed multitasking
+%     \item Overhead for periodic time
+%     \item Synchronization of multiple RiteVM tasks
+%     \item Code size with CBD 
+% \end{itemize}
 
-These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
+We evaluated to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
 In addition, we focused on benefits of CBD.
@@
     \includegraphics[width=8.6cm,clip]{figure/comparison_s_c_m.eps}
-    \vspace{0.5mm}
 \caption{Comparison of application execution time with singletask, co-routine, and multitask}
-    \vspace{1mm}
 \label{fig:comparison_s_c_m}
@@
     \includegraphics[width=8.6cm,clip]{figure/comparison_msec.eps}
-    \vspace{0.5mm}
 \caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-    \vspace{1mm}
 \label{fig:comparison_msec}
@@
     \includegraphics[width=8.6cm,clip]{figure/eval_synchronization.eps}
-    \vspace{0.5mm}
 \caption{Synchronization of multiple RiteVM tasks}
-    \vspace{1mm}
 \label{fig:eval_synchronization}
@@
     \centering
-    \vspace{1mm}
     \caption{C and CDL file code for the number of RiteVMs}
-    \vspace{1mm}
     %\scriptsize
@@
     \centering
-    \vspace{1mm}
 \caption{Comparison of proposed and previous methods}
-    \vspace{2mm}
     %\scriptsize
@@
 
-{\mybf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
+{\bf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
 The VM runs a significant subset of the Python language with few resources on a microcontroller.
@@
 
-{\mybf Owl system:} The Owl system is an embedded Python runtime system.
+{\bf Owl system:} The Owl system is an embedded Python runtime system.
 It is a complete system for ARM Cortex-M3 microcontrollers.
@@
 
-{\mybf eLua:} eLua (embedded Lua) offers a full implementation of the Lua programming language for embedded systems.
+{\bf eLua:} eLua (embedded Lua) offers a full implementation of the Lua programming language for embedded systems.
 Lua is one of the most popular scripting languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
@@
 
-{\mybf Squirrel:} Squirrel is an object-oriented programming language designed as a lightweight scripting language that satisfies the real-time requirements of applications.
+{\bf Squirrel:} Squirrel is an object-oriented programming language designed as a lightweight scripting language that satisfies the real-time requirements of applications.
 Squirrel was inspired by Lua.
@@
 
-{\mybf mruby:} mruby, a lightweight implementation of the Ruby language, has been proposed for embedded systems.
+{\bf mruby:} mruby, a lightweight implementation of the Ruby language, has been proposed for embedded systems.
 mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
@@
 
-{\mybf mruby on TECS:} mruby on TECS is a component-based framework for running mruby programs.
+{\bf mruby on TECS:} mruby on TECS is a component-based framework for running mruby programs.
 mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.

### 2016-05-29 CPSNA2016/paper.tex
update CPSNA2016

@@
     numbersep=1zw,%
-    %lineskip=-0.5ex%
+    lineskip=-0.5ex%
 }

### 2016-06-03 CPSNA2016/paper.tex
update

--- 2016-05-25 CPSNA2016/paper.tex
@@
 %
-% File: thesis.tex
+% File: paper.tex
 % Created: 月 11 30 08:00 午後 2015 東京 (標準時)
@@
 \input{dummy/dummy.tex}
-\documentclass[conference]{IEEEtran}
+\documentclass[conference]{IEEEtran/IEEEtran}
 \usepackage[dvipdfmx]{graphicx}
@@
     identifierstyle={\small},%
-    commentstyle={\small\itshape},%
+    commentstyle={\footnotesize\itshape},%
     keywordstyle={\small},%\bfseries},%
@@
     numbersep=1zw,%
-    %lineskip=-0.5ex%
+    lineskip=-0.5ex%
 }
 
-\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
+% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
+\title{Efficient Development Framework with mruby for Embedded Systems}
 \author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
@@
 Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
-To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
-In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
-Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
-To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
-The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
-The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
-In addition, multiple mruby programs can run cooperatively in the proposed framework.
-Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
-Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
+To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
+This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
+In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
+% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
+% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
+% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
+% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
+% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
+% In addition, multiple mruby programs can run cooperatively in the proposed framework.
+% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
+% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
 Experimental results demonstrate the advantages of the proposed framework.
@@
 \section{Introduction}
-Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
+Currently, embedded systems must demonstrate high quality and high performance.
 This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
 
-Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
+Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}.
 Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
@@
 In addition, component-based systems are flexible with regard to extensibility and specification changes.
-The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
+TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
 
@@
 However, development in C language results in large code size, incurs high costs, and requires significant development time.
-In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts. 
+In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
 % script languages have high-productivity from their usability.
@@
 To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
-This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
+This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
 % mruby on TECS supports to effectively run mruby script language on embedded systems.
@@
 Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
-Moreover, mruby on TECS only supports a storage/ROM device for loading mruby programs.
-Consequently, if mruby programs are modified, a secure digital (SD) card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart real-time operating systems (RTOSs) on the target device.
-In addition, although mruby on TECS can support multiple virtual machines (multi-VMs), executing multiple tasks requires the developers to call the OS function.
+mruby on TECS only supports a storage/ROM device for loading mruby programs.
+Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
+In addition, although mruby on TECS can support multi-VM, executing multiple tasks requires the developers to call the OS function.
 
@@
 To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
-Note that RiteVM is the Ruby VM specifically designed for embedded systems.
-The RiteVM scheduler manages the execution of multiple RiteVMs and allows developers to program multitasking more easily than the current version of mruby on TECS.
+% Note that RiteVM is the Ruby VM specifically designed for embedded systems.
+The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., VMs designed for mruby) and allows developers to program multitasking more easily than the current version of mruby on TECS.
 
@@
 \begin{enumerate}
+    \vspace{-2mm}
 \item {\bf Improved software development efficiency.}
 Developers do not need to rewrite a storage/ROM device and restart an RTOS.
-The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
+% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
 \item {\bf Execution of multiple mruby programs concurrently or in parallel.}
@@
 The paper focuses on the benefits of CBD and provides specific examples.
+    \vspace{-2mm}
 \end{enumerate}
@@
 {\bf Organization}: The reminder of this paper is organized as follows.
-Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
-Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
+Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
 Section \ref{sec:Evaluation} evaluates the proposed framework.
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
-    \caption{System model of the proposed framework}
-    \label{fig:proposed}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
+%     \caption{System model of the proposed framework}
+%     \label{fig:proposed}
+% \end{figure}
 
-\section{Background}
-\label{sec:Background}
-Figure \ref{fig:proposed} shows the system model of the proposed framework.
-Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
-Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
-Bytecodes transferred from the host via Bluetooth can run in multitask.
+% \section{Background}
+% \label{sec:Background}
+% Figure \ref{fig:proposed} shows the system model of the proposed framework.
+% Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
+% Bytecodes are transferred from the host to the target device via Bluetooth, and each RiteVM is allocated a bytecode.
+% Bytecodes transferred from the host via Bluetooth can run in multitask.
+%
+% \subsection{mruby}
+% \label{sec:mruby}
+% mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+% Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
+% It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+% Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+%
+% mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+% In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+% The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+% The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
+%     \caption{mruby/RiteVM mechanism}
+%     \label{fig:mruby}
+% \end{figure}
+%
+% \subsection{TECS}
+% \label{sec:TECS}
+% TECS is a component system suitable for embedded systems.
+% TECS can increase productivity and reduce development costs due to improved reusability of software components.
+% TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+%
+% In TECS, component deployment and composition are performed statically.
+% Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+% TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+%
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
+%     \caption{Component Diagram}
+%     \label{fig:component}
+% \end{figure}
+%
+% \subsubsection{Component Model}
+% Figure \ref{fig:component} shows a component diagram.
+% A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
+% An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+% A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+% {\it Cell} functions are implemented in C.
+%
+% The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+% A {\it signature} is the interface definition of a {\it cell}.
+% The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+% Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+%
+%
+% \subsubsection{Component Description}
+% In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% % TECS code is written in CDL (component description language) file.
+% These components are described as follows.
+%
+% \begin{description}
+%     \item[{\bf Signature Description}]\mbox{}\\
+%         The {\it signature} defines a {\it cell} interface.
+%         The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+%         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+% \begin{figure}[t]
+% \centering
+% \begin{lstlisting}
+% signature sMotor {
+%     int32_t getCounts( void );
+%     ER resetCounts( void );
+%     ER setPower( [in]int power );
+%     ER stop( [in] bool_t brake );
+%     ER rotate( [in] int degrees, [in] uint32_t speed_abs,
+%               [in] bool_t blocking );
+%     void initializePort( [in]int32_t type );
+% };
+% \end{lstlisting}
+% \caption{Signature Description}
+% \label{signature}
+% \end{figure}
+%     \item[{\bf Celltype Description}]\mbox{}\\
+%         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+%         A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+%         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+%         {\it Call} ports are defined similarly.
+%         Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+% \begin{figure}[t]
+% \centering
+% \begin{lstlisting}
+% celltype tCaller {
+%     call sMotor cMotor;
+% };
+% celltype tMotor {
+%     entry sMotor eMotor;
+%     attr { int32_t port; };
+%     var { int32_t currentSpeed = 0; };
+% };
+% \end{lstlisting}
+% \caption{Celltype Description}
+% \label{celltype}
+% \end{figure}
+%     \item[{\bf Build Description}]\mbox{}\\
+%         The build description is used to instantiate and connect {\it cell}s.
+%         Figure \ref{build} shows an example of a build description.
+%         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+%         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+%         In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+%         {\it C\_EXP} calls macros defined in C files.
+%
+% \begin{figure}[t]
+% \centering
+% \begin{lstlisting}
+% cell tMotor Motor {
+%     port = C_EXP("PORT_A");
+% };
+% cell tCaller Caller {
+%     cMotor = Motor.eMotor;
+% };
+% \end{lstlisting}
+% \caption{Build Description}
+% \label{build}
+% \end{figure}
+%
+% \end{description}
+%
+% \subsection{mruby on TECS}
+% \label{sec:mruby on TECS}
+% % mruby on TECS is a component-based framework for running script language.
+% % This framework uses two technologies, mruby and TECS.
+%
+% \subsubsection{System Model}
+% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+% TECS components support various embedded drivers such as motor and sensor drivers.
+%
+% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% % The mruby-TECS bridge is described in more detail bellow.
+%
+% In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+% However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.
+%
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+% \caption{System model of existing mruby on TECS}
+% \label{fig:mrubyontecs}
+% \end{figure}
+%
+% \subsubsection{mruby-TECS Bridge}
+% There is a significant difference between the execution times of mruby and C language codes.
+% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+% Thus, it is difficult to use mruby exclusively.
+%
+% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
+%
+% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+% The left side of BridgeMotor belongs to the mruby program.
+% The right side of BridgeMotor belongs to TECS component.
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+% \caption{mruby-TECS bridge}
+% \label{fig:mruby_TECS_bridge}
+% \end{figure}
+%
+% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+%
+% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+%
 
-\subsection{mruby}
-\label{sec:mruby}
-mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
-Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
-It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
-Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+\section{System Model}
+\label{sec:System Model}
+The proposed framework is an extended framework of mruby on TECS, and utilizes mruby and TECS.
+These basic technologies are described in appendix of this paper.
 
-mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
-In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
-The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
-    \caption{mruby/RiteVM mechanism}
-    \label{fig:mruby}
-\end{figure}
-
-\subsection{TECS}
-\label{sec:TECS}
-TECS is a component system suitable for embedded systems.
-TECS can increase productivity and reduce development costs due to improved reusability of software components.
-TECS also provides component diagrams, which help developers visualize the overall structure of a system.
-
-In TECS, component deployment and composition are performed statically.
-Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
-    \caption{Component Diagram}
-    \label{fig:component}
-\end{figure}
-
-\subsubsection{Component Model}
-Figure \ref{fig:component} shows a component diagram.
-A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
-An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
-{\it Cell} functions are implemented in C.
-
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
-
-\subsubsection{Component Description}
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
-These components are described as follows.
-
-\begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
-        The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-signature sMotor {
-    int32_t getCounts( void );
-    ER resetCounts( void );
-    ER setPower( [in]int power );
-    ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
-              [in] bool_t blocking );
-    void initializePort( [in]int32_t type );
-};
-\end{lstlisting}
-\caption{Signature Description}
-\label{signature}
-\end{figure}
-    \item[{\bf Celltype Description}]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
-        {\it Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-celltype tCaller {
-    call sMotor cMotor;
-};
-celltype tMotor {
-    entry sMotor eMotor;
-    attr {
-        int32_t port;
-    };
-    var {
-        int32_t currentSpeed = 0;
-    };
-};
-\end{lstlisting}
-\caption{Celltype Description}
-\label{celltype}
-\end{figure}
-    \item[{\bf Build Description}]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
-        {\it C\_EXP} calls macros defined in C files.
-
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-cell tMotor Motor {
-    port = C_EXP("PORT_A");
-};
-cell tCaller Caller {
-    cMotor = Motor.eMotor;
-};
-\end{lstlisting}
-\caption{Build Description}
-\label{build}
-\end{figure}
-
-\end{description}
-
-\subsection{mruby on TECS}
-\label{sec:mruby on TECS}
-% mruby on TECS is a component-based framework for running script language.
-% This framework uses two technologies, mruby and TECS.
-
-\subsubsection{System Model}
-The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
-Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
-TECS components support various embedded drivers such as motor and sensor drivers.
-
-An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
-The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
-% The mruby-TECS bridge is described in more detail bellow.
-
-In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
-\caption{System model of existing mruby on TECS}
-\label{fig:mrubyontecs}
-\end{figure}
-
-\subsubsection{mruby-TECS Bridge}
-There is a significant difference between the execution times of mruby and C language codes.
-According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
-Thus, it is difficult to use mruby exclusively.
-
-Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
-However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
-% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
-
-Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
-The left side of BridgeMotor belongs to the mruby program.
-The right side of BridgeMotor belongs to TECS component.
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
-\caption{mruby-TECS bridge}
-\label{fig:mruby_TECS_bridge}
-\end{figure}
-
-The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-
-The generated mruby-TECS bridge supports registration of classes and methods for mruby.
-Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
-
-\section{Design and Implementation}
-\label{sec:Design and Implementation}
-Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
+Figure \ref{fig:system_model} shows the system model of the proposed framework.
 Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
-The RiteVM reads the transferred bytecode and executes it with libraries.
+The RiteVM reads the transferred bytecode and executes it with libraries (Section \ref{sec:Bluetooth loader for mruby bytecode}).
 The mruby applications run simultaneously due to synchronized processing.
-The RiteVM scheduler switches RiteVM tasks because multiple tasks can run concurrently.
-The following subsection explains these functionalities.
+The RiteVM scheduler switches RiteVM tasks, and multiple tasks can run concurrently (Section \ref{sec:RiteVM Scheduler}).
+mruby applications are synchronized by the Eventflag (Section \ref{sec:Synchronization of Multiple RiteVM Tasks}).
+In this paper, TOPPERS/HRP2 \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
 
@@
     \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
-\caption{Detailed system model of the proposed framework}
+    \vspace{-3mm}
+\caption{System model of the proposed framework}
+    \vspace{-3mm}
 \label{fig:system_model}
+\end{figure}
+
+\section{Design and Implementation}
+\label{sec:Design and Implementation}
+% The following subsection explains these functionalities.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
+    \vspace{-3mm}
+\caption{Component diagram of RiteVM with Bluetooth loader}
+    \vspace{-3mm}
+\label{fig:component_bluetooth}
 \end{figure}
@@
 \label{sec:Bluetooth loader for mruby bytecode}
-This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader, for mruby bytecode.\footnote{
+This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader.\footnote{
 The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
@@
 The generated bytecodes are transferred from the host to the target device via Bluetooth.
-This saves time since Bluetooth pairing can be avoided because the loader can load the bytecode continuously.
+% This saves time since Bluetooth pairing can be avoided because the loader can load the bytecode continuously.
 
 \subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
-\caption{Component diagram of Bluetooth loader for mruby bytecode}
-\label{fig:component_bluetooth}
-\end{figure}
 The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
@@
 Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
-The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
+The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
 The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/control_flow.eps}
-\caption{Process flow of Bluetooth loader for mruby bytecode}
+    \includegraphics[height=3.0cm,width=8.6cm,clip]{figure/control_flow.eps}
+    \vspace{-3mm}
+\caption{Process flow of RiteVM with Bluetooth loader}
+    \vspace{-3mm}
 \label{fig:control_flow}
@@
 \begin{lstlisting}
-/* tRiteVMBluetooth.cdl */
 celltype tRiteVMBluetooth1 {
@@
     attr {
+      FLGPTN setPattern;
       [omit]char_t *mrubyLib;
-      char_t *irepLib = 
-                    C_EXP("&$cell_global$_irep");
-      uint32_t irepAppSize = 
-                    C_EXP( BUFFER_SIZE );
-      FLGPTN setptn;
+      char_t *irepLib = C_EXP("&$cell_global$_irep");
+      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
     };
@@
         mrbc_context *context;
-        [size_is(irepAppSize)] uint8_t *irepApp;
+        [size_is(irepAppSize)] char_t *irepApp;
     };
@@
 \end{lstlisting}
-\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
+    \vspace{-3mm}
+\caption{Celltype description for RiteVM with Bluetooth loader}
+    \vspace{-3mm}
 \label{celltype_mrubybluetooth}
@@
 \begin{lstlisting}
-/* tRiteVMBluetooth.c */
-void
-eMrubyBody_main( CELLIDX idx )
-{
+void eMrubyBody_main( CELLIDX idx ) {
   /* Omit: start of exclusive process by semaphore */
@@
   VAR_mrb = mrb_open();
-  /* Omit: error check for mrb_state */
   /* New mruby context */
   VAR_context = mrbc_context_new( VAR_mrb );
-  /* Omit: initialization of mruby-TECS bridge */
-  /* Omit: synchronization of
-                initializing mruby application */
+  /* Omit: synchronization of initializing mruby application */
   /* Load mruby library bytecode */
-  mrb_load_irep_cxt( VAR_mrb,
-                        ATTR_irepLib, VAR_context );
+  mrb_load_irep_cxt( VAR_mrb, ATTR_irepLib, VAR_context );
   /* Load mruby application bytecode and run */
-  mrb_load_irep_cxt( VAR_mrb,
-                        VAR_irepApp, VAR_context );
-  if ( mrb->exc ) {
-    /* Failure to execute */
-    mrb_p( VAR_mrb, 
-                mrb_obj_value( VAR_mrb->exc ) );
-    exit( 0 );
-  }
-  /* Omit: synchronization of
-                terminating mruby application */
+  mrb_load_irep_cxt( VAR_mrb, VAR_irepApp, VAR_context );
+  /* Omit: synchronization of terminating mruby application */
   /* Free mruby context */
@@
 \end{lstlisting}
-\caption{Main code for RiteVM with Bluetooth loader for mruby bytecode}
+    \vspace{-3mm}
+\caption{Main code for RiteVM with Bluetooth loader}
+    \vspace{-3mm}
 \label{maincode_mrubybluetooth}
@@
 
-First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
+First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); line 4 in Figure \ref{maincode_mrubybluetooth}).
 The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
-This process is exclusively carried out by the semaphore.
+This process is exclusively carried out by the semaphore to prevent the other loading from interrupting.
 
-Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}(B); lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
+Second, {\it mrb\_state} and {\it mrbc\_context} pointers (Figure \ref{fig:control_flow}(B); lines 7, 9 in Figure \ref{maincode_mrubybluetooth}).
 {\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
@@
 
-Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); lines 17-19 in Figure \ref{maincode_mrubybluetooth}).
+Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); line 12 in Figure \ref{maincode_mrubybluetooth}).
 The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
@@
 
-Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
-The mruby application bytecode is stored in an array of {\it irepApp}, which differs from the array that holds the mruby library bytecode.
-Note that two bytecodes are read separately in the RiteVM.
+Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); line 14 in Figure \ref{maincode_mrubybluetooth}).
+The mruby application bytecode is stored in an array of {\it irepApp}.
+Note that two bytecodes, irepLib and irepApp, are read separately in the RiteVM.
 
-Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
+Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
 When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
-
-The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
-When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
+% The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
+% When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
 The proposed framework supports continuous loading; thus, this process loops.
-After the variables are freed, the RiteVM waits for the next mruby application bytecode.
+After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
 
@@
     \includegraphics[width=8.6cm,clip]{figure/rotateReadyQueue.eps}
+    \vspace{-3mm}
 \caption{RiteVM scheduler design}
+    \vspace{-3mm}
 \label{fig:rotateReadyQueue}
@@
     \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
+    \vspace{-3mm}
 \caption{Component diagram of RiteVM scheduler}
+    \vspace{-3mm}
 \label{fig:cyclic_handler}
@@
 A co-routine is non-preemptive multitasking, which does not receive OS support because developers must switch tasks manually.
-A co-routine cannot take advantage of multicore processing.
+% A co-routine cannot take advantage of multicore processing.
 
@@
 mruby applications can run concurrently without calling an OS function.
-The application programs can also utilize existing programs because their structures do not change.
-
+% The application programs can also utilize existing programs because their structures do not change.
 The RiteVM scheduler is a fair scheduler that is implemented as a TECS component in the proposed framework.
-Therefore, when developers create software with priority-based scheduling, the RiteVM scheduler can be removed easily.
+Therefore, when developers create software with fixed-priority based scheduling, the RiteVM scheduler can be removed easily.
 
 \subsubsection{RiteVM Scheduler Design}
-A RiteVM scheduler is a periodic handler, and {\it rotateReadyQueue}, which is a service call of $\mu$ITRON to switch tasks with equal priority, is implemented as the main process of the handler.
-In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
-The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
-{\it rotateReadyQueue} is described as follows.
-
 Here, assumed that two tasks with equal priority are in an infinite loop.
@@
 
-When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
-Note that the argument of {\it rotateReadyQueue} is the priority.
+The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
+A RiteVM scheduler is a periodic handler, and {\it rotateReadyQueue}, which is a service call of $\mu$ITRON to switch tasks with equal priority, is implemented as the main process of the handler.
+% In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
+% {\it rotateReadyQueue} is described as follows.
+{\it rotateReadyQueue} switches tasks with equal priority.
+% Note that the argument of {\it rotateReadyQueue} is the priority.
+In addition, {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
+For example, three tasks are in the order Task1, 2, and 3.
+In this case, the order is rotated to Task2, 3, and 1 when the function is called.
 
-In addition, {\it rotateReadyQueue} can be performed if the number of tasks is more than two.
-For example, three tasks are in the order task1, task2, and task3.
-In this case, the order is rotated to task2, task3, and task1 when {\it rotateReadyQueue} is called.
-
-\begin{figure}[t]
-    \centering
-    \begin{lstlisting}
-/* tRiteVMScheduler.cdl */
-celltype tCyclicHandler {
-    [inline] entry sCyclic eCyclic;
-    call siHandlerBody  ciBody;
-    attr {
-        [omit] ATR    attribute   = C_EXP("TA_NULL");
-    	[omit] RELTIM cyclicTime;
-    	[omit] RELTIM cyclicPhase;
-    };
-};
-celltype tRiteVMSchedulerMain {
-    require tKernel.eiKernel;
-    entry   siHandlerBody eiBody;
-    attr {
-        PRI priority;
-    };
-};
-
-composite tRiteVMScheduler {
-    attr {
-        ATR    attribute      = C_EXP("TA_NULL");
-        RELTIM cyclicTime  = 1;
-        RELTIM cyclicPhase = 1;
-        PRI    priority;
-    };
-    cell tRiteVMSchedulerMain RiteVMSchedulerMain {
-        priority = composite.priority;
-    };
-    cell tCyclicHandler CyclicHandler {
-        ciBody      = RiteVMSchedulerMain.eiBody;
-        attribute   = composite.attribute;
-        cyclicTime  = composite.cyclicTime;
-        cyclicPhase = composite.cyclicPhase;
-    };
-};
-    \end{lstlisting}
-\caption{Celltype description of RiteVM scheduler}
-\label{celltype_cyclic_handler}
-\end{figure}
+% \begin{figure}[t]
+%     \centering
+%     \begin{lstlisting}
+% /* tRiteVMScheduler.cdl */
+% celltype tCyclicHandler {
+%     [inline] entry sCyclic eCyclic;
+%     call siHandlerBody  ciBody;
+%     attr {
+%         [omit] ATR    attribute   = C_EXP("TA_NULL");
+%     	[omit] RELTIM cyclicTime;
+%     	[omit] RELTIM cyclicPhase;
+%     };
+% };
+% celltype tRiteVMSchedulerMain {
+%     require tKernel.eiKernel;
+%     entry   siHandlerBody eiBody;
+%     attr {
+%         PRI priority;
+%     };
+% };
+%
+% composite tRiteVMScheduler {
+%     attr {
+%         ATR    attribute      = C_EXP("TA_NULL");
+%         RELTIM cyclicTime  = 1;
+%         RELTIM cyclicPhase = 1;
+%         PRI    priority;
+%     };
+%     cell tRiteVMSchedulerMain RiteVMSchedulerMain {
+%         priority = composite.priority;
+%     };
+%     cell tCyclicHandler CyclicHandler {
+%         ciBody      = RiteVMSchedulerMain.eiBody;
+%         attribute   = composite.attribute;
+%         cyclicTime  = composite.cyclicTime;
+%         cyclicPhase = composite.cyclicPhase;
+%     };
+% };
+%     \end{lstlisting}
+% \caption{Celltype description of RiteVM scheduler}
+% \label{celltype_cyclic_handler}
+% \end{figure}
 \begin{figure}[t]
@@
     cyclicPhase = 1;
-    priority    =
-        C_EXP("RITEVM_PRIORITY");
+    priority    = C_EXP("RITEVM_PRIORITY");
 };
 \end{lstlisting}
+    \vspace{-3mm}
 \caption{Build description of RiteVM scheduler}
+    \vspace{-3mm}
 \label{build_cyclic_handler}
@@
 Figure \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
-The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
+The RiteVM scheduler is a {\it composite cell} which consists of CyclicHandler and RiteVMSchedulerMain.
 The CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
@@
 Note that {\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
-The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
-The attribute is used as the {\it rotateReadyQueue} arguments.
+% Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
+% The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
+% The attribute is used as the {\it rotateReadyQueue} arguments.
 
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
-\caption{Design of Eventflag using TECS (only differences are shown)}
-\label{fig:Eventflag}
-\end{figure}
-
 \subsection{Synchronization of Multiple RiteVM Tasks}
+\label{sec:Synchronization of Multiple RiteVM Tasks}
 In the proposed framework, RiteVMs read mruby bytecodes and then execute applications.
 Eventflag is applied to synchronize the initiation of multiple mruby applications.
-Each task sets a flag pattern, such as 0x01 (01) and 0x02 (10), and then waits for the flag pattern 0x3 (11) with AND.
+Each task sets a flag pattern, such as 0x01 (01) and 0x02 (10), and then waits for the flag pattern 0x03 (11) with AND.
 This process can also be applied to more tasks.
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
+    \vspace{-3mm}
+\caption{Design of Eventflag using TECS (only differences are shown)}
+    \vspace{-3mm}
+\label{fig:Eventflag}
+\end{figure}
+
 \subsection{Utilization of Component-Based Development}
 % This section describes the design applying component-based development.
-In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as components.
+In the proposed framework, RiteVMs, the scheduler, and Eventflags are implemented as components.
 Therefore, developers can add, remove, or reuse these components easily.
-For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
+For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import("tRiteVMScheduler.cdl");}.
 CBD eliminates the need for developers to rewrite kernel configuration files.
@@
 Here, {\it [optional]} means that the code is run only when the call port is connected.
-Note that the C file does not need to be rewritten even if the Eventflag is not used.
-
-\begin{table}[t]
-    \centering
-\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
-    %\scriptsize
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||c|c|c}
-                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
-          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
-          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
-          Compile Time  & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
-    \end{tabular}
-    }
-    \label{tab:size_and_time}
-\end{table}
+Thus, the C file does not need to be rewritten even if the Eventflag is not used.
 
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/comparison_s_c_m.eps}
-\caption{Comparison of application execution time with singletask, co-routine, and multitask}
-\label{fig:comparison_s_c_m}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/comparison_msec.eps}
-\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-\label{fig:comparison_msec}
-\end{figure}
-
-\subsection{Improving Software Development Efficiency by Bluetooth Loader}
+\subsection{Improving Development Efficiency by Bluetooth Loader}
 The Bluetooth loader for mruby bytecode can reduce the development time.
@@
 
+\begin{table}[t]
+    \centering
+    \vspace{-2mm}
+\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
+    \vspace{-2mm}
+    %\scriptsize
+    {\tabcolsep=0.3cm
+    \begin{tabular}{l||r|r|c}
+                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
+          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
+          Loading Time      & 305.081 msec & 7.774 msec &   $\times$39.2          \\
+          Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
+    \end{tabular}
+    }
+          \vspace{-3mm}
+    \label{tab:size_and_time}
+\end{table}
+
 \subsection{RiteVM Scheduler}
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
+    \vspace{-3mm}
+\caption{Comparison of application execution time}
+    \vspace{-3mm}
+\label{fig:comparison_s_c_m}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
+    \vspace{-3mm}
+\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
+    \vspace{-3mm}
+\label{fig:comparison_msec}
+\end{figure}
 \subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/eval_synchronization.eps}
+    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/eval_synchronization.eps}
+    \vspace{-3mm}
 \caption{Synchronization of multiple RiteVM tasks}
+    \vspace{-3mm}
 \label{fig:eval_synchronization}
@@
 
-\begin{table}[t]
-    \centering
-    \caption{C and CDL file code for the number of RiteVMs}
-    %\scriptsize
-    {\tabcolsep=0.2cm
-    \begin{tabular}{c||c|c|c}
-                & (A)       & (B)     & Diff  \\ \hline
-        C (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
-        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
-        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
-    \end{tabular}
-    }
-    \label{tab:codesize}
-\end{table}
-
-\begin{table*}[t]
-    \centering
-\caption{Comparison of proposed and previous methods}
-    %\scriptsize
-    {\tabcolsep=0.05cm
-    \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
-        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
-        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
-    \end{tabular}
-    }
-    \label{tab:comparison}
-\end{table*}
+% \begin{table*}[t]
+%     \centering
+% \caption{Comparison of proposed and previous methods}
+%     %\scriptsize
+%     {\tabcolsep=0.05cm
+%     \begin{tabular}{c||c|ccccccc}
+%         & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
+%         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
+%         Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
+%         eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+%         Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
+%         mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
+%         mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
+%         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
+%     \end{tabular}
+%     }
+%     \label{tab:comparison}
+% \end{table*}
 
@@
 
+\begin{table}[t]
+    \centering
+    % \vspace{-2mm}
+    \caption{C and CDL file code for the number of RiteVMs}
+    \vspace{-2mm}
+    %\scriptsize
+    {\tabcolsep=0.3cm
+    \begin{tabular}{l||c|c|c}
+                & (A)       & (B)     & Diff  \\ \hline
+        C (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
+        C (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
+        CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
+        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
+    \end{tabular}
+    }
+          \vspace{-3mm}
+    \label{tab:codesize}
+\end{table}
+
 \section{Related Work}
 \label{sec:Related work}
-
-Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
@@
 {\bf eLua:} eLua (embedded Lua) offers a full implementation of the Lua programming language for embedded systems.
-Lua is one of the most popular scripting languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
+Lua is one of the most popular scripting languages for embedded systems \cite{par:Lua}.
 Lua supports a co-routine, which is referred to as cooperative multitasking.
@@
 {\bf Squirrel:} Squirrel is an object-oriented programming language designed as a lightweight scripting language that satisfies the real-time requirements of applications.
-Squirrel was inspired by Lua.
+% Squirrel was inspired by Lua.
 The Squirrel API is very similar to Lua and the table code is based on that of Lua; Squirrel also supports co-routines.
@@
 mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
-In addition, software can be developed using CBD with mruby on TECS.
-Although multitasking has been supported in the current mruby on TECS, developers must be familiar with the functions of the RTOS to use multitasking.
-Co-routines are also supported by mruby on TECS.
+Moreover, TECS supports CBD.
+Although multitasking has been supported in the current mruby on TECS, it is not user-friendly for developers.
+% Co-routines are also supported by mruby on TECS.
 
-Table \ref{tab:comparison} compares the proposed framework to previous methods.
-The proposed framework implements all of the features shown in the table.
-In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
+% Table \ref{tab:comparison} compares the proposed framework to previous methods.
+% The proposed framework implements all of the features shown in the table.
+% In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
 
@@
 Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
-The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
-In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
+The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than co-routines for multitasking.
+Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
 
 The proposed framework is developed using CBD.
-In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
-Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
+The RiteVMs, the scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse them easily as required.
+Developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
 For software developed with priority-based scheduling, developers only have to remove the RiteVM scheduler.
 % Component-based development can increase productivity.
-Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.
+Note that our prototype system is open-source and can be downloaded from our website \cite{url:download}.
 
-In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin, and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
+In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin.
+% and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
 Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
@@
 %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgement}
-This work was supported by JSPS KAKENHI Grant Number 15H05305.
-We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
+% \section*{Acknowledgement}
+% This work was supported by JSPS KAKENHI Grant Number 15H05305.
+% We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{abbrv}
+\bibliographystyle{IEEEtranBST2/IEEEtran}
 \bibliography{ref}
 
+\newpage
+\appendices
+\section{mruby}
+mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
+It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+
+mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
+    \vspace{-2mm}
+    \caption{mruby/RiteVM mechanism}
+    \vspace{-2mm}
+    \label{fig:mruby}
+\end{figure}
+
+\section{TECS}
+TECS is a component system suitable for embedded systems.
+TECS can increase productivity and reduce development costs due to improved reusability of software components.
+TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+
+In TECS, component deployment and composition are performed statically.
+Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
+    \vspace{-2mm}
+    \caption{Component Diagram}
+    \vspace{-2mm}
+    \label{fig:component}
+\end{figure}
+
+\subsubsection{Component Model}
+Figure \ref{fig:component} shows a component diagram.
+A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
+An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+{\it Cell} functions are implemented in C.
+
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+
+\subsubsection{Component Description}
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% TECS code is written in CDL (component description language) file.
+These components are described as follows.
+
+\begin{description}
+    \item[{\bf Signature Description}]\mbox{}\\
+        The {\it signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+\begin{figure}[ht]
+\centering
+\begin{lstlisting}
+signature sMotor {
+    int32_t getCounts( void );
+    ER resetCounts( void );
+    ER setPower( [in]int power );
+    ER stop( [in] bool_t brake );
+    ER rotate( [in] int degrees, [in] uint32_t speed_abs,\\ [in] bool_t blocking );
+    void initializePort( [in]int32_t type );
+};
+\end{lstlisting}
+    \vspace{-2mm}
+\caption{Signature Description}
+    \vspace{-2mm}
+\label{signature}
+\end{figure}
+    \item[{\bf Celltype Description}]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+\begin{figure}[ht]
+\centering
+\begin{lstlisting}
+celltype tCaller {
+    call sMotor cMotor;
+};
+celltype tMotor {
+    entry sMotor eMotor;
+    attr { int32_t port; };
+    var { int32_t currentSpeed = 0; };
+};
+\end{lstlisting}
+    \vspace{-2mm}
+\caption{Celltype Description}
+    \vspace{-2mm}
+\label{celltype}
+\end{figure}
+    \item[{\bf Build Description}]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
+        Figure \ref{build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
+
+\begin{figure}[ht]
+\centering
+\begin{lstlisting}
+cell tMotor Motor {
+    port = C_EXP("PORT_A");
+};
+cell tCaller Caller {
+    cMotor = Motor.eMotor;
+};
+\end{lstlisting}
+    \vspace{-2mm}
+\caption{Build Description}
+    \vspace{-2mm}
+\label{build}
+\end{figure}
+
+\end{description}
+
+\section{mruby on TECS}
+\subsection{System Model}
+The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+TECS components support various embedded drivers such as motor and sensor drivers.
+
+An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+    \vspace{-2mm}
+\caption{System model of existing mruby on TECS}
+    \vspace{-2mm}
+\label{fig:mrubyontecs}
+\end{figure}
+
+\subsection{mruby-TECS Bridge}
+There is a significant difference between the execution times of mruby and C language codes.
+According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+Thus, it is difficult to use mruby exclusively.
+
+Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
+
+Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+The left side of BridgeMotor belongs to the mruby program.
+The right side of BridgeMotor belongs to TECS component.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+    \vspace{-2mm}
+\caption{mruby-TECS bridge}
+    \vspace{-2mm}
+\label{fig:mruby_TECS_bridge}
+\end{figure}
+
+The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+
+The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+
 \end{document}

### 2016-06-07 CPSNA2016/paper.tex
update CPSNA2016

@@
 \input{dummy/dummy.tex}
-\documentclass[conference]{IEEEtran/IEEEtran}
+\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
 \usepackage[dvipdfmx]{graphicx}
@@
 % \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
-\title{Efficient Development Framework with mruby for Embedded Systems}
+\title{Efficient Development Framework with mruby \\for Embedded Systems}
 \author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
@@
 \begin{abstract}
-Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
+Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale such by cyber physical systems.
 To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
@@
 
+% \keywords{embedded software; scripting language; component-based development}
+\begin{IEEEkeywords}
+embedded software; scripting language; component-based development
+\end{IEEEkeywords}
+
 \section{Introduction}
-Currently, embedded systems must demonstrate high quality and high performance.
+Currently, embedded systems such as Cyber Physical Systems must demonstrate high quality and high performance.
 This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
@@
 This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
-To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
+In the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device via Bluetooth.
 % Note that RiteVM is the Ruby VM specifically designed for embedded systems.
-The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., VMs designed for mruby) and allows developers to program multitasking more easily than the current version of mruby on TECS.
+The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., mruby VM) and allows developers to program multitasking more easily than the current version of mruby on TECS.
 
@@
 \label{sec:Bluetooth loader for mruby bytecode}
-This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader.\footnote{
+This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
 The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
@@
 
-\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
-The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
-This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
+\subsubsection{RiteVM Component with Bluetooth Loader}
+The proposed framework provides a RiteVM with a Bluetooth loader as a TECS component.
+This component is an extended RiteVM component described in \cite{par:mrubyonTECS}.
 It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
@@
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
-The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
-Bytecode on the host is transferred and received.
+The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader.
+Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
 In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
+The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.
 
@@
 
-Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
-The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.
-
 First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); line 4 in Figure \ref{maincode_mrubybluetooth}).
@@
 \subsection{Improving Development Efficiency by Bluetooth Loader}
-The Bluetooth loader for mruby bytecode can reduce the development time.
+The Bluetooth loader can reduce the development time.
 With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
@@
 The scheduler interrupts and switches tasks, which causes this overhead.
-It takes approximately 3 $\mu$sec on average to switch tasks once.
+% It takes approximately 3 $\mu$sec on average to switch tasks once.
 
@@
 \label{sec:Related work}
-Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 

### 2016-06-07 CPSNA2016/paper.tex
update CPSNA2016

@@
 \usepackage{amssymb}
+\usepackage{float}
 \usepackage{enumerate,cite,url}
@@
 % \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
-\title{Efficient Development Framework with mruby \\for Embedded Systems}
+\title{Efficient Development Framework with mruby\\for Embedded Systems}
 \author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
@@
 \begin{abstract}
-Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale such by cyber physical systems.
+Recently, the productivity of embedded systems applied to Cyber Physical Systems has become problematic due to their increasing complexity and scale.
 To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
 This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
-In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
+In the proposed framework, a Bluetooth loader which receives an mruby bytecode, and a RiteVM scheduler which simplifies multitasking are implemented.
 % In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
@@
 \section{Introduction}
-Currently, embedded systems such as Cyber Physical Systems must demonstrate high quality and high performance.
+Cyber Physical Systems (CPS) is the important keyword for enriching our lives.
+Embedded systems e.g., Internet of Things applications, are applied to the CPS and expected to demonstrate high quality and high performance.
 This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
@@
 Currently, most software are programmed in C language.
-However, development in C language results in large code size, incurs high costs, and requires significant development time.
+However, development in C language results in the large source code, incurs high costs, and requires significant development time.
 In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
@@
 With the proposed framework, only mruby applications are transferred, and the mruby libraries are preserved on the storage/ROM device beforehand.
-As a result, RiteVMs can share mruby libraries.
-In addition, a RiteVM can use its own library, which other RiteVMs should not use.
+% As a result, RiteVMs can share mruby libraries.
+% In addition, a RiteVM can use its own library, which other RiteVMs should not use.
 
@@
 The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader.
-Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
+Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader, such as RiteVMBluetooth1.
 In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
-The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.
+The main process of tRiteVMBluetooth is shown in Figure \ref{maincode_mrubybluetooth}.
 
@@
 \label{fig:control_flow}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-celltype tRiteVMBluetooth1 {
-    entry sTaskBody eMrubyBody;
-    [optional] call sEventflag cEventflag[];
-    [optional] call sSemaphore cSemaphore;
-    attr {
-      FLGPTN setPattern;
-      [omit]char_t *mrubyLib;
-      char_t *irepLib = C_EXP("&$cell_global$_irep");
-      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
-    };
-    var {
-        mrb_state *mrb;
-        mrbc_context *context;
-        [size_is(irepAppSize)] char_t *irepApp;
-    };
-};
-\end{lstlisting}
-    \vspace{-3mm}
-\caption{Celltype description for RiteVM with Bluetooth loader}
-    \vspace{-3mm}
-\label{celltype_mrubybluetooth}
 \end{figure}
@@
 
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+celltype tRiteVMBluetooth1 {
+    /* An entry port for tTask */
+    entry sTaskBody eMrubyBody;
+    /* A call port for Eventflag components */
+    [optional] call sEventflag cEventflag[];
+    /* A call port for a Semaphore component */
+    [optional] call sSemaphore cSemaphore;
+    attr {
+      [omit]char_t *mrubyLib;
+      char_t *irepLib = C_EXP("&$cell_global$_irep");
+    };
+    var {
+      mrb_state *mrb;
+      mrbc_context *context;
+      [size_is(irepAppSize)] char_t *irepApp;
+    };
+};
+\end{lstlisting}
+    \vspace{-3mm}
+\caption{Celltype description for RiteVM with Bluetooth loader}
+    \vspace{-3mm}
+\label{celltype_mrubybluetooth}
+\end{figure}
+
 First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); line 4 in Figure \ref{maincode_mrubybluetooth}).
@@
 
-Second, {\it mrb\_state} and {\it mrbc\_context} pointers (Figure \ref{fig:control_flow}(B); lines 7, 9 in Figure \ref{maincode_mrubybluetooth}).
-{\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
-{\it mrb\_state} is a set of states and global variables used in mruby.
-The synchronization of multiple tasks is performed in this processing phase.
-The RiteVM that finishes execution at this point waits for the another RiteVM to finish loading and initialization.
+Second, {\it mrb\_state} and {\it mrbc\_context} pointers are initialized (Figure \ref{fig:control_flow}(B); lines 7, 9 in Figure \ref{maincode_mrubybluetooth}).
+{\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}, and which are a set of states and global variables used in mruby.
+Note that the synchronization of multiple tasks is performed in this processing phase (Section \ref{sec:Synchronization of Multiple RiteVM Tasks}).
+% The RiteVM that finishes execution at this point waits for the another RiteVM to finish loading and initialization.
 
@@
 {\it irepLib} is the pointer of the array in which the bytecode of mruby libraries is stored.
-To summarize, the bytecode of mruby libraries is stored as an attribute of the component during the first compilation.
+To summarize, the bytecode of mruby libraries is stored as an attribute of the component (i.e., {\it irepLib}) during the first compilation.
 
@@
 The mruby application bytecode is stored in an array of {\it irepApp}.
-Note that two bytecodes, irepLib and irepApp, are read separately in the RiteVM.
-
-Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
-When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
+Here, {\it [size\_is()]} is the specifier for an array.
+Note that two bytecodes, {\it irepLib} and {\it irepApp}, are read separately in the RiteVM.
+
+Finally, the RiteVM runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
+When an mruby application is modified, only the bytecode of the application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
 % The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
@@
 After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
+In addition, the proposed framework supports the reset component which force applications stop and free, thus developers can transfer new bytecodes and run tasks.
 
@@
 
-\subsection{Improving Development Efficiency by Bluetooth Loader}
+{\bf Improving Development Efficiency by Bluetooth Loader}:
 The Bluetooth loader can reduce the development time.
@@
 In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
-The size, load process time, and compilation time for an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
-The overhead of load processing to load a zero byte bytecode is 50.933 msec.
-Similarly, compilation overhead to compile a zero byte program is 46.9 msec.
+To confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
+Loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
+Similarly, the overhead to compile a zero byte program is 46.9 msec.
 The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
@@
     \vspace{-2mm}
-\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
+\caption{Comparison between an application with and without libraries}
     \vspace{-2mm}
@@
 
-\subsection{RiteVM Scheduler}
+{\bf RiteVM Scheduler}:
 A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
+We decided a program with 100,000 loops as an mruby application for the evaluation of execution time.
 Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.
@@
 \end{figure}
-\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
-In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
-This shows that the proposed design is superior to co-routine in terms of execution time.
+\subsubsection{Execution Time of Singletasking, Co-routine, and Proposed Multitasking}
+Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to co-routine in terms of execution time.
 Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
 The scheduler interrupts and switches tasks, which causes this overhead.
+Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitasking and co-routine.
+Therefore, the scheduler enables developers multitasking as the more efficient approach than co-routine.
+Here, the periodic time of the scheduler is 1 msec.
 % It takes approximately 3 $\mu$sec on average to switch tasks once.
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
+{\bf Synchronization of Multiple RiteVM Tasks}:
 To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
@@
 
-\subsection{Benefits of Component-Based Development}
+{\bf Benefits of Component-Based Development}:
 In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
@@
 %\subsubsection{Code size utilizing component-based development}
-To demonstrate the superiority of CBD, a comparison of the number of lines of codes between two C and CDL files is shown in Table \ref{tab:codesize}.
+To demonstrate the superiority of CBD, a comparison of the number of lines of C and CDL codes between two situations is shown in Table \ref{tab:codesize}.
 In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Figure \ref{fig:Eventflag}, respectively. 
 For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
-Note that (B)'s C file can be utilized without modification regardless of the number of RiteVMs.
-Moreover, the number of code lines of two CDL files are equal.
+Moreover, (B)'s C file can be utilized without modification regardless of the number of RiteVMs, while the number of code lines of two CDL files are equal.
 Skillful CBD yields advantages such as the decreased number of lines of codes and non-modified codes, which facilitates high productivity and maintainability.
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
+    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
     \vspace{-2mm}
@@
     \caption{Component Diagram}
-    \vspace{-2mm}
+    \vspace{-5mm}
     \label{fig:component}
@@
 
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
-
-\subsubsection{Component Description}
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
-These components are described as follows.
-
-\begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
-        The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
-\begin{figure}[ht]
+\begin{figure}[H]
 \centering
@@
 signature sMotor {
-    int32_t getCounts( void );
-    ER resetCounts( void );
     ER setPower( [in]int power );
     ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees, [in] uint32_t speed_abs,\\ [in] bool_t blocking );
     void initializePort( [in]int32_t type );
@@
 \caption{Signature Description}
-    \vspace{-2mm}
+    \vspace{-5mm}
 \label{signature}
 \end{figure}
-    \item[{\bf Celltype Description}]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
-        {\it Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
-\begin{figure}[ht]
+
+\begin{figure}[H]
 \centering
@@
 \caption{Celltype Description}
-    \vspace{-2mm}
+    \vspace{-5mm}
 \label{celltype}
 \end{figure}
-    \item[{\bf Build Description}]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
-        {\it C\_EXP} calls macros defined in C files.
-
-\begin{figure}[ht]
+
+\begin{figure}[H]
 \centering
@@
 
-\end{description}
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+
+\subsubsection{Component Description}
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% TECS code is written in CDL (component description language) file.
+These components are described as follows.
+
+% \begin{description}
+    %\item[
+    {\bf Signature Description:\ }%]\mbox{}\\
+        {\it Signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+
+    %\item[
+    {\bf Celltype Description:\ }%]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+
+    %\item[
+    {\bf Build Description:\ }%]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
+        Figure \ref{build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
+
+% \end{description}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering
@@
 The right side of BridgeMotor belongs to TECS component.
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering

### 2016-06-09 CPSNA2016/paper.tex
update CPSNA2016

@@
 % \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
-\title{Efficient Development Framework with mruby\\for Embedded Systems}
+\title{Lightweight Ruby Framework for Improving Embedded Software Efficiency}
+% \title{Efficient Development Framework with mruby\\for Embedded Systems}
 \author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
@@
 Recently, the productivity of embedded systems applied to Cyber Physical Systems has become problematic due to their increasing complexity and scale.
-To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
+To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., a lightweight Ruby) and supports component-based development, has been proposed.
 This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
@@
 % Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
-Experimental results demonstrate the advantages of the proposed framework.
+% Experimental results demonstrate the advantages of the proposed framework.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-embedded software; scripting language; component-based development
+scripting language; cyber physical systems; embedded software; component-based development
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Cyber Physical Systems (CPS) is the important keyword for enriching our lives.
+Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
 Embedded systems e.g., Internet of Things applications, are applied to the CPS and expected to demonstrate high quality and high performance.
@@
 % mruby on TECS also makes execution time 100 times faster than that of mruby.
-
 %This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
-Even though execution times of mruby on TECS are 100 times faster than those of mruby, it is not particularly efficient, at present, and imposes a heavy burden on developers.
+Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
+Moreover, Ruby is often utilized in network programming, therefore the framework can be applicable for the software involved network such as CPS applications.
+
+However, it is not particularly efficient, at present, and imposes a heavy burden on developers.
 mruby on TECS only supports a storage/ROM device for loading mruby programs.
@@
 \begin{enumerate}
-    \vspace{-2mm}
+    % \vspace{-2mm}
 \item {\bf Improved software development efficiency.}
@@
 The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
-\item {\bf Benefits of CBD:}
-The paper focuses on the benefits of CBD and provides specific examples.
-    \vspace{-2mm}
+\item {\bf Benefits of CBD.}
+The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
+    % \vspace{-2mm}
 \end{enumerate}
@@
 The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
-Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
+Note that the completed software production should be compiled and linked on the storage/ROM device beforehand.
 }
@@
 The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
+An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
+The proposed loader novelly supports a load of bytecodes.
 
@@
 
-We evaluated to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
+We evaluated to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to existing multitask processing or co-routine, and that the initiation of mruby applications are synchronized.
 In addition, we focused on benefits of CBD.
@@
 
-{\bf Improving Development Efficiency by Bluetooth Loader}:
+{\bf Improving Development Efficiency by Bluetooth Loader.}
 The Bluetooth loader can reduce the development time.
@@
 
-{\bf RiteVM Scheduler}:
-A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-We decided a program with 100,000 loops as an mruby application for the evaluation of execution time.
-Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
+{\bf RiteVM Scheduler.}
+A comparison of the application execution time with singletask, proposed, existing multitask, and co-routine is shown in Figure \ref{fig:comparison_s_c_m}.
+We applied a program with 100,000 loops as an mruby application for the evaluation of execution time so that the overhead comes out.
+Here, in the multitask and co-routine, we prepared two tasks and the programs looped 50,000 times for each task.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
     \vspace{-3mm}
@@
     \centering
-    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
+    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
     \vspace{-3mm}
@@
 \end{figure}
-\subsubsection{Execution Time of Singletasking, Co-routine, and Proposed Multitasking}
-Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to co-routine in terms of execution time.
+\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
+Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
 Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
 The scheduler interrupts and switches tasks, which causes this overhead.
-Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitasking and co-routine.
-Therefore, the scheduler enables developers multitasking as the more efficient approach than co-routine.
+Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
+Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
 Here, the periodic time of the scheduler is 1 msec.
@@
     \centering
-    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/eval_synchronization.eps}
+    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/eval_synchronization.eps}
     \vspace{-3mm}
@@
 
-{\bf Synchronization of Multiple RiteVM Tasks}:
+{\bf Synchronization of Multiple RiteVM Tasks.}
 To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
@@
 
-{\bf Benefits of Component-Based Development}:
+{\bf Benefits of Component-Based Development.}
 In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
@@
         \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
+        \vspace{-3mm}
     \end{tabular}
@@
 
-{\bf mruby:} mruby, a lightweight implementation of the Ruby language, has been proposed for embedded systems.
-mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
+{\bf mruby:} mruby, a lightweight Ruby, has been proposed for embedded systems.
+mruby programs can run on a RiteVM which reads the mruby bytecode.
 Note that the RiteVM only supports a single thread.
@@
 Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
-The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than co-routines for multitasking.
+The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than the existing technique and co-routines for multitasking.
 Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
@@
 
-\newpage
+\clearpage
 \appendices

### 2016-06-10 CPSNA2016/paper.tex
update CPSNA2016

@@
 An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
-The proposed loader novelly supports a load of bytecodes.
+The proposed loader newly supports a load of bytecodes.
 
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
+    \includegraphics[height=1.8cm,width=8.6cm,clip]{figure/cyclic_handler.eps}
     \vspace{-3mm}
@@
 Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
+The {\it delay} function and co-routine method run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
+The scheduler runs as the periodic handler of RTOS.
 Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
@@
 Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
-Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
+% Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
 Here, the periodic time of the scheduler is 1 msec.

### 2016-06-10 CPSNA2016/paper.tex
update CPSNA2016

@@
 Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
-Embedded systems e.g., Internet of Things applications, are applied to the CPS and expected to demonstrate high quality and high performance.
+Embedded systems are applied to the CPS and expected to demonstrate high quality and high performance.
 This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
@@
 Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
-Moreover, Ruby is often utilized in network programming, therefore the framework can be applicable for the software involved network such as CPS applications.
+Moreover, Ruby is often utilized in network programming, therefore mruby on TECS can be applicable for the software involved network such as CPS applications.
 
@@
 \label{sec:System Model}
-The proposed framework is an extended framework of mruby on TECS, and utilizes mruby and TECS.
-These basic technologies are described in appendix of this paper.
+The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
+mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.
 
@@
 The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
-Note that the completed software production should be compiled and linked on the storage/ROM device beforehand.
+Note that the bytecode after the development phase should be compiled and linked on the storage/ROM device beforehand.
 }
@@
 An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
-The proposed loader newly supports a load of bytecodes.
+The proposed loader newly supports a load for bytecodes of scripting languages.
 
@@
 Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
-The {\it delay} function and co-routine method run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
+The {\it delay} and co-routine methods run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
 The scheduler runs as the periodic handler of RTOS.
@@
 Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
-% Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
+Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
 Here, the periodic time of the scheduler is 1 msec.
@@
 \section{mruby}
+\label{apn:mruby}
 mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
@@
 The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
-\begin{figure}[h]
+\begin{figure}[b]
     \centering
     \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
-    \vspace{-2mm}
+    \vspace{-3mm}
     \caption{mruby/RiteVM mechanism}
-    \vspace{-2mm}
+    \vspace{-3mm}
     \label{fig:mruby}
@@
 \section{TECS}
+\label{apn:TECS}
 TECS is a component system suitable for embedded systems.
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
     \centering
@@
 {\it Cell} functions are implemented in C.
+
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+
+\subsubsection{Component Description}
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% TECS code is written in CDL (component description language) file.
+These components are described as follows.
+
+% \begin{description}
+    %\item[
+    {\bf Signature Description:\ }%]\mbox{}\\
+        {\it Signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+
+    %\item[
+    {\bf Celltype Description:\ }%]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+
+    %\item[
+    {\bf Build Description:\ }%]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
+        Figure \ref{build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
+
+% \end{description}
 
@@
 \end{figure}
-
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
-
-\subsubsection{Component Description}
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
-These components are described as follows.
-
-% \begin{description}
-    %\item[
-    {\bf Signature Description:\ }%]\mbox{}\\
-        {\it Signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
-
-    %\item[
-    {\bf Celltype Description:\ }%]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
-        {\it Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
-
-    %\item[
-    {\bf Build Description:\ }%]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
-        {\it C\_EXP} calls macros defined in C files.
-
-% \end{description}
-
-\section{mruby on TECS}
-\subsection{System Model}
-The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
-Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
-TECS components support various embedded drivers such as motor and sensor drivers.
-
-An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
-The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
-% In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
-    \vspace{-2mm}
-\caption{System model of existing mruby on TECS}
-    \vspace{-2mm}
-\label{fig:mrubyontecs}
-\end{figure}
-
-\subsection{mruby-TECS Bridge}
-There is a significant difference between the execution times of mruby and C language codes.
-According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
-Thus, it is difficult to use mruby exclusively.
-
-Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
-However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
-% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
-
-Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
-The left side of BridgeMotor belongs to the mruby program.
-The right side of BridgeMotor belongs to TECS component.
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
-    \vspace{-2mm}
-\caption{mruby-TECS bridge}
-    \vspace{-2mm}
-\label{fig:mruby_TECS_bridge}
-\end{figure}
-
-The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-
-The generated mruby-TECS bridge supports registration of classes and methods for mruby.
-Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
-
+% \section{mruby on TECS}
+% \subsection{System Model}
+% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+% TECS components support various embedded drivers such as motor and sensor drivers.
+%
+% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
+%
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+%     \vspace{-2mm}
+% \caption{System model of existing mruby on TECS}
+%     \vspace{-2mm}
+% \label{fig:mrubyontecs}
+% \end{figure}
+%
+% \subsection{mruby-TECS Bridge}
+% There is a significant difference between the execution times of mruby and C language codes.
+% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+% Thus, it is difficult to use mruby exclusively.
+%
+% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
+%
+% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+% The left side of BridgeMotor belongs to the mruby program.
+% The right side of BridgeMotor belongs to TECS component.
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+%     \vspace{-2mm}
+% \caption{mruby-TECS bridge}
+%     \vspace{-2mm}
+% \label{fig:mruby_TECS_bridge}
+% \end{figure}
+%
+% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+%
+% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+%
 \end{document}

### 2016-08-16 CPSNA2016/short_paper.tex
add short_paper

--- 2016-06-10 CPSNA2016/paper.tex
@@
 \begin{abstract}
-Recently, the productivity of embedded systems applied to Cyber Physical Systems has become problematic due to their increasing complexity and scale.
+Recently, the productivity of embedded systems applied to Cyber physical systems has become problematic due to their increasing complexity and scale.
 To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., a lightweight Ruby) and supports component-based development, has been proposed.
-This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
-In the proposed framework, a Bluetooth loader which receives an mruby bytecode, and a RiteVM scheduler which simplifies multitasking are implemented.
+This paper proposes an extended framework of mruby on TECS that improves development efficiency more than the current version.
+In the proposed framework, a Bluetooth loader that receives an mruby bytecode, and a RiteVM scheduler that simplifies multitasking are implemented.
 % In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
@@
 \section{Introduction}
-Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
-Embedded systems are applied to the CPS and expected to demonstrate high quality and high performance.
+Cyber Physical Systems (CPS) are important keywords for enriching our lives.
+Embedded systems are applied to the CPS and are expected to demonstrate high quality and performance.
 This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
@@
 Currently, most software are programmed in C language.
-However, development in C language results in the large source code, incurs high costs, and requires significant development time.
+However, development in C language results in a large source code, incurs high costs, and requires significant development time.
 In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
@@
 %This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
-Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
-Moreover, Ruby is often utilized in network programming, therefore mruby on TECS can be applicable for the software involved network such as CPS applications.
-
-However, it is not particularly efficient, at present, and imposes a heavy burden on developers.
+The execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of the C language.
+Moreover, Ruby is often used in network programming; therefore, mruby on TECS can be applicable for the software involved networks such as CPS applications.
+
+However, at present, mruby on TECS is not particularly efficient, and imposes a heavy burden on developers.
 mruby on TECS only supports a storage/ROM device for loading mruby programs.
-Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
+Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or the ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
 In addition, although mruby on TECS can support multi-VM, executing multiple tasks requires the developers to call the OS function.
@@
 The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
-\item {\bf Benefits of CBD.}
+\item {\bf Benefits of CBD:}
 The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
@@
 
-{\bf Organization}: The reminder of this paper is organized as follows.
+{\bf Organization}: The remainder of this paper is organized as follows.
 Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
@@
 \label{sec:System Model}
-The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
-mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.
+The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS, which are also described in \cite{par:mrubyonTECS}.
 
@@
 The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
-An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
+An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} can support a load of object files.
 The proposed loader newly supports a load for bytecodes of scripting languages.
@@
 The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
-This process is exclusively carried out by the semaphore to prevent the other loading from interrupting.
+This process is exclusively carried out by the semaphore in order to prevent the other loading from interrupting.
 
@@
 After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
-In addition, the proposed framework supports the reset component which force applications stop and free, thus developers can transfer new bytecodes and run tasks.
+In addition, the proposed framework supports the reset component that forces applications to stop and free; enabling developers to transfer new bytecodes and run tasks.
 
@@
 \subsubsection{RiteVM Scheduler Design}
-Here, assumed that two tasks with equal priority are in an infinite loop.
- In the current system, when one task is executed first, the other task would not be executed because the first task runs in the loop.
+Here, assume that two tasks with equal priority are in an infinite loop.
+In the current system, when one task is executed, the other task does not get executed because the first task runs in a loop.
 
@@
 
-We evaluated to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to existing multitask processing or co-routine, and that the initiation of mruby applications are synchronized.
-In addition, we focused on benefits of CBD.
+We demonstrated that a Bluetooth loader can improve the efficiency of software development and that the proposed multitask processing executes effectively compared with existing multitask processing or co-routine.
+In addition, the initiation of mruby applications is synchronized.
+Moreover, we focused on the benefits of CBD.
 We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
 
-{\bf Improving Development Efficiency by Bluetooth Loader.}
+{\bf Improving Development Efficiency by Bluetooth Loader:}
 The Bluetooth loader can reduce the development time.
@@
 In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
-To confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
-Loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
+In order to confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
+The loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
 Similarly, the overhead to compile a zero byte program is 46.9 msec.
@@
 Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
-The {\it delay} and co-routine methods run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
+The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
 The scheduler runs as the periodic handler of RTOS.
@@
 The scheduler interrupts and switches tasks, which causes this overhead.
-Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
+Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
 Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
@@
 
-{\bf Synchronization of Multiple RiteVM Tasks.}
+{\bf Synchronization of Multiple RiteVM Tasks:}
 To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
@@
 
-{\bf Benefits of Component-Based Development.}
+{\bf Benefits of Component-Based Development:}
 In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
@@
 
-\clearpage
-\appendices
-\section{mruby}
-\label{apn:mruby}
-mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
-Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
-It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
-Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
-
-mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
-In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
-The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
-\begin{figure}[b]
-    \centering
-    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
-    \vspace{-3mm}
-    \caption{mruby/RiteVM mechanism}
-    \vspace{-3mm}
-    \label{fig:mruby}
-\end{figure}
-
-\section{TECS}
-\label{apn:TECS}
-TECS is a component system suitable for embedded systems.
-TECS can increase productivity and reduce development costs due to improved reusability of software components.
-TECS also provides component diagrams, which help developers visualize the overall structure of a system.
-
-In TECS, component deployment and composition are performed statically.
-Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
-
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
-    \vspace{-2mm}
-    \caption{Component Diagram}
-    \vspace{-5mm}
-    \label{fig:component}
-\end{figure}
-
-\subsubsection{Component Model}
-Figure \ref{fig:component} shows a component diagram.
-A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
-An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
-{\it Cell} functions are implemented in C.
-
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
-
-\subsubsection{Component Description}
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
-These components are described as follows.
-
-% \begin{description}
-    %\item[
-    {\bf Signature Description:\ }%]\mbox{}\\
-        {\it Signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
-
-    %\item[
-    {\bf Celltype Description:\ }%]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
-        {\it Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
-
-    %\item[
-    {\bf Build Description:\ }%]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
-        {\it C\_EXP} calls macros defined in C files.
-
-% \end{description}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-signature sMotor {
-    ER setPower( [in]int power );
-    ER stop( [in] bool_t brake );
-    void initializePort( [in]int32_t type );
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Signature Description}
-    \vspace{-5mm}
-\label{signature}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-celltype tCaller {
-    call sMotor cMotor;
-};
-celltype tMotor {
-    entry sMotor eMotor;
-    attr { int32_t port; };
-    var { int32_t currentSpeed = 0; };
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Celltype Description}
-    \vspace{-5mm}
-\label{celltype}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-cell tMotor Motor {
-    port = C_EXP("PORT_A");
-};
-cell tCaller Caller {
-    cMotor = Motor.eMotor;
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Build Description}
-    \vspace{-2mm}
-\label{build}
-\end{figure}
-% \section{mruby on TECS}
-% \subsection{System Model}
-% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
-% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
-% TECS components support various embedded drivers such as motor and sensor drivers.
-%
-% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
-% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
-% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
-%
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+% \clearpage
+% \appendices
+% \section{mruby}
+% \label{apn:mruby}
+% mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+% Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
+% It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+% Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+%
+% mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+% In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+% The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+% The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
+% \begin{figure}[b]
+%     \centering
+%     \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
+%     \vspace{-3mm}
+%     \caption{mruby/RiteVM mechanism}
+%     \vspace{-3mm}
+%     \label{fig:mruby}
+% \end{figure}
+%
+% \section{TECS}
+% \label{apn:TECS}
+% TECS is a component system suitable for embedded systems.
+% TECS can increase productivity and reduce development costs due to improved reusability of software components.
+% TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+%
+% In TECS, component deployment and composition are performed statically.
+% Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+% TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+%
+% \begin{figure}[b]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
 %     \vspace{-2mm}
-% \caption{System model of existing mruby on TECS}
+%     \caption{Component Diagram}
+%     \vspace{-5mm}
+%     \label{fig:component}
+% \end{figure}
+%
+% \subsubsection{Component Model}
+% Figure \ref{fig:component} shows a component diagram.
+% A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
+% An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+% A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+% {\it Cell} functions are implemented in C.
+%
+%
+% The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+% A {\it signature} is the interface definition of a {\it cell}.
+% The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+% Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+%
+%
+% \subsubsection{Component Description}
+% In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% % TECS code is written in CDL (component description language) file.
+% These components are described as follows.
+%
+% % \begin{description}
+%     %\item[
+%     {\bf Signature Description:\ }%]\mbox{}\\
+%         {\it Signature} defines a {\it cell} interface.
+%         The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+%         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+%
+%     %\item[
+%     {\bf Celltype Description:\ }%]\mbox{}\\
+%         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+%         A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+%         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+%         {\it Call} ports are defined similarly.
+%         Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+%     
+%     %\item[
+%     {\bf Build Description:\ }%]\mbox{}\\
+%         The build description is used to instantiate and connect {\it cell}s.
+%         Figure \ref{build} shows an example of a build description.
+%         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+%         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+%         In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+%         {\it C\_EXP} calls macros defined in C files.
+%         
+% % \end{description} 
+%
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% signature sMotor {
+%     ER setPower( [in]int power );
+%     ER stop( [in] bool_t brake );
+%     void initializePort( [in]int32_t type );
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \label{fig:mrubyontecs}
-% \end{figure}
-%
-% \subsection{mruby-TECS Bridge}
-% There is a significant difference between the execution times of mruby and C language codes.
-% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
-% Thus, it is difficult to use mruby exclusively.
-%
-% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
-% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
-% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
-%
-% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
-% The left side of BridgeMotor belongs to the mruby program.
-% The right side of BridgeMotor belongs to TECS component.
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+% \caption{Signature Description}
+%     \vspace{-5mm}
+% \label{signature}
+% \end{figure}
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% celltype tCaller {
+%     call sMotor cMotor;
+% };
+% celltype tMotor {
+%     entry sMotor eMotor;
+%     attr { int32_t port; };
+%     var { int32_t currentSpeed = 0; };
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \caption{mruby-TECS bridge}
+% \caption{Celltype Description}
+%     \vspace{-5mm}
+% \label{celltype}
+% \end{figure}
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% cell tMotor Motor {
+%     port = C_EXP("PORT_A");
+% };
+% cell tCaller Caller {
+%     cMotor = Motor.eMotor;
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \label{fig:mruby_TECS_bridge}
-% \end{figure}
-%
-% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-%
-% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
-% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
-%
+% \caption{Build Description}
+%     \vspace{-2mm}
+% \label{build}
+% \end{figure}
+% % \section{mruby on TECS}
+% % \subsection{System Model}
+% % The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+% % Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+% % TECS components support various embedded drivers such as motor and sensor drivers.
+% %
+% % An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+% % The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% % % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+% % mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
+% %
+% % \begin{figure}[t]
+% %     \centering
+% %     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+% %     \vspace{-2mm}
+% % \caption{System model of existing mruby on TECS}
+% %     \vspace{-2mm}
+% % \label{fig:mrubyontecs}
+% % \end{figure}
+% %
+% % \subsection{mruby-TECS Bridge}
+% % There is a significant difference between the execution times of mruby and C language codes.
+% % According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+% % Thus, it is difficult to use mruby exclusively.
+% %
+% % Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+% % However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% % % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
+% %
+% % Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+% % The left side of BridgeMotor belongs to the mruby program.
+% % The right side of BridgeMotor belongs to TECS component.
+% % \begin{figure}[t]
+% %     \centering
+% %     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+% %     \vspace{-2mm}
+% % \caption{mruby-TECS bridge}
+% %     \vspace{-2mm}
+% % \label{fig:mruby_TECS_bridge}
+% % \end{figure}
+% %
+% % The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+% %
+% % The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+% % Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+% % Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+% %
 \end{document}

### 2016-10-20 CPSNA2016/enago/paper.tex
adjust

--- 2016-06-10 CPSNA2016/paper.tex
@@
 Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
-
-%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Acknowledgement}
-% This work was supported by JSPS KAKENHI Grant Number 15H05305.
-% We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
-%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtranBST2/IEEEtran}
-\bibliography{ref}
-
-\clearpage
-\appendices
-\section{mruby}
-\label{apn:mruby}
-mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
-Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
-It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
-Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
-
-mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
-In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
-The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
-The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
-\begin{figure}[b]
-    \centering
-    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
-    \vspace{-3mm}
-    \caption{mruby/RiteVM mechanism}
-    \vspace{-3mm}
-    \label{fig:mruby}
-\end{figure}
-
-\section{TECS}
-\label{apn:TECS}
-TECS is a component system suitable for embedded systems.
-TECS can increase productivity and reduce development costs due to improved reusability of software components.
-TECS also provides component diagrams, which help developers visualize the overall structure of a system.
-
-In TECS, component deployment and composition are performed statically.
-Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
-
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
-    \vspace{-2mm}
-    \caption{Component Diagram}
-    \vspace{-5mm}
-    \label{fig:component}
-\end{figure}
-
-\subsubsection{Component Model}
-Figure \ref{fig:component} shows a component diagram.
-A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
-An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
-{\it Cell} functions are implemented in C.
-
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
-
-\subsubsection{Component Description}
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
-These components are described as follows.
-
-% \begin{description}
-    %\item[
-    {\bf Signature Description:\ }%]\mbox{}\\
-        {\it Signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
-
-    %\item[
-    {\bf Celltype Description:\ }%]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
-        {\it Call} ports are defined similarly.
-        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
-
-    %\item[
-    {\bf Build Description:\ }%]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
-        {\it C\_EXP} calls macros defined in C files.
-
-% \end{description}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-signature sMotor {
-    ER setPower( [in]int power );
-    ER stop( [in] bool_t brake );
-    void initializePort( [in]int32_t type );
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Signature Description}
-    \vspace{-5mm}
-\label{signature}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-celltype tCaller {
-    call sMotor cMotor;
-};
-celltype tMotor {
-    entry sMotor eMotor;
-    attr { int32_t port; };
-    var { int32_t currentSpeed = 0; };
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Celltype Description}
-    \vspace{-5mm}
-\label{celltype}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\begin{lstlisting}
-cell tMotor Motor {
-    port = C_EXP("PORT_A");
-};
-cell tCaller Caller {
-    cMotor = Motor.eMotor;
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{Build Description}
-    \vspace{-2mm}
-\label{build}
-\end{figure}
-% \section{mruby on TECS}
-% \subsection{System Model}
-% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
-% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
-% TECS components support various embedded drivers such as motor and sensor drivers.
-%
-% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
-% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
-% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
-% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
-%
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+%
+% %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % \section*{Acknowledgement}
+% % This work was supported by JSPS KAKENHI Grant Number 15H05305.
+% % We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
+% %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \bibliographystyle{IEEEtranBST2/IEEEtran}
+% \bibliography{ref}
+%
+%
+% \clearpage
+% \appendices
+% \section{mruby}
+% \label{apn:mruby}
+% mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+% Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
+% It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+% Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+%
+% mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+% In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+% The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+% The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
+% \begin{figure}[b]
+%     \centering
+%     \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
+%     \vspace{-3mm}
+%     \caption{mruby/RiteVM mechanism}
+%     \vspace{-3mm}
+%     \label{fig:mruby}
+% \end{figure}
+%
+% \section{TECS}
+% \label{apn:TECS}
+% TECS is a component system suitable for embedded systems.
+% TECS can increase productivity and reduce development costs due to improved reusability of software components.
+% TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+%
+% In TECS, component deployment and composition are performed statically.
+% Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+% TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+%
+% \begin{figure}[b]
+%     \centering
+%     \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
 %     \vspace{-2mm}
-% \caption{System model of existing mruby on TECS}
+%     \caption{Component Diagram}
+%     \vspace{-5mm}
+%     \label{fig:component}
+% \end{figure}
+%
+% \subsubsection{Component Model}
+% Figure \ref{fig:component} shows a component diagram.
+% A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
+% An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+% A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+% {\it Cell} functions are implemented in C.
+%
+%
+% The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+% A {\it signature} is the interface definition of a {\it cell}.
+% The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+% Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
+%
+%
+% \subsubsection{Component Description}
+% In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% % TECS code is written in CDL (component description language) file.
+% These components are described as follows.
+%
+% % \begin{description}
+%     %\item[
+%     {\bf Signature Description:\ }%]\mbox{}\\
+%         {\it Signature} defines a {\it cell} interface.
+%         The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+%         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+%
+%     %\item[
+%     {\bf Celltype Description:\ }%]\mbox{}\\
+%         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+%         A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+%         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+%         {\it Call} ports are defined similarly.
+%         Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+%     
+%     %\item[
+%     {\bf Build Description:\ }%]\mbox{}\\
+%         The build description is used to instantiate and connect {\it cell}s.
+%         Figure \ref{build} shows an example of a build description.
+%         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+%         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+%         In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+%         {\it C\_EXP} calls macros defined in C files.
+%         
+% % \end{description} 
+%
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% signature sMotor {
+%     ER setPower( [in]int power );
+%     ER stop( [in] bool_t brake );
+%     void initializePort( [in]int32_t type );
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \label{fig:mrubyontecs}
-% \end{figure}
-%
-% \subsection{mruby-TECS Bridge}
-% There is a significant difference between the execution times of mruby and C language codes.
-% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
-% Thus, it is difficult to use mruby exclusively.
-%
-% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
-% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
-% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
-%
-% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
-% The left side of BridgeMotor belongs to the mruby program.
-% The right side of BridgeMotor belongs to TECS component.
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+% \caption{Signature Description}
+%     \vspace{-5mm}
+% \label{signature}
+% \end{figure}
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% celltype tCaller {
+%     call sMotor cMotor;
+% };
+% celltype tMotor {
+%     entry sMotor eMotor;
+%     attr { int32_t port; };
+%     var { int32_t currentSpeed = 0; };
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \caption{mruby-TECS bridge}
+% \caption{Celltype Description}
+%     \vspace{-5mm}
+% \label{celltype}
+% \end{figure}
+%
+% \begin{figure}[H]
+% \centering
+% \begin{lstlisting}
+% cell tMotor Motor {
+%     port = C_EXP("PORT_A");
+% };
+% cell tCaller Caller {
+%     cMotor = Motor.eMotor;
+% };
+% \end{lstlisting}
 %     \vspace{-2mm}
-% \label{fig:mruby_TECS_bridge}
-% \end{figure}
-%
-% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-%
-% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
-% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
-% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
-%
+% \caption{Build Description}
+%     \vspace{-2mm}
+% \label{build}
+% \end{figure}
+% % \section{mruby on TECS}
+% % \subsection{System Model}
+% % The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+% % Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+% % TECS components support various embedded drivers such as motor and sensor drivers.
+% %
+% % An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+% % The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+% % % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
+% % mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
+% %
+% % \begin{figure}[t]
+% %     \centering
+% %     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
+% %     \vspace{-2mm}
+% % \caption{System model of existing mruby on TECS}
+% %     \vspace{-2mm}
+% % \label{fig:mrubyontecs}
+% % \end{figure}
+% %
+% % \subsection{mruby-TECS Bridge}
+% % There is a significant difference between the execution times of mruby and C language codes.
+% % According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+% % Thus, it is difficult to use mruby exclusively.
+% %
+% % Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+% % However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+% % % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
+% %
+% % Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+% % The left side of BridgeMotor belongs to the mruby program.
+% % The right side of BridgeMotor belongs to TECS component.
+% % \begin{figure}[t]
+% %     \centering
+% %     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
+% %     \vspace{-2mm}
+% % \caption{mruby-TECS bridge}
+% %     \vspace{-2mm}
+% % \label{fig:mruby_TECS_bridge}
+% % \end{figure}
+% %
+% % The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+% %
+% % The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+% % Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+% % Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+% %
 \end{document}

### 2016-10-20 CPSNA2016/paper.tex
adjust

@@
 The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
-\item {\bf Benefits of CBD.}
-The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
+\item {\bf Benefits of CBD:}
+The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a scheduler, and Eventflags).
     % \vspace{-2mm}
@@
 \label{sec:System Model}
-The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
-mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.
+The proposed framework is an extension of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS, which are described in Appendices \ref{apn:mruby} and \ref{apn:TECS}.
 

### 2016-10-20 CPSNA2016/short_paper.tex
adjust

@@
 \input{dummy/dummy.tex}
-\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
+%\documentclass[10pt, conference, compsocconf]{IEEEtran/IEEEtran}
+\documentclass[10pt, conference]{IEEEtran/IEEEtran}
 \usepackage[dvipdfmx]{graphicx}
@@
 \item {\bf Benefits of CBD:}
-The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
+The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a scheduler, and Eventflags).
     % \vspace{-2mm}
@@
 \label{sec:System Model}
-The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS, which are also described in \cite{par:mrubyonTECS}.
+The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS\footnote{mruby, TECS, and mruby on TECS are described in detail in \cite{par:mrubyonTECS}}.
 
@@
 \label{sec:Related work}
-Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
-
-{\bf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
+Open-source runtime systems for scripting languages have been proposed such p14p \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+
+{\bf p14p:} p14p is a Python runtime system that uses a reduced Python VM called PyMite.
 The VM runs a significant subset of the Python language with few resources on a microcontroller.
@@
 The Owl toolchain produces relocatable memory images that are directly runnable on the microcontroller from Python code objects.
-Note that the Owl system interpreter is the same as that of python-on-a-chip.
+Note that the Owl system interpreter is the same as that of p14p.
 
@@
 The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is more effective than the existing technique and co-routines for multitasking.
-Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
+% Moreover, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
+Moreover, multiple RiteVM tasks are synchronized.
 
@@
 %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Acknowledgement}
-% This work was supported by JSPS KAKENHI Grant Number 15H05305.
+\section*{Acknowledgement}
+This work was supported by JSPS KAKENHI Grant Number 15H05305.
 % We thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
+\vspace{-3mm}
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{IEEEtranBST2/IEEEtran}
+\bibliographystyle{IEEEtran/IEEEtranBST/IEEEtran}
 \bibliography{ref}

### 2016-10-20 jssst/paper.tex
adjust

--- 2016-04-08 EMSOFT2016/paper.tex
@@
+% Sample file for the use of compsoft style file.
 %
-% File: thesis.tex
-% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
-% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
+\documentclass[S,R,E]{article/compsoft}
+
+% Preamble
 %
-\input{dummy/dummy.tex}
-\documentclass{sig-alternate-05-2015}
-%\usepackage[dvipdfmx]{graphicx}
+% 「コンピュータソフトウェア」誌に掲載される論文の場合，次で
+% 巻数，号数，開始ページ，終了ページを指定する．
+\volNoPp{29}{1}{78}{84}
+
+% ワークショップによる推薦論文の場合，ワークショップ名を指定する．
+% \suisen{ワークショップ名}
+
+% 特集の場合，特集のタイトルを与える．
+% \tokushu{特集のタイトル}
+
+% 大会論文の場合，¥taikai で開催年を指定する．ここで指定した年から
+% 大会の回数は計算される．
+% \taikai{2009}
+
+% ここに，使用するパッケージを列挙する．
+%\usepackage[dvips]{graphics}
+\usepackage[dvipdfmx]{graphicx}
 \usepackage{amssymb}
+\usepackage{float}
 \usepackage{enumerate,cite,url}
@@
     numbersep=1zw,%
-    %lineskip=-0.5ex%
+    lineskip=-0.5ex%
 }
 
-% Copyright
-\setcopyright{acmcopyright}
-% DOI
-\doi{10.475/123_4}
-% ISBN
-\isbn{123-4567-24-567/08/06}
-%Conference
-\conferenceinfo{EMSOFT '16}{October 2--7, 2016, Pittsburgh, USA}
-\acmPrice{\$15.00}
-
-\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
-\numberofauthors{3}
-\author{
-\alignauthor
-Takuro Yamamoto\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Wallamaloo, New Zealand}\\
-       % \email{trovato@corporation.com}
-\alignauthor
-Hiroshi Oyama\\
-    \affaddr{OKUMA Corporation}\\
-    \affaddr{Aichi, JAPAN}\\
-       % \affaddr{Dublin, Ohio 43017-6221}\\
-       % \email{webmaster@marysville-ohio.com}
-\alignauthor
-Takuya Azumi\\
-    \affaddr{Graduate School of Engineering Science, Osaka University}\\
-    \affaddr{Osaka, JAPAN}\\
-       % \affaddr{Hekla, Iceland}\\
-       % \email{larst@affiliation.org}
-}
-%\author{Takuro Yamamoto}
-%\date{\today}
+% ユーザが定義したマクロなどはここに置く．ただし学会誌のスタイルの
+% 再定義は原則として避けること．
 
 \begin{document}
-\maketitle
-\begin{abstract}
-Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
-To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
+
+% 論文のタイトル
+\title{Lightweight Ruby Framework\\ for Improving Embedded Software Efficiency}
+
+% 著者
+% 和文論文の場合，姓と名の間には半角スペースを入れ，
+% 複数の著者の間は全角スペースで区切る
+%
+\author{Takuro Yamamoto　Hiroshi Oyama　Takuya Azumi}
+%
+% ここにタイトル英訳 (英文の場合は和訳) を書く．
+%
+\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発フレームワーク}
+%
+% ここに著者英文表記 (英文の場合は和文表記) および
+% 所属 (和文および英文) を書く．
+% 複数著者の所属はまとめてよい．
+%
+\shozoku{山本　拓朗, 安積　卓也}{大阪大学大学院基礎工学研究科}%
+{Graduate School of Engineering Science, Osaka University}
+\shozoku{大山　博司}{オークマ株式会社}%
+{OKUMA Corporation}
+
+%
+% 出典情報は \shutten とすれば出力される．
+\shutten
+%
+% 受付年月日，記事カテゴリなどは自動的に生成される．
+\uketsuke{2011}{12}{15}
+%
+% その他，脚注に入れるものがあれば，¥note に記述する．
+%\note{脚注に入れる内容}
+
+%
+% 和文アブストラクト
+% \Jabstract{%
+% 近年，組込みシステムは複雑化・大規模化しているため，ソフトウェアの生産性が問題になっている．
+% 組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
+% 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
+% さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+% 本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
+% さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する．
+% }
+%
+% 英文アブストラクト（本サンプルの原論文にはなし）
+\Eabstract{
+The complexity and scale of embedded software have increased.
+To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
 In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
 Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
-To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
-The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
-The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
-In addition, multiple mruby programs can run cooperatively in the proposed framework.
-Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
+This paper proposed an extended mruby on TECS framework that improves development efficiency more than the current framework.
+We implemented a Bluetooth loader receives an mruby bytecode, and a RiteVM scheduler simplifies multitasking.
 Synchronization of initializing multiple tasks is also implemented using an Eventflag.
 Experimental results demonstrate the advantages of the proposed framework.
-\end{abstract}
+}
+%
+\maketitle
 
-\keywords{embedded software; scripting language; component-based development}
+%%%%%%%%%%%本文%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=14cm,clip]{figure/proposed.eps}
     \caption{System model of the proposed framework}
-    \vspace{1mm}
     \label{fig:proposed}
-\end{figure}
+\end{figure*}
 
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/mruby.eps}
     \caption{mruby/RiteVM mechanism}
-    \vspace{1mm}
     \label{fig:mruby}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
-    % \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
     \caption{Component Diagram}
-    \vspace{1mm}
     \label{fig:component}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.eps}
 \caption{System model of existing mruby on TECS}
-    \vspace{1mm}
 \label{fig:mrubyontecs}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/mruby_TECS_bridge.eps}
 \caption{mruby-TECS bridge}
-    \vspace{1mm}
 \label{fig:mruby_TECS_bridge}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/system_model.eps}
 \caption{Detailed system model of the proposed framework}
-    \vspace{1mm}
 \label{fig:system_model}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/component_bluetooth.eps}
 \caption{Component diagram of Bluetooth loader for mruby bytecode}
-    \vspace{1mm}
 \label{fig:component_bluetooth}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/control_flow.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/control_flow.eps}
 \caption{Process flow of Bluetooth loader for mruby bytecode}
-    \vspace{1mm}
 \label{fig:control_flow}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/rotateReadyQueue.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
 \caption{RiteVM scheduler design}
-    \vspace{1mm}
 \label{fig:rotateReadyQueue}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
-    % \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
 \caption{Component diagram of RiteVM scheduler}
-    \vspace{1mm}
 \label{fig:cyclic_handler}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/Eventflag.eps}
 \caption{Design of Eventflag using TECS (only differences are shown)}
-    \vspace{1mm}
 \label{fig:Eventflag}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/comparison_s_c_m.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
 \caption{Comparison of application execution time with singletask, co-routine, and multitask}
-    \vspace{1mm}
 \label{fig:comparison_s_c_m}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/comparison_msec.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
 \caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-    \vspace{1mm}
 \label{fig:comparison_msec}
@@
     \centering
-    \includegraphics[width=8.6cm,clip]{figure/eval_synchronization.eps}
-    \vspace{0.5mm}
+    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
 \caption{Synchronization of multiple RiteVM tasks}
-    \vspace{1mm}
 \label{fig:eval_synchronization}
@@
 \end{table}
-
-\begin{table*}[t]
-    \centering
-    \vspace{1mm}
-\caption{Comparison of proposed and previous methods}
-    \vspace{2mm}
-    %\scriptsize
-    {\tabcolsep=0.05cm
-    \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
-        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
-        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
-    \end{tabular}
-    }
-    \label{tab:comparison}
-\end{table*}
 
@@
 
+\begin{table*}[t]
+    \caption{Comparison of proposed and previous methods}
+    \label{tab:comparison}
+    \begin{center}
+    \begin{tabular}{c||c|ccccccc}
+        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
+        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
+        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
+        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
+        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
+        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
+    \end{tabular}
+    \end{center}
+\end{table*}
+
 Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
-{\mybf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
+{\bf python-on-a-chip:} python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
 The VM runs a significant subset of the Python language with few resources on a microcontroller.
@@
 In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
+
+\section{Results of Research}
+\label{sec:}
+The mruby on TECS framework has been certified for the official platform of ET Robocon 2016.
+In addition, the proposed framework on LEGO MINDSTORMS EV3 has been commercialized by Afrel Co., Ltd.
 
@@
 \section{Acknowledgement}
+
 This work was supported by JSPS KAKENHI Grant Number 15H05305.
 We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
+
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%本文終わり%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{choshashoukai}
+%
+% \chosha{山本拓朗}
+% {2016年大阪大学基礎工学部システム科学科卒．
+% }
+% \chosha{大山博司}
+% {
+% }
+% \chosha{安積卓也}
+% {
+% }
+%
+% \end{choshashoukai}
+
 \end{document}

### 2016-10-25 jssst/paper.tex
add software journal
Add related work (ChaiScript)

@@
 \documentclass[S,R,E]{article/compsoft}
-
 % Preamble
@@
 % 巻数，号数，開始ページ，終了ページを指定する．
-\volNoPp{29}{1}{78}{84}
+\volNoPp{0}{0}{0}{0}
 
@@
 % 論文のタイトル
-\title{Lightweight Ruby Framework\\ for Improving Embedded Software Efficiency}
+\title{Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development}
 
@@
 %
-\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発フレームワーク}
+\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発コンポーネントベースフレームワーク}
 %
@@
 % 受付年月日，記事カテゴリなどは自動的に生成される．
-\uketsuke{2011}{12}{15}
+\uketsuke{0000}{00}{00}
 %
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=14cm,clip]{figure/proposed.eps}
+    \includegraphics[width=6.5cm,clip]{figure/proposed.eps}
     \caption{System model of the proposed framework}
     \label{fig:proposed}
-\end{figure*}
+\end{figure}
 
@@
     ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
+    ER rotate( [in] int degrees,
+               [in] uint32_t speed_abs,
                 [in] bool_t blocking );
@@
 /* tRiteVMBluetooth.c */
-void
-eMrubyBody_main( CELLIDX idx )
+void eMrubyBody_main( CELLIDX idx )
 {
@@
   mrb_load_irep_cxt( VAR_mrb,
-                        ATTR_irepLib, VAR_context );
+                     ATTR_irepLib,
+                     VAR_context );
   /* Load mruby application bytecode and run */
   mrb_load_irep_cxt( VAR_mrb,
-                        VAR_irepApp, VAR_context );
+                     VAR_irepApp,
+                     VAR_context );
   if ( mrb->exc ) {
@@
     attr {
-        [omit] ATR    attribute   = C_EXP("TA_NULL");
+        [omit] ATR    attribute   =
+                            C_EXP("TA_NULL");
     	[omit] RELTIM cyclicTime;
@@
 \caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
-    %\scriptsize
+    \scriptsize
     {\tabcolsep=0.1cm
@@
     \caption{C and CDL file code for the number of RiteVMs}
-    %\scriptsize
-    {\tabcolsep=0.2cm
+    \footnotesize
+    {\tabcolsep=0.1cm
     \begin{tabular}{c||c|c|c}
@@
         CDL    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
-        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
+        \multicolumn{3}{l}{ $\alpha$ : the number of RiteVMs}
     \end{tabular}
@@
     \begin{center}
-    \begin{tabular}{c||c|ccccccc}
-        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Management} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Applications} & Co-routine \\ \hline
-        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
-        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
+    {\tabcolsep=0.05cm
+    \begin{tabular}{c||c|cccccc}
+        & \shortstack{Bluetooth\\Loader}
+        & \shortstack{Call\\C Function} 
+        & \shortstack{Legacy Code of\\Embedded System} 
+        & \shortstack{VM\\Management} 
+        & \shortstack{VM\\Scheduler} 
+        & \shortstack{Synchronization\\of Applications} \\ \hline
+        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
+        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
+        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
+        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
+        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
+        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
+        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
+        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
     \end{tabular}
+    }
     \end{center}
@@
 
-Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, ChaiScript\cite{url:ChaiScript}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
 
@@
 Note that a co-routine can only suspend and resume multiple routines; thus, a Lua co-routine is not like multitasks in multitask systems.
+
+{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
+It is a dialect of ECMAScript (a.k.a. JavaScript).
+ChaiScript is header only, that is, it only needs to include the header files in order to use it in an application.
+ChaiScript will support co-routines, but not now.
 
@@
 \section{Results of Research}
-\label{sec:}
-The mruby on TECS framework has been certified for the official platform of ET Robocon 2016.
-In addition, the proposed framework on LEGO MINDSTORMS EV3 has been commercialized by Afrel Co., Ltd.
+\label{sec:Results}
+The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/}.
+
+In addition, the proposed framework on LEGO MINDSTORMS EV3 has been commercialized for education by Afrel Co., Ltd\footnote{http://www.afrel.co.jp/lineup/textset (in Japanese)}, which is an official partner of LEGO Education.
 

### 2016-10-25 jssst/paper.tex
Add results of research

@@
         eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
-        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
+        ChaiScript \cite{url:ChaiScript}             &            &            &            &    -       &    -        &            \\
         Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
@@
 \label{sec:Results}
-The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/}.
+The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
+In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.
 

### 2016-10-27 jssst/paper.tex
Modify the section to Utilization Results
add table and modify conclusion

@@
 Related work is discussed in Section \ref{sec:Related work}.
+In Section \ref{sec:Results}, the utilization results are reported.
 Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.
@@
 \label{sec:Background}
-Figure \ref{fig:proposed} shows the system model of the proposed framework.
+Fig.\ref{fig:proposed} shows the system model of the proposed framework.
 Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
@@
 Bytecodes transferred from the host via Bluetooth can run in multitask.
+
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilize two technologies i.e., mruby and TECS.
+In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.
 
@@
 In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
-The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
+The mruby/RiteVM mechanism is shown in Fig.\ref{fig:mruby}.
 The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
@@
 \subsubsection{Component Model}
-Figure \ref{fig:component} shows a component diagram.
+Fig.\ref{fig:component} shows a component diagram.
 A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
@@
         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
@@
         The build description is used to instantiate and connect {\it cell}s.
-        Figure \ref{build} shows an example of a build description.
+        Fig.\ref{build} shows an example of a build description.
         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
         {\it C\_EXP} calls macros defined in C files.
@@
 \label{sec:mruby on TECS}
-% mruby on TECS is a component-based framework for running script language.
-% This framework uses two technologies, mruby and TECS.
+mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
+This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using script language without slowdown of the execution time.
 
-\subsubsection{System Model}
-The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
+\subsubsection{System Model of mruby on TECS}
+The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
 Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
@@
 
-Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+Fig.\ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
 The left side of BridgeMotor belongs to the mruby program.
@@
 \label{sec:Design and Implementation}
-Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
+Fig.\ref{fig:system_model} shows the detailed system model of the proposed framework.
 Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
@@
 
-Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
+Fig.\ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
@@
  /* New mruby context */
-  VAR_context = mrbc_context_new( VAR_mrb );
-  /* Omit: initialization of mruby-TECS bridge */
+ VAR_context = mrbc_context_new(VAR_mrb);
+ /* Omit: initialize mruby-TECS bridge */
  /* Omit: synchronization of
@@
 
-Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
-The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.
+Fig.\ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
+The main tRiteVMBluetooth code is shown in Fig.\ref{maincode_mrubybluetooth}.
 
-First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); lines 6-7 in Figure \ref{maincode_mrubybluetooth}).
-The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
-This process is exclusively carried out by the semaphore.
+First, the Bluetooth loader receives the mruby application bytecode from the host (Fig.\ref{fig:control_flow}(A); lines 5-6 in Fig.\ref{maincode_mrubybluetooth}).
+The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Fig.\ref{celltype_mrubybluetooth}.
+This process is exclusively carried out by the semaphore to prevent the other loading from interrupting.
 
-Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Figure \ref{fig:control_flow}(B); lines 9-14 in Figure \ref{maincode_mrubybluetooth}).
+Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Fig.\ref{fig:control_flow}(B); lines 8-13 in Fig.\ref{maincode_mrubybluetooth}).
 {\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
@@
 
-Third, the RiteVM reads the bytecode of mruby libraries (Figure \ref{fig:control_flow}(C); lines 17-19 in Figure \ref{maincode_mrubybluetooth}).
+Third, the RiteVM reads the bytecode of mruby libraries (Fig.\ref{fig:control_flow}(C); lines 16-19 in Fig.\ref{maincode_mrubybluetooth}).
 The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
 For example, the motor class defines methods to rotate and stop a motor.
-The tRiteVMBluetooth {\it cell} has the attributes shown in Figure \ref{celltype_mrubybluetooth}.
+The tRiteVMBluetooth {\it cell} has the attributes shown in Fig.\ref{celltype_mrubybluetooth}.
 {\it ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\it VAR}.
@@
 
-Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Figure \ref{fig:control_flow}(D); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
+Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Fig.\ref{fig:control_flow}(D); lines 20-23 in Fig.\ref{maincode_mrubybluetooth}).
 The mruby application bytecode is stored in an array of {\it irepApp}, which differs from the array that holds the mruby library bytecode.
@@
 
-Finally, the mruby task runs (Figure \ref{fig:control_flow}(E); lines 20-22 in Figure \ref{maincode_mrubybluetooth}).
+Finally, the mruby task runs (Fig.\ref{fig:control_flow}(E); lines 20-23 in Fig.\ref{maincode_mrubybluetooth}).
 When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
 
-The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
-When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
+The process shown in Fig.\ref{maincode_mrubybluetooth} (lines 24-29) is carried out when an exception occurs.
+When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 32-35 in Fig.\ref{maincode_mrubybluetooth}).
 The proposed framework supports continuous loading; thus, this process loops.
@@
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
-The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
+The design of the RiteVM scheduler is shown in Fig.\ref{fig:rotateReadyQueue}. 
 {\it rotateReadyQueue} is described as follows.
@@
 
-When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
+When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Fig.\ref{fig:rotateReadyQueue}.
 Note that the argument of {\it rotateReadyQueue} is the priority.
@@
 
-Figure \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
-The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
+Fig.\ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
+The RiteVM scheduler is a {\it composite cell} which consists of CyclicHandler and RiteVMSchedulerMain.
 The CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
@@
 Note that {\it rotateReadyQueue} is implemented as the body.
-Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
+Fig.\ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
 The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
@@
 
-Figure \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
+Fig.\ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
 The RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
@@
 Eventflag is applied to synchronize the initiation of multiple mruby applications.
-Each task sets a flag pattern, such as 0x01 (01) and 0x02 (10), and then waits for the flag pattern 0x3 (11) with AND.
+Each task sets a flag pattern, such as 0x01 (01) and 0x02 (10), and then waits for the flag pattern 0x03 (11) with AND.
 This process can also be applied to more tasks.
-For example, for four RiteVM tasks, each task sets a flag pattern, such as 0x01 (0001), 0x02 (0010), 0x04 (0100), and 0x08 (1000), and then waits 0x0f (1111) with AND, as shown in Figure \ref{fig:Eventflag}(A).
+For example, for four RiteVM tasks, each task sets a flag pattern, such as 0x01 (0001), 0x02 (0010), 0x04 (0100), and 0x08 (1000), and then waits 0x0f (1111) with AND, as shown in Fig.\ref{fig:Eventflag}(A).
 
@@
 Therefore, developers can add, remove, or reuse these components easily.
-For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
+For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import("tRiteVMScheduler.cdl");}.
 CBD eliminates the need for developers to rewrite kernel configuration files.
@@
 In the proposed framework, this advantage is applied in the Eventflag component.
-The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
+The set pattern and wait pattern are defined as attributes of the component as shown in Fig.\ref{fig:Eventflag} (B).
 This design, e.g., {\it cEventflag\_set(ATTR\_setPattern)}, enables the program without ``if'' statements and reuses an identical C file.
@@
 Here, {\it [optional]} means that the code is run only when the call port is connected.
-Note that the C file does not need to be rewritten even if the Eventflag is not used.
+Thus, the C file does not need to be rewritten even if the Eventflag is not used.
+
+\section{Experimental Evaluation}
+\label{sec:Evaluation}
+This section discusses experimental results.
+To analyze the advantages of the proposed framework, we evaluated the following.
+\begin{itemize}
+    \item Execution time of the platform
+    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
+    \item Execution time with singletasking, co-routine, and proposed multitasking
+    \item Overhead for periodic time
+    \item Synchronization of multiple RiteVM tasks
+    \item Code size with CBD 
+\end{itemize}
+
+These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
+In addition, we focused on benefits of CBD.
+We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
+
+\subsection{Improving Software Development Efficiency by Bluetooth Loader}
+
+\begin{table}[t]
+    \centering
+\caption{Development procedure of existing and proposed framework}
+    \scriptsize
+    {\tabcolsep=0.1cm
+    \begin{tabular}{c||c}
+                            & Development procedure \\ \hline
+        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
+        Proposed framework  &          (4)          \\ \hline
+        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
+        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
+        \multicolumn{2}{l}{ (3): Restart the RTOS on target (about 4 sec)} \\
+        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
+    \end{tabular}
+    }
+    \label{tab:procedure}
+\end{table}
 
@@
 
-\section{Experimental Evaluation}
-\label{sec:Evaluation}
-This section discusses experimental results.
-To analyze the advantages of the proposed framework, we evaluated the following.
-\begin{itemize}
-%    \item Execution time of the platform
-    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
-    \item Execution time with singletasking, co-routine, and proposed multitasking
-    \item Overhead for periodic time
-    \item Synchronization of multiple RiteVM tasks
-    \item Code size with CBD 
-\end{itemize}
-
-These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
-In addition, we focused on benefits of CBD.
-We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
-\caption{Comparison of application execution time with singletask, co-routine, and multitask}
-\label{fig:comparison_s_c_m}
-\end{figure}
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
-\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-\label{fig:comparison_msec}
-\end{figure}
-
-\subsection{Improving Software Development Efficiency by Bluetooth Loader}
 The Bluetooth loader for mruby bytecode can reduce the development time.
 With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
+In the proposed framework, the development procedure is shortened as shown Table \ref{tab:procedure}
 For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
 In addition, the proposed framework eliminates the need to restart the target RTOS.
+Note that the time of restarting the RTOS including initializing device drivers is 4 sec in case of  EV3 platform \cite{par:EV3}
 
@@
 \subsection{RiteVM Scheduler}
-A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
+
+A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
 A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
@@
 \subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
-In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
-This shows that the proposed design is superior to co-routine in terms of execution time.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
+\caption{Comparison of application execution time with singletask, co-routine, and multitask}
+\label{fig:comparison_s_c_m}
+\end{figure}
+
+Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
+The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
+The scheduler runs as the periodic handler of RTOS.
+% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
+% This shows that the proposed design is superior to co-routine in terms of execution time.
 Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
-The scheduler interrupts and switches tasks, which causes this overhead.
+The scheduler interrupts and switches tasks, which causes this overhead.Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
+Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
+Here, the periodic time of the scheduler is 1 msec.
 It takes approximately 3 $\mu$sec on average to switch tasks once.
@@
 \subsubsection{Periodic Time Overhead}
-Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
+\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
+\label{fig:comparison_msec}
+\end{figure}
+
+Fig.\ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
 The lower limit of the periodic time is 1 msec due to the specifications of TOPPERS/HRP2, i.e., the RTOS.
@@
 
+\subsection{Synchronization of Multiple RiteVM Tasks}
+
  \begin{figure}[t]
@@
 \end{figure}
+
+To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
+We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
+It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
+Fig.\ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
+% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
+% The periodic time is one msec, and the number of RiteVM is four.
+The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
+As shown in Fig.\ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.
+
+\subsection{Benefits of Component-Based Development}
 
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
-To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
-We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
-It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
-Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
-% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
-% The periodic time is one msec, and the number of RiteVM is four.
-The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
-As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.
-
-\subsection{Benefits of Component-Based Development}
 In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
@@
 %\subsubsection{Code size utilizing component-based development}
-To demonstrate the superiority of CBD, a comparison of the number of lines of codes between two C and CDL files is shown in Table \ref{tab:codesize}.
-In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Figure \ref{fig:Eventflag}, respectively. 
+To demonstrate the superiority of CBD, a comparison of the number of lines of codes C and ACL codes between two situations is shown in Table \ref{tab:codesize}.
+In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig.\ref{fig:Eventflag}, respectively. 
 For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.
@@
 In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
+Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied scripting languages other than mruby if VM mechanism is used.
 
-\section{Results of Research}
+\section{Actual Results}
 \label{sec:Results}
@@
 \label{sec:Conclusion}
-This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
-The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
-The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
-%Thus, the proposed framework can be utilized on the devices without Bluetooth.
-The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
-Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
+This paper presented an extended framework of mruby on TECS.
+In the proposed framework, we implements a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
+The Bluetooth loader improves software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on a target device.
+The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
+The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
+Our experimental results show the advantages of the proposed framework.
 The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
@@
 Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
-For software developed with priority-based scheduling, developers only have to remove the RiteVM scheduler.
+For software developed with fixed-priority based scheduling, developers only have to remove the RiteVM scheduler.
 % Component-based development can increase productivity.

### 2016-10-30 jssst/paper.tex
Modify the syncronization in Evaluation section

@@
 We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
-It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
-Fig.\ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
+It was confirmed that the time was within the theoretical value. Theoretical value is 
+\begin{displaymath}
+    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1)}
+\end{displaymath}
+Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
 % Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
 % The periodic time is one msec, and the number of RiteVM is four.
-The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
-As shown in Fig.\ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.
+Note that the periodic time is 1 msec.
+As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value respectively, which indicates successful synchronization of multiple RiteVM tasks.
 

### 2016-10-30 jssst/paper.tex
Modify the text by enago

@@
 
-The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilize two technologies i.e., mruby and TECS.
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilizes two technologies: mruby and TECS.
 In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.
@@
 mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
-This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using script language without slowdown of the execution time.
+This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.
 
@@
     \centering
-\caption{Development procedure of existing and proposed framework}
+\caption{Development procedure of existing and proposed frameworks}
     \scriptsize
@@
         \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
-        \multicolumn{2}{l}{ (3): Restart the RTOS on target (about 4 sec)} \\
+        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
         \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
@@
 In addition, the proposed framework eliminates the need to restart the target RTOS.
-Note that the time of restarting the RTOS including initializing device drivers is 4 sec in case of  EV3 platform \cite{par:EV3}
+Note that the time of restarting the RTOS, including initializing device drivers, is 4 sec in case of the EV3 platform \cite{par:EV3}
 
@@
 To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
-We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
+We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
 It was confirmed that the time was within the theoretical value. Theoretical value is 
 \begin{displaymath}
-    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1)}
+    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
 \end{displaymath}
@@
 Note that the periodic time is 1 msec.
-As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value respectively, which indicates successful synchronization of multiple RiteVM tasks.
+As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
 
@@
 It is a dialect of ECMAScript (a.k.a. JavaScript).
-ChaiScript is header only, that is, it only needs to include the header files in order to use it in an application.
+ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
 ChaiScript will support co-routines, but not now.
@@
 In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
-Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied scripting languages other than mruby if VM mechanism is used.
+Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied to scripting languages other than mruby if the VM mechanism is used.
 
@@
 The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
-In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.
+In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.
 
@@
 This paper presented an extended framework of mruby on TECS.
-In the proposed framework, we implements a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
-The Bluetooth loader improves software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on a target device.
+In the proposed framework, we implement a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
+The Bluetooth loader improves the software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on the target device.
 The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
@@
 Our experimental results show the advantages of the proposed framework.
-The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
+The Bluetooth loader can improve the software development efficiency of mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
 In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
@@
 Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
-For software developed with fixed-priority based scheduling, developers only have to remove the RiteVM scheduler.
+For software developed with fixed-priority-based scheduling, developers only have to remove the RiteVM scheduler.
 % Component-based development can increase productivity.

### 2016-10-30 jssst/paper.tex
Editing the text

@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
-\caption{RiteVM scheduler design}
-\label{fig:rotateReadyQueue}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
-\caption{Component diagram of RiteVM scheduler}
-\label{fig:cyclic_handler}
-\end{figure}
-
 \subsection{RiteVM Scheduler}
@@
 Therefore, when developers create software with priority-based scheduling, the RiteVM scheduler can be removed easily.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
+\caption{RiteVM scheduler design}
+\label{fig:rotateReadyQueue}
+\end{figure} 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
+\caption{Component diagram of RiteVM scheduler}
+\label{fig:cyclic_handler}
+\end{figure}
 
@@
     \centering
-\caption{Comparison of size and load process time between an mruby application with and without mruby libraries}
+\caption{Size and load process time of an mruby application with/without libraries}
     \scriptsize
@@
 
-A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
-A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
-Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.
-
-\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
-
 \begin{figure}[t]
@@
 
+% A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
+% A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
+% Here, the singletask program looped 100,000 times and the multitask and co-routine programs looped 50,000 times for each task.
+
+%\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
+{%\bf Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
+
 Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
@@
 % This shows that the proposed design is superior to co-routine in terms of execution time.
+
 Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
@@
 
-\subsubsection{Periodic Time Overhead}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
-\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-\label{fig:comparison_msec}
-\end{figure}
+%\subsubsection{Periodic Time Overhead}
+%{\bf Periodic Time Overhead}
 
@@
 Note that a smaller periodic time is better for multitasking due to concurrent or parallel processing.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
+\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
+\label{fig:comparison_msec}
+\end{figure}
 

### 2016-10-31 jssst/paper.tex
Modify RiteVM Tasks to RiteVMs
Final version

@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
+\subsection{Synchronization of Multiple RiteVMs}
 
@@
     \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
-\caption{Synchronization of multiple RiteVM tasks}
+\caption{Synchronization of multiple RiteVMs}
 \label{fig:eval_synchronization}
@@
 We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
-It was confirmed that the time was within the theoretical value. Theoretical value is 
+It was confirmed that the time was within the theoretical value which is 
 \begin{displaymath}
@@
         & \shortstack{Synchronization\\of Applications} \\ \hline
+        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
         python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
@@
         eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
-        ChaiScript \cite{url:ChaiScript}             &            &            &            &    -       &    -        &            \\
         Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
@@
 
-Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, ChaiScript\cite{url:ChaiScript}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+Open-source runtime systems for scripting languages have been proposed such as ChaiScript\cite{url:ChaiScript}, python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
+
+{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
+It is a dialect of ECMAScript (a.k.a. JavaScript).
+ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
+ChaiScript will support co-routines, but not now.
 
@@
 Note that a co-routine can only suspend and resume multiple routines; thus, a Lua co-routine is not like multitasks in multitask systems.
-
-{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
-It is a dialect of ECMAScript (a.k.a. JavaScript).
-ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
-ChaiScript will support co-routines, but not now.
 
@@
 
-\section{Actual Results}
+\section{Practical Use}
 \label{sec:Results}

### 2016-11-29 ISORC2016/paper.tex
Add ISORC2016

%% paper.tex
%% for ISORC 2016
%% 2016/11/29
%% by Takuro Yamamoto

\documentclass[conference]{IEEEtran/IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\cite{par:mruby}

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section
\bibliographystyle{IEEEtranBST2/IEEEtran}
\bibliography{ref}

% that's all folks
\end{document}

### 2016-12-05 ISORC2016/paper.tex
Update text

@@
 % \documentclass[conference]{../sty/IEEEtran}
+
+% Package List
+%\usepackage[dvips]{graphics}
+\usepackage[dvipdfmx]{graphicx}
+\usepackage{amssymb}
+\usepackage{float}
+\usepackage{enumerate,cite,url}
+\usepackage{listings,jlisting}
+\lstset{%
+    language={c},%
+    basicstyle={\small},%
+    identifierstyle={\small},%
+    commentstyle={\footnotesize\itshape},%
+    keywordstyle={\small},%\bfseries},%
+    ndkeywordstyle={\small},%
+    stringstyle={\small\it},
+    frame={tb},
+    breaklines=true,
+    columns=[l]{fullflexible},%
+    numbers=left,%
+    xrightmargin=0zw,%
+    xleftmargin=3zw,%
+    numberstyle={\scriptsize},%
+    stepnumber=1,
+    numbersep=1zw,%
+    lineskip=-0.5ex%
+}
 
@@
 % 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+% \author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+% Homer Simpson\IEEEauthorrefmark{2},
+% James Kirk\IEEEauthorrefmark{3}, 
+% Montgomery Scott\IEEEauthorrefmark{3} and
+% Eldon Tyrell\IEEEauthorrefmark{4}}
+% \IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+% Georgia Institute of Technology,
+% Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+% \IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+% Email: homer@thesimpsons.com}
+% \IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+% Telephone: (800) 555--1212, Fax: (888) 555--1212}
+% \IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
 
@@
 \begin{abstract}
-The abstract goes here.
+
+Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
+
+TINET is a TCP/IP protocol stack for embedded systems.
+TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
+Therefore, it is difficult to maintain, extend, and analysis the software.
+
+To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
+The component-based TINET provides software developers high productivity such as change of network buffer size and add/remove TCP (or UDP) function.
+We evaluate the component-based TINET compared with the original TINET, and confirm that the overheads of execution time and memory consumption are low and  that the configurability is improved.
+
+In this paper, we also demonstrates a use case of the dynamic component connection method of TECS with a network application.
+
 \end{abstract}
@@
 \section{Introduction}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
+\label{sec:Introduction}
 
-\hfill mds
+Internet of Things (IoT) is an essential keyword for the next era.
+Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
+Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
+Therefore, embedded network software is required for the high productivity and quality.
 
-\hfill August 26, 2015
+TINET (Tomakomai InterNETworking) \cite{url:TINET} is a compact TCP/IP protocol stack for embedded systems.
+TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
+TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
+However, there are several issues that TINET consists of many complex source codes.
+It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.
 
-\cite{par:mruby}
+In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
+TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+{\bf Contributions:} This paper provides the following contributions.
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+\begin{enumerate}
+
+    \item {\bf Improve configurability}
+
+    \item {\bf Dynamic connection method}
+
+    \item {\bf Support legacy codes}
+
+    % \item {\bf Software visualization}
+
+\end{enumerate}
+
+{\bf Organization}: The remainder of this paper is organized as follows.
+Section \ref{sec:Basic Technology} introduces the basic technologies, i.e., TINET and TECS.
+Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
+Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
+Related work is discussed in Section \ref{sec:Related Work}.
+Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.
+
+\section{Basic Technology}
+\label{sec:Basic Technology}
+
+\subsection{TINET}
+
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS project.
+To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
+
+\begin{enumerate}
+    \item Minimum copy frequency
+    \item Elimination of dynamic memory control
+    \item Asynchronous interface
+    \item Error detailed per API
+\end{enumerate}
+
+TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
+
+\subsubsection{Overview}
+
+Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
+    \caption{Hierarchy Diagram of TINET and TOPPERS/ASP3}
+    \label{fig:TINET_Hier}
+\end{figure}
+
+\subsection{TECS}
+\label{sec:TECS}
+
+TECS is a component system suitable for embedded systems.
+TECS can increase productivity and reduce development costs due to improved reusability of software components.
+TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+
+In TECS, component deployment and composition are performed statically.
+Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
+    \caption{Component Diagram}
+    \label{fig:component}
+\end{figure}
+
+\subsubsection{Component Model}
+
+Fig.\ref{fig:component} shows a component diagram.
+A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
+An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+{\it Cell} functions are implemented in C.
+
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
+
+\subsubsection{Component Description}
+
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+These components are described as follows.
+
+\begin{description}
+    \item[{\bf Signature Description}]\mbox{}\\
+        The {\it signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sMotor {
+    int32_t getCounts( void );
+    ER resetCounts( void );
+    ER setPower( [in]int power );
+    ER stop( [in] bool_t brake );
+    ER rotate( [in] int degrees,
+               [in] uint32_t speed_abs,
+                [in] bool_t blocking );
+    void initializePort( [in]int32_t type );
+};
+\end{lstlisting}
+\caption{Signature Description}
+\label{signature}
+\end{figure}
+    \item[{\bf Celltype Description}]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+celltype tCaller {
+    call sMotor cMotor;
+};
+celltype tMotor {
+    entry sMotor eMotor;
+    attr {
+        int32_t port;
+    };
+    var {
+        int32_t currentSpeed = 0;
+    };
+};
+\end{lstlisting}
+\caption{Celltype Description}
+\label{celltype}
+\end{figure}
+    \item[{\bf Build Description}]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
+        Fig.\ref{build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+cell tMotor Motor {
+    port = C_EXP("PORT_A");
+};
+cell tCaller Caller {
+    cMotor = Motor.eMotor;
+};
+\end{lstlisting}
+\caption{Build Description}
+\label{build}
+\end{figure}
+
+\end{description}
+
+\section{Design and Implementation}
+\label{sec:Design and Implementation}
+
+\subsection{TECS Adapter}
+
+TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
+An adapter connects a TECS component, links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
+Software developers can utilize an existing application for TECS owing to the adapter.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/TECS_Adapter.pdf}
+    \caption{TECS Adapter}
+    \label{fig:TECS_Adapter}
+\end{figure}
+
+\section{Evaluation and Demonstration}
+\label{sec:Evaluation and Demonstration}
+
+\begin{table}[t]
+    \centering
+    \caption{Evaluation Board Environment}
+    \begin{tabular}{l|l}
+        \hline\hline
+        Board           &   GR-PEACH                \\
+        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
+        Flash ROM       &   8 MB                    \\
+        RAM             &   10 MB                   \\
+        LAN Controller  &   LAN8710A                \\
+        \hline
+    \end{tabular}
+    \label{tab:Evaluation_Board_Environment}
+\end{table}
+
+\section{Related Work}
+\label{sec:Related Work}
 
 \section{Conclusion}
-The conclusion goes here.
+\label{sec:Conclusion}
 
@@
 \section*{Acknowledgment}
-
-The authors would like to thank...
 

### 2016-12-16 ISORC2017/paper.tex
Update

--- 2016-12-05 ISORC2016/paper.tex
@@
     language={c},%
-    basicstyle={\small},%
+    basicstyle={\small\ttfamily},%
     identifierstyle={\small},%
@@
 
-TINET (Tomakomai InterNETworking) \cite{url:TINET} is a compact TCP/IP protocol stack for embedded systems.
+TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
 TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
@@
 
+Component-based development is an approach to improve software productivity.
+Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+Component-based systems are flexible to software extension and specification changes.
+In addition, individual Component diagrams enable the visualization of an entire system.
+
 In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
-TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET.
+TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
+TECS supports static configuration, that component behaviors and interconnections are defined statically, thus TECS can optimize the overhead of componentization.
 
@@
 
-    \item {\bf Improve configurability}
+    \item {\bf Improve configurability}\mbox{}\\
+        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resize network buffer, add/remove TCP (or UDP) functions, and support both IPv4 and IPv6.
+        In addition, a component diagram provides visualization of TINET, a complicated system.
 
-    \item {\bf Dynamic connection method}
+    \item {\bf Dynamic connection method}\mbox{}\\
 
-    \item {\bf Support legacy codes}
-
+    \item {\bf Support legacy codes}\mbox{}\\
+        TECS supports the adapter to call TECS functions from C codes, thus TINET+TECS can use an existing application.
     % \item {\bf Software visualization}
@@
 
-TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS project.
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
 To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
@@
 TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
+TINET has been released as open source.
 
@@
 
+\subsection{send, receive specifier}
+
+TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
+TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.
+
+in is a specifier for input arguments.
+A callee side uses the memory of arguments with in while executing the callee function.
+When the processing returns to the caller side, the caller can reuse and deallocate the memory.
+
+send is also a specifier for transferring data to a callee from a caller such as in.
+The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
+In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
+On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.
+
+out is a specifier for output arguments.
+A callee writes data in the memory allocated by a caller, and the caller receives the data.
+
+receive is also a specifier for a caller receiving data from a callee such as out.
+The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
+While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
+Deallocating the memory is performed in the caller in both cases.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/SendReceive.pdf}
+    \caption{Differences between in/out and send/receive}
+    \label{fig:SendReceive}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sNicDriver {
+  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp,
+             [in]int32_t size,
+             [in]uint8_t align);
+  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp,
+            [out]int32_t *size,
+            [in]uint8_t align);
+    /* Omit: other functions */
+};
+\end{lstlisting}
+\caption{An example of send and receive}
+\label{src:SendReceive}
+\end{figure}
+
 \subsection{TECS Adapter}

### 2016-12-16 jssst/diff/1025.tex
Update

--- 2016-10-30 jssst/paper.tex
@@
 
-The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilizes two technologies: mruby and TECS.
-In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.
-
 \subsection{mruby}
@@
 \label{sec:mruby on TECS}
-mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
-This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.
+% mruby on TECS is a component-based framework for running script language.
+% This framework uses two technologies, mruby and TECS.
 
-\subsubsection{System Model of mruby on TECS}
+\subsubsection{System Model}
 The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
@@
 Therefore, developers can add, remove, or reuse these components easily.
-For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import("tRiteVMScheduler.cdl");}.
+For example, if the RiteVM scheduler is not necessary for the software, developers should comment out only the CDL file, e.g., {\it //import(<tRiteVMScheduler.cdl>);}.
 CBD eliminates the need for developers to rewrite kernel configuration files.
@@
 Thus, the C file does not need to be rewritten even if the Eventflag is not used.
-
-\section{Experimental Evaluation}
-\label{sec:Evaluation}
-This section discusses experimental results.
-To analyze the advantages of the proposed framework, we evaluated the following.
-\begin{itemize}
-    \item Execution time of the platform
-    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
-    \item Execution time with singletasking, co-routine, and proposed multitasking
-    \item Overhead for periodic time
-    \item Synchronization of multiple RiteVM tasks
-    \item Code size with CBD 
-\end{itemize}
-
-These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
-In addition, we focused on benefits of CBD.
-We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
-
-\subsection{Improving Software Development Efficiency by Bluetooth Loader}
-
-\begin{table}[t]
-    \centering
-\caption{Development procedure of existing and proposed frameworks}
-    \scriptsize
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||c}
-                            & Development procedure \\ \hline
-        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
-        Proposed framework  &          (4)          \\ \hline
-        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
-        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
-        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
-        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
-    \end{tabular}
-    }
-    \label{tab:procedure}
-\end{table}
 
@@
 
+\section{Experimental Evaluation}
+\label{sec:Evaluation}
+This section discusses experimental results.
+To analyze the advantages of the proposed framework, we evaluated the following.
+\begin{itemize}
+%    \item Execution time of the platform
+    \item Size and time of transferred mruby bytecodes by the Bluetooth loader
+    \item Execution time with singletasking, co-routine, and proposed multitasking
+    \item Overhead for periodic time
+    \item Synchronization of multiple RiteVM tasks
+    \item Code size with CBD 
+\end{itemize}
+
+These evaluations were performed to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to singletasking or co-routine, and that the initiation of mruby applications are synchronized.
+In addition, we focused on benefits of CBD.
+We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
+\caption{Comparison of application execution time with singletask, co-routine, and multitask}
+\label{fig:comparison_s_c_m}
+\end{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
+\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
+\label{fig:comparison_msec}
+\end{figure}
+
+\subsection{Improving Software Development Efficiency by Bluetooth Loader}
 The Bluetooth loader for mruby bytecode can reduce the development time.
 With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
-In the proposed framework, the development procedure is shortened as shown Table \ref{tab:procedure}
 For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
 In addition, the proposed framework eliminates the need to restart the target RTOS.
-Note that the time of restarting the RTOS, including initializing device drivers, is 4 sec in case of the EV3 platform \cite{par:EV3}
 
@@
 \subsection{RiteVM Scheduler}
-
 A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
@@
 \subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/comparison_s_c_m.eps}
-\caption{Comparison of application execution time with singletask, co-routine, and multitask}
-\label{fig:comparison_s_c_m}
-\end{figure}
-
 Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
@@
 \subsubsection{Periodic Time Overhead}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/comparison_msec.eps}
-\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
-\label{fig:comparison_msec}
-\end{figure}
-
 Fig.\ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
@@
 
-\subsection{Synchronization of Multiple RiteVM Tasks}
-
  \begin{figure}[t]
@@
 \end{figure}
-
-To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
-We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
-It was confirmed that the time was within the theoretical value. Theoretical value is 
-\begin{displaymath}
-    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
-\end{displaymath}
-Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
-% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
-% The periodic time is one msec, and the number of RiteVM is four.
-Note that the periodic time is 1 msec.
-As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
-
-\subsection{Benefits of Component-Based Development}
 
@@
 
+\subsection{Synchronization of Multiple RiteVM Tasks}
+To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
+We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
+It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
+Fig.\ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
+% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
+% The periodic time is one msec, and the number of RiteVM is four.
+The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
+As shown in Fig.\ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.
+
+\subsection{Benefits of Component-Based Development}
 In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
@@
 It is a dialect of ECMAScript (a.k.a. JavaScript).
-ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
+ChaiScript is header only, that is, it only needs to include the header files in order to use it in an application.
 ChaiScript will support co-routines, but not now.
@@
 In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
-Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied to scripting languages other than mruby if the VM mechanism is used.
+Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied scripting languages other than mruby if VM mechanism is used.
 
-\section{Actual Results}
+\section{Utilization Results}
 \label{sec:Results}
 The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
-In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.
+In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.
 
@@
 \label{sec:Conclusion}
-This paper presented an extended framework of mruby on TECS.
-In the proposed framework, we implement a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
-The Bluetooth loader improves the software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on the target device.
-The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
-The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
-Our experimental results show the advantages of the proposed framework.
-The Bluetooth loader can improve the software development efficiency of mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
+This paper presents an extended framework of mruby on TECS, i.e., the proposed framework implements a Bluetooth loader for mruby bytecode and a RiteVM scheduler.
+The Bluetooth loader improves software development efficiency by eliminating the need to rewrite a storage/ROM device and restart an RTOS.
+The proposed framework can be applied to various embedded systems because the loader can use both Bluetooth and a wired serial connection.
+%Thus, the proposed framework can be utilized on the devices without Bluetooth.
+The RiteVM scheduler simplifies multitasking compared to the current mruby on TECS.
+Our experimental results for the Bluetooth loader and RiteVM scheduler show their advantages.
+The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
 In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.
@@
 Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
-For software developed with fixed-priority-based scheduling, developers only have to remove the RiteVM scheduler.
+For software developed with fixed-priority based scheduling, developers only have to remove the RiteVM scheduler.
 % Component-based development can increase productivity.

### 2016-12-16 jssst/diff/1027.tex
Update

--- 2016-12-16 jssst/diff/1025.tex
@@
 
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilize two technologies i.e., mruby and TECS.
+In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.
+
 \subsection{mruby}
@@
 \label{sec:mruby on TECS}
-% mruby on TECS is a component-based framework for running script language.
-% This framework uses two technologies, mruby and TECS.
+mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
+This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using script language without slowdown of the execution time.
 
-\subsubsection{System Model}
+\subsubsection{System Model of mruby on TECS}
 The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
@@
 \begin{itemize}
-%    \item Execution time of the platform
+    \item Execution time of the platform
     \item Size and time of transferred mruby bytecodes by the Bluetooth loader
@@
 
-\section{Utilization Results}
+\section{Actual Results}
 \label{sec:Results}

### 2016-12-16 ISORC2017/diff/20161216.tex
Add 20161216.tex

--- 2016-12-16 ISORC2017/paper.tex
@@
 TINET is a TCP/IP protocol stack for embedded systems.
-TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
+Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
 Therefore, it is difficult to maintain, extend, and analysis the software.
@@
 To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
-The component-based TINET provides software developers high productivity such as change of network buffer size and add/remove TCP (or UDP) function.
-We evaluate the component-based TINET compared with the original TINET, and confirm that the overheads of execution time and memory consumption are low and  that the configurability is improved.
+The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
+We evaluate the component-based TINET compared with the original TINET.
+We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.
 
@@
 TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
-TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
+TINET needs only small memory for its TCP/IP protocol stack; therefore it is suitable for embedded systems.
 However, there are several issues that TINET consists of many complex source codes.
-It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.
+In other words, TINET is composed of many files and defines many macros.
+This may take a lot of time for software developers to maintain, extend, and analysis the software.
 
@@
 Component-based systems are flexible to software extension and specification changes.
-In addition, individual Component diagrams enable the visualization of an entire system.
+In addition, individual component diagrams enable the visualization of an entire system.
 
@@
 TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
-TECS supports static configuration, that component behaviors and interconnections are defined statically, thus TECS can optimize the overhead of componentization.
+TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
 
@@
     \item {\bf Improve configurability}\mbox{}\\
-        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resize network buffer, add/remove TCP (or UDP) functions, and support both IPv4 and IPv6.
+        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and support both IPv4 and IPv6.
         In addition, a component diagram provides visualization of TINET, a complicated system.
@@
 TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
-To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
+To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
 
@@
 TECS is a component system suitable for embedded systems.
-TECS can increase productivity and reduce development costs due to improved reusability of software components.
+TECS can increase productivity and reduce development costs owing to improved reusability of software components.
 TECS also provides component diagrams, which help developers visualize the overall structure of a system.
@@
 The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
+Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
 
@@
 
-In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+In TECS, components are described with component description language (CDL).
+CDL can be divided into three categories: {\it signature}, {\it celltype}, and build description.
 These components are described as follows.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig.\ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output respectively.
 \begin{figure}[t]
@@
         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
-        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
+        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
         {\it C\_EXP} calls macros defined in C files.
@@
 
-\subsection{send, receive specifier}
+\subsection{send/receive specifier}
 
-TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
-TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.
+TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
+TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.
 
-in is a specifier for input arguments.
-A callee side uses the memory of arguments with in while executing the callee function.
+{\it in} is a specifier for input arguments.
+A callee side uses the memory of arguments with {\it in} during executing the callee function.
 When the processing returns to the caller side, the caller can reuse and deallocate the memory.
 
-send is also a specifier for transferring data to a callee from a caller such as in.
-The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
-In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
-On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.
+{\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
+The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
+On the other hand, in case of {\it send}, the caller allocates the data memory and the callee deallocates it.
 
-out is a specifier for output arguments.
+{\it out} is a specifier for output arguments.
 A callee writes data in the memory allocated by a caller, and the caller receives the data.
 
-receive is also a specifier for a caller receiving data from a callee such as out.
-The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
-While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
+{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
+The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
 Deallocating the memory is performed in the caller in both cases.
@@
 TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
-An adapter connects a TECS component, links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
+An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
 Software developers can utilize an existing application for TECS owing to the adapter.

### 2016-12-22 ISORC2017/paper.tex
Update variously

@@
 \author{\IEEEauthorblockN{Takuro Yamamoto}
-\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
+\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
 \and
@@
 \IEEEauthorblockN{Takuya Azumi}
-\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
+\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
 }
@@
 Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
-
 TINET is a TCP/IP protocol stack for embedded systems.
-TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
+Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
 Therefore, it is difficult to maintain, extend, and analysis the software.
@@
 Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
-Therefore, embedded network software is required for the high productivity and quality.
+It is not practical to implement the same communication function as a general computer because embedded systems have several restrictions such as low memory capacity.
 
@@
 TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
-TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
+TINET needs only small memory for its TCP/IP protocol stack; therefore it is suitable for embedded systems.
 However, there are several issues that TINET consists of many complex source codes.
-It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.
+In other words, TINET is composed of many files and defines many macros.
+This may take a lot of time for software developers to maintain, extend, and analysis the software.
+Embedded network software is required for the high productivity and quality.
 
@@
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:Basic Technology} introduces the basic technologies, i.e., TINET and TECS.
+Section \ref{sec:System Model} introduces the system model and basic technologies, i.e., TINET and TECS.
 Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
@@
 
-\section{Basic Technology}
-\label{sec:Basic Technology}
+\section{System Model}
+\label{sec:System Model}
+
+This section describes system model, including the basic technologies such as TINET and TECS.
+System model of the proposed system is shown as Fig. \ref{fig:System Model}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
+    \caption{System model}
+    \label{fig:SystemModel}
+\end{figure}
 
@@
 TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
-To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
+TINET has been released as open source.
+
+\subsubsection{Overview}
+
+TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
+Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
+
+To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
 
@@
 
-TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
-TINET has been released as open source.
-
-\subsubsection{Overview}
-
-Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
-
 \begin{figure}[t]
@@
     \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
-    \caption{Hierarchy Diagram of TINET and TOPPERS/ASP3}
+    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
     \label{fig:TINET_Hier}
@@
 
-\subsection{send, receive specifier}
+\subsection{Component of protocol stack}
 
-TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
-TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/ComponentProtocolStack.pdf}
+    \caption{Component diagram of protocol stack}
+    \label{fig:ComponentProtocolStack}
+\end{figure}
 
-in is a specifier for input arguments.
-A callee side uses the memory of arguments with in while executing the callee function.
+\subsection{send/receive specifier}
+
+TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
+TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.
+
+{\it in} is a specifier for input arguments.
+A callee side uses the memory of arguments with {\it in} during executing the callee function.
 When the processing returns to the caller side, the caller can reuse and deallocate the memory.
 
-send is also a specifier for transferring data to a callee from a caller such as in.
-The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
-In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
-On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.
+{\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
+The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
+On the other hand, in case of {\it send}, the caller allocates the data memory and the callee deallocates it.
 
-out is a specifier for output arguments.
+{\it out} is a specifier for output arguments.
 A callee writes data in the memory allocated by a caller, and the caller receives the data.
 
-receive is also a specifier for a caller receiving data from a callee such as out.
-The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
-While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
+{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
+The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
 Deallocating the memory is performed in the caller in both cases.
@@
 
+Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}.
+
+{\bf uIP:}
+uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
+uIP only requires about five kilobytes of code size and several hundred bytes of RAM.
+uIP has been ported to various systems and has found its way into many commercial products.
+After ver.
+1.0 is released, later versions of uIP, including uIPv6, are integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontroller to the Internet.
+
+{\bf lwIP:}
+lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems.
+The focus of lwIP is to reduce memory resource while still having a full scale TCP.
+lwIP requires about 40 kilobytes of ROM and tens of kilobytes of RAM.
+lwIP is larger than uIP, but provides better throughput.
+
+{\bf CiAO/IP:}
+
 \section{Conclusion}

### 2016-12-23 ISORC2017/paper.tex
Update paper.tex

@@
 % affiliations
-\author{\IEEEauthorblockN{Takuro Yamamoto}
+\author{
+\IEEEauthorblockN{Takuro Yamamoto}
 \IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
@@
 \IEEEauthorblockN{Takuma Hara}
-\IEEEauthorblockA{}
+\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
 \and
 \IEEEauthorblockN{Takuya Ishikawa}
-\IEEEauthorblockA{}
+\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
 \and
@@
 \IEEEauthorblockN{Hiroaki Takada}
-\IEEEauthorblockA{}
+\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
 \and
@@
 % 
-% \author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-% Homer Simpson\IEEEauthorrefmark{2},
-% James Kirk\IEEEauthorrefmark{3}, 
-% Montgomery Scott\IEEEauthorrefmark{3} and
-% Eldon Tyrell\IEEEauthorrefmark{4}}
-% \IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-% Georgia Institute of Technology,
-% Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-% \IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-% Email: homer@thesimpsons.com}
-% \IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-% Telephone: (800) 555--1212, Fax: (888) 555--1212}
-% \IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+% \author{
+% \IEEEauthorblockN{
+% Takuro Yamamoto\IEEEauthorrefmark{1},
+% Takuma Hara\IEEEauthorrefmark{2},
+% Takuya Ishikawa\IEEEauthorrefmark{2}, 
+% Hiroshi Oyama\IEEEauthorrefmark{3},
+% Hiroaki Takada\IEEEauthorrefmark{2} and
+% Takuya Azumi\IEEEauthorrefmark{1}}
+% \IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
+% \IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
+% \IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
+% }
 
@@
 Component-based development is an approach to improve software productivity.
-Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+Component-based development is a design technique that can be applied to reusable software development \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
 Component-based systems are flexible to software extension and specification changes.
@@
 TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
+This paper evaluates the overheads of execution time and memory consumption and amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
 
@@
     \item {\bf Support legacy codes}\mbox{}\\
-        TECS supports the adapter to call TECS functions from C codes, thus TINET+TECS can use an existing application.
+        TECS supports the adapter to call TECS functions from existing C codes, thus TINET+TECS can be applied to an existing application.
     % \item {\bf Software visualization}
@@
     \caption{System model}
-    \label{fig:SystemModel}
+    \label{fig:System Model}
 \end{figure}
@@
 
-\subsubsection{Overview}
-
-TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, a realtime kernel.
-Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
-TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
-
 To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
 
-\begin{enumerate}
+\begin{itemize}
     \item Minimum copy frequency
@@
     \item Error detailed per API
-\end{enumerate}
+\end{itemize}
+
+\subsubsection{Overview}
+
+TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
+TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
+Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+% TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
+Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
+In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
+In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.
+
+In TINET, the number of the data copy between each protocol layers is minimized.
+A TCP/IP protocol stack for general computers has large overheads of execution time and memory consumption because the data is copied at each protocol layers.
+To solve the problem, TINET does pass the pointer of the data buffer between each protocol layers, not perform data copy.
 
@@
 
-\subsection{Component of protocol stack}
+TINET+TECS, the proposed componentized TCP/IP protocol stack, consists of some TECS components.
+This section describes the components with component diagrams.
+In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.
+
+\subsection{Components of protocol stack}
 
@@
 
-TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
+TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
 An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.

### 2017-01-05 ISORC2017/paper.tex
Update paper.tex

@@
 % affiliations
-\author{
-\IEEEauthorblockN{Takuro Yamamoto}
-\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
-\and
-\IEEEauthorblockN{Takuma Hara}
-\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
-\and
-\IEEEauthorblockN{Takuya Ishikawa}
-\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
-\and
-\IEEEauthorblockN{Hiroshi Oyama}
-\IEEEauthorblockA{OKUMA Corporation}
-\and
-\IEEEauthorblockN{Hiroaki Takada}
-\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
-\and
-\IEEEauthorblockN{Takuya Azumi}
-\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
-}
+% \author{
+% \IEEEauthorblockN{Takuro Yamamoto}
+% \IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
+% \and
+% \IEEEauthorblockN{Takuma Hara}
+% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
+% \and
+% \IEEEauthorblockN{Takuya Ishikawa}
+% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
+% \and
+% \IEEEauthorblockN{Hiroshi Oyama}
+% \IEEEauthorblockA{OKUMA Corporation}
+% \and
+% \IEEEauthorblockN{Hiroaki Takada}
+% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
+% \and
+% \IEEEauthorblockN{Takuya Azumi}
+% \IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
+% }
 
@@
 % 
-% \author{
-% \IEEEauthorblockN{
-% Takuro Yamamoto\IEEEauthorrefmark{1},
-% Takuma Hara\IEEEauthorrefmark{2},
-% Takuya Ishikawa\IEEEauthorrefmark{2}, 
-% Hiroshi Oyama\IEEEauthorrefmark{3},
-% Hiroaki Takada\IEEEauthorrefmark{2} and
-% Takuya Azumi\IEEEauthorrefmark{1}}
-% \IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
-% \IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
-% \IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
-% }
+\author{
+\IEEEauthorblockN{
+Takuro Yamamoto\IEEEauthorrefmark{1},
+Takuma Hara\IEEEauthorrefmark{2},
+Takuya Ishikawa\IEEEauthorrefmark{2}, 
+Hiroshi Oyama\IEEEauthorrefmark{3},
+Hiroaki Takada\IEEEauthorrefmark{2} and
+Takuya Azumi\IEEEauthorrefmark{1}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
+\IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
+}
 
@@
 TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
-This paper evaluates the overheads of execution time and memory consumption and amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
+This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
 
@@
 
+The components of protocol stack for TINET+TECS is shown as Fig. \ref{fig:ComponentProtocolStack}.
+Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
+In TINET+TECS, the components are divided for each protocol, and the functionalities such as input function and output function are defined as each a component.
+Therefore, software visibility is improving because of small grain components.
+
+To utilize the protocol stack as same as the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
+The communication object component is a component corresponding to a CEP or REP of the original TINET.
+An application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
+
+The protocol stack of TINET+TECS supports coexistence of multiple protocols.
+By developing the IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without a modification of component implementation.
+
 \begin{figure}[t]
@@
 
-\subsection{send/receive specifier}
+\subsection{Memory allocator component}
+
+\subsubsection{send/receive specifier}
 
@@
 
+\subsection{Network timer component}
+
 \subsection{TECS Adapter}
@@
 
+\subsection{Evaluation environment}
+
+GR-PEACH is employed as the evaluation board.
+We connected the board and the host PC with a LAN cable, and evaluated the data transmission and reception.
+The detail specification of the board is shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
+We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2.
+
 \begin{table}[t]
@@
     \end{tabular}
-    \label{tab:Evaluation_Board_Environment}
+    \label{tab:EvaluationBoardEnvironment}
 \end{table}
@@
 
+The authers would like to thank OO for supporting this research.
+This work is supported by JSPS KAKENHI Grant Number 15H05305.
+
 % trigger a \newpage just before the given reference

### 2017-01-06 jssst/paper.tex
Add Chosha Shoukai

@@
 
-% \begin{choshashoukai}
-%
-% \chosha{山本拓朗}
-% {2016年大阪大学基礎工学部システム科学科卒．
-% }
-% \chosha{大山博司}
-% {
-% }
-% \chosha{安積卓也}
-% {
-% }
-%
-% \end{choshashoukai}
+\begin{choshashoukai}
+
+\chosha{Takuro Yamamoto}
+{
+Takuro Yamamoto received his B.E. degree from Osaka University in 2016. His research interests include real-time and embedded systems.
+}
+\chosha{Hiroshi Oyama}
+{
+Hiroshi Oyama received Dr. Engineering degree from Gifu University in 2002.
+He works at Okuma Corporation as Senior Engineer and also works at Nagoya University as Visiting Professor.
+He is studying software components and programming language for embedded systems.
+}
+\chosha{Takuya Azumi}
+{
+Takuya Azumi is an Assistant Professor at the Graduate School of Engineering Science, Osaka University. 
+He received his Ph.D. degree from the Graduate School of Information Science, Nagoya University.
+From 2008 to 2010, he was under the research fellowship for young scientists for Japan Society for the Promotion of Science.
+From 2010 to 2014, he was an Assistant Professor at the College of Information Science and Engineering, Ritsumeikan University.
+His research interests include real-time operating systems and component based development.
+He is a member of IEEE, ACM, IPSJ, and IEICE.
+}
+
+\end{choshashoukai}
 

### 2017-01-11 jssst/paper.tex
Modify the points by reviewers

@@
 
-{\bf Contributions}: The proposed framework provides the following contributions:
+{\bf Contributions}: The proposed framework provides the following contributions.
 \begin{enumerate}
-\item {\bf Improved software development efficiency.}
+\item {\bf Improved software development efficiency:}
 Developers do not need to rewrite a storage/ROM device and restart an RTOS.
 The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
-\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
+\item {\bf Execution of multiple mruby programs concurrently or in parallel:}
 Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
-\item {\bf Synchronized execution of multiple RiteVM tasks.}
+\item {\bf Synchronized execution of multiple RiteVM tasks:}
 The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
@@
 \label{sec:Background}
-Fig.\ref{fig:proposed} shows the system model of the proposed framework.
+Fig. \ref{fig:proposed} shows the system model of the proposed framework.
 Note that the RiteVMs and the mruby library are assumed to be prepared in advance.
@@
 In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
-The mruby/RiteVM mechanism is shown in Fig.\ref{fig:mruby}.
+The mruby/RiteVM mechanism is shown in Fig. \ref{fig:mruby}.
 The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
@@
 \subsubsection{Component Model}
-Fig.\ref{fig:component} shows a component diagram.
+Fig. \ref{fig:component} shows a component diagram.
 A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig. \ref{signature}).
         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
@@
         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig. \ref{celltype}).
         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
@@
         The build description is used to instantiate and connect {\it cell}s.
-        Fig.\ref{build} shows an example of a build description.
+        Fig. \ref{build} shows an example of a build description.
         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
         {\it C\_EXP} calls macros defined in C files.
@@
 \subsubsection{System Model of mruby on TECS}
-The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
+The present mruby on TECS system model is shown in Fig. \ref{fig:mrubyontecs}.
 Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
@@
 
-Fig.\ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
+Fig. \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
 The left side of BridgeMotor belongs to the mruby program.
@@
 \label{sec:Design and Implementation}
-Fig.\ref{fig:system_model} shows the detailed system model of the proposed framework.
+Fig. \ref{fig:system_model} shows the detailed system model of the proposed framework.
 Each mruby application bytecode transferred from the host to the target device is received by the loader in the RiteVM.
@@
 
-Fig.\ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
+Fig. \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
 The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
@@
 \label{fig:control_flow}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-/* tRiteVMBluetooth.cdl */
-celltype tRiteVMBluetooth1 {
-    entry sTaskBody eMrubyBody;
-    [optional] call sEventflag cEventflag[];
-    [optional] call sSemaphore cSemaphore;
-    attr {
-      [omit]char_t *mrubyLib;
-      char_t *irepLib = 
-                C_EXP("&$cell_global$_irep");
-      uint32_t irepAppSize = 
-                C_EXP( BUFFER_SIZE );
-      FLGPTN setptn;
-    };
-    var {
-        mrb_state *mrb;
-        mrbc_context *context;
-        [size_is(irepAppSize)] uint8_t *irepApp;
-    };
-};
-\end{lstlisting}
-\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
-\label{celltype_mrubybluetooth}
 \end{figure}
@@
 
-Fig.\ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
-The main tRiteVMBluetooth code is shown in Fig.\ref{maincode_mrubybluetooth}.
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+/* tRiteVMBluetooth.cdl */
+celltype tRiteVMBluetooth1 {
+    entry sTaskBody eMrubyBody;
+    [optional] call sEventflag cEventflag[];
+    [optional] call sSemaphore cSemaphore;
+    attr {
+      [omit]char_t *mrubyLib;
+      char_t *irepLib = 
+                C_EXP("&$cell_global$_irep");
+      uint32_t irepAppSize = 
+                C_EXP( BUFFER_SIZE );
+      FLGPTN setptn;
+    };
+    var {
+        mrb_state *mrb;
+        mrbc_context *context;
+        [size_is(irepAppSize)] uint8_t *irepApp;
+    };
+};
+\end{lstlisting}
+\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
+\label{celltype_mrubybluetooth}
+\end{figure}
 
-First, the Bluetooth loader receives the mruby application bytecode from the host (Fig.\ref{fig:control_flow}(A); lines 5-6 in Fig.\ref{maincode_mrubybluetooth}).
-The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Fig.\ref{celltype_mrubybluetooth}.
+Fig. \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
+The main tRiteVMBluetooth code is shown in Fig. \ref{maincode_mrubybluetooth}.
+
+First, the Bluetooth loader receives the mruby application bytecode from the host (Fig. \ref{fig:control_flow}(A); lines 5-6 in Fig. \ref{maincode_mrubybluetooth}).
+The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Fig. \ref{celltype_mrubybluetooth}.
 This process is exclusively carried out by the semaphore to prevent the other loading from interrupting.
 
-Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Fig.\ref{fig:control_flow}(B); lines 8-13 in Fig.\ref{maincode_mrubybluetooth}).
+Second, {\it mrb\_state} and {\it mrbc\_context} pointers, and mruby-TECS bridges are initialized (Fig. \ref{fig:control_flow}(B); lines 8-13 in Fig. \ref{maincode_mrubybluetooth}).
 {\it VAR\_mrb} and {\it VAR\_context} show the variables of the {\it cell}.
@@
 
-Third, the RiteVM reads the bytecode of mruby libraries (Fig.\ref{fig:control_flow}(C); lines 16-19 in Fig.\ref{maincode_mrubybluetooth}).
+Third, the RiteVM reads the bytecode of mruby libraries (Fig. \ref{fig:control_flow}(C); lines 16-19 in Fig. \ref{maincode_mrubybluetooth}).
 The mruby libraries are a set of Ruby classes, such as the motor and sensor classes.
 For example, the motor class defines methods to rotate and stop a motor.
-The tRiteVMBluetooth {\it cell} has the attributes shown in Fig.\ref{celltype_mrubybluetooth}.
+The tRiteVMBluetooth {\it cell} has the attributes shown in Fig. \ref{celltype_mrubybluetooth}.
 {\it ATTR} indicates an attribute which is a fixed value that cannot be rewritten, unlike {\it VAR}.
@@
 
-Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Fig.\ref{fig:control_flow}(D); lines 20-23 in Fig.\ref{maincode_mrubybluetooth}).
+Fourth, the RiteVM reads the bytecode of the mruby application transferred via Bluetooth (Fig. \ref{fig:control_flow}(D); lines 20-23 in Fig. \ref{maincode_mrubybluetooth}).
 The mruby application bytecode is stored in an array of {\it irepApp}, which differs from the array that holds the mruby library bytecode.
@@
 
-Finally, the mruby task runs (Fig.\ref{fig:control_flow}(E); lines 20-23 in Fig.\ref{maincode_mrubybluetooth}).
+Finally, the mruby task runs (Fig. \ref{fig:control_flow}(E); lines 20-23 in Fig. \ref{maincode_mrubybluetooth}).
 When an mruby application is modified, only the bytecode of the modified application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
 
-The process shown in Fig.\ref{maincode_mrubybluetooth} (lines 24-29) is carried out when an exception occurs.
-When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 32-35 in Fig.\ref{maincode_mrubybluetooth}).
+The process shown in Fig. \ref{maincode_mrubybluetooth} (lines 24-29) is carried out when an exception occurs.
+When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 32-35 in Fig. \ref{maincode_mrubybluetooth}).
 The proposed framework supports continuous loading; thus, this process loops.
@@
 In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
-The design of the RiteVM scheduler is shown in Fig.\ref{fig:rotateReadyQueue}. 
+The design of the RiteVM scheduler is shown in Fig. \ref{fig:rotateReadyQueue}. 
 {\it rotateReadyQueue} is described as follows.
@@
 
-When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Fig.\ref{fig:rotateReadyQueue}.
+When {\it rotateReadyQueue} is called, tasks with equal priority are switched as shown in Fig. \ref{fig:rotateReadyQueue}.
 Note that the argument of {\it rotateReadyQueue} is the priority.
@@
 
-Fig.\ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
+Fig. \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
 The RiteVM scheduler is a {\it composite cell} which consists of CyclicHandler and RiteVMSchedulerMain.
@@
 Note that {\it rotateReadyQueue} is implemented as the body.
-Fig.\ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
+Fig. \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
 The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
@@
 
-Fig.\ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
+Fig. \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
 The RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
@@
 This process can also be applied to more tasks.
-For example, for four RiteVM tasks, each task sets a flag pattern, such as 0x01 (0001), 0x02 (0010), 0x04 (0100), and 0x08 (1000), and then waits 0x0f (1111) with AND, as shown in Fig.\ref{fig:Eventflag}(A).
+For example, for four RiteVM tasks, each task sets a flag pattern, such as 0x01 (0001), 0x02 (0010), 0x04 (0100), and 0x08 (1000), and then waits 0x0f (1111) with AND, as shown in Fig.
+\ref{fig:Eventflag}(A).
 
@@
 In the proposed framework, this advantage is applied in the Eventflag component.
-The set pattern and wait pattern are defined as attributes of the component as shown in Fig.\ref{fig:Eventflag} (B).
+The set pattern and wait pattern are defined as attributes of the component as shown in Fig. \ref{fig:Eventflag} (B).
 This design, e.g., {\it cEventflag\_set(ATTR\_setPattern)}, enables the program without ``if'' statements and reuses an identical C file.
@@
 
-% A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig.\ref{fig:comparison_s_c_m}.
+% A comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Fig. \ref{fig:comparison_s_c_m}.
 % A program with 100,000 loops was used as an mruby application for the evaluation of execution time.
@@
 
-Fig.\ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
+Fig. \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
 The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
 The scheduler runs as the periodic handler of RTOS.
-% In Fig.\ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
+% In Fig. \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
 % This shows that the proposed design is superior to co-routine in terms of execution time.
@@
 
-Fig.\ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
+Fig. \ref{fig:comparison_msec} shows the execution time of multitasking with the periodic handler.
 The lower limit of the periodic time is 1 msec due to the specifications of TOPPERS/HRP2, i.e., the RTOS.
@@
 To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
-We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
-It was confirmed that the time was within the theoretical value which is 
+We measured the execution time from the execution of the first RiteVM task to that of the last RiteVM task.
+Fig. \ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
+Note that the periodic time is 1 msec.
+It was confirmed that the execution time was within the theoretical value which is 
 \begin{displaymath}
@@
 \end{displaymath}
-Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
-% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
-% The periodic time is one msec, and the number of RiteVM is four.
-Note that the periodic time is 1 msec.
-As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
+In the case of two RiteVM tasks, the theoretical value is 1 msec and the execution time does not exceed the theoretical value. 
+As shown in Fig. \ref{fig:eval_synchronization}, the execution time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
 
@@
 To demonstrate the superiority of CBD, a comparison of the number of lines of codes C and ACL codes between two situations is shown in Table \ref{tab:codesize}.
-In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig.\ref{fig:Eventflag}, respectively. 
+In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig. \ref{fig:Eventflag}, respectively. 
 For C, (B)'s code lines do not increase even if the number of RiteVMs increases, while (A)'s code lines increase as the number of RiteVMs increases.

### 2017-01-11 jssst/reply_letter.tex
Add reply letter

\documentclass{article}

\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{fancybox}
\usepackage{ascmac}
\usepackage{xspace}
%\usepackage{pdfpages}
\usepackage{pifont}
\usepackage{array}

\newcommand\st{\textsuperscript{st}\xspace}
\newcommand\nd{\textsuperscript{nd}\xspace}
\newcommand\rd{\textsuperscript{rd}\xspace}

\begin{document}

% cover letter
\begin{flushleft}
  2017-01-13\newline 
  ソフトウェア論文特集\newline
  論文・記事番号：16-S-05\newline
  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
\end{flushleft}
\textbf{Dear Editor and Reviewer,}\newline

We highly appreciate the insightful suggestions and detailed valuable comments on our paper. 
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.\newline\newline

\begin{flushleft}
  Yours sincerely,\newline

  Takuro Yamamoto\newline
  Osaka University\newline
  Email address: t-yamamoto@hopf.sys.es.osaka-u.ac.jp\newline
\end{flushleft}

\clearpage

\section{Response to 1\st reviewer}

\begin{enumerate}

\item \begin{flushleft}
    \textbf{Comment:
}初見では、Fig.21 をどう解釈すればよいかが分かりにくかったです。
図の解釈について説明を追加いただければ、多くの読者にとってわかりやすくなると思います。
  \end{flushleft}

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
We have added and modified the section as follows. (page 13)

\begin{itembox}[|]{4.3 Synchronization of Multiple RiteVMs}
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the execution time from the execution of the first RiteVM task to that of the last RiteVM task.
Fig. 21 shows the case of two to eight RiteVM tasks.
Note that the periodic time is 1 msec.
It was confirmed that the execution time was within the theoretical value which is {\it\scriptsize periodic time $\times$ (number of RiteVM tasks - 1).}
In the case of two RiteVM tasks, the theoretical value is 1 msec and the execution time does not exceed the theoretical value. 
As shown in Fig. 21, the execution time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
\end{itembox}\\
  \end{flushleft}

\item \begin{flushleft}
    \textbf{Comment:}
3ページ左カラムの下から2行目で「4. Benets of CBD:」で始まっていますが、他の項目は「.」で終わっています。
この点、ご確認ください。
  \end{flushleft}

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your careful reading.
We have modified other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
  \end{flushleft}

\end{enumerate}

\newpage

\section{Response to 2\nd reviewer}

\begin{enumerate}

\item \begin{flushleft}
    \textbf{Comment:}
Figure 11 seems to be a wrong diagram.
Maybe this is an old version.
Please replace it with a correct one so that A, B, C, D matches to the description in the text.
  \end{flushleft}

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
As you said, we used the different figure.
We have replaced it with the correct figure. (page 7)
  \end{flushleft}

\item \begin{flushleft}
    \textbf{Comment:}
The first reference of Figure 12 from the text is after Figure 13 is refereed.
Please change the order.
  \end{flushleft}

  \begin{flushleft}
    \textbf{Our reply:}
Thank you for your suggestion.
We have switched the order of Fig. 12 and Fig. 13. (page 7-8)
  \end{flushleft}

\end{enumerate}

\end{document}

### 2017-01-11 jssst/reply_letter.tex
Modify the reply letter

@@
   著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
-\end{flushleft}
-\textbf{Dear Editor and Reviewer,}\newline
-
-We highly appreciate the insightful suggestions and detailed valuable comments on our paper. 
-The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
-We have attached the last paper review and revised paper in our reply letter.
-We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.\newline\newline
-
-\begin{flushleft}
-  Yours sincerely,\newline
-
-  Takuro Yamamoto\newline
-  Osaka University\newline
-  Email address: t-yamamoto@hopf.sys.es.osaka-u.ac.jp\newline
-\end{flushleft}
-
-\clearpage
 
@@
 
-\newpage
-
 \section{Response to 2\nd reviewer}

### 2017-01-17 jssst/paper.tex
Final version (最終原稿)

@@
                             & Development procedure \\ \hline
-        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
+        Existiting framework &    (1) + (2) + (3)    \\ %\hline
         Proposed framework  &          (4)          \\ \hline
@@
 %\subsubsection{Code size utilizing component-based development}
-To demonstrate the superiority of CBD, a comparison of the number of lines of codes C and ACL codes between two situations is shown in Table \ref{tab:codesize}.
+To demonstrate the superiority of CBD, a comparison of the number of lines of C and CDL codes between two situations is shown in Table \ref{tab:codesize}.
 In Table \ref{tab:codesize}, (A) and (B) represent the source files in the upper and lower parts of Fig. \ref{fig:Eventflag}, respectively. 
@@
 In the future, CDL files for the RiteVM and mruby-TECS bridge will be generated automatically using a plugin, and developers will be able to transfer bytecodes using the ZMODEM protocol on the command line.
-Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
+Moreover, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.\newline
 
 %%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgement}
-
+% \section*{Acknowledgement}
+{\bf Acknowledgement}\ 
 This work was supported by JSPS KAKENHI Grant Number 15H05305.
@@
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{abbrv}
+\bibliographystyle{article/jssst}
 \bibliography{ref}

### 2017-01-17 jssst/reply_letter.tex
Final version (最終原稿)

--- 2017-01-11 jssst/reply_letter.tex
@@
 \end{flushleft}
+
 \textbf{Dear Editor and Reviewer,}\newline
@@
 We have attached the last paper review and revised paper in our reply letter.
-We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.\newline\newline
+In the revised paper, newly added and modified sentences are written in the bold and red colored font so that the reviewers can easily find them.
+We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.
+\newline\newline
 
@@
     \textbf{Our reply:}
-Thank you for your suggestion.
+Thank you for your thoughtful suggestion.
 We have added and modified the section as follows. (page 13)
@@
     \textbf{Our reply:}
-Thank you for your careful reading.
-We have modified other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
+Thank you for pointing out the wrong expression.
+We have modified the other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
   \end{flushleft}
@@
 \end{enumerate}
-
-\newpage
 
@@
     \textbf{Our reply:}
-Thank you for your suggestion.
+Thank you very much for your careful reading.
 As you said, we used the different figure.
@@
     \textbf{Our reply:}
-Thank you for your suggestion.
+Thank you for your thoughtful comment.
 We have switched the order of Fig. 12 and Fig. 13. (page 7-8)

### 2017-01-24 ISORC2017/diff/20170123.tex
Add diff of 20170123

--- 2017-01-05 ISORC2017/paper.tex
@@
     language={c},%
-    basicstyle={\small\ttfamily},%
-    identifierstyle={\small},%
+    basicstyle={\footnotesize\ttfamily},%
+    identifierstyle={\footnotesize},%
     commentstyle={\footnotesize\itshape},%
-    keywordstyle={\small},%\bfseries},%
-    ndkeywordstyle={\small},%
-    stringstyle={\small\it},
+    keywordstyle={\footnotesize},%\bfseries},%
+    ndkeywordstyle={\footnotesize},%
+    stringstyle={\footnotesize\it},
     frame={tb},
@@
 Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
-It is not practical to implement the same communication function as a general computer because embedded systems have several restrictions such as low memory capacity.
+It is not practical to implement the same TCP/IP protocol stack as a general computer because embedded systems have several restrictions such as low memory capacity.
 
@@
 
-In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
+This paper proposes component-based TCP/IP protocol stack, i.e., componentized TINET, to improve the configurability and scalability of software.
 TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
@@
     \item {\bf Improve configurability}\mbox{}\\
-        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and support both IPv4 and IPv6.
+        Since TINET+TECS is a component-based system, the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and supporting both IPv4 and IPv6.
         In addition, a component diagram provides visualization of TINET, a complicated system.
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
     \caption{System model}
@@
 
-TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
+TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
 TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
@@
 
+A TCP reception point called Reception Point (REP) is prepared to wait for a connection request from the partner side.
+An REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes, and performs functions like {\it bind()} and {\it listen()}.
+
 In TINET, the number of the data copy between each protocol layers is minimized.
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/TINET_Hier.pdf}
     \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
+    \includegraphics[width=7.0cm,clip]{figure/component_diagram.eps}
     \caption{Component Diagram}
@@
 
-Fig.\ref{fig:component} shows a component diagram.
+Fig. \ref{fig:component} shows a component diagram.
 A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig.\ref{signature}).
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig. \ref{signature}).
         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output respectively.
@@
         The build description is used to instantiate and connect {\it cell}s.
-        Fig.\ref{build} shows an example of a build description.
+        Fig. \ref{build} shows an example of a build description.
         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
@@
 
+This section describes design and implementation of the proposed framework, TINET+TECS.
+The proposed framework is component-based TCP/IP protocol stack for embedded systems, i.e., componentized TINET using TECS.
+In addition, A TECS novel functionality, dynamic connection method, and TECS adapter to support legacy codes are described with the use case of the proposed framework.
+
+\subsection{TINET+TECS}
 TINET+TECS, the proposed componentized TCP/IP protocol stack, consists of some TECS components.
-This section describes the components with component diagrams.
-In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.
+This section describes the components of TINET+TECS framework with component diagrams.
+% In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.
 
-\subsection{Components of protocol stack}
+\subsubsection{Components of protocol stack}
 
@@
 Therefore, software visibility is improving because of small grain components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/ComponentProtocolStack.pdf}
+    \caption{Component diagram of protocol stack}
+    \label{fig:ComponentProtocolStack}
+\end{figure}
+
+The components of each protocol are described below.\\
+
+{\bf Application layer:}
+An application in TINET+TECS is implemented as a component such as tApplication.
+Software with TINET uses ITRON TCP/IP API such as {\it tcp\_snd\_buf} and {\it tcp\_rcv\_buf}.
+In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendBuffer} and {\it cTCPAPI\_receiveBuffer}.
+Moreover, TINET+TECS supporting a TECS adapter (\ref{sec:TECS Adapter}), an exiting application with TINET can run on TINET+TECS framework without transporting.
+Therefore, software can be developed either with exiting methods or as a TECS component.
+
+{\bf Transport layer:}
+tTCPCEP (tUDPCEP) is a CEP compornent for TCP (UDP), and tREP is a REP component.
+For example, a server program supporting multiple clients can be developed by preparing the multiple tTCPCEP components.
+tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components performing the receiving and sending processing respectively in the transport layer.
+
+{\bf Network layer:}
+tIPv4Input and tIPv4Output are components performing the receiving and sending processing respectively in the network layer.
+tIPv4Functions component performs some functions such as checksum, tICMP component is for the ICMP protocol, and tIPv4RoutingTable component operates a routing table.
+
+{\bf Data link layer:}
+tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components performing the receiving and sending processing respectively in the data link layer.
+tArp component is for the ARP protocol.
+
+{\bf Physical layer:}
+tNetworkInterfaceContoroller component implements a network device driver.
+Software can run on other devices by replacing the component because only the component depends on the target device.\\
 
@@
 
+\subsubsection{Memory allocator component}
+
+The original TINET eliminates dynamic memory control to meet the sever memory restriction of embedded systems.
+A memory area for sending/receiving data in the protocol stack is allocated and released within an predetermined area.
+Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
+The component provides a requested memory area from the memory area statically allocated.
+
+The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown as Fig. \ref{fig:tMemoryAllocator}.
+tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
+tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
+On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.
+
+In addition, TINET+TECS utilizes {\it send/receive} specifier of TECS to minimize the memory copy frequency, which is a functionality supported by TINET.
+
 \begin{figure}[t]
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/ComponentProtocolStack.pdf}
-    \caption{Component diagram of protocol stack}
-    \label{fig:ComponentProtocolStack}
+    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
+    \caption{Component diagram of tMemoryAllocator}
+    \label{fig:tMemoryAllocator}
 \end{figure}
 
-\subsection{Memory allocator component}
-
-\subsubsection{send/receive specifier}
-
+{\bf send/receive specifier:}
 TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/SendReceive.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
     \caption{Differences between in/out and send/receive}
@@
 signature sNicDriver {
-  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp,
+  void start(
+    [send(sNetworkAlloc),size_is(size)]
+        int8_t *outputp,
     [in]int32_t size,
     [in]uint8_t align);
-  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp,
+  void read(
+    [receive(sNetworkAlloc),size_is(*size)]
+        int8_t **inputp,
     [out]int32_t *size,
@@
 
-\subsection{Network timer component}
+\subsubsection{Network timer component}
+
+\subsection{Dynamic Connection of TECS}
 
 \subsection{TECS Adapter}
+\label{sec:TECS Adapter}
 
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/TECS_Adapter.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
     \caption{TECS Adapter}
@@
 
-The authers would like to thank OO for supporting this research.
+The authers would like to thank H. Nagashima for supporting this research.
 This work is supported by JSPS KAKENHI Grant Number 15H05305.

### 2017-02-03 ISORC2017/paper.tex
Update

@@
 Therefore, it is difficult to maintain, extend, and analysis the software.
-
-To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
+To improve the scalability and configurability, this paper has proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
 The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
@@
 We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.
-
-In this paper, we also demonstrates a use case of the dynamic component connection method of TECS with a network application.
 
@@
 
-Internet of Things (IoT) is an essential keyword for the next era.
-Such as wearable devices, smart devices, and smart homes, various things are connected to the Internet, enriching our lives.
+Internet of Things (IoT) is an essential keyword for the next era \cite{par:IoTIndustries} \cite{par:IoTComputing}.
+Various things, such as wearable devices, smart devices, and smart homes, connected to the Internet will enrich our lives.
 Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
-It is not practical to implement the same communication function as a general computer because embedded systems have several restrictions such as low memory capacity.
+It is not practical to implement the same TCP/IP protocol stack as a general computer because embedded systems have several restrictions such as low memory capacity.
 
@@
 
-Component-based development is an approach to improve software productivity.
-Component-based development is a design technique that can be applied to reusable software development \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+An approach to improve software productivity is component-based development, which is a design technique that can be applied to reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
 Component-based systems are flexible to software extension and specification changes.
@@
 
-In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
+This paper proposes component-based TCP/IP protocol stack, i.e., TINET+TECS, to improve the configurability and scalability of software.
 TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
 TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
+
+In addition, the proposed framework utilizes dynamic connection, a novel method of TECS, to switch component bindings dynamically.
+A general TCP/IP protocol server dynamically processes the requested port i.e., HTTP (port: 80), HTTPS (prot: 443).
+However, embedded systems can not dynamically generate components due to the strict memory restriction.
+TINET+TECS statically generates components, and dynamically combines them.
+Therefore,
+
+In the proposed framework, software application can be developed by not only TECS method but also existing method.
+Software appication can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
+Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
+The legacy codes such as an existing application can be supported in the proposed framework.
+
 This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
@@
     \item {\bf Dynamic connection method}\mbox{}\\
+        Dynamically switching the binding of components, that is switching between a communication endpoint and reception point of TINET, realizes a TCP/IP protocol stack for embedded systems.
 
     \item {\bf Support legacy codes}\mbox{}\\
-        TECS supports the adapter to call TECS functions from existing C codes, thus TINET+TECS can be applied to an existing application.
+        TINET+TECS can be applied to an existing application because TECS supports the adapter to call TECS functions from C codes. 
     % \item {\bf Software visualization}
@@
 This section describes system model, including the basic technologies such as TINET and TECS.
-System model of the proposed system is shown as Fig. \ref{fig:System Model}.
+System model of the proposed framework is shown as Fig. \ref{fig:SystemModel}.
+TINET+TECS is a component-based TCP/IP protocol stack, so TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
+CEP and REP (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
+Moreover, TECS adapter supports the legacy codes such as an existing application.
 
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/SystemModel.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
     \caption{System model}
-    \label{fig:System Model}
+    \label{fig:SystemModel}
 \end{figure}
@@
 \subsection{TINET}
+\label{sec:TINET}
 
-TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
 TINET has been released as open source.
@@
 
-TINET runs as middleware on TOPPERS/ASP3 \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
+TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
 TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
-Fig. \ref{fig:TINET_Hier} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
 % TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
@@
 In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.
+
+A TCP reception point called Reception Point (REP) is prepared to wait for a connection request from the partner side.
+An REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes, and performs functions like {\it bind()} and {\it listen()}.
 
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/TINET_Hier.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
     \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
-    \label{fig:TINET_Hier}
+    \label{fig:TINETHierarchyDiagram}
 \end{figure}
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
+    \includegraphics[width=7.0cm,clip]{figure/ComponentDiagram.pdf}
     \caption{Component Diagram}
-    \label{fig:component}
+    \label{fig:ComponentDiagram}
 \end{figure}
@@
 
-Fig.\ref{fig:component} shows a component diagram.
+Fig. \ref{fig:ComponentDiagram} shows a component diagram.
 A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig.\ref{signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output respectively.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sIPv4Output (Fig. \ref{src:signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in], [out], and [inout] are used, which represent input, output, and input/output respectively.
+        [size\_is({\it len})] represents an array of size {\it len}.
 \begin{figure}[t]
@@
 \begin{lstlisting}
-signature sMotor {
-    int32_t getCounts( void );
-    ER resetCounts( void );
-    ER setPower( [in]int power );
-    ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees,
-               [in] uint32_t speed_abs,
-                [in] bool_t blocking );
-    void initializePort( [in]int32_t type );
+signature sIPv4Output {
+  T_IN4_ADDR getIPv4Address(void);
+  ER         getOffset([inout]T_OFF_BUF *offset);
+  ER         setHeader([inout,size_is(size)]
+                        int8_t *outputp,
+                        [in]int32_t size,
+                        [in]T_IN4_ADDR dstaddr,
+                        [in]T_IN4_ADDR srcaddr);
+    /* Omit: other functions */
 };
 \end{lstlisting}
-\caption{Signature Description}
-\label{signature}
+\caption{Signature description}
+\label{src:signature}
 \end{figure}
@@
         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
-        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sIPv4Output, and an {\it entry} port name, e.g., eIPv4Output, follow the keyword {\it entry}.
         {\it Call} ports are defined similarly.
@@
 \begin{lstlisting}
-celltype tCaller {
-    call sMotor cMotor;
+celltype tIPv4Output {
+    /* Entry port */
+    entry sIPv4Output eOutput;
+
+    /* Call port */
+    call sEthernetOutput cEthernetOutput;
+    /* Omit: other call ports */
+
+    attr {  /* Attribute */
+        uint16_t fragInit = 0;
     };
-celltype tMotor {
-    entry sMotor eMotor;
-    attr {
-        int32_t port;
-    };
-    var {
-        int32_t currentSpeed = 0;
+    var {   /* Variable */
+        uint16_t fragId = fragInit;
     };
@@
 \end{lstlisting}
-\caption{Celltype Description}
-\label{celltype}
+\caption{Celltype description}
+\label{src:celltype}
 \end{figure}
@@
         The build description is used to instantiate and connect {\it cell}s.
-        Fig.\ref{build} shows an example of a build description.
-        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        Fig. \ref{src:build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
         A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
-        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
         {\it C\_EXP} calls macros defined in C files.
@@
 \begin{lstlisting}
-cell tMotor Motor {
-    port = C_EXP("PORT_A");
+cell tIPv4Output IPv4Output {
+    /* Omit: other build description */
+
+    fragInit = 0; /* Attribute */
 };
-cell tCaller Caller {
-    cMotor = Motor.eMotor;
+cell tTCPOutput TCPOutput {
+    cIPv4Output = IPv4Output.eOutput;
+    /* Omit: other build description */
 };
 \end{lstlisting}
-\caption{Build Description}
-\label{build}
+\caption{Build description}
+\label{src:build}
 \end{figure}
@@
 
+\subsubsection{Memory allocator component}
+
+The original TINET eliminates dynamic memory control to meet the sever memory restriction of embedded systems.
+A memory area for sending/receiving data in the protocol stack is allocated and released within an predetermined area.
+Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
+The component provides a requested memory area from the memory area statically allocated.
+
+The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown as Fig. \ref{fig:tMemoryAllocator}.
+tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
+tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
+On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.
+
+In addition, TINET+TECS utilizes {\it send/receive} specifier of TECS to minimize the memory copy frequency, which is a functionality supported by TINET.
+
 \begin{figure}[t]
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/ComponentProtocolStack.pdf}
-    \caption{Component diagram of protocol stack}
-    \label{fig:ComponentProtocolStack}
+    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
+    \caption{Component diagram of tMemoryAllocator}
+    \label{fig:tMemoryAllocator}
 \end{figure}
 
-\subsection{Memory allocator component}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
+    \caption{Differences between in/out and send/receive}
+    \label{fig:SendReceive}
+\end{figure}
 
-\subsubsection{send/receive specifier}
-
+{\bf send/receive specifier:}
 TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
@@
 \centering
-    \includegraphics[width=6.5cm,clip]{figure/SendReceive.pdf}
-    \caption{Differences between in/out and send/receive}
-    \label{fig:SendReceive}
-\end{figure}
-
-\begin{figure}[t]
-\centering
 \begin{lstlisting}
 signature sNicDriver {
-  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp,
+  void start(
+    [send(sNetworkAlloc),size_is(size)]
+        int8_t *outputp,
     [in]int32_t size,
     [in]uint8_t align);
-  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp,
+  void read(
+    [receive(sNetworkAlloc),size_is(*size)]
+        int8_t **inputp,
     [out]int32_t *size,
@@
 
-\subsection{Network timer component}
+\subsubsection{Network timer component}
+
+\subsection{Dynamic Connection of TECS}
+\label{sec:DynamicConnection}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
+    \caption{Dynamic connection}
+    \label{fig:DynamicConnection}
+\end{figure}
+
+TECS supports dynamic connection method as a novel functionality.
+Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
+Note that all components are statically generated in TECS.
+TECS can optimize the overhead of componentization because components are statically configured.
+Dynamically generating the components causes a lot of memory consumption, which is a serious propoblem for embedded systems with strict memory constraint.
+The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.
+
+TINET+TECS utilizes the dynamic connection to swith between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
+For example, when processing with HTTP protocol, CEP passively opens with REP of port number 80.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \caption{Dynamic connection between CEP and REP}
+    \label{fig:DynamicConnectionUseCase}
+\end{figure}
+
+To utilize dynamic connection, the selector should be defined.
+The selector connects all the components that can be dynamically connnected, to refer the descripter of them.
+Descriptor is an identifier to access the component.
+cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
+{\it [ref\_desc]} is described to identify the call port refers to descriptors. 
+In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
+
+A CEP component has two call ports.
+cRepSelector port connects eRepSelector port of tRepSelector cell and cREP4 port connects either of tREP cells (Lines 13-15 in Fig. \ref{src:DynamicCDLcode}).
+cREP port is defined with {\it [dynamic]} to identify the call port dynamically switch the components.
+The call port with {\it [dynamic]} specifier is not optimized and allocated in RAM by a plug-in.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sRepSelector {
+    void  getRep([out]Descriptor(sREP4) *desc,
+                 [in]int_t i);
+};
+
+celltype tRepSelector {
+    entry sRepSelector eRepSelector;
+    [ref_desc]
+        call sREP4 cREP[NUM_REP];
+};
+
+celltype tTCPCEP {
+    call sRepSelector cRepSelector;
+    [dynamic]
+        call sREP4 cREP;
+    /* Omit: other call/entry ports */
+    /* Omit: attributes and variables */
+};
+\end{lstlisting}
+\caption{Signature and celltype description for dynamic connection}
+\label{src:DynamicCDLcode}
+\end{figure}
+
+Fig. \ref{src:DynamicCcode} shows a sample code of dynamic connection.
+The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} with TECS, which is utilized to be the state waiting for connection request.
+In the function, dynamic connection is performed as shown in Fig. \ref{src:DynamicCcode}.
+First, get the descriptor of REP to be joined (Line 3 in Fig. \ref{src:DynamicCcode}).
+The first argument, {\it \&desc}, is a variable to store the descriptor information, and the second argument, {\it repid}, is the index of tREP cells.
+Next, set the desctriptor (Line 5 in Fig. \ref{src:DynamicCcode}).
+cREP port combines the tREP cell that descriptor specify.
+Thus, the tCEP cell can call the function of tREP cell to be joined (Line 7 in Fig. \ref{src:DynamicCcode}).
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+eAPI_accept (.., ..) {
+    /* Get a descripter of intended REP cell */
+    cRepSelector_getRep(&desc, repid);
+    /* Set the descripter */
+    cREP_set_descriptor(desc);
+    /* Call the function of intended REP cell */
+    cREP_getEndpoint();
+}
+\end{lstlisting}
+\caption{Accept function (a dynamic connection example)}
+\label{src:DynamicCcode}
+\end{figure}
 
 \subsection{TECS Adapter}
+\label{sec:TECS Adapter}
 
@@
 
-\section{Evaluation and Demonstration}
-\label{sec:Evaluation and Demonstration}
+\section{Evaluation}
+\label{sec:Evaluation}
 
@@
 
-Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}.
+Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}, lwIP \cite{par:lwIP}.
 
@@
 
+In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS}.
+Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
+We will support the functionality that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
+
 % conference papers do not normally have an appendix
@@
 
-The authers would like to thank OO for supporting this research.
+The authers would like to thank Hiroaki Nagashima for supporting this research.
 This work is supported by JSPS KAKENHI Grant Number 15H05305.

### 2017-02-07 ISORC2017/diff/20170207.tex
Add the current version to diff

--- 2017-02-03 ISORC2017/paper.tex
@@
 
+\setcounter{topnumber}{5}       % ページ上部の図表は 5 個まで
+\def\topfraction{1.00}          % ページの上 1.00 まで図表で占めて可
+\setcounter{bottomnumber}{5}    % ページ下部の図表は 5 個まで
+\def\bottomfraction{1.00}       % ページの下 1.00 まで図表で占めて可
+\setcounter{totalnumber}{10}    % ページあたりの図表は 10 個まで
+\def\textfraction{0.04}         % ページうち本文が占める割合の下限
+
 % As a general rule, do not put math, special symbols or citations
@@
 Therefore, it is difficult to maintain, extend, and analysis the software.
-To improve the scalability and configurability, this paper has proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
+To improve the scalability and configurability, this paper proposes TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
 The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
+TINET+TECS utilizes a dynamic connection method of TECS components to satisfy the original TINET specification.
 We evaluate the component-based TINET compared with the original TINET.
-We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.
+Experimental results show that the overheads of execution time and memory consumption are low, and that the configurability is improved.
 
@@
 TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
-TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
+TECS supports static configuration, which statically defines component behaviors and interconnections.
+Thus, TECS can optimize the overhead of componentization.
 
-In addition, the proposed framework utilizes dynamic connection, a novel method of TECS, to switch component bindings dynamically.
-A general TCP/IP protocol server dynamically processes the requested port i.e., HTTP (port: 80), HTTPS (prot: 443).
-However, embedded systems can not dynamically generate components due to the strict memory restriction.
-TINET+TECS statically generates components, and dynamically combines them.
-Therefore,
+In addition, satisfying the original TINET specification, the proposed framework utilizes dynamic connection, a method of TECS, to dynamically switch component bindings.
+A general TCP/IP protocol server dynamically processes the requested port, i.e., HTTP (port: 80) and HTTPS (port: 443).
+However, embedded systems are restricted dynamic processing due to the strict memory restriction.
+TINET supports static generation of CEPs and REPs, which is like sockets.
+As TINET+TECS statically generates components and dynamically combines them as well as TINET, TINET+TECS reduces dynamically increasing memory consumption.
 
-In the proposed framework, software application can be developed by not only TECS method but also existing method.
-Software appication can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
+In the proposed framework, software applications can be developed by not only TECS method but also existing method.
+The software applications can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
 Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
-The legacy codes such as an existing application can be supported in the proposed framework.
+The adapter allows the use of existing TCP/IP applications without modification.
 
@@
 
-This section describes system model, including the basic technologies such as TINET and TECS.
+This section describes the system model of TINET+TECS, including the basic technologies such as TINET and TECS.
 System model of the proposed framework is shown as Fig. \ref{fig:SystemModel}.
@@
 CEP and REP (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
-Moreover, TECS adapter supports the legacy codes such as an existing application.
+Moreover, TECS adapter supports the legacy codes for existing applications.
 
@@
     \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
-    \caption{System model}
+    \caption{System model of TINET+TECS}
     \label{fig:SystemModel}
@@
 
-The components of protocol stack for TINET+TECS is shown as Fig. \ref{fig:ComponentProtocolStack}.
+The components of a protocol stack for TINET+TECS is shown in Fig. \ref{fig:ComponentProtocolStack}.
 Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
@@
 An application in TINET+TECS is implemented as a component such as tApplication.
-Software with TINET uses ITRON TCP/IP API such as {\it tcp\_snd\_buf} and {\it tcp\_rcv\_buf}.
-In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendBuffer} and {\it cTCPAPI\_receiveBuffer}.
-Moreover, TINET+TECS supporting a TECS adapter (\ref{sec:TECS Adapter}), an exiting application with TINET can run on TINET+TECS framework without transporting.
-Therefore, software can be developed either with exiting methods or as a TECS component.
+Software with TINET uses ITRON TCP/IP API \cite{url:ITRON_TCP/IP_API_Spec} such as {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat}.
+In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
+Moreover, TINET+TECS supporting a TECS adapter (\ref{sec:TECS Adapter}), an existing application with TINET can run on TINET+TECS framework without transporting.
+Therefore, software can be developed either with existing methods or as a TECS component.
 
 {\bf Transport layer:}
-tTCPCEP (tUDPCEP) is a CEP compornent for TCP (UDP), and tREP is a REP component.
+tTCPCEP (tUDPCEP) is a CEP component for TCP (UDP), and tREP is a REP component.
 For example, a server program supporting multiple clients can be developed by preparing the multiple tTCPCEP components.
@@
 The communication object component is a component corresponding to a CEP or REP of the original TINET.
-An application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
+Application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
 
@@
 
-The original TINET eliminates dynamic memory control to meet the sever memory restriction of embedded systems.
-A memory area for sending/receiving data in the protocol stack is allocated and released within an predetermined area.
+The original TINET eliminates dynamic memory control to meet the severe memory restriction of embedded systems.
+A memory area for sending/receiving data in the protocol stack is allocated and released within a predetermined area.
 Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
@@
 {\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
-The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
 In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
@@
 {\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
-The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
 While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
@@
 
-\subsubsection{Network timer component}
+% \subsubsection{Network timer component}
 
@@
 
-TECS supports dynamic connection method as a novel functionality.
+TECS supports dynamic connection as a new functionality.
 Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
@@
 TECS can optimize the overhead of componentization because components are statically configured.
-Dynamically generating the components causes a lot of memory consumption, which is a serious propoblem for embedded systems with strict memory constraint.
+Dynamically generating the components causes a lot of memory consumption, which is a serious problem for embedded systems with strict memory constraint.
 The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.
 
-TINET+TECS utilizes the dynamic connection to swith between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+TINET+TECS utilizes the dynamic connection to switch between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
 In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
@@
 To utilize dynamic connection, the selector should be defined.
-The selector connects all the components that can be dynamically connnected, to refer the descripter of them.
-Descriptor is an identifier to access the component.
+The selector connects all the components that can be dynamically connnected, to refer the descriptor of them.
+Descriptor is an identifier to access the component \cite{par:optimization}.
 cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
@@
 eAPI_accept (.., ..) {
-    /* Get a descripter of intended REP cell */
+    /* Get a descriptor of intended REP cell */
     cRepSelector_getRep(&desc, repid);
-    /* Set the descripter */
+    /* Set the descriptor */
     cREP_set_descriptor(desc);
@@
 
-\subsection{Evaluation environment}
+This section describes our experimental evaluation to demonstrate the effectiveness of the proposed framework.
+
+\subsection{Evaluation Environment}
 
@@
 The detail specification of the board is shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
-We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2.
+We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2
 
@@
 \end{table}
+
+\subsection{Performance of TINET+TECS}
+
+To demonstrate the low overhead of TINET+TECS, we evaluates the execution time and the memory consumption of TINET+TECS compared with TINET.
+
+Fig. \ref{fig:EvaluationOfExecutionTime} shows the comparison of execution time between TINET and TINET+TECS.
+The APIs used for the evaluation are {\it tcp\_snd\_dat} to send TCP data and {\it tcp\_rcv\_dat} to receive TCP data.
+For {\it tcp\_snd\_dat}, we measured the executing time from the API calling by the application to the return of the processing result.
+In TINET+TECS, the process is performed in the order of tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed of Fig.
+\ref{fig:ComponentProtocolStack}.
+For {\it tcp\_rcv\_dat}, we measured the execution time from the data receiving in the LAN driver to the data acquisition in the application.
+In TINET+TECS, the process is performed in the order of tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication of Fig. \ref{fig:ComponentProtocolStack}.
+The execution time of TINET+TECS is as well as that of TINET; the overhead is about 0000 usec.
+{\it send/receive} specifiers enable to access the buffer address without data copies.
+Therefore, the overhead of componentization does not effect the execution time.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \caption{Execution time of TINET and TINET+TECS}
+    \label{fig:EvaluationOfExecutionTime}
+\end{figure}
+
+TABLE \ref{tab:EvaluationOfMemoryConsumption} shows the memory consumption of TINET and TINET+TECS.
+The memory consumption of TINET+TECS increases about 0000\% compared with TINET.
+The processes and data to manage TECS components, such as initialization of cells, descriptors, function tables, and skeleton functions, cause the increase memory consumption.
+
+\begin{table}[t]
+    \centering
+    \caption{Memory consumption of TINET and TINET+TECS}
+    \begin{tabular}{c|r|r}
+        \hline\hline
+                  &   TINET         &   TINET+TECS   \\ \hline
+        RAM       &   10,000 Bytes  &   10,000 Bytes \\
+        ROM       &   10,000 Bytes  &   10,000 Bytes \\
+        RAM + ROM &   20,000 Bytes  &   20,000 Bytes \\
+        \hline
+    \end{tabular}
+    \label{tab:EvaluationOfMemoryConsumption}
+\end{table}
+
+Next, to demonstrate the improved configurability, we measured the code lines for modification as shown in TABLE \ref{tab:EvaluationOfConfigurabilty}.
+We can change the composition of the protocol stack with a small workload.
+Thus, the proposed framework improves the configurability.
+
+\begin{table}[t]
+    \centering
+    \caption{Modified code lines of CDL}
+    \begin{tabular}{c|r|r|r}
+        \hline\hline
+                         &   Size          &   Size (- Default)  & CDL  \\ \hline
+        Default          &   10,000 Bytes  &   10,000 Bytes      & 0    \\
+        I                &   10,000 Bytes  &   10,000 Bytes      & 2    \\
+        I + I\hspace{-.1em}I &   20,000 Bytes  &   20,000 Bytes  & 5    \\
+        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I   &   20,000 Bytes  &   20,000 Bytes  & 20 \\
+        \hline
+    \end{tabular}
+    \label{tab:EvaluationOfConfigurability}
+\end{table}
+
+\subsection{Dynamic Connection}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \caption{Component diagrams of two cases (with/without dynamic connection)}
+    \label{fig:ComparisonOfDynamicConnection}
+\end{figure}
+
+We evaluated the memory consumption without and with TECS dynamic connection.
+As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP component should statically connect to all REP components in the case dynamic connection is not used.
+As the number of REPs increases, call ports of CEP are required for that.
+Thus, it consumes a lot of memory. 
+Dynamic connection reduces the memory consumption because only one call port of CEP for REP, which is drawn with red lines in the right of Fig.
+\ref{fig:ComparisonOfDynamicConnection}, is required per CEP.
+Even when the number of REPs increases, a call port of the selector, not the CEP, is joined.
+
+Fig. \ref{fig:EvaluationOfDynamicConnection} shows the memory consumption of two cases, without/with dynamic connection.
+The case of dynamic connection consumes the RAM memory more than the other case because the call ports with {\it [dynamic]} is not optimized and allocated in RAM areas as mentioned in Section \ref{sec:DynamicConnection}.
+The total memory consumption is fewer in the proposed framework.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
+    \caption{Memory consumption of two cases (with/without dynamic connection)}
+    \label{fig:EvaluationOfDynamicConnection}
+\end{figure}
+
+\subsection{Overhead of Adapter}
+
+TINET+TECS supports existing applications because of the TECS adapter.
+To analyze the overhead of TECS adapter, we measured execution time of API with the adapter such as {\it tcp\_snd\_dat/eAPI\_sendData}.
+As shown in Fig. \ref{fig:EvaluationOfAdapter}, the overhead of TECS adapter is very small because the adapter only passes the parameters to TECS components from C codes.
+Therefore, TECS adapter does not affect the system.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/EvaluationOfAdapter.pdf}
+    \caption{Execution time of two cases (without/with TECS adapter)}
+    \label{fig:EvaluationOfAdapter}
+\end{figure}
 
@@
 {\bf CiAO/IP:}
+\\
+\\
+Should be written
+\\
+\\
 
@@
 
-In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS}.
+This paper proposes TINET+TECS, a component-based TCP/IP protocol stack for embedded systems.
+TINET+TECS is componentized TINET, which is a compact TCP/IP protocol stack, using TECS.
+TINET consists of many macros and complicated codes and the software productivity are low.
+The proposed framework improves the configurability while suppressing the overhead of componentization.
+The proposed framework also improves the scalability because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
+
+In addition, this paper presents dynamic connection, a new method of TECS.
+The method enables dynamic processing while reducing memory consumption.
+To satisfy TINET specification that TINET support static generation of CEPs and REPs, TINET+TECS utilizes dynamic connection.
+TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
+
+In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS} to manage IoT devices.
 Note that mruby is a scripting language for embedded systems \cite{par:mruby}.

### 2017-02-11 ISORC2017/paper.tex
Add the option for figures
Add the figures and tables of evaluations

@@
 
-This paper proposes component-based TCP/IP protocol stack, i.e., TINET+TECS, to improve the configurability and scalability of software.
-TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
-TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
+This paper proposes a component-based TCP/IP protocol stack for embedded systems, i.e., TINET+TECS, to improve the configurability and scalability of TCP/IP software.
+TECS (TOPPERS Embedded Component System) \cite{par:TECS} \cite{par:hr-tecs} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
+TECS supports static configuration, which statically defines component behaviors and interconnections.
+Thus, TECS can optimize the overhead of componentization.
 
-In addition, the proposed framework utilizes dynamic connection, a novel method of TECS, to switch component bindings dynamically.
-A general TCP/IP protocol server dynamically processes the requested port i.e., HTTP (port: 80), HTTPS (prot: 443).
-However, embedded systems can not dynamically generate components due to the strict memory restriction.
-TINET+TECS statically generates components, and dynamically combines them.
-Therefore,
+In addition, satisfying the original TINET specification, the proposed framework utilizes dynamic connection, a method of TECS, to dynamically switch component bindings.
+A general TCP/IP protocol server dynamically processes the requested port, i.e., HTTP (port: 80) and HTTPS (port: 443).
+However, embedded systems are restricted dynamic processing due to the strict memory restriction.
+TINET supports static generation of CEPs and REPs which are like sockets.
+As TINET+TECS statically generates components and dynamically combines them as well as TINET, TINET+TECS reduces dynamically increasing memory consumption.
 
-In the proposed framework, software application can be developed by not only TECS method but also existing method.
-Software appication can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
+In the proposed framework, software applications can be developed by not only TECS method but also existing method.
+The software applications can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
 Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
-The legacy codes such as an existing application can be supported in the proposed framework.
+The adapter allows the use of existing TCP/IP applications without modification.
 
 This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
+Moreover, the advantages of dynamic connection in terms of memory consumption and the low overhead of the TECS adapter are demonstrated.
 
@@
 Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
-Section \ref{sec:Evaluation and Demonstration} evaluates the proposed framework.
+Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates the advantages.
 Related work is discussed in Section \ref{sec:Related Work}.
@@
 
-This section describes system model, including the basic technologies such as TINET and TECS.
-System model of the proposed framework is shown as Fig. \ref{fig:SystemModel}.
-TINET+TECS is a component-based TCP/IP protocol stack, so TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
-CEP and REP (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
-Moreover, TECS adapter supports the legacy codes such as an existing application.
+This section describes the system model of TINET+TECS, including the basic technologies such as TINET and TECS.
+System model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
+TINET+TECS is a component-based TCP/IP protocol stack, and the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
+CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
+Moreover, TECS adapter supports the legacy codes for existing TCP/IP applications.
 
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/SystemModel.pdf}
-    \caption{System model}
+    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
+    \caption{System model of TINET+TECS}
     \label{fig:SystemModel}
@@
 TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
+
 Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
     \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/ComponentDiagram.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
     \caption{Component Diagram}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/ComponentProtocolStack.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
     \caption{Component diagram of protocol stack}
@@
 
-The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown as Fig. \ref{fig:tMemoryAllocator}.
+The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown in Fig. \ref{fig:tMemoryAllocator}.
 tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
     \caption{Component diagram of tMemoryAllocator}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
     \caption{Differences between in/out and send/receive}
@@
 {\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
-The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
+The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
 While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
 Deallocating the memory is performed in the caller in both cases.
+
+As shown in Fig.
+\ref{src:SendReceive}, the arguments of sending and receiving data such as {\it outputp} and {\it inputp} are defines with the {\it send/receive} specifiers in the signature description.
 
@@
 \end{lstlisting}
-\caption{An example of send and receive}
+\caption{Signature description of the nic driver (An example of send/receive)}
 \label{src:SendReceive}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
     \caption{Dynamic connection}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
     \caption{Dynamic connection between CEP and REP}
@@
 TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
-An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
-Software developers can utilize an existing application for TECS owing to the adapter.
+An adapter is implemented between C codes and a TECS component, and links a C function to a TECS function shown in Fig. \ref{fig:TECS_Adapter}.
+In TINET+TECS, when the application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls the function of tTCPCEP such as {\it eAPI\_sendData}.
+Note that {\it tcp\_snd\_dat} is defined with the name {\it eAPI\_sendData} in TINET+TECS.
+The adapter wraps the APIs used in the existing applications into TECS functions.
+Therefore, software developers can utilize an existing TCP/IP application by using the adapter.
 
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
-    \caption{TECS Adapter}
+    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
+    \caption{TECS adapter}
     \label{fig:TECS_Adapter}
@@
 
+\subsection{Performance of TINET+TECS}
+
+To demonstrate the low overhead of TINET+TECS, we evaluated the execution time and the memory consumption of TINET+TECS compared with TINET.
+
+The comparison of execution time between TINET and TINET+TECS is shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
+The APIs used for the evaluation are {\it tcp\_snd\_dat} to send TCP data and {\it tcp\_rcv\_dat} to receive TCP data.
+For {\it tcp\_snd\_dat}, we measured the executing time from the API calling by the application to the return of the processing result.
+In TINET+TECS, the process is performed in the order of tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed of Fig.
+\ref{fig:ComponentProtocolStack}.
+For {\it tcp\_rcv\_dat}, we measured the execution time from the data receiving in the LAN driver to the data acquisition in the application.
+In TINET+TECS, the process is performed in the order of tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication of Fig. \ref{fig:ComponentProtocolStack}.
+The execution time of TINET+TECS is as well as that of TINET; the overhead is about 3 usec.
+{\it send/receive} specifiers enable to access the buffer address without data copies.
+Therefore, the overhead of componentization does not effect the execution time.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \caption{Execution time of TINET and TINET+TECS}
+    \label{fig:EvaluationOfExecutionTime}
+\end{figure}
+
+The memory consumptions of TINET and TINET+TECS are compared in TABLE \ref{tab:EvaluationOfMemoryConsumption}.
+The memory consumption of TINET+TECS increases about 2.5\% compared with TINET.
+The processes and data to manage TECS components, such as initialization of cells, descriptors, function tables, and skeleton functions, cause the increase memory consumption.
+
+\begin{table}[t]
+    \centering
+    \caption{Memory consumption of TINET and TINET+TECS}
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                    &   text       &  data    &   bss      &  total     \\ \hline
+        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
+        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+        \hline
+        \multicolumn{5}{r}{Including the application and kernel objects}
+    \end{tabular}
+    \label{tab:EvaluationOfMemoryConsumption}
+\end{table}
+
+As shown in TABLE \ref{tab:EvaluationOfConfigurabilty}, the code lines for modification were measured to demonstrate the improved configurability.
+We can change the composition of the protocol stack with a small workload.
+Thus, the proposed framework improves the configurability.
+
+\begin{table}[t]
+    \centering
+    \caption{Modified code lines of CDL}
+    \begin{tabular}{c|r|r|r}
+        \hline\hline
+                         &   Size       &   Size (- Default)  & CDL  \\ \hline
+        Default          &   325.23 KB  &             0 KB    &  0 lines   \\
+        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
+        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
+        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
+        \hline
+        \multicolumn{4}{l}{I: Remove TCP}\\
+        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
+        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
+    \end{tabular}
+    \label{tab:EvaluationOfConfigurability}
+\end{table}
+
+\subsection{Dynamic Connection}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \caption{Component diagrams of two cases (without/with dynamic connection)}
+    \label{fig:ComparisonOfDynamicConnection}
+\end{figure}
+
+The memory consumption without and with TECS dynamic connection was evaluated.
+As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP component should statically connect to all REP components in the case dynamic connection is not used.
+As the number of REPs increases, call ports of CEP are required for that.
+Thus, it consumes a lot of memory. 
+Dynamic connection reduces the memory consumption because only one call port of CEP for REP, which is drawn with red lines in the right of Fig.
+\ref{fig:ComparisonOfDynamicConnection}, is required per CEP.
+Even when the number of REPs increases, a call port of the selector, not the CEP, is joined.
+
+The memory consumption of two cases, without/with dynamic connection, is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
+The case of dynamic connection consumes the RAM memory more than the other case because the call ports with {\it [dynamic]} is not optimized and allocated in RAM areas as mentioned in Section \ref{sec:DynamicConnection}.
+The total memory consumption is fewer in the proposed framework.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
+    \caption{Memory consumption of two cases (with/without dynamic connection)}
+    \label{fig:EvaluationOfDynamicConnection}
+\end{figure}
+
+\begin{table}[t]
+    \centering
+    \caption{CDL code lines of without/with dynamic connection}
+    \begin{tabular}{l|r|r|r}
+        \hline\hline
+                     &  without  &  with  &  Diff  \\ \hline
+        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
+        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
+        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
+        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
+        \hline
+    \end{tabular}
+    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
+\end{table}
+
+\begin{figure}[t]
+ \centering
+ \begin{lstlisting}
+/* without Dynamic Connection */
+cell tTCPCEP TCPCEP_000 {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+cell tTCPCEP TCPCEP_001 {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+..
+cell tTCPCEP TCPCEP_00n {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+ \end{lstlisting}
+ \centering
+ \begin{lstlisting}
+/* with Dynamic Connection */
+cell tRepSelector RepSelector {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+cell tTCPCEP TCPCEP_000 {
+    cRepSelector = RepSelector.eRepSelector;
+};
+cell tTCPCEP TCPCEP_001 {
+    cRepSelector = RepSelector.eRepSelector;
+};
+..
+cell tTCPCEP TCPCEP_00n {
+    cRepSelector = RepSelector.eRepSelector;
+};
+ \end{lstlisting}
+ \caption{Comparison of CDL descriptions between without/with dynamic connection}
+ \label{src:ComparisonOfCDL}
+\end{figure}
+
+The comparison of CDL code lines of without/with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
+As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
+In the left part of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
+In the right part of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
+Since the difference spreads as the number of CEPs and REPs increases, it is effective for software that uses many ports.
+
+\subsection{Overhead of Adapter}
+
+The execution time of API with the adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} to analyze the overhead of TECS adapter which supports existing applications.
+As shown in Fig. \ref{fig:EvaluationOfAdapter}, the overhead of TECS adapter is very small because the adapter only passes the parameters to TECS components from C codes.
+Therefore, TECS adapter does not affect the system.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
+    \caption{Execution time of two cases (without/with TECS adapter)}
+    \label{fig:EvaluationOfAdapter}
+\end{figure}
+
 \section{Related Work}
@@
 uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
-uIP only requires about five kilobytes of code size and several hundred bytes of RAM.
+    uIP only requires about five KB of code size and several hundreds bytes of RAM.
 uIP has been ported to various systems and has found its way into many commercial products.
@@
 The focus of lwIP is to reduce memory resource while still having a full scale TCP.
-lwIP requires about 40 kilobytes of ROM and tens of kilobytes of RAM.
+lwIP requires about 40 KB of ROM and tens of KB of RAM.
 lwIP is larger than uIP, but provides better throughput.
 
-{\bf CiAO/IP:}
+% {\bf CiAO/IP:}
+% \\
+% \\
+% Should be written
+% \\
+% \\
 
@@
 
-In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS}.
+This paper proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems.
+TINET+TECS is componentized TINET, which is a compact TCP/IP protocol stack, using TECS.
+TINET consists of many macros and complicated codes and the software productivity are low.
+The proposed framework improves the configurability while suppressing the overhead of componentization.
+The proposed framework also improves the scalability because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
+
+In addition, this paper presents dynamic connection, a new method of TECS, to enable dynamic processing while reducing memory consumption.
+To satisfy TINET specification that TINET support static generation of CEPs and REPs, TINET+TECS utilizes dynamic connection.
+TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
+
+In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS} to easily manage IoT devices.
 Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
-We will support the functionality that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
+We will support the functionalities that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
 

### 2017-02-11 ISORC2017/evaluation/extract_data.rb

@@ -1,0 +1,57 @@
+#extract_data.rb
+
+#
+#テキストファイルから実験結果のみを抽出する
+#
+def ex_data(input, output)
+    outFile = File.open(output, 'w')
+    File.open(input) do |f|
+        f.each_line do |line|
+            if line.include?("time")
+                if /[\d]*[\d]/ =~ "#{line}" then
+                    outFile.puts $&
+                end
+            end
+        end
+    end
+    outFile.close
+end
+
+input = "Adapter_tcp_snd_dat.log"               #<------
+output = "parsed_#{input}"
+
+ex_data("#{input}", output)
+
+dataFile = output
+#
+#
+
+sheetNumber = 0                  #<-------
+headerName = ""         #<-------
+
+#
+#Excel の操作
+#
+require 'rubyXL'
+
+#
+# xls = "ExecutionTime.xlsx"
+xls = "Adapter.xlsx"
+workbook = RubyXL::Parser.parse(xls)
+worksheet = workbook[sheetNumber]
+
+column = 3
+row = 1
+worksheet.add_cell(0, column, headerName)
+File.open(dataFile) do |f|
+    f.each_line do |line|
+        worksheet.add_cell(row, column, "#{line.chomp}")
+        row += 1
+        # if /[\d]*[\d]/ =~ "#{line}" then
+        #     worksheet.add_cell(raw, 0, $&)
+        #     raw += 1
+        # end
+    end
+end
+
+workbook.write(xls)

### 2017-02-11 ISORC2017/diff/20170208.tex
Add the tex file at 2017/02/08

--- 2017-02-11 ISORC2017/paper.tex
@@
     \caption{Memory consumption of TINET and TINET+TECS}
-    \begin{tabular}{c|r|r|r|r}
+    \begin{tabular}{c|r|r}
         \hline\hline
-                    &   text       &  data    &   bss      &  total     \\ \hline
-        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
-        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+                  &   TINET      &   TINET+TECS  \\ \hline
+        ROM       &   74.93 KB   &   76.62 KB   \\
+        RAM       &   27.36 KB   &   28.24 KB   \\
+        ROM + RAM &   102.29 KB  &   103.86 KB   \\
         \hline
-        \multicolumn{5}{r}{Including the application and kernel objects}
     \end{tabular}
@@
                          &   Size       &   Size (- Default)  & CDL  \\ \hline
-        Default          &   325.23 KB  &             0 KB    &  0 lines   \\
-        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
-        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
-        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
+        Default          &   104.86 KB  &   0 KB           & 0    \\
+        I                &   80.79 KB   &   - 24.07 KB     & 18    \\
+        I + I\hspace{-.1em}I &   80.50 KB  &   - 26.35 KB  & 26    \\
+        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I   & 72.03 KB & - 32.83 KB  & 31 \\
         \hline
-        \multicolumn{4}{l}{I: Remove TCP}\\
-        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
-        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
     \end{tabular}
@@
 \end{figure}
-
-\begin{table}[t]
-    \centering
-    \caption{CDL code lines of without/with dynamic connection}
-    \begin{tabular}{l|r|r|r}
-        \hline\hline
-                     &  without  &  with  &  Diff  \\ \hline
-        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
-        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
-        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
-        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
-        \hline
-    \end{tabular}
-    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
-\end{table}
-
-\begin{figure}[t]
- \centering
- \begin{lstlisting}
-/* without Dynamic Connection */
-cell tTCPCEP TCPCEP_000 {
-    cREP[0] = REP_000.eREP;
-    ..
-    cREP[n] = REP_00n.eREP;
-};
-cell tTCPCEP TCPCEP_001 {
-    cREP[0] = REP_000.eREP;
-    ..
-    cREP[n] = REP_00n.eREP;
-};
-..
-cell tTCPCEP TCPCEP_00n {
-    cREP[0] = REP_000.eREP;
-    ..
-    cREP[n] = REP_00n.eREP;
-};
- \end{lstlisting}
- \centering
- \begin{lstlisting}
-/* with Dynamic Connection */
-cell tRepSelector RepSelector {
-    cREP[0] = REP_000.eREP;
-    ..
-    cREP[n] = REP_00n.eREP;
-};
-cell tTCPCEP TCPCEP_000 {
-    cRepSelector = RepSelector.eRepSelector;
-};
-cell tTCPCEP TCPCEP_001 {
-    cRepSelector = RepSelector.eRepSelector;
-};
-..
-cell tTCPCEP TCPCEP_00n {
-    cRepSelector = RepSelector.eRepSelector;
-};
- \end{lstlisting}
- \caption{Comparison of CDL descriptions between without/with dynamic connection}
- \label{src:ComparisonOfCDL}
-\end{figure}
-
-The comparison of CDL code lines of without/with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
-As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
-In the left part of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
-In the right part of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
-Since the difference spreads as the number of CEPs and REPs increases, it is effective for software that uses many ports.
 

### 2017-02-11 ISORC2017/paper.tex
Fix abstract by enago

@@
 % Do not put math or special symbols in the title.
-\title{TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems}
+\title{TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems}
 
@@
 
-Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
-TINET is a TCP/IP protocol stack for embedded systems.
-Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
-Therefore, it is difficult to maintain, extend, and analysis the software.
-To improve the scalability and configurability, this paper proposes TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
-The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
-TINET+TECS utilizes a dynamic connection method of TECS components to satisfy the original TINET specification.
-We evaluate the component-based TINET compared with the original TINET.
-Experimental results show that the overheads of execution time and memory consumption are low, and that the configurability is improved.
+% Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
+High productivity embedded network software is required to run embedded systems within the Internet of Things (IoT).
+Tomakomai InterNETworking (TINET) is a Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stack for use in embedded systems.
+Although TINET is a compact protocol stack, it comprises many complex source codes and is difficult to maintain, extend, and analyze.
+To improve scalability and configurability, this paper proposes TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS), a component-based TCP/IP protocol stack for embedded systems.
+This component-based TINET offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionality.
+TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
+The results of an experimental comparison between the proposed component-based and original TINETs show that the execution time and memory consumption overhead are reduced and the configurability is improved.
 

### 2017-02-11 ISORC2017/paper.tex
Fix introduction by enago

@@
 
-Internet of Things (IoT) is an essential keyword for the next era \cite{par:IoTIndustries} \cite{par:IoTComputing}.
-Various things, such as wearable devices, smart devices, and smart homes, connected to the Internet will enrich our lives.
-Embedded systems are the elements constituting IoT, e.g., sensing data and controlling actuators.
-It is not practical to implement the same TCP/IP protocol stack as a general computer because embedded systems have several restrictions such as low memory capacity.
+The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices, smart devices, and smart homes, will be connected via the Internet to further enrich people's lives.
+However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of, for example, low memory capacity.
 
-TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
-TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
-TINET needs only small memory for its TCP/IP protocol stack; therefore it is suitable for embedded systems.
-However, there are several issues that TINET consists of many complex source codes.
-In other words, TINET is composed of many files and defines many macros.
-This may take a lot of time for software developers to maintain, extend, and analysis the software.
-Embedded network software is required for the high productivity and quality.
+Tomakomai InterNETworking (TINET) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
+As TINET supports functionalities such as a minimum copy frequency and the elimination of dynamic memory control, it requires significantly reduced memory for its TCP/IP protocol stack and is therefore suitable for embedded systems.
+However, TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
+Thus, embedded network software is required for high productivity and quality.
 
-An approach to improve software productivity is component-based development, which is a design technique that can be applied to reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD}, such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+One approach to improving software productivity is component-based development, a design technique that can be applied in reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD} such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, or SaveCCM \cite{par:SAVEapproach}.
 Component-based systems are flexible to software extension and specification changes.
-In addition, individual component diagrams enable the visualization of an entire system.
 
-This paper proposes a component-based TCP/IP protocol stack for embedded systems, i.e., TINET+TECS, to improve the configurability and scalability of TCP/IP software.
-TECS (TOPPERS Embedded Component System) \cite{par:TECS} \cite{par:hr-tecs} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
-TECS supports static configuration, which statically defines component behaviors and interconnections.
-Thus, TECS can optimize the overhead of componentization.
+This paper proposes a component-based TCP/IP protocol stack for embedded systems--TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS)--to improve the configurability and scalability of TCP/IP software.
+Because it is a component system suitable for embedded systems, TECS \cite{par:TECS} \cite{par:hr-tecs} is used to componentize TINET in the proposed protocol stack.
+As TECS supports static configurations that statically define component behaviors and interconnections, it can optimize the componentization overhead.
 
-In addition, satisfying the original TINET specification, the proposed framework utilizes dynamic connection, a method of TECS, to dynamically switch component bindings.
-A general TCP/IP protocol server dynamically processes the requested port, i.e., HTTP (port: 80) and HTTPS (port: 443).
-However, embedded systems are restricted dynamic processing due to the strict memory restriction.
-TINET supports static generation of CEPs and REPs which are like sockets.
-As TINET+TECS statically generates components and dynamically combines them as well as TINET, TINET+TECS reduces dynamically increasing memory consumption.
+In addition to satisfying the original TINET specifications, the proposed framework utilizes the TECS dynamic connection capability to dynamically switch component bindings.
+Although general TCP/IP protocol servers dynamically process requested ports, i.e., HTTP (port: 80) and HTTPS (port: 443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
+TINET supports the static generation of Communication Endpoints (CEPs) and Reception Points (REPs), which are similar to sockets.
+As TINET+TECS, like TINET, statically generates components and dynamically combines them in the same manner, TINET+TECS reduces the dynamic increase of memory consumption.
 
-In the proposed framework, software applications can be developed by not only TECS method but also existing method.
-The software applications can be developed as a TECS component because TINET+TECS is a component-based framework using TECS.
-Moreover, TECS supports an adapter to call functions of TECS components from non TECS codes.
-The adapter allows the use of existing TCP/IP applications without modification.
+In the proposed framework, software applications can be developed using both TECS method and existing methods.
+Software applications can be developed as TECS components because TINET+TECS is a component-based framework.
+Furthermore, TECS supports the use of an adapter to call TECS component functions from non-TECS codes, which allows for the use of existing TCP/IP applications without modification.
 
-This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.
-Moreover, the advantages of dynamic connection in terms of memory consumption and the low overhead of the TECS adapter are demonstrated.
+This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities in order to improve configurability with small overheads.
+Furthermore, the advantages of dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.
 
-{\bf Contributions:} This paper provides the following contributions.
+{\bf Contributions:} This paper provides the following contributions:
 
@@
     \item {\bf Improve configurability}\mbox{}\\
-        Since TINET+TECS is a component-based system, the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and supporting both IPv4 and IPv6.
-        In addition, a component diagram provides visualization of TINET, a complicated system.
+        Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
+        In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.
 
     \item {\bf Dynamic connection method}\mbox{}\\
-        Dynamically switching the binding of components, that is switching between a communication endpoint and reception point of TINET, realizes a TCP/IP protocol stack for embedded systems.
+        Dynamically switching the binding of components, that is, switching between a TINET communication endpoint and REP, realizes a TCP/IP protocol stack for an embedded system.
 
     \item {\bf Support legacy codes}\mbox{}\\
-        TINET+TECS can be applied to an existing application because TECS supports the adapter to call TECS functions from C codes. 
+        TINET+TECS can be applied to existing applications because TECS supports the ability of the adapter to call TECS functions from C codes. 
     % \item {\bf Software visualization}
@@
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:System Model} introduces the system model and basic technologies, i.e., TINET and TECS.
+Section \ref{sec:System Model} introduces the system model and its basic technologies, i.e., TINET and TECS.
 Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
-Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates the advantages.
+Section \ref{sec:Evaluation} evaluates the proposed framework and demonstrates its advantages.
 Related work is discussed in Section \ref{sec:Related Work}.
@@
     \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
-    \caption{Hierarchy diagram of TINET and TOPPERS/ASP3}
+    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
     \label{fig:TINETHierarchyDiagram}

### 2017-02-11 ISORC2017/paper.tex
Fix system model by enago

@@
 
-This section describes the system model of TINET+TECS, including the basic technologies such as TINET and TECS.
-System model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
-TINET+TECS is a component-based TCP/IP protocol stack, and the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
-CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings by TECS method.
-Moreover, TECS adapter supports the legacy codes for existing TCP/IP applications.
+This section describes the system model of TINET+TECS, including basic technologies such as TINET and TECS.
+A system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
+TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
+CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method.
+Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications.
 
@@
 
-TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
-TINET has been released as open source.
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
+TINET has been released as an open-source tool.
 
-To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:
+To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the following functions:
 
 \begin{itemize}
-    \item Minimum copy frequency
-    \item Elimination of dynamic memory control
-    \item Asynchronous interface
-    \item Error detailed per API
+    \item minimum copy frequency,
+    \item elimination of dynamic memory control,
+    \item asynchronous interfacing,
+    \item error detailing per API.
 \end{itemize}
@@
 
-TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, which is a realtime kernel based on $\mu$ITRON \cite{par:microITRON}.
-TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP because TINET is compatible with TOPPERS RTOS.
+TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, a real-time kernel based on $\mu$ITRON \cite{par:microITRON}.
+As it is compatible with TOPPERS RTOS, TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP.
 
@@
 % TINET supports ITRON TCP/IP API such as {\it tcp\_snd\_buf}, {\it tcp\_rcv\_buf}, {\it udp\_snd\_buf}, and {\it udp\_rcv\_buf}.
-Users transmit and receive the data using a Communication End Point (CEP) which is an interface like a socket.
-In transmission process, headers are attached to the data body passed to the CEP at each protocol layer, and the data is transmitted from the network device.
-In reception process, headers of the data body received in the network device are analyzed at each protocol layer, and the data is passed to the CEP.
+Users transmit and receive data using a Communication End Point (CEP), an interface that functions like a socket.
+In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
+In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.
 
-A TCP reception point called Reception Point (REP) is prepared to wait for a connection request from the partner side.
-An REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes, and performs functions like {\it bind()} and {\it listen()}.
+A TCP reception point called the REP stands by to receive connection requests from the partner side.
+The REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes and performs functions such {\it bind()} and {\it listen()}.
 
-In TINET, the number of the data copy between each protocol layers is minimized.
-A TCP/IP protocol stack for general computers has large overheads of execution time and memory consumption because the data is copied at each protocol layers.
-To solve the problem, TINET does pass the pointer of the data buffer between each protocol layers, not perform data copy.
+In TINET, the amount of data copying between each protocol layers is minimized.
+In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
+To solve this problem, TINET does passes the pointer of the data buffer between each protocol layer instead of performing data copying.
 
@@
 
-TECS is a component system suitable for embedded systems.
-TECS can increase productivity and reduce development costs owing to improved reusability of software components.
-TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+TECS is a component system suitable for embedded systems that can increase productivity and reduce development costs based on the improved reusability of software components.
+TECS also provides component diagrams that can help developers visualize the overall structure of a system.
 
-In TECS, component deployment and composition are performed statically.
-Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+In TECS, component deployment and composition are performed statically, and as a consequently, component connection does not incur significant overhead, and memory requirements can be reduced.
+TECS has various features such as source level portability and fine-grained components and can be implemented in C.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
-    \caption{Component Diagram}
+    \caption{Component diagram}
     \label{fig:ComponentDiagram}
@@
 
-\subsubsection{Component Model}
+\subsubsection{Component model}
 
 Fig. \ref{fig:ComponentDiagram} shows a component diagram.
-A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
-An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
-A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+{\it Cells}, which are instance of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
+An {\it entry} port is an interface that provides functions to other {\it cells}, whereas a {\it call} port is an interface that enables the use of other {\it cells}' functions.
+Each {\it cell} has one or more {\it entry} ports and {\it call} ports.
 {\it Cell} functions are implemented in C.
 
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
-A {\it signature} is the interface definition of a {\it cell}.
-The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions that defines the interface definition of the {\it cell}.
+The {\it cell's} {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
 Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
 
-\subsubsection{Component Description}
+\subsubsection{Component description}
 
-In TECS, components are described with component description language (CDL).
+In TECS, components are described using component description language (CDL).
 CDL can be divided into three categories: {\it signature}, {\it celltype}, and build description.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sIPv4Output (Fig. \ref{src:signature}).
-        In TECS, to clarify the function of an interface, specifiers such as [in], [out], and [inout] are used, which represent input, output, and input/output respectively.
-        [size\_is({\it len})] represents an array of size {\it len}.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s''--for instance, sIPv4Output (Fig. \ref{src:signature}).
+        To clarify the function of an interface, specifiers such as [in], [out], and [inout] are used in TECS to represent the input, output, and input/output, respectively.
+        Similarly, [size\_is({\it len})] represents an array of size {\it len}.
 \begin{figure}[t]
@@
     \item[{\bf Celltype Description}]\mbox{}\\
-        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        The {\it celltype} defines the {\it entry} ports, {\it call} ports, attributes, and variables.
         A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tIPv4Output (Fig. \ref{src:celltype}).
@@
         In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
-        {\it C\_EXP} calls macros defined in C files.
+        {\it C\_EXP} can be used to call macros defined in C files.
 

### 2017-02-11 ISORC2017/paper.tex
Fix design and implementation by enago

@@
 In addition to satisfying the original TINET specifications, the proposed framework utilizes the TECS dynamic connection capability to dynamically switch component bindings.
-Although general TCP/IP protocol servers dynamically process requested ports, i.e., HTTP (port: 80) and HTTPS (port: 443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
+Although general TCP/IP protocol servers dynamically process requested ports, i.e., Hypertext Transfer Protocol (HTTP, port: 80) and Hypertext Transfer Protocol Secure (HTTPS, port: 443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
 TINET supports the static generation of Communication Endpoints (CEPs) and Reception Points (REPs), which are similar to sockets.
@@
 
-This section describes design and implementation of the proposed framework, TINET+TECS.
-The proposed framework is component-based TCP/IP protocol stack for embedded systems, i.e., componentized TINET using TECS.
-In addition, A TECS novel functionality, dynamic connection method, and TECS adapter to support legacy codes are described with the use case of the proposed framework.
+This section describes the design and implementation of the proposed TINET+TECS framework.
+The proposed framework is a component-based TCP/IP protocol stack for embedded systems: in other words, a componentized TINET using TECS.
+In this section, a new TECS functionality--the dynamic connection method--and the TECS adapter to support legacy codes are described via a use case of the proposed framework.
 
 \subsection{TINET+TECS}
-TINET+TECS, the proposed componentized TCP/IP protocol stack, consists of some TECS components.
-This section describes the components of TINET+TECS framework with component diagrams.
+TINET+TECS, the proposed componentized TCP/IP protocol stack, comprises a number of some TECS components.
+This section describes the components of the TINET+TECS framework with the aid of component diagrams.
 % In addition, TECS functionalities applied to the proposed system such as {\it send}/{\it receive} specifier and adapter are explained.
 
-\subsubsection{Components of protocol stack}
+\subsubsection{Components of a protocol stack}
 
-The components of a protocol stack for TINET+TECS is shown in Fig. \ref{fig:ComponentProtocolStack}.
-Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
-In TINET+TECS, the components are divided for each protocol, and the functionalities such as input function and output function are defined as each a component.
-Therefore, software visibility is improving because of small grain components.
+The components of a TINET+TECS protocol stack are shown in Fig. \ref{fig:ComponentProtocolStack}.
+Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
+In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
+By using such small grain components, software visibility is improved.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
-    \caption{Component diagram of protocol stack}
+    \caption{Component diagram of a protocol stack}
     \label{fig:ComponentProtocolStack}
@@
 
-The components of each protocol are described below.\\
+The components of each protocol are described in the following.\\
 
@@
 In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
-Moreover, TINET+TECS supporting a TECS adapter (\ref{sec:TECS Adapter}), an existing application with TINET can run on TINET+TECS framework without transporting.
-Therefore, software can be developed either with existing methods or as a TECS component.
+Moreover, in TINET+TECS supporting a TECS adapter (\ref{sec:TECS Adapter}), an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, software can be developed either using existing methods or as TECS components.
 
 {\bf Transport layer:}
-tTCPCEP (tUDPCEP) is a CEP component for TCP (UDP), and tREP is a REP component.
-For example, a server program supporting multiple clients can be developed by preparing the multiple tTCPCEP components.
-tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components performing the receiving and sending processing respectively in the transport layer.
+tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components TCP (UDP).
+For example, a server program supporting multiple clients can be developed by preparing multiple tTCPCEP components.
+tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components for performing, respectively, receiving and sending processing in the transport layer.
 
 {\bf Network layer:}
-tIPv4Input and tIPv4Output are components performing the receiving and sending processing respectively in the network layer.
-tIPv4Functions component performs some functions such as checksum, tICMP component is for the ICMP protocol, and tIPv4RoutingTable component operates a routing table.
+tIPv4Input and tIPv4Output are components that perform, respectively, the receiving and sending processing in the network layer.
+The tIPv4Functions component performs functions such as checksum, the tICMP component is for implementing the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
 
 {\bf Data link layer:}
-tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components performing the receiving and sending processing respectively in the data link layer.
-tArp component is for the ARP protocol.
+tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components for performing, respectively, receiving and sending processing in the data link layer.
+The tArp component is used for the Address Resolution Protocol (ARP).
 
 {\bf Physical layer:}
-tNetworkInterfaceContoroller component implements a network device driver.
-Software can run on other devices by replacing the component because only the component depends on the target device.\\
+The tNetworkInterfaceContoroller component implements a network device driver.
+Software can be run on other devices by replacing the component because only the component depends on the target device.\\
 
-To utilize the protocol stack as same as the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
-The communication object component is a component corresponding to a CEP or REP of the original TINET.
+To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
+The communication object component corresponds to a CEP or REP of the original TINET.
 Application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
 
-The protocol stack of TINET+TECS supports coexistence of multiple protocols.
-By developing the IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without a modification of component implementation.
+The protocol stack of TINET+TECS supports the coexistence of multiple protocols.
+Though its use of IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without modification of component implementation.
 
@@
 
-The original TINET eliminates dynamic memory control to meet the severe memory restriction of embedded systems.
+The original TINET eliminates dynamic memory control to meet the severe memory restrictions of embedded systems.
 A memory area for sending/receiving data in the protocol stack is allocated and released within a predetermined area.
-Memory allocator component performs the elimination of dynamic memory control in TINET+TECS.
-The component provides a requested memory area from the memory area statically allocated.
+The memory allocator component allows for elimination of dynamic memory control in TINET+TECS by providing a requested memory area from the statically allocated memory area.
 
-The memory allocator component connects to as many tFixedSizeMemoryPool as needed, shown in Fig. \ref{fig:tMemoryAllocator}.
-tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 to alloc and release a memory area of the requested size. 
-tFixedSizeMemoryPool components with various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
-On the other hands, all components which need allocate and deallocate memory connect to the memory allocator component, e.g., tTCPInput and tEthernetOutput.
+The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig. \ref{fig:tMemoryAllocator}.
+tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and release memory areas of a requested size. 
+tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
+On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.
 
-In addition, TINET+TECS utilizes {\it send/receive} specifier of TECS to minimize the memory copy frequency, which is a functionality supported by TINET.
+In addition, TINET+TECS utilizes the TECS {\it send/receive} specifier to minimize the memory copy frequency, which is a functionality supported by TINET.
 
@@
 
-{\bf send/receive specifier:}
-TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
-TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.
+{\bf Send/receive specifiers:}
+TECS supports {\it send}/{\it receive} interface specifiers \cite{par:RPC}.
+TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies:
 
-{\it in} is a specifier for input arguments.
-A callee side uses the memory of arguments with {\it in} during executing the callee function.
+\begin{itemize}
+\item {\it in} is a specifier for input arguments.
+A callee side uses the memory of arguments with {\it in} when executing the callee function.
 When the processing returns to the caller side, the caller can reuse and deallocate the memory.
 
-{\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
-The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
-In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
-On the other hand, in case of {\it send}, the caller allocates the data memory and the callee deallocates it.
+\item {\it send} is another specifier for transferring data to a callee from a caller such as {\it in}.
+The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
+In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
+By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.
 
-{\it out} is a specifier for output arguments.
-A callee writes data in the memory allocated by a caller, and the caller receives the data.
+\item {\it out} is a specifier for output arguments through which a callee writes data in the memory allocated by a caller while the caller receives the data.
 
-{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
-The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown in Fig. \ref{fig:SendReceive}.
-While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
-Deallocating the memory is performed in the caller in both cases.
+\item {\it receive} is another specifier for a caller receiving data from a callee such as {\it out}.
+The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
+In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
+Deallocating of the memory is performed in the caller in both cases.
+\end{itemize}
 
 As shown in Fig.
-\ref{src:SendReceive}, the arguments of sending and receiving data such as {\it outputp} and {\it inputp} are defines with the {\it send/receive} specifiers in the signature description.
+\ref{src:SendReceive}, data sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
 
@@
 
-\subsection{Dynamic Connection of TECS}
+\subsection{Dynamic connection in TECS}
 \label{sec:DynamicConnection}
@@
 
-TECS supports dynamic connection as a new functionality.
-Dynamic connection is a method to switch the binding of components at runtime as shown in Fig. \ref{fig:DynamicConnection}.
-Note that all components are statically generated in TECS.
-TECS can optimize the overhead of componentization because components are statically configured.
-Dynamically generating the components causes a lot of memory consumption, which is a serious problem for embedded systems with strict memory constraint.
-The proposed framework realizes the componentization of TINET while satisfying the memory constraint, because components statically generate and dynamically connect in TECS.
+TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
+Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
+Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
+The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.
 
-TINET+TECS utilizes the dynamic connection to switch between CEP and REP components as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
-In a server application, CEP is associated with REP in the state waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout)}.
-For example, when processing with HTTP protocol, CEP passively opens with REP of port number 80.
+TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
+For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.
 
@@
 
-To utilize dynamic connection, the selector should be defined.
-The selector connects all the components that can be dynamically connnected, to refer the descriptor of them.
-Descriptor is an identifier to access the component \cite{par:optimization}.
-cREP ports are call ports array, which connect the number of tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
-{\it [ref\_desc]} is described to identify the call port refers to descriptors. 
-In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
+To utilize dynamic connectivity, a selector should be defined.
+A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
+The cREP ports form a call port array connecting to connecting to all tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
+{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
+In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
 
-A CEP component has two call ports.
-cRepSelector port connects eRepSelector port of tRepSelector cell and cREP4 port connects either of tREP cells (Lines 13-15 in Fig. \ref{src:DynamicCDLcode}).
-cREP port is defined with {\it [dynamic]} to identify the call port dynamically switch the components.
-The call port with {\it [dynamic]} specifier is not optimized and allocated in RAM by a plug-in.
+A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 13--15 in Fig.
+\ref{src:DynamicCDLcode}).
+The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
+The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.
 
@@
 Fig. \ref{src:DynamicCcode} shows a sample code of dynamic connection.
-The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} with TECS, which is utilized to be the state waiting for connection request.
-In the function, dynamic connection is performed as shown in Fig. \ref{src:DynamicCcode}.
-First, get the descriptor of REP to be joined (Line 3 in Fig. \ref{src:DynamicCcode}).
-The first argument, {\it \&desc}, is a variable to store the descriptor information, and the second argument, {\it repid}, is the index of tREP cells.
-Next, set the desctriptor (Line 5 in Fig. \ref{src:DynamicCcode}).
-cREP port combines the tREP cell that descriptor specify.
-Thus, the tCEP cell can call the function of tREP cell to be joined (Line 7 in Fig. \ref{src:DynamicCcode}).
+The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for connection request.
+Dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
+First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
+The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
+Next, the descriptor is set (Line 5 in Fig.
+\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.
+\ref{src:DynamicCcode}).
 
@@
 \end{lstlisting}
-\caption{Accept function (a dynamic connection example)}
+\caption{Accept function (Dynamic connection example)}
 \label{src:DynamicCcode}
@@
 
-\subsection{TECS Adapter}
+\subsection{TECS adapter}
 \label{sec:TECS Adapter}
 
-TECS supports {\it Adapter} functionality which enables to call a function in TECS from existing C codes.
-An adapter is implemented between C codes and a TECS component, and links a C function to a TECS function shown in Fig. \ref{fig:TECS_Adapter}.
-In TINET+TECS, when the application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls the function of tTCPCEP such as {\it eAPI\_sendData}.
-Note that {\it tcp\_snd\_dat} is defined with the name {\it eAPI\_sendData} in TINET+TECS.
-The adapter wraps the APIs used in the existing applications into TECS functions.
-Therefore, software developers can utilize an existing TCP/IP application by using the adapter.
+TECS supports {\it Adapter} functionality, which enables to calling a function in TECS from existing C codes.
+The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECS_Adapter}.
+In TINET+TECS, when an application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls a function of tTCPCEP such as {\it eAPI\_sendData}.
+Note that {\it tcp\_snd\_dat} is defined under the name {\it eAPI\_sendData} in TINET+TECS.
+The adapter wraps the APIs used in the existing applications into TECS functions, enabling software developers to utilize an existing TCP/IP application via the adapter.
 

### 2017-02-11 ISORC2017/paper.tex
Fix evaluation, related work, and conclusion by enago

@@
 
-This section describes our experimental evaluation to demonstrate the effectiveness of the proposed framework.
+This section describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
 
-\subsection{Evaluation Environment}
+\subsection{Evaluation environment}
 
-GR-PEACH is employed as the evaluation board.
-We connected the board and the host PC with a LAN cable, and evaluated the data transmission and reception.
-The detail specification of the board is shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
+GR-PEACH was employed as the evaluation board.
+Detailed specifications of the board are shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
 We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2
+To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data transmission and reception.
 
@@
 
-To demonstrate the low overhead of TINET+TECS, we evaluated the execution time and the memory consumption of TINET+TECS compared with TINET.
+To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the comparison results shown in Fig.
+\ref{fig:EvaluationOfExecutionTime}.
 
-The comparison of execution time between TINET and TINET+TECS is shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
-The APIs used for the evaluation are {\it tcp\_snd\_dat} to send TCP data and {\it tcp\_rcv\_dat} to receive TCP data.
-For {\it tcp\_snd\_dat}, we measured the executing time from the API calling by the application to the return of the processing result.
-In TINET+TECS, the process is performed in the order of tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed of Fig.
+The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
+For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
+In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
 \ref{fig:ComponentProtocolStack}.
-For {\it tcp\_rcv\_dat}, we measured the execution time from the data receiving in the LAN driver to the data acquisition in the application.
-In TINET+TECS, the process is performed in the order of tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication of Fig. \ref{fig:ComponentProtocolStack}.
-The execution time of TINET+TECS is as well as that of TINET; the overhead is about 3 usec.
-{\it send/receive} specifiers enable to access the buffer address without data copies.
-Therefore, the overhead of componentization does not effect the execution time.
+For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
+In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
+The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 ms.
+As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \caption{Execution time of TINET and TINET+TECS}
+    \caption{Execution times of TINET and TINET+TECS}
     \label{fig:EvaluationOfExecutionTime}
@@
 The memory consumptions of TINET and TINET+TECS are compared in TABLE \ref{tab:EvaluationOfMemoryConsumption}.
-The memory consumption of TINET+TECS increases about 2.5\% compared with TINET.
-The processes and data to manage TECS components, such as initialization of cells, descriptors, function tables, and skeleton functions, cause the increase memory consumption.
+The memory consumption of TINET+TECS is about 1\% higher than that of TINET, as the data and processes such as initialization of cells, descriptors, function tables, and skeleton functions needed to manage TECS components increase memory consumption.
 
@@
 As shown in TABLE \ref{tab:EvaluationOfConfigurabilty}, the code lines for modification were measured to demonstrate the improved configurability.
-We can change the composition of the protocol stack with a small workload.
-Thus, the proposed framework improves the configurability.
+This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
 
@@
 
-\subsection{Dynamic Connection}
+\subsection{Dynamic connection}
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \caption{Component diagrams of two cases (without/with dynamic connection)}
+    \caption{Component diagrams for two cases (without/with dynamic connection)}
     \label{fig:ComparisonOfDynamicConnection}
@@
 
-The memory consumption without and with TECS dynamic connection was evaluated.
-As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP component should statically connect to all REP components in the case dynamic connection is not used.
-As the number of REPs increases, call ports of CEP are required for that.
-Thus, it consumes a lot of memory. 
-Dynamic connection reduces the memory consumption because only one call port of CEP for REP, which is drawn with red lines in the right of Fig.
-\ref{fig:ComparisonOfDynamicConnection}, is required per CEP.
-Even when the number of REPs increases, a call port of the selector, not the CEP, is joined.
+Memory consumption without and with TECS dynamic connection was then evaluated.
+As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if dynamic connection is not used.
+As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
+Dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig.
+\ref{fig:ComparisonOfDynamicConnection}.
+Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.
 
-The memory consumption of two cases, without/with dynamic connection, is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
-The case of dynamic connection consumes the RAM memory more than the other case because the call ports with {\it [dynamic]} is not optimized and allocated in RAM areas as mentioned in Section \ref{sec:DynamicConnection}.
-The total memory consumption is fewer in the proposed framework.
+Memory consumption of without and with dynamic connection is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
+The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
+However, the overall memory consumption is lower under the proposed framework.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
-    \caption{Memory consumption of two cases (with/without dynamic connection)}
+    \caption{Memory consumption in two cases (with/without dynamic connection)}
     \label{fig:EvaluationOfDynamicConnection}
@@
 
-The comparison of CDL code lines of without/with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
+The comparison of CDL code lines of without and with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
 As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
-In the left part of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
-In the right part of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
-Since the difference spreads as the number of CEPs and REPs increases, it is effective for software that uses many ports.
+In the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
+In the right panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
+It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
 
-\subsection{Overhead of Adapter}
+\subsection{Adapter overhead}
 
-The execution time of API with the adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} to analyze the overhead of TECS adapter which supports existing applications.
-As shown in Fig. \ref{fig:EvaluationOfAdapter}, the overhead of TECS adapter is very small because the adapter only passes the parameters to TECS components from C codes.
-Therefore, TECS adapter does not affect the system.
+The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
+As shown in Fig.
+\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
-    \caption{Execution time of two cases (without/with TECS adapter)}
+    \caption{Execution times in two cases (without/with TECS adapter)}
     \label{fig:EvaluationOfAdapter}
@@
 {\bf uIP:}
-uIP (microIP) is a very small TCP/IP stack intended for tiny 8-bit and 16-bit microcontrollers.
-    uIP only requires about five KB of code size and several hundreds bytes of RAM.
+uIP (microIP) is a very small TCP/IP stack intended for tiny 8- and 16-bit microcontrollers.
+uIP requires only about 5 KB of code size and several hundred bytes of RAM.
 uIP has been ported to various systems and has found its way into many commercial products.
-After ver.
-1.0 is released, later versions of uIP, including uIPv6, are integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontroller to the Internet.
+Following the release of ver.
+1.0, later versions of uIP, including uIPv6, have been integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontrollers to the Internet.
 
 {\bf lwIP:}
-lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems.
-The focus of lwIP is to reduce memory resource while still having a full scale TCP.
+lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems that is intended to reduce memory resource usage while still maintaining a full-scale TCP.
 lwIP requires about 40 KB of ROM and tens of KB of RAM.
@@
 This paper proposed TINET+TECS, a component-based TCP/IP protocol stack for embedded systems.
-TINET+TECS is componentized TINET, which is a compact TCP/IP protocol stack, using TECS.
-TINET consists of many macros and complicated codes and the software productivity are low.
-The proposed framework improves the configurability while suppressing the overhead of componentization.
-The proposed framework also improves the scalability because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
+TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
+Because TINET comprises many macros and complicated codes, its software productivity is low.
+The proposed framework improves on TINET's configurability while suppressing the overhead of componentization.
+Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
 
-In addition, this paper presents dynamic connection, a new method of TECS, to enable dynamic processing while reducing memory consumption.
-To satisfy TINET specification that TINET support static generation of CEPs and REPs, TINET+TECS utilizes dynamic connection.
-TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
+This paper also presented dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
+TINET+TECS utilizes dynamic connection to satisfy the TINET specification for supporting static generation of CEPs and REPs.
+As the TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
 
-In the future, the proposed framework will cooperate with mruby on TECS \cite{par:mrubyonTECS} to easily manage IoT devices.
+In future work, we will adapt the proposed framework to cooperate with mruby on TECS \cite{par:mrubyonTECS} to more easily manage IoT devices.
 Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
-We will support the functionalities that TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
+We will support functionalities in which TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.
 

### 2017-02-11 ISORC2017/paper.tex
Adjustment

@@
 
-The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices, smart devices, and smart homes, will be connected via the Internet to further enrich people's lives.
-However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of, for example, low memory capacity.
+The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
+However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of low memory capacity.
 
@@
 This paper proposes a component-based TCP/IP protocol stack for embedded systems--TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS)--to improve the configurability and scalability of TCP/IP software.
-Because it is a component system suitable for embedded systems, TECS \cite{par:TECS} \cite{par:hr-tecs} is used to componentize TINET in the proposed protocol stack.
+Because it is a component system suitable for embedded systems, TECS is used to componentize TINET in the proposed protocol stack.
 As TECS supports static configurations that statically define component behaviors and interconnections, it can optimize the componentization overhead.
 
-In addition to satisfying the original TINET specifications, the proposed framework utilizes the TECS dynamic connection capability to dynamically switch component bindings.
-Although general TCP/IP protocol servers dynamically process requested ports, i.e., Hypertext Transfer Protocol (HTTP, port: 80) and Hypertext Transfer Protocol Secure (HTTPS, port: 443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
+To satisfy the original TINET specifications, TINET+TECS utilizes the TECS dynamic connection method to dynamically switch component bindings.
+Although general TCP/IP protocol servers dynamically process requested ports, i.e., Hypertext Transfer Protocol (HTTP, port:80) and Hypertext Transfer Protocol Secure (HTTPS, port:443), embedded systems are restricted in their dynamic processing ability owing to strict memory constraints.
 TINET supports the static generation of Communication Endpoints (CEPs) and Reception Points (REPs), which are similar to sockets.
@@
 
-This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities in order to improve configurability with small overheads.
+This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities to improve configurability with small overheads.
 Furthermore, the advantages of dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.
 
-{\bf Contributions:} This paper provides the following contributions:
+% {\bf Contributions:}
+This paper provides the following contributions:
 
-\begin{enumerate}
-
-    \item {\bf Improve configurability}\mbox{}\\
+{\bf Improve configurability:}
 Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
@@
 
-    \item {\bf Dynamic connection method}\mbox{}\\
+{\bf Dynamic connection method:}
 Dynamically switching the binding of components, that is, switching between a TINET communication endpoint and REP, realizes a TCP/IP protocol stack for an embedded system.
 
-    \item {\bf Support legacy codes}\mbox{}\\
+{\bf Support legacy codes:}
 TINET+TECS can be applied to existing applications because TECS supports the ability of the adapter to call TECS functions from C codes. 
@@
 
-\end{enumerate}
-
-{\bf Organization}: The remainder of this paper is organized as follows.
+% {\bf Organization:}
+The remainder of this paper is organized as follows.
 Section \ref{sec:System Model} introduces the system model and its basic technologies, i.e., TINET and TECS.
@@
     \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
-    \caption{System model of TINET+TECS}
-    \label{fig:SystemModel}
+    \vspace{-1mm} \caption{System model of TINET+TECS}
+    \vspace{-1mm} \label{fig:SystemModel}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
-    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
-    \label{fig:TINETHierarchyDiagram}
+    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
+    \vspace{-1mm} \label{fig:TINETHierarchyDiagram}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentDiagram.pdf}
-    \caption{Component diagram}
-    \label{fig:ComponentDiagram}
+    \vspace{-1mm} \caption{Component diagram}
+    \vspace{-1mm} \label{fig:ComponentDiagram}
 \end{figure}
@@
 
-The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions that defines the interface definition of the {\it cell}.
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, a set of functions that defines the interface definition of the {\it cell}.
 The {\it cell's} {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
-Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
+Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.
 
@@
 
-\begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
+{\bf Signature Description:}
 The {\it signature} defines a {\it cell} interface.
@@
 Similarly, [size\_is({\it len})] represents an array of size {\it len}.
+
 \begin{figure}[t]
@@
 \end{lstlisting}
-\caption{Signature description}
-\label{src:signature}
+\vspace{-1mm} \caption{Signature description}
+\vspace{-1mm} \label{src:signature}
 \end{figure}
-    \item[{\bf Celltype Description}]\mbox{}\\
+
+{\bf Celltype Description:}
 The {\it celltype} defines the {\it entry} ports, {\it call} ports, attributes, and variables.
@@
 Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+
 \begin{figure}[t]
@@
     entry sIPv4Output eOutput;
-
     /* Call port */
@@
     /* Omit: other call ports */
-
     attr {  /* Attribute */
@@
 \end{lstlisting}
-\caption{Celltype description}
-\label{src:celltype}
+\vspace{-1mm} \caption{Celltype description}
+\vspace{-1mm} \label{src:celltype}
 \end{figure}
-    \item[{\bf Build Description}]\mbox{}\\
-        The build description is used to instantiate and connect {\it cell}s.
+
+{\bf Build Description:}
+The build description is used to instantiate and bind {\it cell}s.
 Fig. \ref{src:build} shows an example of a build description.
 A {\it celltype} name and {\it cell} name, e.g., tIPv4Output and IPv4Output, respectively, follow the keyword {\it cell}.
-        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
+% A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
 In Fig. \ref{src:build}, {\it entry} port eIPv4Output in {\it cell} IPv4Output is connected to {\it call} port cIPv4Output in {\it cell} TCPOutput.
@@
     /* Omit: other build description */
-
     fragInit = 0; /* Attribute */
@@
 \end{lstlisting}
-\caption{Build description}
-\label{src:build}
+\vspace{-1mm} \caption{Build description}
+\vspace{-1mm} \label{src:build}
 \end{figure}
-
-\end{description}
 
@@
 By using such small grain components, software visibility is improved.
+The components of each protocol are described in the following.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
-    \caption{Component diagram of a protocol stack}
-    \label{fig:ComponentProtocolStack}
+    \vspace{-1mm} \caption{Component diagram of a protocol stack}
+    \vspace{-1mm} \label{fig:ComponentProtocolStack}
 \end{figure}
-
-The components of each protocol are described in the following.\\
 
@@
 {\bf Network layer:}
-tIPv4Input and tIPv4Output are components that perform, respectively, the receiving and sending processing in the network layer.
-The tIPv4Functions component performs functions such as checksum, the tICMP component is for implementing the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
+The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
+The tIPv4Functions component performs functions such as checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
 
@@
 tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components for performing, respectively, receiving and sending processing in the data link layer.
-The tArp component is used for the Address Resolution Protocol (ARP).
+The tArp component is for implementing the Address Resolution Protocol (ARP).
 
@@
 The tNetworkInterfaceContoroller component implements a network device driver.
-Software can be run on other devices by replacing the component because only the component depends on the target device.\\
+Software can be run on other devices by replacing the component because only the component depends on the target device.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
-    \caption{Component diagram of tMemoryAllocator}
-    \label{fig:tMemoryAllocator}
+    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
+    \vspace{-1mm} \label{fig:tMemoryAllocator}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
-    \caption{Differences between in/out and send/receive}
-    \label{fig:SendReceive}
+    \vspace{-1mm} \caption{Differences between in/out and send/receive}
+    \vspace{-1mm} \label{fig:SendReceive}
 \end{figure}
@@
 \end{lstlisting}
-\caption{Signature description of the nic driver (An example of send/receive)}
-\label{src:SendReceive}
+\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
+\vspace{-1mm} \label{src:SendReceive}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
-    \caption{Dynamic connection}
-    \label{fig:DynamicConnection}
+    \vspace{-1mm} \caption{Dynamic connection}
+    \vspace{-1mm} \label{fig:DynamicConnection}
 \end{figure}
@@
 TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
-In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}\\tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
+In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
 For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.
@@
     \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
-    \caption{Dynamic connection between CEP and REP}
-    \label{fig:DynamicConnectionUseCase}
+    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
+    \vspace{-1mm} \label{fig:DynamicConnectionUseCase}
 \end{figure}
@@
 A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
-The cREP ports form a call port array connecting to connecting to all tREP cells (Line 9 in Fig. \ref{src:DynamicCDLcode}).
+The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
 {\it [ref\_desc]} is used to identify call ports referring to descriptors. 
@@
 
-A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 13--15 in Fig.
+A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig.
 \ref{src:DynamicCDLcode}).
@@
 };
-
 celltype tRepSelector {
@@
 };
-
 celltype tTCPCEP {
@@
 \end{lstlisting}
-\caption{Signature and celltype description for dynamic connection}
-\label{src:DynamicCDLcode}
+\vspace{-1mm} \caption{Signature and celltype description for dynamic connection}
+\vspace{-1mm} \label{src:DynamicCDLcode}
 \end{figure}
@@
 \end{lstlisting}
-\caption{Accept function (Dynamic connection example)}
-\label{src:DynamicCcode}
+\vspace{-1mm} \caption{Accept function (Dynamic connection example)}
+\vspace{-1mm} \label{src:DynamicCcode}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
-    \caption{TECS adapter}
-    \label{fig:TECS_Adapter}
+    \vspace{-1mm} \caption{TECS adapter}
+    \vspace{-1mm} \label{fig:TECS_Adapter}
 \end{figure}
@@
 Detailed specifications of the board are shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
-We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2
-To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data transmission and reception.
+We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
+To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.
 
@@
     \centering
-    \caption{Evaluation Board Environment}
+    \vspace{-1mm} \caption{Evaluation Board Environment}
     \begin{tabular}{l|l}
@@
 
-To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the comparison results shown in Fig.
-\ref{fig:EvaluationOfExecutionTime}.
+To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \caption{Execution times of TINET and TINET+TECS}
-    \label{fig:EvaluationOfExecutionTime}
+    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
+    \vspace{-1mm} \label{fig:EvaluationOfExecutionTime}
 \end{figure}
@@
     \centering
-    \caption{Memory consumption of TINET and TINET+TECS}
+    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
     \begin{tabular}{c|r|r|r|r}
@@
 
-As shown in TABLE \ref{tab:EvaluationOfConfigurabilty}, the code lines for modification were measured to demonstrate the improved configurability.
+As shown in TABLE \ref{tab:EvaluationOfConfigurability}, the code lines for modification were measured to demonstrate the improved configurability.
 This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
@@
     \centering
-    \caption{Modified code lines of CDL}
+    \vspace{-1mm} \caption{Modified code lines of CDL}
     \begin{tabular}{c|r|r|r}
         \hline\hline
-                         &   Size       &   Size (- Default)  & CDL  \\ \hline
+                         &   Size       &   Size (-- Default) & CDL  \\ \hline
         Default          &   325.23 KB  &              0 KB   &  0 lines   \\
-        I                &   305.40 KB  &       - 19.83 KB    & 18 lines    \\
-        I + I\hspace{-.1em}I &   304.12 KB  &   - 21.10 KB    & 27 lines   \\
-        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & - 21.77 KB  & 32 lines \\
+        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
+        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
+        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
         \hline
@@
     \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \caption{Component diagrams for two cases (without/with dynamic connection)}
-    \label{fig:ComparisonOfDynamicConnection}
+    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection cases}
+    \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
 \end{figure}
@@
 
-\begin{figure}[t]
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
+%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
+%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
+% \end{figure}
+\begin{table}[t]
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
-    \caption{Memory consumption in two cases (with/without dynamic connection)}
+    \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
+        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
+        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
+        \hline
+    \end{tabular}
     \label{fig:EvaluationOfDynamicConnection}
-\end{figure}
+\end{table}
 
@@
     \centering
-    \caption{CDL code lines of without/with dynamic connection}
+    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
     \begin{tabular}{l|r|r|r}
@@
  \end{lstlisting}
- \caption{Comparison of CDL descriptions between without/with dynamic connection}
- \label{src:ComparisonOfCDL}
+ \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
+ \vspace{-1mm} \label{src:ComparisonOfCDL}
 \end{figure}
 
-The comparison of CDL code lines of without and with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection}, to demonstrate improved configurability by dynamic connection.
+The code lines in CDL of without and with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection} to demonstrate improved configurability.
 As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
@@
     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
-    \caption{Execution times in two cases (without/with TECS adapter)}
-    \label{fig:EvaluationOfAdapter}
+    \vspace{-1mm} \caption{Execution times in two cases (without/with TECS adapter)}
+    \vspace{-1mm} \label{fig:EvaluationOfAdapter}
 \end{figure}

### 2017-04-07 ICESS2017/paper.tex
Add ICESS2017

--- 2017-02-11 ISORC2017/paper.tex
@@
 Hiroshi Oyama\IEEEauthorrefmark{3},
-Hiroaki Takada\IEEEauthorrefmark{2} and
+Hiroaki Takada\IEEEauthorrefmark{2}, and
 Takuya Azumi\IEEEauthorrefmark{1}}
@@
 A system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
-TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components.
-CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method.
-Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications.
+TINET+TECS is a component-based TCP/IP protocol stack in which the TCP output task (tTCPOutput) and Ethernet input task (tEhternetInput) are implemented as TECS components (Section \ref{sec:TINET+TECS}).
+CEPs and REPs (Section \ref{sec:TINET}), which are also implemented as TECS components, dynamically switch bindings using the TECS method (Section \ref{sec:DynamicConnection}).
+Moreover, the TECS adapter supports the legacy codes for existing TCP/IP applications (Section \ref{sec:TECSAdapter}).
 
@@
 \subsection{TINET+TECS}
+\label{sec:TINET+TECS}
+
 TINET+TECS, the proposed componentized TCP/IP protocol stack, comprises a number of some TECS components.
@@
 TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
+In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
 Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
@@
 \subsection{TECS adapter}
-\label{sec:TECS Adapter}
+\label{sec:TECSAdapter}
 
@@
 
-Memory consumption of without and with dynamic connection is shown in Fig. \ref{fig:EvaluationOfDynamicConnection}.
+Memory consumption of without and with dynamic connection is shown in TABLE \ref{fig:EvaluationOfDynamicConnection}.
 The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
@@
     \centering
-    \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
+    \vspace{-1mm} \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
+    {\tabcolsep = 1mm
     \begin{tabular}{c|r|r|r|r}
@@
     \end{tabular}
+    }
     \label{fig:EvaluationOfDynamicConnection}
@@
 
-\subsection{Adapter overhead}
-
-The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
-As shown in Fig.
-\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.
-
 \begin{figure}[t]
@@
 
+\subsection{Adapter overhead}
+
+The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
+As shown in Fig.
+\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.
+
 \section{Related Work}
@@
 
-Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP}, lwIP \cite{par:lwIP}.
+Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.
 
@@
 As the TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
+TINET+TECS and application programs used in the evaluation are all open-source, and may be downloaded from our website \cite{url:TINET+TECS}.
 

### 2017-04-16 ICESS2017/paper.tex
Fix figures in evaluation
Final version

@@
 
-The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTIndustries} \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
+The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
 However, as the IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, it is often not practical to implement the same Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stacks used by traditional computing systems because embedded systems face restrictions in terms of low memory capacity.
@@
 Tomakomai InterNETworking (TINET) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
-As TINET supports functionalities such as a minimum copy frequency and the elimination of dynamic memory control, it requires significantly reduced memory for its TCP/IP protocol stack and is therefore suitable for embedded systems.
+As TINET supports functionalities such as a minimum copy frequency and the elimination of dynamic memory control, it requires significantly reduced memory for its TCP/IP protocol stack and is, therefore, suitable for embedded systems.
 However, TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
@@
 
-One approach to improving software productivity is component-based development, a design technique that can be applied in reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD} such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, or SaveCCM \cite{par:SAVEapproach}.
+One approach to improving software productivity is component-based development (CBD), a design technique that can be applied in reusable software development for embedded systems \cite{par:Crnkovic}\cite{par:CBD} such as TECS \cite{par:TECS} \cite{par:hr-tecs}, AUTOSAR \cite{url:AUTOSAR}, or SaveCCM \cite{par:SAVEapproach}.
 Component-based systems are flexible to software extension and specification changes.
@@
 In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
-To solve this problem, TINET does passes the pointer of the data buffer between each protocol layer instead of performing data copying.
+To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of performing data copying.
 
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
     \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
@@
 
-In TECS, component deployment and composition are performed statically, and as a consequently, component connection does not incur significant overhead, and memory requirements can be reduced.
+In TECS, component deployment and composition are performed statically, and as a consequently, a component connection does not incur significant overhead, and memory requirements can be reduced.
 TECS has various features such as source level portability and fine-grained components and can be implemented in C.
@@
 Fig. \ref{fig:ComponentDiagram} shows a component diagram.
-{\it Cells}, which are instance of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
+{\it Cells}, which are instances of components in TECS, consist of {\it entry} ports, {\it call} ports, attributes, and internal variables.
 An {\it entry} port is an interface that provides functions to other {\it cells}, whereas a {\it call} port is an interface that enables the use of other {\it cells}' functions.
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature description}
+\vspace{-2mm} \caption{Signature description}
 \vspace{-1mm} \label{src:signature}
@@
     call sEthernetOutput cEthernetOutput;
-    /* Omit: other call ports */
     attr {  /* Attribute */
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Celltype description}
+\vspace{-2mm} \caption{Celltype description}
 \vspace{-1mm} \label{src:celltype}
@@
 cell tIPv4Output IPv4Output {
-    /* Omit: other build description */
     fragInit = 0; /* Attribute */
@@
     cIPv4Output = IPv4Output.eOutput;
-    /* Omit: other build description */
 };
 \end{lstlisting}
-\vspace{-1mm} \caption{Build description}
+\vspace{-2mm} \caption{Build description}
 \vspace{-1mm} \label{src:build}
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/tMemoryAllocator.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
     \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/SendReceive.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
     \vspace{-1mm} \caption{Differences between in/out and send/receive}
@@
 As shown in Fig.
-\ref{src:SendReceive}, data sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
+\ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
+Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
+Common object request broker architecture (CORBA) does not consider memory sharing; CORBA has no functionalities
+such as {\it send}/{\it receive}.
 
@@
     [send(sNetworkAlloc),size_is(size)]
-        int8_t *outputp,
-    [in]int32_t size,
-    [in]uint8_t align);
+        int8_t *outputp, .., ..);
   void read(
     [receive(sNetworkAlloc),size_is(*size)]
-        int8_t **inputp,
-    [out]int32_t *size,
-    [in]uint8_t align);
+        int8_t **inputp, .., ..);
     /* Omit: other functions */
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
+\vspace{-2mm} \caption{Signature description of the nic driver (An example of send/receive)}
 \vspace{-1mm} \label{src:SendReceive}
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/DynamicConnection.pdf}
-    \vspace{-1mm} \caption{Dynamic connection}
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
+    \vspace{-3mm} \caption{Dynamic connection}
     \vspace{-1mm} \label{fig:DynamicConnection}
@@
 
-TECS supports dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
+TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
 In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
@@
 
-TINET+TECS utilizes dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
 In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
     \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature and celltype description for dynamic connection}
+\vspace{-2mm} \caption{Signature and celltype description for dynamic connection}
 \vspace{-1mm} \label{src:DynamicCDLcode}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Accept function (Dynamic connection example)}
+\vspace{-2mm} \caption{Accept function (Dynamic connection example)}
 \vspace{-1mm} \label{src:DynamicCcode}
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/TECS_Adapter.pdf}
+    \includegraphics[width=7.0cm,clip]{figure/TECS_Adapter.pdf}
     \vspace{-1mm} \caption{TECS adapter}
@@
 
-\subsection{Evaluation environment}
+% \subsection{Evaluation environment}
 
@@
     \vspace{-1mm} \caption{Evaluation Board Environment}
+\vspace{-2mm}
     \begin{tabular}{l|l}
@@
 In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
-The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 ms.
+The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
 As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfExecutionTime.pdf}
     \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
@@
     \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
+\vspace{-2mm}
     \begin{tabular}{c|r|r|r|r}
@@
     \vspace{-1mm} \caption{Modified code lines of CDL}
+\vspace{-2mm}
     \begin{tabular}{c|r|r|r}
@@
     \end{tabular}
+\vspace{-3mm}
     \label{tab:EvaluationOfConfigurability}
@@
     \vspace{-1mm} \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
+\vspace{-2mm}
     {\tabcolsep = 1mm
@@
     \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
+\vspace{-2mm}
     \begin{tabular}{l|r|r|r}
@@
  \end{lstlisting}
+ \vspace{-2mm}
  \centering
@@
  \end{lstlisting}
- \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
+ \vspace{-2mm} \caption{Two CDL codes (without/with dynamic connection)}
  \vspace{-1mm} \label{src:ComparisonOfCDL}
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/EvaluationOfAdapter.pdf}
+    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfAdapter.pdf}
     \vspace{-1mm} \caption{Execution times in two cases (without/with TECS adapter)}
@@
 
+\begin{table*}[t]
+    \caption{Comparison of related and proposed framework}
+    \label{tab:comparison}
+\vspace{-2mm}
+    \centering
+    \begin{tabular}{c||ccccccc}
+        \hline\hline
+        & \shortstack{Configurability}
+        & \shortstack{Generation} 
+        & \shortstack{Binding} 
+        & \shortstack{Support CBD} 
+        & \shortstack{Memory saving} \\ \hline
+        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
+        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
+        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
+        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
+    \end{tabular}
+        \vspace{-5mm}
+\end{table*}
+
 \section{Related Work}
@@
 
+Table \ref{tab:comparison} shows a comparison of TINET+TECS and previous work.
 Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.
@@
 lwIP is larger than uIP, but provides better throughput.
+To customize protocols and buffer size, users should handle a lot of macros.
+
+Note that the proposed framework, TINET+TECS, has demonstrated all features shown in Table \ref{tab:comparison}.
+In particular, TINET+TECS is configurable and is suitable for embedded systems with memory constraint.
 
@@
 
-In future work, we will adapt the proposed framework to cooperate with mruby on TECS \cite{par:mrubyonTECS} to more easily manage IoT devices.
-Note that mruby is a scripting language for embedded systems \cite{par:mruby}.
+In future work, we will adapt the proposed framework to cooperate with mruby on TECS \cite{par:mrubyonTECS}, to more easily manage IoT devices.
 We will support functionalities in which TINET functions can be utilized from mruby programs as an extension of mruby-socket \cite{url:mruby-library}.

### 2017-06-22 ICESS2017/paper.tex
Final version
Camera-Ready ver.

@@
 This paper evaluates the overheads of execution time and memory consumption and the amount of code line changes needed to add and remove functionalities to improve configurability with small overheads.
-Furthermore, the advantages of dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.
+Furthermore, the advantages of the dynamic connection in terms of the memory consumption and low overhead of the TECS adapter are demonstrated.
 
@@
 
-TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a realtime operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a real-time operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
 TINET has been released as an open-source tool.
@@
 TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
-In a server application, CEP is associated with REP in the state of waiting for connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
+In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
 For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.
@@
 \end{lstlisting}
-\vspace{-2mm} \caption{Signature and celltype description for dynamic connection}
+\vspace{-2mm} \caption{Signature and celltype description for the dynamic connection}
 \vspace{-1mm} \label{src:DynamicCDLcode}
@@
 
-Fig. \ref{src:DynamicCcode} shows a sample code of dynamic connection.
-The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for connection request.
-Dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
+Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
+The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
+The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
 First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
@@
 \end{lstlisting}
-\vspace{-2mm} \caption{Accept function (Dynamic connection example)}
+\vspace{-2mm} \caption{Accept function (a dynamic connection example)}
 \vspace{-1mm} \label{src:DynamicCcode}
@@
     \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection cases}
+    \vspace{-1mm} \caption{Component diagrams for without/with the dynamic connection cases}
     \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
@@
 Memory consumption without and with TECS dynamic connection was then evaluated.
-As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if dynamic connection is not used.
+As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
 As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
-Dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig.
+The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig.
 \ref{fig:ComparisonOfDynamicConnection}.
@@
 
-The code lines in CDL of without and with dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection} to demonstrate improved configurability.
+The code lines in CDL of without and with the dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection} to demonstrate improved configurability.
 As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
@@
     \end{tabular}
-        \vspace{-5mm}
 \end{table*}
@@
 
-This paper also presented dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
-TINET+TECS utilizes dynamic connection to satisfy the TINET specification for supporting static generation of CEPs and REPs.
+This paper also presented the dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
+TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.
 As the TECS adapter supports legacy codes, existing TCP/IP applications can run without modification in the proposed framework.
@@
 
-The authers would like to thank Hiroaki Nagashima for supporting this research.
+The authors would like to thank Hiroaki Nagashima for supporting this research.
 This work is supported by JSPS KAKENHI Grant Number 15H05305.

### 2017-06-23 kansai/paper.tex
Add kansai (ipsj)

--- 2016-02-23 ETNET2016/thesis.tex
@@
-%        File: thesis.tex
-%     Created: Tue Feb 16 06:00 PM 2016 J
-% Last Change: Tue Feb 16 06:00 PM 2016 J
+%        File: paper.tex
+%     Created: Fri Jun 23 06:00 PM 2017 J
+% Last Change: Fri Jun 23 06:00 PM 2017 J
 %
 \input{../EMSOFT2016/dummy/dummy.tex}
-%\documentclass[submit]{ipsj_v2/UTF8/ipsj}
-%\documentclass{ipsj}
-%\documentclass[submit,techrep]{ipsj_v2/UTF8/ipsj}
-\documentclass[submit,techrep]{ipsj}
+\documentclass[submit]{ipsj_v2/UTF8/ipsj}
 
@@
 
-\title{Bluetoothを用いたマルチVM対応\\mrubyバイトコードローダ}
+\title{組込みシステムに適した動的メモリアロケータのコンポーネント化}
 
-\etitle{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}
+\etitle{Componentized Dynamic Memory Allocator for Embedded Systems}
 
-\affiliate{OU}{大阪大学基礎工学部\\
+\affiliate{OU}{大阪大学基礎工学研究科\\
 School of Engineering Science, Osaka University}
@@
 
-\affiliate{GOU}{大阪大学基礎工学研究科\\
-Graduate School of Engineering Science, Osaka University}
-
 \author{山本 拓朗}{Takuro Yamamoto}{OU}%[joho.taro@ipsj.or.jp]
 \author{大山 博司}{Hiroshi Oyama}{OKUMA}%
-\author{安積 卓也}{Takuya Azumi}{GOU}%[gakkai.jiro@ipsj.or.jp]
-
-\begin{abstract}
-近年，組込みシステムは複雑化・大規模化しているため，ソフトウェアの生産性が問題になっている．
-組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
-現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
-さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
-本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
-さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する．
-\vspace{-4mm}
-\end{abstract}
-
-% \begin{jkeyword}
-% 情報処理学会論文誌ジャーナル，\LaTeX，スタイルファイル，べからず集
-% \end{jkeyword}
-
-\begin{eabstract}
-In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
-For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
-In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
-Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of RTOSs to effectively execute multiple mruby programs in concurrent.
-To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
-In addition, multiple mruby programs cooperatively run in the proposed framework.
-%A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
-\vspace{-4mm}
-\end{eabstract}
-
-% \begin{ekeyword}
-% IPSJ Journal, \LaTeX, style files, ``Dos and Don'ts'' list
-% \end{ekeyword}
+\author{安積 卓也}{Takuya Azumi}{OU}%[gakkai.jiro@ipsj.or.jp]
 
@@
 \section{はじめに}
-\vspace{-2mm}
-近年，組込みシステムは高品質・高性能化に伴い，複雑化・大規模化している上に，製品の低コスト化や短期間での開発も要求されている．
 
-ソフトウェアを効率的に開発するアプローチに，コンポーネントベース開発がある．
-%コンポーネントベース開発は，再利用可能なコンポーネントを構成するための設計手法である．
-コンポーネント化されたソフトウェアは，再利用性が高く，検証が容易になるため，複雑・大規模なソフトウェアを効率的に開発できる．
-システムの拡張や仕様変更に柔軟に対応できる．
-組込みシステムのコンポーネント技術として，TECS (TOPPERS Embedded Component System)\cite{par:TECS}やAUTOSAR\cite{url:AUTOSAR}がある．
+\section{基礎技術}
+\label{sec:Background}
 
-効率的なソフトウェア開発のもう一つのアプローチとして，スクリプト言語がある．
-現在の組込みソフトウェアのほとんどはC言語で開発されているが，C言語による開発はコストが高く，開発期間も長くなる．
-スクリプト言語は，その使いやすさから高い生産性を持っているため，効率的かつ短期間での開発ができる．
-有名なスクリプト言語として，Ruby，Perl，Python，Luaなどがある．
+\subsection{TLSF}
 
-しかし，スクリプト言語は生産性が高い反面，C言語よりも実行時間が遅く，実行時間にばらつきがある．
-多くの組込みシステムは，リアルタイム性が重要であるため，スクリプト言語を組込みシステムに利用することは難しい．
-
-%mruby on TECSは，スクリプト言語であるmruby使用したコンポーネントベース開発が可能なフレームワークである\cite{par:mrubyonTECS}．
-mruby on TECS \cite{par:mrubyonTECS}は，mruby(軽量Ruby)\cite{par:mruby}と，組込みシステム向けのコンポーネントシステムであるTECSを利用したフレームワークである．
-mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べてアプリケーションを約100倍速く実行できる．
-
-現状のmruby on TECSでは，いくつかの問題がある．
-mruby on TECSは，mrubyプログラムをロードするための方法として，SDカードやROMへの書き込みにしか対応していないため，作業効率が悪い．
-例えば，LEGO MINDSTORMS EV3のプラットフォーム\cite{par:EV3}を利用した場合，mrubyプログラムを修正する度に，SDカードの抜き差しを行う必要がある．
-%mruby on TECS では，mruby プログラムを修正する度にターゲットデバイスでSD カードまたはROMに書き込みし，OS を再起動する必要がある．
-さらに，mruby on TECSはマルチVMに対応しているが，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない．
-
-% mrubyバイトコードローダによって，開発者ははじめの一度だけ記憶装置にプラットフォーム部分を書き込み，mrubyアプリケーションのバイトコードをホストからターゲットデバイスへBluetoothを用いて転送し，実行することが可能になる．
-% 繰り返してSDカードの抜き差しやROMへの書き込みをする手間が省けるため，作業効率は向上する．
-% RiteVMスケジューラは複数のmrubyアプリケーションを
-本論文では，上記の問題を解決するため，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダおよびRiteVMスケジューラを提案する．
-% 提案フレームワークでは，プラットフォーム部分をコンパイル・リンクし，ターゲットデバイス上で起動する．
-% ホストPC 側では，mruby アプリケーション(.rb) をバイトコード(.mrb) にコンパイルし，Bluetooth を通してターゲットデバイスにバイトコードを転送する． 
-% ターゲットデバイス側では，RiteVM に実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmruby ライブラリと合わせてアプリケーションを実行する．
-% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる．
-% RiteVMに実装されたローダが，ホストから転送されたバイトコードを受信し，アプリケーションを実行する．
-% これによって，繰り返しSDカードの抜き差しやROMへの書き込みをする手間やOSを再起動する時間が省けるため，作業効率を上げることができる．
-% さらに，各VM の処理を平等に実行するRiteVM スケジューラを提供することで，マルチタスク処理を効率的に利用できる．
-
-本論文における貢献は次の通りである．
-mrubyバイトコードローダにより，ソフトウェア開発における作業効率を向上させる．
-RiteVMスケジューラにより，複数のmrubyプログラムを効率的に並行動作させる．
-コンポーネントベース開発の利点を明らかにする．
-% Contribution: The proposed framework gives the contribution in the following points.
-% 1) To improve the software development efficiency:
-% Developers do not need to rewrite a storage/ROM device and also to restart an OS. 
-% The loader supports the continuous loading, which saves the Bluetooth setup time. 
-% Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
-% 2) To effectively execute multiple mruby programs in concurrent or/and parallel: 
-% Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
-% In addition, synchronization of multiple tasks is also implemented.
-% 3) To focus on the benefits of component-based developments:
-% This paper shows the specific examples for the benefits of component-based development.
-
-本論文の構成を次に述べる．
-まず\ref{sec:Background}章で，提案フレームワークのベースであるmruby on TECSについて述べる．
-\ref{sec:Design and Implementation}章では，提案フレームワークの設計と実装について述べる．
-\ref{sec:Evaluation}章では，提案フレームワークの作業効率や実行時間のオーバヘッドを評価する．
-\ref{sec:Related Work}章では，関連研究について述べる．
-最後に，\ref{sec:Conclusion}章で本論文をまとめる．
-
-% Organization: The paper is organized as follows. 
-% Section 2 introduces the basic technologies i.e. mruby, TECS and mruby on TECS. 
-% Section 3 describes the design and implementation of the proposed framework in detail. 
-% Section 4 evaluates the proposed framework, Section 5 discusses related work, and then Section 6 concludes this paper.
-\vspace{-2mm}
-\section{mruby on TECS (既存フレームワーク)}
-\vspace{-2mm}
-\label{sec:Background}
-% 図\ref{fig:proposed}に提案フレームワークのシステムモデルを示す．
-% RiteVMとmrubyライブラリを含むプラットフォーム部分は，始めにターゲットデバイス上で起動されている．
-% mrubyアプリケーションのバイトコードは，ホストからターゲットデバイスへと転送される．
-% それぞれバイトコードは，RiteVMに割り当てられ，並行して起動される．
-%
-この章では，提案フレームワークのベースになっているmruby on TECSについて述べる．
-mruby on TECSで利用されているmrubyとTECSについても述べる．
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/proposed.pdf}
-%     \caption{システムモデル}
-%     \label{fig:proposed}
-% \end{figure}
-\vspace{-5mm}
-\subsection{mruby (軽量Ruby)}
-% mrubyは，ISO規格の一部に準拠したRubyの軽量実装である．
-% Ruby\cite{url:Ruby}は，オブジェクト指向型のスクリプト言語である．
-% 特徴としてシンプルな文法なため読みやすくかつ使いやすい上に，C言語よりも少ないコード量で記述できる．
-% 他にも，クラスやメソッドといったオブジェクト指向関数，例外，ガベージコレクションなどの機能により，生産性を向上させることができる．
-
-mrubyは，Rubyの高い生産性を持ち，Rubyより少ないリソースで動作するため，組込みシステムに適している．
-mrubyには，RiteVMと呼ばれるVMが実装されており，どのOS上でも同じmrubyプログラムを実行できる．
-%図\ref{fig:mruby}にRiteVMのメカニズムを示す．
-mrubyコンパイラは，mrubyプログラム(.rb)を，中間言語であるバイトコード(.mrb)にコンパイルする．
-%RiteVMが実装されていれば，どのターゲットデバイス上でも同じmrubyプログラムを実行できる．
-
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby.pdf}
-%     \caption{Mechanism of mruby/RiteVM}
-%     \label{fig:mruby}
-% \end{figure}
-\vspace{-5mm}
-\subsection{TECS\cite{par:TECS}}
+\subsection{TECS}
 %TECSは，組込みシステム向けのコンポーネントシステムである．
@@
     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
-    \vspace{-4mm}
     \caption{TECSコンポーネント図の例}
-    \vspace{-5mm}
     \label{fig:component}
@@
 \end{lstlisting}
-    \vspace{-2mm}
 \caption{シグニチャ記述}
-\vspace{-5mm}
 \label{signature}
@@
 \end{lstlisting}
-    \vspace{-2mm}
 \caption{セルタイプ記述}  
-\vspace{-4mm}
 \label{celltype}
@@
 \end{lstlisting}
-    \vspace{-2mm}
 \caption{組上げ記述}
-\vspace{-4mm}
 \label{build}
@@
 % \end{description}
-\vspace{-5mm} 
-\subsection{mruby on TECS}
-\label{sec:mruby on TECS}
-mruby on TECSは，mrubyを用いたコンポーネントベース開発が可能なフレームワークである．
-%\subsubsection{システムモデル}
-%図\ref{fig:mrubyontecs}にmruby on TECSのシステムモデルを示す．
-mrubyバイトコードはそれぞれ，コンポーネント化されたRTOS (リアルタイムOS)のタスクとして，RiteVM上で実行される．
-%TECSのコンポーネントは，モータドライバやセンサドライバのような組込みドライバをサポートしている．
-さらに，mruby-TECSブリッジによって，mrubyプログラムからC言語の関数を呼び出すことができる．
-%mruby-TECSブリッジについては，以下で詳しく説明する．
 
-本研究では，RTOSとして，TOPPERS/HRP2\cite{par:hr-tecs}を使用した．
-TOPPERS/HRP2は，$\mu$ITRON\cite{par:microITRON}をベースにしたメモリ保護機能を持つRTOSである．
-しかし，TECSは，TOPPERS/HRP2だけでなく，OSEK\cite{par:OSEK}やTOPPERS/ASP\cite{par:ASP}といったRTOSにも対応しているため，mruby on TECSはRTOSに依存しない．
+\section{設計と実装}
+\label{sec:Design and Implementation}
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mrubyontecs.pdf}
-%     \caption{System Model of existing mruby on TECS}
-%     \label{fig:mrubyontecs}
-% \end{figure}
+\section{評価実験}
+\label{sec:Evaluation}
 
-% \subsubsection{mruby-TECSブリッジ}
-% mrubyとC言語には，実行時間に大きな差がある．
-% \cite{par:mrubyonTECS}によると, mrubyプログラムは，C言語より実行時間が数百倍遅い．
-% これによって，mrubyプログラムをすべてアプリケーションに使用することは難しい．
-% mrubyを使用することにより，生産性やメンテナンス性を向上させることができる一方で，アクチュエータやセンサを制御するようなアプリケーションの重要な部分をC言語で実装することも必要である．
-%
-% 図\ref{fig:mruby_TECS_bridge}に，モータ制御に対するmruby-TECSブリッジの例を示す．
-% BridgeMotorの左部分は，mrubyプログラムであり，右部分は，TECSのコンポーネントである．
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/mruby_TECS_bridge.pdf}
-%     \caption{mruby-TECS Bridge}
-%     \label{fig:mruby_TECS_bridge}
-% \end{figure}
-%
-% mruby-TECSブリッジは，mrubyプログラムからの呼び出しを受け取るためのセルタイプと，C関数を呼び出すためのmrubyクラスを生成する．
-% 生成されたmruby-TECSブリッジのコードがmrubyのクラスとメソッドを登録する．
-% これによって，mrubyプログラムからあるメソッドが呼ばれると，mruby-TECSブリッジがTECSコンポーネントで定義されたC関数を呼び出す．
-%
-\vspace{-2mm}
-\section{設計と実装}
-\vspace{-2mm}
-\label{sec:Design and Implementation}
-図\ref{fig:system_model}に提案フレームワークのシステムモデルを示す．
-ホストから転送されたmrubyアプリケーションのバイトコードは，それぞれのRiteVMに実装されたローダで受信され，同期処理され実行される．
-RiteVMスケジューラはタスクを周期的に切り替えるため，mrubyアプリケーションは並行動作できる．
-mrubyアプリケーションの起動はイベントフラグを用いた同期機構により同期される．　
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/system_model.pdf}
-    \vspace{-2mm}
-    \caption{提案フレームワークのシステムモデル}
-\vspace{-3mm}
-    \label{fig:system_model}
-\end{figure}
-\vspace{-3mm}
-\subsection{Bluetoothを用いたmrubyバイトコードローダ}
-\label{sec:mruby bytecode loader using Bluetooth}
-この章では，Bluetoothを用いたmrubyバイトコードローダについて述べる．
-既存フレームワークでは，mrubyバイトコードをプラットフォームに組み込んでいるため，mrubyプログラムを修正する度にプラットフォーム部分をもう一度コンパイル・リンクし，SDカードやROMに再度書き込み，OSを再起動する必要がある．
-%このような作業を繰り返すことで，作業効率は悪くなる．
-提案フレームワークでは，一度だけSDカードやROMに書き込むため，作業効率を向上できる．
+\section{関連研究}
+\label{sec:Related Work}
 
-mrubyプログラムは，アプリケーション部分とライブラリ部分に分けられる．
-%mrubyアプリケーションは，開発者が主にプログラムするメインのコードであり，mrubyライブラリには，motorクラスやsensorクラスといったRubyクラスのようにアプリケーションで利用される関数群が定義されている．
-アプリケーションとライブラリをまとめたバイトコードを転送・実行することもできるが，提案フレームワークでは，ライブラリ部分はプラットフォームに組み込み，アプリケーション部分のみを転送する．
-この設計により，転送するバイトコードのサイズや処理時間の無駄を省ける．
-さらに，各RiteVMでライブラリを共有することや，固有のライブラリを持つことも可能になる．
-
-%提案フレームワークでは，mrubyバイトコードの連続ローディングにも対応している．
-
-\subsubsection{ローダを実装したRiteVMのコンポーネント}
-%ローダを実装したRiteVMはTECSのコンポーネントとして提供されている．
-ローダは，mruby on TECSで提供されているRiteVMコンポーネント\cite{par:mrubyonTECS}を拡張して実装した．
-このコンポーネントでは，転送されたバイトコードの受信に加え，RiteVMのコンフィグレーションが行われる．
-
-図\ref{fig:component_bluetooth}に，MrubyTask1とMrubyBluetooth1のコンポーネントの例を示す．
-MrubyTask1は，コンポーネント化されたRTOS (TOPPERS/HRP2)のタスクである．
-MrubyBluetooth1は，ローダを実装したRiteVMコンポーネントであり，転送されるバイトコードを受信する．
-バイナリ転送プロトコルは，汎用性が良く，パフォーマンスが高いため，ZMODEM\cite{par:ZMODEM}を適用した．
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_bluetooth.pdf}
-    \vspace{-2mm}
-    \caption{ローダを実装したRiteVMのコンポーネント図}
-\vspace{-5mm}
-    \label{fig:component_bluetooth}
-\end{figure}
-
-図\ref{fig:control_flow}にローダを実装したRiteVMがmrubyプログラムを実行するまでのフローチャート，図\ref{maincode_mrubybluetooth}に処理のソースコードを示す．
-
-はじめに，mrubyで使われる状態と変数のセットである{\it mrb\_state}と{\it mrbc\_context}のポインタを初期化する(図\ref{fig:control_flow}：A，図\ref{maincode_mrubybluetooth}：2-5行目)．
-%{\it mrb\_state}は，mrubyで使われる状態と変数のセットである．
-
-次に，mrubyライブラリのバイトコードを読み込む(図\ref{fig:control_flow}：B，図\ref{maincode_mrubybluetooth}：8行目)．
-図\ref{celltype_mrubybluetooth}に示す通り，tMrubyBluetoothのセルは属性を持っている．
-{\it mrubyFile}はmrubyライブラリのファイルを示しており，{\it [omit]}はTECSジェネレータによってのみ使われるため，この属性はメモリを消費しない．
-{\it irep}は，mrubyライブラリのバイトコードが格納されている配列へのポインタである．
-つまり，mrubyライブラリは始めのコンパイル時にコンポーネントの属性として，配列に保存される．
-
-次に，転送されてきたmrubyアプリケーションのバイトコードを読み込む(図\ref{fig:control_flow}：C，図\ref{maincode_mrubybluetooth}：10，12行目)．
-mrubyアプリケーションのバイトコードは，変数uint8\_t型の配列{\it irepApp}に格納される．
-２つのバイトコードは，それぞれ別の配列に保存されており，別々に読み込まれる．
-
-最後に，RiteVMはmrubyアプリケーションであるタスクを実行する(図\ref{fig:control_flow}：D，図\ref{maincode_mrubybluetooth}：12行目)．
-mrubyアプリケーションのプログラムが修正された場合は，そのバイトコードのみを再転送する．
-%以上の処理のソースコードを図\ref{maincode_mrubybluetooth}に示す．
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/control_flow.pdf}
-    \vspace{-2mm}
-    \caption{ローダの処理フローチャート}
-\vspace{-5mm}
-    \label{fig:control_flow}
-\end{figure}
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-celltype tMrubyBluetooth{
-  entry sTaskBody eMrubyBody;
-  attr{
-    [omit]char_t *mrubyFile;
-    char_t *irep = C_EXP("&$cell_global$_irep");
-    uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
-  };
-  var{ [size_is(irepAppSize)] uint8_t *irepApp; };
-};
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{ローダを実装したRiteVMのセルタイプ記述}
-\vspace{-4mm}
-\label{celltype_mrubybluetooth}
-\end{figure}
-\begin{figure}[t]
-\centering
-\begin{lstlisting}
-void eMrubyBody_main( CELLIDX idx ){
-  /*Omit: Declaration variables*/
-  mrb=mrb_open(); /*New mrb_state*/
-  /*Omit: error check for mrb_state*/
-  c=mrbc_context_new( mrb ); /*New mrbc_context*/
-  /*Omit: initialization of mruby-TECS bridge*/
-  /*Load mruby library bytecode and run*/
-  mrb_load_irep_cxt( mrb, ATTR_irep, c );
-  /*Receive the bytecode via Bluetooth*/
-  bluetooth_loader( VAR_irepApp );
-  /*Load mruby application bytecode and run*/
-  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
-  mrbc_context_free( mrb, c ); /*Free mruby context*/
-  mrb_close( mrb ); /*Free interpreter instance*/
-}
-
-\end{lstlisting}
-    \vspace{-2mm}
-\caption{ローダを実装したRiteVMのメインコード}
-\vspace{-3mm}
-\label{maincode_mrubybluetooth}
-\end{figure} 
-\vspace{-5mm}
-\subsection{マルチタスク処理}
-\label{sec:Multitask}
-この章では，提案フレームワークでのマルチタスク処理の設計について述べる．
-%mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの知識を熟知している必要がある．
-
-マルチタスク処理のアプローチの一つにコルーチンがある．
-コルーチンは，協調的スレッドであり，開発者が{\it resume}や{\it yield}といった関数を呼び出すことで並行動作できるが，ノンプリエンプティブな処理で，開発者自身がタスクの切り替えを行う必要があるため，OSのサポートやマルチコアの恩恵を受けることができない．
-Rubyのコルーチンは，Fiberクラス\cite{url:co-routine}に定義されている．
-
-その他にも，$\mu$ITRONのサービスコールである{\it delay()}を使った手法がある．
-このサービスコールは，引数として与えられた時間だけ，そのタスクの起動を遅らせる．
-{\it delay()}は，固定優先度スケジューリングの場合に用いられるが，フェアスケジューリングの場合には使用することが難しい．
-
-提案フレームワークでは，フェアスケジューラであるRiteVMスケジューラを提供し，複数のVMを平等に並行動作させる．
-RiteVMスケジューラはRiteVMタスクが同じ優先度を持つ場合に利用でき，開発者がOSの関数を呼び出すことなく，マルチタスク処理が可能になる．
-その上，既存のアプリケーションプログラムの構造を変えることなく使うことができる．
-
-\subsubsection{RiteVMスケジューラ}
-RiteVMスケジューラは，周期ハンドラを利用して実装し，同優先度のタスクの実行を切り替える$\mu$ITRONのサービスコールである{\it rotateReadyQueue}を周期的に呼び出す．
-%{\it rotateReadyQueue}は，同優先度のタスクの実行を切り替える関数である．
-RiteVMスケジューラの設計を図\ref{fig:rotateReadyQueue}に示す．
-
-% 無限ループを持った同優先度の2つのタスクの場合を考える．
-% 現状のシステムでは，始めにタスクが起動すると，そのタスクが無限ループに入るため，もう片方のタスクが起動することができない．
-
-{\it rotateReadyQueue}が呼ばれると，図\ref{fig:rotateReadyQueue}に示す通り，同優先度タスクの実行順序が切り替わる．
-{\it rotateReadyQueue}の引数は，優先度である．
-
-{\it rotateReadyQueue}は，2つ以上のタスクの場合にでも利用できる．
-例えば，３つのタスクA，B，Cが順に起動する場合，{\it rotateReadyQueue}が呼ばれると，B，C，Aの順にタスクの実行順序は切り替わる．
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
-    \vspace{-2mm}
-    \caption{RiteVMスケジューラの設計}
-\vspace{-5mm}
-    \label{fig:rotateReadyQueue}
-\end{figure}
-
-\subsubsection{RiteVMスケジューラのコンポーネント}
-%図\ref{fig:cyclic_handler}にRiteVMスケジューラのコンポーネント図を示す．
-RiteVMスケジューラのコンポーネントは，CyclicHandlerとCyclicMainから構成される．
-CyclicHandlerセルは，3つの属性(attribute，cyclicTime，cyclicPhase)を持っており，$\mu$ITRONの周期ハンドラ\cite{par:microITRON}の設定を行う．
-%$\mu$ITRONの周期ハンドラは，\cite{par:microITRON}に詳しく書かれている．
-%周期ハンドラは，5つの引数(ID, attribute, cyclic time, cyclic phase, access pattern)を持っている．
-%CyclicHandlerセルは，3つの属性(attribute, cyclicTime, cyclicPhase)を持っている．
-CyclicMainセルは，周期ハンドラの処理を行うコンポーネントであり，{\it rotateReadyQueue}が実装されている．
-%図\ref{celltype_cyclic_handler}に，セルタイプtCyclicMainのセルタイプ記述を示す．
-呼び口は，カーネルの機能である{\it rotateReadyQueue}を使用するためにカーネルセルの受け口({\it tkernel.eiKernel})に接続されている．
-属性は，{\it rotateReadyQueue}の引数として使われる．
-
-%図\ref{build_cyclic_handler}に，図\ref{fig:cyclic_handler}に示されるコンポーネントの組上げ記述を示す．
-図\ref{build_cyclic_handler}に，RiteVMスケジューラの組上げ記述を示す．
-%CyclicHandlerセル部分では，cyclicTimeやcyclicPhaseといった属性で与えられる周期ハンドラの設定を行う．
-attributeには，OSが起動すると実行状態になる属性である{\it TA\_STA}，周期時間には，1msが与えられる．
-CyclicMainセル部分は，属性priorityを持っており，mrubyタスクの優先度であるRITEVM\_PRIORITYが与えられる．
-
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/cyclic_handler.pdf}
-%     \caption{Component Diagram of Cyclic Handler}
-%     \label{fig:cyclic_handler}
-% \end{figure}
-% \begin{figure}[t]
-%     \centering
-%     \begin{lstlisting}
-% celltype tCyclicHandler {
-%     [inline] entry sCyclic eCyclic;
-%     call  siHandlerBody  ciBody;
-%     attr {
-%     	[omit] ATR    attribute = C_EXP("TA_NULL");
-%     	[omit] RELTIM cyclicTime;
-%     	[omit] RELTIM cyclicPhase = 0;
-%     };
-% };
-% celltype tCyclicMain{
-%     require tKernel.eiKernel;
-%     entry siHandlerBody eiBody;
-%     attr {
-%         PRI priority;
-%     };
-% };
-%     \end{lstlisting}
-%     \caption{Celltype Description of Cyclic Handler}
-%     \label{celltype_cyclic_handler}
-% \end{figure}
-\begin{figure}[t]
-    \centering
-    \begin{lstlisting}
-cell tCyclicHandler CyclicHandler{
-    ciBody = CyclicMain.eiBody;
-    attribute = C_EXP("TA_STA");
-    cyclicTime = 1;
-    cyclicPhase = 1;
-};
-cell tCyclicMain CyclicMain{
-    priority = C_EXP("RITEVM_PRIORITY");
-};
-   \end{lstlisting}
-    \vspace{-2mm}
-    \caption{RiteVMスケジューラの組上げ記述}
-\vspace{-3mm}
-    \label{build_cyclic_handler}
-\end{figure}
-
-\subsubsection{mrubyアプリケーションの同期機構}
-複数のmrubyアプリケーションの起動を同期させるために，イベントフラグを用いて同期処理を行った．
-%タスクはそれぞれ0x01(01)，0x02(10)のパターンをセットし，待ちパターン0x3(11)でAND待ちする．
-%この機構は，2つ以上のタスクの場合でも適用できる．
-RiteVMが4つの場合，各VMはそれぞれ，イベントフラグに0x01(0001)，0x02(0010)，0x04(0100)，0x08(1000)のパターンをセットし，待ち状態へと遷移する(図\ref{fig:Eventflag} (A))．
-イベントフラグが待ちパターン0x0f(1111)になると，各VMは実行可能状態になり，アプリケーションを同時に実行する．
-
-さらに，バイトコードの連続ローディングに対応するため，アプリケーションの終了も同期する．
-終了も同期することで，すぐに終了するアプリケーションのRiteVMが次のロード待機状態に入るのを防げ，すべてのRiteVMは同時に次のロード待機状態になる．
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/Eventflag.pdf}
-    \vspace{-2mm}
-    \caption{TECSを用いたイベントフラグの設計 {\scriptsize *差分のみ示す}}
-\vspace{-3mm}
-    \label{fig:Eventflag}
-\end{figure}
-\vspace{-5mm}
-\subsection{コンポーネントベース開発の利点}
-この章では，コンポーネントベース開発の利点を使った設計について述べる．
-提案フレームワークは，RiteVMやRiteVMスケジューラ，イベントフラグをコンポーネントとして提供しているため，開発者はそれらのコンポーネントを容易に付け外し，再利用できる．
-例えば，RiteVMスケジューラの機能を外したい場合，図\ref{build_cyclic_handler}に示されるcdlファイルを{\it //import($<$tRiteVMScheduler.cdl$>$);}とコメントアウトするだけで良いため，開発者はカーネルの設定ファイルを修正する手間を省くことができる．
-
-それに加えて，コンポーネントベース開発ではコード量を減らすことができる．
-図\ref{fig:Eventflag} (B)に示す通り，イベントフラグのセットパターンと待ちパターンを属性として定義する．
-{\it cEventflag\_set(ATTR\_setPattern)}のように，if文なしでプログラムを記述でき，RiteVMの数に関わらず同じcファイルを使用できる．
-さらに，TECSのオプション{\it [optional]}によって，呼び口が結合した場合のみ処理を行うため，イベントフラグを利用しない場合でも同じCファイルを利用できる．
-
-\vspace{-2mm}
-\section{評価実験}
-\vspace{-2mm}
-\label{sec:Evaluation}
-この章では，評価実験の結果と考察について述べる．
-提案フレームワークの利点を分析するため，
-%プラットフォームの起動時間
-転送するバイトコードのサイズと処理時間およびコンパイル時間，シングルタスク，コルーチン，マルチタスクの実行時間，周期時間によるオーバヘッド，コンポーネントベース開発を利用したコード行数の評価を行った．
-% \begin{itemize}
-% %    \item プラットフォームの起動時間
-%     \item 転送されるmrubyバイトコードのサイズと処理時間およびコンパイル時間
-%     \item シングルタスク，コルーチン，マルチタスクの実行時間
-%     \item 周期時間によるオーバヘッド
-% %   \item mrubyアプリケーションの同期
-%     \item コンポーネントベース開発を利用したコード行数
-% \end{itemize}
-
-% These evaluations are performed in order to indicate that an mruby bytecode loader improves the software development efficiency, and that the proposed multitask processing effectively executes compared with singletasking or co-routine, and also the overhead of the cyclic period.
-本評価実験は，ターゲットデバイスとして，LEGO MINDSTORMS EV3 (300MHz ARM9-based Sitara AM1808 system-on-a-chip)を使用した．
-コンパイラは，gcc 4.9.3 -O2 および mrubyのバージョンは1.2.0である．
-
-表\ref{tab:size_and_time}に，mrubyアプリケーションのバイトコードと，ライブラリとアプリケーションを合わせたバイトコードのサイズ，ロード処理時間，コンパイル時間の比較を示す\footnote{0バイトのバイトコードを処理した場合にかかるロード処理時間のオーバヘッドは，50.933 msである．
-同様に0バイトのバイトコードをコンパイルした場合にかかるコンパイルのオーバヘッドは，46.9 msである．}．
-mrubyアプリケーションのみのバイトコードの方が，ライブラリを含めた場合よりも，すべての点で優れている．
-上記の結果は，RiteVM一つの評価であるため，RiteVMの数が増えるにつれ，この差は広がっていく．
-さらに，この設計ではSDカードやROMを上書きする手間や，OSを再起動する手間も省くことができる．
-以上より，提案フレームワークは，既存フレームワークより作業効率を向上できる．
-
-% The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
-% The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
-% Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
-% The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
-% The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
-% %In the proposed framework, developers send only mruby application and prepare mruby library in advance.
-% %Therefore, the design can send the bytecode faster.
-% In addition, the design can save the time to connect a storage/ROM device to restart an OS.
-% These advantages lead improvement of the software development efficiency.
-
-\begin{table}[t]
-    \centering
-    \caption{バイトコードのサイズと処理時間およびコンパイル時間}
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||c|c|c}
-                            & App\&Lib     & App        &   App\&Lib/App  \\ \hline
-          Bytecode Size     & 14,044 bytes & 199 bytes  &   $\times$70.6          \\ %\hline
-          Loading Time & 305.081 msec & 7.774 msec &   $\times$39.2          \\
-          Compile Time      & 8.7 msec     & 0.3 msec   &   $\times$29.0          \\
-    \end{tabular}
-    }
-    \vspace{-5mm}
-    \label{tab:size_and_time}
-\end{table}
-
-次に，図\ref{fig:comparison_s_c_m}に，シングルタスク，コルーチン，マルチタスクの実行時間を示す．
-評価用アプリケーションとして，100,000回ループするプログラム(マルチタスクおよびコルーチンは，2つのタスクでそれぞれ50,000回ループ)を用いた．
-実行時間の観点では，提案手法のマルチタスクは，コルーチンより有効である．
-シングルタスクと比べても，RiteVMスケジューラのオーバヘッドは約5\%と実用的に問題ない．
-タスクの切り替えそのものにかかる時間は，約3$\mu$sある．
-RiteVMスケジューラは，周期的に割り込み，タスクの切り替えの処理を行うため，これがオーバヘッドとなっている．
-
-% The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
-% The 100,000 times loop program is used as mruby application for evaluation of execution time.
-% In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
-% In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
-% While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
-% This result shows the proposed design is superior to co-routine in terms of execution time.
-% The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
-% Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
-% %The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
-% %Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
-% The scheduler interrupts and switches tasks, which causes this overhead.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_s_c_m.pdf}
-    \vspace{-2mm}
-    \caption{シングルタスク，コルーチン，マルチタスクの実行時間}
-\vspace{-3mm}
-    \label{fig:comparison_s_c_m}
-\end{figure}
-
-図\ref{fig:comparison_msec}は，RiteVMスケジューラの周期時間ごとの実行時間を示している．
-この評価では，TOPPERS/HRP2の仕様により周期時間の下限を1msとした．
-一方で，周期時間が大きいとアプリケーションに影響を与える可能性があるため，上限を8msとした．
-周期時間が大きいほど，タスクの切り替え回数は減少するため，実行時間は小さくなることが分かる．
-%1msecと10msecでは，約3\%減少している．
-1msと8msでは，約1\%しか減少していない．
-小さい周期時間でもオーバヘッドは大きくないため，効率的にタスクを並行動作できる．
-%しかし，周期時間によるオーバヘッドは，誤差に埋もれるほど小さい．
-
-% Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
-% A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
-% More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
-% Each execution time of cyclic period is the same as the others.
-% That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
-% This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
-% The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/comparison_msec.pdf}
-    \vspace{-2mm}
-    \caption{周期時間によるオーバヘッド}
-\vspace{-3mm}
-    \label{fig:comparison_msec}
-\end{figure}
-
-表\ref{tab:codesize}に，2つのcファイルとcdlファイルのコード行数と変更行数の比較を示す．
-(A)と(B)はそれぞれ，図\ref{fig:Eventflag}の上部と下部を指している．
-(A)のcファイルは，RiteVMの数に比例して増えているのに対して，(B)のcファイルは同じである上に，RiteVMの数に関わらず，修正することなく同一のファイルを使用できる．
-cdlファイルに差はない．
-コンポーネントベース開発を上手く活用することで，コードの行数が減ることを示した．%高い生産性やメンテナンス性につながる．
-その上，RiteVMの数に限らず同じcファイルを利用できる．%ため，開発者がファイルを修正する手間を省くこともできる．
-
-% To indicate the superior of component-based development, the comparison of code lines between two c files is shown in Table \ref{tab:codesize}.
-% (A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
-% In terms of c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
-% (B) is not modified, and can be utilized regardless of the number of RiteVMs.
-% Moreover, lines of two cdl files are equal.
-% The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.
-
-\begin{table}[t]
-    \centering
-    \caption{コンポーネントベース開発を利用したコード行数} 
-    \begin{tabular}{c||cc|c}
-                & (A)       & (B)     & Diff  \\ \hline
-        c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
-        c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
-        cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
-        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
-    \end{tabular}
-    \vspace{-2mm}
-    \label{tab:codesize}
-\end{table}
-
-\vspace{-1mm}
-\section{関連研究}
-\vspace{-2mm}
-\label{sec:Related Work}
-% \begin{table*}[t]
-%     \centering
-%     \caption{関連研究}
-%     {\tabcolsep=0.1cm
-%     \begin{tabular}{c||c|ccccccc}
-%         & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
-%         python-on-a-chip\cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
-%         Owl system\cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
-%         eLua\cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
-%         mruby\cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
-%         mruby on TECS\cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
-%         Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
-%     \end{tabular}
-% }
-%     \label{tab:comparison}
-% \end{table*}
-現在，スクリプト言語を適用した組込みシステム向けのランタイムシステムとして，次のものが開発されている．
-python-on-a-chip\cite{url:python-on-a-chip}，Owl system\cite{par:owl}，eLua\cite{url:eLua}，mruby\cite{par:mruby}，mruby on TECS\cite{par:mrubyonTECS}．
-
-python-on-a-chip (p14p)は，PyMyteと呼ばれるPythonVMを使用するPythonランタイムシステムである．
-PyMyteは，低リソースでPythonプログラムを実行する．
-p14pでは，複数のグリーンスレッドを並行動作できる．
-
-Owl systemは，組込みシステム向けのPythonランタイムシステムであり，ARM Cortex-M3 マイコン上で動く．
-Owlツールチェーンは，Pythonコードから，マイコン上で直接起動するメモリイメージを生成する．
-Owl systemは，p14pのインタプリタを使用している．
-
-eLuaは，Luaの組込みシステム向け実装である．
-%Luaは，最も人気のある組込み向けスクリプト言語のひとつである\cite{url:Lua}, \cite{par:Lua}.
-Luaは，コルーチンをサポートしているが，ノンプリエンプティブであるため，マルチタスク処理を行うのは難しい．
-
-%mruby(軽量Ruby)は，組込みシステムに適したスクリプト言語である．
-%mrubyプログラムは，RiteVM上で実行される．
-mrubyは，コルーチンをサポートしているが，RTOSのマルチタスクには対応していない．
-
-%mruby on TECSは，mrubyを使ったコンポーネントベース開発が可能なフレームワークである．
-%mruby on TECSは，mrubyより実行速度が100倍速い．
-mruby on TECSは，マルチタスクに対応しているが，開発者がRTOSの機能を呼び出す必要がある．
-
-%表\ref{tab:comparison}に，提案フレームワークと既存研究の比較を示す．
-%提案フレームワークでは，ローダに加えて，VMスケジューラとアプリケーションの同期機構を提供する．
-
-\vspace{-1mm}
 \section{おわりに}
-\vspace{-2mm}
 \label{sec:Conclusion}
-本研究では，mruby on TECSの拡張として，Bluetoothを用いたmrubyバイトコードローダとRiteVMスケジューラを提案した．
-ローダによって，開発者はSDカードやROMを上書きする手間や，OSを再起動する手間が省けるため，ソフトウェア開発の作業効率を向上できる．
-ローダは，Bluetoothだけでなく，有線のシリアル通信にも対応しているため，様々な組込みシステムに適用できる．
-RiteVMスケジューラは複数のmrubyアプリケーションを効率良く並行実行し，同期機構によりタスク起動を同期する．
-実験評価では，ローダによる作業効率の向上やマルチタスク設計の有用性，コンポーネントベース開発の利点を示した．
-
-さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる．
-%RiteVMスケジューラも容易に付け外しできるため，開発者は，フェアスケジューリングか固定優先度スケジューリングかを選択することもできる．
-%コンポーネントベース開発は，生産性を向上させ，システムの複雑さを減らすことができる．
-
-ソフトウェア開発をさらに効率良く行うために，%プラグインを使用したRiteVMやmruby-TECSブリッジのcdlファイルの自動生成や，
-VM間の通信機能や，コマンドライン上でのバイトコード転送機能を提供することが，今後の課題である．
 
 %%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-2mm}
 \bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}
-\bibliography{ETNET}
+\bibliography{ref}
 

### 2017-06-23 kansai/set_env.sh

@@ -1,0 +1,1 @@
+export PATH=$PWD/ipsj_v2/UTF8:$PATH

### 2017-06-23 kansai/set_env.sh
Remove set_env.sh

@@ -1,1 +1,0 @@
-export PATH=$PWD/ipsj_v2/UTF8:$PATH

### 2017-06-23 kansai/paper.tex
Update paper.tex

@@
     numbersep=1zw,%
-    lineskip=-1.5ex%
+    lineskip=-0.5ex%
 }
@@
 \section{はじめに}
+近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている．
+組込みシステムには，厳しいリソース制約があり，効率的なメモリ確保が要求される．
+さらに，リアルタイム性を要求される組込みシステムでは，メモリ確保の実行時間も重要である．
+
+このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSFアロケータが提案されている．
+TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常にオーダー1で実行するため最悪実行時間が存在しない．
+TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで利用されている．
+
+しかし，現状では，複数のスレッドが並行動作すると，メモリの衝突が起きる場合がある．
+本研究では，組込み向けコンポーネントシステムTECSを用いてTLSFアロケータをコンポーネント化し，スレッドセーフなアロケータを実現した．
+さらに，メモリサイズの変更等が柔軟になる．
 
@@
 \subsection{TLSF}
+\label{sec:TLSF}
+TLSF (Two-Level Segregate Fit)アロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
+TLSF
 
 \subsection{TECS}
-%TECSは，組込みシステム向けのコンポーネントシステムである．
-TECSによるコンポーネントベース開発は，ソフトウェアの再利用性を上げるため，生産性を向上できる．
-%システム全体の構造を可視化するため，システムの難しさを減らすことができる．
-%ソフトウェアの共通部分はコンポーネントとして扱われるため，開発の重複を減らし，生産性を向上させる．
+TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクトで開発されている組込みシステム向けのコンポーネントシステムである．
+コンポーネントベース開発は，ソフトウェアの部品(コンポーネント)を組み合わせて開発を行う手法である．
+ソフトウェアの再利用性が改善する上に，コンポーネント図によりシステム全体の構造を可視化するため，ソフトウェア開発の生産性を向上できる．
+さらに，システムの拡張や仕様変更にも柔軟に対応することができる．
 
@@
 \subsubsection{コンポーネントモデル}
-図\ref{fig:component}にコンポーネント図の例を示す．
+図\ref{fig:component}にTECSコンポーネント図の例を示す．
 TECSでは，インスタンス化されたコンポーネントはセル({\it cell})と呼ばれ，受け口({\it entry})，呼び口({\it call})，属性，変数を持つ．
@@
 
-% \begin{description}
-%     \item[{\bf シグニチャ記述}]\mbox{}\\
+\begin{description}
+    \item[{\bf シグニチャ記述}]\mbox{}\\
         シグニチャ記述は，セルのインタフェースを定義する．
@@
 
-    % \item[{\bf セルタイプ記述}]\mbox{}\\
+    \item[{\bf セルタイプ記述}]\mbox{}\\
         セルタイプ記述は，受け口，呼び口，属性，変数を用いてセルタイプを定義する．
@@
 \begin{lstlisting}
-celltype tCaller{
+celltype tCaller {
     call sMotor cMotor;
 };
-celltype tMotor{
+celltype tMotor {
     entry sMotor eMotor;
@@
 
-    % \item[{\bf 組上げ記述}]\mbox{}\\
+    \item[{\bf 組上げ記述}]\mbox{}\\
         組上げ記述は，セルをインスタンス化し，セルを結合する．
@@
         呼び口名，``="，結合先の受け口名の順に記述し，セルを結合する．
-        図\ref{build}では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが接続されている．
+        図\ref{build}では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが結合されている．
 
@@
 \begin{lstlisting}
-cell tMotor Motor{
+cell tMotor Motor {
 };
-cell tCaller Caller{
+cell tCaller Caller {
     cMotor = Motor.eMotor;
@@
 
-% \end{description}
+\end{description}
 

### 2017-06-27 kansai/paper.tex
Update paper.tex

@@
 
-\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
-\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
-\def\|{\verb|}
-
-\setcounter{巻数}{53}%vol53=2012
-\setcounter{号数}{10}
-\setcounter{page}{1}
-
 \begin{document}
 
-\title{組込みシステムに適した動的メモリアロケータのコンポーネント化}
+\title{組込みシステムに適した\\動的メモリアロケータのコンポーネント化}
 
@@
 \affiliate{OU}{大阪大学基礎工学研究科\\
-School of Engineering Science, Osaka University}
+Graduate School of Engineering Science, Osaka University}
 
@@
 近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている．
-組込みシステムには，厳しいリソース制約があり，効率的なメモリ確保が要求される．
-さらに，リアルタイム性を要求される組込みシステムでは，メモリ確保の実行時間も重要である．
+多くの組込みシステムは，厳しいリソース制約を持っており，効率的なメモリ確保が要求される．
+さらに，リアルタイム性を要求される組込みシステムでは，メモリ確保の実行時間も重要となる．
 
-このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSFアロケータが提案されている．
+このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている．
 TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常にオーダー1で実行するため最悪実行時間が存在しない．
@@
 しかし，現状では，複数のスレッドが並行動作すると，メモリの衝突が起きる場合がある．
-本研究では，組込み向けコンポーネントシステムTECSを用いてTLSFアロケータをコンポーネント化し，スレッドセーフなアロケータを実現した．
+本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を用いてTLSFアロケータをコンポーネント化し，スレッドセーフなアロケータを実現した．
 さらに，メモリサイズの変更等が柔軟になる．
+
+% 本論文における貢献は次の通りである．
+% \begin{enumerate}
+%
+% \end{enumerate}
 
@@
 \label{sec:Design and Implementation}
+本章では，TLSFアロケータのコンポーネント設計について述べる．
+% 図\ref{fig:TLSFComponent}に，コンポーネント化されたTLSFアロケータのコンポーネント図を示す．
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+[deviate]
+signature sMalloc {
+    int    initializeMemoryPool(void);
+    void   *calloc( [in]size_t nelem, [in]size_t elem_size );
+    void   *malloc( [in]size_t size );
+    void   *realloc( [in]const void *ptr, [in]size_t new_size );
+    void   free( [in]const void *ptr );
+};
+\end{lstlisting}
+\caption{メモリ管理用のシグニチャ記述}  
+\label{src:TLSFSignature}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+celltype tTLSFMalloc {
+    [inline]
+        entry  sMalloc  eMalloc;
+    attr {
+        /* memory pool size in bytes */
+        size_t  memoryPoolSize;
+    };
+    var {
+        [size_is( memoryPoolSize / 8 )]
+            uint64_t   *pool;
+    };
+};
+\end{lstlisting}
+\caption{TLSFアロケータのセルタイプ記述}  
+\label{src:TLSFCelltype}
+\end{figure}
 

### 2017-06-29 kansai/paper.tex
Update paper.tex

@@
 しかし，現状では，複数のスレッドが並行動作すると，メモリの衝突が起きる場合がある．
-本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を用いてTLSFアロケータをコンポーネント化し，スレッドセーフなアロケータを実現した．
-さらに，メモリサイズの変更等が柔軟になる．
+本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を用いてTLSFアロケータをコンポーネント化する．
+コンポーネント化されたTLSFアロケータでは，各コンポーネントで独自のヒープ領域を保持するため，スレッドセーフなアロケータを実現できる．
+さらに，コンポーネントとして特性を利用できるため，メモリサイズの変更等が柔軟になる．
+本論文では，提案するTLSFメモリアロケータコンポーネントのユースケースとして，利用例を述べる．
 
-% 本論文における貢献は次の通りである．
+% 本論文における貢献は以下の通りである．
 % \begin{enumerate}
@@
 
-\section{基礎技術}
-\label{sec:Background}
+本論文の構成は次の通りである．
+まず\ref{sec:ComponentBasedDevelopment}章で，コンポーネントベース開発と提案するアロケータのベースとして用いるTECSについて述べる．
+\ref{sec:Design and Implementation}章では，TLSFアロケータのコンポーネント設計と実装について述べる．
+\ref{sec:Use Case}章では，ユースケースとして，利用例を述べる．
+\ref{sec:Related Work}章では，関連研究を述べ，最後に\ref{sec:Conclusion}章で本論文をまとめる．
 
-\subsection{TLSF}
-\label{sec:TLSF}
-TLSF (Two-Level Segregate Fit)アロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
-TLSF
+\section{コンポーネントベース開発}
+\label{sec:ComponentBasedDevelopment}
 
-\subsection{TECS}
-TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクトで開発されている組込みシステム向けのコンポーネントシステムである．
+ソフトウェア開発の生産性を向上させる手法のひとつにコンポーネントベース開発がある．
 コンポーネントベース開発は，ソフトウェアの部品(コンポーネント)を組み合わせて開発を行う手法である．
@@
 
-% TECSでのコンポーネントの生成と結合は静的に行われるため，最適化され，実行時間や消費メモリのオーバヘッドは少ない．
+\subsection{TECS}
+TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクトで開発されている組込みシステム向けのコンポーネント技術である．
+TECSでは，コンポーネントの生成と結合はすべて静的に行われ，最適化されるため，コンポーネント化における実行時間や消費メモリのオーバヘッドを抑えることができる．
 % 他の特徴として，C言語での実装，ソースレベルでの移植性，コンポーネントの粒度が小さいことなどがある．
@@
     entry sMotor eMotor;
-    attr{ int32_t attr = 100; };
-    var{ int32_t var; };
+    attr {
+        int32_t attr = 100;
+    };
+    var {
+        int32_t var;
+    };
 };
@@
 \label{sec:Design and Implementation}
+
 本章では，TLSFアロケータのコンポーネント設計について述べる．
 % 図\ref{fig:TLSFComponent}に，コンポーネント化されたTLSFアロケータのコンポーネント図を示す．
+
+\subsection{TLSF}
+\label{sec:TLSF}
+TLSF (Two-Level Segregate Fit)アロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
 

### 2017-07-03 kansai/paper.tex
Update paper.tex

@@
     \centering
-    \includegraphics[width=8cm,clip]{../EMSOFT2016/figure/component_diagram.pdf}
+    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
     \caption{TECSコンポーネント図の例}
@@
 \section{設計と実装}
-\label{sec:Design and Implementation}
+\label{sec:DesignImplementation}
 
@@
 
-\section{評価実験}
-\label{sec:Evaluation}
+\section{ユースケース}
+\label{sec:UseCase}
+
+本章では，提案するコンポーネント化されたTLSFメモリアロケータのユースケースとして，利用されるプラットフォームとその効果について述べる．
+
+\subsection{mruby on TECS}
+\label{sec:mrubyonTECS}
+
+mruby on TECS は，mruby (軽量Ruby)を用いたコンポーネントベース開発が可能な組込みソフトウェア開発フレームワークである．
+スクリプト言語を用いることで，組込みソフトウェア開発の生産性向上を目指している．
+一般に，スクリプト言語は実行速度が遅いため，組込みソフトウェアに向いていないが，mruby on TECSでは，mruby-TECSブリッジの機能によって，mruby プログラムからC 言語の関数を呼び出すことができるため，C言語と変わらない速度でプログラムを実行することができる．
+mrubyプログラムは，mrubyコンパイラによってバイトコードに変換され，RiteVMと呼ばれるVM上で実行される．
+本フレームワークでは，RiteVMやRTOS (Real-Time OS)の機能もすべてTECSによってコンポーネント化されている．
+
+% 本研究では，RTOS として，TOPPERS/HRP2 [6] を使用した．
+% TOPPERS/HRP2 は，$\mu$ITRONをベースにしたメモリ保護機能を持つRTOSである．
+% しかし，TECSはTOPPERS/HRP2 だけでなく，OSEKやTOPPERS/ASPといったRTOS にも対応しているため，mruby on TECS はRTOS に依存しない．
+
+\subsubsection{マルチVM対応}
+
+本フレームワークでは，VMが行うメモリ管理にTLSFメモリアロケータを採用している．
+しかし，既存のTLSFメモリアロケータではスレッドセーフではないため，複数のスレッドからメモリの確保や解放を行うと，メモリ衝突が起きてしまう．
+VMは高い頻度でメモリの確保と解放を繰り返すため，マルチVMとして複数のVMを起動すると，すぐに衝突を起こしてしまう．
+
+図\ref{fig:TLSF-mruby}のように，VMにTLSFメモリアロケータコンポーネントを結合し，各VMで独自のヒープ領域を持つように設計する．
+各VMがそれぞれメモリプールを保持しているため，複数のVMがメモリ衝突を起こすことなく，実行できる．
+さらに，RiteVMはインクリメンタルGC (Garbage Collection)を行うが，独自のメモリプールを保持しているため，GCを始めたVMがGCの実行によって，他のVMの実行を妨げることもない．
+
+\subsection{TINET+TECS}
+\label{sec:TINET+TECS}
+
+TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)をTECSによってコンポーネント化したTCP/IPプロトコルスタックである．
 
 \section{関連研究}
-\label{sec:Related Work}
+\label{sec:RelatedWork}
 

### 2017-07-04 kansai/paper.tex
Update paper.tex

@@
 \end{lstlisting}
-\caption{TLSFアロケータのセルタイプ記述}  
+\caption{TLSFメモリアロケータのセルタイプ記述}  
 \label{src:TLSFCelltype}
@@
 TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)をTECSによってコンポーネント化したTCP/IPプロトコルスタックである．
+複雑で大規模なソースコードやマクロで構成されているTINETをTECSによってコンポーネント化することで，実行時間やメモリ消費量のオーバヘッドを抑えつつ，TCP/UDPやIPv4/IPv6といった通信プロトコルの変更等のコンフィグラビリティが向上している．
+
+\subsubsection{データ送受信用のメモリ管理}
 

### 2017-07-05 kansai/paper.tex
Update paper.tex

@@
 このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている．
-TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常にオーダー1で実行するため最悪実行時間が存在しない．
+TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため最悪実行時間が存在しない．
 TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで利用されている．
@@
 \label{sec:TLSF}
-TLSF (Two-Level Segregate Fit)アロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
+TLSF (Two-Level Segregate Fit)メモリアロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
+メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常にオーダー1で実行するため最悪実行時間が存在しない．
+TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで利用されている．
 
@@
 
+データの送受信処理を行う際，各プロトコルでメモリ領域の確保と解放が行われる．
+TINET+TECSやTINETは，プロトコル間のデータコピー回数を最少とするなど，組込みシステムの厳しいメモリ制約に対応している．
+しかし，現状ではTOPPERS/ASPでサポートされている固定長メモリアロケータを利用している．
+
+TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できる．
+したがって，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
+TINET+TECSは，TECSによってコンポーネント化されているため，提案するTLSFメモリアロケータコンポーネントを拡張することが容易になっている．
+
 \section{関連研究}

### 2017-07-10 kansai/paper.tex
Update

@@
 
-% 本論文における貢献は以下の通りである．
-% \begin{enumerate}
-%
-% \end{enumerate}
+本論文における貢献は以下の通りである．
+\begin{itemize}
+    \item 複数のスレッドが並行動作しても排他制御なしでスレッドセーフに動作する
+    \item 各スレッドで独自のヒープ領域を容易に設定できる
+    \item コンポーネント化により再利用性が向上するため，様々なシステムに拡張できる
+    \item コンポーネント図により可視化できるため，機能役割の理解が容易になる
+\end{itemize}
 
@@
 TLSF (Two-Level Segregate Fit)メモリアロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
-メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常にオーダー1で実行するため最悪実行時間が存在しない．
-TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで利用されている．
+TLSFメモリアロケータは以下のような特徴がある．
+\begin{description}
+    \item[{\bf リアルタイム性}]\mbox{}\\
+        メモリの確保や解放にかかる最悪実行時間はデータサイズに依存しないため，常に$O(1)$で実行される．
+        応答時間を見積もることができるため，リアルタイムシステムに適したメモリアロケータである．
+    \item[{高速}]\mbox{}\\
+        最悪実行時間が常に見積もれることに加え，TLSFは高速に実行される．
+        x86アーキテクチャで最大168のプロセッサ命令を実行することができる．
+    \item[{効率的なメモリ消費}]\mbox{}\\
+        TLSFでは，メモリの断片化(フラグメンテーション)を抑えることで，メモリ効率化を実現している．
+        様々なテストで，平均フラグメンテーション15％未満，最大フラグメンテーション25％未満を得ている．
+\end{description}
+
+\subsubsection{TLSFアルゴリズム}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
+    \caption{TLSFアルゴリズム}
+    \label{fig:TLSF}
+\end{figure}
+
+\subsubsection{コンポーネント設計}
 

### 2017-07-12 kansai/paper.tex
Update paper.tex

@@
 \input{../EMSOFT2016/dummy/dummy.tex}
-\documentclass[submit]{ipsj_v2/UTF8/ipsj}
+\documentclass[submit,techrep]{ipsj_v2/UTF8/ipsj}
 
@@
 \section{はじめに}
-近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている．
+近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている\cite{par:IoTIndustries}\cite{par:IoTComputing}．
 多くの組込みシステムは，厳しいリソース制約を持っており，効率的なメモリ確保が要求される．
@@
 
-このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている．
+このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている\cite{par:TLSF}\cite{url:TLSF}．
 TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため最悪実行時間が存在しない．
@@
 しかし，現状では，複数のスレッドが並行動作すると，メモリの衝突が起きる場合がある．
-本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を用いてTLSFアロケータをコンポーネント化する．
+本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System)\cite{par:TECS} を用いてTLSFアロケータをコンポーネント化する．
 コンポーネント化されたTLSFアロケータでは，各コンポーネントで独自のヒープ領域を保持するため，スレッドセーフなアロケータを実現できる．
@@
 まず\ref{sec:ComponentBasedDevelopment}章で，コンポーネントベース開発と提案するアロケータのベースとして用いるTECSについて述べる．
-\ref{sec:Design and Implementation}章では，TLSFアロケータのコンポーネント設計と実装について述べる．
-\ref{sec:Use Case}章では，ユースケースとして，利用例を述べる．
-\ref{sec:Related Work}章では，関連研究を述べ，最後に\ref{sec:Conclusion}章で本論文をまとめる．
+\ref{sec:DesignImplementation}章では，TLSFメモリアロケータのコンポーネント設計と実装について述べる．
+\ref{sec:UseCase}章では，ユースケースとして，利用例を述べる．
+\ref{sec:RelatedWork}章では，関連研究を述べ，最後に\ref{sec:Conclusion}章で本論文をまとめる．
 
@@
 
-ソフトウェア開発の生産性を向上させる手法のひとつにコンポーネントベース開発がある．
+ソフトウェア開発の生産性を向上させる手法のひとつにコンポーネントベース開発がある\cite{par:Crnkovic}\cite{par:CBD}．
 コンポーネントベース開発は，ソフトウェアの部品(コンポーネント)を組み合わせて開発を行う手法である．
@@
 さらに，システムの拡張や仕様変更にも柔軟に対応することができる．
+組込みシステム向けのコンポーネント技術として，TECSやAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SaveCCM}がある．
 
 \subsection{TECS}
-TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクトで開発されている組込みシステム向けのコンポーネント技術である．
+TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクト\cite{url:TOPPERS}で開発されている組込みシステム向けのコンポーネント技術である．
 TECSでは，コンポーネントの生成と結合はすべて静的に行われ，最適化されるため，コンポーネント化における実行時間や消費メモリのオーバヘッドを抑えることができる．
@@
     ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
-              [in] bool_t blocking );
+    ER rotate( [in] int degrees, [in] uint32_t speed_abs, [in] bool_t blocking );
     void initializePort( [in]int32_t type );
@@
     attr {
-        int32_t attr = 100;
+        int32_t port;
     };
     var {
-        int32_t var;
+        int32_t currentSpeed = 0;
     };
@@
 
-本章では，TLSFアロケータのコンポーネント設計について述べる．
-% 図\ref{fig:TLSFComponent}に，コンポーネント化されたTLSFアロケータのコンポーネント図を示す．
-
 \subsection{TLSF}
@@
 
+TLSFアルゴリズムは，メモリブロックを2段階に分類して，要求されたメモリサイズに最適なメモリブロックを検索する．
+図\ref{fig:TLSF}にTLSFアルゴリズムの概要を示す．
+例として，$malloc(100)$というメモリ確保の要求がされた場合を考える．
+まず第一段階では，要求されたメモリサイズの最上位ビットで分類する．
+この場合，100を2進数で表すと1100100であるため，最上位ビットから64から128の範囲であることが分かる．
+次に第二段階では，さらに細かい分類を行う．
+今回の場合，64から128を4分割しており，100は96-111のブロックに入る．
+この範囲にあるフリーブロック\footnote{フリーブロックは使用可能なメモリブロックのことである．}を使用するという流れである．
+
+単純な固定サイズブロック確保では最大50\%の無駄を生じてしまうが，TLSFでは2段階で細かく分類するため，メモリ効率が良いアルゴリズムとなっている．
+また，検索にかかる時間も高速で常に同じ速度で実行される．
+
 \begin{figure}[t]
@@
 
-\subsubsection{コンポーネント設計}
+\subsection{コンポーネント設計}
+
+TLSFメモリアロケータのコンポーネント設計について述べる．
+
+図\ref{src:TLSFSignature}は，アロケータが使用するメモリ管理用のシグニチャ記述である．
+メモリプール初期化関数$initializeMemoryPool$，メモリ確保用の関数$calloc, malloc, realloc$，そしてメモリ解放用の関数$free$をシグニチャとして定義している．
 
@@
     int    initializeMemoryPool(void);
-    void   *calloc( [in]size_t nelem, [in]size_t elem_size );
+    void   *calloc( [in]size_t nelem,
+                    [in]size_t elem_size );
     void   *malloc( [in]size_t size );
-    void   *realloc( [in]const void *ptr, [in]size_t new_size );
+    void   *realloc( [in]const void *ptr,
+                     [in]size_t new_size );
     void   free( [in]const void *ptr );
@@
 
-mruby on TECS は，mruby (軽量Ruby)を用いたコンポーネントベース開発が可能な組込みソフトウェア開発フレームワークである．
+mruby on TECS は，mruby (軽量Ruby)\cite{par:mruby}\cite{url:mruby}を用いたコンポーネントベース開発が可能な組込みソフトウェア開発フレームワークである\cite{par:mrubyonTECS}．
 スクリプト言語を用いることで，組込みソフトウェア開発の生産性向上を目指している．
@@
 
-図\ref{fig:TLSF-mruby}のように，VMにTLSFメモリアロケータコンポーネントを結合し，各VMで独自のヒープ領域を持つように設計する．
-各VMがそれぞれメモリプールを保持しているため，複数のVMがメモリ衝突を起こすことなく，実行できる．
+図\ref{fig:UseCase_mruby}のように，VMにTLSFメモリアロケータコンポーネントを結合し，各VMで独自のヒープ領域を持つように設計する．
+各VMが結合しているTLSFコンポーネントがそれぞれメモリプールを保持しているため，複数のVMがメモリ衝突を起こすことなく，実行できる．
+図\ref{fig:UseCase_mruby}では，1つ目のVMが1MB (1024*1024)のヒープ領域，2つ目のVMが2MB (2*1024*1024)のヒープ領域を持っていることを示している．
+コンポーネント化により，各VMで異なるヒープ領域を設定することが容易になっている．
 さらに，RiteVMはインクリメンタルGC (Garbage Collection)を行うが，独自のメモリプールを保持しているため，GCを始めたVMがGCの実行によって，他のVMの実行を妨げることもない．
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
+    \caption{RiteVMとTLSFのコンポーネント図}
+    \label{fig:UseCase_mruby}
+\end{figure}
 
@@
 
-TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)をTECSによってコンポーネント化したTCP/IPプロトコルスタックである．
+TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)\cite{url:TINET}をTECSによってコンポーネント化したTCP/IPプロトコルスタックである．
 複雑で大規模なソースコードやマクロで構成されているTINETをTECSによってコンポーネント化することで，実行時間やメモリ消費量のオーバヘッドを抑えつつ，TCP/UDPやIPv4/IPv6といった通信プロトコルの変更等のコンフィグラビリティが向上している．
@@
 TINET+TECSやTINETは，プロトコル間のデータコピー回数を最少とするなど，組込みシステムの厳しいメモリ制約に対応している．
-しかし，現状ではTOPPERS/ASPでサポートされている固定長メモリアロケータを利用している．
-
+しかし，現状ではTOPPERS/ASP\footnote{TOPPERS/ASPは，$\mu$ITRON\cite{par:microITRON}をベースにしたリアルタイムOSである．}でサポートされている固定長メモリアロケータを利用している．
 TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できる．
 したがって，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
+
+さらに，図\ref{fig:UseCase_TINET}のように，固定長メモリアロケータは異なるサイズのメモリプールを用意し，必要に応じてメモリプールを選択する必要がある．
+TLSFメモリアロケータコンポーネントを利用することで，メモリプールを選択する必要もなく，効率的にメモリ管理を行うことが可能になる．
 TINET+TECSは，TECSによってコンポーネント化されているため，提案するTLSFメモリアロケータコンポーネントを拡張することが容易になっている．
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
+    \caption{固定長メモリアロケータとTLSFメモリアロケータ}
+    \label{fig:UseCase_TINET}
+\end{figure}
 
@@
 \label{sec:Conclusion}
+
+本論文では，リアルタイムシステムに適した動的メモリアロケータであるTLSFメモリアロケータのコンポーネント化を提案した．
+提案するコンポーネント化されたTLSFメモリアロケータは独自のヒープ領域を保持できるため，複数のスレッドから同時にメモリの確保や解放を行っても，メモリ競合が起こすことがない．
+ヒープ領域のサイズはコンポーネントの内部変数として設定するため，サイズ変更も容易になる．
+
+提案するTLSFメモリアロケータは，コンポーネント化によって再利用性も向上している．
+利用したいシステムのメモリアロケータ部分をTLSFコンポーネントに入れ替えるだけで，利用可能となる．
+さらに，コンポーネント図によってシステムを可視化でき，複雑で大規模なシステムを把握することに役立つ．
+
+今後は，提案するTLSFコンポーネントの拡張として，統計情報を取得できるような機能を提供する．
+メモリ確保の頻度や残りのヒープ領域サイズ等の情報を取得することで，メモリ制約の厳しい組込みシステムのソフトウェア開発の一助となると考えている．
 

### 2017-07-13 kansai/paper.tex
Update

@@
 
-\title{組込みシステムに適した\\動的メモリアロケータのコンポーネント化}
+\title{
+    {\Huge 組込みシステムに適した動的メモリアロケータのコンポーネント化}
+  \\{\huge Componentized Dynamic Memory Allocator for Embedded Systems}
+}
 
-\etitle{Componentized Dynamic Memory Allocator for Embedded Systems}
+\etitle{\vspace{-3.5cm}}
+% \etitle{Componentized Dynamic Memory Allocator for Embedded Systems}
 
@@
 
-\author{山本 拓朗}{Takuro Yamamoto}{OU}%[joho.taro@ipsj.or.jp]
-\author{大山 博司}{Hiroshi Oyama}{OKUMA}%
-\author{安積 卓也}{Takuya Azumi}{OU}%[gakkai.jiro@ipsj.or.jp]
+\author{　{\LARGE 山本　拓朗}}{{\Large Takuro Yamamoto}}{OU}%[joho.taro@ipsj.or.jp]
+\author{　　{\LARGE 大山　博司}}{{\Large Hiroshi Oyama}}{OKUMA}%
+\author{　　{\LARGE 安積　卓也}}{{\Large Takuya Azumi}}{OU}%[gakkai.jiro@ipsj.or.jp]
 
@@
 \section{はじめに}
+
 近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている\cite{par:IoTIndustries}\cite{par:IoTComputing}．
@@
 このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている\cite{par:TLSF}\cite{url:TLSF}．
-TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため最悪実行時間が存在しない．
-TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで利用されている．
+TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため最悪実行時間を見積もることができ，リアルタイムシステムに適した動的メモリアロケータである．
+TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで採用されている．
 
 しかし，現状では，複数のスレッドが並行動作すると，メモリの衝突が起きる場合がある．
-本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System)\cite{par:TECS} を用いてTLSFアロケータをコンポーネント化する．
-コンポーネント化されたTLSFアロケータでは，各コンポーネントで独自のヒープ領域を保持するため，スレッドセーフなアロケータを実現できる．
+本研究では，組込み向けコンポーネントシステムであるTECS (TOPPERS Embedded Component System)\cite{url:TECS}\cite{par:TECS} を用いてTLSFアロケータをコンポーネント化する．
+TECSを用いたコンポーネントベース開発は，ソフトウェアの再利用性を向上させ，システムを可視化できるため，ソフトウェア開発の生産性を向上させることができる．
+コンポーネント化されたTLSFアロケータは，各コンポーネントが独自のヒープ領域を保持するため，スレッドセーフなメモリアロケータを実現できる．
 さらに，コンポーネントとして特性を利用できるため，メモリサイズの変更等が柔軟になる．
-本論文では，提案するTLSFメモリアロケータコンポーネントのユースケースとして，利用例を述べる．
+本論文では，TLSFメモリアロケータコンポーネントを提案し，そのユースケースとして，利用例を述べる．
 
@@
 \ref{sec:DesignImplementation}章では，TLSFメモリアロケータのコンポーネント設計と実装について述べる．
-\ref{sec:UseCase}章では，ユースケースとして，利用例を述べる．
-\ref{sec:RelatedWork}章では，関連研究を述べ，最後に\ref{sec:Conclusion}章で本論文をまとめる．
+\ref{sec:UseCase}章では，ユースケースとして，利用例を述べ, 最後に\ref{sec:Conclusion}章で本論文をまとめる．
 
@@
 組込みシステム向けのコンポーネント技術として，TECSやAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SaveCCM}がある．
+本研究で利用したTECSについて次で述べる．
 
 \subsection{TECS}
+
 TECS (TOPPERS Embedded Component System)は，TOPPERSプロジェクト\cite{url:TOPPERS}で開発されている組込みシステム向けのコンポーネント技術である．
 TECSでは，コンポーネントの生成と結合はすべて静的に行われ，最適化されるため，コンポーネント化における実行時間や消費メモリのオーバヘッドを抑えることができる．
-% 他の特徴として，C言語での実装，ソースレベルでの移植性，コンポーネントの粒度が小さいことなどがある．
+さらに，組込みシステム開発に広く用いられているC言語による開発を採用しており，組込みシステムに特化したコンポーネントシステムである．
 
 \subsubsection{コンポーネントモデル}
+
 図\ref{fig:component}にTECSコンポーネント図の例を示す．
@@
 \subsubsection{コンポーネント記述}
-TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述に分類され，cdlファイルに記述する．
+TECSのコンポーネント記述は，シグニチャ記述，セルタイプ記述，組上げ記述に分類され，CDL (Component Description Language)ファイルに記述する．
 図\ref{fig:component}のコンポーネント記述について次に述べる．
@@
 signature sMotor {
+    void initializePort( [in]int32_t type );
     int32_t getCounts( void );
@@
     ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees, [in] uint32_t speed_abs, [in] bool_t blocking );
-    void initializePort( [in]int32_t type );
+    ER rotate( [in] int degrees,
+                [in] uint32_t speed_abs,
+                [in] bool_t blocking );
 };
@@
 
+\subsubsection{開発フロー}
+
+図\ref{fig:DevelopmentFlow}にTECSを利用した開発フローを示す．
+TECSジェネレータは，CDLファイルから，C言語のインターフェースコード(.hや.c)とリアルタイムOSのシステム設定ファイル(.cfg)を生成する．
+
+TECSを用いたソフトウェア開発者は，コンポーネント設計者とアプリケーション開発者に分けられる．
+コンポーネント設計者は，セル間のインターフェースであるシグニチャやセルの型であるセルタイプを定義する．
+これらが定義されたCDLファイルから生成されたテンプレートコードを利用し，コンポーネントの提供する機能や振る舞いをC言語で実装する．
+コンポーネントの機能を実装したソースコードは，セルタイプコードと呼ばれる．
+アプリケーション開発者は，コンポーネント図や定義済みのセルタイプを利用して，組上げ記述によりセル同士を結合させることでアプリケーションを開発する．
+最終的にヘッダ，インターフェースコード，セルタイプコードをコンパイル・リンクすることで，アプリケーションモジュールが生成される．
+
 \section{設計と実装}
@@
 TLSFメモリアロケータのコンポーネント設計について述べる．
-
-図\ref{src:TLSFSignature}は，アロケータが使用するメモリ管理用のシグニチャ記述である．
-メモリプール初期化関数$initializeMemoryPool$，メモリ確保用の関数$calloc, malloc, realloc$，そしてメモリ解放用の関数$free$をシグニチャとして定義している．
+本研究では，TECSを用いてTLSFをコンポーネント化を行っている．
+使用したTLSFのバージョンは，2.4.6である\footnote{http://www.gii.upv.es/tlsf/main/repo}．
 
@@
 
+図\ref{src:TLSFSignature}は，アロケータが使用するメモリ管理用のシグニチャ記述である．
+メモリプール初期化関数{\it initializeMemoryPool}，メモリ確保用の関数{\it calloc}, {\it malloc}, {\it realloc}，そしてメモリ解放用の関数{\it free}をシグニチャとして定義している．
+
 \begin{figure}[t]
@@
 \label{src:TLSFCelltype}
+\end{figure}
+
+TLSFメモリアロケータコンポーネントのセルタイプ記述を図\ref{src:TLSFCelltype}に示す．
+受け口{\it eMalloc}は，メモリ管理(確保や解放)を行うすべてのコンポーネントと結合される．
+ここで，{\it [inline]}は受け口関数をインライン関数として提供するための指定子である．
+メモリプールサイズをコンポーネントの属性として，メモリプールへのポインタをコンポーネントの内部変数として定義している．
+各コンポーネントが独自のヒープ領域を保持しているため，異なるスレッドで同時にメモリ管理用の関数を呼び出した場合でも，排他制御を行うことなく，メモリ競合を起こさない．
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
+    \caption{コンポーネント化される前のTLSF}
+    \label{fig:WithoutTECS}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
+    \caption{コンポーネント化されたTLSF}
+    \label{fig:WithTECS}
+\end{figure}
+
+図\ref{fig:WithoutTECS}に示すように，コンポーネント化を行う前のTLSFでは，ヒープ領域を複数のスレッドで共有しているため，複数のスレッドからメモリの確保や解放を同時に行うとメモリ競合が生じる場合があった．
+図\ref{fig:WithTECS}のように，TECSを用いてTLSFのコンポーネント化を行うと，各コンポーネントが独自にヒープ領域を保持し，その中でメモリ管理を行うため，排他制御なしでスレッドセーフに動作することが可能になる．
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+void*
+mrb_TECS_allocf(mrb_state *mrb, void *p, size_t size, void *ud)
+{
+    CELLCB	*p_cellcb= (CELLCB *)ud;
+    if (size == 0) {
+        cMalloc_free(p);
+        //tlsf_free(p);
+        return NULL;
+    }
+    else if (p){
+        //return tlsf_realloc(p,size);
+        return cMalloc_realloc(p, size);
+    }
+    else {
+        //return tlsf_malloc(size);
+        return cMalloc_malloc(size);
+    }
+}
+\end{lstlisting}
+\caption{TLSFメモリアロケータコンポーネントの利用部分}  
+\label{src:TLSFC}
 \end{figure}
@@
 
-TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)\cite{url:TINET}をTECSによってコンポーネント化したTCP/IPプロトコルスタックである．
+TINET+TECSは，組込み向けのTCP/IPプロトコルスタックであるTINET (Tomakomai InterNETworking)\cite{url:TINET}\cite{par:TINET}をTECSによってコンポーネント化したTCP/IPプロトコルスタックである\cite{par:TINET+TECS}．
 複雑で大規模なソースコードやマクロで構成されているTINETをTECSによってコンポーネント化することで，実行時間やメモリ消費量のオーバヘッドを抑えつつ，TCP/UDPやIPv4/IPv6といった通信プロトコルの変更等のコンフィグラビリティが向上している．
@@
 TINET+TECSやTINETは，プロトコル間のデータコピー回数を最少とするなど，組込みシステムの厳しいメモリ制約に対応している．
-しかし，現状ではTOPPERS/ASP\footnote{TOPPERS/ASPは，$\mu$ITRON\cite{par:microITRON}をベースにしたリアルタイムOSである．}でサポートされている固定長メモリアロケータを利用している．
+しかし，現状ではTOPPERS/ASP\footnote{TOPPERS/ASPは，TOPPERSプロジェクトで開発されている$\mu$ITRON\cite{par:microITRON}をベースにしたリアルタイムOSである．}でサポートされている固定長メモリアロケータを利用している．
 TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できる．
@@
 
-\section{関連研究}
-\label{sec:RelatedWork}
+% \section{関連研究}
+% \label{sec:RelatedWork}
 
@@
 今後は，提案するTLSFコンポーネントの拡張として，統計情報を取得できるような機能を提供する．
-メモリ確保の頻度や残りのヒープ領域サイズ等の情報を取得することで，メモリ制約の厳しい組込みシステムのソフトウェア開発の一助となると考えている．
+メモリ確保の頻度や残りのヒープ領域サイズ等の情報を取得することで，メモリ制約の厳しい組込みシステムのソフトウェア開発の一助になると考えている．
 

### 2017-07-25 kansai/paper.tex
Update paper.tex

@@
 \usepackage{enumerate,cite,url}
+\usepackage{fancyhdr}
 \usepackage{listings,jlisting}
@@
 
+\pagestyle{empty}
+
 \begin{document}
@@
 
-\affiliate{OU}{大阪大学基礎工学研究科\\
+\affiliate{OU}{大阪大学大学院基礎工学研究科\\
 Graduate School of Engineering Science, Osaka University}
@@
 
+\thispagestyle{fancy}
+\renewcommand{\headrulewidth}{0pt} % ヘッダーの羅線をなくす
+\lhead[]{\vspace{+1.5cm} \huge A-03 \vspace{-1.5cm}}
+\chead[]{}
+\rhead[]{\vspace{+1.0cm} 2017 年度情報処理学会関西支部 支部大会 \\ \ \\ \vspace{-1.0cm}}
+\cfoot[]{}
+
 \section{はじめに}
 
-近年，組込みシステムは多くの機器に組み込まれており，このIoT社会を支える重要な役割を担っている\cite{par:IoTIndustries}\cite{par:IoTComputing}．
+近年，組込みシステムは高性能化しており，このIoT社会を支える重要な役割を担っている\cite{par:IoTIndustries}\cite{par:IoTComputing}．
 多くの組込みシステムは，厳しいリソース制約を持っており，効率的なメモリ確保が要求される．
@@
 
+\vspace{3mm}
 \subsubsection{コンポーネントモデル}
@@
 
+\vspace{3mm}
 \subsubsection{コンポーネント記述}
@@
 
+\vspace{3mm}
 \subsubsection{開発フロー}
 
-図\ref{fig:DevelopmentFlow}にTECSを利用した開発フローを示す．
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
+    \caption{TECSの開発フロー}
+    \label{fig:TECSFlow}
+\end{figure}
+
+図\ref{fig:TECSFlow}にTECSを利用した開発フローを示す．
 TECSジェネレータは，CDLファイルから，C言語のインターフェースコード(.hや.c)とリアルタイムOSのシステム設定ファイル(.cfg)を生成する．
@@
 
+本研究では，組込みシステム向けの動的メモリアロケータであるTLSFメモリアロケータのコンポーネント化を行った．
+本章では，TLSFメモリアロケータについて詳細を述べ，提案するTLSFメモリアロケータのコンポーネント設計について述べる．
+
 \subsection{TLSF}
 \label{sec:TLSF}
-TLSF (Two-Level Segregate Fit)メモリアロケータは，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
+TLSF (Two-Level Segregate Fit)メモリアロケータ\cite{par:TLSF}\cite{url:TLSF}は，M. Masmanoらによって提案されたリアルタイムシステムに適した動的メモリアロケータである．
 TLSFメモリアロケータは以下のような特徴がある．
@@
         最悪実行時間が常に見積もれることに加え，TLSFは高速に実行される．
-        x86アーキテクチャで最大168のプロセッサ命令を実行することができる．
+        % x86アーキテクチャで最大168のプロセッサ命令を実行することができる．
     \item[{効率的なメモリ消費}]\mbox{}\\
@@
 単純な固定サイズブロック確保では最大50\%の無駄を生じてしまうが，TLSFでは2段階で細かく分類するため，メモリ効率が良いアルゴリズムとなっている．
-また，検索にかかる時間も高速で常に同じ速度で実行される．
+さらに，検索にかかる時間も高速で常に同じ速度で実行される．
 
@@
 \begin{lstlisting}
-[deviate]
 signature sMalloc {
@@
 \begin{lstlisting}
+cell tTask Task_001 {
+    cMalloc = TLSFMalloc_001.eMalloc;
+};
+cell tTLSFMalloc TLSFMalloc_001 {
+    memoryPoolSize = 1024*1024; /* 1MB */
+};
+cell tTask Task_002 {
+    cMalloc = TLSFMalloc_002.eMalloc;
+};
+cell tTLSFMalloc TLSFMalloc_002 {
+    memoryPoolSize = 2*1024*1024; /* 2MB */
+};
+\end{lstlisting}
+\caption{TLSFメモリアロケータコンポーネントの組上げ記述}  
+\label{src:TLSFBuild}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
 void*
-mrb_TECS_allocf(mrb_state *mrb, void *p, size_t size, void *ud)
+mrb_TECS_allocf(mrb_state *mrb, void *p, 
+                  size_t size, void *ud)
 {
-    CELLCB	*p_cellcb= (CELLCB *)ud;
+    CELLCB	*p_cellcb = (CELLCB *)ud;
     if (size == 0) {
+        //tlsf_free(p);
         cMalloc_free(p);
-        //tlsf_free(p);
         return NULL;
     }
-    else if (p){
-        //return tlsf_realloc(p,size);
+    else if (p) {
+        //return tlsf_realloc(p, size);
         return cMalloc_realloc(p, size);
@@
 
+図\ref{src:TLSFBuild}に，図\ref{fig:WithTECS}のコンポーネント図で表されるTLSFメモリアロケータコンポーネントの組上げ記述を示す\footnote{他にも呼び口や受け口，属性，内部変数を記述するが，ここでは簡略化のため省略している．}．
+2組のタスクコンポーネントとTLSFコンポーネントが結合されている．
+それぞれのメモリプールサイズは5行目及び11行目のように内部変数として設定可能である．
+図\ref{src:TLSFC}は，TLSFメモリアロケータコンポーネントの受け口関数を実際に呼び出しているコード部分である．
+利用部分は，\ref{sec:mrubyonTECS}章で紹介するmruby on TECSフレームワーク\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}で，VMがメモリ管理を行う関数である．
+8行目は，TLSFメモリアロケータコンポーネントの{\it free}関数を呼び出している．
+{\it cMalloc\_}は，呼び口名を表わしている(図\ref{src:TLSFBuild}の2行目)
+同様に，13行目，17行目はメモリ確保を行っている部分である．
+図\ref{src:TLSFC}のコードが実行されるセルが，{\it Task\_001}の場合は{\it TLSFMalloc\_001}で，{\it Task\_002}の場合は{\it TLSFMalloc\_002}でメモリ管理が行われる．
+このように，TECSを用いたコンポーネントベース開発では，それぞれ結合しているセルは異なるものの，同じコードで動作させることが出来る．
+
 \section{ユースケース}
@@
 
-mruby on TECS は，mruby (軽量Ruby)\cite{par:mruby}\cite{url:mruby}を用いたコンポーネントベース開発が可能な組込みソフトウェア開発フレームワークである\cite{par:mrubyonTECS}．
+mruby on TECS は，mruby (軽量Ruby)\cite{par:mruby}\cite{url:mruby}を用いたコンポーネントベース開発が可能な組込みソフトウェア開発フレームワークである\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}．
 スクリプト言語を用いることで，組込みソフトウェア開発の生産性向上を目指している．
@@
 mrubyプログラムは，mrubyコンパイラによってバイトコードに変換され，RiteVMと呼ばれるVM上で実行される．
-本フレームワークでは，RiteVMやRTOS (Real-Time OS)の機能もすべてTECSによってコンポーネント化されている．
+本フレームワークでは，RiteVMやリアルタイムOSの機能もすべてTECSによってコンポーネント化されている．
 
@@
 
-\subsubsection{マルチVM対応}
+% \subsubsection{マルチVM対応}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
+    \caption{RiteVMとTLSFのコンポーネント図}
+    \label{fig:UseCase_mruby}
+\end{figure}
 
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
-    \caption{RiteVMとTLSFのコンポーネント図}
-    \label{fig:UseCase_mruby}
-\end{figure}
-
 \subsection{TINET+TECS}
@@
 
-\subsubsection{データ送受信用のメモリ管理}
-
-データの送受信処理を行う際，各プロトコルでメモリ領域の確保と解放が行われる．
-TINET+TECSやTINETは，プロトコル間のデータコピー回数を最少とするなど，組込みシステムの厳しいメモリ制約に対応している．
-しかし，現状ではTOPPERS/ASP\footnote{TOPPERS/ASPは，TOPPERSプロジェクトで開発されている$\mu$ITRON\cite{par:microITRON}をベースにしたリアルタイムOSである．}でサポートされている固定長メモリアロケータを利用している．
-TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できる．
-したがって，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
-
-さらに，図\ref{fig:UseCase_TINET}のように，固定長メモリアロケータは異なるサイズのメモリプールを用意し，必要に応じてメモリプールを選択する必要がある．
-TLSFメモリアロケータコンポーネントを利用することで，メモリプールを選択する必要もなく，効率的にメモリ管理を行うことが可能になる．
-TINET+TECSは，TECSによってコンポーネント化されているため，提案するTLSFメモリアロケータコンポーネントを拡張することが容易になっている．
+% \subsubsection{データ送受信用のメモリ管理}
 
@@
 \end{figure}
+
+データの送受信処理を行う際，各プロトコルでメモリ領域の確保と解放が行われる．
+TINET+TECSやTINETは，プロトコル間のデータコピー回数を最少とするなど，組込みシステムの厳しいメモリ制約に対応している．
+しかし，現状ではTOPPERS/ASP\footnote{TOPPERS/ASPは，TOPPERSプロジェクトで開発されている$\mu$ITRON\cite{par:microITRON}をベースにしたリアルタイムOSである．}でサポートされている固定長メモリアロケータを利用している．
+TCP/IPプロトコルスタックでは，TCP層やIP層，Ethernet層といった各層でメモリの確保や解放が繰り返されるので，アロケータの役割は重要になっている．
+図\ref{fig:UseCase_TINET}のように，TINET+TECSではメモリ管理を行うすべてのコンポーネントがアロケータと結合されている．
+TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できるため，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
+
+さらに，図\ref{fig:UseCase_TINET}のように，固定長メモリアロケータは異なるサイズのメモリプールを用意し，必要に応じてメモリプールを選択する必要がある．
+TLSFメモリアロケータコンポーネントを利用することで，メモリプールを選択する必要もなく，効率的にメモリ管理を行うことが可能になる．
+TINET+TECSは，TECSによってコンポーネントベースで開発されているため，提案するTLSFメモリアロケータコンポーネントの拡張性も良い．
 
@@
 提案するTLSFメモリアロケータは，コンポーネント化によって再利用性も向上している．
+ユースケースとして，mruby on TECSフレームワークや，TINET+TECSで利用できることを述べたが，その他にもTECSを採用したリアルタイムOSであるTOPPERS/ASP3\cite{par:ASP3}やTOPPERS/HRP2\cite{par:hr-tecs}に適用することも可能である．
 利用したいシステムのメモリアロケータ部分をTLSFコンポーネントに入れ替えるだけで，利用可能となる．
@@
 
-今後は，提案するTLSFコンポーネントの拡張として，統計情報を取得できるような機能を提供する．
+今後は，提案するTLSFコンポーネントの拡張として，統計情報を取得できる機能を提供する．
 メモリ確保の頻度や残りのヒープ領域サイズ等の情報を取得することで，メモリ制約の厳しい組込みシステムのソフトウェア開発の一助になると考えている．

### 2017-07-26 kansai/paper.tex
Update -- Final ver.

@@
 このような要求を満たす，組込みシステムに適した動的メモリアロケータとして，TLSF (Two-Level Segregate Fit) アロケータが提案されている\cite{par:TLSF}\cite{url:TLSF}．
-TLSFアロケータは，メモリブロックを2段階で分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため最悪実行時間を見積もることができ，リアルタイムシステムに適した動的メモリアロケータである．
+TLSFアロケータは，メモリブロックを2段階で細かく分類することでメモリ利用効率を向上させており，常に$O(1)$で実行するため，最悪実行時間を見積もることができ，リアルタイムシステムに適した動的メモリアロケータである．
 TLSFアロケータは，メモリ利用効率が良く，リアルタイムシステムに向いているため，多くのリアルタイムOSで採用されている．
@@
 さらに，システムの拡張や仕様変更にも柔軟に対応することができる．
-組込みシステム向けのコンポーネント技術として，TECSやAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SaveCCM}がある．
+組込みシステム向けのコンポーネント技術として，TECSやAUTOSAR\cite{url:AUTOSAR}，SaveCCM\cite{par:SAVEapproach}がある．
 本研究で利用したTECSについて次で述べる．
@@
 図\ref{fig:TECSFlow}にTECSを利用した開発フローを示す．
-TECSジェネレータは，CDLファイルから，C言語のインターフェースコード(.hや.c)とリアルタイムOSのシステム設定ファイル(.cfg)を生成する．
+TECSジェネレータは，CDLファイルから，C言語のインタフェースコード(.hや.c)とリアルタイムOSのシステム設定ファイル(.cfg)を生成する．
 
 TECSを用いたソフトウェア開発者は，コンポーネント設計者とアプリケーション開発者に分けられる．
-コンポーネント設計者は，セル間のインターフェースであるシグニチャやセルの型であるセルタイプを定義する．
+コンポーネント設計者は，セル間のインタフェースであるシグニチャやセルの型であるセルタイプを定義する．
 これらが定義されたCDLファイルから生成されたテンプレートコードを利用し，コンポーネントの提供する機能や振る舞いをC言語で実装する．
@@
 アプリケーション開発者は，コンポーネント図や定義済みのセルタイプを利用して，組上げ記述によりセル同士を結合させることでアプリケーションを開発する．
-最終的にヘッダ，インターフェースコード，セルタイプコードをコンパイル・リンクすることで，アプリケーションモジュールが生成される．
+最終的にヘッダ，インタフェースコード，セルタイプコードをコンパイル・リンクすることで，アプリケーションモジュールが生成される．
 
@@
 メモリプールサイズをコンポーネントの属性として，メモリプールへのポインタをコンポーネントの内部変数として定義している．
-各コンポーネントが独自のヒープ領域を保持しているため，異なるスレッドで同時にメモリ管理用の関数を呼び出した場合でも，排他制御を行うことなく，メモリ競合を起こさない．
+各コンポーネントが独自のヒープ領域を保持しているため，異なるスレッドで同時にメモリ管理用の関数を呼び出した場合でも，排他制御を行うことなく，メモリ競合を起こさずに動作させることが可能になる．
 
@@
 8行目は，TLSFメモリアロケータコンポーネントの{\it free}関数を呼び出している．
-{\it cMalloc\_}は，呼び口名を表わしている(図\ref{src:TLSFBuild}の2行目)
+{\it cMalloc\_}は，呼び口名(図\ref{src:TLSFBuild}の2行目)を表している.
 同様に，13行目，17行目はメモリ確保を行っている部分である．
-図\ref{src:TLSFC}のコードが実行されるセルが，{\it Task\_001}の場合は{\it TLSFMalloc\_001}で，{\it Task\_002}の場合は{\it TLSFMalloc\_002}でメモリ管理が行われる．
-このように，TECSを用いたコンポーネントベース開発では，それぞれ結合しているセルは異なるものの，同じコードで動作させることが出来る．
+図\ref{src:TLSFC}のコードが実行されるセルが，{\it Task\_001}の場合は{\it TLSFMalloc\_001}コンポーネントで，{\it Task\_002}の場合は{\it TLSFMalloc\_002}コンポーネントでそれぞれメモリ管理が行われる．
+このように，TECSを用いたコンポーネントベース開発では，それぞれ結合しているセルは異なるものの，実際にCコードを修正することなく，同じコードで動作させることが可能になる．
 
@@
 図\ref{fig:UseCase_TINET}のように，TINET+TECSではメモリ管理を行うすべてのコンポーネントがアロケータと結合されている．
-TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度でメモリ効率を向上できるため，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
+TLSFメモリアロケータは，固定長メモリアロケータと比べて，同じ速度で実行できる上に，メモリ効率を向上できるため，TINET+TECSにTLSFメモリアロケータを組み込むことで，より良いメモリ効率を期待できる．
 

### 2017-10-26 kansai/paper.tex
Final version

@@
         シグニチャ記述は，セルのインタフェースを定義する．
-        図\ref{signature}に示す通り，{\it signature}キーワードに続けて，シグニチャ名(sMotor)を記述する．
+        図\ref{signature}に示す通り，{\it signature}キーワードに続けて，シグニチャ名({\it sMotor})を記述する．
         %図\ref{signature}のようにシグニチャsMotorを定義できる.
-        TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，[in]と[out]という指定子が付けられる．
+        TECSでは，インタフェースの定義を明確にするために，入力と出力にはそれぞれ，{\it [in]}と{\it [out]}という指定子が付けられる．
 
@@
         セルタイプ記述は，受け口，呼び口，属性，変数を用いてセルタイプを定義する．
-        {\it celltype}キーワードに続けて，セルタイプ名(tCaller)を記述する．
+        {\it celltype}キーワードに続けて，セルタイプ名({\it tCaller})を記述する．
         図\ref{celltype}に示す通り，受け口は，{\it entry}キーワードに続けて，シグニチャ名，受け口名を記述する．
@@
         呼び口名，``="，結合先の受け口名の順に記述し，セルを結合する．
-        図\ref{build}では，セルCallerの呼び口cMotorと，セルMotorの受け口eMotorが結合されている．
+        図\ref{build}では，セル{\it Caller}の呼び口{\it cMotor}と，セル{\it Motor}の受け口{\it eMotor}が結合されている．
 
@@
 
-図\ref{fig:UseCase_mruby}のように，VMにTLSFメモリアロケータコンポーネントを結合し，各VMで独自のヒープ領域を持つように設計する．
+そこで図\ref{fig:UseCase_mruby}のように，VMにTLSFメモリアロケータコンポーネントを結合し，各VMで独自のヒープ領域を持つように設計する．
 各VMが結合しているTLSFコンポーネントがそれぞれメモリプールを保持しているため，複数のVMがメモリ衝突を起こすことなく，実行できる．
@@
 利用したいシステムのメモリアロケータ部分をTLSFコンポーネントに入れ替えるだけで，利用可能となる．
-さらに，コンポーネント図によってシステムを可視化でき，複雑で大規模なシステムを把握することに役立つ．
+さらに，コンポーネント図によってシステムを可視化でき，複雑で大規模なシステムを把握することにも役立つ．
 

### 2017-11-06 ipsj/paper.tex
Add ipsj

\documentclass[JIP]{ipsj_v2/UTF8/ipsj}

\usepackage{graphicx}
\usepackage{latexsym}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{22}% vol22=2014
\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
\setcounter{page}{1}

\received{2014}{3}{4}
%\rereceived{2011}{10}{1}   % optional
%\rerereceived{2011}{10}{31} % optional
\accepted{2014}{8}{1}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\begin{document}

\title{How to Prepare Your Papers for the JIP\\
(ipsj.cls version 1.7)}

\affiliate{IPSJ}{Information Processing Society of Japan, 
Chiyoda, Tokyo 101--0062, Japan}
\affiliate{JU}{Johoshori University, Chiyoda, Tokyo 101--0062, Japan}
\paffiliate{PJU}{Johoshori University}

\author{Taro Joho}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
\author{Hanako Shori}{JU}[shori.hanako@johosyori-u.ac.jp]
\author{Jiro Gakkai}{IPSJ}

\begin{abstract}
This document is a guide for preparing drafts to be submitted to the
Journal of Information Processing (JIP) and for the final camera-ready
manuscripts of papers to appear in the JIP that use \LaTeX and special
style files.  Since this document itself is produced with these style
files, it will help you to refer to its source file, which is
distributed with these style files.
\end{abstract}

\begin{keyword}
Journal of Information Processing, \LaTeX, style files, ``Dos and
 Don'ts'' list
\end{keyword}

\maketitle

%1
\section{Introduction}

The Information Processing Society of Japan (IPSJ) publishes Journal of
Information Processing (JIP) as its flagship international journal.
Thus far, the JIP adopted the landscape A4 format for publishing papers,
but it has changed this format to the portrait A4 format because of many
requests from authors.  Corresponding to this format change, the JIP
accepts the portrait A4 format for submitting papers.

Following with this change, we, the Editorial Board of the JIP, prepared
a new style file for \LaTeX\@.  In this manuscript, we first describe
the usage of the style file.  The basic strategy of the new style file
is to require no special knowledge of command usage that does not use
standard \LaTeX commands.  Authors of a paper can use standard \LaTeX
commands to keep within the formatting restrictions of the paper, such
as setting space pitches and margins.  The guideline of the paper format
will be described in Section~\ref{body}.  Since this manuscript itself
also is written with the style file, we hope it will help with writing a
paper.

The Editorial Board of the JIP has also prepared a ``Dos and Don'ts''
list of matters an author should consider while writing a paper.  We
have added the list to the latter portion of this manuscript.  Please
use the list as a checklist for preparing to submit a paper.

%2
\section{Flow from Submission to Publishing}
%2.1
\subsection{Preparation}

The JIP author's kit including the \LaTeX style files can be downloaded
from the following URL:
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/style.html|
\end{quote}
The kit includes the following files:
\begin{enumerate}
\item \|ipsj.cls|: style file for ipsj journals
\item \|ipsjpref.sty|: style for the foreword
\item \|jsample.tex|: source for the Japanese version of this guide
\item \|esample.tex|: source of this guide
\item \|ipsjsort-e.bst|: bibtex style (sorted)
\item \|ipsjunsrt-e.bst|: bibtex style (unsorted)
\item \|bibsample.bib|: sample of bibliographic data (Japanese)
\item \|ebibsample.bib|: sample of bibliographic data (English)

\item \|ipsjtech.sty|: style file for technical report
\item \ \|tech-jsample.tex|: source for the Japanese version of technical report
\item \ \|tech-esample.tex|: source for the English version of technical report
\end{enumerate}

Since the kit has variants corresponding to multiple platforms,
including UNIX workstations, Windows (DOS), and Macintosh machines, an
appropriate variant can be selected and unpacked on the target
platform.

Since {\LaTeXe} is required as an execution environment, please install
it.

Regarding manuscripts written with Microsoft Word, a corresponding
company will convert them into \LaTeX\@.  This means that the Microsoft
Word format is used just a reference.

\footnotetext{The real author is the Editorial Board of JIP.}

%2.2
\subsection{Draft Submission}

First, generate a PDF file from your \LaTeX source and style file under
your {\LaTeXe} environment and check that the generated PDF file can be
read with the Adobe PDF reader.  After that, register your email address
into the Paper Review Management System (PRMS) through the following
URL:
\begin{quote}
 \small
 \|https://www.ipsj.or.jp/prms/author_pre_submit.do|
\end{quote}

\noindent
The system will return an email including another URL for submitting
your paper. The manual for submission via the PRMS is available at the
following URL: 
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/manual/|\\
 \|e_manual.html|
\end{quote}

The JIP adopts \textit{single blind review}, 
where you will not know reviewers names.

%2.3
\subsection{Final Version}

After you receive the notification of acceptance, revise your paper in
accordance with the comments from the referees.
The layout of
figures and tables should be fixed. After that, \textit{check your paper
again and again to completely remove description errors}.

Send \textit{both the {\LaTeX} file package and the hard copy} to the
IPSJ\@. The standard contents of the file package are .tex and .bbl. If
you include PostScript files and/or special style files, add them into
the package. Note that \textit{you must not split your source into
multiple .tex files} because it is hard for printers to access multiple
files when they modify your source. Also, carefully make sure that the
package contains all necessary files, especially special style files.

Details on the file transfer, including its destination and packaging
method, will be provided to you by the IPSJ secretariat.

%2.4
\subsection{Proofreading, Typesetting, and Publishing}

The IPSJ may change terms in your paper as per its standard, and the
printing house may modify your source to make it fit the standard
printing style.  Even if they make no changes, the result printed at the
printing house may be different from what you printed because of
differences in the {\LaTeX} execution environment.  Therefore, the
galley proofs of your paper will be sent to you so that you can check if
those modifications and/or differences are acceptable.  If not, correct
errors with red ink.  Note that \textit{this proofreading is not for
correcting your errors}, which should have been corrected before sending
the final version.

Your paper will be typeset after errors you notify us about (if any) are
corrected and will be published as part of the JIP.

%3
\section{Guide for Formatting a Paper}

The JIP, as opposed to conference proceedings, has a traditional and
\textit{stiff} style.  This makes the style files also \textit{stiff}
and strongly restricts customizability, which is one of the most useful
features of {\LaTeX}.  For example, you must not change \textit{style
parameters}, such as \verb+\texheight+.  It is not easy to show which
customizations are allowed, but the rule ``Don't tamper with it unless
you are confident'' should suffice.

Note that if you do something you should not, \textit{you may not have
error messages but simply unattractive results}.

The source file must use the following format.  Underlined parts can be
omitted from draft versions.

%4
\section{Configuration of Paper}
\label{body}

The source file must use the following format.  Underlined parts can be
omitted from draft versions.  Note that a few additional commands, shown
in A.1 of the Appendix, are available for a paper included in the
Transactions.

\vskip\baselineskip

\noindent
\|\documentclass[JIP]{ipsj}|\\
\quad Specify other option styles if necessary.\\
\quad Specify auxiliary styles with \|\usepackage|.\\
\\
\Underline{\|\setcounter{|{\bf volume}\|}{<volume>}|}\\
\Underline{\|\setcounter{|{\bf number}\|}{<number>}|}\\
\Underline{\|\setcounter{|{\bf page}\|}{<first-page>}|}\\
\Underline{\|\|{\bf received}\|{<year>}{<month>}{<day>}|}\\
\Underline{\|\|{\bf accepted}\|{<year>}{<month>}{<day>}|}\\
\quad Define your own macros if necessary.\\\\
\quad If you cannot use the \|txfonts| package, please do not use the following command\\
\Underline{\|\usepackage[varg]{txfonts}|}\\
\Underline{\|\makeatletter|}\\
\Underline{\|\input{ot1txtt.fd}|}\\
\Underline{\|\makeatother|}\\\\
\|\begin{document}|\\[.5em]
\|\title{<title>}|\\[.5em]
\Underline{\|\affiliate{<affiliation-label>}{<affiliation>}|}\\\\
\quad Declare current affiliation with \|\paffilabel| if necessary.\\
\Underline{\|\paffiliate{<affiliation-label>}{<affiliation>}|}\\\\
\Underline{\|\author{1st-author}{affiliation-label}[E-mail]|}\\
\Underline{\|\author{2nd-author}{affiliation-label}|}\\\\
\|\begin{abstract}|\\
\quad\|<abstract>|\\
\|\end{abstract}|\\\\
\|\begin{keyword}|\\
\quad\|<keyword>|\\
\|\end{keyword}|\\\\
\|\maketitle|\\\\
\|\section{|heading-of-1st-section\|}|\\
\dots\dots\dots\dots\dots\\
\quad \|<main text>|\\
\dots\dots\dots\dots\dots\\\\
\quad Put acknowledgments here with the acknowledgment environment if any.\\
\|\begin{acknowledgment}|\\
\|\end{acknowledgment}|\\\\
\|\begin{thebibliography}{99}%9 or 99|\\
\|\bibitem{1}|\\
\|\bibitem{2}|\\
\|\end{thebibliography}|\\\\
\quad Put appendices here following \|\appendix| if any.\\
\|\appendix|\\
\|\section{|heading-of-1st-section\|}|\\\\
\Underline{\|\begin{biography}|}\\
\Underline{\|\profile{<1st-author>}{<biography-of-1st-author>}|}\\
\Underline{\|\profile{<2nd-author>}{<biography-of-2nd-author>}|}\\
\Underline{\|\end{biography}|}\\
\|\end{document}|

%4.1
\subsection{Option Style}

The following six styles are available as optional arguments of the
\|\documentclass|.  If the JIP option is not used, the program will use
the standard Japanese paper style as the default.

\begin{enumerate}
\item\|JIP|\footnote{English should be used for the English version of the Transactions.}
\quad For English documents
\item\|invited| \quad For invited papers
\item\|sigrecommended| \quad For recommended papers
\item\|technote| \quad For technical notes
\item\|preface| \quad For the preface of an issue
\end{enumerate}

Any combination of these options can be used.

If you specify auxiliary style files with the
\|\usepackage|, you must include them in the file package when you send
your final version to the IPSJ\@.

However, style files included in the {\LaTeXe} standard distribution
(e.g., graphicx) may be omitted.  Note that style files may be
incompatible with the style of the Journal Transaction.

%4.1.1
\subsubsection{Optional style exclusively for technical reports}

In addition to the options described above, 
an option intended exclusively for technical reports is available.
\begin{quote}
\|techrep|\quad technical report
\end{quote}

If \|\documentclass[techrep,JIP]{ipsj}| is used,
the technical-report style will be applied.

%4.2
\subsection{Title, Author Names, etc.}

Describe the title of your paper, author names and affiliations, and
abstract using the commands and environment shown in Section~\ref{body}.
Then, perform \verb+\maketitle+ to automatically put them at the
appropriate position.  In the draft version, the title and abstract are
automatically printed onto separate pages, while author names and
affiliations are not printed in order to make your paper anonymous.

%4.2.1
\subsubsection{Title}

The title specified with \verb+\title+ is made centered.  Even if the
title is too long to fit onto one line, \textit{an automatic line break
is not performed}.  If your title is long, insert \verb+\\+ into the
appropriate positions to break the lines.  A multiple line title is
first flushed left and then centered with respect to the widest line.

The title also appears in the header of odd numbered pages.  If your
title is too long, provide a shortened title for the header to
\verb+\title+ as its optional argument as follows.

%4.2.2
\subsubsection{Author Name and Affiliation}

When indicating the affiliation of each author with a label (first
citation) and starting from the first author, by using \|\affiliate|,
numbered footnotes will be generated that show the affiliations.  When
several authors are affiliated with the same organization, the
affiliation needs to be indicated only once.  For the author's current
affiliation, use \|\paffiliate| and provide the label and affiliated
organization as before.  If the affiliated organization arguments are
entered as current and a line break is inserted using \|\\|, the author
name will be automatically defined by \|\author|.  Immediately after the
author's name, enter the affiliation label and the author's e-mail
address.

Where there are several authors, repeating \|\author| will generate
additional authors in sequence (two authors, three authors, and so
forth).

To add current affiliations or multiple affiliations, delineate the
affiliate label using commas to include additional data.

%4.2.3
\subsubsection{Abstract}

The abstract of your paper should only be used in the \verb+abstract+
environment.

%4.2.4
\subsubsection{Keywords}

The keywords of your paper should be included as the content for the
 \verb+keyword+ environment.

%4.3
\subsection{Main part}

%4.3.1
\subsubsection{Sectioning}

{\LaTeX} standard commands such as \|\section| and \|\sub-| \|section|
are available for sectioning. The section heading of \|\section|
occupies two lines, while others are put into one line.

%4.3.2
\subsubsection{Fixed Baselines}

Each page of the JIP is formatted with the double-column style.  The
printing tradition of double-column requires that a line in the left
column and its neighbor in the right column have the same baseline.  To
meet this requirement, the style files carefully control the progression
of baselines when a vertical space is inserted for section titles and so
on.

%4.3.3
\subsubsection{Font Size}

You will see that various size fonts are used in the printed result of
your paper.  Since these fonts are automatically and carefully chosen by
the style files, you are free from the headache of selecting proper
fonts.  In fact, it is strongly recommended not to use
font-size-changing commands such as \verb+\large+ and \verb+\small+ in
the main text because they are quite harmful to retaining fixed
baselines.

%4.3.4
\subsubsection{Itemizing}

There is no special format for itemization. You can use the standard
\|enumerate|, \|itemize|, \|description| environment.

%4.3.5
\subsubsection{Footnotes}

The command \|\footnote| produces footnotes with reference marks such as
\footnote{An example of footnote 1.} and \footnote{An example of
footnote 2.}.  When there is more than one footnote within a single
page, please note that it is necessary to run \LaTeX\ twice to process
them correctly.  Moreover, it is sometimes preferable to separate a
footnote and its mark into different columns.  This can be achieved
using the \|\footnotemark| and \|\footnotetext| commands. The footnote
numbering produced by \LaTeX\ is continuous throughout the paper; it
does not restart on each new page.

%4.3.6
\subsubsection{Overfulls and Underfulls}

The final result must be free from any overfulls.  It is well known that
almost all overfulls can be avoided with a little effort when writing
sentences.  For example, avoiding long in-text formulas and \|\verb| is
very effective.  However, tricks using the \|flushleft| environment,
\|\\|, or \|\linebreak| are not recommended because they cause quite
unattractive results.

For underfulls, you will conveniently get the following warning message,
\begin{quote}\footnotesize*
\|Underfull| \|\hbox| \|(badness 10000)| \|detected|
\end{quote}
by inserting \|\\| at the end of a paragraph.  This message is also
output when you use \|\\| just before a list-like environment, just
before an \|\item|, and at the end of the environment. Such underfulls
cause unattractive empty lines and a flood of warnings that will hide
important error messages.

%4.4
\subsection{Formulas}\label{sec:ITEM}

%4.4.1
\subsubsection{In-text Formulas}

In-text formulas may be surrounded by any proper math-open\slash close
pair, i.e. \|$| and \|$|, \|\(| and \|\)|, or \|\begin| and \|\end| for
the \|math| environment. Note that tall materials in in-text formulas,
such as \smash{$\frac{a}{b}$} (\|\frac{a}{b}|), are unattractive and
will disarrange the baseline progression.

%4.4.2
\subsubsection{Displayed Formulas}

Displayed formulas {\em must not be surrounded by the pair
\|$$|}.  Instead, use the \|\[| and \|\]| pair or one of the environments
\|displaymath|, \|equation|, or \|eqnarray|.  These commands\slash
environments indent formulas (not centered) and keep fixed baselines as
follows.
\begin{equation}
\Delta_l = \sum_{i=l+1}^L\delta_{pi}.
\end{equation}

%4.4.3
\subsubsection{Eqnarray environment}

For a sequence of two or more related formulas (equations), use the
\|eqnarray| environment to line them up at equal (or unequal) signs
instead of \|\[| \ \|\]| or the \|equation| environment.

%4.4.4
\subsubsection{Special Fonts}

It is strongly recommended to use only standard {\LaTeX} math
fonts.  Otherwise, you must report that you are using special fonts.

\begin{figure}[tb]%1
\setbox0\vbox{\it
\hbox{\|\begin{figure}[tb]|}
\hbox{\quad \|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure}\|}}
\centerline{\fbox{\box0}}
\caption{Single column figure with caption\\
explicitly broken by $\backslash\backslash$}
\label{fig:single}
\end{figure}

\begin{figure}[tb]%2
\begin{minipage}[t]{0.5\columnwidth}
\footnotesize
\setbox0\vbox{
\hbox{\|\begin{minipage}[t]%|}
\hbox{\|  {0.5\columnwidth}|}
\hbox{\|\captionType{table}|}
\hbox{\|\caption{| \ldots \|}|}
\hbox{\|\ecaption{| \ldots \|}|}
\hbox{\|\label{| \ldots \|}|}
\hbox{\|\makebox[\textwidth][c]{%|}
\hbox{\|\begin{tabular}[t]{lcr}|}
\hbox{\|\hline\hline|}
\hbox{\|left&center&right\\\hline|}
\hbox{\|L1&C1&R1\\|}
\hbox{\|L2&C2&R2\\\hline|}
\hbox{\|\end{tabular}}|}
\hbox{\|\end{minipage}|}}
\hbox{}
\centerline{\fbox{\box0}}
\caption{Contents of table \protect\ref{tab:right}}
\label{fig:left}
\end{minipage}%
\begin{minipage}[t]{0.5\columnwidth}
\CaptionType{table}
\caption{A table built by Fig.\ \protect\ref{fig:left}}
\label{tab:right}
\makebox[\textwidth][c]{\begin{tabular}[t]{lcr}\hline\hline
left&center&right\\\hline
L1&C1&R1\\
L2&C2&R2\\\hline
\end{tabular}}
\end{minipage}
\end{figure}

\begin{figure}[t]
\setbox0\vbox{\it
\hbox{\|\begin{figure}[tb]|}
\hbox{\quad \|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure}\|}}
\centerline{\fbox{\box0}}
\caption{Single column figure with caption\\
explicitly broken by $\backslash\backslash$}
\end{figure}

\begin{figure*}[t]
\setbox0\vbox{\large
\hbox{\|\begin{figure*}[t]|}
\hbox{\quad\|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure*}|}}
\centerline{\fbox{\hbox to.9\textwidth{\hss\box0\hss}}}
\caption{Double column figure}
\label{fig:double}
\end{figure*}

%4.5
\subsection{Figures}

A figure fit to one column is specified by the form shown in
\figref{fig:single}. Note that you must not specify the \|h| option.

The \|\caption| of a figure should be given below the figure body
together with a \|\label| command.  A long caption will be automatically
broken into two or more lines and centered with respect to the widest
line.  You can assist, however, with the line breaking by adding \|\\|
to obtain a more beautiful result, especially for two-line captions, as
shown in \figref{fig:single}.

If you want to rank two or more figures and/or tables in a \|figure| (or
\|table|) environment in order to save space, enclose each figure\slash
table and its \|\caption| in a \|minipage| environment as shown in
\figref{fig:left} and \tabref{tab:right}. Also, as in a \|figure|
environment, the caption for \tabref{tab:right} is correctly typeset
because the \|minipage| for it has the \|\captionType{table}| command to
specify the type of caption.  The command can of course be used with the
\|figure| argument to give a figure caption.

\Figref{fig:double} shows how to make a double column figure.

You may use any size font, as shown in \figref{fig:double}. Also, you
may include an encapsulated PostScript file (so called EPS file) as the
body of a figure. To include, use
%
\begin{quote}
\|\usepackage{graphicx}|
\end{quote}
%
in the preamble and put the \|\includegraphics| command where you wish
to embed the EPS graphics with its file name (and options if necessary).

You might have noticed that the first reference to \figref{fig:single}
is bold-faced, while the second and third are typed in roman fonts.
This font switching is a rule of the Journal\slash Transactions and will
be automatically performed if you use \|\figref{<|label\|>}| instead of
\|Fig.~\ref{<|label\|>}|.  Another rule is that ``Figure'' must be used
instead of ``Fig.''\ if the reference is the first word of a sentence,
such as was the first reference to \figref{fig:double} above.
Unfortunately, this switching is too hard to do automatically, so you
must use \|\figref{<|label\|>}| in such cases.

%4.6
\subsection{Tables}

A table with many rules is not very beautiful. \tabref{tab:example}
shows an example of a table with standard style rules. Note that the
uppermost rule is doubled, and no rules are drawn on the left and right
edges. The caption should be put above the table. The default font size
for tables is \|\footnotesize|. Any reference to a table should be made
using \|\tabref{<|label\|>}|.

\begin{table}[tb]
\caption{Sections and sub-sections in which list-like environments are used (example of table)}
\label{tab:example}
\hbox to\hsize{\hfil
\begin{tabular}{l|lll}\hline\hline
&enumerate&itemize&description\\\hline
type-1&	2 & 3 & 4.5 \\
type-2&	---& 4.11 & 4.7 \\
type-3&	2 & --- & 4.5\\
type-4&	--- & 4.8 & 4.3 \\\hline
\multicolumn{4}{l}{type-1\,: {\tt enumerate}, etc.\quad
	type-2\,: {\tt enumerate*}, etc.}\\
\multicolumn{4}{l}{type-3\,: {\tt Enumerate}, etc.\quad
	type-4\,: {\tt ENUMERATE}, etc.}\\
\end{tabular}\hfil}
\end{table}

%4.7
\subsection{Citations, Reference, Acknowledgements}

%4.7.1
\subsubsection{Citations}

The command \|\cite| is used to add citations in the text.  Cited labels
are sorted automatically and separated by using square brackets \|[ ]|.
Thus,
\begin{quote}
\|The paper \cite{companion,latex} is|\\
\|an overview of \LaTeX|.
\end{quote}
will produce
\begin{quote}
The paper \cite{companion,latex} is an overview of \LaTeX.
\end{quote}

%4.7.2
\subsubsection{List of References}

References should be arranged in alphabetical or cited order.
It is recommended to use BiB{\TeX} and style files 
\|ipsjsort-e.bst|
(alphabetical order) or \|ipsjunsort-e.bst| (cited order) to make
references fit to the traditional style.
Remember that you must include \|.bbl| file in the file package, instead of
\|.bib|.
If you cannot use BiB{\TeX} and have to make references manually using the
bibliography environment, observe the references of this guide carefully
and follow its style.

%4.7.3
\subsubsection{Acknowledgments and Appendices}

If you want to acknowledge people, put your acknowledgments just before
the references and enclose them in the \|acknowledgment| environment.

Appendices, if there are any, should be put just after the references
and \|\appendix| command.  Sectioning commands produces headings like
{\bf \ref{A1}}, {\bf \ref{A2}}, and so on in the appendices.

%4.8
\subsection{Biography}

Biographies of authors are positioned at the end of the document, just
before \|\end{document}|, as follows.
%
\begin{quote}
\|\begin{biography}|\\
\|\profile{<|1st-author's-name\|>}|\\
\mbox{}\quad\|{<|biography-of-1st-author\|>}|\\
\|\author{<|2nd-author's-name\|>}|\\
\mbox{}\quad\|{<|biography-of-2nd-author\|>}|\\
\mbox{}\quad $\ldots\ldots\ldots$ \\
\|\end{biography}|
\end{quote}

Generally, photographs used in author biographies should be identification photographs.

The printers will crop these photographs to a size of 30\,mm by 25\,mm. 
Avoid using photographs that contain missing portions of the face or photographs 
in which the outline of the face is difficult to distinguish against the background. 
It is recommended to use photographs that have no background or that 
have light-colored backgrounds. 
When digitally submitting photographs for the author biography, 
the photograph must have a resolution of at least 300\,dpi and must 
have been captured using a camera with at least one megapixel resolution. 
Since photographs for the author biographies will be incorporated into 
digital data by the printers at the time the composition is prepared, 
it is not necessary to digitally insert the photographs into the draft.

%5
\section{Check List of ``Dos and Don'ts''}

%5.1
\subsection{The basics of writing}

\begin{itemize}
\item[$\Box$] Describe a paper so that readers understand the novelty,
	      availability, and reliability of the research.
\item[$\Box$] Try to make a paper easy to read (discontinuity in the
	      story and obscure backgrounds or themes are a burden to
	      readers). 
\item[$\Box$] Revisit the paper if the problem to be solved is not
	      generalized (entirely focused on a problem at XX
	      University, etc.) or if the paper reports deliverables
	      only and does not describe the problem itself. 
\item[$\Box$] Rethink the paper if its conclusion is not clearly
	      described, it does not adequately point out its
	      applicability, limits, and controversial points, or its
	      conclusion does not follow the contents. 
\item[$\Box$] Expressions that are inappropriate for scientific papers
	      and that are hard to understand should be reconsidered. 
\item[$\Box$] Second thought is necessary if sentences are in colloquial
	      style. 
\item[$\Box$] Check the structure of chapters and sections and the
	      organization of the paper. 
\item[$\Box$] Do not make the paper so that grasping the meaning is
	      difficult without guessing from the context. 
\item[$\Box$] Confirm if the explanation of the hypotheses is enough and
	      does not contain any gaps in meaning. 
\item[$\Box$] The authors should not submit a manuscript that includes
	      redundant and/or too brief descriptions.
\item[$\Box$] The authors should eliminate undefined terminologies.
\end{itemize}

%5.2
\subsection{Show novelty and usefulness clearly}

\begin{itemize}
\item[$\Box$] The authors should not submit a manuscript that does not
	      clarify the motivation and the goal of their study and the
	      relationship to other existing studies.
\item[$\Box$] The authors should not submit a manuscript that does not
	      clarify what technologies are well/publicly known and what
	      idea they are newly/originally proposing. 
\item[$\Box$] The authors should provide sufficient references in their
	      manuscript to back up the originality of their study. 
\item[$\Box$] The authors should not submit a manuscript in which the
	      readers cannot understand their proposal (or cannot find
	      any originality in it) because it consists entirely of
	      abstractive and/or conceptual descriptions. 
\item[$\Box$] The authors should not submit a manuscript that lacks
	      discussions on the effectiveness of their proposal. 
\end{itemize}

%5.3
\subsection{Concrete attention to writing}

\begin{itemize}
\item[$\Box$] The authors should not submit a manuscript whose Japanese
	      title does not match its content correctly.
\item[$\Box$] The authors should not submit a manuscript whose English
	      title does not match its content correctly or that
	      contains incorrect English usage.
\item[$\Box$] The paper should be revised when its abstract does not
	      show its purpose or is written in inadequate English.
\item[$\Box$] The paper should be revised when symbols and abbreviations
	      are not popular, wordings are not adequate, or the
	      explanations of its pictures and tables are not adequate.
\item[$\Box$] The paper should be revised when special wordings, which
	      are popular only in an individual or local group or a
	      small company, are used without any explanations.
\item[$\Box$] The paper should be revised when its pictures or tables
	      are not semantically clear or they contain mistakes.
\item[$\Box$] The paper should be revised when its pictures or tables
	      are not visually clear.
\item[$\Box$] The paper should be revised when the size or the scale of
	      its pictures or tables are not adequate.
\end{itemize}

%5.4
\subsection{Regarding references}

\begin{itemize}
\item[$\Box$] The number of references should be more than 10 (Some
	      opinions say more than 20 or 30 in some research areas.
\item[$\Box$] A sufficient number of references are required to show the
	      paper's novelty.
\item[$\Box$] The paper should be revised when it has an insufficient
	      number of references.
\item[$\Box$] Referring to appropriate papers written by Japanese
	      authors contributes to the further progression of the
	      Japanese research community.
\item[$\Box$] Do not include self-citations excessively.
\end{itemize}

%5.5
\subsection{Double submission}

\begin{itemize}
\item[$\Box$] Double submission of the original paper is
	      prohibited. However, it is permissible to submit a paper
	      accepted at an international conference and free from
	      copyright issues.
\item[$\Box$] Do not use the same figures or charts already included in
	      other original papers, except those that have proper
	      citations.
\item[$\Box$] Be careful not to have overlap between the paper and other
	      published articles.
\end{itemize}

%5.6
\subsection{Check by other researchers}

\begin{itemize}
\item[$\Box$] Proofreading by experienced persons with many accepted
	      papers is strongly recommended.
\item[$\Box$] Take care to avoid leaps of logic from the viewpoint of
	      the readers.
\end{itemize}

%5.7
\subsection{Miscellaneous}

\begin{itemize}
\item[$\Box$] After the first review round, do not modify the paper
	      except for the stated conditions for acceptance without
	      the reviewers' approval.

\item[$\Box$] The authors cannot select reviewers.

\item[$\Box$] Fill the self-check sheet carefully before submitting the
	      paper.
\end{itemize}

\newpage%%

%6
\section{Concluding Remarks}

We dare not dream that the style files are perfect but rather wish to
improve them with your cooperation and hope that you will let us know of
any complaints, comments, suggestions by e-mail to: 
\begin{quote}
\|editt@ipsj.or.jp|.
\end{quote}

\begin{acknowledgment}
We wrote this article based on the guideline for A4 landscape layout.
We are grateful to Prof.\ Hiroshi Nakashima from Kyoto University,
for his valuable comments on making a class-file, 
and his consent to usage of BiB{\TeX} files.
We are also very thankful to the editorial committee for their
contributions in writing the guideline for the A4 landscape layout.
\end{acknowledgment}

\begin{thebibliography}{99}
\bibitem{companion}%1
Goossens, M., Mittelbach, F. and Samarin, A.:
{\it The LaTeX Companion},
Addison Wesley, Reading, 
Massachusetts (1993).

\bibitem{latex}%2
Lamport, L.: 
{\it A Document Preparation System {\LaTeX} User's Guide \& Reference Manual}, 
Addison Wesley, Reading, Massachusetts (1986).

\bibitem{article1}%3
Itoh, S. and Goto, N.: 
An Adaptive Noiseless Coding for Sources with Big Alphabet Size, 
{\it Trans.\ IEICE},  
Vol.E74, No.9, pp.2495--2503 (1991).

\bibitem{article2}%4
Abrahamson, K., Dadoun, N., Kirkpatrick, D.G. and Przytycka, T.: 
A Simple Parallel Tree Contraction Algorithm, 
{\it J.\ Algorithms},  
Vol.10, No.2,
pp.287--302 (1989).

\bibitem{article3}%5
Yamakami, T.: Exploratory Session Analysis in the Mobile Clickstream, 
{\it IPSJ Digital Courier},  
Vol.3, pp.14--20 (online), \\
\doi{10.2197/ipsjdc.3.14} (2007).

\bibitem{book1}%6
Foley, J.D. et al.: 
Computer Graphics --- Principles and Practice, 
System Programming Series, Addison-Wesley, 
Reading, Massachusetts, 2nd edition (1990).

\bibitem{book2}%7
Chang, C.L. and Lee, R.C.T.: 
Symbolic Logic and Mechanical Theorem Proving, 
Academic Press, New York (1973).

\bibitem{booklet1}%8
{Institute for New Generation Computer Technology}: 
Overview of the Fifth Generation Computer Project, 
distributed in {FGCS'92} (1992).
(in Japanese).

\bibitem{inbook1}%9
Knuth, D.E.: 
Art of Computer Programming,
{\it Fundamental Algorithms}, 
Vol.1, chapter 2, 
pp.371--381, 
Addison-Wesley, 2nd edition (1973).

\bibitem{incollection1}%10
Schwartz, A.J.: 
Subdividing B{\'e}zier Curves and Surfaces, 
{\it Geometric Modeling: Algorithms and New Trends\/} 
(Farin, G.E., ed.), 
SIAM, Philadelphia,
pp.55--66 (1987).

\bibitem{inproceedings1}%11
Baraff, D.:
Curved Surfaces and Coherence for Non-penetrating Rigid Body
Simulation, 
{\it Proc.\ SIGGRAPH '90\/} (Beach, R.J., ed.), 
Dallas,
Texas, ACM, Addison-Wesley, 
pp.19--28 (1990).

\bibitem{inproceedings2}%12
Nakashima, H. et al.: 
OhHelp: A Scalable Domain-Decomposing Dynamic Load
Balancing for Particle-in-Cell Simulations, 
{\it Proc.\ Intl.\ Conf. Supercomputing}, 
pp.90--99 (online),\\
\doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).

\bibitem{manual1}%13
Adobe Systems Inc.: 
{\it PostScript Language Reference Manual}, 
Reading,
Massachusetts (1985).

\bibitem{mastersthesis1}%14
Ohno, K.: 
Efficient Message Communication of Concurrent Logic Programming
Language KL1 Based on Static Analysis, 
Master's thesis, 
Dept.\ Information Science, Kyoto University (1995).

\bibitem{misc1}%15
Saito, Y. and Nakashima, H.: 
{\tt ipsjpapers.sty} (1995).
(Style file for Trans. IPSJ distributed to authors.).

\bibitem{phdthesis1}%16
Weihl, W.: 
Specification and Implementation of Atomic Data Types, 
PhD Thesis,
MIT, Boston (1984).

\bibitem{proceedings1}%17
Institute for New Generation Computer Technology: 
{\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
Vol.1 (1992).

\bibitem{WarD:WAM-1}%18
Warren, D.H.D.: An Abstract {Prolog} Instruction Set, 
Technical Report 309,
Artificial Intelligence Center, 
SRI International (1983).

\bibitem{unpublished}%19
Editorial Board of Trans.\ IPSJ:
How to Typeset Your Papers in {\LaTeX}
(Version 1) (1995).
(distributed to authors).

\bibitem{webpage1}%20
Kay, A.: Welcome to Squeakland, Squeakland (online),\\
\urle{http://www.squeakland.org/community/biography/\\
alanbio.html}
\refdatee{2007-4-5}.

\bibitem{webpage2}%21
Nakashima, H.: 
A {WEB} Page, Kyoto University (online),\\
\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
a.web.page.of.long.url/}
\refdatee{2010-10-30}.

\bibitem{webpage3}%22
Nakashima, H.: 
Another {WEB} Page, 
Kyoto University (online),\\
\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
a.web.page.of.much.longer.url/} 
\refdatee{2010-10-30}.

\end{thebibliography}

\appendix

%A.1
\section{How to Write an Appendix}
\label{A1}

To add an appendix, write the command \|\appendix| immediately following
the reference list.  Within the appendix, the \|\section| command creates
numbered headings such as \ref{A1} and \ref{A2}.

%A.1.1
\subsection{Example of a Heading}
The command \|\subsection| in the appendix gives this kind of heading.

%A.2
\section{Commands for Transactions}
\label{A2}

Each transaction has its own subtitle, abbreviation code, and serial
number. This information is given by using the following commands for
the \|\documentclass| option in the final version.

\begin{itemize}
\item \|PRO| (Trans.\ Programming)
\item \|TOM| (Trans.\ Mathematical Modeling and Its Applications)
\item \|TOD| (Trans.\ Database)
\item \|ACS| (Trans.\ Advanced Computing Systems)
\item \|CDS| (Trans.\ Consumer Device \& System)
\item \|DC | (Trans.\ Digital Content)
\item \|TCE| (Trans.\ Computer and Education)
\item \|TBIO| (Bioinformatics)
\item \|SLDM| (System LSI Design Methodology)
\item \|CVA| (Computer Vision and Applications)
\end{itemize}

Moreover, for papers in English, the command \|english| can be added. For
example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
English document.

Note that the research group has a ``month of publication'' number that
does not correspond to the ``issue month number'' of the
transaction. You may be notified by the IPSJ or the Editorial Board of
the \|<month>| in order to set the month of publication counter as
follows.

\begin{quote}
\|\setcounter{month}{month of publication}|
\end{quote}

In addition, commands are provided for executing unique functions for
several transactions, as shown in the following sections.

%A.3
\section{Unique Commands for Each Part}

Since each of the parts has its own detailed specifications, the same
command may produce different results in two different parts.

In some cases, the \|<Revised date>| and \|<Second revised| \|date>| are
inputted. These can be added as a preamble by using

\begin{quote}
\|\rereceived{<year>}{<month>}{<day>}|\\
\|\rerereceived {<year>}{<month>}{<day>}|
\end{quote}

%A.3.1
\subsection{Unique Functions for Programming (PRO)}

Issues of Transactions on Programming (PRO) includes not only regular
papers but also abstracts from research presentations delivered in the
research groups of SIGPRO\@. The file for an abstract consists of
material from the \|\documentclass| to the \maketitle of the format
shown in Section~\ref{body}. That is, the file does not have a main
text. Note that the reception and acceptance dates are not required, but
the date of presentation has to be given:
\begin{quote}
\|\Presented{<year>}{<month>}{<day>}|
\end{quote}

%A.3.2
\subsection{Unique Functions for Database (TOD)}

The name of the editor in charge for the paper included in The
Transactions on Database (TOD) is specified by
\begin{quote}
\|\edInCharge{<name-of-editor>}|
\end{quote}

Also, following a change in style, the command is entered at the end of
the paper, directly before \|\end{document}|.

%A.3.3
\subsection{Unique Functions for Consumer Devices \& Systems (CDS)}

In the ``Transactions on Consumer Devices \& Systems,'' since the
headings differ depending on the type of document, the type of heading
is to be changed with the option.

The types are:
\begin{itemize}
\item \|systems  | Paper on Consumer Systems
\item \|services | Paper on Consumer Services
\item \|devices  | Paper on Consumer Devices
\item \|Research | Research Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.4
\subsection{Unique Functions for Digital Content (DCON)}

In the ``Transactions on Digital Content,'' since the
headings differ depending on the type of document, the type of heading
is to be changed with the option.

The types are:
\begin{itemize}
\item \|Research | Research Paper
\item \|Practice | Practice Paper
\item \|Content  | Content Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.5
\subsection{Unique Functions for Computer and Education (TCE)}

In the ``Transactions on Computer and Education,'' since the headings
differ depending on the type of document, the type of heading is
to be changed with the option.

The types are:
\begin{itemize}
\item \|No specification  | Regular Paper (Default)
\item \|Short             | Short Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.6
\subsection{Unique Functions for Bioinformatics (TBIO)}

Since papers in Transactions on Bioinformatics (TBIO) are in English,
specifying the TBIO option will cause the program to assume that the
English option has been specified. This effectively means that the
English option can be omitted.

The following three categories define the different types of papers.
\begin{itemize}
\item \|No specification | Original Paper (Default)
\item \|Data             | Database/Software Paper
\item \|Survey           | Survey Paper
\end{itemize}

Therefore, \|\documentclass[TBIO]{ipsj}| will be an original paper, and
\|\documentclass[TBIO,Survey]{ipsj}| will be a survey paper.

Moreover, as with TOD, the name of the editor in charge of the paper is
specified by using \|\Editor|, but in this case, the text is introduced with ``Communicated by.'' Therefore, the name of the editor is positioned directly before \|\end{document}|, as with TOD.

%A.3.7
\subsection{Unique Functions for Computer Vision and Applications (CVA)}

The Transactions of Computer Vision and Applications is also an English
language journal, allowing the English option to be omitted.

There are three classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Research         | Research Paper
\item \|system           | Systems Paper
\item \|Express          | Express Paper
\end{itemize}

As with TBIO, the name of the editor in charge is inserted, and the
inserted text is introduced with ``Communicated by.''

%A.3.8
\subsection{Unique Functions for System LSI Design Methodology (SLDM)}

The Transactions of System LSI Design and Methodology (SLDM) is also an
English language journal, allowing the English option to be omitted.

There are two classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Short            | Short Paper
\end{itemize}

SDLM also enters the name of the editor in charge, but automatic
insertion is treated differently depending on the paper.

Normally, text is inserted using ``Recommended by Associate Editor:,''
but it is only when the ``invited'' option is included that the
insertion text becomes ``Invited by Editor-in-Chief:.''

\begin{biography}
\profile{Taro Joho}{was born in 1970. He received his M.S.\ degree from
Johoshori University in 1994.
He joined
the Information
Processing Society of Japan in 1994.
He is currently an associate professor at
\mbox{Johoshori} University.
His research interest is online
publishing systems. He is a member of the IEEE and ACM\@.}
%
\profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
became an associate professor at Gakkai University in 1992 and a
professor at Johoshori University in 1997. Her current research
interest is online publishing systems. She received the Kiyasu Kinen
award in 2010. She is a Board Member of the IPSJ and a member of the
IEICE, IEEE-CS, and ACM\@.} 
%
\profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
from Johoshori University in 1994 and has been engaged in the
Information Processing Society of Japan since 1994. His research
interest is online publishing systems. He is a member of the IEEE and
ACM\@.}
%
\end{biography}
\end{document}

### 2017-11-06 ipsj/paper.tex
Create a base file

@@
 
-\title{How to Prepare Your Papers for the JIP\\
-(ipsj.cls version 1.7)}
+\title{Component-based Software Development Framework \\for Embedded IoT Devices}
 
-\affiliate{IPSJ}{Information Processing Society of Japan, 
-Chiyoda, Tokyo 101--0062, Japan}
-\affiliate{JU}{Johoshori University, Chiyoda, Tokyo 101--0062, Japan}
-\paffiliate{PJU}{Johoshori University}
+\affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
+\affiliate{NAGOYA}{Graduate School of Information Science, Nagoya University}
+\affiliate{OKUMA}{OKUMA Corporation}
 
-\author{Taro Joho}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
-\author{Hanako Shori}{JU}[shori.hanako@johosyori-u.ac.jp]
-\author{Jiro Gakkai}{IPSJ}
+\author{Takuro Yamamoto}{OSAKA}
+\author{Takuma Hara}{NAGOYA}
+\author{Takuya Ishikawa}{NAGOYA}
+\author{Hiroshi Oyama}{OKUMA}
+\author{Hiroaki Takada}{NAGOYA}
+\author{Takuya Azumi}{OSAKA}
 
 \begin{abstract}
-This document is a guide for preparing drafts to be submitted to the
-Journal of Information Processing (JIP) and for the final camera-ready
-manuscripts of papers to appear in the JIP that use \LaTeX and special
-style files.  Since this document itself is produced with these style
-files, it will help you to refer to its source file, which is
-distributed with these style files.
+
 \end{abstract}
@@
 \begin{keyword}
-Journal of Information Processing, \LaTeX, style files, ``Dos and
- Don'ts'' list
+
 \end{keyword}
@@
 
-The Information Processing Society of Japan (IPSJ) publishes Journal of
-Information Processing (JIP) as its flagship international journal.
-Thus far, the JIP adopted the landscape A4 format for publishing papers,
-but it has changed this format to the portrait A4 format because of many
-requests from authors.  Corresponding to this format change, the JIP
-accepts the portrait A4 format for submitting papers.
-
-Following with this change, we, the Editorial Board of the JIP, prepared
-a new style file for \LaTeX\@.  In this manuscript, we first describe
-the usage of the style file.  The basic strategy of the new style file
-is to require no special knowledge of command usage that does not use
-standard \LaTeX commands.  Authors of a paper can use standard \LaTeX
-commands to keep within the formatting restrictions of the paper, such
-as setting space pitches and margins.  The guideline of the paper format
-will be described in Section~\ref{body}.  Since this manuscript itself
-also is written with the style file, we hope it will help with writing a
-paper.
-
-The Editorial Board of the JIP has also prepared a ``Dos and Don'ts''
-list of matters an author should consider while writing a paper.  We
-have added the list to the latter portion of this manuscript.  Please
-use the list as a checklist for preparing to submit a paper.
-
 %2
-\section{Flow from Submission to Publishing}
-%2.1
-\subsection{Preparation}
-
-The JIP author's kit including the \LaTeX style files can be downloaded
-from the following URL:
-\begin{quote}
- \small
- \|http://www.ipsj.or.jp/jip/submit/style.html|
-\end{quote}
-The kit includes the following files:
-\begin{enumerate}
-\item \|ipsj.cls|: style file for ipsj journals
-\item \|ipsjpref.sty|: style for the foreword
-\item \|jsample.tex|: source for the Japanese version of this guide
-\item \|esample.tex|: source of this guide
-\item \|ipsjsort-e.bst|: bibtex style (sorted)
-\item \|ipsjunsrt-e.bst|: bibtex style (unsorted)
-\item \|bibsample.bib|: sample of bibliographic data (Japanese)
-\item \|ebibsample.bib|: sample of bibliographic data (English)
-
-\item \|ipsjtech.sty|: style file for technical report
-\item \ \|tech-jsample.tex|: source for the Japanese version of technical report
-\item \ \|tech-esample.tex|: source for the English version of technical report
-\end{enumerate}
-
-Since the kit has variants corresponding to multiple platforms,
-including UNIX workstations, Windows (DOS), and Macintosh machines, an
-appropriate variant can be selected and unpacked on the target
-platform.
-
-Since {\LaTeXe} is required as an execution environment, please install
-it.
-
-Regarding manuscripts written with Microsoft Word, a corresponding
-company will convert them into \LaTeX\@.  This means that the Microsoft
-Word format is used just a reference.
-
-\footnotetext{The real author is the Editorial Board of JIP.}
-
-%2.2
-\subsection{Draft Submission}
-
-First, generate a PDF file from your \LaTeX source and style file under
-your {\LaTeXe} environment and check that the generated PDF file can be
-read with the Adobe PDF reader.  After that, register your email address
-into the Paper Review Management System (PRMS) through the following
-URL:
-\begin{quote}
- \small
- \|https://www.ipsj.or.jp/prms/author_pre_submit.do|
-\end{quote}
-
-\noindent
-The system will return an email including another URL for submitting
-your paper. The manual for submission via the PRMS is available at the
-following URL: 
-\begin{quote}
- \small
- \|http://www.ipsj.or.jp/jip/submit/manual/|\\
- \|e_manual.html|
-\end{quote}
-
-The JIP adopts \textit{single blind review}, 
-where you will not know reviewers names.
-
-%2.3
-\subsection{Final Version}
-
-After you receive the notification of acceptance, revise your paper in
-accordance with the comments from the referees.
-The layout of
-figures and tables should be fixed. After that, \textit{check your paper
-again and again to completely remove description errors}.
-
-Send \textit{both the {\LaTeX} file package and the hard copy} to the
-IPSJ\@. The standard contents of the file package are .tex and .bbl. If
-you include PostScript files and/or special style files, add them into
-the package. Note that \textit{you must not split your source into
-multiple .tex files} because it is hard for printers to access multiple
-files when they modify your source. Also, carefully make sure that the
-package contains all necessary files, especially special style files.
-
-Details on the file transfer, including its destination and packaging
-method, will be provided to you by the IPSJ secretariat.
-
-%2.4
-\subsection{Proofreading, Typesetting, and Publishing}
-
-The IPSJ may change terms in your paper as per its standard, and the
-printing house may modify your source to make it fit the standard
-printing style.  Even if they make no changes, the result printed at the
-printing house may be different from what you printed because of
-differences in the {\LaTeX} execution environment.  Therefore, the
-galley proofs of your paper will be sent to you so that you can check if
-those modifications and/or differences are acceptable.  If not, correct
-errors with red ink.  Note that \textit{this proofreading is not for
-correcting your errors}, which should have been corrected before sending
-the final version.
-
-Your paper will be typeset after errors you notify us about (if any) are
-corrected and will be published as part of the JIP.
+\section{System Model}
 
 %3
-\section{Guide for Formatting a Paper}
-
-The JIP, as opposed to conference proceedings, has a traditional and
-\textit{stiff} style.  This makes the style files also \textit{stiff}
-and strongly restricts customizability, which is one of the most useful
-features of {\LaTeX}.  For example, you must not change \textit{style
-parameters}, such as \verb+\texheight+.  It is not easy to show which
-customizations are allowed, but the rule ``Don't tamper with it unless
-you are confident'' should suffice.
-
-Note that if you do something you should not, \textit{you may not have
-error messages but simply unattractive results}.
-
-The source file must use the following format.  Underlined parts can be
-omitted from draft versions.
+\section{Proposed Framework}
 
 %4
-\section{Configuration of Paper}
-\label{body}
-
-The source file must use the following format.  Underlined parts can be
-omitted from draft versions.  Note that a few additional commands, shown
-in A.1 of the Appendix, are available for a paper included in the
-Transactions.
-
-\vskip\baselineskip
-
-\noindent
-\|\documentclass[JIP]{ipsj}|\\
-\quad Specify other option styles if necessary.\\
-\quad Specify auxiliary styles with \|\usepackage|.\\
-\\
-\Underline{\|\setcounter{|{\bf volume}\|}{<volume>}|}\\
-\Underline{\|\setcounter{|{\bf number}\|}{<number>}|}\\
-\Underline{\|\setcounter{|{\bf page}\|}{<first-page>}|}\\
-\Underline{\|\|{\bf received}\|{<year>}{<month>}{<day>}|}\\
-\Underline{\|\|{\bf accepted}\|{<year>}{<month>}{<day>}|}\\
-\quad Define your own macros if necessary.\\\\
-\quad If you cannot use the \|txfonts| package, please do not use the following command\\
-\Underline{\|\usepackage[varg]{txfonts}|}\\
-\Underline{\|\makeatletter|}\\
-\Underline{\|\input{ot1txtt.fd}|}\\
-\Underline{\|\makeatother|}\\\\
-\|\begin{document}|\\[.5em]
-\|\title{<title>}|\\[.5em]
-\Underline{\|\affiliate{<affiliation-label>}{<affiliation>}|}\\\\
-\quad Declare current affiliation with \|\paffilabel| if necessary.\\
-\Underline{\|\paffiliate{<affiliation-label>}{<affiliation>}|}\\\\
-\Underline{\|\author{1st-author}{affiliation-label}[E-mail]|}\\
-\Underline{\|\author{2nd-author}{affiliation-label}|}\\\\
-\|\begin{abstract}|\\
-\quad\|<abstract>|\\
-\|\end{abstract}|\\\\
-\|\begin{keyword}|\\
-\quad\|<keyword>|\\
-\|\end{keyword}|\\\\
-\|\maketitle|\\\\
-\|\section{|heading-of-1st-section\|}|\\
-\dots\dots\dots\dots\dots\\
-\quad \|<main text>|\\
-\dots\dots\dots\dots\dots\\\\
-\quad Put acknowledgments here with the acknowledgment environment if any.\\
-\|\begin{acknowledgment}|\\
-\|\end{acknowledgment}|\\\\
-\|\begin{thebibliography}{99}%9 or 99|\\
-\|\bibitem{1}|\\
-\|\bibitem{2}|\\
-\|\end{thebibliography}|\\\\
-\quad Put appendices here following \|\appendix| if any.\\
-\|\appendix|\\
-\|\section{|heading-of-1st-section\|}|\\\\
-\Underline{\|\begin{biography}|}\\
-\Underline{\|\profile{<1st-author>}{<biography-of-1st-author>}|}\\
-\Underline{\|\profile{<2nd-author>}{<biography-of-2nd-author>}|}\\
-\Underline{\|\end{biography}|}\\
-\|\end{document}|
-
-%4.1
-\subsection{Option Style}
-
-The following six styles are available as optional arguments of the
-\|\documentclass|.  If the JIP option is not used, the program will use
-the standard Japanese paper style as the default.
-
-\begin{enumerate}
-\item\|JIP|\footnote{English should be used for the English version of the Transactions.}
-\quad For English documents
-\item\|invited| \quad For invited papers
-\item\|sigrecommended| \quad For recommended papers
-\item\|technote| \quad For technical notes
-\item\|preface| \quad For the preface of an issue
-\end{enumerate}
-
-Any combination of these options can be used.
-
-If you specify auxiliary style files with the
-\|\usepackage|, you must include them in the file package when you send
-your final version to the IPSJ\@.
-
-However, style files included in the {\LaTeXe} standard distribution
-(e.g., graphicx) may be omitted.  Note that style files may be
-incompatible with the style of the Journal Transaction.
-
-%4.1.1
-\subsubsection{Optional style exclusively for technical reports}
-
-In addition to the options described above, 
-an option intended exclusively for technical reports is available.
-\begin{quote}
-\|techrep|\quad technical report
-\end{quote}
-
-If \|\documentclass[techrep,JIP]{ipsj}| is used,
-the technical-report style will be applied.
-
-%4.2
-\subsection{Title, Author Names, etc.}
-
-Describe the title of your paper, author names and affiliations, and
-abstract using the commands and environment shown in Section~\ref{body}.
-Then, perform \verb+\maketitle+ to automatically put them at the
-appropriate position.  In the draft version, the title and abstract are
-automatically printed onto separate pages, while author names and
-affiliations are not printed in order to make your paper anonymous.
-
-%4.2.1
-\subsubsection{Title}
-
-The title specified with \verb+\title+ is made centered.  Even if the
-title is too long to fit onto one line, \textit{an automatic line break
-is not performed}.  If your title is long, insert \verb+\\+ into the
-appropriate positions to break the lines.  A multiple line title is
-first flushed left and then centered with respect to the widest line.
-
-The title also appears in the header of odd numbered pages.  If your
-title is too long, provide a shortened title for the header to
-\verb+\title+ as its optional argument as follows.
-
-%4.2.2
-\subsubsection{Author Name and Affiliation}
-
-When indicating the affiliation of each author with a label (first
-citation) and starting from the first author, by using \|\affiliate|,
-numbered footnotes will be generated that show the affiliations.  When
-several authors are affiliated with the same organization, the
-affiliation needs to be indicated only once.  For the author's current
-affiliation, use \|\paffiliate| and provide the label and affiliated
-organization as before.  If the affiliated organization arguments are
-entered as current and a line break is inserted using \|\\|, the author
-name will be automatically defined by \|\author|.  Immediately after the
-author's name, enter the affiliation label and the author's e-mail
-address.
-
-Where there are several authors, repeating \|\author| will generate
-additional authors in sequence (two authors, three authors, and so
-forth).
-
-To add current affiliations or multiple affiliations, delineate the
-affiliate label using commas to include additional data.
-
-%4.2.3
-\subsubsection{Abstract}
-
-The abstract of your paper should only be used in the \verb+abstract+
-environment.
-
-%4.2.4
-\subsubsection{Keywords}
-
-The keywords of your paper should be included as the content for the
- \verb+keyword+ environment.
-
-%4.3
-\subsection{Main part}
-
-%4.3.1
-\subsubsection{Sectioning}
-
-{\LaTeX} standard commands such as \|\section| and \|\sub-| \|section|
-are available for sectioning. The section heading of \|\section|
-occupies two lines, while others are put into one line.
-
-%4.3.2
-\subsubsection{Fixed Baselines}
-
-Each page of the JIP is formatted with the double-column style.  The
-printing tradition of double-column requires that a line in the left
-column and its neighbor in the right column have the same baseline.  To
-meet this requirement, the style files carefully control the progression
-of baselines when a vertical space is inserted for section titles and so
-on.
-
-%4.3.3
-\subsubsection{Font Size}
-
-You will see that various size fonts are used in the printed result of
-your paper.  Since these fonts are automatically and carefully chosen by
-the style files, you are free from the headache of selecting proper
-fonts.  In fact, it is strongly recommended not to use
-font-size-changing commands such as \verb+\large+ and \verb+\small+ in
-the main text because they are quite harmful to retaining fixed
-baselines.
-
-%4.3.4
-\subsubsection{Itemizing}
-
-There is no special format for itemization. You can use the standard
-\|enumerate|, \|itemize|, \|description| environment.
-
-%4.3.5
-\subsubsection{Footnotes}
-
-The command \|\footnote| produces footnotes with reference marks such as
-\footnote{An example of footnote 1.} and \footnote{An example of
-footnote 2.}.  When there is more than one footnote within a single
-page, please note that it is necessary to run \LaTeX\ twice to process
-them correctly.  Moreover, it is sometimes preferable to separate a
-footnote and its mark into different columns.  This can be achieved
-using the \|\footnotemark| and \|\footnotetext| commands. The footnote
-numbering produced by \LaTeX\ is continuous throughout the paper; it
-does not restart on each new page.
-
-%4.3.6
-\subsubsection{Overfulls and Underfulls}
-
-The final result must be free from any overfulls.  It is well known that
-almost all overfulls can be avoided with a little effort when writing
-sentences.  For example, avoiding long in-text formulas and \|\verb| is
-very effective.  However, tricks using the \|flushleft| environment,
-\|\\|, or \|\linebreak| are not recommended because they cause quite
-unattractive results.
-
-For underfulls, you will conveniently get the following warning message,
-\begin{quote}\footnotesize*
-\|Underfull| \|\hbox| \|(badness 10000)| \|detected|
-\end{quote}
-by inserting \|\\| at the end of a paragraph.  This message is also
-output when you use \|\\| just before a list-like environment, just
-before an \|\item|, and at the end of the environment. Such underfulls
-cause unattractive empty lines and a flood of warnings that will hide
-important error messages.
-
-%4.4
-\subsection{Formulas}\label{sec:ITEM}
-
-%4.4.1
-\subsubsection{In-text Formulas}
-
-In-text formulas may be surrounded by any proper math-open\slash close
-pair, i.e. \|$| and \|$|, \|\(| and \|\)|, or \|\begin| and \|\end| for
-the \|math| environment. Note that tall materials in in-text formulas,
-such as \smash{$\frac{a}{b}$} (\|\frac{a}{b}|), are unattractive and
-will disarrange the baseline progression.
-
-%4.4.2
-\subsubsection{Displayed Formulas}
-
-Displayed formulas {\em must not be surrounded by the pair
-\|$$|}.  Instead, use the \|\[| and \|\]| pair or one of the environments
-\|displaymath|, \|equation|, or \|eqnarray|.  These commands\slash
-environments indent formulas (not centered) and keep fixed baselines as
-follows.
-\begin{equation}
-\Delta_l = \sum_{i=l+1}^L\delta_{pi}.
-\end{equation}
-
-%4.4.3
-\subsubsection{Eqnarray environment}
-
-For a sequence of two or more related formulas (equations), use the
-\|eqnarray| environment to line them up at equal (or unequal) signs
-instead of \|\[| \ \|\]| or the \|equation| environment.
-
-%4.4.4
-\subsubsection{Special Fonts}
-
-It is strongly recommended to use only standard {\LaTeX} math
-fonts.  Otherwise, you must report that you are using special fonts.
-
-\begin{figure}[tb]%1
-\setbox0\vbox{\it
-\hbox{\|\begin{figure}[tb]|}
-\hbox{\quad \|<|figure-body\|>|}
-\hbox{\|\caption{<|caption\|>}|}
-\hbox{\|\label{| $\ldots$ \|}|}
-\hbox{\|\end{figure}\|}}
-\centerline{\fbox{\box0}}
-\caption{Single column figure with caption\\
-explicitly broken by $\backslash\backslash$}
-\label{fig:single}
-\end{figure}
-
-\begin{figure}[tb]%2
-\begin{minipage}[t]{0.5\columnwidth}
-\footnotesize
-\setbox0\vbox{
-\hbox{\|\begin{minipage}[t]%|}
-\hbox{\|  {0.5\columnwidth}|}
-\hbox{\|\captionType{table}|}
-\hbox{\|\caption{| \ldots \|}|}
-\hbox{\|\ecaption{| \ldots \|}|}
-\hbox{\|\label{| \ldots \|}|}
-\hbox{\|\makebox[\textwidth][c]{%|}
-\hbox{\|\begin{tabular}[t]{lcr}|}
-\hbox{\|\hline\hline|}
-\hbox{\|left&center&right\\\hline|}
-\hbox{\|L1&C1&R1\\|}
-\hbox{\|L2&C2&R2\\\hline|}
-\hbox{\|\end{tabular}}|}
-\hbox{\|\end{minipage}|}}
-\hbox{}
-\centerline{\fbox{\box0}}
-\caption{Contents of table \protect\ref{tab:right}}
-\label{fig:left}
-\end{minipage}%
-\begin{minipage}[t]{0.5\columnwidth}
-\CaptionType{table}
-\caption{A table built by Fig.\ \protect\ref{fig:left}}
-\label{tab:right}
-\makebox[\textwidth][c]{\begin{tabular}[t]{lcr}\hline\hline
-left&center&right\\\hline
-L1&C1&R1\\
-L2&C2&R2\\\hline
-\end{tabular}}
-\end{minipage}
-\end{figure}
-
-\begin{figure}[t]
-\setbox0\vbox{\it
-\hbox{\|\begin{figure}[tb]|}
-\hbox{\quad \|<|figure-body\|>|}
-\hbox{\|\caption{<|caption\|>}|}
-\hbox{\|\label{| $\ldots$ \|}|}
-\hbox{\|\end{figure}\|}}
-\centerline{\fbox{\box0}}
-\caption{Single column figure with caption\\
-explicitly broken by $\backslash\backslash$}
-\end{figure}
-
-\begin{figure*}[t]
-\setbox0\vbox{\large
-\hbox{\|\begin{figure*}[t]|}
-\hbox{\quad\|<|figure-body\|>|}
-\hbox{\|\caption{<|caption\|>}|}
-\hbox{\|\label{| $\ldots$ \|}|}
-\hbox{\|\end{figure*}|}}
-\centerline{\fbox{\hbox to.9\textwidth{\hss\box0\hss}}}
-\caption{Double column figure}
-\label{fig:double}
-\end{figure*}
-
-%4.5
-\subsection{Figures}
-
-A figure fit to one column is specified by the form shown in
-\figref{fig:single}. Note that you must not specify the \|h| option.
-
-The \|\caption| of a figure should be given below the figure body
-together with a \|\label| command.  A long caption will be automatically
-broken into two or more lines and centered with respect to the widest
-line.  You can assist, however, with the line breaking by adding \|\\|
-to obtain a more beautiful result, especially for two-line captions, as
-shown in \figref{fig:single}.
-
-If you want to rank two or more figures and/or tables in a \|figure| (or
-\|table|) environment in order to save space, enclose each figure\slash
-table and its \|\caption| in a \|minipage| environment as shown in
-\figref{fig:left} and \tabref{tab:right}. Also, as in a \|figure|
-environment, the caption for \tabref{tab:right} is correctly typeset
-because the \|minipage| for it has the \|\captionType{table}| command to
-specify the type of caption.  The command can of course be used with the
-\|figure| argument to give a figure caption.
-
-\Figref{fig:double} shows how to make a double column figure.
-
-You may use any size font, as shown in \figref{fig:double}. Also, you
-may include an encapsulated PostScript file (so called EPS file) as the
-body of a figure. To include, use
-%
-\begin{quote}
-\|\usepackage{graphicx}|
-\end{quote}
-%
-in the preamble and put the \|\includegraphics| command where you wish
-to embed the EPS graphics with its file name (and options if necessary).
-
-You might have noticed that the first reference to \figref{fig:single}
-is bold-faced, while the second and third are typed in roman fonts.
-This font switching is a rule of the Journal\slash Transactions and will
-be automatically performed if you use \|\figref{<|label\|>}| instead of
-\|Fig.~\ref{<|label\|>}|.  Another rule is that ``Figure'' must be used
-instead of ``Fig.''\ if the reference is the first word of a sentence,
-such as was the first reference to \figref{fig:double} above.
-Unfortunately, this switching is too hard to do automatically, so you
-must use \|\figref{<|label\|>}| in such cases.
-
-%4.6
-\subsection{Tables}
-
-A table with many rules is not very beautiful. \tabref{tab:example}
-shows an example of a table with standard style rules. Note that the
-uppermost rule is doubled, and no rules are drawn on the left and right
-edges. The caption should be put above the table. The default font size
-for tables is \|\footnotesize|. Any reference to a table should be made
-using \|\tabref{<|label\|>}|.
-
-\begin{table}[tb]
-\caption{Sections and sub-sections in which list-like environments are used (example of table)}
-\label{tab:example}
-\hbox to\hsize{\hfil
-\begin{tabular}{l|lll}\hline\hline
-&enumerate&itemize&description\\\hline
-type-1&	2 & 3 & 4.5 \\
-type-2&	---& 4.11 & 4.7 \\
-type-3&	2 & --- & 4.5\\
-type-4&	--- & 4.8 & 4.3 \\\hline
-\multicolumn{4}{l}{type-1\,: {\tt enumerate}, etc.\quad
-	type-2\,: {\tt enumerate*}, etc.}\\
-\multicolumn{4}{l}{type-3\,: {\tt Enumerate}, etc.\quad
-	type-4\,: {\tt ENUMERATE}, etc.}\\
-\end{tabular}\hfil}
-\end{table}
-
-%4.7
-\subsection{Citations, Reference, Acknowledgements}
-
-%4.7.1
-\subsubsection{Citations}
-
-The command \|\cite| is used to add citations in the text.  Cited labels
-are sorted automatically and separated by using square brackets \|[ ]|.
-Thus,
-\begin{quote}
-\|The paper \cite{companion,latex} is|\\
-\|an overview of \LaTeX|.
-\end{quote}
-will produce
-\begin{quote}
-The paper \cite{companion,latex} is an overview of \LaTeX.
-\end{quote}
-
-%4.7.2
-\subsubsection{List of References}
-
-References should be arranged in alphabetical or cited order.
-It is recommended to use BiB{\TeX} and style files 
-\|ipsjsort-e.bst|
-(alphabetical order) or \|ipsjunsort-e.bst| (cited order) to make
-references fit to the traditional style.
-Remember that you must include \|.bbl| file in the file package, instead of
-\|.bib|.
-If you cannot use BiB{\TeX} and have to make references manually using the
-bibliography environment, observe the references of this guide carefully
-and follow its style.
-
-%4.7.3
-\subsubsection{Acknowledgments and Appendices}
-
-If you want to acknowledge people, put your acknowledgments just before
-the references and enclose them in the \|acknowledgment| environment.
-
-Appendices, if there are any, should be put just after the references
-and \|\appendix| command.  Sectioning commands produces headings like
-{\bf \ref{A1}}, {\bf \ref{A2}}, and so on in the appendices.
-
-%4.8
-\subsection{Biography}
-
-Biographies of authors are positioned at the end of the document, just
-before \|\end{document}|, as follows.
-%
-\begin{quote}
-\|\begin{biography}|\\
-\|\profile{<|1st-author's-name\|>}|\\
-\mbox{}\quad\|{<|biography-of-1st-author\|>}|\\
-\|\author{<|2nd-author's-name\|>}|\\
-\mbox{}\quad\|{<|biography-of-2nd-author\|>}|\\
-\mbox{}\quad $\ldots\ldots\ldots$ \\
-\|\end{biography}|
-\end{quote}
-
-Generally, photographs used in author biographies should be identification photographs.
-
-The printers will crop these photographs to a size of 30\,mm by 25\,mm. 
-Avoid using photographs that contain missing portions of the face or photographs 
-in which the outline of the face is difficult to distinguish against the background. 
-It is recommended to use photographs that have no background or that 
-have light-colored backgrounds. 
-When digitally submitting photographs for the author biography, 
-the photograph must have a resolution of at least 300\,dpi and must 
-have been captured using a camera with at least one megapixel resolution. 
-Since photographs for the author biographies will be incorporated into 
-digital data by the printers at the time the composition is prepared, 
-it is not necessary to digitally insert the photographs into the draft.
+\section{Evaluation}
 
 %5
-\section{Check List of ``Dos and Don'ts''}
-
-%5.1
-\subsection{The basics of writing}
-
-\begin{itemize}
-\item[$\Box$] Describe a paper so that readers understand the novelty,
-	      availability, and reliability of the research.
-\item[$\Box$] Try to make a paper easy to read (discontinuity in the
-	      story and obscure backgrounds or themes are a burden to
-	      readers). 
-\item[$\Box$] Revisit the paper if the problem to be solved is not
-	      generalized (entirely focused on a problem at XX
-	      University, etc.) or if the paper reports deliverables
-	      only and does not describe the problem itself. 
-\item[$\Box$] Rethink the paper if its conclusion is not clearly
-	      described, it does not adequately point out its
-	      applicability, limits, and controversial points, or its
-	      conclusion does not follow the contents. 
-\item[$\Box$] Expressions that are inappropriate for scientific papers
-	      and that are hard to understand should be reconsidered. 
-\item[$\Box$] Second thought is necessary if sentences are in colloquial
-	      style. 
-\item[$\Box$] Check the structure of chapters and sections and the
-	      organization of the paper. 
-\item[$\Box$] Do not make the paper so that grasping the meaning is
-	      difficult without guessing from the context. 
-\item[$\Box$] Confirm if the explanation of the hypotheses is enough and
-	      does not contain any gaps in meaning. 
-\item[$\Box$] The authors should not submit a manuscript that includes
-	      redundant and/or too brief descriptions.
-\item[$\Box$] The authors should eliminate undefined terminologies.
-\end{itemize}
-
-%5.2
-\subsection{Show novelty and usefulness clearly}
-
-\begin{itemize}
-\item[$\Box$] The authors should not submit a manuscript that does not
-	      clarify the motivation and the goal of their study and the
-	      relationship to other existing studies.
-\item[$\Box$] The authors should not submit a manuscript that does not
-	      clarify what technologies are well/publicly known and what
-	      idea they are newly/originally proposing. 
-\item[$\Box$] The authors should provide sufficient references in their
-	      manuscript to back up the originality of their study. 
-\item[$\Box$] The authors should not submit a manuscript in which the
-	      readers cannot understand their proposal (or cannot find
-	      any originality in it) because it consists entirely of
-	      abstractive and/or conceptual descriptions. 
-\item[$\Box$] The authors should not submit a manuscript that lacks
-	      discussions on the effectiveness of their proposal. 
-\end{itemize}
-
-%5.3
-\subsection{Concrete attention to writing}
-
-\begin{itemize}
-\item[$\Box$] The authors should not submit a manuscript whose Japanese
-	      title does not match its content correctly.
-\item[$\Box$] The authors should not submit a manuscript whose English
-	      title does not match its content correctly or that
-	      contains incorrect English usage.
-\item[$\Box$] The paper should be revised when its abstract does not
-	      show its purpose or is written in inadequate English.
-\item[$\Box$] The paper should be revised when symbols and abbreviations
-	      are not popular, wordings are not adequate, or the
-	      explanations of its pictures and tables are not adequate.
-\item[$\Box$] The paper should be revised when special wordings, which
-	      are popular only in an individual or local group or a
-	      small company, are used without any explanations.
-\item[$\Box$] The paper should be revised when its pictures or tables
-	      are not semantically clear or they contain mistakes.
-\item[$\Box$] The paper should be revised when its pictures or tables
-	      are not visually clear.
-\item[$\Box$] The paper should be revised when the size or the scale of
-	      its pictures or tables are not adequate.
-\end{itemize}
-
-%5.4
-\subsection{Regarding references}
-
-\begin{itemize}
-\item[$\Box$] The number of references should be more than 10 (Some
-	      opinions say more than 20 or 30 in some research areas.
-\item[$\Box$] A sufficient number of references are required to show the
-	      paper's novelty.
-\item[$\Box$] The paper should be revised when it has an insufficient
-	      number of references.
-\item[$\Box$] Referring to appropriate papers written by Japanese
-	      authors contributes to the further progression of the
-	      Japanese research community.
-\item[$\Box$] Do not include self-citations excessively.
-\end{itemize}
-
-%5.5
-\subsection{Double submission}
-
-\begin{itemize}
-\item[$\Box$] Double submission of the original paper is
-	      prohibited. However, it is permissible to submit a paper
-	      accepted at an international conference and free from
-	      copyright issues.
-\item[$\Box$] Do not use the same figures or charts already included in
-	      other original papers, except those that have proper
-	      citations.
-\item[$\Box$] Be careful not to have overlap between the paper and other
-	      published articles.
-\end{itemize}
-
-%5.6
-\subsection{Check by other researchers}
-
-\begin{itemize}
-\item[$\Box$] Proofreading by experienced persons with many accepted
-	      papers is strongly recommended.
-\item[$\Box$] Take care to avoid leaps of logic from the viewpoint of
-	      the readers.
-\end{itemize}
-
-%5.7
-\subsection{Miscellaneous}
-
-\begin{itemize}
-\item[$\Box$] After the first review round, do not modify the paper
-	      except for the stated conditions for acceptance without
-	      the reviewers' approval.
-
-\item[$\Box$] The authors cannot select reviewers.
-
-\item[$\Box$] Fill the self-check sheet carefully before submitting the
-	      paper.
-\end{itemize}
-
-\newpage%%
+\section{Related Work}
 
 %6
-\section{Concluding Remarks}
-
-We dare not dream that the style files are perfect but rather wish to
-improve them with your cooperation and hope that you will let us know of
-any complaints, comments, suggestions by e-mail to: 
-\begin{quote}
-\|editt@ipsj.or.jp|.
-\end{quote}
+\section{Conclusion}
 
 \begin{acknowledgment}
-We wrote this article based on the guideline for A4 landscape layout.
-We are grateful to Prof.\ Hiroshi Nakashima from Kyoto University,
-for his valuable comments on making a class-file, 
-and his consent to usage of BiB{\TeX} files.
-We are also very thankful to the editorial committee for their
-contributions in writing the guideline for the A4 landscape layout.
+
 \end{acknowledgment}
 
-\begin{thebibliography}{99}
-\bibitem{companion}%1
-Goossens, M., Mittelbach, F. and Samarin, A.:
-{\it The LaTeX Companion},
-Addison Wesley, Reading, 
-Massachusetts (1993).
+% \begin{biography}
+% \profile{Taro Joho}{was born in 1970. He received his M.S. degree from
+% Johoshori University in 1994.
+% He joined
+% the Information
+% Processing Society of Japan in 1994.
+% He is currently an associate professor at
+% \mbox{Johoshori} University.
+% His research interest is online
+% publishing systems. He is a member of the IEEE and ACM\@.}
+% %
+% \profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
+% Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
+% became an associate professor at Gakkai University in 1992 and a
+% professor at Johoshori University in 1997. Her current research
+% interest is online publishing systems. She received the Kiyasu Kinen
+% award in 2010. She is a Board Member of the IPSJ and a member of the
+% IEICE, IEEE-CS, and ACM\@.} 
+% %
+% \profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
+% from Johoshori University in 1994 and has been engaged in the
+% Information Processing Society of Japan since 1994. His research
+% interest is online publishing systems. He is a member of the IEEE and
+% ACM\@.}
+% %
+% \end{biography}
 
-\bibitem{latex}%2
-Lamport, L.: 
-{\it A Document Preparation System {\LaTeX} User's Guide \& Reference Manual}, 
-Addison Wesley, Reading, Massachusetts (1986).
-
-\bibitem{article1}%3
-Itoh, S. and Goto, N.: 
-An Adaptive Noiseless Coding for Sources with Big Alphabet Size, 
-{\it Trans.\ IEICE},  
-Vol.E74, No.9, pp.2495--2503 (1991).
-
-\bibitem{article2}%4
-Abrahamson, K., Dadoun, N., Kirkpatrick, D.G. and Przytycka, T.: 
-A Simple Parallel Tree Contraction Algorithm, 
-{\it J.\ Algorithms},  
-Vol.10, No.2,
-pp.287--302 (1989).
-
-\bibitem{article3}%5
-Yamakami, T.: Exploratory Session Analysis in the Mobile Clickstream, 
-{\it IPSJ Digital Courier},  
-Vol.3, pp.14--20 (online), \\
-\doi{10.2197/ipsjdc.3.14} (2007).
-
-\bibitem{book1}%6
-Foley, J.D. et al.: 
-Computer Graphics --- Principles and Practice, 
-System Programming Series, Addison-Wesley, 
-Reading, Massachusetts, 2nd edition (1990).
-
-\bibitem{book2}%7
-Chang, C.L. and Lee, R.C.T.: 
-Symbolic Logic and Mechanical Theorem Proving, 
-Academic Press, New York (1973).
-
-\bibitem{booklet1}%8
-{Institute for New Generation Computer Technology}: 
-Overview of the Fifth Generation Computer Project, 
-distributed in {FGCS'92} (1992).
-(in Japanese).
-
-\bibitem{inbook1}%9
-Knuth, D.E.: 
-Art of Computer Programming,
-{\it Fundamental Algorithms}, 
-Vol.1, chapter 2, 
-pp.371--381, 
-Addison-Wesley, 2nd edition (1973).
-
-\bibitem{incollection1}%10
-Schwartz, A.J.: 
-Subdividing B{\'e}zier Curves and Surfaces, 
-{\it Geometric Modeling: Algorithms and New Trends\/} 
-(Farin, G.E., ed.), 
-SIAM, Philadelphia,
-pp.55--66 (1987).
-
-\bibitem{inproceedings1}%11
-Baraff, D.:
-Curved Surfaces and Coherence for Non-penetrating Rigid Body
-Simulation, 
-{\it Proc.\ SIGGRAPH '90\/} (Beach, R.J., ed.), 
-Dallas,
-Texas, ACM, Addison-Wesley, 
-pp.19--28 (1990).
-
-\bibitem{inproceedings2}%12
-Nakashima, H. et al.: 
-OhHelp: A Scalable Domain-Decomposing Dynamic Load
-Balancing for Particle-in-Cell Simulations, 
-{\it Proc.\ Intl.\ Conf. Supercomputing}, 
-pp.90--99 (online),\\
-\doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).
-
-\bibitem{manual1}%13
-Adobe Systems Inc.: 
-{\it PostScript Language Reference Manual}, 
-Reading,
-Massachusetts (1985).
-
-\bibitem{mastersthesis1}%14
-Ohno, K.: 
-Efficient Message Communication of Concurrent Logic Programming
-Language KL1 Based on Static Analysis, 
-Master's thesis, 
-Dept.\ Information Science, Kyoto University (1995).
-
-\bibitem{misc1}%15
-Saito, Y. and Nakashima, H.: 
-{\tt ipsjpapers.sty} (1995).
-(Style file for Trans. IPSJ distributed to authors.).
-
-\bibitem{phdthesis1}%16
-Weihl, W.: 
-Specification and Implementation of Atomic Data Types, 
-PhD Thesis,
-MIT, Boston (1984).
-
-\bibitem{proceedings1}%17
-Institute for New Generation Computer Technology: 
-{\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
-Vol.1 (1992).
-
-\bibitem{WarD:WAM-1}%18
-Warren, D.H.D.: An Abstract {Prolog} Instruction Set, 
-Technical Report 309,
-Artificial Intelligence Center, 
-SRI International (1983).
-
-\bibitem{unpublished}%19
-Editorial Board of Trans.\ IPSJ:
-How to Typeset Your Papers in {\LaTeX}
-(Version 1) (1995).
-(distributed to authors).
-
-\bibitem{webpage1}%20
-Kay, A.: Welcome to Squeakland, Squeakland (online),\\
-\urle{http://www.squeakland.org/community/biography/\\
-alanbio.html}
-\refdatee{2007-4-5}.
-
-\bibitem{webpage2}%21
-Nakashima, H.: 
-A {WEB} Page, Kyoto University (online),\\
-\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
-a.web.page.of.long.url/}
-\refdatee{2010-10-30}.
-
-\bibitem{webpage3}%22
-Nakashima, H.: 
-Another {WEB} Page, 
-Kyoto University (online),\\
-\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
-a.web.page.of.much.longer.url/} 
-\refdatee{2010-10-30}.
-
-\end{thebibliography}
-
-\appendix
-
-%A.1
-\section{How to Write an Appendix}
-\label{A1}
-
-To add an appendix, write the command \|\appendix| immediately following
-the reference list.  Within the appendix, the \|\section| command creates
-numbered headings such as \ref{A1} and \ref{A2}.
-
-%A.1.1
-\subsection{Example of a Heading}
-The command \|\subsection| in the appendix gives this kind of heading.
-
-%A.2
-\section{Commands for Transactions}
-\label{A2}
-
-Each transaction has its own subtitle, abbreviation code, and serial
-number. This information is given by using the following commands for
-the \|\documentclass| option in the final version.
-
-\begin{itemize}
-\item \|PRO| (Trans.\ Programming)
-\item \|TOM| (Trans.\ Mathematical Modeling and Its Applications)
-\item \|TOD| (Trans.\ Database)
-\item \|ACS| (Trans.\ Advanced Computing Systems)
-\item \|CDS| (Trans.\ Consumer Device \& System)
-\item \|DC | (Trans.\ Digital Content)
-\item \|TCE| (Trans.\ Computer and Education)
-\item \|TBIO| (Bioinformatics)
-\item \|SLDM| (System LSI Design Methodology)
-\item \|CVA| (Computer Vision and Applications)
-\end{itemize}
-
-Moreover, for papers in English, the command \|english| can be added. For
-example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
-English document.
-
-Note that the research group has a ``month of publication'' number that
-does not correspond to the ``issue month number'' of the
-transaction. You may be notified by the IPSJ or the Editorial Board of
-the \|<month>| in order to set the month of publication counter as
-follows.
-
-\begin{quote}
-\|\setcounter{month}{month of publication}|
-\end{quote}
-
-In addition, commands are provided for executing unique functions for
-several transactions, as shown in the following sections.
-
-%A.3
-\section{Unique Commands for Each Part}
-
-Since each of the parts has its own detailed specifications, the same
-command may produce different results in two different parts.
-
-In some cases, the \|<Revised date>| and \|<Second revised| \|date>| are
-inputted. These can be added as a preamble by using
-
-\begin{quote}
-\|\rereceived{<year>}{<month>}{<day>}|\\
-\|\rerereceived {<year>}{<month>}{<day>}|
-\end{quote}
-
-%A.3.1
-\subsection{Unique Functions for Programming (PRO)}
-
-Issues of Transactions on Programming (PRO) includes not only regular
-papers but also abstracts from research presentations delivered in the
-research groups of SIGPRO\@. The file for an abstract consists of
-material from the \|\documentclass| to the \maketitle of the format
-shown in Section~\ref{body}. That is, the file does not have a main
-text. Note that the reception and acceptance dates are not required, but
-the date of presentation has to be given:
-\begin{quote}
-\|\Presented{<year>}{<month>}{<day>}|
-\end{quote}
-
-%A.3.2
-\subsection{Unique Functions for Database (TOD)}
-
-The name of the editor in charge for the paper included in The
-Transactions on Database (TOD) is specified by
-\begin{quote}
-\|\edInCharge{<name-of-editor>}|
-\end{quote}
-
-Also, following a change in style, the command is entered at the end of
-the paper, directly before \|\end{document}|.
-
-%A.3.3
-\subsection{Unique Functions for Consumer Devices \& Systems (CDS)}
-
-In the ``Transactions on Consumer Devices \& Systems,'' since the
-headings differ depending on the type of document, the type of heading
-is to be changed with the option.
-
-The types are:
-\begin{itemize}
-\item \|systems  | Paper on Consumer Systems
-\item \|services | Paper on Consumer Services
-\item \|devices  | Paper on Consumer Devices
-\item \|Research | Research Paper
-\end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.4
-\subsection{Unique Functions for Digital Content (DCON)}
-
-In the ``Transactions on Digital Content,'' since the
-headings differ depending on the type of document, the type of heading
-is to be changed with the option.
-
-The types are:
-\begin{itemize}
-\item \|Research | Research Paper
-\item \|Practice | Practice Paper
-\item \|Content  | Content Paper
-\end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.5
-\subsection{Unique Functions for Computer and Education (TCE)}
-
-In the ``Transactions on Computer and Education,'' since the headings
-differ depending on the type of document, the type of heading is
-to be changed with the option.
-
-The types are:
-\begin{itemize}
-\item \|No specification  | Regular Paper (Default)
-\item \|Short             | Short Paper
-\end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.6
-\subsection{Unique Functions for Bioinformatics (TBIO)}
-
-Since papers in Transactions on Bioinformatics (TBIO) are in English,
-specifying the TBIO option will cause the program to assume that the
-English option has been specified. This effectively means that the
-English option can be omitted.
-
-The following three categories define the different types of papers.
-\begin{itemize}
-\item \|No specification | Original Paper (Default)
-\item \|Data             | Database/Software Paper
-\item \|Survey           | Survey Paper
-\end{itemize}
-
-Therefore, \|\documentclass[TBIO]{ipsj}| will be an original paper, and
-\|\documentclass[TBIO,Survey]{ipsj}| will be a survey paper.
-
-Moreover, as with TOD, the name of the editor in charge of the paper is
-specified by using \|\Editor|, but in this case, the text is introduced with ``Communicated by.'' Therefore, the name of the editor is positioned directly before \|\end{document}|, as with TOD.
-
-%A.3.7
-\subsection{Unique Functions for Computer Vision and Applications (CVA)}
-
-The Transactions of Computer Vision and Applications is also an English
-language journal, allowing the English option to be omitted.
-
-There are three classes of documents:
-\begin{itemize}
-\item \|No specification | Regular Paper (Default)
-\item \|Research         | Research Paper
-\item \|system           | Systems Paper
-\item \|Express          | Express Paper
-\end{itemize}
-
-As with TBIO, the name of the editor in charge is inserted, and the
-inserted text is introduced with ``Communicated by.''
-
-%A.3.8
-\subsection{Unique Functions for System LSI Design Methodology (SLDM)}
-
-The Transactions of System LSI Design and Methodology (SLDM) is also an
-English language journal, allowing the English option to be omitted.
-
-There are two classes of documents:
-\begin{itemize}
-\item \|No specification | Regular Paper (Default)
-\item \|Short            | Short Paper
-\end{itemize}
-
-SDLM also enters the name of the editor in charge, but automatic
-insertion is treated differently depending on the paper.
-
-Normally, text is inserted using ``Recommended by Associate Editor:,''
-but it is only when the ``invited'' option is included that the
-insertion text becomes ``Invited by Editor-in-Chief:.''
-
-\begin{biography}
-\profile{Taro Joho}{was born in 1970. He received his M.S.\ degree from
-Johoshori University in 1994.
-He joined
-the Information
-Processing Society of Japan in 1994.
-He is currently an associate professor at
-\mbox{Johoshori} University.
-His research interest is online
-publishing systems. He is a member of the IEEE and ACM\@.}
-%
-\profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
-Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
-became an associate professor at Gakkai University in 1992 and a
-professor at Johoshori University in 1997. Her current research
-interest is online publishing systems. She received the Kiyasu Kinen
-award in 2010. She is a Board Member of the IPSJ and a member of the
-IEICE, IEEE-CS, and ACM\@.} 
-%
-\profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
-from Johoshori University in 1994 and has been engaged in the
-Information Processing Society of Japan since 1994. His research
-interest is online publishing systems. He is a member of the IEEE and
-ACM\@.}
-%
-\end{biography}
 \end{document}

### 2017-11-06 ipsj/paper.tex
Add TLSF+TECS section

@@
 
-\usepackage{graphicx}
+\usepackage[dvipdfmx]{graphicx}
 \usepackage{latexsym}
+\usepackage{amssymb}
+\usepackage{float}
+\usepackage{enumerate,cite,url}
+\usepackage{listings,jlisting}
+\lstset{%
+    language={c},%
+    basicstyle={\small},%
+    identifierstyle={\small},%
+    commentstyle={\footnotesize\itshape},%
+    keywordstyle={\small},%\bfseries},%
+    ndkeywordstyle={\small},%
+    stringstyle={\small\it},
+    frame={tb},
+    breaklines=true,
+    columns=[l]{fullflexible},%
+    numbers=left,%
+    xrightmargin=0zw,%
+    xleftmargin=3zw,%
+    numberstyle={\scriptsize},%
+    stepnumber=1,
+    numbersep=1zw,%
+    lineskip=-0.5ex%
+}
 
@@
 
-\title{Component-based Software Development Framework \\for Embedded IoT Devices}
+\title{Component-based Software Development Framework \\for Embedded IoT Devices（仮）}
 
@@
 
+\subsection{TLSF+TECS}
+\label{sec:TLSF+TECS}
+
+\subsubsection{TLSF}
+
+TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
+TLSF memory allocator has the following features.
+\begin{description}
+    \item[Real-time property]\mbox{}\\
+        The worst execution time required for allocating and deallocating memory does not depend on the data size.
+        TLSF always works with $O(1)$, and it is possible to estimate the response time.
+    \item[Fast speed]\mbox{}\\
+        In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
+    \item[Efficient memory consumption]\mbox{}\\
+        Memory efficiency is improved by suppressing memory fragmentation.
+        Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
+\end{description}
+
+\subsubsection{TLSF Algorithms}
+
+TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
+The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
+Consider a case where a request, $malloc(100)$, is called to allocate a memory.
+In the first step, it is classified by the most significant bit of the requested memory size.
+In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
+In the second step, it is further classified.
+In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
+Free block \footnote{Free block is an available memory block.} in this range is used.
+
+A simple fixed-size memory block allocator results in waste of up to 50\%, but TLSF classifies it finely in two steps, so it is a memory efficient algorithm.
+In addition, TLSF searches at the same speed and at high speed, $O(1)$.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
+    \caption{TLSF Algorithm}
+    \label{fig:TLSF}
+\end{figure}
+
+\subsubsection{Component Design of TLSF memory allocator}
+
+This section describes the component design of TLSF memory allocator.
+In this research, we are using TECS to componentize TLSF.
+The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sMalloc {
+    int    initializeMemoryPool(void);
+    void   *calloc( [in]size_t nelem,
+                    [in]size_t elem_size );
+    void   *malloc( [in]size_t size );
+    void   *realloc( [in]const void *ptr,
+                     [in]size_t new_size );
+    void   free( [in]const void *ptr );
+};
+\end{lstlisting}
+\caption{Signature description of memory management}  
+\label{src:TLSFSignature}
+\end{figure}
+
+Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
+It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+celltype tTLSFMalloc {
+    [inline]
+        entry  sMalloc  eMalloc;
+    attr {
+        /* memory pool size in bytes */
+        size_t  memoryPoolSize;
+    };
+    var {
+        [size_is( memoryPoolSize / 8 )]
+            uint64_t   *pool;
+    };
+};
+\end{lstlisting}
+\caption{Celltype description of TLSF memory allocator component}  
+\label{src:TLSFCelltype}
+\end{figure}
+
+The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
+An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
+Here, {\it [inline]} is a specifier for Implementation as inline functions.
+A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as an variable.
+Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
+    \caption{TLSF before componentization}
+    \label{fig:WithoutTECS}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
+    \caption{TLSF after componentization}
+    \label{fig:WithTECS}
+\end{figure}
+
+As shown in Fig.
+\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
+In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
+It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+cell tTask Task_001 {
+    cMalloc = TLSFMalloc_001.eMalloc;
+};
+cell tTLSFMalloc TLSFMalloc_001 {
+    memoryPoolSize = 1024*1024; /* 1MB */
+};
+cell tTask Task_002 {
+    cMalloc = TLSFMalloc_002.eMalloc;
+};
+cell tTLSFMalloc TLSFMalloc_002 {
+    memoryPoolSize = 2*1024*1024; /* 2MB */
+};
+\end{lstlisting}
+\caption{Build description of TLSF memory allocator component}
+\label{src:TLSFBuild}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+void*
+mrb_TECS_allocf(mrb_state *mrb, void *p, 
+                  size_t size, void *ud)
+{
+    CELLCB	*p_cellcb = (CELLCB *)ud;
+    if (size == 0) {
+        //tlsf_free(p);
+        cMalloc_free(p);
+        return NULL;
+    }
+    else if (p) {
+        //return tlsf_realloc(p, size);
+        return cMalloc_realloc(p, size);
+    }
+    else {
+        //return tlsf_malloc(size);
+        return cMalloc_malloc(size);
+    }
+}
+\end{lstlisting}
+\caption{Example of TLSF memory allocator component}  
+\label{src:TLSFC}
+\end{figure}
+
+Fig.
+\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.
+\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Two sets of task components and TLSF components are combined.
+Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
+Fig. \ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
+The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
+Lines 8 calls the {\it free} function of the TLSF memory allocator component.
+{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig. \ref{src:TLSFBuild}).
+Likewise, Lines 13 and 17 call the function for memory allocation.
+The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
+In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
+
 %4
@@
 \end{acknowledgment}
+
+%Reference
+\bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}
+\bibliography{ref}
 

### 2017-11-06 ipsj/paper.tex
Add TECS part

@@
 \section{System Model}
+
+\subsection{TECS}
+TECS is a component system suitable for embedded systems.
+TECS can increase productivity and reduce development costs due to improved reusability of software components.
+TECS also provides component diagrams, which help developers visualize the overall structure of a system.
+
+In TECS, component deployment and composition are performed statically.
+Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
+TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/component_diagram.pdf}
+    \caption{Component Diagram}
+    \label{fig:component}
+\end{figure}
+
+\subsubsection{Component Model}
+Fig. \ref{fig:component} shows a component diagram.
+A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
+An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
+A {\it cell} has one or more {\it entry} ports and {\it call} ports.
+{\it Cell} functions are implemented in C.
+
+The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
+A {\it signature} is the interface definition of a {\it cell}.
+The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
+Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.
+
+\subsubsection{Component Description}
+In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
+% TECS code is written in CDL (component description language) file.
+These components are described as follows.
+
+\begin{description}
+    \item[{\bf Signature Description}]\mbox{}\\
+        The {\it signature} defines a {\it cell} interface.
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig. \ref{signature}).
+        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sMotor {
+    int32_t getCounts( void );
+    ER resetCounts( void );
+    ER setPower( [in]int power );
+    ER stop( [in] bool_t brake );
+    ER rotate( [in] int degrees,
+               [in] uint32_t speed_abs,
+                [in] bool_t blocking );
+    void initializePort( [in]int32_t type );
+};
+\end{lstlisting}
+\caption{Signature Description}
+\label{signature}
+\end{figure}
+    \item[{\bf Celltype Description}]\mbox{}\\
+        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig. \ref{celltype}).
+        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
+        {\it Call} ports are defined similarly.
+        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+celltype tCaller {
+    call sMotor cMotor;
+};
+celltype tMotor {
+    entry sMotor eMotor;
+    attr {
+        int32_t port;
+    };
+    var {
+        int32_t currentSpeed = 0;
+    };
+};
+\end{lstlisting}
+\caption{Celltype Description}
+\label{celltype}
+\end{figure}
+    \item[{\bf Build Description}]\mbox{}\\
+        The build description is used to instantiate and connect {\it cell}s.
+        Fig. \ref{build} shows an example of a build description.
+        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
+        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
+        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        {\it C\_EXP} calls macros defined in C files.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+cell tMotor Motor {
+    port = C_EXP("PORT_A");
+};
+cell tCaller Caller {
+    cMotor = Motor.eMotor;
+};
+\end{lstlisting}
+\caption{Build Description}
+\label{build}
+\end{figure}
+
+\end{description}
 

### 2017-11-06 ipsj/paper.tex
Add TECS development flow

@@
 \end{description}
+
+\subsubsection{開発フロー}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
+    \caption{Development flow using TECS}
+    \label{fig:TECSFlow}
+\end{figure}
+
+Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
+TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.
+
+Software developers using TECS can be divided into component designers and application developers.
+Component designers define signatures, which are interfaces between cells, and celltypes, which are types of cells.
+Using the template code generated from the CDL file in which these are defined, component designers implement the functions and behaviors of the component in C language.
+The source code implementing the function of the component is called a celltype code.
+Application developers develop applications by using component diagrams and predefined celltype to connect cells with build description.
+An application module is generated by compiling and linking the header, the interface code, and the celltype code.
 

### 2017-11-06 ipsj/paper.tex
Add system model

@@
 \section{System Model}
+\label{sec:System Model}
+
+This section describes the system model of the proposed framework, including basic technologies such as TECS.
+The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
+
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
+In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mrubyonTECS}) are described.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
+    \caption{System model of the proposed framework}
+    \label{fig:SystemModel}
+\end{figure}
+
+\subsection{mruby}
+\label{sec:mruby}
 
 \subsection{TECS}
+\label{sec:TECS}
+
 TECS is a component system suitable for embedded systems.
@@
 
-\subsubsection{開発フロー}
+\subsubsection{Development Flow}
 
@@
 An application module is generated by compiling and linking the header, the interface code, and the celltype code.
+
+\subsection{mruby on TECS}
+\label{sec:mrubyonTECS}
 

### 2017-11-07 ipsj/paper.tex
Remove spaces of Fig.xx

@@
 This section describes the system model of the proposed framework, including basic technologies such as TECS.
-The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
+The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
 
@@
 \subsubsection{Component Model}
-Fig. \ref{fig:component} shows a component diagram.
+Fig.\ref{fig:component} shows a component diagram.
 A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
@@
         The {\it signature} defines a {\it cell} interface.
-        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig. \ref{signature}).
+        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
         In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
@@
         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
-        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig. \ref{celltype}).
+        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
         To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
@@
         The build description is used to instantiate and connect {\it cell}s.
-        Fig. \ref{build} shows an example of a build description.
+        Fig.\ref{build} shows an example of a build description.
         A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
         To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
-        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
+        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
         {\it C\_EXP} calls macros defined in C files.
@@
 
-Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
+Fig.\ref{fig:TECSFlow} shows the development flow using TECS.
 TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.
@@
 TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
-The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
+The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
 Consider a case where a request, $malloc(100)$, is called to allocate a memory.
@@
 
-Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
+Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
 It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.
@@
 
-The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
+The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
 An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
@@
 
-As shown in Fig.
-\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
-In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
+As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
+In the research, TLSF is componentized using TECS as shown in Fig.\ref{fig:WithTECS}.
 It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.
@@
 
-Fig.
-\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.
-\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
 Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
-Fig. \ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
+Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
+Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
 The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
 Lines 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig. \ref{src:TLSFBuild}).
+{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig.\ref{src:TLSFBuild}).
 Likewise, Lines 13 and 17 call the function for memory allocation.

### 2017-11-08 ipsj/paper.tex
Add Introduction

@@
 \affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
-\affiliate{NAGOYA}{Graduate School of Information Science, Nagoya University}
+\affiliate{NAGOYA}{Graduate School of Informatics, Nagoya University}
 \affiliate{OKUMA}{OKUMA Corporation}
@@
 \section{Introduction}
+\label{sec:Introduction}
+
+The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
+The IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, and they must demonstrate high quality and high performance.
+This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
+
+Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
+Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
+Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
+Individual component diagrams enable the visualization of an entire system.
+In addition, component-based systems are flexible with regard to extensibility and specification changes.
+The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
+
+In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
+Currently, most embedded software are programmed in C language.
+However, development in C language results in large code size, incurs high costs, and requires significant development time.
+In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.
+
+For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
+Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
+Therefore, applying scripting languages to embedded systems is difficult.
+To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
+This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
+
+This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
+In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS \cite{par:TINET+TECS}, is comprised, and it is possible to utilize TINET function from mruby programs.
+
+TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
+TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
+TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
+
+In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
+TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by deviding memory blocks in two stages.
+In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
+TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has its own heap area.
+
+{\bf Contributions}: The proposed framework provides the following contributions.
+\begin{enumerate}
+\item {\bf :}
+\item {\bf :}
+\item {\bf :}
+\item {\bf :}
+\end{enumerate}
+
+{\bf Organization}: The remainder of this paper is organized as follows.
+Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., mruby, TECS, and mruby on TECS.
+Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
+Section \ref{sec:Evaluation} evaluates the proposed framework.
+Related work is discussed in Section \ref{sec:Related Work}.
+Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.
 
@@
 \section{Proposed Framework}
+\label{sec:Proposed Framework}
 
@@
 
-\subsubsection{Component Design of TLSF memory allocator}
+\subsubsection{Component Design of TLSF}
 
@@
 \section{Evaluation}
+\label{sec:Evaluation}
 
@@
 \section{Related Work}
+\label{sec:Related Work}
 
@@
 \section{Conclusion}
+\label{sec:Conclusion}
 

### 2017-11-08 ipsj/paper.tex
Update System Model

@@
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., mruby, TECS, and mruby on TECS.
+Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
 Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
@@
 The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
-In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mrubyonTECS}) are described.
+In this section, TECS,  mruby, and mruby on TECS framework are described.
 
@@
 \end{figure}
-
-\subsection{mruby}
-\label{sec:mruby}
 
@@
 
+\subsection{mruby}
+\label{sec:mruby}
+
+mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
+It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
+Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.
+
+mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
+In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
+The mruby/RiteVM mechanism is shown in Fig.\ref{fig:mruby}.
+The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/mruby.pdf}
+    \caption{mruby/RiteVM mechanism}
+    \label{fig:mruby}
+\end{figure}
+
 \subsection{mruby on TECS}
 \label{sec:mrubyonTECS}
+
+mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
+This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.
+
+\subsubsection{System Model of mruby on TECS}
+The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
+Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+TECS components support various embedded drivers such as motor and sensor drivers.
+
+An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
+The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
+
+In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
+However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.pdf}
+\caption{System model of existing mruby on TECS}
+\label{fig:mrubyontecs}
+\end{figure}
+
+\subsubsection{mruby-TECS Bridge}
+There is a significant difference between the execution times of mruby and C language codes.
+According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
+Thus, it is difficult to use mruby exclusively.
+
+Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
+However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
+
+Fig.\ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
+The left side of BridgeMotor belongs to the mruby program.
+The right side of BridgeMotor belongs to TECS component.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=6.5cm,clip]{figure/mrubyTECSbridge.pdf}
+\caption{mruby-TECS bridge}
+\label{fig:mrubyTECSbridge}
+\end{figure}
+
+The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
+
+The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
+Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
 

### 2017-11-08 ipsj/paper.tex
Add TINET+TECS

@@
 
+\subsection{TINET+TECS}
+\label{sec:TINET+TECS}
+
+\subsubsection{TINET}
+
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a real-time operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
+TINET has been released as an open-source tool.
+
+To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the following functions:
+
+\begin{itemize}
+    \item minimum copy frequency,
+    \item elimination of dynamic memory control,
+    \item asynchronous interfacing,
+    \item error detailing per API.
+\end{itemize}
+
+{\bf Overview:}
+TINET runs as middleware on TOPPERS/ASP3 \cite{par:ASP3} \cite{url:ASP3}, a real-time kernel based on $\mu$ITRON \cite{par:microITRON}.
+As it is compatible with TOPPERS RTOS, TINET also supports other RTOSs such as TOPPERS/ASP and TOPPERS/JSP.
+
+Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+Users transmit and receive data using a Communication End Point (CEP), an interface that functions like a socket.
+In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
+In the reception process, the headers of the data bodies received by the network device are analyzed at each protocol layer, and the data are then passed to the CEP.
+
+A TCP reception point called the REP stands by to receive connection requests from the partner side.
+The REP has an IP address ({\it myaddr}) and a port number ({\it myportno}) as attributes and performs functions such {\it bind()} and {\it listen()}.
+
+In TINET, the amount of data copying between each protocol layers is minimized.
+In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
+To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of performing data copying.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
+    \label{fig:TINETHierarchyDiagram}
+\end{figure}
+
+\subsubsection{Component Design of TINET+TECS}
+
+TINET+TECS, the proposed componentized TCP/IP protocol stack, comprises a number of some TECS components.
+This section describes the components of the TINET+TECS framework with the aid of component diagrams.
+
+\subsubsection*{Components of a protocol stack}
+
+The components of a TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
+Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
+In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
+By using such small grain components, software visibility is improved.
+The components of each protocol are described in the following.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
+    \caption{Component diagram of a protocol stack}
+    \label{fig:ComponentProtocolStack}
+\end{figure}
+
+{\bf Application layer:}
+An application in TINET+TECS is implemented as a component such as tApplication.
+Software with TINET uses ITRON TCP/IP API \cite{url:ITRON_TCP/IP_API_Spec} such as {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat}.
+In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
+Moreover, in TINET+TECS supporting a TECS adapter, an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, software can be developed either using existing methods or as TECS components.
+
+{\bf Transport layer:}
+tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components TCP (UDP).
+For example, a server program supporting multiple clients can be developed by preparing multiple tTCPCEP components.
+tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components for performing, respectively, receiving and sending processing in the transport layer.
+
+{\bf Network layer:}
+The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
+The tIPv4Functions component performs functions such as checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
+
+{\bf Data link layer:}
+tEthernetInputTaskBody and tEthernetOutputTaskBody (tEthernetOutput) are components for performing, respectively, receiving and sending processing in the data link layer.
+The tArp component is for implementing the Address Resolution Protocol (ARP).
+
+{\bf Physical layer:}
+The tNetworkInterfaceContoroller component implements a network device driver.
+Software can be run on other devices by replacing the component because only the component depends on the target device.
+
+To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
+The communication object component corresponds to a CEP or REP of the original TINET.
+Application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
+
+The protocol stack of TINET+TECS supports the coexistence of multiple protocols.
+Though its use of IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without modification of component implementation.
+
+\subsubsection*{Memory allocator component}
+
+The original TINET eliminates dynamic memory control to meet the severe memory restrictions of embedded systems.
+A memory area for sending/receiving data in the protocol stack is allocated and released within a predetermined area.
+The memory allocator component allows for elimination of dynamic memory control in TINET+TECS by providing a requested memory area from the statically allocated memory area.
+
+The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
+tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and release memory areas of a requested size. 
+tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
+On the other hand, all components that need to allocate or deallocate memory, e.g., tTCPInput and tEthernetOutput, connect to the memory allocator component.
+
+In addition, TINET+TECS utilizes the TECS {\it send/receive} specifier to minimize the memory copy frequency, which is a functionality supported by TINET.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
+    \caption{Component diagram of tMemoryAllocator}
+    \label{fig:tMemoryAllocator}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
+    \caption{Differences between in/out and send/receive}
+    \label{fig:SendReceive}
+\end{figure}
+
+{\bf Send/receive specifiers:}
+TECS supports {\it send}/{\it receive} interface specifiers \cite{par:RPC}.
+TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies:
+
+\begin{itemize}
+\item {\it in} is a specifier for input arguments.
+A callee side uses the memory of arguments with {\it in} when executing the callee function.
+When the processing returns to the caller side, the caller can reuse and deallocate the memory.
+
+\item {\it send} is another specifier for transferring data to a callee from a caller such as {\it in}.
+The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
+In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
+By contrast, in the case of {\it send}, the caller allocates the data memory and the callee deallocates it.
+
+\item {\it out} is a specifier for output arguments through which a callee writes data in the memory allocated by a caller while the caller receives the data.
+
+\item {\it receive} is another specifier for a caller receiving data from a callee such as {\it out}.
+The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
+In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
+Deallocating of the memory is performed in the caller in both cases.
+\end{itemize}
+
+As shown in Fig.\ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
+Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
+Common object request broker architecture (CORBA) does not consider memory sharing; CORBA has no functionalities
+such as {\it send}/{\it receive}.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sNicDriver {
+  void start(
+    [send(sNetworkAlloc),size_is(size)]
+        int8_t *outputp, .., ..);
+  void read(
+    [receive(sNetworkAlloc),size_is(*size)]
+        int8_t **inputp, .., ..);
+    /* Omit: other functions */
+};
+\end{lstlisting}
+\caption{Signature description of the nic driver (An example of send/receive)}
+\label{src:SendReceive}
+\end{figure}
+
 \subsection{TLSF+TECS}
@@
 
-\subsubsection{Component Design of TLSF}
+\subsubsection{Component Design of TLSF+TECS}
 

### 2017-11-09 ipsj/paper.tex
Update

@@
 \usepackage{enumerate,cite,url}
+\usepackage{color}
 \usepackage{listings,jlisting}
@@
 
-This section describes the system model of the proposed framework, including basic technologies such as TECS.
+This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
 The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
+In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
+mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
+Moreover, the proposed framework comprises TLSF+TECS.
+TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
 
-The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
-In this section, TECS,  mruby, and mruby on TECS framework are described.
+The following subsection explains TECS, mruby, and mruby on TECS framework.
 
@@
 In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.
+However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.
 
@@
 The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-
 The generated mruby-TECS bridge supports registration of classes and methods for mruby.
@@
 \label{sec:Proposed Framework}
+
+\textcolor{red}{TODO: セクションの概要を追加}
+
+\subsection{Extended mruby on TECS (仮)}
+
+\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}
 
@@
 Lines 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the calle port (Lines 2 in Fig.\ref{src:TLSFBuild}).
+{\it cMalloc\_} represents the name of the call port (Lines 2 in Fig.\ref{src:TLSFBuild}).
 Likewise, Lines 13 and 17 call the function for memory allocation.

### 2017-11-10 ipsj/paper.tex
Update Proposed Framework

@@
 
-\textcolor{red}{TODO: セクションの概要を追加}
+The proposed framework is an extended mruby on TECS framework for network programming.
+It can use TINET+TECS functions from mruby programs.
+TINET+TECS is a component-based TCP/IP protocol stack comprised in the proposed framework, and it compensates for the original TINET's weak point, that it is hard to maintain, extend, and analyze the software due to many complex source codes and improves the configurability.
+In addition, TLSF+TECS, a component-based dynamic memory allocator, is used for memory management of mruby's RiteVMs and TCP/IP buffers in the proposed framework.
+Since each component holds its own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption which is a merit of TLSF.
 

### 2017-11-13 ipsj/paper.tex
Fix typo

@@
 In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
-Currently, most embedded software are programmed in C language.
+Currently, most embedded software is programmed in C language.
 However, development in C language results in large code size, incurs high costs, and requires significant development time.
@@
 Software developers using TECS can be divided into component designers and application developers.
-Component designers define signatures, which are interfaces between cells, and celltypes, which are types of cells.
+Component designers define {\it signature}s, which are interfaces between {\it cell}s, and {\it celltype}s, which are types of {\it cell}s.
 Using the template code generated from the CDL file in which these are defined, component designers implement the functions and behaviors of the component in C language.
-The source code implementing the function of the component is called a celltype code.
-Application developers develop applications by using component diagrams and predefined celltype to connect cells with build description.
-An application module is generated by compiling and linking the header, the interface code, and the celltype code.
+The source code implementing the function of the component is called a {\it celltype} code.
+Application developers develop applications by using component diagrams and predefined {\it celltype} to connect {\it cell}s with build description.
+An application module is generated by compiling and linking the header, the interface code, and the {\it celltype} code.
 
@@
 \subsubsection{System Model of mruby on TECS}
-The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
+The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
 Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.pdf}
+    \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
 \caption{System model of existing mruby on TECS}
-\label{fig:mrubyontecs}
+\label{fig:mrubyonTECS}
 \end{figure}
@@
 The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
-tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and release memory areas of a requested size. 
+tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and releasing memory areas of a requested size. 
 tFixedSizeMemoryPool components of various sizes are prepared, and an appropriate memory area can be allocated according to the used data size.
@@
         TLSF always works with $O(1)$, and it is possible to estimate the response time.
-    \item[Fast speed]\mbox{}\\
-        In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
+    % \item[Fast speed]\mbox{}\\
+    %     In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
     \item[Efficient memory consumption]\mbox{}\\
@@
 In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
-Free block \footnote{Free block is an available memory block.} in this range is used.
+Free block\footnote{Free block is an available memory block.} in this range is used.
 
@@
 Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
-It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signatures.
+It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.
 
@@
 Here, {\it [inline]} is a specifier for Implementation as inline functions.
-A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as an variable.
+A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
 Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
@@
 Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as an variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
+Each memory pool size can be configured as a variable (Line 5 and 11 in Fig.\ref{src:TLSFBuild}).
 Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
 The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
-Lines 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the call port (Lines 2 in Fig.\ref{src:TLSFBuild}).
-Likewise, Lines 13 and 17 call the function for memory allocation.
+Line 8 calls the {\it free} function of the TLSF memory allocator component.
+{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
+Likewise, Line 13 and 17 call the function for memory allocation.
 The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.

### 2017-11-13 ipsj/paper.tex
Add Evaluation

@@
 
-\subsection{Extended mruby on TECS (仮)}
-
-\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}
-
 \subsection{TINET+TECS}
@@
 \end{figure}
+
+\subsection{Extended mruby on TECS (仮)}
+
+\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}
 
@@
 
+This section describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
+
+% \subsection{Evaluation environment}
+
+GR-PEACH was employed as the evaluation board.
+Detailed specifications of the board are shown in Table \ref{tab:EvaluationBoardEnvironment}.
+We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
+To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.
+
+\begin{table}[t]
+    \centering
+    \caption{Evaluation Board Environment}
+    \begin{tabular}{l|l}
+        \hline\hline
+        Board           &   GR-PEACH                \\
+        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
+        Flash ROM       &   8 MB                    \\
+        RAM             &   10 MB                   \\
+        LAN Controller  &   LAN8710A                \\
+        \hline
+    \end{tabular}
+    \label{tab:EvaluationBoardEnvironment}
+\end{table}
+
+\subsection{Performance of TINET+TECS}
+
+To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
+
+The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
+For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
+In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
+\ref{fig:ComponentProtocolStack}.
+For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
+In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
+The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
+As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \caption{Execution times of TINET and TINET+TECS}
+    \label{fig:EvaluationOfExecutionTime}
+\end{figure}
+
+The memory consumptions of TINET and TINET+TECS are compared in Table \ref{tab:EvaluationOfMemoryConsumption}.
+The memory consumption of TINET+TECS is about 1\% higher than that of TINET, as the data and processes such as initialization of cells, descriptors, function tables, and skeleton functions needed to manage TECS components increase memory consumption.
+
+\begin{table}[t]
+    \centering
+    \caption{Memory consumption of TINET and TINET+TECS}
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                    &   text       &  data    &   bss      &  total     \\ \hline
+        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
+        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+        \hline
+        \multicolumn{5}{r}{Including the application and kernel objects}
+    \end{tabular}
+    \label{tab:EvaluationOfMemoryConsumption}
+\end{table}
+
+As shown in Table \ref{tab:EvaluationOfConfigurability}, the code lines for modification were measured to demonstrate the improved configurability.
+This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
+
+\begin{table}[t]
+    \centering
+    \caption{Modified code lines of CDL}
+    \begin{tabular}{c|r|r|r}
+        \hline\hline
+                         &   Size       &   Size (-- Default) & CDL  \\ \hline
+        Default          &   325.23 KB  &              0 KB   &  0 lines   \\
+        I                &   305.40 KB  &       -- 19.83 KB   & 18 lines   \\
+        I + I\hspace{-.1em}I &   304.12 KB  &   -- 21.10 KB   & 27 lines   \\
+        I + I\hspace{-.1em}I + I\hspace{-.1em}I\hspace{-.1em}I & 303.45 KB & -- 21.77 KB  & 32 lines \\
+        \hline
+        \multicolumn{4}{l}{I: Remove TCP}\\
+        \multicolumn{4}{l}{I\hspace{-.1em}I: Remove ICMP}\\
+        \multicolumn{4}{l}{I\hspace{-.1em}I\hspace{-.1em}I: Change network buffer (Remove memory pools)}
+    \end{tabular}
+    \label{tab:EvaluationOfConfigurability}
+\end{table}
+
+\subsection{Performance of TLSF+TECS}
+
 %5

### 2017-11-14 ipsj/paper.tex
Update References

@@
 Therefore, applying scripting languages to embedded systems is difficult.
-To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
+To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{mrubyonTECS3}.
 This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
@@
 This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
-In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS \cite{par:TINET+TECS}, is comprised, and it is possible to utilize TINET function from mruby programs.
+In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
 
@@
 This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
-The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
+The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
 The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
@@
 Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
-The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS2} which is introduced in Section \ref{sec:mrubyonTECS}.
+The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3} which is introduced in Section \ref{sec:mrubyonTECS}.
 Line 8 calls the {\it free} function of the TLSF memory allocator component.

### 2017-11-14 ipsj/paper.tex
Update Introduction
Add contributions

@@
 In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
-
 TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
@@
 TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
-
+In the case of only sending values obtained by sensors, it is better to custimize easily, such as removing unused functions.
+The improved configurability leads to satisfy strict memory constrains of embedded systems.
 In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
@@
 \begin{enumerate}
-\item {\bf :}
-\item {\bf :}
-\item {\bf :}
-\item {\bf :}
+\item {\bf Applicable to various devices:}
+The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
+mruby code is portable, so it is possible to run the same program on different devices.
+
+\item {\bf Improve configurability:}
+Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
+In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.
+
+\item {\bf Thread-safe memory allocator:}
+TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
+Moreover, each thread can easily set its own heap area.
+
 \end{enumerate}

### 2017-11-14 ipsj/paper.tex
Add TLSF+TECS's use cases

@@
 
+\subsubsection{Multiple RiteVM}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
+    \caption{Component description of RiteVM and TLSF+TECS}
+    \label{fig:UseCase_mruby}
+\end{figure}
+
+The proposed framework uses TLSF memory allocator for memory management of RiteVMs.
+However, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple, memory contention will occur.
+As a RiteVM allocates and deallocates memory at high frequency, the memory contention immediately occurs in the case of multiple VMs.
+
+The TLSF components are connected to the RiteVMs to hold its own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
+Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
+Fig.\ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
+It is easy to set different heap areas in each RiteVM.
+In addition, RiteVM performs incremental GC (Garbage Collection), and a VM that started GC does not disturb the execution of other VMs by running GC.
+
+\subsubsection{Memory management for data sending and receiving}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
+    \caption{Fixed-size and TLSF memory allocator components}
+    \label{fig:UseCase_TINET}
+\end{figure}
+
+In TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer, so the role of allocator is important.
+TINET+TECS combines all components that manage memory with the allocator.
+The TLSF memory allocator can execute at the same speed as compared with the fixed-size memory allocator which TOPPERS/ASP3 supports as standard, and can improve the memory efficiency.
+In addition, as shown in Fig.\ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
+TLSF+TECS efficiently manages the memory without selecting a memory pool.
+Since TINET+TECS is component-based system, TLSF+TECS can be easily extended to TINET+TECS.
+
 %4

### 2017-11-14 ipsj/paper.tex
Add TLSF+TECS's use cases
Add mruby's use case

@@
 
-\subsection{Extended mruby on TECS (仮)}
-
-\textcolor{red}{TODO: mrubyからTINETを利用する説明とかmrubyでエコーサーバのコード例とか}
-
 \subsection{TLSF+TECS}
@@
 %4
+\subsection{Use case}
+\label{sec:UseCase}
+
+In the proposed framework, applications can call TINET functions such as TCP and UDP from mruby programs because mruby-TECS bridge automatically generates the code linking mruby and C.
+Fig.\ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
+mruby makes it easier to develop applications than existing TINET, i.e., C language.
+
+In the case of a simple application, a few functions are only used and there are some unused functions.
+For example, the application only uses a function to send by TCP protocol as shown in Fig.\ref{src:mruby}.
+The proposed framework incorporates TINET+TECS, and can easily custimize such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
+It can be applied to embedded systems with strict memory constraints by removing unused functions.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+begin
+    io = AnalogIO.new(A0, INPUT)
+    cep = TCP.new()	
+    cep.accept
+    loop do		
+        val = io.read  
+        cep.snd val.to_s + "\n"		
+        RTOS.delay(1000)			
+    end
+rescue => e	
+    puts "[ERROR]" + e
+end
+\end{lstlisting}
+\caption{Example of mruby application}
+\label{src:mruby}
+\end{figure}
+
 \section{Evaluation}

### 2017-11-14 ipsj/paper.tex
Add Related Work

@@
 
+To develop the software of IoT systems, several approaches have been proposed \cite{par:frameworkCPS} such as General-purpose Programming Languages (GPLs), Wireless Sensor Network (WSN) macroprogramming, Cloud-based platforms, and Model-Driven Development (MDD).
+
+The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
+However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
+
+WSN macroprogramming provides abstractions to specify high-level collaborative behaviors, while hiding low-level details such as message passing and state maintenance.
+nesC, a programming language used to build applications for the TinyOS platform \cite{par:nesc}, has been proposed.
+nesC/TinyOS is designed for WSN nodes with limited resources e.g., 8 kilobytes of program memory, 512 bytes of RAM, but not supported TCP/IP implementation.
+
+Cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop).
+In addition, it offers the ease deployment and evolution because the application logic is centrally located in a cloud platform.
+However, it is platform-dependent design, and restricts developers in terms of functionality such as in-network aggregation or direct node-to-node communication locally.
+
+To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
+MDD provides the benefits of re-usable, platform-independent, extensible design, however it needs long development time to build a MDD system.
+
 %6

### 2017-11-15 ipsj/paper.tex
Fix title
Add Dynamic Connection

@@
 
-\title{Component-based Software Development Framework \\for Embedded IoT Devices（仮）}
+\title{Component-Based mruby Platform for IoT Devices}
 
@@
 
+\subsubsection{Dynamic connection in TECS}
+\label{sec:DynamicConnection}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
+    \vspace{-3mm} \caption{Dynamic connection}
+    \vspace{-1mm} \label{fig:DynamicConnection}
+\end{figure}
+
+TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
+In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
+Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
+Dynamically generating components causes a good deal of memory consumption, which is a serious problem for embedded systems with strict memory constraints.
+The proposed framework can take advantage of the componentization in TINET while satisfying the memory constraint because components are statically generated and dynamically connected in TECS.
+
+TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
+For example, when processing with the HTTP protocol, CEP passively opens with an REP of port number 80.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \caption{Dynamic connection between CEP and REP}
+    \label{fig:DynamicConnectionUseCase}
+\end{figure}
+
+To utilize dynamic connectivity, a selector should be defined.
+A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
+The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
+{\it [ref\_desc]} is used to identify call ports referring to descriptors. 
+In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
+
+A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig.
+\ref{src:DynamicCDLcode}).
+The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
+The call port with the {\it [dynamic]} specifier is not optimized and is allocated in RAM using a plug-in.
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+signature sRepSelector {
+    void  getRep([out]Descriptor(sREP4) *desc,
+                 [in]int_t i);
+};
+celltype tRepSelector {
+    entry sRepSelector eRepSelector;
+    [ref_desc]
+        call sREP4 cREP[NUM_REP];
+};
+celltype tTCPCEP {
+    call sRepSelector cRepSelector;
+    [dynamic]
+        call sREP4 cREP;
+    /* Omit: other call/entry ports */
+    /* Omit: attributes and variables */
+};
+\end{lstlisting}
+\caption{Signature and celltype description for the dynamic connection}
+\label{src:DynamicCDLcode}
+\end{figure}
+
+Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
+The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
+The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
+First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
+The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
+Next, the descriptor is set (Line 5 in Fig.
+\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.
+\ref{src:DynamicCcode}).
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+eAPI_accept (.., ..) {
+    /* Get a descriptor of intended REP cell */
+    cRepSelector_getRep(&desc, repid);
+    /* Set the descriptor */
+    cREP_set_descriptor(desc);
+    /* Call the function of intended REP cell */
+    cREP_getEndpoint();
+}
+\end{lstlisting}
+\caption{Accept function (a dynamic connection example)}
+\label{src:DynamicCcode}
+\end{figure}
+
 \subsection{TLSF+TECS}
@@
 
+\subsection{Dynamic connection}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \vspace{-1mm} \caption{Component diagrams for without/with the dynamic connection cases}
+    \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
+\end{figure}
+
+Memory consumption without and with TECS dynamic connection was then evaluated.
+As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
+As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
+The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig.
+\ref{fig:ComparisonOfDynamicConnection}.
+Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.
+
+Memory consumption of without and with dynamic connection is shown in TABLE \ref{fig:EvaluationOfDynamicConnection}.
+The dynamic connection case consumes the more RAM memory because, as mentioned in Section \ref{sec:DynamicConnection}, call ports with {\it [dynamic]} are not optimized and allocated in RAM areas.
+However, the overall memory consumption is lower under the proposed framework.
+
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
+%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
+%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
+% \end{figure}
+\begin{table}[t]
+    \centering
+    \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
+    {\tabcolsep = 1mm
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                &  CEP:1 REP:1 & CEP:1 REP:5 & CEP:2 REP:5 & CEP:5 REP:10 \\ \hline
+        without &  324.98 KB   & 325.34 KB   & 326.39 KB   & 331.68 KB   \\
+        with    &  325.23 KB   & 325.32 KB   & 327.24 KB   & 330.48 KB   \\
+        \hline
+    \end{tabular}
+    }
+    \label{fig:EvaluationOfDynamicConnection}
+\end{table}
+
+\begin{table}[t]
+    \centering
+    \caption{CDL code lines of without/with dynamic connection}
+    \begin{tabular}{l|r|r|r}
+        \hline\hline
+                     &  without  &  with  &  Diff  \\ \hline
+        CEP:1 REP:1  &  344 lines     &  347 lines  &  -3 lines   \\
+        CEP:1 REP:5  &  369 lines     &  367 lines  &   2 lines   \\
+        CEP:2 REP:5  &  387 lines     &  382 lines  &   5 lines   \\
+        CEP:5 REP:10 &  485 lines     &  445 lines  &  40 lines   \\
+        \hline
+    \end{tabular}
+    \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
+\end{table}
+
+\begin{figure}[t]
+ \centering
+ \begin{lstlisting}
+/* without Dynamic Connection */
+cell tTCPCEP TCPCEP_000 {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+cell tTCPCEP TCPCEP_001 {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+..
+cell tTCPCEP TCPCEP_00n {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+ \end{lstlisting}
+ \centering
+ \begin{lstlisting}
+/* with Dynamic Connection */
+cell tRepSelector RepSelector {
+    cREP[0] = REP_000.eREP;
+    ..
+    cREP[n] = REP_00n.eREP;
+};
+cell tTCPCEP TCPCEP_000 {
+    cRepSelector = RepSelector.eRepSelector;
+};
+cell tTCPCEP TCPCEP_001 {
+    cRepSelector = RepSelector.eRepSelector;
+};
+..
+cell tTCPCEP TCPCEP_00n {
+    cRepSelector = RepSelector.eRepSelector;
+};
+ \end{lstlisting}
+ \caption{Two CDL codes (without/with dynamic connection)}
+ \label{src:ComparisonOfCDL}
+\end{figure}
+
+The code lines in CDL of without and with the dynamic connection is shown in TABLE \ref{tab:EvaluationOfConfigurabilityByDynamicConnection} to demonstrate improved configurability.
+As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
+In the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
+In the right panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
+It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
+
 \subsection{Performance of TLSF+TECS}

### 2017-11-15 ipsj/paper.tex
Add Conclusion

@@
 
+This paper presented an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
+In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS brigde.
+Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
+TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
+It improves on TINET's configurability while suppressing the overhead of componentization.
+Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
+This paper also presented the dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
+TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.
+TLSF+TECS is a component-based dynamic allocator.
+Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
+The heap size can be easily changed because it is set as a variable of the component.
+In addition, the RiteVMs, TLSF+TECS, TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
+Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.
+In the future, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.\newline
+
 \begin{acknowledgment}

### 2017-11-15 ipsj/paper.tex
Add Acknowledgments
Add Abstract

@@
 
+High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
+To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
+This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
+The proposed framework can call Tomakomai InterNETworking (TINET), a Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stack for use in embedded systems, functions from mruby programs.
+In addition, this paper proposes two component-based functionality such as a componentized TINET--TINET+TECS--and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator--TLSF+TECS--.
+TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionality.
+TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
+TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
+The results of an experimental comparison between the proposed component-based and original TINETs show that the execution time and memory consumption overhead are reduced and the configurability is improved.
+
 \end{abstract}
@@
 \begin{acknowledgment}
-
+This work was supported by JSPS KAKENHI Grant Number 15H05305.
+The authors would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
 \end{acknowledgment}

### 2017-11-15 ipsj/paper.tex
Add Keywords
Update Related Work

@@
 \begin{keyword}
-
+software development framework, component-based development, embedded systems, Internet of Things
 \end{keyword}
@@
 TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
-In the case of only sending values obtained by sensors, it is better to custimize easily, such as removing unused functions.
-The improved configurability leads to satisfy strict memory constrains of embedded systems.
+In the case of only sending values obtained by sensors, it is better to easily customize the minimum configuration of the TCP/IP protocol stack, such as removing unused functions.
+The improved configurability leads to satisfying strict memory constraints of embedded systems.
 In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
@@
 The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
-mruby code is portable, so it is possible to run the same program on different devices.
+mruby code is portable.
+Therefore, it is possible to run the same program on different devices.
 
@@
 TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
-Moreover, each thread can easily set its own heap area.
+Moreover, each thread can easily set own heap area.
 
@@
 
-The components of a TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
+The components of the TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
 Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
@@
 
-In TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer, so the role of allocator is important.
+In the TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer.
+Therefore, the role of allocator is important.
 TINET+TECS combines all components that manage memory with the allocator.
@@
 TLSF+TECS efficiently manages the memory without selecting a memory pool.
-Since TINET+TECS is component-based system, TLSF+TECS can be easily extended to TINET+TECS.
+TLSF+TECS can be easily extended to TINET+TECS since TINET+TECS is a component-based system.
 
@@
 For example, the application only uses a function to send by TCP protocol as shown in Fig.\ref{src:mruby}.
-The proposed framework incorporates TINET+TECS, and can easily custimize such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
+The proposed framework incorporates TINET+TECS, and can easily customize the TCP/IP protocol stack such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
 It can be applied to embedded systems with strict memory constraints by removing unused functions.
@@
 However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
+Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
 
@@
 
-Cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop).
+Cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop) \cite{par:cloud-based}.
 In addition, it offers the ease deployment and evolution because the application logic is centrally located in a cloud platform.
 However, it is platform-dependent design, and restricts developers in terms of functionality such as in-network aggregation or direct node-to-node communication locally.
+The cloud-based mruby framework, enzi Board \cite{url:enzi}, has been proposed.
+enzi can be developed and simulated on the Web, and developer can download and run the program on the board.
 
 To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
-MDD provides the benefits of re-usable, platform-independent, extensible design, however it needs long development time to build a MDD system.
+MDD provides the benefits of re-usable, platform-independent, extensible design, however it needs long development time to build an MDD system.
 

### 2017-11-15 ipsj/paper.tex
Fix typo

@@
 Therefore, applying scripting languages to embedded systems is difficult.
-To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{mrubyonTECS3}.
+To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{par:mrubyonTECS3}.
 This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

### 2017-11-16 ipsj/paper.tex
Fix the pointed

@@
 This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
-The proposed framework can call Tomakomai InterNETworking (TINET), a Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stack for use in embedded systems, functions from mruby programs.
-In addition, this paper proposes two component-based functionality such as a componentized TINET--TINET+TECS--and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator--TLSF+TECS--.
-TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionality.
+The proposed framework can enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
+In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
 TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
 TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
-The results of an experimental comparison between the proposed component-based and original TINETs show that the execution time and memory consumption overhead are reduced and the configurability is improved.
+Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
 
@@
 \begin{keyword}
-software development framework, component-based development, embedded systems, Internet of Things
+Internet of Things, software development framework, component-based development, embedded systems
 \end{keyword}
@@
 In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
-TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by deviding memory blocks in two stages.
+TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by dividing memory blocks in two stages.
 In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
-TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has its own heap area.
+TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has own heap area.
 
@@
 \item {\bf Improve configurability:}
-Because TINET+TECS is a component-based system, its software can flexibly change as system's configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
+Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
 In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.
@@
 The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
-Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
+Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
 TECS components support various embedded drivers such as motor and sensor drivers.
@@
 In addition, TLSF+TECS, a component-based dynamic memory allocator, is used for memory management of mruby's RiteVMs and TCP/IP buffers in the proposed framework.
-Since each component holds its own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption which is a merit of TLSF.
+Since each component holds own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption which is a merit of TLSF.
 
@@
 
-In TINET, the amount of data copying between each protocol layers is minimized.
+In TINET, the amount of data copying between each protocol layer is minimized.
 In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
@@
 
-A simple fixed-size memory block allocator results in waste of up to 50\%, but TLSF classifies it finely in two steps, so it is a memory efficient algorithm.
+A simple fixed-size memory block allocator results in the waste of up to 50 \%.
+However, TLSF classifies it finely in two steps.
+Therefore, it is a memory efficient algorithm.
 In addition, TLSF searches at the same speed and at high speed, $O(1)$.
@@
 A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
-Each component holds its own heap area, so even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
+Each component holds own heap area.
+Therefore, even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
 
@@
 Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as a variable (Line 5 and 11 in Fig.\ref{src:TLSFBuild}).
+Each memory pool size can be configured as a variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
 Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
@@
 {\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
-Likewise, Line 13 and 17 call the function for memory allocation.
+Likewise, Lines 13 and 17 call the function for memory allocation.
 The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
@@
 
-The TLSF components are connected to the RiteVMs to hold its own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
+The TLSF components are connected to the RiteVMs to hold own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
 Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
@@
 
-To develop the software of IoT systems, several approaches have been proposed \cite{par:frameworkCPS} such as General-purpose Programming Languages (GPLs), Wireless Sensor Network (WSN) macroprogramming, Cloud-based platforms, and Model-Driven Development (MDD).
-
-The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
-However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
-Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
+To develop the software of IoT systems, several approaches have been proposed \cite{par:frameworkCPS} such as Wireless Sensor Network (WSN) macroprogramming, Cloud-based platforms, and Model-Driven Development (MDD), General-purpose Programming Languages (GPLs).
 
@@
 
+The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
+However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
+Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
+
+The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
+In addition, mruby on TECS supports legacy code such as motor driver.
+mruby has the same grammar as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
+
 %6
@@
 TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
-It improves on TINET's configurability while suppressing the overhead of componentization.
+It improves on TINET configurability while suppressing the overhead of componentization.
 Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
-This paper also presented the dynamic connection, a new TECS method, to enable dynamic processing while reducing memory consumption.
+
+This paper also presented the dynamic connection, a new TECS functionality, to enable dynamic processing while reducing memory consumption.
 TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.
@@
 The heap size can be easily changed because it is set as a variable of the component.
-In addition, the RiteVMs, TLSF+TECS, TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
+In addition, the RiteVMs, TLSF+TECS, and TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
 Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.

### 2017-11-16 ipsj/paper.tex
Remove an unused section
Final version

@@
     language={c},%
-    basicstyle={\small},%
-    identifierstyle={\small},%
-    commentstyle={\footnotesize\itshape},%
-    keywordstyle={\small},%\bfseries},%
-    ndkeywordstyle={\small},%
-    stringstyle={\small\it},
+    basicstyle={\footnotesize\ttfamily},%
+    identifierstyle={\footnotesize},%
+    commentstyle={\scriptsize\itshape},%
+    keywordstyle={\footnotesize},%\bfseries},%
+    ndkeywordstyle={\footnotesize},%
+    stringstyle={\footnotesize\it},
     frame={tb},
@@
 This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
-The proposed framework can enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
+The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
 In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
@@
 %1
+\vspace{-1mm}
 \section{Introduction}
 \label{sec:Introduction}
+\vspace{-1mm}
 
@@
 
-Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
-Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
-Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
+Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
+Component-Based Development is a design technique that can be applied to reusable software development.
+Verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
 Individual component diagrams enable the visualization of an entire system.
@@
 Therefore, applying scripting languages to embedded systems is difficult.
-To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{par:mrubyonTECS3}.
-This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
+To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS},\cite{par:mrubyonTECS3}.
+This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby},\cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
 
@@
 {\bf Contributions}: The proposed framework provides the following contributions.
-\begin{enumerate}
-\item {\bf Applicable to various devices:}
+
+{\bf Applicable to various devices}
 The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
@@
 
-\item {\bf Improve configurability:}
+{\bf Improve configurability}
 Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
-In addition, the use by TINET+TECS of individual component diagrams enables visualization of an entire system.
-
-\item {\bf Thread-safe memory allocator:}
+In addition, the use of individual component diagrams enables visualization of an entire system.
+
+{\bf Thread-safe memory allocator}
 TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
@@
 
-\end{enumerate}
-
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
+Section \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
 Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
 Section \ref{sec:Evaluation} evaluates the proposed framework.
-Related work is discussed in Section \ref{sec:Related Work}.
-Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.
+Related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.
 
 %2
+\vspace{-1mm}
 \section{System Model}
 \label{sec:System Model}
+\vspace{-1mm}
 
@@
 TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
-
 The following subsection explains TECS, mruby, and mruby on TECS framework.
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/SystemModel.pdf}
-    \caption{System model of the proposed framework}
-    \label{fig:SystemModel}
-\end{figure}
-
+    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
+    \vspace{-1mm} \caption{System model of the proposed framework}
+    \vspace{-2mm} \label{fig:SystemModel}
+\end{figure}
+
+\vspace{-3mm}
 \subsection{TECS}
 \label{sec:TECS}
+\vspace{-1mm}
 
@@
 
-In TECS, component deployment and composition are performed statically.
+TECS statically performs component deployment and composition.
 Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/component_diagram.pdf}
-    \caption{Component Diagram}
-    \label{fig:component}
+    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
+    \vspace{-1mm} \caption{Component Diagram}
+    \vspace{-2mm} \label{fig:component}
 \end{figure}
@@
 Fig.\ref{fig:component} shows a component diagram.
-A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
+A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes and variables.
 An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
@@
 In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
-% TECS code is written in CDL (component description language) file.
 These components are described as follows.
@@
 \begin{description}
-    \item[{\bf Signature Description}]\mbox{}\\
+    \item[{\bf Signature Description}]
         The {\it signature} defines a {\it cell} interface.
@@
 signature sMotor {
-    int32_t getCounts( void );
-    ER resetCounts( void );
+    void initializePort( [in]int32_t type );
     ER setPower( [in]int power );
     ER stop( [in] bool_t brake );
-    ER rotate( [in] int degrees,
-               [in] uint32_t speed_abs,
-                [in] bool_t blocking );
-    void initializePort( [in]int32_t type );
-};
-\end{lstlisting}
-\caption{Signature Description}
-\label{signature}
-\end{figure}
-    \item[{\bf Celltype Description}]\mbox{}\\
+};
+\end{lstlisting}
+\vspace{-2mm} \caption{Signature Description}
+\vspace{-2mm} \label{signature}
+\end{figure}
+    \item[{\bf Celltype Description}]
         The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
@@
     entry sMotor eMotor;
-    attr {
-        int32_t port;
-    };
-    var {
-        int32_t currentSpeed = 0;
-    };
-};
-\end{lstlisting}
-\caption{Celltype Description}
-\label{celltype}
-\end{figure}
-    \item[{\bf Build Description}]\mbox{}\\
+    attr { int32_t port; };
+    var { int32_t currentSpeed = 0; };
+};
+\end{lstlisting}
+\vspace{-2mm} \caption{Celltype Description}
+\vspace{-2mm} \label{celltype}
+\end{figure}
+    \item[{\bf Build Description}]
         The build description is used to instantiate and connect {\it cell}s.
@@
 \end{lstlisting}
-\caption{Build Description}
-\label{build}
+\vspace{-2mm} \caption{Build Description}
+\vspace{-2mm} \label{build}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
-    \caption{Development flow using TECS}
-    \label{fig:TECSFlow}
+    \vspace{-1mm} \caption{Development flow using TECS}
+    \vspace{-2mm} \label{fig:TECSFlow}
 \end{figure}
@@
 
+\vspace{-3mm}
 \subsection{mruby}
 \label{sec:mruby}
+\vspace{-1mm}
 
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/mruby.pdf}
-    \caption{mruby/RiteVM mechanism}
-    \label{fig:mruby}
-\end{figure}
-
+    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
+    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
+    \vspace{-2mm} \label{fig:mruby}
+\end{figure}
+
+\vspace{-3mm}
 \subsection{mruby on TECS}
 \label{sec:mrubyonTECS}
+\vspace{-1mm}
 
@@
 \subsubsection{System Model of mruby on TECS}
-The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
+% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
 Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
 TECS components support various embedded drivers such as motor and sensor drivers.
-
 An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
@@
 
-In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
-However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
-\caption{System model of existing mruby on TECS}
-\label{fig:mrubyonTECS}
-\end{figure}
+In this paper, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
+However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.
+
+% \begin{figure}[t]
+%     \centering
+%     \includegraphics[width=6.5cm,clip]{figure/mrubyonTECS.pdf}
+% \caption{System model of existing mruby on TECS}
+% \label{fig:mrubyonTECS}
+% \end{figure}
 
@@
     \centering
-    \includegraphics[width=6.5cm,clip]{figure/mrubyTECSbridge.pdf}
-\caption{mruby-TECS bridge}
-\label{fig:mrubyTECSbridge}
+    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
+\vspace{-1mm} \caption{mruby-TECS bridge}
+\vspace{-2mm} \label{fig:mrubyTECSbridge}
 \end{figure}
@@
 %3
+\vspace{-1mm}
 \section{Proposed Framework}
 \label{sec:Proposed Framework}
+\vspace{-1mm}
 
@@
 
+\vspace{-3mm}
 \subsection{TINET+TECS}
 \label{sec:TINET+TECS}
+\vspace{-1mm}
 
@@
 
-TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is a real-time operating system (RTOS) developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON\footnote{ITRON is an RTOS developed by the TRON project.} TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
 TINET has been released as an open-source tool.
-
-To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the following functions:
-
-\begin{itemize}
-    \item minimum copy frequency,
-    \item elimination of dynamic memory control,
-    \item asynchronous interfacing,
-    \item error detailing per API.
-\end{itemize}
+To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the functions such as minimum copy frequency, elimination of dynamic memory control, asynchronous interfacing, error detailing per API.
 
@@
 Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
-Users transmit and receive data using a Communication End Point (CEP), an interface that functions like a socket.
+Users send and receive data using a Communication End Point (CEP), an interface that functions like a socket.
 In the transmission process, headers are attached to the data body passed to the CEP at each protocol layer before the data are transmitted from the network device.
@@
 
-In TINET, the amount of data copying between each protocol layer is minimized.
+In TINET, the amount of data copying at each protocol layer is minimized.
 In standard computing systems, the TCP/IP protocol stack has large overheads in terms of execution time and memory consumption because the data are copied at each protocol layer.
-To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of performing data copying.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=7.0cm,clip]{figure/TINETHierarchyDiagram.pdf}
-    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
-    \label{fig:TINETHierarchyDiagram}
+To solve this problem, TINET does pass the pointer of the data buffer between each protocol layer instead of data copying.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
+    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
 \end{figure}
@@
 Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
-In TINET+TECS, the components are divided for each protocol, and functionalities such as input and output functions are defined as respective components.
+In TINET+TECS, the components are divided for each protocol, and functionalities such as input/output functions are defined as respective components.
 By using such small grain components, software visibility is improved.
-The components of each protocol are described in the following.
+The components of each protocol are described as follows.
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
-    \caption{Component diagram of a protocol stack}
-    \label{fig:ComponentProtocolStack}
+    \vspace{-1mm} \caption{Component diagram of a protocol stack}
+    \vspace{-2mm} \label{fig:ComponentProtocolStack}
 \end{figure}
@@
 {\bf Transport layer:}
-tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components TCP (UDP).
+tTCPCEP (tUDPCEP) and tREP are, respectively, CEP and REP components.
 For example, a server program supporting multiple clients can be developed by preparing multiple tTCPCEP components.
-tTCPInput (tUDPInput) and tTCPOutput (tUDPOutput) are components for performing, respectively, receiving and sending processing in the transport layer.
+tTCPInput and tTCPOutput are components for performing, respectively, receiving and sending processing in the transport layer.
 
@@
 
-To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
+To utilize the protocol stack in the same manner in the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and applications.
 The communication object component corresponds to a CEP or REP of the original TINET.
-Application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.
-
-The protocol stack of TINET+TECS supports the coexistence of multiple protocols.
+Application developers can utilize TINET+TECS functionalities by generating and combining as many components as necessary.
+
+TINET+TECS supports the coexistence of multiple protocols.
 Though its use of IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without modification of component implementation.
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/tMemoryAllocator.pdf}
-    \caption{Component diagram of tMemoryAllocator}
-    \label{fig:tMemoryAllocator}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=7.0cm,clip]{figure/SendReceive.pdf}
-    \caption{Differences between in/out and send/receive}
-    \label{fig:SendReceive}
+    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
+    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
+    \vspace{-2mm} \label{fig:tMemoryAllocator}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
+    \vspace{-1mm} \caption{Differences between in/out and send/receive}
+    \vspace{-2mm} \label{fig:SendReceive}
 \end{figure}
@@
 
-\item {\it send} is another specifier for transferring data to a callee from a caller such as {\it in}.
+\item {\it send} is another specifier for transferring data to a callee from a caller.
 The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
@@
 
-\item {\it receive} is another specifier for a caller receiving data from a callee such as {\it out}.
+\item {\it receive} is another specifier for a caller receiving data from a callee.
 The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
@@
 \end{lstlisting}
-\caption{Signature description of the nic driver (An example of send/receive)}
-\label{src:SendReceive}
+\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
+\vspace{-2mm} \label{src:SendReceive}
 \end{figure}
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/DynamicConnection.pdf}
-    \vspace{-3mm} \caption{Dynamic connection}
-    \vspace{-1mm} \label{fig:DynamicConnection}
-\end{figure}
-
-TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
-In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
+    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
+    \vspace{-1mm} \caption{Dynamic connection}
+    \vspace{-2mm} \label{fig:DynamicConnection}
+\end{figure}
+
+TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig.\ref{fig:DynamicConnection}) as a new functionality.
+In Fig.\ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
 Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
@@
 
-TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
+TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig.\ref{fig:DynamicConnectionUseCase}.
 In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
@@
     \centering
-    \includegraphics[width=7.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
-    \caption{Dynamic connection between CEP and REP}
-    \label{fig:DynamicConnectionUseCase}
+    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
+    \vspace{-2mm} \label{fig:DynamicConnectionUseCase}
 \end{figure}
@@
 A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
-The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
+The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig.\ref{src:DynamicCDLcode}).
 {\it [ref\_desc]} is used to identify call ports referring to descriptors. 
-In the case shown in Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
+In the case of Fig.\ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
 
@@
 \end{lstlisting}
-\caption{Signature and celltype description for the dynamic connection}
-\label{src:DynamicCDLcode}
-\end{figure}
-
-Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
+\vspace{-1mm} \caption{Signature and celltype description for the dynamic connection}
+\vspace{-2mm} \label{src:DynamicCDLcode}
+\end{figure}
+
+Fig.\ref{src:DynamicCcode} shows a sample code of the dynamic connection.
 The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
-The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
-First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
+The dynamic connection in the function is performed as shown in Fig.\ref{src:DynamicCcode}.
+First, the descriptor of REP to be joined is obtained (Line 3 in Fig.\ref{src:DynamicCcode}).
 The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
-Next, the descriptor is set (Line 5 in Fig.
-\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.
-\ref{src:DynamicCcode}).
+Next, the descriptor is set (Line 5 in Fig.\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.\ref{src:DynamicCcode}).
 
@@
 \end{lstlisting}
-\caption{Accept function (a dynamic connection example)}
-\label{src:DynamicCcode}
-\end{figure}
-
+\vspace{-1mm} \caption{Accept function (a dynamic connection example)}
+\vspace{-2mm} \label{src:DynamicCcode}
+\end{figure}
+
+\vspace{-3mm}
 \subsection{TLSF+TECS}
 \label{sec:TLSF+TECS}
+\vspace{-1mm}
 
@@
 TLSF memory allocator has the following features.
-\begin{description}
-    \item[Real-time property]\mbox{}\\
+
+{\bf Real-time property:}
 The worst execution time required for allocating and deallocating memory does not depend on the data size.
 TLSF always works with $O(1)$, and it is possible to estimate the response time.
-    % \item[Fast speed]\mbox{}\\
-    %     In addition to being able to always estimate the worst execution time, TLSF is executed at high speed.
-    \item[Efficient memory consumption]\mbox{}\\
+
+{\bf Efficient memory consumption:}
 Memory efficiency is improved by suppressing memory fragmentation.
 Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
-\end{description}
 
@@
 Consider a case where a request, $malloc(100)$, is called to allocate a memory.
-In the first step, it is classified by the most significant bit of the requested memory size.
+First, it is classified by the most significant bit of the requested memory size.
 In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
-In the second step, it is further classified.
+Second, it is further classified.
 In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
@@
     \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
-    \caption{TLSF Algorithm}
-    \label{fig:TLSF}
+    \vspace{-1mm} \caption{TLSF Algorithm}
+    \vspace{-2mm} \label{fig:TLSF}
 \end{figure}
@@
   int    initializeMemoryPool(void);
-    void   *calloc( [in]size_t nelem,
-                    [in]size_t elem_size );
-    void   *malloc( [in]size_t size );
-    void   *realloc( [in]const void *ptr,
-                     [in]size_t new_size );
-    void   free( [in]const void *ptr );
-};
-\end{lstlisting}
-\caption{Signature description of memory management}  
-\label{src:TLSFSignature}
+  void   *calloc([in]size_t nelem,[in]size_t size);
+  void   *malloc([in]size_t size);
+  void   *realloc([in]const void *ptr,[in]size_t size);
+  void   free([in]const void *ptr);
+};
+\end{lstlisting}
+\vspace{-1mm} \caption{Signature description of memory management}  
+\vspace{-2mm} \label{src:TLSFSignature}
 \end{figure}
@@
 celltype tTLSFMalloc {
-    [inline]
-        entry  sMalloc  eMalloc;
+    [inline]entry  sMalloc  eMalloc;
     attr {
-        /* memory pool size in bytes */
         size_t  memoryPoolSize;
@@
     var {
-        [size_is( memoryPoolSize / 8 )]
-            uint64_t   *pool;
-    };
-};
-\end{lstlisting}
-\caption{Celltype description of TLSF memory allocator component}  
-\label{src:TLSFCelltype}
+        [size_is(memoryPoolSize/8)]uint64_t *pool;
+    };
+};
+\end{lstlisting}
+\vspace{-1mm} \caption{Celltype description of TLSF memory allocator component}  
+\vspace{-2mm} \label{src:TLSFCelltype}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
-    \caption{TLSF before componentization}
-    \label{fig:WithoutTECS}
+    \vspace{-1mm} \caption{TLSF before componentization}
+    \vspace{-2mm} \label{fig:WithoutTECS}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
-    \caption{TLSF after componentization}
-    \label{fig:WithTECS}
+    \vspace{-1mm} \caption{TLSF after componentization}
+    \vspace{-2mm} \label{fig:WithTECS}
 \end{figure}
@@
 \end{lstlisting}
-\caption{Build description of TLSF memory allocator component}
-\label{src:TLSFBuild}
+\vspace{-1mm} \caption{Build description of TLSF memory allocator component}
+\vspace{-2mm} \label{src:TLSFBuild}
 \end{figure}
@@
 \end{lstlisting}
-\caption{Example of TLSF memory allocator component}  
-\label{src:TLSFC}
+\vspace{-1mm} \caption{Example of TLSF memory allocator component}  
+\vspace{-2mm} \label{src:TLSFC}
 \end{figure}
@@
 
-\subsubsection{Multiple RiteVM}
+\subsubsection*{Multiple RiteVM}
 
@@
     \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
-    \caption{Component description of RiteVM and TLSF+TECS}
-    \label{fig:UseCase_mruby}
+    \vspace{-1mm} \caption{Component description of RiteVM and TLSF+TECS}
+    \vspace{-2mm} \label{fig:UseCase_mruby}
 \end{figure}
@@
 
-\subsubsection{Memory management for data sending and receiving}
+\subsubsection*{Memory management for data sending and receiving}
 
@@
     \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
-    \caption{Fixed-size and TLSF memory allocator components}
-    \label{fig:UseCase_TINET}
+    \vspace{-1mm} \caption{Fixed-size and TLSF memory allocator components}
+    \vspace{-2mm} \label{fig:UseCase_TINET}
 \end{figure}
@@
 %4
+
+\vspace{-3mm}
 \subsection{Use case}
 \label{sec:UseCase}
+\vspace{-1mm}
 
@@
 \centering
-\begin{lstlisting}
+\begin{lstlisting}[language=Ruby]
 begin
@@
 \end{lstlisting}
-\caption{Example of mruby application}
-\label{src:mruby}
-\end{figure}
-
+\vspace{-1mm} \caption{Example of mruby application}
+\vspace{-2mm} \label{src:mruby}
+\end{figure}
+
+\vspace{-1mm}
 \section{Evaluation}
 \label{sec:Evaluation}
+\vspace{-1mm}
 
 This section describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
-
-% \subsection{Evaluation environment}
-
 GR-PEACH was employed as the evaluation board.
@@
     \end{tabular}
+    \vspace{-2mm}
     \label{tab:EvaluationBoardEnvironment}
@@
 
+\vspace{-3mm}
 \subsection{Performance of TINET+TECS}
+\vspace{-1mm}
 
@@
     \centering
-    \includegraphics[width=7.5cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \caption{Execution times of TINET and TINET+TECS}
-    \label{fig:EvaluationOfExecutionTime}
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
+    \vspace{-2mm} \label{fig:EvaluationOfExecutionTime}
 \end{figure}
@@
     \centering
-    \caption{Memory consumption of TINET and TINET+TECS}
+    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
+    \vspace{-1mm}
     \begin{tabular}{c|r|r|r|r}
@@
     \end{tabular}
+    \vspace{-2mm}
     \label{tab:EvaluationOfMemoryConsumption}
@@
     \centering
-    \caption{Modified code lines of CDL}
+    \vspace{-1mm} \caption{Modified code lines of CDL}
+    \vspace{-1mm}
     \begin{tabular}{c|r|r|r}
@@
     \end{tabular}
+    \vspace{-2mm}
     \label{tab:EvaluationOfConfigurability}
@@
 
+\vspace{-3mm}
 \subsection{Dynamic connection}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8.0cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \vspace{-1mm} \caption{Component diagrams for without/with the dynamic connection cases}
-    \vspace{-1mm} \label{fig:ComparisonOfDynamicConnection}
+\vspace{-1mm}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection}
+    \vspace{-2mm} \label{fig:ComparisonOfDynamicConnection}
 \end{figure}
@@
 Memory consumption without and with TECS dynamic connection was then evaluated.
-As shown in the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
+As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
 As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
-The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right panel of Fig.
+The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right paneof Fig.
 \ref{fig:ComparisonOfDynamicConnection}.
@@
     \centering
-    \caption{Memory consumption in two cases\protect\linebreak (with/without dynamic connection)}
+    \vspace{-1mm} \caption{Memory consumption in two cases\\(with/without dynamic connection)}
+    \vspace{-1mm}
     {\tabcolsep = 1mm
@@
     \end{tabular}
+    \vspace{-2mm}
     }
@@
     \centering
-    \caption{CDL code lines of without/with dynamic connection}
+    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
+    \vspace{-1mm}
     \begin{tabular}{l|r|r|r}
@@
     \end{tabular}
+    \vspace{-2mm}
     \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
@@
  \end{lstlisting}
- \caption{Two CDL codes (without/with dynamic connection)}
- \label{src:ComparisonOfCDL}
+ \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
+ \vspace{-2mm} \label{src:ComparisonOfCDL}
 \end{figure}
@@
 As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
-In the left panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
-In the right panel of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
+In the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
+In the right of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
 It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
 
-\subsection{Performance of TLSF+TECS}
-
 %5
+\vspace{-1mm}
 \section{Related Work}
 \label{sec:Related Work}
+\vspace{-1mm}
 
@@
 nesC, a programming language used to build applications for the TinyOS platform \cite{par:nesc}, has been proposed.
-nesC/TinyOS is designed for WSN nodes with limited resources e.g., 8 kilobytes of program memory, 512 bytes of RAM, but not supported TCP/IP implementation.
+nesC/TinyOS is designed for WSN nodes with limited resources e.g., 8 KB of program memory, 512 bytes of RAM, but not supported TCP/IP implementation.
 
@@
 To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
-MDD provides the benefits of re-usable, platform-independent, extensible design, however it needs long development time to build an MDD system.
+MDD provides the benefits of reusable, platform-independent, extensible design, however it needs long development time to build MDD systems.
 
@@
 The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
-In addition, mruby on TECS supports legacy code such as motor driver.
-mruby has the same grammar as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
+In addition, the extended mruby on TECS supports legacy code such as a motor driver.
+mruby has the same syntax as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
 
 %6
+\vspace{-1mm}
 \section{Conclusion}
 \label{sec:Conclusion}
+\vspace{-1mm}
 
@@
 Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
-The heap size can be easily changed because it is set as a variable of the component.
-In addition, the RiteVMs, TLSF+TECS, and TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
+In addition, the RiteVMs, TINET+TECS, and TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
 Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.
@@
 
+\vspace{-2mm}
 \begin{acknowledgment}
 This work was supported by JSPS KAKENHI Grant Number 15H05305.
-The authors would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
+We would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
 \end{acknowledgment}
+\vspace{-2mm}
 

### 2017-12-05 master/paper.tex
Add master for master's thesis

--- 2017-11-16 ipsj/paper.tex
@@
-\documentclass[JIP]{ipsj_v2/UTF8/ipsj}
+% Master Thesis
+% For Japanese
+% \documentclass[a4j,12pt,oneside,openany]{jsbook}
+% For English
+\documentclass[a4j,12pt,oneside,openany,english]{jsbook}
 
@@
 
-\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
-\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
-\def\|{\verb|}
-
-\setcounter{volume}{22}% vol22=2014
-\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
-\setcounter{page}{1}
-
-\received{2014}{3}{4}
-%\rereceived{2011}{10}{1}   % optional
-%\rerereceived{2011}{10}{31} % optional
-\accepted{2014}{8}{1}
-
-\usepackage[varg]{txfonts}%%!!
-\makeatletter%
-\input{ot1txtt.fd}
-\makeatother%
+% jsbook to report
+\usepackage{styles/utf8/book2report}
+
+% For Theorem, Definition, Example, Proof etc.
+\usepackage{styles/utf8/thesis}
+
+% Title Font
+\renewcommand{\headfont}{\bfseries}
+
+% If the number of pages is small
+\renewcommand{\baselinestretch}{1.1}
 
@@
 
-\title{Component-Based mruby Platform for IoT Devices}
-
-\affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
-\affiliate{NAGOYA}{Graduate School of Informatics, Nagoya University}
-\affiliate{OKUMA}{OKUMA Corporation}
-
-\author{Takuro Yamamoto}{OSAKA}
-\author{Takuma Hara}{NAGOYA}
-\author{Takuya Ishikawa}{NAGOYA}
-\author{Hiroshi Oyama}{OKUMA}
-\author{Hiroaki Takada}{NAGOYA}
-\author{Takuya Azumi}{OSAKA}
+% Title
+\thispagestyle{empty}
+\begin{center}
+\vspace*{5mm}
+{\Huge {\bf Master's Thesis}}\\
+\vspace{2cm}
+% {\Large 題\hspace{8mm}目}\\
+% \vspace{1cm}
+\underline{\LARGE{Component-Based mruby Platform for IoT Devices}} \\
+% \vspace{0.5cm}
+% \underline{\LARGE{My Bachelor Thesis}} \\
+\vspace{12mm}
+{\large Supervisor}\\
+\vspace{6mm}
+\underline{\Large Professor Toshimitsu Ushio}\\
+　\\
+\underline{\Large Assistant Professor Takuya Azumi}\\
+\vspace{8mm}
+{\large By}\\
+\vspace{6mm}
+\underline{\Large Takuro Yamamoto}\\
+\vspace{10mm}
+{\Large February 7, 2018}\\
+\vspace{14mm}
+{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
+\end{center}
+\clearpage
+\setcounter{page}{0}
+\pagenumbering{roman}
 
@@
 
-\begin{keyword}
-Internet of Things, software development framework, component-based development, embedded systems
-\end{keyword}
-
-\maketitle
+% Contens
+\clearpage
+\tableofcontents
+\clearpage
+\setcounter{page}{0}
+\pagenumbering{arabic}
 
 %1
-\vspace{-1mm}
-\section{Introduction}
+\chapter{Introduction}
 \label{sec:Introduction}
-\vspace{-1mm}
 
@@
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
-Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
-Section \ref{sec:Evaluation} evaluates the proposed framework.
-Related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.
+Chapter \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
+Chapter \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
+Chapter \ref{sec:Evaluation} evaluates the proposed framework.
+Related work is discussed in Chapter \ref{sec:Related Work} and Chapter \ref{sec:Conclusion} concludes this paper.
 
 %2
-\vspace{-1mm}
-\section{System Model}
+\chapter{System Model}
 \label{sec:System Model}
-\vspace{-1mm}
-
-This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
+
+This chapter describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
 The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
@@
 TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
-The following subsection explains TECS, mruby, and mruby on TECS framework.
+The following section explains TECS, mruby, and mruby on TECS framework.
 
@@
     \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
-    \vspace{-1mm} \caption{System model of the proposed framework}
-    \vspace{-2mm} \label{fig:SystemModel}
-\end{figure}
-
-\vspace{-3mm}
-\subsection{TECS}
+    \caption{System model of the proposed framework}
+    \label{fig:SystemModel}
+\end{figure}
+
+\section{TECS}
 \label{sec:TECS}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
-    \vspace{-1mm} \caption{Component Diagram}
-    \vspace{-2mm} \label{fig:component}
-\end{figure}
-
-\subsubsection{Component Model}
+    \caption{Component Diagram}
+    \label{fig:component}
+\end{figure}
+
+\subsection{Component Model}
 Fig.\ref{fig:component} shows a component diagram.
@@
 
-\subsubsection{Component Description}
+\subsection{Component Description}
 In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
@@
 \end{lstlisting}
-\vspace{-2mm} \caption{Signature Description}
-\vspace{-2mm} \label{signature}
+\caption{Signature Description}
+\label{signature}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-2mm} \caption{Celltype Description}
-\vspace{-2mm} \label{celltype}
+\caption{Celltype Description}
+\label{celltype}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-2mm} \caption{Build Description}
-\vspace{-2mm} \label{build}
+\caption{Build Description}
+\label{build}
 \end{figure}
@@
 
-\subsubsection{Development Flow}
+\subsection{Development Flow}
 
@@
     \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
-    \vspace{-1mm} \caption{Development flow using TECS}
-    \vspace{-2mm} \label{fig:TECSFlow}
+    \caption{Development flow using TECS}
+    \label{fig:TECSFlow}
 \end{figure}
@@
 
-\vspace{-3mm}
-\subsection{mruby}
+\section{mruby}
 \label{sec:mruby}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/mruby.pdf}
-    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
-    \vspace{-2mm} \label{fig:mruby}
-\end{figure}
-
-\vspace{-3mm}
-\subsection{mruby on TECS}
+    \caption{mruby/RiteVM mechanism}
+    \label{fig:mruby}
+\end{figure}
+
+\section{mruby on TECS}
 \label{sec:mrubyonTECS}
-\vspace{-1mm}
 
@@
 
-\subsubsection{System Model of mruby on TECS}
+\subsection{System Model of mruby on TECS}
 % The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
@@
 
-\subsubsection{mruby-TECS Bridge}
+\subsection{mruby-TECS Bridge}
 There is a significant difference between the execution times of mruby and C language codes.
@@
     \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
-\vspace{-1mm} \caption{mruby-TECS bridge}
-\vspace{-2mm} \label{fig:mrubyTECSbridge}
+\caption{mruby-TECS bridge}
+\label{fig:mrubyTECSbridge}
 \end{figure}
@@
 %3
-\vspace{-1mm}
-\section{Proposed Framework}
+\chapter{Proposed Framework}
 \label{sec:Proposed Framework}
-\vspace{-1mm}
 
@@
 
-\vspace{-3mm}
-\subsection{TINET+TECS}
+\section{TINET+TECS}
 \label{sec:TINET+TECS}
-\vspace{-1mm}
-
-\subsubsection{TINET}
+
+\subsection{TINET}
 
@@
     \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
-    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
-    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
-\end{figure}
-
-\subsubsection{Component Design of TINET+TECS}
+    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
+    \label{fig:TINETHierarchyDiagram}
+\end{figure}
+
+\subsection{Component Design of TINET+TECS}
 
@@
 
-\subsubsection*{Components of a protocol stack}
+\subsection*{Components of a protocol stack}
 
@@
     \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
-    \vspace{-1mm} \caption{Component diagram of a protocol stack}
-    \vspace{-2mm} \label{fig:ComponentProtocolStack}
+    \caption{Component diagram of a protocol stack}
+    \label{fig:ComponentProtocolStack}
 \end{figure}
@@
 
-\subsubsection*{Memory allocator component}
+\subsection*{Memory allocator component}
 
@@
     \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
-    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
-    \vspace{-2mm} \label{fig:tMemoryAllocator}
+    \caption{Component diagram of tMemoryAllocator}
+    \label{fig:tMemoryAllocator}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
-    \vspace{-1mm} \caption{Differences between in/out and send/receive}
-    \vspace{-2mm} \label{fig:SendReceive}
+    \caption{Differences between in/out and send/receive}
+    \label{fig:SendReceive}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
-\vspace{-2mm} \label{src:SendReceive}
-\end{figure}
-
-\subsubsection{Dynamic connection in TECS}
+\caption{Signature description of the nic driver (An example of send/receive)}
+\label{src:SendReceive}
+\end{figure}
+
+\subsection{Dynamic connection in TECS}
 \label{sec:DynamicConnection}
@@
     \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
-    \vspace{-1mm} \caption{Dynamic connection}
-    \vspace{-2mm} \label{fig:DynamicConnection}
+    \caption{Dynamic connection}
+    \label{fig:DynamicConnection}
 \end{figure}
@@
     \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
-    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
-    \vspace{-2mm} \label{fig:DynamicConnectionUseCase}
+    \caption{Dynamic connection between CEP and REP}
+    \label{fig:DynamicConnectionUseCase}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature and celltype description for the dynamic connection}
-\vspace{-2mm} \label{src:DynamicCDLcode}
+\caption{Signature and celltype description for the dynamic connection}
+\label{src:DynamicCDLcode}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Accept function (a dynamic connection example)}
-\vspace{-2mm} \label{src:DynamicCcode}
-\end{figure}
-
-\vspace{-3mm}
-\subsection{TLSF+TECS}
+\caption{Accept function (a dynamic connection example)}
+\label{src:DynamicCcode}
+\end{figure}
+
+\section{TLSF+TECS}
 \label{sec:TLSF+TECS}
-\vspace{-1mm}
-
-\subsubsection{TLSF}
+
+\subsection{TLSF}
 
@@
 
-\subsubsection{TLSF Algorithms}
+\subsection{TLSF Algorithms}
 
@@
     \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
-    \vspace{-1mm} \caption{TLSF Algorithm}
-    \vspace{-2mm} \label{fig:TLSF}
-\end{figure}
-
-\subsubsection{Component Design of TLSF+TECS}
+    \caption{TLSF Algorithm}
+    \label{fig:TLSF}
+\end{figure}
+
+\subsection{Component Design of TLSF+TECS}
 
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature description of memory management}  
-\vspace{-2mm} \label{src:TLSFSignature}
+\caption{Signature description of memory management}  
+\label{src:TLSFSignature}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Celltype description of TLSF memory allocator component}  
-\vspace{-2mm} \label{src:TLSFCelltype}
+\caption{Celltype description of TLSF memory allocator component}  
+\label{src:TLSFCelltype}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
-    \vspace{-1mm} \caption{TLSF before componentization}
-    \vspace{-2mm} \label{fig:WithoutTECS}
+    \caption{TLSF before componentization}
+    \label{fig:WithoutTECS}
 \end{figure}
@@
     \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
-    \vspace{-1mm} \caption{TLSF after componentization}
-    \vspace{-2mm} \label{fig:WithTECS}
+    \caption{TLSF after componentization}
+    \label{fig:WithTECS}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Build description of TLSF memory allocator component}
-\vspace{-2mm} \label{src:TLSFBuild}
+\caption{Build description of TLSF memory allocator component}
+\label{src:TLSFBuild}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Example of TLSF memory allocator component}  
-\vspace{-2mm} \label{src:TLSFC}
+\caption{Example of TLSF memory allocator component}  
+\label{src:TLSFC}
 \end{figure}
@@
 
-\subsubsection*{Multiple RiteVM}
+\subsection*{Multiple RiteVM}
 
@@
     \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
-    \vspace{-1mm} \caption{Component description of RiteVM and TLSF+TECS}
-    \vspace{-2mm} \label{fig:UseCase_mruby}
+    \caption{Component description of RiteVM and TLSF+TECS}
+    \label{fig:UseCase_mruby}
 \end{figure}
@@
 
-\subsubsection*{Memory management for data sending and receiving}
+\subsection*{Memory management for data sending and receiving}
 
@@
     \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
-    \vspace{-1mm} \caption{Fixed-size and TLSF memory allocator components}
-    \vspace{-2mm} \label{fig:UseCase_TINET}
+    \caption{Fixed-size and TLSF memory allocator components}
+    \label{fig:UseCase_TINET}
 \end{figure}
@@
 
-\vspace{-3mm}
-\subsection{Use case}
+\section{Use case}
 \label{sec:UseCase}
-\vspace{-1mm}
 
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Example of mruby application}
-\vspace{-2mm} \label{src:mruby}
-\end{figure}
-
-\vspace{-1mm}
-\section{Evaluation}
+\caption{Example of mruby application}
+\label{src:mruby}
+\end{figure}
+
+\chapter{Evaluation}
 \label{sec:Evaluation}
-\vspace{-1mm}
-
-This section describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
+
+This chapter describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
 GR-PEACH was employed as the evaluation board.
@@
     \centering
-    \vspace{-1mm} \caption{Evaluation Board Environment}
+    \caption{Evaluation Board Environment}
     \begin{tabular}{l|l}
@@
     \end{tabular}
-    \vspace{-2mm}
     \label{tab:EvaluationBoardEnvironment}
@@
 
-\vspace{-3mm}
-\subsection{Performance of TINET+TECS}
-\vspace{-1mm}
+\section{Performance of TINET+TECS}
 
@@
     \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
-    \vspace{-2mm} \label{fig:EvaluationOfExecutionTime}
+    \caption{Execution times of TINET and TINET+TECS}
+    \label{fig:EvaluationOfExecutionTime}
 \end{figure}
@@
     \centering
-    \vspace{-1mm} \caption{Memory consumption of TINET and TINET+TECS}
-    \vspace{-1mm}
+    \caption{Memory consumption of TINET and TINET+TECS}
     \begin{tabular}{c|r|r|r|r}
@@
     \end{tabular}
-    \vspace{-2mm}
     \label{tab:EvaluationOfMemoryConsumption}
@@
     \centering
-    \vspace{-1mm} \caption{Modified code lines of CDL}
-    \vspace{-1mm}
+    \caption{Modified code lines of CDL}
     \begin{tabular}{c|r|r|r}
@@
     \end{tabular}
-    \vspace{-2mm}
     \label{tab:EvaluationOfConfigurability}
@@
 
-\vspace{-3mm}
-\subsection{Dynamic connection}
-\vspace{-1mm}
+\section{Dynamic connection}
 
@@
     \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \vspace{-1mm} \caption{Component diagrams for without/with dynamic connection}
-    \vspace{-2mm} \label{fig:ComparisonOfDynamicConnection}
+    \caption{Component diagrams for without/with dynamic connection}
+    \label{fig:ComparisonOfDynamicConnection}
 \end{figure}
@@
 %     \includegraphics[width=8.0cm,clip]{figure/EvaluationOfDynamicConnection.pdf}
-%     \vspace{-1mm} \caption{Memory consumption in two cases (with/without dynamic connection)}
-%     \vspace{-1mm} \label{fig:EvaluationOfDynamicConnection}
+%     \caption{Memory consumption in two cases (with/without dynamic connection)}
+%     \label{fig:EvaluationOfDynamicConnection}
 % \end{figure}
@@
     \centering
-    \vspace{-1mm} \caption{Memory consumption in two cases\\(with/without dynamic connection)}
-    \vspace{-1mm}
+    \caption{Memory consumption in two cases (with/without dynamic connection)}
     {\tabcolsep = 1mm
@@
     \end{tabular}
-    \vspace{-2mm}
     }
@@
     \centering
-    \vspace{-1mm} \caption{CDL code lines of without/with dynamic connection}
-    \vspace{-1mm}
+    \caption{CDL code lines of without/with dynamic connection}
     \begin{tabular}{l|r|r|r}
@@
     \end{tabular}
-    \vspace{-2mm}
     \label{tab:EvaluationOfConfigurabilityByDynamicConnection}
@@
  \end{lstlisting}
- \vspace{-1mm} \caption{Two CDL codes (without/with dynamic connection)}
- \vspace{-2mm} \label{src:ComparisonOfCDL}
+ \caption{Two CDL codes (without/with dynamic connection)}
+ \label{src:ComparisonOfCDL}
 \end{figure}
@@
 %5
-\vspace{-1mm}
-\section{Related Work}
+\chapter{Related Work}
 \label{sec:Related Work}
-\vspace{-1mm}
 
@@
 %6
-\vspace{-1mm}
-\section{Conclusion}
+\chapter{Conclusion}
 \label{sec:Conclusion}
-\vspace{-1mm}
 
@@
 Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.
-In the future, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.\newline
-
-\vspace{-2mm}
+In the future, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
+
 \begin{acknowledgment}
@@
 \end{acknowledgment}
-\vspace{-2mm}
 
 %Reference
-\bibliographystyle{ipsj_v2/UTF8/ipsjunsrt-e}
+\bibliographystyle{styles/utf8/myjunsrt}
 \bibliography{ref}
 
-% \begin{biography}
-% \profile{Taro Joho}{was born in 1970. He received his M.S. degree from
-% Johoshori University in 1994.
-% He joined
-% the Information
-% Processing Society of Japan in 1994.
-% He is currently an associate professor at
-% \mbox{Johoshori} University.
-% His research interest is online
-% publishing systems. He is a member of the IEEE and ACM\@.}
-% %
-% \profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
-% Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
-% became an associate professor at Gakkai University in 1992 and a
-% professor at Johoshori University in 1997. Her current research
-% interest is online publishing systems. She received the Kiyasu Kinen
-% award in 2010. She is a Board Member of the IPSJ and a member of the
-% IEICE, IEEE-CS, and ACM\@.} 
-% %
-% \profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
-% from Johoshori University in 1994 and has been engaged in the
-% Information Processing Society of Japan since 1994. His research
-% interest is online publishing systems. He is a member of the IEEE and
-% ACM\@.}
-% %
-% \end{biography}
-
 \end{document}

### 2017-12-12 master/paper.tex
Fix Title
Fix the size of figures

@@
 % \vspace{1cm}
-\underline{\LARGE{Component-Based mruby Platform for IoT Devices}} \\
-% \vspace{0.5cm}
-% \underline{\LARGE{My Bachelor Thesis}} \\
+\underline{\LARGE{Component-Based Software Development Framework}} \\
+\vspace{0.5cm}
+\underline{\LARGE{for Embedded IoT Devices}} \\
 \vspace{12mm}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
+    \includegraphics[width=10cm,clip]{figure/SystemModel.pdf}
     \caption{System model of the proposed framework}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
+    \includegraphics[width=10cm,clip]{figure/component_diagram.pdf}
     \caption{Component Diagram}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
+    \includegraphics[width=10cm,clip]{figure/TECSFlow.pdf}
     \caption{Development flow using TECS}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
+    \includegraphics[width=10cm,clip]{figure/mruby.pdf}
     \caption{mruby/RiteVM mechanism}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
+    \includegraphics[width=10cm,clip]{figure/mrubyTECSbridge.pdf}
 \caption{mruby-TECS bridge}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \includegraphics[width=10cm,clip]{figure/TINETHierarchyDiagram.pdf}
     \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
+    \includegraphics[width=10cm,clip]{figure/tMemoryAllocator.pdf}
     \caption{Component diagram of tMemoryAllocator}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
+    \includegraphics[width=10cm,clip]{figure/SendReceive.pdf}
     \caption{Differences between in/out and send/receive}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
+    \includegraphics[width=10cm,clip]{figure/DynamicConnection.pdf}
     \caption{Dynamic connection}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
+    \includegraphics[width=10cm,clip]{figure/TLSF.pdf}
     \caption{TLSF Algorithm}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
+    \includegraphics[width=10cm,clip]{figure/WithoutTECS.pdf}
     \caption{TLSF before componentization}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
+    \includegraphics[width=10cm,clip]{figure/WithTECS.pdf}
     \caption{TLSF after componentization}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
+    \includegraphics[width=10cm,clip]{figure/UseCase_mruby.pdf}
     \caption{Component description of RiteVM and TLSF+TECS}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
+    \includegraphics[width=10cm,clip]{figure/UseCase_TINET.pdf}
     \caption{Fixed-size and TLSF memory allocator components}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \includegraphics[width=10cm,clip]{figure/EvaluationOfExecutionTime.pdf}
     \caption{Execution times of TINET and TINET+TECS}
@@
     \centering
-    \includegraphics[width=8cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \includegraphics[width=10cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
     \caption{Component diagrams for without/with dynamic connection}

### 2017-12-20 master/paper.tex
Follow the comments

@@
 The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
-In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
 TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
@@
 Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
-Component-Based Development is a design technique that can be applied to reusable software development.
+Component-based development is a design technique that can be applied to reusable software development.
 Verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
@@
 In addition, component-based systems are flexible with regard to extensibility and specification changes.
-The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
+The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are used as typical component-based development for embedded systems.
 
@@
 In the case of only sending values obtained by sensors, it is better to easily customize the minimum configuration of the TCP/IP protocol stack, such as removing unused functions.
-The improved configurability leads to satisfying strict memory constraints of embedded systems.
+The improved configurability leads to satisfying strict memory constraints of IoT Devices.
 In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
@@
 Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+TECS can be implemented in C, and demonstrates various feature such as source-level portability and fine-grained components.
 
@@
 Fig.\ref{fig:component} shows a component diagram.
-A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes and variables.
+A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes, and variables.
 An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
@@
     ER setPower( [in]int power );
-    ER stop( [in] bool_t brake );
+    ER stop( [in]bool_t brake );
 };
@@
     entry sMotor eMotor;
-    attr { int32_t port; };
-    var { int32_t currentSpeed = 0; };
+    attr {
+        int32_t port;
+    };
+    var {
+        int32_t currentSpeed = 0;
+    };
 };
@@
 signature sNicDriver {
-  void start(
-    [send(sNetworkAlloc),size_is(size)]
-        int8_t *outputp, .., ..);
-  void read(
-    [receive(sNetworkAlloc),size_is(*size)]
-        int8_t **inputp, .., ..);
+    void start( [send(sNetworkAlloc),size_is(size)]int8_t *outputp, .., .. );
+    void read( [receive(sNetworkAlloc),size_is(*size)]int8_t **inputp, .., .. );
     /* Omit: other functions */
@@
 signature sRepSelector {
-    void  getRep([out]Descriptor(sREP4) *desc,
-                 [in]int_t i);
+    void  getRep( [out]Descriptor(sREP4) *desc, [in]int_t i );
 };
@@
     /* Get a descriptor of intended REP cell */
-    cRepSelector_getRep(&desc, repid);
+    cRepSelector_getRep( &desc, repid );
     /* Set the descriptor */
-    cREP_set_descriptor(desc);
+    cREP_set_descriptor( desc );
     /* Call the function of intended REP cell */
@@
 Therefore, it is a memory efficient algorithm.
-In addition, TLSF searches at the same speed and at high speed, $O(1)$.
+In addition, TLSF searches at the same speed and high speed, $O(1)$.
 
@@
 signature sMalloc {
-  int    initializeMemoryPool(void);
-  void   *calloc([in]size_t nelem,[in]size_t size);
-  void   *malloc([in]size_t size);
-  void   *realloc([in]const void *ptr,[in]size_t size);
-  void   free([in]const void *ptr);
+  int    initializeMemoryPool( void );
+  void   *calloc( [in]size_t nelem, [in]size_t size );
+  void   *malloc( [in]size_t size );
+  void   *realloc( [in]const void *ptr, [in]size_t size );
+  void   free( [in]const void *ptr );
 };
@@
 void*
-mrb_TECS_allocf(mrb_state *mrb, void *p, 
-                  size_t size, void *ud)
+mrb_TECS_allocf( mrb_state *mrb, void *p, size_t size, void *ud )
 {
@@
     if (size == 0) {
-        //tlsf_free(p);
-        cMalloc_free(p);
+        //tlsf_free( p );
+        cMalloc_free( p );
         return NULL;
@@
     else if (p) {
-        //return tlsf_realloc(p, size);
-        return cMalloc_realloc(p, size);
+        //return tlsf_realloc( p, size );
+        return cMalloc_realloc( p, size );
     }
     else {
-        //return tlsf_malloc(size);
-        return cMalloc_malloc(size);
+        //return tlsf_malloc( size );
+        return cMalloc_malloc( size );
     }
@@
 As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
-The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right paneof Fig.
-\ref{fig:ComparisonOfDynamicConnection}.
+The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right of Fig. \ref{fig:ComparisonOfDynamicConnection}.
 Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.
@@
 To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
-MDD provides the benefits of reusable, platform-independent, extensible design, however it needs long development time to build MDD systems.
+MDD provides the benefits of reusable, platform-independent, extensible design; however, it needs long development time to build MDD systems.
 
@@
 This paper presented an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
-In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS brigde.
+In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS bridge.
 Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.

### 2017-12-20 master/paper.tex
Add publication list

@@
 
+%Publication List
+\chapter*{Publication List}
+\addcontentsline{toc}{chapter}{Published List}
+\section*{Journal}
+\begin{enumerate}[{[}1{]}]
+\item
+    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
+    ``Component-Based mruby Platform for IoT Devices,"
+    \emph{IPSJ Journal of Information Processing},
+    2017 (submitted).
+\item
+    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
+    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
+    \emph{JSSST Journal on Computer Software},
+    vol. 34, no. 4, pp. 3-16, 2017.
+\end{enumerate}
+
+\section*{International Conference}
+\begin{enumerate}[{[}1{]}]
+\item
+    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada and Takuya Azumi,
+    ``TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems,''
+    \emph{In Proceedings of the IEEE 14th International Conference on Embedded Software and Systems (ICESS)},
+    2017.
+\item
+    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
+    ``Lightweight Ruby Framework for Improving Embedded Software Efficiency,''
+    \emph{In Proceedings of the 4th IEEE International Conference on Cyber-Physical Systems, Networks, and Applications (CPSNA)},
+    pp. 71-76, 2016.
+\end{enumerate}
+
 \end{document}

### 2017-12-22 master/paper.tex
Update Acknowledgment

@@
 \begin{acknowledgment}
-This work was supported by JSPS KAKENHI Grant Number 15H05305.
-We would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
+I would like to express my deep sense of gratitude to my adviser Professor Toshimitsu Ushio and Assistant Professor Takuya Azumi, Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
+Professor Ushio and Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
+I am deeply grateful to my advisers Hiroshi Oyama and Hiroaki Nagashima for their helpful comments on this thesis and warm encouragement.
+Finally, I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
 \end{acknowledgment}

### 2018-01-10 master/paper.tex
Fix file format to unix from dos

@@
 
+\section{Performance of TLSF+TECS}
+
+TLSF+TECS provides a functionality that acquires statistical information on dynamic memory usage status.
+It is possible to analyze the operation status of TLSF such as GC on RiteVMs because TLSF+TECS acquires memory statistical information: the frequency of memory allocation/deallocation and the usage size of heap area.
+
+Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=10cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
+    \label{fig:EvaluationOfTLSFStatistics}
+\end{figure}
+
 %5

### 2018-01-10 master/paper.tex
Add evaluation of TLSF+TECS

@@
 Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
+When the VM is activated, a large memory is allocated and the initialization is performed.
+After that, the application is running and the VM is termnated.
+The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
+TLSF+TECS can visualize the behavior of GC and help to verify its operation.
+Furthermore, when the VM is terminated, the memory used by VM is not completely released and a little used memory remains.
+In this way, it is useful for finding bugs related to memory, which is hard to find.
 

### 2018-01-10 master/paper.tex
Update publication list

@@
 
+\section*{Domestic Conference}
+\begin{enumerate}[{[}1{]}]
+\item
+    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
+    ``Componentized Dynamic Memory Allocator for Embedded Systems,''
+    \emph{in Proceedings of IPSJ Kansai-Branch Convention 2017},
+    A-3, 2017 (in Japanese).
+\item
+    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
+    ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
+    \emph{in Proceedings of ETNET2016},
+    No.8, pp.1-6, 2016 (in Japanese).
+\end{enumerate}
+
 \end{document}

### 2018-01-10 master/paper.tex
Add TECS adapter

@@
 
+\subsection{TECS adapter}
+\label{sec:TECSAdapter}
+
+TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to calling a function in TECS from existing C codes.
+The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECSAdapter}.
+In TINET+TECS, when an application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls a function of tTCPCEP such as {\it eAPI\_sendData}.
+Note that {\it tcp\_snd\_dat} is defined under the name {\it eAPI\_sendData} in TINET+TECS.
+The adapter wraps the APIs used in the existing applications into TECS functions, enabling software developers to utilize an existing TCP/IP application via the adapter.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=10cm,clip]{figure/TECSAdapter.pdf}
+    \caption{TECS adapter}
+    \label{fig:TECSAdapter}
+\end{figure}
+
+Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby program.
+
 \section{TLSF+TECS}
@@
 
+\subsection{Adapter overhead}
+
+The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
+As shown in Fig.
+\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=10cm,clip]{figure/EvaluationOfAdapter.pdf}
+    \caption{Execution times in two cases (without/with TECS adapter)}
+    \label{fig:EvaluationOfAdapter}
+\end{figure}
+
 \section{Performance of TLSF+TECS}

### 2018-01-11 master/paper.tex
Fix a little
Update related work

@@
     \centering
-    \caption{Evaluation Board Environment}
+    \caption{Evaluation board environment}
     \begin{tabular}{l|l}
@@
     \caption{Memory consumption in two cases (with/without dynamic connection)}
-    {\tabcolsep = 1mm
     \begin{tabular}{c|r|r|r|r}
@@
     \end{tabular}
-    }
     \label{fig:EvaluationOfDynamicConnection}
@@
 
-\subsection{Adapter overhead}
+\section{Adapter overhead}
 
@@
 However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
-Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
-
-The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
-In addition, the extended mruby on TECS supports legacy code such as a motor driver.
+
+\section{Scripting languages for embedded systems}
+
+Open-source runtime systems for scripting languages have been proposed such as ChaiScript\cite{url:ChaiScript}, python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, and mruby \cite{par:mruby}, \cite{url:mruby}.
+
+{\bf ChaiScript:}
+ChaiScript is a scripting language to be embedded in C++ applications.
+It is a dialect of ECMAScript (a.k.a. JavaScript).
+ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
+ChaiScript will support co-routines, but not now.
+
+{\bf python-on-a-chip:}
+python-on-a-chip (p14p) is a Python runtime system that uses a reduced Python VM called PyMite.
+The VM runs a significant subset of the Python language with few resources on a microcontroller.
+p14p can also run multiple stackless green threads.
+
+{\bf Owl system:}
+The Owl system is an embedded Python runtime system.
+It is a complete system for ARM Cortex-M3 microcontrollers.
+The Owl toolchain produces relocatable memory images that are directly runnable on the microcontroller from Python code objects.
+Note that the Owl system interpreter is the same as that of python-on-a-chip.
+
+{\bf eLua:}
+eLua (embedded Lua) offers a full implementation of the Lua programming language for embedded systems.
+Lua is one of the most popular scripting languages for embedded systems \cite{url:Lua}, \cite{par:Lua}.
+Lua supports a co-routine, which is referred to as cooperative multitasking.
+A co-routine in Lua is used as an independently executed thread.
+Note that a co-routine can only suspend and resume multiple routines; thus, a Lua co-routine is not like multitasks in multitask systems.
+
+{\bf Squirrel:}
+Squirrel is an object-oriented programming language designed as a lightweight scripting language that satisfies the real-time requirements of applications.
+Squirrel was inspired by Lua.
+The Squirrel API is very similar to Lua and the table code is based on that of Lua; Squirrel also supports co-routines.
+
+{\bf mruby:}
+mruby, a lightweight implementation of the Ruby language, has been proposed for embedded systems.
+mruby programs can run on a RiteVM, which is the VM for mruby and reads the mruby bytecode.
+Note that the RiteVM only supports a single thread.
+In addition, mruby supports co-routines but does not support multitasking for RTOSs.
 mruby has the same syntax as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
+
+The proposed framework is a component-based framework for running mruby programs.
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+Software can be developed using CBD with mruby on TECS.
+In addition to supporting multitasking and co-routines, the mruby on TECS framework can be utilized RTOS functionalities such as periodic tasks and semaphores and supports legacy code such as a motor driver.
+
+\section{TCP/IP protocol stacks for embedded systems}
+
+Open-source TCP/IP protocol stacks for embedded systems have been developed such uIP \cite{par:uIP} and lwIP \cite{par:lwIP}.
+
+{\bf uIP:}
+uIP (microIP) is a very small TCP/IP stack intended for tiny 8- and 16-bit microcontrollers.
+uIP requires only about 5 KB of code size and several hundred bytes of RAM.
+uIP has been ported to various systems and has found its way into many commercial products.
+Following the release of ver.
+1.0, later versions of uIP, including uIPv6, have been integrated with Contiki OS \cite{par:Contiki},\cite{url:Contiki}, an operating system to connect tiny microcontrollers to the Internet.
+
+{\bf lwIP:}
+lwIP (lightweightIP) is a small TCP/IP implementation for embedded systems that is intended to reduce memory resource usage while still maintaining a full-scale TCP.
+lwIP requires about 40 KB of ROM and tens of KB of RAM.
+lwIP is larger than uIP, but provides better throughput.
+To customize protocols and buffer size, users should handle a lot of macros.
+
+{\bf TINET:}
+TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by the TOPPERS Project \cite{url:TOPPERS}.
+To satisfy restrictions for embedded systems, TINET supports several functions such as minimum copy frequency and elimination of  dynamic memory control.
+Since TINET is TINET statically generates CEPs and REPs, which are like sockets.
+
+The proposed framework, TINET+TECS, can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
+TINET+TECS improves configurability more than TINET and is suitable for embedded systems with memory constraint.
 

### 2018-01-11 master/paper.tex
Add tables and update related work

@@
 
+Table \ref{tab:Scripting} compares the proposed framework to previous work.
 The proposed framework is a component-based framework for running mruby programs.
@@
 In addition to supporting multitasking and co-routines, the mruby on TECS framework can be utilized RTOS functionalities such as periodic tasks and semaphores and supports legacy code such as a motor driver.
+
+\begin{table*}[t]
+    \caption{Comparison of open-source scripting Languages for embedded systems}
+    \label{tab:Scripting}
+    \centering
+    {\small \tabcolsep = 1mm
+    \begin{tabular}{c||cccccc}
+        \hline\hline
+        & \shortstack{Call\\C functions} 
+        & \shortstack{Legacy code of\\embedded system} 
+        & \shortstack{Multitasking} 
+        & \shortstack{Co-routines}
+        & \shortstack{RTOS\\functionalities} \\ \hline
+        ChaiScript \cite{url:ChaiScript}              &            &            &            &              &              \\
+        python-on-a-chip \cite{url:python-on-a-chip}  &            &            &            & green thread &              \\
+        Owl system \cite{par:owl}                     & \checkmark & Partially  &            & green thread &              \\
+        eLua \cite{url:eLua}                          & \checkmark & Partially  &            & \checkmark   &              \\
+        Squirrel \cite{url:Squirrel}                  & \checkmark &            &            & \checkmark   &              \\
+        mruby \cite{par:mruby}                        & \checkmark &            &            & \checkmark   &              \\
+        Proposed framework                            & \checkmark & \checkmark & \checkmark & \checkmark   & \checkmark   \\
+    \end{tabular}
+    }
+\end{table*}
 
@@
 
+Table \ref{tab:TCP/IP} shows a comparison of TINET+TECS and previous work.
+Note that the proposed framework, TINET+TECS, has demonstrated all features shown in Table \ref{tab:TCP/IP}.
+TINET+TECS improves configurability more than TINET and is suitable for embedded systems with memory constraint.
 The proposed framework, TINET+TECS, can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
-TINET+TECS improves configurability more than TINET and is suitable for embedded systems with memory constraint.
+
+\begin{table*}[t]
+    \caption{Comparison of open-source TCP/IP protocol stacks for embedded systems}
+    \label{tab:TCP/IP}
+    \centering
+    {\small \tabcolsep = 1mm
+    \begin{tabular}{c||ccccccc}
+        \hline\hline
+        & \shortstack{Configurability}
+        & \shortstack{Generation} 
+        & \shortstack{Binding} 
+        & \shortstack{Support CBD} 
+        & \shortstack{Memory saving} \\ \hline
+        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
+        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
+        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
+        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
+    \end{tabular}
+    }
+\end{table*}
 
 %6
-\chapter{Conclusion}
+\chapter{Conclusions}
 \label{sec:Conclusion}

### 2018-01-11 master/paper.tex
Increase font size of source code and fix a figure

@@
     language={c},%
-    basicstyle={\footnotesize\ttfamily},%
-    identifierstyle={\footnotesize},%
-    commentstyle={\scriptsize\itshape},%
-    keywordstyle={\footnotesize},%\bfseries},%
-    ndkeywordstyle={\footnotesize},%
-    stringstyle={\footnotesize\it},
+    basicstyle={\small\ttfamily},%
+    identifierstyle={\small},%
+    commentstyle={\footnotesize\itshape},%
+    keywordstyle={\small},%\bfseries},%
+    ndkeywordstyle={\small},%
+    stringstyle={\small\it},
     frame={tb},
@@
 \begin{figure}[t]
+ \begin{minipage}[t]{0.5\hsize}
   \centering
@@
   \end{lstlisting}
+ \end{minipage}
+ \begin{minipage}[t]{0.5\hsize}
   \centering
@@
   \end{lstlisting}
+ \end{minipage}
  \caption{Two CDL codes (without/with dynamic connection)}

### 2018-01-15 master/paper.tex
Fix typo

@@
 signature sNicDriver {
-    void start( [send(sNetworkAlloc),size_is(size)]int8_t *outputp, .., .. );
-    void read( [receive(sNetworkAlloc),size_is(*size)]int8_t **inputp, .., .. );
+  void start([send(sNetworkAlloc),size_is(size)]int8_t *outputp, .., ..);
+  void read([receive(sNetworkAlloc),size_is(*size)]int8_t **inputp, .., ..);
     /* Omit: other functions */
@@
 
-TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to calling a function in TECS from existing C codes.
+TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to call functions in TECS from existing C codes.
 The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECSAdapter}.
@@
 celltype tTLSFMalloc {
-    [inline]entry  sMalloc  eMalloc;
+    [inline]
+        entry  sMalloc  eMalloc;
     attr {
@@
     var {
-        [size_is(memoryPoolSize/8)]uint64_t *pool;
+        [size_is(memoryPoolSize/8)]
+            uint64_t *pool;
     };
@@
 When the VM is activated, a large memory is allocated and the initialization is performed.
-After that, the application is running and the VM is termnated.
+After that, the application is running and the VM is terminated.
 The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
@@
 \chapter*{Publication List}
-\addcontentsline{toc}{chapter}{Published List}
+\addcontentsline{toc}{chapter}{Publication List}
 \section*{Journal}

### 2018-01-20 master/abstract/abstract.tex
Add abstract

--- 2016-02-13 abstract/abstract.tex
@@
-\documentclass[a4j,10pt,twocolumn]{utf8/abstract}
+\documentclass[a4j,10pt,twocolumn]{../styles/utf8/abstract}
 %\documentclass[a4j,9pt,twocolumn]{abstract}
-\usepackage[dvipdfmx]{graphicx}
-\usepackage{amssymb}
+\usepackage{graphicx}
 \usepackage[varg]{txfonts}
@@
 
-\title{mruby Bytecode Loader Using Bluetooth in Multi-VM Environment}	% 論文のタイトル
-\author{山本 拓朗} 		% 著者
-\studentid{09C12174} 	% 学籍番号
+\title{論文のタイトル}	% 論文のタイトル
+\author{氏名} 		% 著者
+\studentid{01C3456789} 	% 学籍番号
 \lab{潮}		% 研究室名
@@
 % 英語なら以下2行を定義
-\englishtitle
-\jptitle{Bluetoothを用いたマルチVM対応mrubyバイトコードローダ}  % 日本語のタイトル
+%\englishtitle
+%\jptitle{日本語の題名}  % 日本語のタイトル
 
@@
 
-\section{まえがき}
-近年，組込みシステムは複雑化・大規模化しているため，組込みソフトウェアの生産性が問題になっている．
-組込みソフトウェア開発の生産性の向上を目的として，組込みシステム向けのスクリプト言語であるmruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSが提案されている \cite{mrubyontecs}．
+\section{緒論}
 
-現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
-さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
+\section{次に}
 
-本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
-さらに，複数のmrubyアプリケーションを協調動作できるフレームワークを提案する.
-
-\section{既存フレームワークの問題点}
-mruby on TECSは，mrubyと，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである.
-
-スクリプト言語は生産性が高い反面，C言語に比べると実行速度が遅いため，組込みシステムに適用するのは難しい.
-mruby on TECSでは，mrubyプログラムからC言語の関数を呼ぶ機能を提供しており，mrubyに比べて，アプリケーションを約100倍速く実行できる.
-
-mruby on TECSでは，mrubyプログラムを修正する度にターゲットデバイスでSDカードを抜き差しし，OSを再起動する必要がある.
-さらに，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
-　
-\section{提案フレームワーク}
-提案フレームワークは，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダと，実用的なマルチタスク処理の実装を行った.
-システムモデルを図\ref{fig:system_model}に示す.
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=7cm,clip]{Abst_SystemModel.pdf}
-    \caption{システムモデル}
-    \label{fig:system_model}
-\end{figure}
-
-提案フレームワークでは，プラットフォーム（図\ref{fig:system_model}の下部）をコンパイル・リンクし，ターゲットデバイス上で起動する.
-ホストPC側では，mrubyアプリケーション (.rb) をバイトコード (.mrb) にコンパイルし，Bluetoothを通してターゲットデバイスにバイトコードを転送する.
-ターゲットデバイス側では，RiteVMに実装されたローダが転送されたバイトコードを受信し，すでにプラットフォームに含まれているmrubyライブラリと合わせてアプリケーションを実行する.
-これによって，SDカードを抜き差しする手間やOSを再起動する時間が省けるため，作業効率を上げることができる.
-
-さらに，各VMの処理を平等に実行するRiteVMスケジューラを提供することで，マルチタスク処理を効率的に利用できる.
-%$\mu$ITRON \cite{microITRON} のサービスコールである{\it rotateReadyQueue}を使った
-%開発者にとって使いやすい設計にした.
-%{\it rotateReadyQueue}は，同じ優先度のタスクの実行順序を切り替える機能である.
-複数タスク間の同期にはイベントフラグ処理を適用し，すべてのタスクが同時に起動するように実装した.
-イベントフラグのセットパターンや待ちパターンは，各コンポーネントの属性として定義する.
-これによって，VMの数に関わらず，同じCファイルを利用できる.
-
-提案フレームワークでは，RiteVMやRiteVMスケジューラ，イベントフラグはすべてTECSのコンポーネントとして実装されているため，開発者の必要に応じて容易に機能の取り外しができる.
-
-表\ref{tab:comparison}に，提案フレームワークと既存フレームワークの比較を示す.
-提案フレームワークでは，Bluetoothを用いたバイトコードローダに加え，VMスケジューラおよびアプリケーションの同期が可能になった.
+\section{それから}
 
 \section{結論}
-Bluetoothを用いたmrubyバイトコードローダによって，mruby on TECSでのソフトウェア開発の作業効率を向上させ，RiteVMスケジューラは複数のmrubyアプリケーションを効率良く実行する.
-さらに，提案フレームワークで提供される機能はコンポーネントであるため，機能の取り外しや再利用が容易になる.
-
-実験評価では，ローダによる作業効率の向上やオーバヘッドの少ないマルチタスク設計の有用性，コンポーネントベース開発の利点を示した.
-
-\begin{table}[t]
-    \centering
-    \caption{関連研究}
-    \scriptsize
-    {\tabcolsep=0.1cm
-    \begin{tabular}{c||c|c|c|c}
-        & \shortstack{Bluetooth\\Loader} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization\\of Application} \\ \hline
-        eLua                &            &            & &           \\
-        Owl system          &            &            & &           \\
-        mruby on TECS       &            & \checkmark & &           \\
-        Proposed framework  & \checkmark & \checkmark & \checkmark &\checkmark \\
-    \end{tabular}
-    }
-    \label{tab:comparison}
-\end{table}
 
@@
 \begin{thebibliography}{1}
-\bibitem{mrubyontecs} T. Azumi, and Y. Nagahara, and H. Oyama, and N. Nishio, 
-    ``mruby on TECS: Component-Based Framework for Running Script Program," 
-    in Proceedings of the 18th IEEE International Symposium on Real-Time Distributed Computing (ISORC), 
-    pp.252-259, 
-    2015. 
+\bibitem{}
 \end{thebibliography}

### 2018-01-20 master/abstract/abstract.tex
Add the title and author

@@
 %\documentclass[a4j,9pt,twocolumn]{abstract}
-\usepackage{graphicx}
-\usepackage[varg]{txfonts}
-%%% \begin{document}の前に，各エントリーを記述する
 
-\title{論文のタイトル}	% 論文のタイトル
-\author{氏名} 		% 著者
-\studentid{01C3456789} 	% 学籍番号
+\usepackage[dvipdfmx]{graphicx}
+\usepackage{latexsym}
+\usepackage{amssymb}
+\usepackage{float}
+\usepackage{enumerate,cite,url}
+\usepackage{color}
+\usepackage{listings,jlisting}
+\lstset{%
+    language={c},%
+    basicstyle={\small\ttfamily},%
+    identifierstyle={\small},%
+    commentstyle={\footnotesize\itshape},%
+    keywordstyle={\small},%\bfseries},%
+    ndkeywordstyle={\small},%
+    stringstyle={\small\it},
+    frame={tb},
+    breaklines=true,
+    columns=[l]{fullflexible},%
+    numbers=left,%
+    xrightmargin=0zw,%
+    xleftmargin=3zw,%
+    numberstyle={\scriptsize},%
+    stepnumber=1,
+    numbersep=1zw,%
+    lineskip=-0.5ex%
+}
+
+\title{Component-Based Software Development Framework\\for Embedded IoT Devices}	% 論文のタイトル
+\author{山本 拓朗} 		% 著者
+\studentid{29C16100} 	% 学籍番号
 \lab{潮}		% 研究室名
@@
 % 英語なら以下2行を定義
-%\englishtitle
-%\jptitle{日本語の題名}  % 日本語のタイトル
+\englishtitle
+\jptitle{組込みIoTデバイス向けコンポーネントベースソフトウェア開発フレームワーク}  % 日本語のタイトル
 

### 2018-01-22 master/abstract/abstract.tex
Update

@@
 \englishtitle
-\jptitle{組込みIoTデバイス向けコンポーネントベースソフトウェア開発フレームワーク}  % 日本語のタイトル
+\jptitle{{\Large 組込みIoTデバイス向けコンポーネントベースソフトウェア開発フレームワーク}}  % 日本語のタイトル
 
@@
 
-\section{次に}
+近年，IoT (Internet of Things) 市場の拡大により，組込み機器をネットワークに繋げて操作するために，ソフトウェアの高い生産性が要求されている．
+組込みソフトウェアの生産性向上のため，組込み向けスクリプト言語mruby (軽量Ruby) を用いたコンポーネントベース開発が可能なフレームワーク「mruby on TECS」\cite{par:mrubyonTECS}が提案されている．
 
-\section{それから}
+本研究では，mruby on TECS の拡張として，組込み向けTCP/IPプロトコルスタックTINET の機能をmrubyプログラムから実行できるフレームワークを提案する．
+提案フレームワークでは，TINETのコンポーネント化を行うことで拡張性やコンフィグラビリティが向上し，プロトコルを容易に設定できるようになる．
+さらに，動的メモリアロケータTLSF (Two-Level Segregate Fit) のコンポーネント化も行い，スレッドセーフに複数のスレッドを動作可能なメモリアロケータもフレームワークに組み込んでいる．
+
+\section{mruby on TECS}
+
+mruby on TECS は，mrubyと，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである.
+スクリプト言語はその使いやすさから生産性が高い反面，C 言語に比べると実行速度が遅いため，組込みシステムに適用することは難しい.
+mruby on TECS では，mrubyブリッジというmrubyプログラムからC 言語関数を呼び出す機能を提供しており，mrubyに比べて，アプリケーションを約100 倍速く実行できる.
+
+さらに，TECSによってコンポーネントベースで開発されているため，ソフトウェアの再利用が高く，機能の追加や取り外しが容易に行うことができる．
+
+\section{提案フレームワーク}
+
+提案フレームワークでは，mruby on TECSを拡張して，TCP/IPプロトコルスタックTINET+TECSと動的メモリアロケータTLSF+TECSの実装を行った．
+図\ref{fig:SystemModel}に提案フレームワークのシステムモデルを示す．
+
+TINET+TECSは，TECSによりTINETをコンポーネント化した組込みシステム向けTCP/IPプロトコルスタックである．
+TINETは組込みシステムに適したコンパクトなTCP/IPプロトコルであるが，多くの複雑なソースコードやマクロのせいでコンフィグラビリティが低く，メンテナンスや拡張，検証が難しい．
+TINET+TECSでは，プロトコルの各層をコンポーネントとして実装しているため，TCP層やUDP層の付け外し，IPv4とIPv6の共存，通信用バッファのサイズ変更など，プロトコルの設定が既存のTINETに比べて容易になっている．
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8cm,clip]{../figure/SystemModel.pdf}
+    \vspace{-0.2cm}
+    \caption{システムモデル}
+    \vspace{-0.4cm}
+    \label{fig:SystemModel}
+\end{figure}
+
+TLSF+TECSは，TECSによりTLSFをコンポーネント化した組込みシステム向け動的メモリアロケータである．
+TLSFはメモリ利用効率が良く常に$O(1)$で動作する高速なアロケータであるが，複数のスレッドが並行動作すると，メモリ競合が起きる場合がある．
+TLSF+TECSでは，TLSFコンポーネントが独自のヒープ領域を保持するため，排他制御なしで複数のスレッドを動作させることができる．
+さらにコンポーネントの特性により，ヒープメモリのサイズ変更が柔軟になる．
+
+図\ref{src:Application}は，提案フレームワーク上で動作させるアプリケーションの例を示している．
+mrubyのコードからTINETの機能を利用することができ，IoTデバイスで動作させるようなネットワークソフトウェアを開発することができる．
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+begin
+    io = AnalogIO.new(A0, INPUT)
+    cep = TCP.new()
+    cep.accept
+    loop do
+        val = io.read
+        cep.snd val.to_s + "\n"
+        RTOS.delay(1000)
+    end
+rescue => e
+    puts "[ERROR]" + e
+end
+\end{lstlisting}
+\vspace{-0.2cm}
+\caption{提案フレームワークでのアプリケーション例}  
+\vspace{-0.4cm}
+\label{src:Application}
+\end{figure}
 
 \section{結論}
+
+mruby on TECS フレームワークの拡張として，IoTシステムに適用できる組込みネットワークソフトウェアを開発するフレームワークを提案した．
+提案フレームワークでは，TCP/IPプロトコルスタックであるTINETの機能をmrubyプログラムから呼び出すことができる．
+さらに，ソフトウェアコンポーネントとしてTINET+TECSとTLSF+TECSを実装し，コンポーネント化によるソフトウェア開発の生産性向上を示した．
 
@@
 \begin{thebibliography}{1}
-\bibitem{}
+\bibitem{par:mrubyonTECS}
+    T. Azumi, and Y. Nagahara, and H. Oyama, and N. Nishio, 
+    ``mruby on TECS: Component-Based Framework for Running Script Program," 
+    in Proc. of ISORC, 
+    pp.252-259, 
+    2015. 
 \end{thebibliography}

### 2018-01-25 master/abstract/abstract.tex
Change format to unix
Fix the parts pointed out

@@
 
-近年，IoT (Internet of Things) 市場の拡大により，組込み機器をネットワークに繋げて操作するために，ソフトウェアの高い生産性が要求されている．
-組込みソフトウェアの生産性向上のため，組込み向けスクリプト言語mruby (軽量Ruby) を用いたコンポーネントベース開発が可能なフレームワーク「mruby on TECS」\cite{par:mrubyonTECS}が提案されている．
+近年，IoT (Internet of Things) 市場の拡大により，組込み機器をネットワークに繋げて操作するために，ソフトウェア開発の高い生産性が要求されている．
+組込みソフトウェア開発の生産性向上のため，組込み向けスクリプト言語mruby (軽量Ruby) を用いたコンポーネントベース開発が可能なフレームワークmruby on TECS\cite{par:mrubyonTECS}が提案されている．
 
@@
 TLSF+TECSでは，TLSFコンポーネントが独自のヒープ領域を保持するため，排他制御なしで複数のスレッドを動作させることができる．
-さらにコンポーネントの特性により，ヒープメモリのサイズ変更が柔軟になる．
+さらに，コンポーネントの特性により，ヒープメモリのサイズ変更が柔軟になる．
 
 図\ref{src:Application}は，提案フレームワーク上で動作させるアプリケーションの例を示している．
-mrubyのコードからTINETの機能を利用することができ，IoTデバイスで動作させるようなネットワークソフトウェアを開発することができる．
+mrubyのコードからTINETの機能を利用することができ，IoTデバイスに適用できるネットワークソフトウェアを開発することができる．
 
@@
 
-mruby on TECS フレームワークの拡張として，IoTシステムに適用できる組込みネットワークソフトウェアを開発するフレームワークを提案した．
+mruby on TECS フレームワークの拡張として，IoTデバイスに適用できる組込みネットワークソフトウェアを開発するフレームワークを提案した．
 提案フレームワークでは，TCP/IPプロトコルスタックであるTINETの機能をmrubyプログラムから呼び出すことができる．

### 2018-01-25 master/paper.tex
Fix the parts pointed out

@@
     identifierstyle={\small},%
-    commentstyle={\footnotesize\itshape},%
+    commentstyle={\small\itshape},%
     keywordstyle={\small},%\bfseries},%
@@
 This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
-The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
+The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
 In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
@@
 Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
+Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage helps developers debug and verify the systems.
 
@@
 The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
-The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
+The system model of the proposed framework is shown in Fig. \ref{fig:SystemModel}.
 In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/SystemModel.pdf}
+    \includegraphics[width=12cm,clip]{figure/SystemModel.pdf}
     \caption{System model of the proposed framework}
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/component_diagram.pdf}
+    \includegraphics[width=12cm,clip]{figure/component_diagram.pdf}
     \caption{Component Diagram}
@@
 \subsection{Component Model}
-Fig.\ref{fig:component} shows a component diagram.
+Fig. \ref{fig:component} shows a component diagram.
 A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes, and variables.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/TECSFlow.pdf}
+    \includegraphics[width=12cm,clip]{figure/TECSFlow.pdf}
     \caption{Development flow using TECS}
@@
 
-Fig.\ref{fig:TECSFlow} shows the development flow using TECS.
+Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
 TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/mruby.pdf}
+    \includegraphics[width=12cm,clip]{figure/mruby.pdf}
     \caption{mruby/RiteVM mechanism}
@@
 \subsection{System Model of mruby on TECS}
-% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
+% The present mruby on TECS system model is shown in Fig. \ref{fig:mrubyonTECS}.
 Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
@@
 
-Fig.\ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
+Fig. \ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
 The left side of BridgeMotor belongs to the mruby program.
 The right side of BridgeMotor belongs to TECS component.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=10cm,clip]{figure/mrubyTECSbridge.pdf}
-\caption{mruby-TECS bridge}
-\label{fig:mrubyTECSbridge}
-\end{figure}
-
 The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
@@
 Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=12cm,clip]{figure/mrubyTECSbridge.pdf}
+\caption{mruby-TECS bridge}
+\label{fig:mrubyTECSbridge}
+\end{figure}
 
@@
 
-Fig.\ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
+Fig. \ref{fig:TINETHierarchyDiagram} shows the hierarchy diagram of TINET and TOPPERS/ASP3.
 Users send and receive data using a Communication End Point (CEP), an interface that functions like a socket.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/TINETHierarchyDiagram.pdf}
+    \includegraphics[width=12cm,clip]{figure/TINETHierarchyDiagram.pdf}
     \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
@@
 
-The components of the TINET+TECS protocol stack are shown in Fig.\ref{fig:ComponentProtocolStack}.
+The components of the TINET+TECS protocol stack are shown in Fig. \ref{fig:ComponentProtocolStack}.
 Note that some small particle components, such as a kernel object, data queues, and semaphores, are omitted to simplify the component diagram.
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
+    \includegraphics[width=12cm,clip]{figure/ComponentProtocolStack.pdf}
     \caption{Component diagram of a protocol stack}
@@
 
-The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig.\ref{fig:tMemoryAllocator}.
+The memory allocator component connects to as many tFixedSizeMemoryPool as required, as shown in Fig. \ref{fig:tMemoryAllocator}.
 tFixedSizeMemoryPool is a componentized kernel object of TOPPERS/ASP3 for allocating and releasing memory areas of a requested size. 
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/tMemoryAllocator.pdf}
+    \includegraphics[width=12cm,clip]{figure/tMemoryAllocator.pdf}
     \caption{Component diagram of tMemoryAllocator}
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/SendReceive.pdf}
+    \includegraphics[width=12cm,clip]{figure/SendReceive.pdf}
     \caption{Differences between in/out and send/receive}
@@
 \item {\it send} is another specifier for transferring data to a callee from a caller.
-The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
+The difference between {\it in} and {\it send} is whether the data memory is deallocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
 In the case of the {\it in} specifier, both allocating and deallocating of the data memory are performed in the caller.
@@
 \item {\it receive} is another specifier for a caller receiving data from a callee.
-The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig.\ref{fig:SendReceive}.
+The difference between {\it out} and {\it receive} lies in whether the data memory is allocated in the caller or callee, as shown in Fig. \ref{fig:SendReceive}.
 In the case of {\it out}, the callee writes data in the memory allocated by a caller, whereas in the {\it receive} case, the callee allocates the data memory.
@@
 
-As shown in Fig.\ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
+As shown in Fig.
+\ref{src:SendReceive}, sending and receiving arguments such as {\it outputp} and {\it inputp} are defined using, respectively, the {\it send/receive} specifier in the signature description.
 Developers hardly make mistakes of memory operation because these specifiers completely pass an ownership of memory.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/DynamicConnection.pdf}
+    \includegraphics[width=12cm,clip]{figure/DynamicConnection.pdf}
     \caption{Dynamic connection}
@@
 
-TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig.\ref{fig:DynamicConnection}) as a new functionality.
-In Fig.\ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
+TECS supports a dynamic connection, a method for switching the binding of components at runtime (Fig. \ref{fig:DynamicConnection}) as a new functionality.
+In Fig. \ref{fig:DynamicConnection}, the solid line represents binding and the dotted line represents non-binding.
 Note that all components are statically generated in TECS, which can optimize the overhead of componentization because components are statically configured.
@@
 
-TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig.\ref{fig:DynamicConnectionUseCase}.
+TINET+TECS utilizes the dynamic connection to switch between CEP and REP components, as shown in Fig. \ref{fig:DynamicConnectionUseCase}.
 In a server application, CEP is associated with REP in the state of waiting for a connection request from clients\footnote{tcp\_acp\_cep(ID cepid, ID repid, T\_IPV4EP *p\_dstaddr, TMO tmout).}.
@@
     \centering
-    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
+    \includegraphics[width=12cm,clip]{figure/DynamicConnectionUseCase.pdf}
     \caption{Dynamic connection between CEP and REP}
@@
 A selector connects all components that can be dynamically connected under a common descriptor that serves as an identifier to access each component \cite{par:optimization}.
-The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig.\ref{src:DynamicCDLcode}).
+The cREP ports form a call port array connecting to connecting to all tREP cells (Line 8 in Fig. \ref{src:DynamicCDLcode}).
 {\it [ref\_desc]} is used to identify call ports referring to descriptors. 
-In the case of Fig.\ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
+In the case of Fig. \ref{fig:DynamicConnectionUseCase}, the tRepSelector cell connects all tREP cells.
 
@@
 
-Fig.\ref{src:DynamicCcode} shows a sample code of the dynamic connection.
+Fig. \ref{src:DynamicCcode} shows a sample code of the dynamic connection.
 The eAPI\_accept function is the function wrapping {\it tcp\_acp\_cep} under TECS, which is set as the state waiting for a connection request.
-The dynamic connection in the function is performed as shown in Fig.\ref{src:DynamicCcode}.
-First, the descriptor of REP to be joined is obtained (Line 3 in Fig.\ref{src:DynamicCcode}).
+The dynamic connection in the function is performed as shown in Fig. \ref{src:DynamicCcode}.
+First, the descriptor of REP to be joined is obtained (Line 3 in Fig. \ref{src:DynamicCcode}).
 The first argument, {\it \&desc}, is a variable used to store the descriptor information, whereas the second argument, {\it repid}, is the index of tREP cells.
-Next, the descriptor is set (Line 5 in Fig.\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.\ref{src:DynamicCcode}).
+Next, the descriptor is set (Line 5 in Fig.
+\ref{src:DynamicCcode}), and the cREP port combines the tREP cell specified by the descriptor, enabling the tCEP cell to call the function of the tREP cell to be joined (Line 7 in Fig.
+\ref{src:DynamicCcode}).
 
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/TECSAdapter.pdf}
+    \includegraphics[width=12cm,clip]{figure/TECSAdapter.pdf}
     \caption{TECS adapter}
@@
 
-Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby program.
+Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby programs.
 
@@
 
-TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
+TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system.
 TLSF memory allocator has the following features.
@@
 TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
-The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
+The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
 Consider a case where a request, $malloc(100)$, is called to allocate a memory.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/TLSF.pdf}
+    \includegraphics[width=12cm,clip]{figure/TLSF.pdf}
     \caption{TLSF Algorithm}
@@
 This section describes the component design of TLSF memory allocator.
-In this research, we are using TECS to componentize TLSF.
+In this research, TECS is used to componentize TLSF.
 The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
@@
 
-Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
+Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
 It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.
@@
 
-The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
+The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
 An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/WithoutTECS.pdf}
+    \includegraphics[width=12cm,clip]{figure/WithoutTECS.pdf}
     \caption{TLSF before componentization}
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/WithTECS.pdf}
+    \includegraphics[width=12cm,clip]{figure/WithTECS.pdf}
     \caption{TLSF after componentization}
@@
 
-As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
-In the research, TLSF is componentized using TECS as shown in Fig.\ref{fig:WithTECS}.
+As shown in Fig.
+\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
+In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
 It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.
@@
 
-Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Fig.
+\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.
+\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
 Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as a variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
-Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
+Each memory pool size can be configured as a variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
+Fig. \ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
 The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3} which is introduced in Section \ref{sec:mrubyonTECS}.
 Line 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
+{\it cMalloc\_} represents the name of the call port (Line 2 in Fig. \ref{src:TLSFBuild}).
 Likewise, Lines 13 and 17 call the function for memory allocation.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/UseCase_mruby.pdf}
+    \includegraphics[width=12cm,clip]{figure/UseCase_mruby.pdf}
     \caption{Component description of RiteVM and TLSF+TECS}
@@
 
-The TLSF components are connected to the RiteVMs to hold own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
+The TLSF components are connected to the RiteVMs to hold own heap area in each RiteVM as shown in Fig. \ref{fig:UseCase_mruby}.
 Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
-Fig.\ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
+Fig. \ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
 It is easy to set different heap areas in each RiteVM.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/UseCase_TINET.pdf}
+    \includegraphics[width=12cm,clip]{figure/UseCase_TINET.pdf}
     \caption{Fixed-size and TLSF memory allocator components}
@@
 The TLSF memory allocator can execute at the same speed as compared with the fixed-size memory allocator which TOPPERS/ASP3 supports as standard, and can improve the memory efficiency.
-In addition, as shown in Fig.\ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
+In addition, as shown in Fig. \ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
 TLSF+TECS efficiently manages the memory without selecting a memory pool.
@@
 In the proposed framework, applications can call TINET functions such as TCP and UDP from mruby programs because mruby-TECS bridge automatically generates the code linking mruby and C.
-Fig.\ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
+Fig. \ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
 mruby makes it easier to develop applications than existing TINET, i.e., C language.
@@
 In the case of a simple application, a few functions are only used and there are some unused functions.
-For example, the application only uses a function to send by TCP protocol as shown in Fig.\ref{src:mruby}.
+For example, the application only uses a function to send by TCP protocol as shown in Fig. \ref{src:mruby}.
 The proposed framework incorporates TINET+TECS, and can easily customize the TCP/IP protocol stack such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
@@
 Detailed specifications of the board are shown in Table \ref{tab:EvaluationBoardEnvironment}.
-We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
-To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.
+I also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
+To pretest the system, I connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.
 
@@
 
-To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
+To demonstrate the low overhead of TINET+TECS, I compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
 
 The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
-For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
+For {\it tcp\_snd\_dat}, I measured the executing time starting from the API call through the application until the return of the processing result.
 In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
 \ref{fig:ComponentProtocolStack}.
-For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
+For {\it tcp\_rcv\_dat}, I measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
 In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \includegraphics[width=12cm,clip]{figure/EvaluationOfExecutionTime.pdf}
     \caption{Execution times of TINET and TINET+TECS}
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
+    \includegraphics[width=12cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
     \caption{Component diagrams for without/with dynamic connection}
@@
     cREP[0] = REP_000.eREP;
-    ..
+    cREP[1] = REP_001.eREP;
+    ...
     cREP[n] = REP_00n.eREP;
@@
 };
-..
+...
 cell tTCPCEP TCPCEP_00n {
@@
 
+The TECS adapter which enables to call functions in TECS from existing C codes is implemented between C codes and a TECS component and links a C function to a TECS function.
+Therefore, the existing applications can be applied to the proposed framework.
+However, since real-time processing is important for embedded systems, it is meaningless if the execution time is slower than the existing application.
+
+In the section, it is evaluated whether the TECS adapter affects the system.
 The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
 As shown in Fig.
-\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=10cm,clip]{figure/EvaluationOfAdapter.pdf}
+\ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is small because the adapter only passes parameters from C codes to TECS components; thus, the overhead of TECS adapter does not affect the system.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=12cm,clip]{figure/EvaluationOfAdapter.pdf}
     \caption{Execution times in two cases (without/with TECS adapter)}
@@
 
-\section{Performance of TLSF+TECS}
+\section{Memory statistics using TLSF+TECS}
 
@@
 Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
-When the VM is activated, a large memory is allocated and the initialization is performed.
-After that, the application is running and the VM is terminated.
+When the RiteVM is activated, a large memory is allocated and the initialization is performed for several seconds.
+After that, the application is running for about 20 seconds and the RiteVM is terminated.
 The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
 TLSF+TECS can visualize the behavior of GC and help to verify its operation.
-Furthermore, when the VM is terminated, the memory used by VM is not completely released and a little used memory remains.
+Furthermore, when the RiteVM is terminated, the memory used by RiteVM is not completely released and a little used memory (a few kilobytes) remains.
+This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeats activation and shutdown.
 In this way, it is useful for finding bugs related to memory, which is hard to find.
@@
     \centering
-    \includegraphics[width=10cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
     \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
@@
         ChaiScript \cite{url:ChaiScript}              &            &            &            &              &              \\
-        python-on-a-chip \cite{url:python-on-a-chip}  &            &            &            & green thread &              \\
-        Owl system \cite{par:owl}                     & \checkmark & Partially  &            & green thread &              \\
+        python-on-a-chip \cite{url:python-on-a-chip}  &            &            &            & Green thread &              \\
+        Owl system \cite{par:owl}                     & \checkmark & Partially  &            & Green thread &              \\
         eLua \cite{url:eLua}                          & \checkmark & Partially  &            & \checkmark   &              \\
@@
 
-This paper presented an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
+This paper presented an component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
+It is an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
 In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS bridge.
 Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
+
 TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
@@
 Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
-
 This paper also presented the dynamic connection, a new TECS functionality, to enable dynamic processing while reducing memory consumption.
 TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.
+
 TLSF+TECS is a component-based dynamic allocator.
 Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
+The TLSF+TECS functionality to get statistical information of memory usage helps developers analyze the systems and find bugs.
+
 In addition, the RiteVMs, TINET+TECS, and TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
-Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:TECS}.
-In the future, we will support mruby libraries as mrbgems, which is an mruby distribution packaging system.
+Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from the website \cite{url:TECS}.
+In the future, mruby libraries will be supported as mrbgems, which is an mruby distribution packaging system.
 
@@
     \emph{IPSJ Journal of Information Processing},
-    2017 (submitted).
+    2018 (submitted).
 \item

### 2018-01-29 master/abstract/abstract.tex
Fix abstract

--- 2018-01-20 master/abstract/abstract.tex
@@
 
-\section{次に}
+近年，IoT (Internet of Things) 市場の拡大により，組込み機器をネットワークに繋げて操作するために，ソフトウェア開発の高い生産性が要求されている．
+組込みソフトウェア開発の生産性向上のため，スクリプト言語mruby (軽量Ruby) を用いたコンポーネントベース開発が可能なフレームワークmruby on TECS\cite{par:mrubyonTECS}が提案されている．
 
-\section{それから}
+本研究では，IoT機器に対応するため，mruby on TECS の拡張として組込み向けTCP/IPプロトコルスタックTINET の機能をmrubyプログラムから実行できるフレームワークを提案する．
+提案フレームワークでは，TINETのコンポーネント化を行うことで拡張性やコンフィグラビリティが向上し，プロトコルを容易に設定できるようになる．
+さらに，動的メモリアロケータTLSF (Two-Level Segregate Fit) のコンポーネント化も行い，スレッドセーフに複数のスレッドを動作可能なメモリアロケータもフレームワークに組み込んでいる．
+
+\section{mruby on TECS}
+
+mruby on TECS は，スクリプト言語mrubyと，組込みシステムに適したコンポーネントシステムであるTECS (TOPPERS Embedded Component System) を組み合わせたフレームワークである.
+スクリプト言語はその使いやすさから生産性が高い反面，C 言語に比べると実行速度が遅いため，組込みシステムに適用することは難しい.
+mruby on TECS では，mrubyブリッジというmrubyプログラムからC 言語の関数を呼び出す機能を提供しており，mrubyに比べて，アプリケーションを約100 倍速く実行できる.
+
+さらに，TECSによってコンポーネントベースで開発されているため，ソフトウェアの再利用が高く，機能の追加や取り外しが容易である．
+
+\section{提案フレームワーク}
+
+提案フレームワークでは，mruby on TECSを拡張して，TCP/IPプロトコルスタックTINET+TECSと動的メモリアロケータTLSF+TECSの設計・実装を行った．
+図\ref{fig:SystemModel}に提案フレームワークのシステムモデルを示す．
+
+TINET+TECSは，TECSによりTINETをコンポーネント化した組込みシステム向けTCP/IPプロトコルスタックである．
+TINETは組込みシステムに適したコンパクトなTCP/IPプロトコルであるが，多くの複雑なソースコードやマクロのせいでコンフィグラビリティが低く，メンテナンスや拡張・検証が難しい．
+TINET+TECSでは，プロトコルの各層をコンポーネントとして実装しているため，TCP層やUDP層の付け外し，IPv4とIPv6の共存，通信用バッファのサイズ変更など，プロトコルの設定が既存のTINETに比べて容易になっている．
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8cm,clip]{SystemModel.pdf}
+    \vspace{-0.2cm}
+    \caption{システムモデル}
+    \vspace{-0.4cm}
+    \label{fig:SystemModel}
+\end{figure}
+
+TLSF+TECSは，TECSによりTLSFをコンポーネント化した組込みシステム向け動的メモリアロケータである．
+TLSFはメモリ利用効率が良く常に$O(1)$で動作する高速なアロケータであるが，複数のスレッドが並行動作すると，メモリ競合が起きる場合がある．
+TLSF+TECSでは，TLSFコンポーネントが独自のヒープ領域を保持するため，排他制御なしで複数のスレッドを動作させることができる．
+さらに，コンポーネントの特性により，ヒープメモリのサイズ変更が柔軟になる．
+
+図\ref{src:Application}は，提案フレームワーク上で動作させるアプリケーションの例(1秒周期でセンサデータを取得し，送信する)を示している．
+mrubyプログラムからTINETの機能を利用でき，IoTデバイスに適用できるネットワークソフトウェアを開発できる．
+
+\begin{figure}[t]
+\centering
+\begin{lstlisting}
+begin
+    io = AnalogIO.new(A0, INPUT)
+    cep = TCP.new()
+    cep.accept
+    loop do
+        val = io.read
+        cep.snd val.to_s + "\n"
+        RTOS.delay(1000)
+    end
+rescue => e
+    puts "[ERROR]" + e
+end
+\end{lstlisting}
+\vspace{-0.2cm}
+\caption{提案フレームワークでのアプリケーション例}  
+\vspace{-0.7cm}
+\label{src:Application}
+\end{figure}
 
 \section{結論}
+
+mruby on TECS フレームワークの拡張として，IoTデバイス向けのソフトウェアを開発するフレームワークを提案した．
+提案フレームワークでは，TCP/IPプロトコルスタックであるTINETの機能をmrubyプログラムから呼び出せる．
+さらに，ソフトウェアコンポーネントとしてTINET+TECSとTLSF+TECSを実装し，コンポーネント化によるソフトウェア開発の生産性向上を示した．
 
@@
 \begin{thebibliography}{1}
-\bibitem{}
+\bibitem{par:mrubyonTECS}
+    T. Azumi, and Y. Nagahara, and H. Oyama, and N. Nishio, 
+    ``mruby on TECS: Component-Based Framework for Running Script Program," 
+    in Proc. of IEEE ISORC, 
+    pp.252-259, 
+    2015. 
 \end{thebibliography}

### 2018-02-05 master/paper.tex
Add a TLSF evaluation

@@
 \vspace{10mm}
-{\Large February 7, 2018}\\
+{\Large February 2, 2018}\\
 \vspace{14mm}
-{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
+{\Large Division of Mathematical Science for Social Systems,}\\
+{\Large Department of Systems Innovation,}\\
+{\Large Graduate School of Engineering Science, Osaka University}\\
 \end{center}
@@
 
+{\bf Memory usage:}
 Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
@@
     \centering
-    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
     \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
     \label{fig:EvaluationOfTLSFStatistics}
+\end{figure}
+
+{\bf Memory frequency:}
+Fig. \ref{fig:EvaluationOfTLSFFrequency} evaluates how much memory size and how often a RiteVM requests.
+In this evaluation, the same application as Fig. \ref{fig:EvaluationOfTLSFStatistics} runs for about 30 seconds.
+During 30 seconds, the RiteVM requests {\it malloc} quite frequency.
+In the case of designating heap areas with fixed-size memory, it is necessary to property configure memory blocks suitable for an application.
+For example, 10 blocks of 64 bytes, 20 blocks of 128 bytes, and 3 blocks of 64 kilobytes.
+In particular, it is not easy to analyze how many memory blocks are needed with RiteVMs, which consumes memory considerably with a high frequency.
+With TLSF+TECS, you only need to prepare a large heap area; therefore, such a workload and useless memory are eliminated.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
+    \caption{Memory frequency of RiteVM (mruby VM) by TLSFStatistics component}
+    \label{fig:EvaluationOfTLSFFrequency}
 \end{figure}
@@
 
-This paper presented an component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
+This paper presented a component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
 It is an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
@@
     \emph{IPSJ Journal of Information Processing},
-    2018 (submitted).
+    2018 (conditionally accepted).
 \item

### 2018-02-05 master/paper.tex
Fix abstract

@@
 Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
-Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage helps developers debug and verify the systems.
+Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage and frequency helps developers debug and verify the systems.
 

### 2018-02-05 master/paper.tex
Fix typo (paper -> thesis)

@@
 To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
-This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
+This thesis proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
 The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
-In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+In addition, this thesis proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
 TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
@@
 
-This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
+This thesis proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
 In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
@@
 The improved configurability leads to satisfying strict memory constraints of IoT Devices.
-In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
+In addition, this thesis proposes a component-based dynamic memory allocator, TLSF+TECS. 
 TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by dividing memory blocks in two stages.
@@
 
-{\bf Organization}: The remainder of this paper is organized as follows.
+{\bf Organization}: The remainder of this thesis is organized as follows.
 Chapter \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
@@
 Chapter \ref{sec:Evaluation} evaluates the proposed framework.
-Related work is discussed in Chapter \ref{sec:Related Work} and Chapter \ref{sec:Conclusion} concludes this paper.
+Related work is discussed in Chapter \ref{sec:Related Work} and Chapter \ref{sec:Conclusion} concludes this thesis.
 
@@
 
-In this paper, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
+In this thesis, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
 However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.
@@
 
-This paper presented a component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
+This thesis presented a component-based framework that can develop software including network applications for embedded IoT devices using a scripting language.
 It is an extended framework of mruby on TECS, including TINET+TECS and TLSF+TECS.
@@
 Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
-This paper also presented the dynamic connection, a new TECS functionality, to enable dynamic processing while reducing memory consumption.
+This thesis also presented the dynamic connection, a new TECS functionality, to enable dynamic processing while reducing memory consumption.
 TINET+TECS utilizes the dynamic connection to satisfy the TINET specification for supporting the static generation of CEPs and REPs.

### 2018-02-05 master/paper.tex
Fix introduction

@@
 TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has own heap area.
+In TLSF+TECS, developer can get statistical information of memory usage and frequency, which is helpful for analyzing the memory operation and finding bugs.
 
@@
 TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
-Moreover, each thread can easily set own heap area.
+Each thread can easily set own heap area.
+Moreover, statistical information helps developers debug and verify the system.
 

### 2018-02-06 ipsj/reply_letter/paper.tex
Add reply_letter

--- 2017-01-17 jssst/reply_letter.tex
@@
 \begin{flushleft}
-  2017-01-13\newline 
-  ソフトウェア論文特集\newline
-  論文・記事番号：16-S-05\newline
-  題目：Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development\newline
-  著者: Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi\newline
+  2018-03-03\newline 
+  Journal of Information Processing\newline
+  Submission ID: 18-Y008e\newline
+  Title: Component-Based mruby Platform for IoT Devices\newline
+  Authors: Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi\newline
 \end{flushleft}
@@
 \item \begin{flushleft}
-    \textbf{Comment:
-}初見では、Fig.21 をどう解釈すればよいかが分かりにくかったです。
-図の解釈について説明を追加いただければ、多くの読者にとってわかりやすくなると思います。
+    \textbf{Comment:}
   \end{flushleft}
@@
     \textbf{Our reply:}
-Thank you for your thoughtful suggestion.
-We have added and modified the section as follows. (page 13)
 
-\begin{itembox}[|]{4.3 Synchronization of Multiple RiteVMs}
-To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
-We measured the execution time from the execution of the first RiteVM task to that of the last RiteVM task.
-Fig. 21 shows the case of two to eight RiteVM tasks.
-Note that the periodic time is 1 msec.
-It was confirmed that the execution time was within the theoretical value which is {\it\scriptsize periodic time $\times$ (number of RiteVM tasks - 1).}
-In the case of two RiteVM tasks, the theoretical value is 1 msec and the execution time does not exceed the theoretical value. 
-As shown in Fig. 21, the execution time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.
+\begin{itembox}[|]{}
 \end{itembox}\\
@@
     \textbf{Comment:}
-3ページ左カラムの下から2行目で「4. Benets of CBD:」で始まっていますが、他の項目は「.」で終わっています。
-この点、ご確認ください。
   \end{flushleft}
@@
     \textbf{Our reply:}
-Thank you for pointing out the wrong expression.
-We have modified the other contributions to ``:'' such as "Improved software development efficiency:". (page 3)
   \end{flushleft}
@@
     \textbf{Comment:}
-Figure 11 seems to be a wrong diagram.
-Maybe this is an old version.
-Please replace it with a correct one so that A, B, C, D matches to the description in the text.
   \end{flushleft}
@@
     \textbf{Our reply:}
-Thank you very much for your careful reading.
-As you said, we used the different figure.
-We have replaced it with the correct figure. (page 7)
   \end{flushleft}
@@
     \textbf{Comment:}
-The first reference of Figure 12 from the text is after Figure 13 is refereed.
-Please change the order.
   \end{flushleft}
@@
     \textbf{Our reply:}
-Thank you for your thoughtful comment.
-We have switched the order of Fig. 12 and Fig. 13. (page 7-8)
   \end{flushleft}

### 2018-02-06 ipsj/reply_letter/paper.tex
Update reply_letter

@@
 \begin{flushleft}
-  2018-03-03\newline 
+  2018-03-02\newline 
   Journal of Information Processing\newline
@@
 \textbf{Comment:}
+
+Please describe the relation between mruby and proposed framework clearly.
+I think that the developed component can be used as a normal TECS component without mruby.
+I cannot understand why the paper says "mruby."
 \end{flushleft}
@@
 
+Thank you for your suggestion.
+提案した２つの機能：TINET+TECSとTLSF+TECSは、mrubyに限らず、TECSのみで動作するため、他のシステムにも適用できる。
+〇〇ページのフットノートおよび結論に追加する。
 \begin{itembox}[|]{}
@@
 \textbf{Comment:}
+
+Please describe requirements to implement these components for mruby or IoT system using TECS and explain its design associating with the requirements. 
 \end{flushleft}
@@
 \textbf{Our reply:}
+
+2章システムモデルの冒頭に、要件を書き加える。
+\begin{description}
+    \item[R1:] IoTシステムには、ネットワークが重要不可欠であるため、TCP/IP機能が使えること
+    \item[R2:] mrubyはシングルタスクしかサポートしておらず、開発の生産性を高めるためにマルチタスク機能を提供すること
+\end{description}
+\end{flushleft}
+
+\item \begin{flushleft}
+\textbf{Comment:}
+
+The paper should explain evaluation of items described in contribution paragraph in the introduction.
+
+\begin{enumerate}
+\item The authors said "Improve configurability," but there is no description of it in the evaluation section.
+At least you should explain the proposed design can be used in typical cases.
+I cannot understand the validity of your design shown in Fig.
+10 without them.
+Please explain.
+
+\item The paper also describes "Thread-safe memory allocator," but there is no evaluation of it. Please explain.
+\end{enumerate}
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+\begin{enumerate}
+\item 少ないコード変更量でプロトコルの設定を変更できるというコンフィグラビリティ評価を強調する。Fig.10（プロトコルのコンポーネント図）を拡大してTCPのみ、UDPのみ、の図を加えて、プロトコルの変更が容易にできると加える。
+\item TLSF+TECS評価部分で、2つのVMを動かしたグラフ（つまり線が２つあるグラフ）を追加し、「２つのVMで違うアプリケーションが並行動作しているので、スレッドセーフに動作していることも示している」と加える。
+\end{enumerate}
+\end{flushleft}
+
+\item \begin{flushleft}
+\textbf{Comment:}
+
+Please add evaluation of typical usage pattern. The authors demonstrate execution time and memory usage using TCP only.
+
+\begin{enumerate}
+\item Please evaluate execution time of connection time of TCP, UDP, and other supported protocol. If the overhead of them almost same as TCP, please discuss it.
+
+\item Please show memory usages under the typical configuration.
+\end{enumerate}
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+\begin{enumerate}
+\item コメント3-(a)で協調した部分および、UDPの実行時間とメモリ消費量の評価を加える。また、「既存TINETで対応しているTCPとUDPでの評価を行った」と追記。
+
+\item TCPのみ、UDPのみ、両方のメモリ消費量
+\end{enumerate}
 \end{flushleft}
@@
 \end{enumerate}
+
+\clearpage
 
@@
 \item \begin{flushleft}
-    \textbf{Comment:}
+\textbf{Comment:} 構成
+
+タイトルとアブストラクトからは、TOPPERS 上にmrubyのプラットフォームを構築することで、IoTデバイスのproductivityを主張しているように思えますが、4章の評価は、execution time と memory consumptionになっており、こちらを主張したい点のようにも見えます。
+主張したい点を明確にし、評価がその根拠となるように、Abstractを含む論文全体の構成とストーリー展開、タイトルを変更してください。
+
+論文から、オリジナリティはTLSFとよぶダイナミックメモリアロケータを構築したことではないかと推測していますが、読み解くのは容易ではありません。
+\begin{flushleft}
+\textbf{Our reply:}
+
+主張したい点はソフトウェア開発の生産性が向上させるプラットフォームであるため、３章Use CaseにmrubyとC言語比較を加え、mrubyだと開発がより簡単になることを強調する。
+コンフィグラビリティは向上しつつ、execution time と memory consumption のオーバヘッドを抑えることができたという流れにする。
+\end{flushleft}
+\begin{enumerate}
+\item AbstractとIntroduction
+
+いずれもproposeが2回使われていますが、proposeは1回にまとめるべきで、提案は1つとし、含まれている特徴（問題点の解決策）を複数個記すようにした方が読みやすいです。「TINET+TECSおよびTLSF+TECSというフレームワークを提案する」というふうにまとめても良いとは思います。
+また、問題点が一般的な背景ばかりが記されていて、提案方法が必要である問題点をAbstractとIntroductionから読み取ることができません。
+シンプルに、解くべき問題点を列挙し、それに対応づく解決策を挙げるようにしてください。
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+提案は、「IoTデバイス向けのmrubyプラットフォーム」であり、TINET+TECSとTLSF+TECSの「2つの機能を組み込んだ」とする。
+貢献部分に、「TINETのコンフィグラビリティを向上させる」「マルチVMを実現する」と追記する。
+\end{flushleft}
+
+\item 2. System Model
+
+章立ての位置付けとして、この章では、IoTデバイスのproductivity向上についての要件や課題が記されていることを期待して読むのですが、TECSとmrubyの説明にとどまっています。論文は、新規性・有用性は何かを探しながら読むことが目的であり、開発に必要な知識を得ることは目的ではありません。新規性・有用性を主張するのに、必要な内容を記すようにしてください。
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+システムモデルの冒頭に要件を加える。
+\end{flushleft}
+
+\item 3章以降
+
+AbstractおよびIntroductionを修正にともない、そのストーリーにあった内容にしてください。
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+3章UseCaseを3-1にするべきか。
+4章の評価の順番を変える。（コンフィグラビリティ評価、オーバヘッド評価の順番）
+\end{flushleft}
+
+\item 5. Related Work
+
+MDDについてサーベイがありますが、execution time と memory consumptionを評価するならば、それと関連したサーベイをしてください。
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+execution time と memory consumption は補足的な評価である。今回のサーベイはIoTシステムにおけるソフトウェア開発手法である。
+\end{flushleft}
+
+\end{enumerate}
 \end{flushleft}
@@
 \item \begin{flushleft}
-    \textbf{Comment:}
+\textbf{Comment:} 英語
+
+理解できる英語ですが、論文誌の英語としては、全体的に、品質を向上させる必要があります。論文中に頻出する誤りとして、代表的な例は、下記が挙げられます。
+abstractの二文目”To improve the productivity, ...”
+この文章のTo…ではじまる文章ですが、懸垂分詞の誤りがあります。また、whichの修飾が適切でなく、主語と述語動詞の距離が長いです。以上のような問題点が散在しています。
 \end{flushleft}
@@
 \textbf{Our reply:}
+
+不定詞のTo として書いた。
+英文校正をかけた。
+\end{flushleft}
+
+\item \begin{flushleft}
+\textbf{Comment:} 引用
+
+・2.2冒頭
+
+mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+は、https://mruby.org/
+の引用と思われます。引用番号を記すようにしてください。また、webの引用については、検索した日付をIPSJ論文誌の決まりに従い、入れるようにしてください。
+
+mruby. Retrieved December 1, 2017 from https://mruby.org/
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+引用を追加する。
+Web引用の日付けを追加する。
+\end{flushleft}
+
+\item \begin{flushleft}
+\textbf{Comment:}
+
+些細な誤りですが、Abstract の中程” The proposed framework enables that that mruby ” というふうにthat が重複しています。
+上記の懸垂分詞やthatの重複などは、英語校正業者でなくても、メジャーな文法チェッカー程度で十分に修正できます。
+
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+指摘部分は修正した。
+他の部分も英文校正にかけ、修正を行う。
 \end{flushleft}

### 2018-02-07 master/paper.tex
Fix by enago

--- 2018-02-05 master/paper.tex
@@
 
-High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
-To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
-This thesis proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
-The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
-In addition, this thesis proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
-TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
+In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
+To improve productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
+Based on the above information, this thesis proposes an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
+The proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
+Further, this thesis proposes two component-based functionalities, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+Here, TINET+TECS improves scalability and configurability and offers software developers high levels of productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
 TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
-TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
-Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
-Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage and frequency helps developers debug and verify the systems.
+Futher, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
+The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; I conclude that configurability is improved.
+Finally, the TLSF+TECS functionality which obtains and report statistical information regarding mruby's virtual machine (VM) memory usage and frequency of memory requests, helps developers debug and verify their embedded IoT systems.
 
@@
 
-The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
-The IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, and they must demonstrate high quality and high performance.
-This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
-
-Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
-Component-based development is a design technique that can be applied to reusable software development.
-Verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
+The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, such as wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
+The IoT uses embedded systems such as data sensors and controlling actuators, as elemental constituents; therefore, these devices must demonstrate consistently high levels of quality and runtime performance.
+These requirements have consequently led to an increase in their complexity and scale; further, to be successful and widely adopted by users, these systems must have low production costs and short development cycles.
+
+Complex and large-scale software systems can be developed efficiently using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
+Particularly, component-based development is a design technique that is applicable to the development of reusable software.
+Given its importance in terms of reliability, verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
 Individual component diagrams enable the visualization of an entire system.
-In addition, component-based systems are flexible with regard to extensibility and specification changes.
-The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are used as typical component-based development for embedded systems.
-
-In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
-Currently, most embedded software is programmed in C language.
-However, development in C language results in large code size, incurs high costs, and requires significant development time.
-In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.
-
-For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
-Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
-Therefore, applying scripting languages to embedded systems is difficult.
-To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS},\cite{par:mrubyonTECS3}.
-This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby},\cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
-
-This thesis proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
-In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
-TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
-TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
-TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
-In the case of only sending values obtained by sensors, it is better to easily customize the minimum configuration of the TCP/IP protocol stack, such as removing unused functions.
-The improved configurability leads to satisfying strict memory constraints of IoT Devices.
-In addition, this thesis proposes a component-based dynamic memory allocator, TLSF+TECS. 
-TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by dividing memory blocks in two stages.
-In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
-TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has own heap area.
-
-{\bf Contributions}: The proposed framework provides the following contributions.
-
-{\bf Applicable to various devices}
-The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
-mruby code is portable.
+Further, component-based systems are flexible in terms of their extensibility and resilience to specification changes.
+Typical component-based development environments focused on embedded systems include the TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+
+In addition to specific development environments, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to develop quality software.
+Currently, most embedded software is implemented using the C language.
+However, development in C typically results in large code size, high costs, and significant development time.
+In contrast, the use of scripting languages improves efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.
+
+Embedded systems often have real-time requirements; therefore, real-time properties, such as estimating worst-case execution times, are very important.
+Although scripting languages are easy to use and read, their execution typically requires more time than that required for executing the code written in C.
+Therefore, applying scripting languages to embedded systems poses a major difficulty.
+To address this limitation, in \cite{par:mrubyonTECS},\cite{par:mrubyonTECS3}, mruby on TECS has been proposed as a component-based framework for efficiently running script-based programs.
+This framework integrates two key technologies, i.e., mruby, which is a lightweight implementation of Ruby designed specifically for embedded systems \cite{par:mruby},\cite{url:mruby} and TECS, which is a component-based framework also designed specifically for embedded systems \cite{par:TECS}.
+
+This thesis proposes an extended framework for mruby on TECS that can be applied to embedded network software development involving IoT devices.
+The proposed framework makes it possible to utilize Tomakomai Internetworking (TINET) functions from within the mruby programs.
+Note that TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET} that comprises a number of complex source code files, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
+To overcome the above problem, TINET+TECS is a componentized TINET implementation that incorporates TECS to improve the configurability and scalability of TCP/IP software.
+For IoT applications that should only be sending values obtained by one or more than one sensors, it is ideal to easily customize the minimum configuration of the TCP/IP protocol stack, e.g., by removing unused functions.
+This improved configurability also leads to satisfying strict memory constraints of IoT devices.
+In addition to TINET+TECS, this thesis proposes a component-based dynamic memory allocator based on Two-Level Segregate Fit (TLSF) called TLSF+TECS.
+Note that TLSF is a dynamic memory allocator designed specifically for real-time systems that always runs in constant time (i.e., $O(1)$) and improves memory usage efficiency by dividing memory blocks in two distinct stages.
+In the current version of TLSF, memory contention may occur when multiple threads run simultaneously.
+To address this problem, TLSF+TECS is a componentized TLSF memory allocator that is also entirely thread-safe because each component has its own heap area from which memory is actually allocated.
+In TLSF+TECS, developers can also obtain statistical information regarding memory usage and frequency of memory requests, which is crucial in analyzing memory operations and locating bugs.
+
+{\bf Contributions}: The proposed framework provides the following three key contributions.
+
+{\bf Applicability to various devices.}
+The proposed framework does not depend on real-time operating systems (RTOSs) or specific hardware; instead, it can be utilized by various devices, i.e., mruby code is portable.
 Therefore, it is possible to run the same program on different devices.
 
-{\bf Improve configurability}
-Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
-In addition, the use of individual component diagrams enables visualization of an entire system.
-
-{\bf Thread-safe memory allocator}
-TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
-Moreover, each thread can easily set own heap area.
-
-{\bf Organization}: The remainder of this thesis is organized as follows.
-Chapter \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
-Chapter \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
-Chapter \ref{sec:Evaluation} evaluates the proposed framework.
-Related work is discussed in Chapter \ref{sec:Related Work} and Chapter \ref{sec:Conclusion} concludes this thesis.
+{\bf Improved configurability.}
+Because TINET+TECS is a component-based system, its software can flexibly change in response to system configuration changes, such as resizing of network buffers, adding or removing TCP (or UDP) functionality, and supporting both IPv4 or IPv6.
+Further, the use of individual component diagrams enables visualizations of the entire system.
+
+{\bf Thread-safe memory allocation}
+TLSF+TECS safely runs multiple threads without exclusive control even if the threads operate in parallel.
+To achieve this, each thread can easily set up its own heap area.
+Further, statistical information is available to help developers debug and verify the specific memory usage of the given system.
+
+{\bf Organization}: In addition to this introductory section, the remainder of this thesis is organized as follows.
+Chapter \ref{sec:System Model} introduces the system model and the fundamental technologies, i.e., TECS, mruby, and mruby on TECS.
+Next, Chapter \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
+Chapter \ref{sec:Evaluation} provides a detailed evaluation of the proposed framework.
+Finally, related work is discussed in Chapter \ref{sec:Related Work}, and Chapter \ref{sec:Conclusion} concludes this thesis.
 
@@
 
-TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system.
-TLSF memory allocator has the following features.
-
-{\bf Real-time property:}
-The worst execution time required for allocating and deallocating memory does not depend on the data size.
-TLSF always works with $O(1)$, and it is possible to estimate the response time.
-
-{\bf Efficient memory consumption:}
+The TLSF memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator that is suitable for use in the real-time systems.
+As such, the TLSF memory allocator provides the following two features.
+
+{\bf Real-time property.}
+In TLSF, the worst-case execution time required for allocating and deallocating memory does not depend on the given data size.
+Instead, TLSF always runs in constant time (i.e., $O(1)$), and it is possible to estimate response time.
+
+{\bf Efficient memory consumption.}
 Memory efficiency is improved by suppressing memory fragmentation.
-Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
-
-\subsection{TLSF Algorithms}
-
-TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
-The overview of TLSF algorithm is shown in Fig. \ref{fig:TLSF}.
-Consider a case where a request, $malloc(100)$, is called to allocate a memory.
-First, it is classified by the most significant bit of the requested memory size.
-In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
-Second, it is further classified.
-In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
-Free block\footnote{Free block is an available memory block.} in this range is used.
-
-A simple fixed-size memory block allocator results in the waste of up to 50 \%.
-However, TLSF classifies it finely in two steps.
+Various experiments have achieved an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
+
+\subsection{TLSF Algorithm}
+
+As illustrated in Fig. \ref{fig:TLSF}, the TLSF algorithm classifies memory blocks into two stages and searches for a memory block that optimally lines up with the requested memory size.
+Particularly, consider the case in which a request to dynamically allocate 98 bytes is made via $malloc()$.
+First, the request is classified based on the leftmost 1 bit in the requested memory size.
+In this example, since 98 is represented in binary as byte 01100010, it falls in the range of 64-128 based on the leftmost 1 bit.
+Second, the request is further classified as follows.
+The range from 64 to 128 is further divided into four equally sized groups, which 98 falling into the block ranging from 96 to 111.
+A free block\footnote{A free block is an available memory block.} in this range is then used to fulfill the memory allocation request.
+
+Without using the above approach, a simple fixed-size memory block allocator results in wasted memory blocks of up to 50\%.
+As illustrated above, TLSF classifies the memory allocation process finely in two steps.
 Therefore, it is a memory efficient algorithm.
-In addition, TLSF searches at the same speed and high speed, $O(1)$.
+Fortunately, given its design, TLSF searches for memory blocks in constant time (i.e., $O(1)$).
 
@@
 
-This section describes the component design of TLSF memory allocator.
-In this research, TECS is used to componentize TLSF.
-The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
+This section describes the component design of the TLSF memory allocator.
+Note that I use TECS to componentize TLSF.
+Further, the version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
 
@@
 
-Fig. \ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
-It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.
+In Fig. \ref{src:TLSFSignature}, I summarize the function signatures used by the allocator for memory management.
+Particularly, this component defines the memory pool initialization function {\it initializeMemoryPool()}, memory allocation functions {\it calloc()}, {\it malloc()}, {\it realloc()}, and the memory release function {\it free()}.
 
@@
 
-The celltype description of the TLSF memory allocator component is shown in Fig. \ref{src:TLSFCelltype}.
-An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
-Here, {\it [inline]} is a specifier for Implementation as inline functions.
-A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
-Each component holds own heap area.
-Therefore, even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
+Next, Fig. \ref{src:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
+Here, entry port {\it eMalloc} is connected to all components that perform memory management, including {\it malloc()} and {\it free()}.
+Further, {\it [inline]} is a specifier to implement as an inline function.
+Memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
+Note that each component maintains its own heap area.
+Therefore, even when calling memory management functions simultaneously from different threads, it is possible to operate without any memory contention.
 
@@
 As shown in Fig.
-\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
-In the research, TLSF is componentized using TECS as shown in Fig. \ref{fig:WithTECS}.
-It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.
+\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously via multiple threads, memory contention may occur in some cases, thus causing intermittent synchronization problems that can be extremely difficult to debug.
+In this study, TLSF is componentized using TECS, as shown in Fig. \ref{fig:WithTECS}.
+It is possible to operate in thread safe without exclusive control because each component independently holds a heap area and manages memory within it.
 
@@
 
-Fig.
-\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.
+Next, Fig.
+\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.
 \ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
-Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as a variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
-Fig. \ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
-The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3} which is introduced in Section \ref{sec:mrubyonTECS}.
-Line 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the call port (Line 2 in Fig. \ref{src:TLSFBuild}).
-Likewise, Lines 13 and 17 call the function for memory allocation.
-The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
-In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
-
-\subsection*{Multiple RiteVM}
+Here, two sets of task components and TLSF components are combined.
+Further, each memory pool size can be configured as a variable (Lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
+Fig. \ref{src:TLSFC} presents the code that actually calls functions of the TLSF memory allocator component.
+The use part shows a function in which the mruby VM allocates memory within the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, which is introduced in Section \ref{sec:mrubyonTECS}.
+Line 8 calls the {\it free()} function of the TLSF memory allocator component.
+{\it cMalloc\_} represents the name of the call port on line 2 in Fig. \ref{src:TLSFBuild}.
+Similarly, lines 13 and 17 call the memory allocation function.
+Particularly, the heap area for the {\it TLSFMalloc\_001} component is used if the code from \ref{src:TLSFC} is executed in {\it Task\_001}; conversely, if that code is executed in {\it Task\_002}, the heap area of the {\it TLSFMalloc\_002} component is used.
+Using this approach, in component-based development using TECS, it is possible to operate with the same code without modifying the underlying C code, although the resulting cells differ.
+
+\subsection*{Multiple RiteVM Instances}
 
@@
 
-The proposed framework uses TLSF memory allocator for memory management of RiteVMs.
-However, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple, memory contention will occur.
-As a RiteVM allocates and deallocates memory at high frequency, the memory contention immediately occurs in the case of multiple VMs.
-
-The TLSF components are connected to the RiteVMs to hold own heap area in each RiteVM as shown in Fig. \ref{fig:UseCase_mruby}.
-Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
-Fig. \ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
-It is easy to set different heap areas in each RiteVM.
-In addition, RiteVM performs incremental GC (Garbage Collection), and a VM that started GC does not disturb the execution of other VMs by running GC.
-
-\subsection*{Memory management for data sending and receiving}
+The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
+Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.
+
+Note that the TLSF components are connected to the RiteVMs to ensure that each component has its own heap area within each RiteVM, as shown in Fig. \ref{fig:UseCase_mruby}.
+Since each TLSF component maintains its own memory pool, multiple RiteVMs can be executed without the possibility of any memory contention.
+In the Fig.
+\ref{fig:UseCase_mruby}, I observe that the first RiteVM has a heap area of 1 MB (i.e., 1024 $\times$ 1024 bytes) and the second RiteVM has a heap area of 2 MB (i.e., 2 $\times$ 1024 $\times$ 1024 bytes).
+As illustrated in the figure, it is easy to configure different-sized heap areas for each RiteVM.
+Further, each RiteVM performs incremental garbage collection (GC), and a RiteVM that has started GC does not disturb the execution of other RiteVMs in its GC execution.
+
+\subsection*{Memory management for sending and receiving data}
 
@@
 
-In the TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer.
-Therefore, the role of allocator is important.
-TINET+TECS combines all components that manage memory with the allocator.
-The TLSF memory allocator can execute at the same speed as compared with the fixed-size memory allocator which TOPPERS/ASP3 supports as standard, and can improve the memory efficiency.
-In addition, as shown in Fig. \ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
-TLSF+TECS efficiently manages the memory without selecting a memory pool.
-TLSF+TECS can be easily extended to TINET+TECS since TINET+TECS is a component-based system.
+In the TCP/IP protocol stack, memory allocation and subsequent deallocation are repeated in each layer, including the TCP, IP, Ethernet, and other layers.
+Therefore, the role of the memory allocator is critical.
+The TINET+TECS framework combines all components that manage memory within the allocator.
+The TLSF memory allocator can execute at the same speed as that of the fixed-size memory allocator that TOPPERS/ASP3 supports as standard; further, the TLSF memory allocator can improve memory efficiency.
+As shown in Fig. \ref{fig:UseCase_TINET}, the fixed-size memory allocator prepares memory pools of different sizes and selects a memory pool whenever it is necessary.
+Conversely, TLSF+TECS efficiently manages memory without the need to select a memory pool.
+Finally, TLSF+TECS can be easily extended to TINET+TECS since TINET+TECS is a component-based system.
 
@@
 
-In the proposed framework, applications can call TINET functions such as TCP and UDP from mruby programs because mruby-TECS bridge automatically generates the code linking mruby and C.
-Fig. \ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
-mruby makes it easier to develop applications than existing TINET, i.e., C language.
-
-In the case of a simple application, a few functions are only used and there are some unused functions.
-For example, the application only uses a function to send by TCP protocol as shown in Fig. \ref{src:mruby}.
-The proposed framework incorporates TINET+TECS, and can easily customize the TCP/IP protocol stack such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
-It can be applied to embedded systems with strict memory constraints by removing unused functions.
+In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
+Fig. \ref{src:mruby} shows an example mruby program that transmits the value acquired from a sensor from the senser to another device.
+In general, mruby makes it easier to develop applications than using C with the existing TINET framework.
+
+For a simple application, typically only a few functions are used, with numerous unused functions.
+As an example, the application code shown in Fig. \ref{src:mruby} only uses a function to send data via TCP.
+The proposed framework incorporates TINET+TECS and can easily customize the TCP/IP protocol stack by removing functions, such as UDP functions, functions that support only IPv4, or TCP receiving functions.
+As such, the proposed framework can be applied to embedded systems with strict memory constraints by removing many unused functions.
 
@@
 
-TLSF+TECS provides a functionality that acquires statistical information on dynamic memory usage status.
-It is possible to analyze the operation status of TLSF such as GC on RiteVMs because TLSF+TECS acquires memory statistical information: the frequency of memory allocation/deallocation and the usage size of heap area.
-
-{\bf Memory usage:}
-Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM acquired by statistical information of TLSF+TECS.
-When the RiteVM is activated, a large memory is allocated and the initialization is performed for several seconds.
-After that, the application is running for about 20 seconds and the RiteVM is terminated.
-The reduction in memory usage at regular time intervals is due to the GC function of RiteVM.
-TLSF+TECS can visualize the behavior of GC and help to verify its operation.
-Furthermore, when the RiteVM is terminated, the memory used by RiteVM is not completely released and a little used memory (a few kilobytes) remains.
-This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeats activation and shutdown.
-In this way, it is useful for finding bugs related to memory, which is hard to find.
+The TLSF+TECS framework also provides functionality to acquire statistical information describing dynamic memory usage.
+Therefore, it is possible to analyze the operational status of the TLSF, GC on RiteVMs, because TLSF+TECS acquires and records the frequency of memory allocations and deallocations, as well as the usage sizes within the heap area.
+I describe memory usage and frequency below.
+
+{\bf Memory usage.}
+Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of a RiteVM, with presented data acquired from the statistical information available via the TLSF+TECS framework.
+From the figure, I observe that when the RiteVM is first activated, a large amount of memory is allocated and initialization is performed for several seconds.
+Next, the application runs for ~20 s and the RiteVM subsequently terminates.
+The reduction in memory usage that occurs at regular intervals is due to the GC function of the RiteVM.
+As such, the TLSF+TECS framework provides users with the ability to visualize GC behavior and help verify its operation.
+Further, when the RiteVM terminates, the memory used by the RiteVM is not completely released, i.e., a few kilobytes remain.
+This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeatedly activates and shuts down.
+Using the proposed environment here proves useful for detecting bugs related to memory, which in practice can be extremely difficult to detect.
 
@@
 
-{\bf Memory frequency:}
-Fig. \ref{fig:EvaluationOfTLSFFrequency} evaluates how much memory size and how often a RiteVM requests.
-In this evaluation, the same application as Fig. \ref{fig:EvaluationOfTLSFStatistics} runs for about 30 seconds.
-During 30 seconds, the RiteVM requests {\it malloc} quite frequency.
-In the case of designating heap areas with fixed-size memory, it is necessary to property configure memory blocks suitable for an application.
-For example, 10 blocks of 64 bytes, 20 blocks of 128 bytes, and 3 blocks of 64 kilobytes.
-In particular, it is not easy to analyze how many memory blocks are needed with RiteVMs, which consumes memory considerably with a high frequency.
-With TLSF+TECS, you only need to prepare a large heap area; therefore, such a workload and useless memory are eliminated.
+{\bf Memory frequency.}
+Fig. \ref{fig:EvaluationOfTLSFFrequency} evaluates the amount of memory and the frequency of memory requests from a RiteVM.
+In this evaluation, the same application used above (i.e., Fig. \ref{fig:EvaluationOfTLSFStatistics}) ran for ~30 s, which during which the RiteVM calls {\it malloc()} rather frequency.
+When designating heap areas with fixed-size memory sizes, it is necessary to properly configure the memory blocks in response to the given application's specific needs.
+For example, this configuration may comprise 10 blocks of 64 bytes, 20 blocks of 128 bytes, and three blocks of 64 kilobytes.
+It is difficult to analyze and determine the number of memory blocks needed with RiteVMs as they consume memory at considerably high frequencies.
+Conversely, with TLSF+TECS framework, developers need only to prepare a large heap area; therefore, the workload of determining the approach to configure the blocks and areas containing useless memory are eliminated.
 

### 2018-02-08 master/paper.tex
Final ver.

@@
 TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
-Futher, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
+Further, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
 The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; I conclude that configurability is improved.
@@
 However, development in C typically results in large code size, high costs, and significant development time.
-In contrast, the use of scripting languages improves efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.
+In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.
 
@@
 
-In this thesis, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
+In this thesis, TOPPERS/ASP3 \cite{par:ASP3},\cite{url:ASP3} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON}.
 However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/ASP3 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2},\cite{par:hr-tecs}.
@@
 In TINET+TECS, the application component calls TECS functions such as {\it cTCPAPI\_sendData} and {\it cTCPAPI\_receiveData}.
-Moreover, in TINET+TECS supporting a TECS adapter, an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, software can be developed either using existing methods or as TECS components.
+Moreover, in TINET+TECS supporting a TECS adapter, an existing application with TINET can run on the TINET+TECS framework without transporting, and therefore, the software can be developed either using existing methods or as TECS components.
 
@@
 The tIPv4Input and tIPv4Output components perform, respectively, the receiving and sending processing in the network layer.
-The tIPv4Functions component performs functions such as checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
+The tIPv4Functions component performs functions such as a checksum, the tICMP component is used for the Internet Control Message Protocol (ICMP), and the tIPv4RoutingTable component operates a routing table.
 
@@
 The tNetworkInterfaceContoroller component implements a network device driver.
-Software can be run on other devices by replacing the component because only the component depends on the target device.
+The software can be run on other devices by replacing the component because only the component depends on the target device.
 
@@
 
-A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig.
+A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11-13 in Fig.
 \ref{src:DynamicCDLcode}).
@@
 Memory efficiency is improved by suppressing memory fragmentation.
-Various experiments have achieved an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
+Various experiments have achieved an average fragmentation of less than 15 \% and a maximum fragmentation of less than 25 \%.
 
@@
 
-The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
+The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since it is difficul to handle multiple memory pools in the existing TLSF, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
 Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.
@@
 In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
-Fig. \ref{src:mruby} shows an example mruby program that transmits the value acquired from a sensor from the senser to another device.
+Fig. \ref{src:mruby} shows an example mruby program that transmits the value acquired from a sensor from the sensor to another device.
 In general, mruby makes it easier to develop applications than using C with the existing TINET framework.
@@
 In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
-The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
+The execution time of TINET+TECS is close to that of TINET, with an overhead of about three us.
 As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
@@
     \includegraphics[width=12cm,clip]{figure/ComparisonOfDynamicConnection.pdf}
-    \caption{Component diagrams for without/with dynamic connection}
+    \caption{Component diagrams for without/with the dynamic connection}
     \label{fig:ComparisonOfDynamicConnection}
@@
 
-Memory consumption without and with TECS dynamic connection was then evaluated.
+Memory consumption without and with TECS the dynamic connection was then evaluated.
 As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
@@
     \centering
-    \caption{Memory consumption in two cases (with/without dynamic connection)}
+    \caption{Memory consumption in two cases (with/without the dynamic connection)}
     \begin{tabular}{c|r|r|r|r}
@@
     \centering
-    \caption{CDL code lines of without/with dynamic connection}
+    \caption{CDL code lines of without/with the dynamic connection}
     \begin{tabular}{l|r|r|r}
@@
  \end{minipage}
- \caption{Two CDL codes (without/with dynamic connection)}
+ \caption{Two CDL codes (without/with the dynamic connection)}
  \label{src:ComparisonOfCDL}
@@
     \includegraphics[width=12cm,clip]{figure/EvaluationOfAdapter.pdf}
-    \caption{Execution times in two cases (without/with TECS adapter)}
+    \caption{Execution times in two cases (without/with the TECS adapter)}
     \label{fig:EvaluationOfAdapter}
@@
     \centering
-    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
     \caption{Memory usage of RiteVM (mruby VM) by TLSFStatistics component}
@@
     \centering
-    \includegraphics[width=11cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
+    \includegraphics[width=12cm,clip]{figure/EvaluationOfTLSFFrequency.pdf}
     \caption{Memory frequency of RiteVM (mruby VM) by TLSFStatistics component}
@@
         & \shortstack{Memory saving} \\ \hline
-        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
-        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
+        uIP \cite{par:uIP}     &  Partially & Dynamic    & Dynamic  &              & \checkmark \\
+        lwIP \cite{par:lwIP}   &  Partially & Dynamic    & Dynamic  &              & \checkmark \\
         TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
@@
 \begin{acknowledgment}
-I would like to express my deep sense of gratitude to my adviser Professor Toshimitsu Ushio and Assistant Professor Takuya Azumi, Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
-Professor Ushio and Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
+I would like to express my deep sense of gratitude to my adviser Assistant Professor Takuya Azumi, Professor Toshimitsu Ushio, and Associate Professor Takafumi Kanazawa,  Graduate School of Engineering Science, Osaka University, for their invaluable, constructive advice and constant encouragement during this work.
+Assistant Professor Azumi's deep knowledge and their eyes for detail have inspired me much.
 I am deeply grateful to my advisers Hiroshi Oyama and Hiroaki Nagashima for their helpful comments on this thesis and warm encouragement.
-Finally, I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
+I would like to thank all members of Ushio Laboratory, especially the members of the Azumi team, for their kind help and cooperation.
+Finally, I would also like to express my gratitude to my family for their moral support and warm encouragements.
 \end{acknowledgment}
@@
     ``Componentized Dynamic Memory Allocator for Embedded Systems,''
-    \emph{in Proceedings of IPSJ Kansai-Branch Convention 2017},
+    \emph{In Proceedings of IPSJ Kansai-Branch Convention 2017},
     A-3, 2017 (in Japanese).
@@
     ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''
-    \emph{in Proceedings of ETNET2016},
+    \emph{In Proceedings of ETNET2016},
     No.8, pp.1-6, 2016 (in Japanese).

### 2018-02-08 master/paper.tex
Fix typo

@@
 \item
-    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada and Takuya Azumi,
+    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
     ``TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems,''
@@
 \item
-    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
+    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
     ``Componentized Dynamic Memory Allocator for Embedded Systems,''
@@
 \item
-    Takuro Yamamoto, Hiroshi Oyama, Takuya Azumi,
+    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
     ``mruby Bytecode Loader Using Bluetooth in Multi-VM Environment,''

### 2018-02-11 ipsj/paper.tex
Remove vpath

@@
 %1
-\vspace{-1mm}
 \section{Introduction}
 \label{sec:Introduction}
-\vspace{-1mm}
 
@@
 %2
-\vspace{-1mm}
 \section{System Model}
 \label{sec:System Model}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
-    \vspace{-1mm} \caption{System model of the proposed framework}
-    \vspace{-2mm} \label{fig:SystemModel}
-\end{figure}
-
-\vspace{-3mm}
+    \caption{System model of the proposed framework}
+    \label{fig:SystemModel}
+\end{figure}
+
 \subsection{TECS}
 \label{sec:TECS}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
-    \vspace{-1mm} \caption{Component Diagram}
-    \vspace{-2mm} \label{fig:component}
+    \caption{Component Diagram}
+    \label{fig:component}
 \end{figure}
@@
 
-\vspace{-3mm}
 \subsection{mruby}
 \label{sec:mruby}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/mruby.pdf}
-    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
-    \vspace{-2mm} \label{fig:mruby}
-\end{figure}
-
-\vspace{-3mm}
+    \caption{mruby/RiteVM mechanism}
+    \label{fig:mruby}
+\end{figure}
+
 \subsection{mruby on TECS}
 \label{sec:mrubyonTECS}
-\vspace{-1mm}
 
@@
 %3
-\vspace{-1mm}
 \section{Proposed Framework}
 \label{sec:Proposed Framework}
-\vspace{-1mm}
 
@@
 
-\vspace{-3mm}
 \subsection{TINET+TECS}
 \label{sec:TINET+TECS}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
-    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
-    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
+    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
+    \label{fig:TINETHierarchyDiagram}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
-\vspace{-2mm} \label{src:SendReceive}
+\caption{Signature description of the nic driver (An example of send/receive)}
+\label{src:SendReceive}
 \end{figure}
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Accept function (a dynamic connection example)}
-\vspace{-2mm} \label{src:DynamicCcode}
-\end{figure}
-
-\vspace{-3mm}
+\caption{Accept function (a dynamic connection example)}
+\label{src:DynamicCcode}
+\end{figure}
+
 \subsection{TLSF+TECS}
 \label{sec:TLSF+TECS}
-\vspace{-1mm}
 
@@
     \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
-    \vspace{-1mm} \caption{TLSF Algorithm}
-    \vspace{-2mm} \label{fig:TLSF}
+    \caption{TLSF Algorithm}
+    \label{fig:TLSF}
 \end{figure}
@@
 
-\vspace{-3mm}
 \subsection{Use case}
 \label{sec:UseCase}
-\vspace{-1mm}
 
@@
 \end{lstlisting}
-\vspace{-1mm} \caption{Example of mruby application}
-\vspace{-2mm} \label{src:mruby}
-\end{figure}
-
-\vspace{-1mm}
+\caption{Example of mruby application}
+\label{src:mruby}
+\end{figure}
+
 \section{Evaluation}
 \label{sec:Evaluation}
-\vspace{-1mm}
 
@@
 
-\vspace{-3mm}
 \subsection{Performance of TINET+TECS}
-\vspace{-1mm}
 
@@
 
-\vspace{-3mm}
 \subsection{Dynamic connection}
-\vspace{-1mm}
 
@@
     \centering
-    \vspace{-1mm} \caption{Memory consumption in two cases\\(with/without dynamic connection)}
-    \vspace{-1mm}
+    \caption{Memory consumption in two cases\\(with/without dynamic connection)}
     {\tabcolsep = 1mm
@@
 %5
-\vspace{-1mm}
 \section{Related Work}
 \label{sec:Related Work}
-\vspace{-1mm}
 
@@
 %6
-\vspace{-1mm}
 \section{Conclusion}
 \label{sec:Conclusion}
-\vspace{-1mm}
 
@@
 
-\vspace{-2mm}
 \begin{acknowledgment}
@@
 \end{acknowledgment}
-\vspace{-2mm}
 

### 2018-02-12 ipsj/paper.tex
Fix the file format
Add the evaluation of TLSF+TECS

@@
 
-mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
+mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard \cite{url:mruby}.
 Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
@@
 It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
+
+\subsection{Memory usage of RiteVMs by TLSF+TECS}
+
+The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control in parallel because each TLSF component holds its own heap area.
+The TLSF+TECS framework provides functionality to acquire statistical information describing dynamic memory usage.
+Therefore, it is possible to analyze the operational status of the TLSF and GC on RiteVMs.
+
+Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of two RiteVMs, with presented data acquired from the statistical information available via the TLSF+TECS framework.
+From the figure, we observe that when the RiteVM are first activated, a large amount of memory is allocated for each RiteVM and initialization are performed within one second.
+Next, the applications runs for ~10 s and the RiteVMs subsequently terminate.
+The reduction in memory usage that occurs at regular intervals is due to the GC function of the RiteVM.
+Here, an application that allocates tens of KB of memory runs on RiteVM 1 and an application that allocates hundreds of KB of memory runs on RiteVM 2.
+Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol} shows the memory usage when two RiteVMs are executed in one heap area with exclusive control.
+In Fig.
+\ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig.
+\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased by 0.3 \% due to exclusive contorol.
+
+As such, the TLSF+TECS framework provides users with the ability to visualize GC behavior and help verify its operation.
+Further, when the RiteVM terminates, the memory used by the RiteVM is not completely released, i.e., a few kilobytes remain.
+This remaining memory causes a memory leak when the number of RiteVMs increases or a RiteVM repeatedly activates and shuts down.
+Using the proposed environment here proves useful for detecting bugs related to memory, which in practice can be extremely difficult to detect.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \caption{Memory usage of RiteVMs with TLSF+TECS}
+    \label{fig:EvaluationOfTLSFStatistics}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfMemoryUsageWithExclusiveContorol.pdf}
+    \caption{Memory usage of RiteVMs with exclusive control}
+    \label{fig:EvaluationOfMemoryUsageWithExclusiveContorol}
+\end{figure}
 

### 2018-02-12 ipsj/paper.tex
Fix 3.2 and 3.3 (by enago)

@@
 
-TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator suitable for the real-time system proposed by M. Masmano et al.
-TLSF memory allocator has the following features.
-
-{\bf Real-time property:}
-The worst execution time required for allocating and deallocating memory does not depend on the data size.
-TLSF always works with $O(1)$, and it is possible to estimate the response time.
-
-{\bf Efficient memory consumption:}
+The TLSF (Two-Level Segregate Fit) memory allocator\cite{par:TLSF}\cite{url:TLSF} is a dynamic memory allocator that is suitable for use in the real-time systems.
+As such, the TLSF memory allocator provides the following two features.
+
+{\bf Real-time property.}
+In TLSF, the worst-case execution time required for allocating and deallocating memory does not depend on the given data size.
+Instead, TLSF always runs in constant time (i.e., $O(1)$), and it is possible to estimate response time.
+
+{\bf Efficient memory consumption.}
 Memory efficiency is improved by suppressing memory fragmentation.
-Various tests have obtained an average fragmentation of less than 15\% and a maximum fragmentation of less than 25\%.
-
-\subsubsection{TLSF Algorithms}
-
-TLSF algorithm classifies memory blocks into two stages and searches for a memory block that is optimal for the requested memory size.
-The overview of TLSF algorithm is shown in Fig.\ref{fig:TLSF}.
-Consider a case where a request, $malloc(100)$, is called to allocate a memory.
-First, it is classified by the most significant bit of the requested memory size.
-In this case, since 100 is represented by binary number as 1100100, it is in the range from 64 to 128 from the most significant bit.
-Second, it is further classified.
-In this case, 64 to 128 are divided into 4, and 100 is in the block of 96 to 111.
-Free block\footnote{Free block is an available memory block.} in this range is used.
-
-A simple fixed-size memory block allocator results in the waste of up to 50 \%.
-However, TLSF classifies it finely in two steps.
+Various experiments have achieved an average fragmentation of less than 15 \% and a maximum fragmentation of less than 25 \% \cite{url:TLSF}.
+
+\subsubsection{TLSF algorithm}
+
+As illustrated in Fig. \ref{fig:TLSF}, the TLSF algorithm classifies memory blocks into two stages and searches for a memory block that optimally lines up with the requested memory size.
+Particularly, consider the case in which a request to dynamically allocate 98 bytes is made via $malloc(98)$.
+First, the request is classified based on the leftmost 1 bit in the requested memory size.
+In this example, since 98 is represented in binary as byte 01100010, it falls in the range of 64-128 based on the leftmost 1 bit.
+Second, the request is further classified as follows.
+The range from 64 to 128 is further divided into four equally sized groups, with 98 falling into the block ranging from 96 to 111.
+A free block\footnote{A free block is an available memory block.} in this range is then used to fulfill the memory allocation request.
+
+Without using the above approach, a simple fixed-size memory block allocator results in wasted memory blocks of up to 50 \%.
+As illustrated above, TLSF classifies the memory allocation process finely in two steps.
 Therefore, it is a memory efficient algorithm.
-In addition, TLSF searches at the same speed and at high speed, $O(1)$.
+Fortunately, given its design, TLSF searches for memory blocks in constant time (i.e., $O(1)$.
 
@@
     \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
-    \caption{TLSF Algorithm}
+    \caption{TLSF algorithm}
     \label{fig:TLSF}
@@
 
-This section describes the component design of TLSF memory allocator.
-In this research, we are using TECS to componentize TLSF.
-The version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
+In this subsection, we describe the component design of the TLSF memory allocator.
+Note that we use TECS to componentize TLSF.
+Further, the version of TLSF used is 2.4.6\footnote{http://www.gii.upv.es/tlsf/main/repo}.
 
@@
 
-Fig.\ref{src:TLSFSignature} is a signature description for memory management used by the allocator.
-It defines the memory pool initialization function {\it initializeMemoryPool}, memory allocation function {\it calloc}, {\it malloc}, {\it realloc}, and memory release function {\it free} as a signature.
+In Fig. \ref{src:TLSFSignature}, we summarize the signature used by the allocator for dynamic memory management.
+Particularly, this component defines the memory pool initialization function {\it initializeMemoryPool()}, memory allocation functions {\it calloc()}, {\it malloc()}, and {\it realloc()}, and the memory release function {\it free()}.
 
@@
 
-The celltype description of the TLSF memory allocator component is shown in Fig.\ref{src:TLSFCelltype}.
-An entry port, {\it eMalloc}, is connected to all components that perform memory management such as $malloc$ and $free$.
-Here, {\it [inline]} is a specifier for Implementation as inline functions.
-A memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
-Each component holds own heap area.
-Therefore, even when calling functions for memory management at the same time in different threads, it is possible to operate without memory contention.
+Next, Fig. \ref{fig:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
+Here, entry port {\it eMalloc} is connected to all components that perform memory management including $malloc()$ and $free()$.
+Further, {\it [inline]} is a specifier to suggest to the TECS generator to implement as an inline function.
+Memory pool size is defined as an attribute, and a pointer to a memory pool is defined as a variable.
+Note that each component maintains its own heap area.
+Therefore, even when calling memory management functions simultaneously from different threads, it is possible to operate without any memory contention.
 
@@
 
-As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously from multiple threads, memory competition may occur in some cases.
-In the research, TLSF is componentized using TECS as shown in Fig.\ref{fig:WithTECS}.
-It is possible to operate in thread safe without exclusive control, because each component independently holds a heap area and manages memory within it.
+As shown in Fig.\ref{fig:WithoutTECS}, since TLSF before componentization shares the heap area with multiple threads, if memory is allocated or released simultaneously via multiple threads, memory contention may occur in some cases, thus causing intermittent synchronization problems that can be extremely difficult to debug.
+In this study, TLSF is componentized using TECS, as shown in Fig.\ref{fig:WithTECS}.
+It is possible to operate in thread safe without exclusive control because each component independently holds a heap area and manages memory within it.
 
@@
 
-Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component shown in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
-Two sets of task components and TLSF components are combined.
-Each memory pool size can be configured as a variable (Lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
-Fig.\ref{src:TLSFC} is the part of the code actually calling the function of the TLSF memory allocator component.
-The use part shows a function that the mruby VM allocates memory in the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3} which is introduced in Section \ref{sec:mrubyonTECS}.
-Line 8 calls the {\it free} function of the TLSF memory allocator component.
-{\it cMalloc\_} represents the name of the call port (Line 2 in Fig.\ref{src:TLSFBuild}).
-Likewise, Lines 13 and 17 call the function for memory allocation.
-The heap area of {\it TLSFMalloc\_001} component is used if the code of \ref{src:TLSFC} is executed in {\it Task\_001}, and if that is executed in {\it Task\_002}, the heap area of {\it TLSFMalloc\_002} component is used, respectively.
-In this way, in the component-based development using TECS, it is possible to operate with the same code without modifying the C code, although the cells are different.
-
-\subsubsection*{Multiple RiteVM}
+Next, Fig.
+\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.
+\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Here, two sets of task components and TLSF components are combined.
+Further, each memory pool size can be configured as a variable (lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
+Fig. \ref{src:TLSFC} presents the code that actually calls functions of the TLSF memory allocator component.
+The use part shows a function in which the RiteVM allocates memory within the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, which we introduced in Section \ref{sec:mrubyonTECS} above.
+Line 8 calls the {\it free()} function of the TLSF memory allocator component.
+{\it cMalloc\_} represents the name of the call port on line 2 in Fig.\ref{src:TLSFBuild}.
+Similarly, lines 13 and 17 call the memory allocation function.
+Particularly, the heap area for the {\it TLSFMalloc\_001} component is used if the code from \ref{src:TLSFC} is executed in {\it Task\_001}; conversely, if that code is executed in {\it Task\_002}, the heap area of the {\it TLSFMalloc\_002} component is used.
+Using this approach, in component-based development using TECS, it is possible to operate with the same code without modifying the underlying C code, although the resulting cells differ.
+
+\subsubsection*{Multiple RiteVM instances}
 
@@
 
-The proposed framework uses TLSF memory allocator for memory management of RiteVMs.
-However, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple, memory contention will occur.
-As a RiteVM allocates and deallocates memory at high frequency, the memory contention immediately occurs in the case of multiple VMs.
-
-The TLSF components are connected to the RiteVMs to hold own heap area in each RiteVM as shown in Fig.\ref{fig:UseCase_mruby}.
-Since each TLSF component holds a memory pool, multiple RiteVMs can be executed without memory contention.
-Fig.\ref{fig:UseCase_mruby} shows that the first RiteVM has a heap area of 1 MB (1024*1024) and the second VM has a heap area of 2 MB (2*1024*1024).
-It is easy to set different heap areas in each RiteVM.
-In addition, RiteVM performs incremental GC (Garbage Collection), and a VM that started GC does not disturb the execution of other VMs by running GC.
-
-\subsubsection*{Memory management for data sending and receiving}
+The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
+Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.
+Note that the TLSF components are connected to the RiteVMs to ensure that each component has its own heap area within each RiteVM, as illustrated in Fig. \ref{fig:UseCase_mruby}.
+Since each TLSF component maintains its own memory pool, multiple RiteVMs can be executed without the possibility of any memory contention.
+In Fig.
+\ref{fig:UseCase_mruby}, we observe that the first RiteVM has a heap area of 1 MB (i.e., 1024 $\times$ 1024 bytes) and the second RiteVM has a heap area of 2 MB (i.e., 2 $\times$ 1024 $\times$ 1024 bytes).
+As illustrated in Fig. \ref{fig:UseCase_mruby}, it is easy to configure different-sized heap areas for each RiteVM.
+Further, each RiteVM performs incremental garbage collection (GC), and a RiteVM that has started GC does not disturb the execution of other RiteVMs in its GC execution.
+
+\subsubsection*{Memory management for sending and receiving data}
 
@@
 
-In the TCP/IP protocol stack, memory allocation and release are repeated in each layer such as TCP layer, IP layer, and Ethernet layer.
-Therefore, the role of allocator is important.
-TINET+TECS combines all components that manage memory with the allocator.
-The TLSF memory allocator can execute at the same speed as compared with the fixed-size memory allocator which TOPPERS/ASP3 supports as standard, and can improve the memory efficiency.
-In addition, as shown in Fig.\ref{fig:UseCase_TINET}, the fixed-size memory allocator needs to prepare memory pools of different sizes, and select a memory pool as necessary.
-TLSF+TECS efficiently manages the memory without selecting a memory pool.
-TLSF+TECS can be easily extended to TINET+TECS since TINET+TECS is a component-based system.
-
-%4
+In the TCP/IP protocol stack, memory allocation and subsequent deallocation are repeated in each layer, including the TCP, IP, Ethernet, and other layers.
+Therefore, the role of the memory allocator is critical.
+The TINET+TECS framework combines all components that manage memory within the allocator.
+The TLSF memory allocator can execute at the same speed as that of the fixed-size memory allocator that TOPPERS/ASP3 supports as standard; further, the TLSF memory allocator can improve memory efficiency.
+As illustrated in Fig. \ref{fig:UseCase_TINET}, the fixed-size memory allocator prepares memory pools of different sizes and selects a memory pool whenever it is necessary.
+Conversely, TLSF+TECS efficiently manages memory without the need to select a memory pool.
+Finally, TLSF+TECS can be easily extended to TINET+TECS since TINET+TECS is a component-based system.
 
@@
 
-In the proposed framework, applications can call TINET functions such as TCP and UDP from mruby programs because mruby-TECS bridge automatically generates the code linking mruby and C.
-Fig.\ref{src:mruby} shows an mruby program to transmit the value acquired from a sensor.
-mruby makes it easier to develop applications than existing TINET, i.e., C language.
-
-In the case of a simple application, a few functions are only used and there are some unused functions.
-For example, the application only uses a function to send by TCP protocol as shown in Fig.\ref{src:mruby}.
-The proposed framework incorporates TINET+TECS, and can easily customize the TCP/IP protocol stack such as removing UDP functions, supporting only IPv4, or removing TCP receiving function.
-It can be applied to embedded systems with strict memory constraints by removing unused functions.
+In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
+Fig. \ref{src:mruby} shows an example of mruby program that transmits the value acquired from the sensor to another device or a server.
+In general, mruby makes it easier to develop applications than using C with the existing TINET.
+
+For a simple application, typically only a few functions are used, with numerous unused functions.
+As an example, the application code shown in Fig. \ref{src:mruby} only uses a function to send data via TCP.
+The proposed framework incorporates TINET+TECS and can easily customize the TCP/IP protocol stack by removing functions, such as UDP functions, functions that support only IPv4, or TCP receiving functions.
+As such, the proposed framework can be applied to embedded systems with strict memory constraints by removing many unused functions.
 
@@
         val = io.read  
-        cep.snd val.to_s + "\n"		
+        cep.send val.to_s + "\n"		
         RTOS.delay(1000)			
@@
 \end{lstlisting}
-\caption{Example of mruby application}
+\caption{An example of mruby application}
 \label{src:mruby}
@@
 
+%4
 \section{Evaluation}
@@
 \ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig.
-\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased by 0.3 \% due to exclusive contorol.
+\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased by 0.4 \% due to exclusive control.
 

### 2018-02-12 ipsj/paper.tex
Fix abstract and introduction (by enago)

@@
 
-High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
-To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
-This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
-The proposed framework enables that that mruby program calls TINET, a TCP/IP protocol stack for use in embedded systems, functions.
-In addition, this paper proposes two component-based functionality such as a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
-TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
+In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
+To improve productivity, the mruby on TOPPERS embedded component system (TECS) framework has been proposed; note that mruby on TECS framework employs a scripting language (i.e., a lightweight Ruby implementation) and supports component-based development.
+In this paper, we propose an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
+Our proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
+Further, the proposed framework incorporates two component-based functions, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+Here, TINET+TECS improves configurability and scalability and offers software developers high levels of productivity through variable network buffer sizes and the ability to add or remove various TCP (or UDP) functions.
 TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
-TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
-Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
+Further, TLSF+TECS is a thread-safe memory allocator that runs at high speeds and efficiently consumes memory.
+The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; further, we conclude that configurability is improved.
+Finally, the TLSF+TECS function which obtains and report statistical information regarding mruby's virtual machine (VM) memory usage, helps developers debug and verify their embedded IoT systems.
 
@@
 
-The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
-The IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, and they must demonstrate high quality and high performance.
-This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.
-
-Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
-Component-Based Development is a design technique that can be applied to reusable software development.
-Verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
+As an essential next evolutionary step for the Internet, the Internet of Things (IoT) connects various items and platforms such as wearable devices and smart devices, via the Internet to further enrich people's lives \cite{par:IoTComputing}.
+The IoT uses embedded systems, such as data sensors and controlling actuators, as elemental constituents; therefore, these devices must demonstrate consistently high levels of quality and runtime performance.
+These requirements have consequently led to an increase in their complexity and scale; further, to be successful and widely adopted by users, these systems must have low production costs and short development cycles.
+
+Complex and large-scale software systems can be developed efficiently using component-based techniques \cite{par:Crnkovic},\cite{par:CBD}.
+Particularly, component-based development is a design technique that is applicable to the development of reusable software.
+Given its importance in terms of reliability, verification of component-based systems has been extensively researched \cite{par:Blaming},\cite{par:Verification}.
 Individual component diagrams enable the visualization of an entire system.
-In addition, component-based systems are flexible with regard to extensibility and specification changes.
-The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.
-
-In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
-Currently, most embedded software is programmed in C language.
-However, development in C language results in large code size, incurs high costs, and requires significant development time.
-In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.
-
-For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
-Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
-Therefore, applying scripting languages to embedded systems is difficult.
-To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS},\cite{par:mrubyonTECS3}.
-This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby},\cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
-
-This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
-In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS, is comprised, and it is possible to utilize TINET function from mruby programs.
-TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
-TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
-TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.
-In the case of only sending values obtained by sensors, it is better to easily customize the minimum configuration of the TCP/IP protocol stack, such as removing unused functions.
-The improved configurability leads to satisfying strict memory constraints of embedded systems.
-In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
-TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by dividing memory blocks in two stages.
-In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
-TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has own heap area.
-
-{\bf Contributions}: The proposed framework provides the following contributions.
-
-{\bf Applicable to various devices}
-The proposed framework does not depend on RTOSs or hardware, it can be utilized in various devices.
-mruby code is portable.
+Further, component-based systems are flexible in terms of their extensibility and resilience to specification changes.
+Typical component-based development environments focused on embedded systems include the TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
+
+In addition to specific development environments, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to develop quality software.
+Currently, most embedded software is implemented using the C language, but development in C typically results in large code size, high costs, and significant development time.
+However, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it effectively supports and promotes the development of reusable scripts.
+
+Embedded systems often have real-time requirements; therefore, real-time properties, such as estimating worst-case execution times, are very important.
+Although scripting languages are easy to use and read, their execution typically requires more time than that required for executing the code written in C.
+Therefore, applying scripting languages to embedded systems poses a major difficulty.
+To address this limitation, in \cite{par:mrubyonTECS} and \cite{par:mrubyonTECS3}, mruby on TECS has been proposed as a component-based framework for efficiently running script-based programs.
+This framework integrates two key technologies, i.e., mruby, which is a lightweight implementation of Ruby designed specifically for embedded systems \cite{par:mruby},\cite{url:mruby} and TECS, which is a component-based framework also designed specifically for embedded systems \cite{par:TECS}.
+
+In this paper, we propose an extended framework for mruby on TECS that can be applied to embedded network software development involving IoT devices.
+The proposed framework makes it possible to utilize Tomakomai Internetworking (TINET) functions from within the mruby programs.
+Note that TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET} that comprises a number of complex source code files, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
+To overcome the above problem, TINET+TECS is a componentized TINET implementation that incorporates TECS to improve the configurability and scalability of TCP/IP software.
+For IoT applications that should only be sending values obtained by one or more than one sensors, it is ideal to easily customize the minimum configuration of the TCP/IP protocol stack, e.g., by removing unused functions.
+This improved configurability also leads to satisfying strict memory constraints of IoT devices.
+
+In addition to TINET+TECS, the proposed framework incorporates a component-based dynamic memory allocator based on Two-Level Segregate Fit (TLSF) called TLSF+TECS.
+Note that TLSF is a dynamic memory allocator designed specifically for real-time systems that always run in constant time (i.e., $O(1)$) and improves memory usage efficiency by dividing memory blocks in two distinct stages.
+In the current version of TLSF, memory contention may occur when multiple threads run simultaneously.
+To address this problem, TLSF+TECS is a componentized TLSF memory allocator that is also entirely thread-safe because each component has its own heap area from which memory is actually allocated.
+In TLSF+TECS, developers can also obtain statistical information regarding memory usage, which is crucial in analyzing memory operations and locating bugs.
+
+{\bf Contributions}: The proposed framework provides the following three contributions.
+
+{\bf Applicability to various devices.}
+The proposed framework does not depend on real-time operating systems (RTOSs) or specific hardware; instead, it can be utilized by various devices, i.e., mruby code is portable.
 Therefore, it is possible to run the same program on different devices.
 
-{\bf Improve configurability}
-Because TINET+TECS is a component-based system, its software can flexibly change as system configuration by, for example, resizing network buffer, adding/removing TCP (or UDP) functionality, or supporting either IPv4 or IPv6.
-In addition, the use of individual component diagrams enables visualization of an entire system.
-
-{\bf Thread-safe memory allocator}
-TLSF+TECS runs thread safely without exclusive control even if multiple threads operate in parallel.
-Moreover, each thread can easily set own heap area.
+{\bf Improved configurability.}
+Because TINET+TECS is a component-based system, its software can flexibly change in response to system configuration changes, such as resizing of network buffers, adding or removing TCP (or UDP) functions, and supporting both IPv4 and IPv6.
+Further, the use of individual component diagrams enables visualizations of the entire system.
+
+{\bf Thread-safe memory allocation}
+TLSF+TECS safely runs multiple threads without exclusive control even if the threads operate in parallel.
+To achieve this, each thread can easily set up its own heap area.
+Further, statistical information is available to help developers debug and verify the specific memory usage of the given system.
 
 {\bf Organization}: The remainder of this paper is organized as follows.
-Section \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
-Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
-Section \ref{sec:Evaluation} evaluates the proposed framework.
-Related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.
+Section \ref{sec:System Model} introduces the system model and fundamental technologies, i.e., TECS, mruby, and mruby on TECS.
+Next, Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
+In Section \ref{sec:Evaluation}, we provides a detailed evaluation of the proposed framework.
+Finally, related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.
 
@@
 
-This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
+This section describes the system model of the proposed framework, including fundamental technologies such as TECS and mruby.
 The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
@@
 
-The proposed framework is an extended mruby on TECS framework for network programming.
-It can use TINET+TECS functions from mruby programs.
-TINET+TECS is a component-based TCP/IP protocol stack comprised in the proposed framework, and it compensates for the original TINET's weak point, that it is hard to maintain, extend, and analyze the software due to many complex source codes and improves the configurability.
-In addition, TLSF+TECS, a component-based dynamic memory allocator, is used for memory management of mruby's RiteVMs and TCP/IP buffers in the proposed framework.
-Since each component holds own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption which is a merit of TLSF.
+The proposed framework is an extended mruby on TECS framework to develop network software for IoT devices.
+Developers can use TCP- and UDP-related functions from mruby programs.
+The proposed framework incorporates two functionalities: TINET+TECS and TLSF+TECS.
+TINET+TECS is a component-based TCP/IP protocol stack comprised in the proposed framework, and it compensates for the original TINET's weak point that it is hard to maintain, extend, and analyze the software due to many complex source codes and improves the configurability.
+TLSF+TECS which is a component-based dynamic memory allocator is used for memory management of RiteVMs and TCP/IP buffers in the proposed framework.
+Since each TLSF component maintains its own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption, which is the advantage of TLSF.
 

### 2018-02-12 ipsj/paper.tex
Add requirements

@@
 In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
-To improve productivity, the mruby on TOPPERS embedded component system (TECS) framework has been proposed; note that mruby on TECS framework employs a scripting language (i.e., a lightweight Ruby implementation) and supports component-based development.
+As an approach to improve the producivity of software development, the mruby on TOPPERS embedded component system (TECS) framework has been proposed; note that mruby on TECS framework employs a scripting language (i.e., a lightweight Ruby implementation) and supports component-based development.
 In this paper, we propose an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
@@
 In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
-mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
-Moreover, the proposed framework comprises TLSF+TECS.
-TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
+mruby programs can call the TINET functions required for network software through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
+
+{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
+\begin{description}
+    \item[R1:]
+        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.
+
+    \item[R2:]
+        Multiple mruby programs can run in pallalel to improve producivity of software development.
+        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
+
+\end{description}
+
 The following subsection explains TECS, mruby, and mruby on TECS framework.

### 2018-02-22 ipsj/paper.tex
Add review 1 to conclusion

@@
 \ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig.
-\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased by 0.4 \% due to exclusive control.
+\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased due to exclusive control.
+In addition to the overhead of execution time, a RiteVM is not affected by other RiteVMs since TLSF+TECS keeps heap area independently.
+GC on a RiteVM is performed periodically; however, there is a part that GC is not performed periodically in RiteVM 1 of Fig. \ref{fig:EvaluationOfExecutionTime}.
+In Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, two RiteVMs share one heap area; therefore, RiteVM 2 is affected by RiteVM 1.
+On the other hand, in Fig. \ref{fig:EvaluationOfTLSFStatistics}, RiteVM 2 is not affected by RiteVM 1.
 
@@
 Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
+
 TINET+TECS is a componentized version of TINET, a compact TCP/IP protocol stack that uses TECS.
@@
 Scalability is also improved because the component-based framework simplifies to add/remove and change protocols such as TCP/UDP, IPv4/IPv6, and Ethernet/PPP.
-
 This paper also presented the dynamic connection, a new TECS functionality, to enable dynamic processing while reducing memory consumption.
@@
 Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
+TINET+TECS and TLSF+TECS can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
+
 In addition, the RiteVMs, TINET+TECS, and TLSF+TECS are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.

### 2018-02-22 ipsj/paper.tex
Fix thread-safe part

@@
 
-The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since the existing TLSF is not thread-safe, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
+The proposed framework uses the TLSF memory allocator for memory management within RiteVMs; however, since it is difficult to hundle multiple memory pools in the existing TLSF, if memory is allocated or deallocated from multiple threads, memory contention will likely occur.
 Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.

### 2018-02-22 ipsj/paper.tex
Add sentences to related work
Fix evaluation

@@
 
-To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
-
-The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
-For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
-In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
-\ref{fig:ComponentProtocolStack}.
-For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
-In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
-The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
-As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \caption{Execution times of TINET and TINET+TECS}
-    \label{fig:EvaluationOfExecutionTime}
-\end{figure}
-
-The memory consumptions of TINET and TINET+TECS are compared in Table \ref{tab:EvaluationOfMemoryConsumption}.
-The memory consumption of TINET+TECS is about 1\% higher than that of TINET, as the data and processes such as initialization of cells, descriptors, function tables, and skeleton functions needed to manage TECS components increase memory consumption.
-
-\begin{table}[t]
-    \centering
-    \caption{Memory consumption of TINET and TINET+TECS}
-    \begin{tabular}{c|r|r|r|r}
-        \hline\hline
-                    &   text       &  data    &   bss      &  total     \\ \hline
-        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
-        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
-        \hline
-        \multicolumn{5}{r}{Including the application and kernel objects}
-    \end{tabular}
-    \label{tab:EvaluationOfMemoryConsumption}
-\end{table}
-
 As shown in Table \ref{tab:EvaluationOfConfigurability}, the code lines for modification were measured to demonstrate the improved configurability.
@@
 
+Next, to demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
+
+The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
+For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
+In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
+\ref{fig:ComponentProtocolStack}.
+For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
+In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
+The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
+As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
+    \caption{Execution times of TINET and TINET+TECS}
+    \label{fig:EvaluationOfExecutionTime}
+\end{figure}
+
+The memory consumptions of TINET and TINET+TECS are compared in Table \ref{tab:EvaluationOfMemoryConsumption}.
+The memory consumption of TINET+TECS is about 1\% higher than that of TINET, as the data and processes such as initialization of cells, descriptors, function tables, and skeleton functions needed to manage TECS components increase memory consumption.
+
+\begin{table}[t]
+    \centering
+    \caption{Memory consumption of TINET and TINET+TECS}
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                    &   text       &  data    &   bss      &  total     \\ \hline
+        TINET       &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
+        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+        \hline
+        \multicolumn{5}{r}{Including the application and kernel objects}
+    \end{tabular}
+    \label{tab:EvaluationOfMemoryConsumption}
+\end{table}
+
 \subsection{Dynamic connection}
@@
 Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.
 
 The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
+Therefore, the proposed framework can reduce memory consumption.
 In addition, the extended mruby on TECS supports legacy code such as a motor driver.

### 2018-02-22 ipsj/reply_letter/paper.tex
Update reply letter

@@
 Thank you for your suggestion.
-提案した２つの機能：TINET+TECSとTLSF+TECSは、mrubyに限らず、TECSのみで動作するため、他のシステムにも適用できる。
-〇〇ページのフットノートおよび結論に追加する。
-\begin{itembox}[|]{}
+The main contribution of this paper is to build a platform for IoT devices with high productivity using mruby.
+However, as the reviewer 1 says, the proposed two functionalities, TINET+TECS and TLSF+TECS, can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
+We added the following sentence in Section 6.
+
+\begin{itembox}[|]{Conclusion}
+TINET+TECS and TLSF+TECS can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
 \end{itembox}\\
+
 \end{flushleft}
@@
 
-2章システムモデルの冒頭に、要件を書き加える。
+We added the requirements at the beginning of Section 2.
+\begin{itembox}[|]{}
+{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
 \begin{description}
-    \item[R1:] IoTシステムには、ネットワークが重要不可欠であるため、TCP/IP機能が使えること
-    \item[R2:] mrubyはシングルタスクしかサポートしておらず、開発の生産性を高めるためにマルチタスク機能を提供すること
+    \item[R1:]
+        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.
+
+    \item[R2:]
+        Multiple mruby programs can run in pallalel to improve producivity of software development.
+        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
+
 \end{description}
+\end{itembox}\\
+
 \end{flushleft}
@@
 \begin{enumerate}
-\item 少ないコード変更量でプロトコルの設定を変更できるというコンフィグラビリティ評価を強調する。Fig.10（プロトコルのコンポーネント図）を拡大してTCPのみ、UDPのみ、の図を加えて、プロトコルの変更が容易にできると加える。
-\item TLSF+TECS評価部分で、2つのVMを動かしたグラフ（つまり線が２つあるグラフ）を追加し、「２つのVMで違うアプリケーションが並行動作しているので、スレッドセーフに動作していることも示している」と加える。
+\item 
+    Table 3 (Modified code lines of CDL) showed the configurability evaluation, but since it is hard to understand, we moved to the beginning of the evaluation section and clarified the point we would like to claim.
+
+\begin{itembox}[|]{Evaluation}
+As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
+This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
+\end{itembox}\\
+
+\item We added evaluations of TLSF+TECS in Section 4.3.
+    This section shows a comparison which two diffrent applications are executed with two ways.
+    One is to hold its own heap (TLSF+TECS), and the other is to utilize a execulusive control such as semaphore.
+
 \end{enumerate}
@@
 \begin{enumerate}
-\item コメント3-(a)で協調した部分および、UDPの実行時間とメモリ消費量の評価を加える。また、「既存TINETで対応しているTCPとUDPでの評価を行った」と追記。
+\item
+    TODO: 
+    We added the execution times with UDP and discussed it.
+    Note, we evaluated only TCP and UDP which are supported by TINET.
+\begin{itembox}[|]{Evaluation}
+Conversely, we evaluated the execution times with UDP as shown in Fig. 29.
+TINET+TECS can run at the same speed as TINET; therefore, the overheads of TINET+TECS are low.
+\end{itembox}\\
 
-\item TCPのみ、UDPのみ、両方のメモリ消費量
+\item
+    TODO:
+    We added the memory usage of only TCP, only UDP, and both TCP and UDP.
+
 \end{enumerate}
@@
 論文から、オリジナリティはTLSFとよぶダイナミックメモリアロケータを構築したことではないかと推測していますが、読み解くのは容易ではありません。
+\end{flushleft}
 \begin{flushleft}
@@
 
-主張したい点はソフトウェア開発の生産性が向上させるプラットフォームであるため、３章Use CaseにmrubyとC言語比較を加え、mrubyだと開発がより簡単になることを強調する。
-コンフィグラビリティは向上しつつ、execution time と memory consumption のオーバヘッドを抑えることができたという流れにする。
+評価部分は，コンポーネント化による実行時間やメモリ消費のオーバヘッドを抑えることができたことを示しています．
+コンフィグラビリティ評価を冒頭におき，主張したい点が分かりやすいように変更しました．
+
 \end{flushleft}
-\begin{enumerate}
-\item AbstractとIntroduction
+
+\begin{flushleft}
+\textbf{1-(a):} AbstractとIntroduction
 
@@
 シンプルに、解くべき問題点を列挙し、それに対応づく解決策を挙げるようにしてください。
+\end{flushleft}
+\begin{flushleft}
+\textbf{Our reply:}
+
+ご指摘ありがとうございます．
+提案すべきは，「IoTデバイス向けのmrubyプラットフォーム」とし，それを実現するためにTINET+TECSとTLSF+TECSの２つの機能を組み込むという表現に修正を行いました(AbstractおよびIntroduction).
+また，問題点と解決策が対応づくように，貢献部分や要件を修正・加筆しました．
+
+\begin{itembox}[|]{Abstract}
+In this paper, we propose an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
+Our proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
+Further, the proposed framework incorporates two component-based functions, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+\end{itembox}\\
+
+% 提案は、「IoTデバイス向けのmrubyプラットフォーム」であり、TINET+TECSとTLSF+TECSの「2つの機能を組み込んだ」とする。
+% 貢献部分に、「TINETのコンフィグラビリティを向上させる」「マルチVMを実現する」と追記する。
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{1-(b):} 2. System Model
+
+章立ての位置付けとして、この章では、IoTデバイスのproductivity向上についての要件や課題が記されていることを期待して読むのですが、TECSとmrubyの説明にとどまっています。論文は、新規性・有用性は何かを探しながら読むことが目的であり、開発に必要な知識を得ることは目的ではありません。新規性・有用性を主張するのに、必要な内容を記すようにしてください。
+\end{flushleft}
+\begin{flushleft}
+\textbf{Our reply:}
+
+2章システムモデルの冒頭に，提案フレームワークを実現するための要件を書き加えました．
+
+\begin{itembox}[|]{}
+{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
+\begin{description}
+    \item[R1:]
+        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.
+
+    \item[R2:]
+        Multiple mruby programs can run in pallalel to improve producivity of software development.
+        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
+
+\end{description}
+\end{itembox}\\
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{1-(c):} 3章以降
+
+AbstractおよびIntroductionを修正にともない、そのストーリーにあった内容にしてください。
+
+\end{flushleft}
+\begin{flushleft}
+\textbf{Our reply:}
+
+上で述べたように，「IoTデバイス向けのmrubyプラットフォーム」を提案し，それを実現するために，２つの機能TINET+TECSとTLSF+TECSを組み込んだというストーリーにしました．
+それに伴い，実現するための要件を加筆し，UDPの評価およびTLSF+TECSの評価を付け加えました．
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{1-(d):} 5. Related Work
+
+MDDについてサーベイがありますが、execution time と memory consumptionを評価するならば、それと関連したサーベイをしてください。
+
+\end{flushleft}
 
@@
 
-提案は、「IoTデバイス向けのmrubyプラットフォーム」であり、TINET+TECSとTLSF+TECSの「2つの機能を組み込んだ」とする。
-貢献部分に、「TINETのコンフィグラビリティを向上させる」「マルチVMを実現する」と追記する。
-\end{flushleft}
+関連研究に，提案フレームワークの利点として，速い実行時間とコンフィグラビリティ性による小さいメモリ消費の2点を加筆しました．
 
-\item 2. System Model
+\begin{itembox}[|]{Related work}
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.
 
-章立ての位置付けとして、この章では、IoTデバイスのproductivity向上についての要件や課題が記されていることを期待して読むのですが、TECSとmrubyの説明にとどまっています。論文は、新規性・有用性は何かを探しながら読むことが目的であり、開発に必要な知識を得ることは目的ではありません。新規性・有用性を主張するのに、必要な内容を記すようにしてください。
+The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
+Therefore, the proposed framework can reduce memory consumption.
+\end{itembox}\\
 
-\begin{flushleft}
-\textbf{Our reply:}
-
-システムモデルの冒頭に要件を加える。
-\end{flushleft}
-
-\item 3章以降
-
-AbstractおよびIntroductionを修正にともない、そのストーリーにあった内容にしてください。
-
-\begin{flushleft}
-\textbf{Our reply:}
-
-3章UseCaseを3-1にするべきか。
-4章の評価の順番を変える。（コンフィグラビリティ評価、オーバヘッド評価の順番）
-\end{flushleft}
-
-\item 5. Related Work
-
-MDDについてサーベイがありますが、execution time と memory consumptionを評価するならば、それと関連したサーベイをしてください。
-
-\begin{flushleft}
-\textbf{Our reply:}
-
-execution time と memory consumption は補足的な評価である。今回のサーベイはIoTシステムにおけるソフトウェア開発手法である。
-\end{flushleft}
-
-\end{enumerate}
-\end{flushleft}
-
-\begin{flushleft}
-\textbf{Our reply:}
 \end{flushleft}
@@
 
-不定詞のTo として書いた。
-英文校正をかけた。
+ご指摘ありがとうございます．
+英文校正を依頼し，表現のミスや誤字・脱字の修正を行いました．
 \end{flushleft}
@@
 
-引用を追加する。
-Web引用の日付けを追加する。
+ご指摘の通り，引用を追加いたしました．
+また，IPSJ論文誌のサンプルを参考にWebの引用について修正を行いました．
 \end{flushleft}
@@
 
-指摘部分は修正した。
-他の部分も英文校正にかけ、修正を行う。
+ご指摘ありがとうございます．
+英文校正を依頼し，表現のミスや誤字・脱字の修正を行いました．
 \end{flushleft}

### 2018-02-24 ipsj/reply_letter/paper.tex
Update reply letter

@@
 \usepackage{a4wide}
-\usepackage{graphicx}
+\usepackage[dvipdfmx]{graphicx}
 \usepackage{fancybox}
@@
 
+\section{Response to Meta-reviewer}
+\begin{enumerate}
+
+\item \begin{flushleft}
+\textbf{Comment:}
+
+Basically, the proposed framework seems to be useful.
+However as the reviewers suggest, this paper is not sophisticated as a research paper including English.
+
+\end{flushleft}
+
+\begin{flushleft}
+\textbf{Our reply:}
+
+Thank you for the comments.
+In order to reflect the comments of reviewers, we fixed abstract and introduction, and added requirements and evaluations such as the execution time and memory consumption of UDP (4.2) and TLSF+TECS (4.4).
+Furthermore, we fixed our English in this paper by a native speaker in a proofreading company.
+For more detail, please see our replies as follows.
+
+\end{flushleft}
+
+\end{enumerate}
+
+\clearpage
+
 \section{Response to 1\st reviewer}
@@
 The main contribution of this paper is to build a platform for IoT devices with high productivity using mruby.
-However, as the reviewer 1 says, the proposed two functionalities, TINET+TECS and TLSF+TECS, can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
+We modified Abstract as follows.
+
+However, as the reviewer 1 mentioned, the proposed two functionalities, TINET+TECS and TLSF+TECS, can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
 We added the following sentence in Section 6.
+
+\begin{itembox}[|]{Abstract}
+In this paper, we propose an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
+Our proposed framework enables mruby programs to utilize Tomakomai Internetworking (TINET), a TCP/IP protocol stack specifically designed for use in embedded systems.
+Further, the proposed framework incorporates two component-based functions, i.e., a componentized TINET stack called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
+\end{itembox}\\
 
@@
 \begin{itembox}[|]{}
-{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
+{\bf Requrements:} The requirements of the proposed mruby platform for IoT devices are defined as follows.
 \begin{description}
@@
     \item[R2:]
-        Multiple mruby programs can run in pallalel to improve producivity of software development.
-        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
+        Multiple mruby programs can run concurrently to improve productivity of software development.
+        A thread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
 
@@
 \item
-    Table 3 (Modified code lines of CDL) showed the configurability evaluation, but since it is hard to understand, we moved to the beginning of the evaluation section and clarified the point we would like to claim.
+    We added the new subsection (4.1) for the configurability evaluation.
 
-\begin{itembox}[|]{Evaluation}
+\begin{itembox}[|]{4.1 Improved configurability}
 As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
@@
 
-\item We added evaluations of TLSF+TECS in Section 4.3.
-    This section shows a comparison which two diffrent applications are executed with two ways.
-    One is to hold its own heap (TLSF+TECS), and the other is to utilize a execulusive control such as semaphore.
+\item
+    We added evaluations of TLSF+TECS in Section 4.3.
+    This section shows a comparison which two different applications are executed with two ways.
+    One is to hold its own heap (TLSF+TECS), and the other is to utilize an exclusive control such as a semaphore.
+
+\begin{itembox}[|]{4.4 Memory usage of RiteVMs by TLSF+TECS}
+The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control concurrently because each TLSF component holds its own heap area.
+The TLSF+TECS framework provides functionality to acquire statistical information describing dynamic memory usage.
+Therefore, it is possible to analyze the operational status of the TLSF and GC on RiteVMs.
+\ldots\ldots
+
+% \begin{figure}[h]
+    \centering
+    \includegraphics[width=8cm,clip]{../figure/EvaluationOfTLSFStatistics.pdf}
+    % \caption{Memory usage of RiteVMs with TLSF+TECS}
+    % \label{fig:EvaluationOfTLSFStatistics}
+% \end{figure}
+
+\end{itembox}\\
 
@@
 \item
-    TODO: 
     We added the execution times with UDP and discussed it.
-    Note, we evaluated only TCP and UDP which are supported by TINET.
-\begin{itembox}[|]{Evaluation}
+    Note that we evaluated TCP and UDP which are supported by TINET.
+
+\begin{itembox}[|]{4.2 Performance of TINET+TECS}
 Conversely, we evaluated the execution times with UDP as shown in Fig. 29.
@@
 \item
-    TODO:
     We added the memory usage of only TCP, only UDP, and both TCP and UDP.
+
+\begin{itembox}[|]{4.2 Performance of TINET+TECS}
+\end{itembox}\\
 
@@
 
-評価部分は，コンポーネント化による実行時間やメモリ消費のオーバヘッドを抑えることができたことを示しています．
-コンフィグラビリティ評価を冒頭におき，主張したい点が分かりやすいように変更しました．
+productivityに関する評価(configurability)の節を新規に追加し，主張したい点が分かりやすいように変更しました．
+execution timeとmemory consumptionの評価は，提案フレームワークを用いたオーバヘッドが小さいことを示しています．
+
+\begin{itembox}[|]{4.1 Improved configurability}
+As shown in Table 2, the code lines for modification were measured to demonstrate the improved configurability.
+This demonstrated the ability to change the composition of the protocol stack with a small workload, confirming that the proposed framework improves the configurability.
+\end{itembox}\\
 
@@
 提案すべきは，「IoTデバイス向けのmrubyプラットフォーム」とし，それを実現するためにTINET+TECSとTLSF+TECSの２つの機能を組み込むという表現に修正を行いました(AbstractおよびIntroduction).
-また，問題点と解決策が対応づくように，貢献部分や要件を修正・加筆しました．
+さらに，問題点と解決策が対応づくように，Introductionの貢献部分や要件(2章)を修正・加筆いたしました．
 
@@
 
-% 提案は、「IoTデバイス向けのmrubyプラットフォーム」であり、TINET+TECSとTLSF+TECSの「2つの機能を組み込んだ」とする。
-% 貢献部分に、「TINETのコンフィグラビリティを向上させる」「マルチVMを実現する」と追記する。
 \end{flushleft}
@@
         Multiple mruby programs can run in pallalel to improve producivity of software development.
-        A theread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
+        A thread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
 
@@
 
-上で述べたように，「IoTデバイス向けのmrubyプラットフォーム」を提案し，それを実現するために，２つの機能TINET+TECSとTLSF+TECSを組み込んだというストーリーにしました．
+上で述べた通り，「IoTデバイス向けのmrubyプラットフォーム」を提案し，それを実現するために，２つの機能TINET+TECSとTLSF+TECSを組み込んだというストーリーにしました．
 それに伴い，実現するための要件を加筆し，UDPの評価およびTLSF+TECSの評価を付け加えました．
@@
 
-関連研究に，提案フレームワークの利点として，速い実行時間とコンフィグラビリティ性による小さいメモリ消費の2点を加筆しました．
+提案フレームワークの利点として，速い実行時間とコンフィグラビリティ性による小さいメモリ消費の2点を関連研究に加筆いたしました．
 
 \begin{itembox}[|]{Related work}
-mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs [9].
 That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.
@@
 ご指摘ありがとうございます．
-英文校正を依頼し，表現のミスや誤字・脱字の修正を行いました．
+英文校正業者にネイティブ校正を依頼し，ご指摘頂いた点を含め，表現のミスや誤字・脱字の修正を行いました．
 \end{flushleft}
@@
 ご指摘の通り，引用を追加いたしました．
-また，IPSJ論文誌のサンプルを参考にWebの引用について修正を行いました．
+IPSJ論文誌のサンプルを参考にWebの引用について修正を行いました．
 \end{flushleft}

### 2018-02-24 ipsj/chosha.tex
Add choshasyoukai

\begin{biography}
\profile{Takuro Yamamoto}
{
received his B.E. degree from Osaka University in 2016.
His research interests include real-time and embedded systems\@.
}
\profile{Takuma Hara}
{
\@.
}
\profile{Takuya Ishikawa}
{
\@.
}
\profile{Hiroshi Oyama}
{
received Dr. Engineering degree from Gifu University in 2002.
He works at Okuma Corporation as Senior Engineer and also works at Nagoya University as Visiting Professor.
He is studying software components and programming language for embedded systems\@.
}
\profile{Hiroaki Takada}
{
is a professor at Institute of Innovation for Future Society, Nagoya University.
He is also a professor and the Executive Director of the Center for Embedded Computing Systems (NCES), the Graduate School of Informatics, Nagoya University.
He received his Ph.D. degree in Information Science from University of Tokyo in 1996.
He was a Research Associate at University of Tokyo from 1989 to 1997, and was a Lecturer and then an Associate Professor at Toyohashi University of Technology from 1998 to 2003.
His research interests include real-time operating systems, real-time scheduling theory, and embedded system design.
He is a member of ACM, IEEE, IEICE, JSSST, and JSAE\@.
}
\profile{Takuya Azumi}
{
is an Assistant Professor at the Graduate School of Engineering Science, Osaka University. 
He received his Ph.D. degree from the Graduate School of Information Science, Nagoya University.
From 2008 to 2010, he was under the research fellowship for young scientists for Japan Society for the Promotion of Science.
From 2010 to 2014, he was an Assistant Professor at the College of Information Science and Engineering, Ritsumeikan University.
His research interests include real-time operating systems and component based development.
He is a member of IEEE, ACM, IPSJ, and IEICE\@.
}

\end{biography}

### 2018-02-24 ipsj/paper.tex
Update (Finanl ver.)

@@
 {\bf Thread-safe memory allocation}
-TLSF+TECS safely runs multiple threads without exclusive control even if the threads operate in parallel.
+TLSF+TECS safely runs multiple threads without exclusive control even if the threads operate concurrently.
 To achieve this, each thread can easily set up its own heap area.
@@
 
-{\bf Requrements:} The requirements for proposing the mruby platform for IoT devices are defined as follows.
+{\bf Requrements:} The requirements of the proposed mruby platform for IoT devices are defined as follows.
 \begin{description}
@@
 
-A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig.
-\ref{src:DynamicCDLcode}).
+A CEP component has two call ports: the cRepSelector port, which connects to the eRepSelector port of tRepSelector cell, and the cREP4 port, which connects to either of the tREP cells (Lines 11--13 in Fig.\ref{src:DynamicCDLcode}).
 The cREP port is defined using {\it [dynamic]} to identify the call port used to dynamically switch the components.
@@
 
-As illustrated in Fig. \ref{fig:TLSF}, the TLSF algorithm classifies memory blocks into two stages and searches for a memory block that optimally lines up with the requested memory size.
+As illustrated in Fig.\ref{fig:TLSF}, the TLSF algorithm classifies memory blocks into two stages and searches for a memory block that optimally lines up with the requested memory size.
 Particularly, consider the case in which a request to dynamically allocate 98 bytes is made via $malloc(98)$.
@@
 
-In Fig. \ref{src:TLSFSignature}, we summarize the signature used by the allocator for dynamic memory management.
+In Fig.\ref{src:TLSFSignature}, we summarize the signature used by the allocator for dynamic memory management.
 Particularly, this component defines the memory pool initialization function {\it initializeMemoryPool()}, memory allocation functions {\it calloc()}, {\it malloc()}, and {\it realloc()}, and the memory release function {\it free()}.
@@
 
-Next, Fig. \ref{fig:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
+Next, Fig.\ref{fig:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
 Here, entry port {\it eMalloc} is connected to all components that perform memory management including $malloc()$ and $free()$.
@@
 
-Next, Fig.
-\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.
-\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Next, Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
 Here, two sets of task components and TLSF components are combined.
-Further, each memory pool size can be configured as a variable (lines 5 and 11 in Fig. \ref{src:TLSFBuild}).
-Fig. \ref{src:TLSFC} presents the code that actually calls functions of the TLSF memory allocator component.
+Further, each memory pool size can be configured as a variable (lines 5 and 11 in Fig.\ref{src:TLSFBuild}).
+Fig.\ref{src:TLSFC} presents the code that actually calls functions of the TLSF memory allocator component.
 The use part shows a function in which the RiteVM allocates memory within the mruby on TECS framework\cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, which we introduced in Section \ref{sec:mrubyonTECS} above.
@@
 Here, as a RiteVM allocates and deallocates memory at high frequencies, memory contention quickly occurs when multiple RiteVMs are instantiated.
-Note that the TLSF components are connected to the RiteVMs to ensure that each component has its own heap area within each RiteVM, as illustrated in Fig. \ref{fig:UseCase_mruby}.
+Note that the TLSF components are connected to the RiteVMs to ensure that each component has its own heap area within each RiteVM, as illustrated in Fig.\ref{fig:UseCase_mruby}.
 Since each TLSF component maintains its own memory pool, multiple RiteVMs can be executed without the possibility of any memory contention.
-In Fig.
-\ref{fig:UseCase_mruby}, we observe that the first RiteVM has a heap area of 1 MB (i.e., 1024 $\times$ 1024 bytes) and the second RiteVM has a heap area of 2 MB (i.e., 2 $\times$ 1024 $\times$ 1024 bytes).
-As illustrated in Fig. \ref{fig:UseCase_mruby}, it is easy to configure different-sized heap areas for each RiteVM.
+In Fig.\ref{fig:UseCase_mruby}, we observe that the first RiteVM has a heap area of 1 MB (i.e., 1024 $\times$ 1024 bytes) and the second RiteVM has a heap area of 2 MB (i.e., 2 $\times$ 1024 $\times$ 1024 bytes).
+As illustrated in Fig.\ref{fig:UseCase_mruby}, it is easy to configure different-sized heap areas for each RiteVM.
 Further, each RiteVM performs incremental garbage collection (GC), and a RiteVM that has started GC does not disturb the execution of other RiteVMs in its GC execution.
@@
 The TLSF memory allocator can execute at the same speed as that of the fixed-size memory allocator that TOPPERS/ASP3 supports as standard; further, the TLSF memory allocator can improve memory efficiency.
-As illustrated in Fig. \ref{fig:UseCase_TINET}, the fixed-size memory allocator prepares memory pools of different sizes and selects a memory pool whenever it is necessary.
+As illustrated in Fig.\ref{fig:UseCase_TINET}, the fixed-size memory allocator prepares memory pools of different sizes and selects a memory pool whenever it is necessary.
 Conversely, TLSF+TECS efficiently manages memory without the need to select a memory pool.
@@
 In the proposed framework, applications can call TINET functions, such as specific TCP- and UDP-related functions, from mruby programs because the mruby-TECS bridge automatically generates the code to link mruby and C.
-Fig. \ref{src:mruby} shows an example of mruby program that transmits the value acquired from the sensor to another device or a server.
+Fig.\ref{src:mruby} shows an example of mruby program that transmits the value acquired from the sensor to another device or a server.
 In general, mruby makes it easier to develop applications than using C with the existing TINET.
@@
 For a simple application, typically only a few functions are used, with numerous unused functions.
-As an example, the application code shown in Fig. \ref{src:mruby} only uses a function to send data via TCP.
+As an example, the application code shown in Fig.\ref{src:mruby} only uses a function to send data via TCP.
 The proposed framework incorporates TINET+TECS and can easily customize the TCP/IP protocol stack by removing functions, such as UDP functions, functions that support only IPv4, or TCP receiving functions.
@@
 
-\subsection{Performance of TINET+TECS}
+\subsection{Improved configurability}
 
@@
 
-Next, to demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.
-
+\subsection{Performance of TINET+TECS}
+
+To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET.
+The results with TCP are shown in Fig.\ref{fig:EvaluationOfExecutionTime}.
 The {\it tcp\_snd\_dat} and {\it tcp\_rcv\_dat} APIs were used in the evaluation to, respectively, send and receive TCP data.
 For {\it tcp\_snd\_dat}, we measured the executing time starting from the API call through the application until the return of the processing result.
-In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.
-\ref{fig:ComponentProtocolStack}.
+In TINET+TECS, this process is performed in the order tApplication, tTCPCEP, tTCPOutputTaskBody, tIPv4Output, tEthernetOutput, tArp, tEthernetOutputTaskBody, and tIfMbed, as shown in Fig.\ref{fig:ComponentProtocolStack}.
 For {\it tcp\_rcv\_dat}, we measured the execution time from the data receipt in the LAN driver until data acquisition in the application.
-In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig. \ref{fig:ComponentProtocolStack}.
+In TINET+TECS, the process is performed in the order tIfMbed, tEthernetInputTaskBody, tIPv4Input, tTCPInput, tTCPCEP, and tApplication, as shown in Fig.\ref{fig:ComponentProtocolStack}.
 The execution time of TINET+TECS is close to that of TINET, with an overhead of about 3 us.
+Conversely, we evaluated the execution times with UDP as shown in Fig.\ref{fig:EvaluationOfExecutionTimeUDP}.
+TINET+TECS can run at the same speed as TINET; therefore, the overheads of TINET+TECS are low.
 As the use of the {\it send/receive} specifier enables accessing of the buffer address without data copying, the componentization overhead does not affect the execution time.
@@
     \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
-    \caption{Execution times of TINET and TINET+TECS}
+    \caption{Execution times of TINET and TINET+TECS with TCP}
     \label{fig:EvaluationOfExecutionTime}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTimeUDP.pdf}
+    \caption{Execution times of TINET and TINET+TECS with UDP}
+    \label{fig:EvaluationOfExecutionTimeUDP}
 \end{figure}
@@
     \caption{Memory consumption of TINET and TINET+TECS}
+    {\tabcolsep = 1mm
     \begin{tabular}{c|r|r|r|r}
@@
         TINET                  &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
-        TINET+TECS  &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+        TINET+TECS (TCP)       &   169.48 KB  &  5.37 KB &  149.01 KB &  323.96 KB \\
+        TINET+TECS (UDP)       &   169.26 KB  &  5.37 KB &  149.04 KB &  323.77 KB \\
+        TINET+TECS (TCP+UDP)   &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
         \hline
@@
     \end{tabular}
+    }
     \label{tab:EvaluationOfMemoryConsumption}
@@
 Memory consumption without and with TECS dynamic connection was then evaluated.
-As shown in the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
+As shown in the left of Fig.\ref{fig:ComparisonOfDynamicConnection}, each CEP component should be statically connected to all REP components if the dynamic connection is not used.
 As the number of REPs increases, additional call ports of CEP are required, in turn increasing the consumption of memory. 
-The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right paneof Fig.
-\ref{fig:ComparisonOfDynamicConnection}.
+The dynamic connection reduces memory consumption because only one CEP-to-REP call port is required per CEP, as illustrated with red lines in the right paneof Fig.\ref{fig:ComparisonOfDynamicConnection}.
 Even if the number of REPs increases, additional call ports can be joined through the selector, instead of the CEPs.
@@
 As the number of CEPs and REPs increases, the amount of CDL code lines to be added increases.
-In the left of Fig. \ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig. \ref{src:ComparisonOfCDL}. 
-In the right of Fig. \ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig. \ref{src:ComparisonOfCDL}. 
+In the left of Fig.\ref{fig:ComparisonOfDynamicConnection}, each CEP connects all REPs as shown in the upper of Fig.\ref{src:ComparisonOfCDL}. 
+In the right of Fig.\ref{fig:ComparisonOfDynamicConnection}, a CEP dynamically connects an REP, and only the selector connects all REPs as shown in the lower of Fig.\ref{src:ComparisonOfCDL}. 
 It is effective for software that uses many ports because the difference spreads as the number of CEPs and REPs increases.
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
+    \caption{Memory usage of RiteVMs with TLSF+TECS}
+    \label{fig:EvaluationOfTLSFStatistics}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=8cm,clip]{figure/EvaluationOfMemoryUsageWithExclusiveContorol.pdf}
+    \caption{Memory usage of RiteVMs with exclusive control}
+    \label{fig:EvaluationOfMemoryUsageWithExclusiveContorol}
+\end{figure}
+
 \subsection{Memory usage of RiteVMs by TLSF+TECS}
 
-The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control in parallel because each TLSF component holds its own heap area.
+The proposed dynamic memory allocator, TLSF+TECS, executes multiple tasks without exclusive control concurrently because each TLSF component holds its own heap area.
 The TLSF+TECS framework provides functionality to acquire statistical information describing dynamic memory usage.
@@
 
-Fig. \ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of two RiteVMs, with presented data acquired from the statistical information available via the TLSF+TECS framework.
+Fig.\ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of two RiteVMs, with presented data acquired from the statistical information available via the TLSF+TECS framework.
 From the figure, we observe that when the RiteVM are first activated, a large amount of memory is allocated for each RiteVM and initialization are performed within one second.
@@
 Here, an application that allocates tens of KB of memory runs on RiteVM 1 and an application that allocates hundreds of KB of memory runs on RiteVM 2.
-Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol} shows the memory usage when two RiteVMs are executed in one heap area with exclusive control.
-In Fig.
-\ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig.
-\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased due to exclusive control.
+Fig.\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol} shows the memory usage when two RiteVMs are executed in one heap area with exclusive control.
+In Fig.\ref{fig:EvaluationOfDynamicConnection}, two applications are finished at 10.837 s, and in Fig.\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, they are finished at 10.877 s, which demonstrates that the execution time of the applications has increased due to exclusive control.
 In addition to the overhead of execution time, a RiteVM is not affected by other RiteVMs since TLSF+TECS keeps heap area independently.
-GC on a RiteVM is performed periodically; however, there is a part that GC is not performed periodically in RiteVM 1 of Fig. \ref{fig:EvaluationOfExecutionTime}.
-In Fig. \ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, two RiteVMs share one heap area; therefore, RiteVM 2 is affected by RiteVM 1.
-On the other hand, in Fig. \ref{fig:EvaluationOfTLSFStatistics}, RiteVM 2 is not affected by RiteVM 1.
+GC on a RiteVM is performed periodically; however, there is a part that GC is not performed periodically in RiteVM 1 of Fig.\ref{fig:EvaluationOfExecutionTime}.
+In Fig.\ref{fig:EvaluationOfMemoryUsageWithExclusiveContorol}, two RiteVMs share one heap area; therefore, RiteVM 2 is affected by RiteVM 1.
+On the other hand, in Fig.\ref{fig:EvaluationOfTLSFStatistics}, RiteVM 2 is not affected by RiteVM 1.
 
@@
 Using the proposed environment here proves useful for detecting bugs related to memory, which in practice can be extremely difficult to detect.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/EvaluationOfTLSFStatistics.pdf}
-    \caption{Memory usage of RiteVMs with TLSF+TECS}
-    \label{fig:EvaluationOfTLSFStatistics}
-\end{figure}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=8cm,clip]{figure/EvaluationOfMemoryUsageWithExclusiveContorol.pdf}
-    \caption{Memory usage of RiteVMs with exclusive control}
-    \label{fig:EvaluationOfMemoryUsageWithExclusiveContorol}
-\end{figure}
 
@@
 Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
-mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
+mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs \cite{par:mrubyonTECS}.
 That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.
@@
 \bibliography{ref}
+
+% \input{chosha}
 

### 2018-02-24 ipsj/reply_letter/paper.tex
Fix to 'highlighted'

@@
 We have attached the last paper review and revised paper in our reply letter.
-In the revised paper, newly added and modified sentences are written in the bold and red colored font so that the reviewers can easily find them.
+In the revised paper, newly added and modified sentences are highlighted so that the reviewers can easily find them.
 We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.
@@
 \begin{itembox}[|]{4.2 Performance of TINET+TECS}
+    \centering
+    {\tabcolsep = 1mm
+    \begin{tabular}{c|r|r|r|r}
+        \hline\hline
+                               &   text       &  data    &   bss      &  total     \\ \hline
+        TINET                  &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
+        TINET+TECS (TCP)       &   169.48 KB  &  5.37 KB &  149.01 KB &  323.96 KB \\
+        TINET+TECS (UDP)       &   169.26 KB  &  5.37 KB &  149.04 KB &  323.77 KB \\
+        TINET+TECS (TCP+UDP)   &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
+        \hline
+        \multicolumn{5}{r}{Including the application and kernel objects}
+    \end{tabular}
+    }
 \end{itembox}\\

### 2018-03-05 ipsj/chosha.tex
Update chosha

@@
 {
-\@.
+received his M.S. degree in Information Science from Nagoya University in 2013.
+His research interests include embedded component technology\@.
 }
@@
 {
-\@.
+received his Ph.D. degree in Information Science from Nagoya University in 2014.
+His research interests include realtime scheduling theory, realtime operating system, and embedded component technology\@.
 }
@@
 {
-is a professor at Institute of Innovation for Future Society, Nagoya University.
+is a professor at Institutes of Innovation for Future Society, Nagoya University.
 He is also a professor and the Executive Director of the Center for Embedded Computing Systems (NCES), the Graduate School of Informatics, Nagoya University.

### 2018-05-15 ipsj/chosha.tex
Final ver.

@@
 {
-is an Assistant Professor at the Graduate School of Engineering Science, Osaka University. 
+is an Associate Professor at the Graduate School of Science and Engineering, Saitama University.
 He received his Ph.D. degree from the Graduate School of Information Science, Nagoya University. 
@@
 From 2010 to 2014, he was an Assistant Professor at the College of Information Science and Engineering, Ritsumeikan University. 
-His research interests include real-time operating systems and component based development.
+From 2014 to 2018, he was an Assistant Professor at the Graduate School of Engineering Science, Osaka University. 
+His research interests include real-time operating systems and component-based development.
 He is a member of IEEE, ACM, IPSJ, and IEICE\@.

### 2018-05-15 ipsj/paper.tex
Remove dates
Update chosha
Submitted ver.
Final ver.

@@
 
-\setcounter{volume}{22}% vol22=2014
-\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
-\setcounter{page}{1}
-
-\received{2014}{3}{4}
+% \setcounter{volume}{22}% vol22=2014
+% \setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
+% \setcounter{page}{1}
+
+% \received{2014}{3}{4}
 %\rereceived{2011}{10}{1}   % optional
 %\rerereceived{2011}{10}{31} % optional
-\accepted{2014}{8}{1}
+% \accepted{2014}{8}{1}
 
@@
 \affiliate{OKUMA}{OKUMA Corporation}
+\affiliate{SAITAMA}{Graduate School of Science and Engineering, Saitama University}
 
@@
 \author{Hiroaki Takada}{NAGOYA}
-\author{Takuya Azumi}{OSAKA}
+\author{Takuya Azumi}{SAITAMA}
 
@@
 In embedded network software running on embedded systems within the Internet of Things (IoT), high levels of runtime efficiency and user productivity are required.
-As an approach to improve the producivity of software development, the mruby on TOPPERS embedded component system (TECS) framework has been proposed; note that mruby on TECS framework employs a scripting language (i.e., a lightweight Ruby implementation) and supports component-based development.
+As an approach to improve the productivity of software development, the mruby on TOPPERS embedded component system (TECS) framework has been proposed; note that mruby on TECS framework employs a scripting language (i.e., a lightweight Ruby implementation) and supports component-based development.
 In this paper, we propose an extended mruby on TECS framework for its application in developing software for IoT devices, including sensors and actuators.
@@
 Next, Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
-In Section \ref{sec:Evaluation}, we provides a detailed evaluation of the proposed framework.
+In Section \ref{sec:Evaluation}, we provide a detailed evaluation of the proposed framework.
 Finally, related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.
@@
     \item[R1:]
-        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for producivity since the network function is essential to the IoT systems.
+        TCP/IP functions can be utilized from mruby programs and the protocol stack can be easily configured for productivity since the network function is essential to the IoT systems.
 
@@
 
-Next, Fig.\ref{fig:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
+Next, Fig.\ref{src:TLSFCelltype} shows the celltype description for the TLSF memory allocator component.
 Here, entry port {\it eMalloc} is connected to all components that perform memory management including $malloc()$ and $free()$.
@@
 
-% \input{chosha}
+\input{chosha}
 

### 2018-05-27 ipsj/chosha.tex
Final submit

@@
 {
-received his Ph.D. degree in Information Science from Nagoya University in 2014.
-His research interests include realtime scheduling theory, realtime operating system, and embedded component technology\@.
+received his Ph.D. degree in information science from Nagoya University in 2013.
+He was a researcher and then a designated assistant professor at the Center for Embedded Computing Systems, Nagoya University from 2014 to 2016.
+His research interests include real-time scheduling theory, real-time operating systems, and embedded software platform\@.
 }
+
 \profile{Hiroshi Oyama}
 {
-received Dr. Engineering degree from Gifu University in 2002.
+received his Dr. Engineering degree from Gifu University in 2002.
 He works at Okuma Corporation as Senior Engineer and also works at Nagoya University as Visiting Professor.

### 2018-05-27 ipsj/paper.tex
Final submit

@@
 The experimental results of the comparison between TINET+TECS and the original TINET show that execution time and memory consumption overhead are both reduced; further, we conclude that configurability is improved.
-Finally, the TLSF+TECS function which obtains and report statistical information regarding mruby's virtual machine (VM) memory usage, helps developers debug and verify their embedded IoT systems.
+Finally, the TLSF+TECS function which obtains and reports statistical information regarding mruby's virtual machine (VM) memory usage, helps developers debug and verify their embedded IoT systems.
 
@@
     \item[R2:]
-        Multiple mruby programs can run concurrently to improve productivity of software development.
+        Multiple mruby programs can run concurrently to improve the productivity of software development.
         A thread-safe memory allocator is required to prevent the multiple mruby tasks from conflicting their memory.
@@
 TECS statically performs component deployment and composition.
-Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
-TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.
+Consequently, connecting components does not incur significant overheads and memory requirements can be reduced.
+TECS can be implemented in C, and demonstrates various features such as source level portability and fine-grained components.
 
@@
 mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
-This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.
+This framework integrates two technologies, mruby and TECS, and enables the development of embedded software using a script language without slowing down the execution time.
 
@@
 % The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
-Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
+Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
 TECS components support various embedded drivers such as motor and sensor drivers.
@@
 The left side of BridgeMotor belongs to the mruby program.
-The right side of BridgeMotor belongs to TECS component.
+The right side of BridgeMotor belongs to the TECS component.
 
@@
 The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
-The generated mruby-TECS bridge supports registration of classes and methods for mruby.
+The generated mruby-TECS bridge supports the registration of classes and methods for mruby.
 Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
@@
 TINET+TECS is a component-based TCP/IP protocol stack comprised in the proposed framework, and it compensates for the original TINET's weak point that it is hard to maintain, extend, and analyze the software due to many complex source codes and improves the configurability.
-TLSF+TECS which is a component-based dynamic memory allocator is used for memory management of RiteVMs and TCP/IP buffers in the proposed framework.
+TLSF+TECS which is a component-based dynamic memory allocator is used for the memory management of RiteVMs and TCP/IP buffers in the proposed framework.
 Since each TLSF component maintains its own heap area, TLSF+TECS allows concurrent operation without exclusive control while improving the efficiency of memory consumption, which is the advantage of TLSF.
@@
 TINET has been released as an open-source tool.
-To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports the functions such as minimum copy frequency, elimination of dynamic memory control, asynchronous interfacing, error detailing per API.
+To satisfy restrictions for embedded systems in terms of, for example, memory capacity, size, and power consumption, TINET supports functions such as minimum copy frequency, elimination of dynamic memory control, asynchronous interfacing, error detailing per API.
 
@@
 A memory area for sending/receiving data in the protocol stack is allocated and released within a predetermined area.
-The memory allocator component allows for elimination of dynamic memory control in TINET+TECS by providing a requested memory area from the statically allocated memory area.
+The memory allocator component allows for the elimination of dynamic memory control in TINET+TECS by providing a requested memory area from the statically allocated memory area.
 
@@
 
-Next, Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for the simplicity.}.
+Next, Fig.\ref{src:TLSFBuild} shows the build description of the TLSF memory allocator component illustrated in Fig.\ref{fig:WithTECS}\footnote{Other call/entry ports, attributes, and valuables are actually described, but it is omitted here for simplicity.}.
 Here, two sets of task components and TLSF components are combined.
@@
 Fig.\ref{fig:EvaluationOfTLSFStatistics} shows the memory usage of two RiteVMs, with presented data acquired from the statistical information available via the TLSF+TECS framework.
-From the figure, we observe that when the RiteVM are first activated, a large amount of memory is allocated for each RiteVM and initialization are performed within one second.
+From the figure, we observe that when the RiteVM are first activated, a large amount of memory is allocated for each RiteVM and initialization is performed within one second.
 Next, the applications runs for ~10 s and the RiteVMs subsequently terminate.
@@
 
-Cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop) \cite{par:cloud-based}.
-In addition, it offers the ease deployment and evolution because the application logic is centrally located in a cloud platform.
-However, it is platform-dependent design, and restricts developers in terms of functionality such as in-network aggregation or direct node-to-node communication locally.
+A cloud-based platform reduces development efforts by providing cloud-base APIs and high-level constructs (e.g., drag-and-drop) \cite{par:cloud-based}.
+In addition, it offers easy deployment and evolution because the application logic is centrally located in a cloud platform.
+However, it is a platform-dependent design, and restricts developers in terms of functionality such as in-network aggregation or direct node-to-node communication locally.
 The cloud-based mruby framework, enzi Board \cite{url:enzi}, has been proposed.
-enzi can be developed and simulated on the Web, and developer can download and run the program on the board.
+enzi can be developed and simulated on the Web, and the developer can download and run the program on the board.
 
 To address the issues of development efforts and platform-dependent design, MDD has been proposed \cite{par:MDD}.
-MDD provides the benefits of reusable, platform-independent, extensible design, however it needs long development time to build MDD systems.
+MDD provides the benefits of reusable, platform-independent, extensible design, however it needs a long development time to build MDD systems.
 
@@
 Therefore, the proposed framework can reduce memory consumption.
-In addition, the extended mruby on TECS supports legacy code such as a motor driver.
-mruby has the same syntax as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
+In addition, the extended mruby on TECS supports a legacy code such as a motor driver.
+mruby has the same syntax as Ruby which has advantages for web application development as it uses in Rails framework \cite{url:rubyonrails}.
 
@@
 In the proposed framework, mruby programs can call TINET+TECS functions through the mruby-TECS bridge.
-Development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
+The development of software for IoT devices such as sensors and actuators will be more efficient due to the high productivity of mruby.
 
@@
 TLSF+TECS is a component-based dynamic allocator.
-Since the TLSF+TECS can hold own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
+Since the TLSF+TECS can hold its own heap area, memory contention will not occur even if memory is simultaneously allocated or released from multiple threads.
 TINET+TECS and TLSF+TECS can be applicable to various embedded systems because these frameworks are executed on TECS and not limited to mruby.
